### 2018-02-16 experiment_info.Rmd
First commit with seed set data

---
title: "Untitled"
output: html_document
---
# Intro

# Methods

The study was done with x species where all the species where consider focal species from xxx to xxx at University of New England. The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time.

Soil was mixed with sand

Hybrids where avoided

Pot size

Number of individuals (started with 24 ending with 16, lack of space)

# Results

Plots of pollen

Morphometry

Ovules

Seed set

Pollen grwoth

Pic of pollen with SEM (pollen size)

Pollen tubes and number of pollen grains

#Discussion

### 2018-02-16 seed_set_plots.R

@@ -1,0 +1,17 @@
+
+#In this script I'm going to represent the seed set of the different species 
+
+#First species Petunia integrifolia, CODE=PEIN, N=10 for each treatment, just represented the ones that we have obtained seed set
+
+
+library(reshape2)
+
+
+seed_set <- read.csv("PEIN_seed_set.csv", sep=";")
+
+seed_set <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = seed_set, na.rm= TRUE)
+
+plot(seed_set)
+
+
+

### 2018-02-19 experiment_info.Rmd
.

@@
 ---
-title: "Untitled"
+title: "Glasshouse experiment"
 output: html_document
@@
 
-The study was done with x species where all the species where consider focal species from xxx to xxx at University of New England.
+The study was done with x species (table 1) where all the species where consider focal species from xxx to xxx at University of New England.
 The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time.
+
+Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
+Had-pollination was realized with 3-4 gentle touches on the surface of the stigma.
+The mixes of pollen were realized based on the pollen counts on an eppendorf.
+Pollen on anthers was counted through Neubaeur chamber.
 
@@
 # Results
+
+```{r}
+
+```
 

### 2018-02-19 seed_set_plots.R

@@ -6,7 +6,13 @@
 
 library(reshape2)
 
+# Consider NA's as 0, I have to double check this
+
 seed_set <- read.csv("PEIN_seed_set.csv", sep=";")
+
+#Delete Cross with lost seeds
+seed_set[c(12,17,19),4] <- NA
+#Deleted
 
 mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = seed_set, na.rm= TRUE)
 
@@ -24,11 +30,12 @@ x <- 1:7
 
 plot(x, avg,
      ylim=range(c(avg-sdev, avg+sdev)),
-     pch=19, xlab="Measurements", ylab="Mean +/- SD",
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
      main="Scatter plot with std.dev error bars"
 )
 # hack: we draw arrows but with very special "arrowheads"
 arrows(x, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)
 
+axis(x, at=1:7, labels = mean_seed_seet$Treatment,cex=0.2, tick = FALSE, padj= -0.5, side = 1)
 
 

### 2018-02-19 EXPERIMENT INFO.Rmd

---
title: "Untitled"
output: html_document
---
# Intro

# Methods

The study was done with x species where all the species where consider focal species from xxx to xxx at University of New England. The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time. Soil was mixed with sand. Plants were fertilized weekly. Flowers were emasculated the day prior anthesis

Treatments were randomized on the plant. Hand-pollination was done with a toothpick with three-four gentle touches on the surface of the stigma. Pollen per anther was counted with Neubaeur chamber N=20. The different treatments applied were control, self, cross, heterospecific with 50% pollen and 100% pollen.

Hybrids where avoided

Pot size 180 mm diameter

Number of individuals (started with 24 ending with 16, lack of space)

# Results

Plots of pollen

Morphometry

Ovules

Seed set

Pollen grwoth

Pic of pollen with SEM (pollen size)

Pollen tubes and number of pollen grains

#Discussion

### 2018-02-20 experiment_info.Rmd
Updating plots

@@
 
+Flower selection criteria: Big flowers, easy/fast growing.
+
 Soil was mixed with sand
@@
 
-```{r}
+**Ovules**
+
+```{r, echo=FALSE}
+
+#OVYLE NUMBER OF THE DIFFERENT SPECIES N=15
+
+library(reshape2)
+
+# Consider NA's as 0, I have to double check this
+
+ovules <- read.csv("Ovules.csv", sep=";")
+
+#plot(ovules)
+
+mean_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = mean, data = ovules, na.rm= TRUE)
+
+colnames(mean_ovule)[2] <- "avg"
+
+sd_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = sd, data = ovules, na.rm= TRUE)
+
+colnames(sd_ovule)[2] <- "sdev"
+
+x <- 1:8
+
+plot(x, mean_ovule$avg,
+     ylim=range(c(mean_ovule$avg-sd_ovule$sdev, mean_ovule$avg+sd_ovule$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="N of Ovules")
+# hack: we draw arrows but with very special "arrowheads"
+arrows(x, mean_ovule$avg-sd_ovule$sdev, x, mean_ovule$avg+sd_ovule$sdev, length=0.05, angle=90, code=3)
+
+axis(x, at=1:8, labels = mean_ovule$Species,cex=0.2, tick = FALSE, padj= -0.5, side = 1)
+
+```
+
+**Seed set Petunia**
+
+```{r, echo=FALSE}
+library(reshape2)
+
+# Consider NA's as 0, I have to double check this
+
+seed_set <- read.csv("PEIN_seed_set.csv", sep=";")
+
+#Delete Cross with lost seeds
+seed_set[c(12,17,19),4] <- NA
+#Deleted
+
+mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = seed_set, na.rm= TRUE)
+
+mean_seed_seet$.-> avg
+
+sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = seed_set, na.rm= TRUE)
+
+sd_seed_seet$. -> sdev
+
+sdev[4] <- 0
+
+#plot(seed_set, cex.axis=0.5)
+
+x <- 1:7
+
+plot(x, avg,
+     ylim=range(c(avg-sdev, avg+sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="PEIN seed set"
+)
+# hack: we draw arrows but with very special "arrowheads"
+arrows(x, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)
+
+axis(x, at=1:7, labels = mean_seed_seet$Treatment,cex.axis=0.8, tick = FALSE, padj= -0.5, side = 1)
 
@@
 Morphometry
-
-Ovules
 

### 2018-03-13 experiment_info.Rmd
species so far
s
ideas

@@
 
+A common trend in natural ecosystems is pollinator sharing (REF).
+Therefore, pollen from different species can arrive to the stigmas of other species.
+The real impact of pollen in a natural ecosystem is still unknown.
+Nonetheless, some advances has been done with recent works where heterospecific pollen effect is evaluated (REFS).
+
 # Methods
@@
 The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time.
+
+For all the species, the day prior anthesis flowers were emasculated and then hand-pollinated next day with toothpicks with 3-4 gentle touches over the stigma surface.
+
+Table of species:
+
+**Solanaceae**
+
+SOLY "Tommy Joe"
+CAAN "California Wonder""
+PEIN "Petunia integrifolia"
+SOME "Solanum melongera"
+
+**Brassicaceae**
+
+Sinapis alba White mustard
+Brassica oleracea var. capitata
+Brassica rapa var. chinensis
+
+**Convolvulaceae**
+
+Ipomoea purpurea
+
+Possible species to include:
+
+Ipomoea aquatica
+
+I. coccinea
+
+Convolvulus sabatius
+
+Sysimbrium spp
+
+Raphanus spp
+
+Eruca sativa
 

### 2018-03-13 experiment_info.Rmd
ideas intro

@@
 
+**Paragraph 1**
 A common trend in natural ecosystems is pollinator sharing (REF).
@@
 The real impact of pollen in a natural ecosystem is still unknown.
-Nonetheless, some advances has been done with recent works where heterospecific pollen effect is evaluated (REFS).
+Nonetheless, some advances has been done with recent works where heterospecific pollen effect has been evaluated (REFS).
+
+**Paragraph 2**
+
+**Paragraph 3**
+
+**Paragraph 4**
 

### 2018-03-29 experiment_info.Rmd
ideas
a little bit of methods

@@
 **Paragraph 1**
+
 A common trend in natural ecosystems is pollinator sharing (REF).
@@
 
+We review the classic predicted traits of hterospecific pollen effect through a matrix of intereactions with heterogeneous traits.
+
 # Methods
 
-The study was done with x species (table 1) where all the species where consider focal species from xxx to xxx at University of New England.
-The rooms where temperature controlled with temperature between xxx at day time to xxx at nigth time.
+The study was conducted in a glasshouse at University of New England (Armidale, Australia).
+Rooms were temperature controlled depending on the requirements of the species.
+The species selected belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
+The criteria of species selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), easy species to grow, low structural flower complexity.
+For the purpose of the experiment all the species where consider as pollen recipient and as pollen donor (see interaction matrix, fig 2).
+Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).
 
 For all the species, the day prior anthesis flowers were emasculated and then hand-pollinated next day with toothpicks with 3-4 gentle touches over the stigma surface.
+
+Check fertiliser type: Hortico (all purpose soluble fertiliser) NPK 23: 3.95: 14
 

### 2018-05-01 Rmd/experiment_info.Rmd
New folders

--- 2018-03-29 experiment_info.Rmd
@@
 
-```{r, echo=FALSE}
-
-#OVYLE NUMBER OF THE DIFFERENT SPECIES N=15
-
-library(reshape2)
-
-# Consider NA's as 0, I have to double check this
-
-ovules <- read.csv("Ovules.csv", sep=";")
-
-#plot(ovules)
-
-mean_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = mean, data = ovules, na.rm= TRUE)
-
-colnames(mean_ovule)[2] <- "avg"
-
-sd_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = sd, data = ovules, na.rm= TRUE)
-
-colnames(sd_ovule)[2] <- "sdev"
-
-x <- 1:8
-
-plot(x, mean_ovule$avg,
-     ylim=range(c(mean_ovule$avg-sd_ovule$sdev, mean_ovule$avg+sd_ovule$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="N of Ovules")
-# hack: we draw arrows but with very special "arrowheads"
-arrows(x, mean_ovule$avg-sd_ovule$sdev, x, mean_ovule$avg+sd_ovule$sdev, length=0.05, angle=90, code=3)
-
-axis(x, at=1:8, labels = mean_ovule$Species,cex=0.2, tick = FALSE, padj= -0.5, side = 1)
-
-```
-
-**Seed set Petunia**
-
-```{r, echo=FALSE}
-library(reshape2)
-
-# Consider NA's as 0, I have to double check this
-
-seed_set <- read.csv("PEIN_seed_set.csv", sep=";")
-
-#Delete Cross with lost seeds
-seed_set[c(12,17,19),4] <- NA
-#Deleted
-
-mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = seed_set, na.rm= TRUE)
-
-mean_seed_seet$.-> avg
-
-sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = seed_set, na.rm= TRUE)
-
-sd_seed_seet$. -> sdev
-
-sdev[4] <- 0
-
-#plot(seed_set, cex.axis=0.5)
-
-x <- 1:7
-
-plot(x, avg,
-     ylim=range(c(avg-sdev, avg+sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="PEIN seed set"
-)
-# hack: we draw arrows but with very special "arrowheads"
-arrows(x, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)
-
-axis(x, at=1:7, labels = mean_seed_seet$Treatment,cex.axis=0.8, tick = FALSE, padj= -0.5, side = 1)
-
-```
-
 Plots of pollen

### 2018-05-03 Rmd/Data_visualization.Rmd
new RMD, meeting tomorrow

---
title: "Data_visualization"
output: pdf_document
---

## Ovules

```{r, warning=FALSE, echo=FALSE}
#load libraries

library(ggplot2)
library(Hmisc)
library(Formula)
#load data
d<-read.csv("Data/Ovules.csv", sep=";")

colnames(d)[1]<-"C. annuum"
colnames(d)[2]<-"S. lycopersicum"
colnames(d)[3]<-"S. melongera"
colnames(d)[4]<-"P. integrifolia"
colnames(d)[5]<-"B. oleracea"
colnames(d)[6]<-"B. rapa"
colnames(d)[7]<-"E. sativa"
colnames(d)[8]<-"S. alba"

#Reorganise data
d <- stack(d)
#Naming columns
colnames(d)[1]<-"ovules"
colnames(d)[2]<-"species"

#subset per family (solanaceae, brassicaceae, convolvulaceae)
solanaceae<-subset(d)[1:60,]
brassicaceae<-subset(d)[61:120,]

# OVULES SOLANACEAE
p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
labs(title="Solanaceae",x="", y = "Ovules")+
theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")

# OVULES BRASSICACEAE

p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
  labs(title="Brassicaceae",x="", y = "Ovules")+
  theme(plot.title = element_text(hjust = 0.5))

p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")

```

### 2018-05-03 Rmd/Data_visualization.Rmd
Ovules boxplot Markdown

@@
 
-## Ovules
+# Ovules per family, **Convolvulaceae is constant 4 or 6**
 
-```{r, warning=FALSE, echo=FALSE}
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
 #load libraries
@@
 #load data
+
+par(mfrow=c(2,1))
+
 d<-read.csv("Data/Ovules.csv", sep=";")

### 2018-05-03 Rmd/Data_visualization.Rmd
plot of pollen, finish IPAQ

@@
 ```
+
+#Pollen per anther, just one Convolvulaceae at the moment
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+library(ggplot2)
+library(forcats)
+library(Hmisc)
+library(Formula)
+
+p <- read.csv("data/Pollen.csv", sep = ";")
+
+#Deleting extra row (21)
+p <-p[-21,]
+
+#boxplot(p)
+#Reorganize data for ggplot
+p<-stack(p)
+#colnames
+colnames(p)[1]<-"pollen"
+colnames(p)[2]<-"species"
+
+all<-p
+solanaceae<-subset(p)[1:100,]
+brassicaceae<- subset(p)[101:180,]
+
+#Solanaceae
+
+p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+  labs(title="Solanaceae",x="", y = "pollen")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+
+#Brassicaceae
+
+p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+  labs(title="Brassicaceae",x="", y = "pollen")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+
+#all
+
+p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+  labs(title="All species",x="", y = "pollen")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+
+```

### 2018-05-03 Scripts/pollen.R

@@ -1,0 +1,47 @@
+library(ggplot2)
+library(forcats)
+library(Hmisc)
+library(Formula)
+
+
+p <- read.csv("data/Pollen.csv", sep = ";")
+
+#Deleting extra row (21)
+p <-p[-21,]
+
+boxplot(p)
+#Reorganize data for ggplot
+p<-stack(p)
+#colnames
+colnames(p)[1]<-"pollen"
+colnames(p)[2]<-"species"
+
+all<-p
+solanaceae<-subset(p)[1:100,]
+brassicaceae<- subset(p)[101:180,]
+
+#Solanaceae
+
+p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+  labs(title="Solanaceae",x="", y = "pollen")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+
+
+#Brassicaceae
+
+p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+  labs(title="Brassicaceae",x="", y = "pollen")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+
+#all
+
+p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+  labs(title="All species",x="", y = "pollen")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+

### 2018-05-15 Rmd/Data_visualization.Rmd
rmd

@@
 library(ggplot2)
-library(forcats)
 library(Hmisc)

### 2018-06-13 Rmd/Data_visualization.Rmd
adding pollen sizes of hydratated pollen (equatorial diameter)

@@
 library(ggplot2)
-library(Hmisc)
-library(Formula)
 #load data
@@
 library(ggplot2)
-library(Hmisc)
-library(Formula)
 

### 2018-06-13 Scripts/traits.R

@@ -170,7 +170,15 @@ tab[4,4] <- "Little fingers"
 tab[5,4] <- "Capitata"
 tab[6,4] <- "Chinensis"
 
-
+#Pollen size (um)
+#IPPU#N=3
+IPPU <- c(99.11,97.78,95.88)
+IPPU <- mean(IPPU)
+tab[10,7] <- IPPU
+#IPAQ#N=3
+IPAQ <- c(73.90,68.61,67.78)
+IPAQ <- round(mean(IPAQ),2)
+tab[9,7] <- IPAQ
 
 barplot(tab$pollen_ovule_ratio, x.axis)
 library(ggplot2)

### 2018-06-18 Rmd/Data_visualization.Rmd
adding colours to ggplot

@@
 library(ggplot2)
+library(colorspace)
+colours <- rainbow_hcl(4, start = 30, end = 300)
+
 #load data
@@
 p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "Ovules")+
+labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
 theme(plot.title = element_text(hjust = 0.5))

### 2018-06-20 Rmd/Data_visualization.Rmd
changes in ggplot

@@
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
 # OVULES BRASSICACEAE
-
 p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-  labs(title="Brassicaceae",x="", y = "Ovules")+
+labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
 theme(plot.title = element_text(hjust = 0.5))
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#all species
+#formating d, to have just the spp of interest
+
+p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=species)+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 

### 2018-06-20 Rmd/Data_visualization.Rmd
general changes for data visualization

@@
 
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=4}
 #load libraries
@@
 d<-read.csv("Data/Ovules.csv", sep=";")
-
+d<- d[,-c(9,11)]
 colnames(d)[1]<-"C. annuum"
@@
 colnames(d)[8]<-"S. alba"
+colnames(d)[9]<-"I. aquatica"
+colnames(d)[10]<-"I. purpurea"
 
@@
 p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=species)+
+labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
 theme(plot.title = element_text(hjust = 0.5))
@@
 ```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+tab <- read.csv("Data/tab.csv", sep="", header = T)
+
+p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
+  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  scale_fill_manual(values=colours)
+p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
+
+```

### 2018-06-20 Scripts/ovules.R

@@ -6,7 +6,7 @@ library(Hmisc)
 library(Formula)
 #load data
 d<-read.csv("Data/Ovules.csv", sep=";")
-
+d<- d[,-c(9,11)]
 colnames(d)[1]<-"C. annuum"
 colnames(d)[2]<-"S. lycopersicum"
 colnames(d)[3]<-"S. melongera"
@@ -15,6 +15,8 @@ colnames(d)[5]<-"B. oleracea"
 colnames(d)[6]<-"B. rapa"
 colnames(d)[7]<-"E. sativa"
 colnames(d)[8]<-"S. alba"
+colnames(d)[9]<-"I. aquatica"
+colnames(d)[10]<-"I. purpurea"
 
 
 #Reorganise data
@@ -22,6 +24,11 @@ d <- stack(d)
 #Naming columns
 colnames(d)[1]<-"ovules"
 colnames(d)[2]<-"species"
+
+family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
+
+d[,"family"] <- family
+
 
 
 #boxplot from ggplot2

### 2018-06-20 Scripts/traits.R

@@ -238,7 +238,7 @@ tab[9,7] <-  "(Les, 2017); DOI: 10.1201/9781315118116"
 tab[10,6] <- "Self-compatible"
 tab[10,7] <-  "(Smith & Rausher, 2006); DOI: 10.1111/j.1469-8137.2006.01933.x" 
 
-
+write.table(tab, file = "data/tab.csv")
 
   
 barplot(tab$pollen_ovule_ratio, x.axis)
@@ -255,6 +255,5 @@ p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), 
   geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   scale_fill_manual(values=colours)
 p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
-
 
 

### 2018-06-20 Rmd/Data_visualization.Rmd
adding family to ovules plot
working on data visualization for meeting

@@
 title: "Data_visualization"
-output: pdf_document
+output:
+      pdf_document
 ---
 
-# Ovules per family, **Convolvulaceae is constant 4 or 6**
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=4}
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
 #load libraries
@@
 par(mfrow=c(2,1))
-
 d<-read.csv("Data/Ovules.csv", sep=";")
@@
 colnames(d)[2]<-"species"
+
+family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
+
+d[,"family"] <- family
 
@@
 ```
+
+```{r echo=FALSE, out.width='80%', fig.align='center'}
+knitr::include_graphics('Images/all_species.png')
+```

### 2018-06-20 Scripts/phylogenetic_distances.R

@@ -8,3 +8,4 @@ rownames(all_species_rbcl) <- species
 all_species_rbcl<- all_species_rbcl[,-1]
 colnames(all_species_rbcl) <- species
 
+#write.csv(all_species_rbcl, file="Data/all_species_rbcl_RMD.csv")

### 2018-06-21 Rmd/Data_visualization.Rmd
Now I'm going to try to represent the data in a different way with summatory of seeds

@@
 #Solanaceae
-
 p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-  labs(title="Solanaceae",x="", y = "pollen")+
+labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
 theme(plot.title = element_text(hjust = 0.5))
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
 #Brassicaceae
-
 p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-  labs(title="Brassicaceae",x="", y = "pollen")+
+labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
 theme(plot.title = element_text(hjust = 0.5))
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
 #all
-
 p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-  labs(title="All species",x="", y = "pollen")+
+labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
 theme(plot.title = element_text(hjust = 0.5))
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
-
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 ```

### 2018-06-21 Scripts/pein_seed_set.R

@@ -17,26 +17,16 @@ sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregat
 colnames(sd_seed_seet)[2] <-"sdev"
 
 
-x <- 1:24
-
-
-plot(x, avg,
-     ylim=range(c(avg-sdev, avg+sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Scatter plot with std.dev error bars"
-)
-# add arrows
-arrows(x, avg-sdev, x, avg+sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_seed_seet$Treatment)
-axis(x, at=1:24, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, adj = 1.25,srt = 45, xpd = TRUE)
 
 #Unify mean and sd with merge
 mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
+#Removing RARA, species not considered because sterility 
+mean_sd<- mean_sd[-c(16,17),]
+
 #Order from lower to higher values the average, to plot it nicely
 mean_sd_ordered <- mean_sd[order(mean_sd$avg),] 
-
-x <- 1:24
+#ploting averages with sd
+x <- 1:22
 plot(x, mean_sd_ordered$avg,
      ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
      pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
@@ -44,8 +34,17 @@ plot(x, mean_sd_ordered$avg,
 # add arrows
 arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
 lablist.x<-as.vector(mean_sd_ordered$Treatment)
-axis(x, at=1:24, labels = FALSE)
+axis(x, at=1:22, labels = FALSE)
 text(x, par("usr")[3] - 0.2, labels = lablist.x, adj = 1.25,srt = 45, xpd = TRUE)
+
+#Now I'm going to try to represent the same data in a different way, summatory of seed set which could be more informative
+
[…]

### 2018-06-25 Rmd/Data_visualization.Rmd
preparing summatory plots
preparing Rmd file

@@
 ```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+#Preparing seed set plots, starting with Petunia
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+
+ par(mfrow=c(1,4))
+
+#read data and cleaning
+pein_seed_set <- read.csv("Data/species_seed_set/PEIN_seed_set.csv", sep=";")
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+#
+##
+###
+#PETUNIA
+###
+##
+#
+
+#Removing RARA, species not considered because sterility
+
+pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
+
+#adding the focal species, first 50%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#adding the focal species, 100%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#Order from lower to higher values the average, to plot it nicely
+pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
+pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
+pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]
+
+p <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. MELONGENA
+###
+##
+#
+
+#Taking out species that weren't used
+some_seed_set <- read.csv("Data/species_seed_set/SOME_seed_set.csv", sep=";")
+some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+
+#adding the focal species, first 50%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+some_seed_set<- some_seed_set[,-3]
+colnames(some_seed_set)[3] <- "Treatment.number"
+colnames(some_seed_set)[4] <- "Seed.production"
+some_seed_set <- rbind(some_seed_set, some_50, some_100)
+some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
+some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
+
+p <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#C. ANNUUM 
+###
+##
+#
+caan_seed_set <- read.csv("Data/species_seed_set/CAAN_seed_set.csv", sep=";")
+
+#adding the focal species, first 50%
+Species <- rep("CAAN", 10)
+Treatment <- rep("CAAN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("CAAN", 10)
+Treatment <- rep("CAAN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+caan_seed_set <- caan_seed_set[,-4]
+colnames(caan_seed_set)[1] <- "Species"
+colnames(caan_seed_set)[2] <- "Treatment"
+colnames(caan_seed_set)[3] <- "Treatment.number"
+colnames(caan_seed_set)[4] <- "Seed.production"
+caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
+caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
+caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
+
+p <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. LYCOPERSICUM
+###
+##
+#
+
+soly_seed_set <- read.csv("Data/species_seed_set/SOLY_seed_set.csv", sep=";")
+soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+soly_seed_set <- soly_seed_set[,-4]
+colnames(soly_seed_set)[1] <- "Species"
+colnames(soly_seed_set)[2] <- "Treatment"
+colnames(soly_seed_set)[3] <- "Treatment.number"
+colnames(soly_seed_set)[4] <- "Seed.production"
+soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
+soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
+soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
+
+p <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+```

### 2018-06-25 Rmd/Data_visualization.Rmd
changes

@@
 #read data and cleaning
-pein_seed_set <- read.csv("Data/species_seed_set/PEIN_seed_set.csv", sep=";")
+pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
 pein_seed_set <- pein_seed_set[-c(42,47,49),]
@@
 #Taking out species that weren't used
-some_seed_set <- read.csv("Data/species_seed_set/SOME_seed_set.csv", sep=";")
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
 some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
@@
 #
-caan_seed_set <- read.csv("Data/species_seed_set/CAAN_seed_set.csv", sep=";")
+caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
 
@@
 
-soly_seed_set <- read.csv("Data/species_seed_set/SOLY_seed_set.csv", sep=";")
+soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
 soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

### 2018-06-25 Rmd/Data_visualization.Rmd
last visualization changes

@@
 library(colorspace)
+library(gridExtra)
+
 colours <- rainbow_hcl(4, start = 30, end = 300)
-
 #load data
@@
 
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+\newpage
+```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
+par(mfrow=c(2,2))
+#load libraries
+library(reshape2)
+library(ggplot2)
+#read data
+pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)
+
+colnames(mean_seed_seet)[2] <-"avg"
+
+sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)
+
+colnames(sd_seed_seet)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
+#Removing RARA, species not considered because sterility 
+mean_sd<- mean_sd[-c(16,17),]
+
+merge_1 <- data.frame(mean_sd, stringsAsFactors = F)
+
+merge_1$Treatment<- as.character(merge_1$Treatment)
+pein <- c("PEIN", NA, NA)
+
+str(merge_1)
+mean_sd_1 <- rbind(merge_1,pein)
+
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered <- mean_sd[order(mean_sd$avg),]
+
+mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]
+
+#ploting averages with sd
+x <- 1:22
+plot(x, mean_sd_ordered$avg,
+     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Petunia integrifolia")
+# add arrows
+arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered$Treatment)
+axis(x, at=1:22, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
+mean_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = some_seed_set, na.rm= TRUE)
+colnames(mean_seed_seet_some)[2] <-"avg"
+sd_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = some_seed_set, na.rm= TRUE)
+colnames(sd_seed_seet_some)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd_some <- merge(mean_seed_seet_some,sd_seed_seet_some, by="Treatment")
+#Delete RARA rows, species not included because sterility
+mean_sd_some <- mean_sd_some[-c(8,9,20),]
+
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered_some <- mean_sd_some[order(mean_sd_some$avg),]
+
+x <- 1:22
+plot(x, mean_sd_ordered_some$avg,
+     ylim=range(c(mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Solanum melongena")
+# add arrows
+arrows(x, mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, x, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered_some$Treatment)
+axis(x, at=1:22, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
+mean_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = caan_seed_set, na.rm= TRUE)
+colnames(mean_seed_seet_caan)[2] <-"avg"
+sd_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = caan_seed_set, na.rm= TRUE)
+colnames(sd_seed_seet_caan)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd_caan <- merge(mean_seed_seet_caan,sd_seed_seet_caan, by="treatment")
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered_caan <- mean_sd_caan[order(mean_sd_caan$avg),]
+
+x <- 1:22
+plot(x, mean_sd_ordered_caan$avg,
+     ylim=range(c(mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Capsicum annuum")
+# add arrows
+arrows(x, mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, x, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered_caan$treatment)
+axis(x, at=1:22, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
+mean_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = soly_seed_set, na.rm= TRUE)
+colnames(mean_seed_seet_soly)[2] <-"avg"
+sd_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = soly_seed_set, na.rm= TRUE)
+colnames(sd_seed_seet_soly)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd_soly <- merge(mean_seed_seet_soly,sd_seed_seet_soly, by="Treatment")
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered_soly <- mean_sd_soly[order(mean_sd_soly$avg),]
+
+x <- 1:26
+plot(x, mean_sd_ordered_soly$avg,
+     ylim=range(c(mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Solanum lycopersicum")
+# add arrows
+arrows(x, mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, x, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered_soly$Treatment)
+axis(x, at=1:26, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+```
+
+\newpage
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',fig.align='center',out.width='70%'}
 #Preparing seed set plots, starting with Petunia
@@
 library(dplyr)
-
- par(mfrow=c(1,4))
+library(ggplot2)
+library(grid)
+library(gridExtra)
+library(egg)
+library(gtable)
 
@@
 
-p <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+plot1 <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
   labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
@@
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+plot1 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-p <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+plot2 <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
   labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
@@
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+plot2 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-p <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+plot3 <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
   labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
@@
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+plot3 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-p <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+plot4 <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
   labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
@@
 
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+plot4 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 

### 2018-07-11 Rmd/ms_draft.Rmd
changes

--- 2018-03-29 experiment_info.Rmd
@@
 
-**Paragraph 1**
+**Paragraph 1** Introduction to the topic
 
-A common trend in natural ecosystems is pollinator sharing (REF).
-Therefore, pollen from different species can arrive to the stigmas of other species.
-The real impact of pollen in a natural ecosystem is still unknown.
-Nonetheless, some advances has been done with recent works where heterospecific pollen effect has been evaluated (REFS).
+Flowerings plants depend highly on animal vectors to be pollinated (Ollerton et al, 2011) and their coevolutive history has lead to a great diversity of floral structures (Refs).
+Generally these different plant species coexist together in natural ecosystems where they compete for pollinators (Refs) or facilitate pollinator's visitation.
+In addition, pollinator sharing is a common feature in natural ecosystems (Ref) and therefore plant species will recieve conspecific pollen but also heterospecific pollen or interspecific pollen (HP or IP).
 
-**Paragraph 2**
+Vamosi species limited by pollen
+
+**Paragraph 2** Research on the topic so far
 
@@
 
-The study was conducted in a glasshouse at University of New England (Armidale, Australia).
-Rooms were temperature controlled depending on the requirements of the species.
-The species selected belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
-The criteria of species selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), easy species to grow, low structural flower complexity.
+The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018.
+Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences.
+The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
+The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), low structural flower complexity and fast life cycle.
 For the purpose of the experiment all the species where consider as pollen recipient and as pollen donor (see interaction matrix, fig 2).
@@
 
+**Table 1**
+```{r}
+
+```
+
+**Hand-pollination**
+
+Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
+Had-pollination was realized with 3-4 gentle touches on the surface of the stigma.
+The mixes of pollen were performed based on the pollen counts on an eppendorf.
+Pollen on anthers was counted through Neubaeur chamber.
+
 For all the species, the day prior anthesis flowers were emasculated and then hand-pollinated next day with toothpicks with 3-4 gentle touches over the stigma surface.
-
-Check fertiliser type: Hortico (all purpose soluble fertiliser) NPK 23: 3.95: 14
-
-Table of species:
 

### 2018-07-31 Rmd/ms_draft.Rmd
message
last changes

@@
 Generally these different plant species coexist together in natural ecosystems where they compete for pollinators (Refs) or facilitate pollinator's visitation.
-In addition, pollinator sharing is a common feature in natural ecosystems (Ref) and therefore plant species will recieve conspecific pollen but also heterospecific pollen or interspecific pollen (HP or IP).
+In addition, pollinator sharing is a common feature in natural ecosystems (Ref) and therefore plant species will recieve conspecific pollen but also heterospecific pollen (HP).
+
+**Paragraph 2** Research on the topic so far
 
 Vamosi species limited by pollen
-
-**Paragraph 2** Research on the topic so far
 

### 2018-07-31 Scripts/petunia_ggplot.R

@@ -1,0 +1,85 @@
+#Preparing seed set plots, starting with Petunia
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+
+#read data and cleaning
+pein_seed_set <- read.csv("Data/species_seed_set/PEIN_seed_set.csv", sep=";")
+#removing samples where seeds got lost, first ones of the experiment
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+#
+##
+###
+#PETUNIA
+###
+##
+#
+#Removing RARA, species not considered because sterility 
+
+pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
+
+#adding the focal species, first 50%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#adding the focal species, 100%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#Order from lower to higher values the average, to plot it nicely
+pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
+pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
+pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+
+library(stringr)
+pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
+pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
+colnames(pein_seed_set_div)=c("non_focal","percentage")
+pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
+pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
[…]

### 2018-08-02 Rmd/Data_visualization.Rmd
chnages

@@
 ```
+
+\newpage
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',out.width='55%'}
+#Preparing seed set plots, starting with Petunia
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+par(mfrow=c(2,3))
+
+#read data and cleaning
+pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
+#removing samples where seeds got lost, first ones of the experiment
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+#
+##
+###
+#PETUNIA
+###
+##
+#
+#Removing RARA, species not considered because sterility
+
+pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
+
+#adding the focal species, first 50%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#adding the focal species, 100%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#Order from lower to higher values the average, to plot it nicely
+pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
+pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
+pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
+pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
+colnames(pein_seed_set_div)=c("non_focal","percentage")
+pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
+pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
+pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
+pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
+pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]
+
+pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
+                           pein_seed_set_flower)
+#deleting extra columns used for data formating
+pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
+#changing non_focal species name
+pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Colur per family
+
+p <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#C. ANNUUM 
+###
+##
+#
+caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
+
+#adding the focal species, first 50%
+Species <- rep("CAAN", 10)
+Treatment <- rep("CAAN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("CAAN", 10)
+Treatment <- rep("CAAN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+caan_seed_set <- caan_seed_set[,-4]
+colnames(caan_seed_set)[1] <- "Species"
+colnames(caan_seed_set)[2] <- "Treatment"
+colnames(caan_seed_set)[3] <- "Treatment.number"
+colnames(caan_seed_set)[4] <- "Seed.production"
+caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
+caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
+caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
+caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
+colnames(caan_seed_set_div)=c("non_focal","percentage")
+caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
+caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
+caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
+caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
+caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]
+
+caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
+                           caan_seed_set_flower)
+#deleting extra columns used for data formating
+caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA
+
+#changing non_focal species name
+caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. LYCOPERSICUM
+###
+##
+#
+
+soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
+soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+soly_seed_set <- soly_seed_set[,-4]
+colnames(soly_seed_set)[1] <- "Species"
+colnames(soly_seed_set)[2] <- "Treatment"
+colnames(soly_seed_set)[3] <- "Treatment.number"
+colnames(soly_seed_set)[4] <- "Seed.production"
+soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
+soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
+soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
+soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
+colnames(soly_seed_set_div)=c("non_focal","percentage")
+soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
+soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
+soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
+soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
+soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]
+
+soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
+                           soly_seed_set_flower)
+#deleting extra columns used for data formating
+soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA
+
+#changing non_focal species name
+soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. MELONGENA
+###
+##
+#
+
+#Taking out species that weren't used
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
+some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+
+#adding the focal species, first 50%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+some_seed_set<- some_seed_set[,-3]
+colnames(some_seed_set)[3] <- "Treatment.number"
+colnames(some_seed_set)[4] <- "Seed.production"
+some_seed_set <- rbind(some_seed_set, some_50, some_100)
+some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
+some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
+some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
+colnames(some_seed_set_div)=c("non_focal","percentage")
+some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
+some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
+some_seed_set_self <- filter(some_seed_set_bind, non_focal %in% c("SELF"))
+some_seed_set_control <- filter(some_seed_set_bind, non_focal %in% c("CONTROL"))
+some_seed_set_flower <- filter(some_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CROSS"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("SELF"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CONTROL"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("FLOWER"),]
+
+some_seed_set_final<-rbind(some_seed_set_bind,some_seed_set_cross, some_seed_set_self, some_seed_set_control,
+                           some_seed_set_flower)
+#deleting extra columns used for data formating
+some_seed_set_final=some_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+some_seed_set_final[some_seed_set_final$Treatment==c("SOME 50%"),4] <- NA
+
+#changing non_focal species name
+some_seed_set_final$Treatment=as.character(some_seed_set_final$Treatment)
+some_seed_set_final$Family[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#B. OLERACEA
+###
+##
+#
+
+brol_seed_set <- read.csv("Data/BROL_seed_set.csv", sep=";")
+brol_seed_set <- filter(brol_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("BROL", 10)
+Treatment <- rep("BROL 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+brol_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("BROL", 10)
+Treatment <- rep("BROL 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+brol_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+colnames(brol_seed_set)[1] <- "Species"
+colnames(brol_seed_set)[2] <- "Treatment"
+colnames(brol_seed_set)[3] <- "Treatment.number"
+colnames(brol_seed_set)[4] <- "Seed.production"
+brol_seed_set <- rbind(brol_seed_set, brol_50, brol_100)
+brol_seed_set$Treatment<- as.character(brol_seed_set$Treatment)
+brol_seed_set <- brol_seed_set[order(brol_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+brol_seed_set_div <- str_split_fixed(as.character(brol_seed_set$Treatment), " ", 2)
+brol_seed_set_div <- data.frame(brol_seed_set_div, stringsAsFactors = F)
+colnames(brol_seed_set_div)=c("non_focal","percentage")
+brol_seed_set_bind <- cbind(brol_seed_set,brol_seed_set_div)
+brol_seed_set_bind <- filter(brol_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(brol_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
+brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
+brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
+brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
+brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
+brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
+brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]
+
+brol_seed_set_final<-rbind(brol_seed_set_bind,brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
+                           brol_seed_set_flower)
+#deleting extra columns used for data formating
+brol_seed_set_final=brol_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+brol_seed_set_final[brol_seed_set_final$Treatment==c("BROL 50%"),4] <- NA
+
+#changing non_focal species name
+brol_seed_set_final$Treatment=as.character(brol_seed_set_final$Treatment)
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#B. RAPA
+###
+##
+#
+
+brra_seed_set <- read.csv("Data/BRRA_seed_set.csv", sep=";")
+brra_seed_set <- filter(brra_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("BRRA", 10)
+Treatment <- rep("BRRA 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+brra_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("BRRA", 10)
+Treatment <- rep("BRRA 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+brra_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+colnames(brra_seed_set)[1] <- "Species"
+colnames(brra_seed_set)[2] <- "Treatment"
+colnames(brra_seed_set)[3] <- "Treatment.number"
+colnames(brra_seed_set)[4] <- "Seed.production"
+brra_seed_set <- rbind(brra_seed_set, brra_50, brra_100)
+brra_seed_set$Treatment<- as.character(brra_seed_set$Treatment)
+brra_seed_set <- brra_seed_set[order(brra_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+brra_seed_set_div <- str_split_fixed(as.character(brra_seed_set$Treatment), " ", 2)
+brra_seed_set_div <- data.frame(brra_seed_set_div, stringsAsFactors = F)
+colnames(brra_seed_set_div)=c("non_focal","percentage")
+brra_seed_set_bind <- cbind(brra_seed_set,brra_seed_set_div)
+brra_seed_set_bind <- filter(brra_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(brra_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+brra_seed_set_cross <- filter(brra_seed_set_bind, non_focal %in% c("Cross"))
+brra_seed_set_self <- filter(brra_seed_set_bind, non_focal %in% c("Self"))
+brra_seed_set_control <- filter(brra_seed_set_bind, non_focal %in% c("Control"))
+brra_seed_set_flower <- filter(brra_seed_set_bind, non_focal %in% c("Flower"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Cross"),]
+brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Self"),]
+brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Control"),]
+brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Flower"),]
+
+brra_seed_set_final<-rbind(brra_seed_set_bind,brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
+                           brra_seed_set_flower)
+#deleting extra columns used for data formating
+brra_seed_set_final=brra_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+brra_seed_set_final[brra_seed_set_final$Treatment==c("BRRA 50%"),4] <- NA
+
+#changing non_focal species name
+brra_seed_set_final$Treatment=as.character(brra_seed_set_final$Treatment)
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#E. VERSICARIA
+###
+##
+#
+
+ersa_seed_set <- read.csv("Data/ersa_seed_set.csv", sep=";")
+ersa_seed_set <- filter(ersa_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("ERSA", 10)
+Treatment <- rep("ERSA 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ersa_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("ERSA", 10)
+Treatment <- rep("ERSA 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ersa_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+colnames(ersa_seed_set)[1] <- "Species"
+colnames(ersa_seed_set)[2] <- "Treatment"
+colnames(ersa_seed_set)[3] <- "Treatment.number"
+colnames(ersa_seed_set)[4] <- "Seed.production"
+ersa_seed_set <- rbind(ersa_seed_set, ersa_50, ersa_100)
+ersa_seed_set$Treatment<- as.character(ersa_seed_set$Treatment)
+ersa_seed_set <- ersa_seed_set[order(ersa_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ersa_seed_set_div <- str_split_fixed(as.character(ersa_seed_set$Treatment), " ", 2)
+ersa_seed_set_div <- data.frame(ersa_seed_set_div, stringsAsFactors = F)
+colnames(ersa_seed_set_div)=c("non_focal","percentage")
+ersa_seed_set_bind <- cbind(ersa_seed_set,ersa_seed_set_div)
+ersa_seed_set_bind <- filter(ersa_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(ersa_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+ersa_seed_set_cross <- filter(ersa_seed_set_bind, non_focal %in% c("Cross"))
+ersa_seed_set_self <- filter(ersa_seed_set_bind, non_focal %in% c("Self"))
+ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
+ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("FC"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Cross"),]
+ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Self"),]
+ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
+ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("FC"),]
+
+ersa_seed_set_final<-rbind(ersa_seed_set_bind,ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
+                           ersa_seed_set_flower)
+#deleting extra columns used for data formating
+ersa_seed_set_final=ersa_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+ersa_seed_set_final[ersa_seed_set_final$Treatment==c("ERSA 50%"),4] <- NA
+
+#changing non_focal species name
+ersa_seed_set_final$Treatment=as.character(ersa_seed_set_final$Treatment)
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+#
+##
+###
+#S. ALBA  
+###
+##
+#
+
+sial_seed_set <- read.csv("Data/sial_seed_set.csv", sep=";")
+sial_seed_set <- filter(sial_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("SIAL", 10)
+Treatment <- rep("SIAL 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+sial_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SIAL", 10)
+Treatment <- rep("SIAL 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+sial_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+colnames(sial_seed_set)[1] <- "Species"
+colnames(sial_seed_set)[2] <- "Treatment"
+colnames(sial_seed_set)[3] <- "Treatment.number"
+colnames(sial_seed_set)[4] <- "Seed.production"
+sial_seed_set <- rbind(sial_seed_set, sial_50, sial_100)
+sial_seed_set$Treatment<- as.character(sial_seed_set$Treatment)
+sial_seed_set <- sial_seed_set[order(sial_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+sial_seed_set_div <- str_split_fixed(as.character(sial_seed_set$Treatment), " ", 2)
+sial_seed_set_div <- data.frame(sial_seed_set_div, stringsAsFactors = F)
+colnames(sial_seed_set_div)=c("non_focal","percentage")
+sial_seed_set_bind <- cbind(sial_seed_set,sial_seed_set_div)
+sial_seed_set_bind <- filter(sial_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(sial_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
+sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
+sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
+sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("FC"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
+sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
+sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
+sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("FC"),]
+
+sial_seed_set_final<-rbind(sial_seed_set_bind,sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
+                           sial_seed_set_flower)
+#deleting extra columns used for data formating
+sial_seed_set_final=sial_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+sial_seed_set_final[sial_seed_set_final$Treatment==c("SIAL 50%"),4] <- NA
+
+#changing non_focal species name
+sial_seed_set_final$Treatment=as.character(sial_seed_set_final$Treatment)
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+p <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+```
+\newpage
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
+#Preparing seed set plots, starting with Petunia
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(lattice)
+#read data and cleaning
+pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
+#removing samples where seeds got lost, first ones of the experiment
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+#
+##
+###
+#PETUNIA
+###
+##
+#
+#Removing RARA, species not considered because sterility
+
+pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
+
+#adding the focal species, first 50%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#adding the focal species, 100%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#Order from lower to higher values the average, to plot it nicely
+pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
+pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
+pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
+pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
+colnames(pein_seed_set_div)=c("non_focal","percentage")
+pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
+pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
+pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
+pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
+pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]
+
+pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
+                           pein_seed_set_flower)
+#deleting extra columns used for data formating
+pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
+#changing non_focal species name
+pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Colur per family
+
+a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5),plot.margin=unit(c(1,1,-0.5,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#C. ANNUUM 
+###
+##
+#
+caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
+
+#adding the focal species, first 50%
+Species <- rep("CAAN", 10)
+Treatment <- rep("CAAN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("CAAN", 10)
+Treatment <- rep("CAAN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+caan_seed_set <- caan_seed_set[,-4]
+colnames(caan_seed_set)[1] <- "Species"
+colnames(caan_seed_set)[2] <- "Treatment"
+colnames(caan_seed_set)[3] <- "Treatment.number"
+colnames(caan_seed_set)[4] <- "Seed.production"
+caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
+caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
+caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
+caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
+colnames(caan_seed_set_div)=c("non_focal","percentage")
+caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
+caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
+caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
+caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
+caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]
+
+caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
+                           caan_seed_set_flower)
+#deleting extra columns used for data formating
+caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA
+
+#changing non_focal species name
+caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
+  theme(plot.title = element_text(hjust = 0.5),plot.margin=unit(c(1,1,-0.5,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. LYCOPERSICUM
+###
+##
+#
+
+soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
+soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+soly_seed_set <- soly_seed_set[,-4]
+colnames(soly_seed_set)[1] <- "Species"
+colnames(soly_seed_set)[2] <- "Treatment"
+colnames(soly_seed_set)[3] <- "Treatment.number"
+colnames(soly_seed_set)[4] <- "Seed.production"
+soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
+soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
+soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
+soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
+colnames(soly_seed_set_div)=c("non_focal","percentage")
+soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
+soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
+soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
+soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
+soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]
+
+soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
+                           soly_seed_set_flower)
+#deleting extra columns used for data formating
+soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA
+
+#changing non_focal species name
+soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5), plot.margin=unit(c(-0.5,1,1,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. MELONGENA
+###
+##
+#
+
+#Taking out species that weren't used
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
+some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+
+#adding the focal species, first 50%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+some_seed_set<- some_seed_set[,-3]
+colnames(some_seed_set)[3] <- "Treatment.number"
+colnames(some_seed_set)[4] <- "Seed.production"
+some_seed_set <- rbind(some_seed_set, some_50, some_100)
+some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
+some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
+some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
+colnames(some_seed_set_div)=c("non_focal","percentage")
+some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
+some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
+some_seed_set_self <- filter(some_seed_set_bind, non_focal %in% c("SELF"))
+some_seed_set_control <- filter(some_seed_set_bind, non_focal %in% c("CONTROL"))
+some_seed_set_flower <- filter(some_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CROSS"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("SELF"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CONTROL"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("FLOWER"),]
+
+some_seed_set_final<-rbind(some_seed_set_bind,some_seed_set_cross, some_seed_set_self, some_seed_set_control,
+                           some_seed_set_flower)
+#deleting extra columns used for data formating
+some_seed_set_final=some_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+some_seed_set_final[some_seed_set_final$Treatment==c("SOME 50%"),4] <- NA
+
+#changing non_focal species name
+some_seed_set_final$Treatment=as.character(some_seed_set_final$Treatment)
+some_seed_set_final$Family[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5), plot.margin=unit(c(-0.5,1,1,1),"cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+gl <- lapply(list(a,b,c,d), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grid.arrange(lg[[1]], lg[[2]], lg[[3]], lg[[4]], nrow=2,ncol=2)
+
+```

### 2018-08-02 Scripts/ggplot_species_seed_set/b_oleracea_ggplot.R

@@ -1,0 +1,118 @@
+#
+##
+###
+#B. OLERACEA
+###
+##
+#
+
+
+brol_seed_set <- read.csv("Data/species_seed_set/BROL_seed_set.csv", sep=";")
+brol_seed_set <- filter(brol_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("BROL", 10)
+Treatment <- rep("BROL 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+brol_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("BROL", 10)
+Treatment <- rep("BROL 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+brol_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+colnames(brol_seed_set)[1] <- "Species"
+colnames(brol_seed_set)[2] <- "Treatment"
+colnames(brol_seed_set)[3] <- "Treatment.number"
+colnames(brol_seed_set)[4] <- "Seed.production"
+brol_seed_set <- rbind(brol_seed_set, brol_50, brol_100)
+brol_seed_set$Treatment<- as.character(brol_seed_set$Treatment)
+brol_seed_set <- brol_seed_set[order(brol_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+brol_seed_set_div <- str_split_fixed(as.character(brol_seed_set$Treatment), " ", 2)
+brol_seed_set_div <- data.frame(brol_seed_set_div, stringsAsFactors = F)
+colnames(brol_seed_set_div)=c("non_focal","percentage")
+brol_seed_set_bind <- cbind(brol_seed_set,brol_seed_set_div)
+brol_seed_set_bind <- filter(brol_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(brol_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
[…]

### 2018-08-02 Scripts/ggplot_species_seed_set/i_aquatica_ggplot.R

@@ -1,0 +1,127 @@
+#
+##
+###
+#I. AQUATICA
+###
+##
+#
+
+
+ipaq_seed_set <- read.csv("Data/species_seed_set/ipaq_seed_set.csv", sep=";")
+colnames(ipaq_seed_set)[1] <- "Species"
+colnames(ipaq_seed_set)[2] <- "Treatment"
+colnames(ipaq_seed_set)[3] <- "Treatment.number"
+colnames(ipaq_seed_set)[4] <- "Seed.production"
+
+ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+
+ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
+ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
+ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
+ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
+colnames(ipaq_seed_set_div)=c("non_focal","percentage")
+ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
+ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
[…]

### 2018-08-02 Scripts/ggplot_species_seed_set/i_purpurea_ggplot.R

@@ -1,0 +1,127 @@
+#
+##
+###
+#I. IPPU
+###
+##
+#
+
+
+ippu_seed_set <- read.csv("Data/species_seed_set/ippu_seed_set.csv", sep=";")
+colnames(ippu_seed_set)[1] <- "Species"
+colnames(ippu_seed_set)[2] <- "Treatment"
+colnames(ippu_seed_set)[3] <- "Treatment.number"
+colnames(ippu_seed_set)[4] <- "Seed.production"
+
+ippu_seed_set <- filter(ippu_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("IPPU", 10)
+Treatment <- rep("IPPU 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ippu_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("IPPU", 10)
+Treatment <- rep("IPPU 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ippu_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+
+ippu_seed_set <- rbind(ippu_seed_set, ippu_50, ippu_100)
+ippu_seed_set$Treatment<- as.character(ippu_seed_set$Treatment)
+ippu_seed_set <- ippu_seed_set[order(ippu_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ippu_seed_set_div <- str_split_fixed(as.character(ippu_seed_set$Treatment), " ", 2)
+ippu_seed_set_div <- data.frame(ippu_seed_set_div, stringsAsFactors = F)
+colnames(ippu_seed_set_div)=c("non_focal","percentage")
+ippu_seed_set_bind <- cbind(ippu_seed_set,ippu_seed_set_div)
+ippu_seed_set_bind <- filter(ippu_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
[…]

### 2018-08-03 Rmd/Data_visualization.Rmd
last changes

@@
 ---
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
-#load libraries
-
-library(ggplot2)
-library(colorspace)
-library(gridExtra)
-
-colours <- rainbow_hcl(4, start = 30, end = 300)
-#load data
-
-par(mfrow=c(2,1))
-d<-read.csv("Data/Ovules.csv", sep=";")
-d<- d[,-c(9,11)]
-colnames(d)[1]<-"C. annuum"
-colnames(d)[2]<-"S. lycopersicum"
-colnames(d)[3]<-"S. melongera"
-colnames(d)[4]<-"P. integrifolia"
-colnames(d)[5]<-"B. oleracea"
-colnames(d)[6]<-"B. rapa"
-colnames(d)[7]<-"E. sativa"
-colnames(d)[8]<-"S. alba"
-colnames(d)[9]<-"I. aquatica"
-colnames(d)[10]<-"I. purpurea"
-
-#Reorganise data
-d <- stack(d)
-#Naming columns
-colnames(d)[1]<-"ovules"
-colnames(d)[2]<-"species"
-
-family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
-
-d[,"family"] <- family
-
-#subset per family (solanaceae, brassicaceae, convolvulaceae)
-solanaceae<-subset(d)[1:60,]
-brassicaceae<-subset(d)[61:120,]
-
-# OVULES SOLANACEAE
-p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-# OVULES BRASSICACEAE
-p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#all species
-#formating d, to have just the spp of interest
-
-p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-```
-
-#Pollen per anther, just one Convolvulaceae at the moment
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
-library(ggplot2)
-
-p <- read.csv("data/Pollen.csv", sep = ";")
-
-#Deleting extra row (21)
-p <-p[-21,]
-
-#boxplot(p)
-#Reorganize data for ggplot
-p<-stack(p)
-#colnames
-colnames(p)[1]<-"pollen"
-colnames(p)[2]<-"species"
-
-all<-p
-solanaceae<-subset(p)[1:100,]
-brassicaceae<- subset(p)[101:180,]
-
-#Solanaceae
-p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#Brassicaceae
-p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#all
-p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-```
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-tab <- read.csv("Data/tab.csv", sep="", header = T)
-
-p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
-  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  scale_fill_manual(values=colours)
-p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
-
-```
-
-```{r echo=FALSE, out.width='80%', fig.align='center'}
-knitr::include_graphics('Images/all_species.png')
-```
-
-\newpage
-```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
-par(mfrow=c(2,2))
-#load libraries
-library(reshape2)
-library(ggplot2)
-#read data
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
-
-mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)
-
-colnames(mean_seed_seet)[2] <-"avg"
-
-sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)
-
-colnames(sd_seed_seet)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
-#Removing RARA, species not considered because sterility 
-mean_sd<- mean_sd[-c(16,17),]
-
-merge_1 <- data.frame(mean_sd, stringsAsFactors = F)
-
-merge_1$Treatment<- as.character(merge_1$Treatment)
-pein <- c("PEIN", NA, NA)
-
-str(merge_1)
-mean_sd_1 <- rbind(merge_1,pein)
-
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered <- mean_sd[order(mean_sd$avg),]
-
-mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]
-
-#ploting averages with sd
-x <- 1:22
-plot(x, mean_sd_ordered$avg,
-     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Petunia integrifolia")
-# add arrows
-arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered$Treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-mean_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = some_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_some)[2] <-"avg"
-sd_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = some_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_some)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_some <- merge(mean_seed_seet_some,sd_seed_seet_some, by="Treatment")
-#Delete RARA rows, species not included because sterility
-mean_sd_some <- mean_sd_some[-c(8,9,20),]
-
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_some <- mean_sd_some[order(mean_sd_some$avg),]
-
-x <- 1:22
-plot(x, mean_sd_ordered_some$avg,
-     ylim=range(c(mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Solanum melongena")
-# add arrows
-arrows(x, mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, x, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_some$Treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
-mean_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = caan_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_caan)[2] <-"avg"
-sd_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = caan_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_caan)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_caan <- merge(mean_seed_seet_caan,sd_seed_seet_caan, by="treatment")
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_caan <- mean_sd_caan[order(mean_sd_caan$avg),]
-
-x <- 1:22
-plot(x, mean_sd_ordered_caan$avg,
-     ylim=range(c(mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Capsicum annuum")
-# add arrows
-arrows(x, mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, x, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_caan$treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-mean_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = soly_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_soly)[2] <-"avg"
-sd_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = soly_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_soly)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_soly <- merge(mean_seed_seet_soly,sd_seed_seet_soly, by="Treatment")
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_soly <- mean_sd_soly[order(mean_sd_soly$avg),]
-
-x <- 1:26
-plot(x, mean_sd_ordered_soly$avg,
-     ylim=range(c(mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Solanum lycopersicum")
-# add arrows
-arrows(x, mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, x, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_soly$Treatment)
-axis(x, at=1:26, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-```
-
-\newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',fig.align='center',out.width='70%'}
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
 #Preparing seed set plots, starting with Petunia
@@
 library(dplyr)
-library(ggplot2)
+library(gridExtra)
 library(grid)
-library(gridExtra)
-library(egg)
-library(gtable)
-
-#read data and cleaning
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
-
-#
-##
-###
-#PETUNIA
-###
-##
-#
-
-#Removing RARA, species not considered because sterility
-
-pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
-
-#adding the focal species, first 50%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
-#adding the focal species, 100%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
-#Order from lower to higher values the average, to plot it nicely
-pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
-pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
-pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]
-
-plot1 <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot1 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#S. MELONGENA
-###
-##
-#
-
-#Taking out species that weren't used
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
-
-#adding the focal species, first 50%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-some_seed_set<- some_seed_set[,-3]
-colnames(some_seed_set)[3] <- "Treatment.number"
-colnames(some_seed_set)[4] <- "Seed.production"
-some_seed_set <- rbind(some_seed_set, some_50, some_100)
-some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
-some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
-
-plot2 <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot2 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#C. ANNUUM 
-###
-##
-#
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
-
-#adding the focal species, first 50%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-caan_seed_set <- caan_seed_set[,-4]
-colnames(caan_seed_set)[1] <- "Species"
-colnames(caan_seed_set)[2] <- "Treatment"
-colnames(caan_seed_set)[3] <- "Treatment.number"
-colnames(caan_seed_set)[4] <- "Seed.production"
-caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
-caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
-caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
-
-plot3 <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot3 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#S. LYCOPERSICUM
-###
-##
-#
-
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-soly_seed_set <- soly_seed_set[,-4]
-colnames(soly_seed_set)[1] <- "Species"
-colnames(soly_seed_set)[2] <- "Treatment"
-colnames(soly_seed_set)[3] <- "Treatment.number"
-colnames(soly_seed_set)[4] <- "Seed.production"
-soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
-soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
-soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
-
-plot4 <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot4 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-```
-
-\newpage
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',out.width='55%'}
-#Preparing seed set plots, starting with Petunia
-
-#There are 3 crosses were seeds were lost (2,7,9)
-#load libraries
-library(reshape2)
-library(ggplot2)
-library(dplyr)
-par(mfrow=c(2,3))
-
+library(lattice)
 #read data and cleaning
@@
 
-p <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 #Different colour per family
-p <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 #Different colour per family
-p <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
   labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 #Different colour per family
-p <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
+d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+gl <- lapply(list(a,b,c,d), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grobz <- lapply(list(a, b, c, d), ggplotGrob)
+grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
+                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
+                           ncol = 2, top="Solanaceae Focal Species")
+
+grid.draw(grobz.plot)
+
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
+library(dplyr)
+
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(lattice)
+library(gtable)
 ##
@@
 #Different colour per family
-p <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 #Different colour per family
-p <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 #Different colour per family
-p <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
   labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 #
@@
 #Different colour per family
-p <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)
+d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")
+
+gl <- lapply(list(a,b,c,d), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grobz <- lapply(list(a, b, c, d), ggplotGrob)
+grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
+                                        rbind(grobz[[2]], grobz[[4]], size = "last")), ncol = 2,top="Brassicaceae Focal species")
+
+grid.draw(grobz.plot)
+
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
+#load libraries
+
+library(ggplot2)
+library(colorspace)
+library(gridExtra)
+
+colours <- rainbow_hcl(4, start = 30, end = 300)
+#load data
+
+par(mfrow=c(2,1))
+d<-read.csv("Data/Ovules.csv", sep=";")
+d<- d[,-c(9,11)]
+colnames(d)[1]<-"C. annuum"
+colnames(d)[2]<-"S. lycopersicum"
+colnames(d)[3]<-"S. melongera"
+colnames(d)[4]<-"P. integrifolia"
+colnames(d)[5]<-"B. oleracea"
+colnames(d)[6]<-"B. rapa"
+colnames(d)[7]<-"E. sativa"
+colnames(d)[8]<-"S. alba"
+colnames(d)[9]<-"I. aquatica"
+colnames(d)[10]<-"I. purpurea"
+
+#Reorganise data
+d <- stack(d)
+#Naming columns
+colnames(d)[1]<-"ovules"
+colnames(d)[2]<-"species"
+
+family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
+
+d[,"family"] <- family
+
+#subset per family (solanaceae, brassicaceae, convolvulaceae)
+solanaceae<-subset(d)[1:60,]
+brassicaceae<-subset(d)[61:120,]
+
+# OVULES SOLANACEAE
+p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
+theme(plot.title = element_text(hjust = 0.5))
 
@@
 
+# OVULES BRASSICACEAE
+p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#all species
+#formating d, to have just the spp of interest
+
+p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
 ```
+
+#Pollen per anther, just one Convolvulaceae at the moment
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+library(ggplot2)
+
+p <- read.csv("data/Pollen.csv", sep = ";")
+
+#Deleting extra row (21)
+p <-p[-21,]
+
+#boxplot(p)
+#Reorganize data for ggplot
+p<-stack(p)
+#colnames
+colnames(p)[1]<-"pollen"
+colnames(p)[2]<-"species"
+
+all<-p
+solanaceae<-subset(p)[1:100,]
+brassicaceae<- subset(p)[101:180,]
+
+#Solanaceae
+p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#Brassicaceae
+p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#all
+p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+tab <- read.csv("Data/tab.csv", sep="", header = T)
+
+p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
+  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  scale_fill_manual(values=colours)
+p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
+
+```
+
+```{r echo=FALSE, out.width='80%', fig.align='center'}
+knitr::include_graphics('Images/all_species.png')
+```
+
 \newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
+```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
+par(mfrow=c(2,2))
+#load libraries
+library(reshape2)
+library(ggplot2)
+#read data
+pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)
+
+colnames(mean_seed_seet)[2] <-"avg"
+
+sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)
+
+colnames(sd_seed_seet)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
+#Removing RARA, species not considered because sterility 
+mean_sd<- mean_sd[-c(16,17),]
+
+merge_1 <- data.frame(mean_sd, stringsAsFactors = F)
+
+merge_1$Treatment<- as.character(merge_1$Treatment)
+pein <- c("PEIN", NA, NA)
+
+str(merge_1)
+mean_sd_1 <- rbind(merge_1,pein)
+
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered <- mean_sd[order(mean_sd$avg),]
+
+mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]
+
+#ploting averages with sd
+x <- 1:22
+plot(x, mean_sd_ordered$avg,
+     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Petunia integrifolia")
+# add arrows
+arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered$Treatment)
+axis(x, at=1:22, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
+mean_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = some_seed_set, na.rm= TRUE)
+colnames(mean_seed_seet_some)[2] <-"avg"
+sd_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = some_seed_set, na.rm= TRUE)
+colnames(sd_seed_seet_some)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd_some <- merge(mean_seed_seet_some,sd_seed_seet_some, by="Treatment")
+#Delete RARA rows, species not included because sterility
+mean_sd_some <- mean_sd_some[-c(8,9,20),]
+
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered_some <- mean_sd_some[order(mean_sd_some$avg),]
+
+x <- 1:22
+plot(x, mean_sd_ordered_some$avg,
+     ylim=range(c(mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Solanum melongena")
+# add arrows
+arrows(x, mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, x, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered_some$Treatment)
+axis(x, at=1:22, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
+mean_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = caan_seed_set, na.rm= TRUE)
+colnames(mean_seed_seet_caan)[2] <-"avg"
+sd_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = caan_seed_set, na.rm= TRUE)
+colnames(sd_seed_seet_caan)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd_caan <- merge(mean_seed_seet_caan,sd_seed_seet_caan, by="treatment")
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered_caan <- mean_sd_caan[order(mean_sd_caan$avg),]
+
+x <- 1:22
+plot(x, mean_sd_ordered_caan$avg,
+     ylim=range(c(mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Capsicum annuum")
+# add arrows
+arrows(x, mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, x, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered_caan$treatment)
+axis(x, at=1:22, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
+mean_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = soly_seed_set, na.rm= TRUE)
+colnames(mean_seed_seet_soly)[2] <-"avg"
+sd_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = soly_seed_set, na.rm= TRUE)
+colnames(sd_seed_seet_soly)[2] <-"sdev"
+
+#Unify mean and sd with merge
+mean_sd_soly <- merge(mean_seed_seet_soly,sd_seed_seet_soly, by="Treatment")
+#Order from lower to higher values the average, to plot it nicely
+mean_sd_ordered_soly <- mean_sd_soly[order(mean_sd_soly$avg),]
+
+x <- 1:26
+plot(x, mean_sd_ordered_soly$avg,
+     ylim=range(c(mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev)),
+     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
+     main="Solanum lycopersicum")
+# add arrows
+arrows(x, mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, x, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev, length=0.05, angle=90, code=3)
+lablist.x<-as.vector(mean_sd_ordered_soly$Treatment)
+axis(x, at=1:26, labels = FALSE)
+text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
+
+```
+
+\newpage
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',fig.align='center',out.width='70%'}
 #Preparing seed set plots, starting with Petunia
@@
 library(dplyr)
+library(ggplot2)
+library(grid)
 library(gridExtra)
-library(grid)
-library(lattice)
+library(egg)
+library(gtable)
+
 #read data and cleaning
 pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-#removing samples where seeds got lost, first ones of the experiment
 pein_seed_set <- pein_seed_set[-c(42,47,49),]
@@
 #
+
 #Removing RARA, species not considered because sterility
@@
 pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
-pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
-colnames(pein_seed_set_div)=c("non_focal","percentage")
-pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
-pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
-pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
-pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
-pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]
-
-pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
-                           pein_seed_set_flower)
-#deleting extra columns used for data formating
-pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
-#changing non_focal species name
-pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-#Colur per family
-
-a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
-  theme(plot.title = element_text(hjust = 0.5),plot.margin=unit(c(1,1,-0.5,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+plot1 <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+plot1 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. MELONGENA
+###
+##
+#
+
+#Taking out species that weren't used
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
+some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+
+#adding the focal species, first 50%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+some_seed_set<- some_seed_set[,-3]
+colnames(some_seed_set)[3] <- "Treatment.number"
+colnames(some_seed_set)[4] <- "Seed.production"
+some_seed_set <- rbind(some_seed_set, some_50, some_100)
+some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
+some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
+
+plot2 <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+plot2 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
-caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
-colnames(caan_seed_set_div)=c("non_focal","percentage")
-caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
-caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
-caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
-caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
-caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]
-
-caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
-                           caan_seed_set_flower)
-#deleting extra columns used for data formating
-caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA
-
-#changing non_focal species name
-caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-#Different colour per family
-b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5),plot.margin=unit(c(1,1,-0.5,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+plot3 <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+plot3 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
-soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
-colnames(soly_seed_set_div)=c("non_focal","percentage")
-soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
-soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
-soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
-soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
-soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]
-
-soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
-                           soly_seed_set_flower)
-#deleting extra columns used for data formating
-soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA
-
-#changing non_focal species name
-soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-#Different colour per family
-c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5), plot.margin=unit(c(-0.5,1,1,1), "cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#S. MELONGENA
-###
-##
-#
-
-#Taking out species that weren't used
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
-
-#adding the focal species, first 50%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-some_seed_set<- some_seed_set[,-3]
-colnames(some_seed_set)[3] <- "Treatment.number"
-colnames(some_seed_set)[4] <- "Seed.production"
-some_seed_set <- rbind(some_seed_set, some_50, some_100)
-some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
-some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
-some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
-colnames(some_seed_set_div)=c("non_focal","percentage")
-some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
-some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
-some_seed_set_self <- filter(some_seed_set_bind, non_focal %in% c("SELF"))
-some_seed_set_control <- filter(some_seed_set_bind, non_focal %in% c("CONTROL"))
-some_seed_set_flower <- filter(some_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CROSS"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("SELF"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CONTROL"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("FLOWER"),]
-
-some_seed_set_final<-rbind(some_seed_set_bind,some_seed_set_cross, some_seed_set_self, some_seed_set_control,
-                           some_seed_set_flower)
-#deleting extra columns used for data formating
-some_seed_set_final=some_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-some_seed_set_final[some_seed_set_final$Treatment==c("SOME 50%"),4] <- NA
-
-#changing non_focal species name
-some_seed_set_final$Treatment=as.character(some_seed_set_final$Treatment)
-some_seed_set_final$Family[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-#Different colour per family
-d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5), plot.margin=unit(c(-0.5,1,1,1),"cm")) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-gl <- lapply(list(a,b,c,d), ggplotGrob)
-library(grid)
-widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
-heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
-lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
-
-grid.arrange(lg[[1]], lg[[2]], lg[[3]], lg[[4]], nrow=2,ncol=2)
+plot4 <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5))
+
+plot4 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 

### 2018-08-03 Rmd/ggplot_2_species_trial.Rmd
last changes

--- 2018-06-25 Rmd/Data_visualization.Rmd
@@
 ---
-title: "Data_visualization"
+title: ''
 output:
-      pdf_document
+  pdf_document: default
+  html_document: default
 ---
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
-#load libraries
-
-library(ggplot2)
-library(colorspace)
-library(gridExtra)
-
-colours <- rainbow_hcl(4, start = 30, end = 300)
-#load data
-
-par(mfrow=c(2,1))
-d<-read.csv("Data/Ovules.csv", sep=";")
-d<- d[,-c(9,11)]
-colnames(d)[1]<-"C. annuum"
-colnames(d)[2]<-"S. lycopersicum"
-colnames(d)[3]<-"S. melongera"
-colnames(d)[4]<-"P. integrifolia"
-colnames(d)[5]<-"B. oleracea"
-colnames(d)[6]<-"B. rapa"
-colnames(d)[7]<-"E. sativa"
-colnames(d)[8]<-"S. alba"
-colnames(d)[9]<-"I. aquatica"
-colnames(d)[10]<-"I. purpurea"
-
-#Reorganise data
-d <- stack(d)
-#Naming columns
-colnames(d)[1]<-"ovules"
-colnames(d)[2]<-"species"
-
-family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
-
-d[,"family"] <- family
-
-#subset per family (solanaceae, brassicaceae, convolvulaceae)
-solanaceae<-subset(d)[1:60,]
-brassicaceae<-subset(d)[61:120,]
-
-# OVULES SOLANACEAE
-p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-# OVULES BRASSICACEAE
-p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#all species
-#formating d, to have just the spp of interest
-
-p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-```
-
-#Pollen per anther, just one Convolvulaceae at the moment
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
-library(ggplot2)
-
-p <- read.csv("data/Pollen.csv", sep = ";")
-
-#Deleting extra row (21)
-p <-p[-21,]
-
-#boxplot(p)
-#Reorganize data for ggplot
-p<-stack(p)
-#colnames
-colnames(p)[1]<-"pollen"
-colnames(p)[2]<-"species"
-
-all<-p
-solanaceae<-subset(p)[1:100,]
-brassicaceae<- subset(p)[101:180,]
-
-#Solanaceae
-p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#Brassicaceae
-p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#all
-p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-```
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-tab <- read.csv("Data/tab.csv", sep="", header = T)
-
-p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
-  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  scale_fill_manual(values=colours)
-p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
-
-```
-
-```{r echo=FALSE, out.width='80%', fig.align='center'}
-knitr::include_graphics('Images/all_species.png')
-```
-
-\newpage
-```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
-par(mfrow=c(2,2))
-#load libraries
-library(reshape2)
-library(ggplot2)
-#read data
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
-
-mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)
-
-colnames(mean_seed_seet)[2] <-"avg"
-
-sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)
-
-colnames(sd_seed_seet)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
-#Removing RARA, species not considered because sterility 
-mean_sd<- mean_sd[-c(16,17),]
-
-merge_1 <- data.frame(mean_sd, stringsAsFactors = F)
-
-merge_1$Treatment<- as.character(merge_1$Treatment)
-pein <- c("PEIN", NA, NA)
-
-str(merge_1)
-mean_sd_1 <- rbind(merge_1,pein)
-
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered <- mean_sd[order(mean_sd$avg),]
-
-mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]
-
-#ploting averages with sd
-x <- 1:22
-plot(x, mean_sd_ordered$avg,
-     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Petunia integrifolia")
-# add arrows
-arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered$Treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-mean_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = some_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_some)[2] <-"avg"
-sd_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = some_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_some)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_some <- merge(mean_seed_seet_some,sd_seed_seet_some, by="Treatment")
-#Delete RARA rows, species not included because sterility
-mean_sd_some <- mean_sd_some[-c(8,9,20),]
-
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_some <- mean_sd_some[order(mean_sd_some$avg),]
-
-x <- 1:22
-plot(x, mean_sd_ordered_some$avg,
-     ylim=range(c(mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Solanum melongena")
-# add arrows
-arrows(x, mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, x, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_some$Treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
-mean_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = caan_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_caan)[2] <-"avg"
-sd_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = caan_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_caan)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_caan <- merge(mean_seed_seet_caan,sd_seed_seet_caan, by="treatment")
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_caan <- mean_sd_caan[order(mean_sd_caan$avg),]
-
-x <- 1:22
-plot(x, mean_sd_ordered_caan$avg,
-     ylim=range(c(mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Capsicum annuum")
-# add arrows
-arrows(x, mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, x, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_caan$treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-mean_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = soly_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_soly)[2] <-"avg"
-sd_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = soly_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_soly)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_soly <- merge(mean_seed_seet_soly,sd_seed_seet_soly, by="Treatment")
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_soly <- mean_sd_soly[order(mean_sd_soly$avg),]
-
-x <- 1:26
-plot(x, mean_sd_ordered_soly$avg,
-     ylim=range(c(mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Solanum lycopersicum")
-# add arrows
-arrows(x, mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, x, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_soly$Treatment)
-axis(x, at=1:26, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-```
-
-\newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',fig.align='center',out.width='70%'}
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
 #Preparing seed set plots, starting with Petunia
@@
 library(dplyr)
-library(ggplot2)
+library(gridExtra)
 library(grid)
-library(gridExtra)
-library(egg)
-library(gtable)
-
+library(lattice)
 #read data and cleaning
 pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
+#removing samples where seeds got lost, first ones of the experiment
 pein_seed_set <- pein_seed_set[-c(42,47,49),]
@@
 #
-
 #Removing RARA, species not considered because sterility
@@
 pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
+#Organizing with just 50% and cross, self, flower control and control on a side
 
-plot1 <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
+library(stringr)
+pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
+pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
+colnames(pein_seed_set_div)=c("non_focal","percentage")
+pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
+pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
 
-plot1 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
+pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
+pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
+pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))
 
-#
-##
-###
-#S. MELONGENA
-###
-##
-#
+#Changing 0 for NA'S FOCAL species
 
-#Taking out species that weren't used
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
+pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]
 
-#adding the focal species, first 50%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-some_seed_set<- some_seed_set[,-3]
-colnames(some_seed_set)[3] <- "Treatment.number"
-colnames(some_seed_set)[4] <- "Seed.production"
-some_seed_set <- rbind(some_seed_set, some_50, some_100)
-some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
-some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
+pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
+                           pein_seed_set_flower)
+#deleting extra columns used for data formating
+pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
+#changing non_focal species name
+pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
+pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
 
-plot2 <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
 
-plot2 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+#Colur per family
+
+a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-plot3 <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
+#Organizing with just 50% and cross, self, flower control and control on a side
 
-plot3 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+library(stringr)
+caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
+caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
+colnames(caan_seed_set_div)=c("non_focal","percentage")
+caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
+caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
+caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
+caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
+caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
+caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]
+
+caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
+                           caan_seed_set_flower)
+#deleting extra columns used for data formating
+caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA
+
+#changing non_focal species name
+caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 
-plot4 <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
+#Organizing with just 50% and cross, self, flower control and control on a side
 
-plot4 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+library(stringr)
+soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
+soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
+colnames(soly_seed_set_div)=c("non_focal","percentage")
+soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
+soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
+soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
+soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
+soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
+soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]
+
+soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
+                           soly_seed_set_flower)
+#deleting extra columns used for data formating
+soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA
+
+#changing non_focal species name
+soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#
+##
+###
+#S. MELONGENA
+###
+##
+#
+
+#Taking out species that weren't used
+some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
+some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+
+#adding the focal species, first 50%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+some_seed_set<- some_seed_set[,-3]
+colnames(some_seed_set)[3] <- "Treatment.number"
+colnames(some_seed_set)[4] <- "Seed.production"
+some_seed_set <- rbind(some_seed_set, some_50, some_100)
+some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
+some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
+some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
+colnames(some_seed_set_div)=c("non_focal","percentage")
+some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
+some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
+some_seed_set_self <- filter(some_seed_set_bind, non_focal %in% c("SELF"))
+some_seed_set_control <- filter(some_seed_set_bind, non_focal %in% c("CONTROL"))
+some_seed_set_flower <- filter(some_seed_set_bind, non_focal %in% c("FLOWER"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CROSS"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("SELF"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CONTROL"),]
+some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("FLOWER"),]
+
+some_seed_set_final<-rbind(some_seed_set_bind,some_seed_set_cross, some_seed_set_self, some_seed_set_control,
+                           some_seed_set_flower)
+#deleting extra columns used for data formating
+some_seed_set_final=some_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+some_seed_set_final[some_seed_set_final$Treatment==c("SOME 50%"),4] <- NA
+
+#changing non_focal species name
+some_seed_set_final$Treatment=as.character(some_seed_set_final$Treatment)
+some_seed_set_final$Family[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+some_seed_set_final$Family[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+#Different colour per family
+d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+gl <- lapply(list(a,b,c,d), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grobz <- lapply(list(a, b, c, d), ggplotGrob)
+grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
+                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
+                           ncol = 2, top="b")
+
+grid.draw(grobz.plot)
 

### 2018-08-03 Rmd/Data_visualization.Rmd
last changes

@@
 pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CROSS"] <- "Cross"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SELF"] <- "Self"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CONTROL"] <- "Control"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
 
@@
 
-a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CROSS"] <- "Cross"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SELF"] <- "Self"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CONTROL"] <- "Control"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
 
 #Different colour per family
-b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CROSS"] <- "Cross"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SELF"] <- "Self"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CONTROL"] <- "Control"
+soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
 
 #Different colour per family
-c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CROSS"] <- "Cross"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SELF"] <- "Self"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CONTROL"] <- "Control"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
 
 #Different colour per family
-d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
-brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))
+brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("Flower"))
 
@@
 brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
-brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]
+brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Flower"),]
 
@@
 brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="FC"] <- "Flower control"
 
 #Different colour per family
-a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="FC"] <- "Flower control"
 
 #Different colour per family
-b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
@@
 ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
-ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("FC"))
+ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("Flower"))
 
@@
 ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
-ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("FC"),]
+ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Flower"),]
 
@@
 ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="FC"] <- "Flower control"
 
 #Different colour per family
-c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 #
@@
 sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
-sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("FC"))
+sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("Flower"))
 
@@
 sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
-sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("FC"),]
+sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Flower"),]
 
@@
 sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="FC"] <- "Flower control"
 
 #Different colour per family
-d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2)+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")
+d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")
 
@@
 ```
-
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}
+
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(lattice)
+
+#Preparing seed set plots, starting with Petunia
+#
+##
+###
+#I. AQUATICA
+###
+##
+#
+
+ipaq_seed_set <- read.csv("Data/ipaq_seed_set.csv", sep=";")
+colnames(ipaq_seed_set)[1] <- "Species"
+colnames(ipaq_seed_set)[2] <- "Treatment"
+colnames(ipaq_seed_set)[3] <- "Treatment.number"
+colnames(ipaq_seed_set)[4] <- "Seed.production"
+
+ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+
+ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
+ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
+ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
+ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
+colnames(ipaq_seed_set_div)=c("non_focal","percentage")
+ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
+ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(ipaq_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+ipaq_seed_set_cross <- filter(ipaq_seed_set_bind, Treatment %in% c("cross"))
+ipaq_seed_set_self <- filter(ipaq_seed_set_bind, Treatment %in% c("self"))
+ipaq_seed_set_control <- filter(ipaq_seed_set_bind, Treatment %in% c("control"))
+ipaq_seed_set_flower <- filter(ipaq_seed_set_bind, Treatment %in% c("flower control"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("cross"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("self"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("control"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("flower control"),]
+
+ipaq_seed_set_final<-rbind(ipaq_seed_set_bind,ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
+                           ipaq_seed_set_flower)
+#deleting extra columns used for data formating
+ipaq_seed_set_final=ipaq_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+ipaq_seed_set_final[ipaq_seed_set_final$Treatment==c("IPPA 50%"),4] <- NA
+
+#changing non_focal species name
+ipaq_seed_set_final$Treatment=as.character(ipaq_seed_set_final$Treatment)
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
+
+#Different colour per family
+a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="Ipomea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+ippu_seed_set <- read.csv("Data/ippu_seed_set.csv", sep=";")
+colnames(ippu_seed_set)[1] <- "Species"
+colnames(ippu_seed_set)[2] <- "Treatment"
+colnames(ippu_seed_set)[3] <- "Treatment.number"
+colnames(ippu_seed_set)[4] <- "Seed.production"
+
+ippu_seed_set <- filter(ippu_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("IPPU", 10)
+Treatment <- rep("IPPU 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ippu_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("IPPU", 10)
+Treatment <- rep("IPPU 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ippu_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+
+ippu_seed_set <- rbind(ippu_seed_set, ippu_50, ippu_100)
+ippu_seed_set$Treatment<- as.character(ippu_seed_set$Treatment)
+ippu_seed_set <- ippu_seed_set[order(ippu_seed_set$Treatment),]
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ippu_seed_set_div <- str_split_fixed(as.character(ippu_seed_set$Treatment), " ", 2)
+ippu_seed_set_div <- data.frame(ippu_seed_set_div, stringsAsFactors = F)
+colnames(ippu_seed_set_div)=c("non_focal","percentage")
+ippu_seed_set_bind <- cbind(ippu_seed_set,ippu_seed_set_div)
+ippu_seed_set_bind <- filter(ippu_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(ippu_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+ippu_seed_set_cross <- filter(ippu_seed_set_bind, Treatment %in% c("cross"))
+ippu_seed_set_self <- filter(ippu_seed_set_bind, Treatment %in% c("self"))
+ippu_seed_set_control <- filter(ippu_seed_set_bind, Treatment %in% c("control"))
+ippu_seed_set_flower <- filter(ippu_seed_set_bind, Treatment %in% c("flower control"))
+
+#Changing 0 for NA'S FOCAL species
+
+# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("cross"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("self"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("control"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("flower control"),]
+
+ippu_seed_set_final<-rbind(ippu_seed_set_bind,ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
+                           ippu_seed_set_flower)
+#deleting extra columns used for data formating
+ippu_seed_set_final=ippu_seed_set_final[,-c(5,6)]
+#adding NA'S to the focal species
+ippu_seed_set_final[ippu_seed_set_final$Treatment==c("IPPU 50%"),4] <- NA
+
+#changing non_focal species name
+ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"
+
+#Different colour per family
+b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="Ipomea purpurea",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+
+#read data and cleaning
+
+gl <- lapply(list(a,b), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grobz <- lapply(list(a, b), ggplotGrob)
+grobz.plot <- arrangeGrob(grobs = list(rbind(grobz[[1]], size = "last"),
+                                        rbind(grobz[[2]], size = "last")), ncol = 2,top="Convolvulaceae")
+
+grid.draw(grobz.plot)
+
+```
+
+\newpage
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}

### 2018-08-03 Rmd/ggplot_2_species_trial.Rmd
last changes

@@
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
-#Preparing seed set plots, starting with Petunia
 
-#There are 3 crosses were seeds were lost (2,7,9)
-#load libraries
 library(reshape2)
@@
 library(lattice)
-#read data and cleaning
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-#removing samples where seeds got lost, first ones of the experiment
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
 
+#Preparing seed set plots, starting with Petunia
 #
@@
 ###
-#PETUNIA
+#I. AQUATICA
 ###
@@
 #
-#Removing RARA, species not considered because sterility
 
-pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
+ipaq_seed_set <- read.csv("Data/ipaq_seed_set.csv", sep=";")
+colnames(ipaq_seed_set)[1] <- "Species"
+colnames(ipaq_seed_set)[2] <- "Treatment"
+colnames(ipaq_seed_set)[3] <- "Treatment.number"
+colnames(ipaq_seed_set)[4] <- "Seed.production"
+
+ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
 
 #adding the focal species, first 50%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 50%", 10)
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 50%", 10)
 Treatment.number <- seq(1:10)
 Seed.production <- rep(0, 10)
-pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
 #adding the focal species, 100%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 100%", 10)
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 100%", 10)
 Treatment.number <- seq(1:10)
 Seed.production <- rep(0, 10)
-pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
 #Order from lower to higher values the average, to plot it nicely
-pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
-pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
-pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
+
+ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
+ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
+ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]
+
 #Organizing with just 50% and cross, self, flower control and control on a side
@@
 library(stringr)
-pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
-pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
-colnames(pein_seed_set_div)=c("non_focal","percentage")
-pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
-pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
+ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
+ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
+colnames(ipaq_seed_set_div)=c("non_focal","percentage")
+ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
+ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")
+
 #Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+#pein_seed_set_common <- filter(ipaq_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
 
-pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
-pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
-pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
-pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))
+ipaq_seed_set_cross <- filter(ipaq_seed_set_bind, Treatment %in% c("cross"))
+ipaq_seed_set_self <- filter(ipaq_seed_set_bind, Treatment %in% c("self"))
+ipaq_seed_set_control <- filter(ipaq_seed_set_bind, Treatment %in% c("control"))
+ipaq_seed_set_flower <- filter(ipaq_seed_set_bind, Treatment %in% c("flower control"))
 
@@
 # I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("cross"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("self"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("control"),]
+ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("flower control"),]
 
-pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
-                           pein_seed_set_flower)
+ipaq_seed_set_final<-rbind(ipaq_seed_set_bind,ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
+                           ipaq_seed_set_flower)
 #deleting extra columns used for data formating
-pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
+ipaq_seed_set_final=ipaq_seed_set_final[,-c(5,6)]
 #adding NA'S to the focal species
-pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
+ipaq_seed_set_final[ipaq_seed_set_final$Treatment==c("IPPA 50%"),4] <- NA
+
 #changing non_focal species name
-pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+ipaq_seed_set_final$Treatment=as.character(ipaq_seed_set_final$Treatment)
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
 
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
 
-#Colur per family
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
 
-a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+#Different colour per family
+a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Ipomea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
-#
-##
-###
-#C. ANNUUM 
-###
-##
-#
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
+ippu_seed_set <- read.csv("Data/ippu_seed_set.csv", sep=";")
+colnames(ippu_seed_set)[1] <- "Species"
+colnames(ippu_seed_set)[2] <- "Treatment"
+colnames(ippu_seed_set)[3] <- "Treatment.number"
+colnames(ippu_seed_set)[4] <- "Seed.production"
+
+ippu_seed_set <- filter(ippu_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
 
 #adding the focal species, first 50%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 50%", 10)
+Species <- rep("IPPU", 10)
+Treatment <- rep("IPPU 50%", 10)
 Treatment.number <- seq(1:10)
 Seed.production <- rep(0, 10)
-caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+ippu_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
 #adding the focal species, 100%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 100%", 10)
+Species <- rep("IPPU", 10)
+Treatment <- rep("IPPU 100%", 10)
 Treatment.number <- seq(1:10)
 Seed.production <- rep(0, 10)
-caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+ippu_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
 #Order from lower to higher values the average, to plot it nicely
-caan_seed_set <- caan_seed_set[,-4]
-colnames(caan_seed_set)[1] <- "Species"
-colnames(caan_seed_set)[2] <- "Treatment"
-colnames(caan_seed_set)[3] <- "Treatment.number"
-colnames(caan_seed_set)[4] <- "Seed.production"
-caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
-caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
-caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
+
+ippu_seed_set <- rbind(ippu_seed_set, ippu_50, ippu_100)
+ippu_seed_set$Treatment<- as.character(ippu_seed_set$Treatment)
+ippu_seed_set <- ippu_seed_set[order(ippu_seed_set$Treatment),]
 
@@
 library(stringr)
-caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
-caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
-colnames(caan_seed_set_div)=c("non_focal","percentage")
-caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
-caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")
+ippu_seed_set_div <- str_split_fixed(as.character(ippu_seed_set$Treatment), " ", 2)
+ippu_seed_set_div <- data.frame(ippu_seed_set_div, stringsAsFactors = F)
+colnames(ippu_seed_set_div)=c("non_focal","percentage")
+ippu_seed_set_bind <- cbind(ippu_seed_set,ippu_seed_set_div)
+ippu_seed_set_bind <- filter(ippu_seed_set_bind, percentage!="100%")
 
 #Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+#pein_seed_set_common <- filter(ippu_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
 
-caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
-caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
-caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
-caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))
+ippu_seed_set_cross <- filter(ippu_seed_set_bind, Treatment %in% c("cross"))
+ippu_seed_set_self <- filter(ippu_seed_set_bind, Treatment %in% c("self"))
+ippu_seed_set_control <- filter(ippu_seed_set_bind, Treatment %in% c("control"))
+ippu_seed_set_flower <- filter(ippu_seed_set_bind, Treatment %in% c("flower control"))
 
@@
 # I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("cross"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("self"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("control"),]
+ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("flower control"),]
 
-caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
-                           caan_seed_set_flower)
+ippu_seed_set_final<-rbind(ippu_seed_set_bind,ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
+                           ippu_seed_set_flower)
 #deleting extra columns used for data formating
-caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
+ippu_seed_set_final=ippu_seed_set_final[,-c(5,6)]
 #adding NA'S to the focal species
-caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA
+ippu_seed_set_final[ippu_seed_set_final$Treatment==c("IPPU 50%"),4] <- NA
 
 #changing non_focal species name
-caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
+ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
 
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"
 
 #Different colour per family
-b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
+  labs(title="Ipomea purpurea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
 
-#
-##
-###
-#S. LYCOPERSICUM
-###
-##
-#
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
 
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+#read data and cleaning
 
-#adding the focal species, first 50%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-soly_seed_set <- soly_seed_set[,-4]
-colnames(soly_seed_set)[1] <- "Species"
-colnames(soly_seed_set)[2] <- "Treatment"
-colnames(soly_seed_set)[3] <- "Treatment.number"
-colnames(soly_seed_set)[4] <- "Seed.production"
-soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
-soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
-soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
-soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
-colnames(soly_seed_set_div)=c("non_focal","percentage")
-soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
-soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
-soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
-soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
-soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]
-
-soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
-                           soly_seed_set_flower)
-#deleting extra columns used for data formating
-soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA
-
-#changing non_focal species name
-soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-#Different colour per family
-c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#S. MELONGENA
-###
-##
-#
-
-#Taking out species that weren't used
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
-
-#adding the focal species, first 50%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-some_seed_set<- some_seed_set[,-3]
-colnames(some_seed_set)[3] <- "Treatment.number"
-colnames(some_seed_set)[4] <- "Seed.production"
-some_seed_set <- rbind(some_seed_set, some_50, some_100)
-some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
-some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
-some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
-colnames(some_seed_set_div)=c("non_focal","percentage")
-some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
-some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
-some_seed_set_self <- filter(some_seed_set_bind, non_focal %in% c("SELF"))
-some_seed_set_control <- filter(some_seed_set_bind, non_focal %in% c("CONTROL"))
-some_seed_set_flower <- filter(some_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CROSS"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("SELF"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CONTROL"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("FLOWER"),]
-
-some_seed_set_final<-rbind(some_seed_set_bind,some_seed_set_cross, some_seed_set_self, some_seed_set_control,
-                           some_seed_set_flower)
-#deleting extra columns used for data formating
-some_seed_set_final=some_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-some_seed_set_final[some_seed_set_final$Treatment==c("SOME 50%"),4] <- NA
-
-#changing non_focal species name
-some_seed_set_final$Treatment=as.character(some_seed_set_final$Treatment)
-some_seed_set_final$Family[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-#Different colour per family
-d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.2) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-gl <- lapply(list(a,b,c,d), ggplotGrob)
+gl <- lapply(list(a,b), ggplotGrob)
 library(grid)
@@
 
-grobz <- lapply(list(a, b, c, d), ggplotGrob)
-grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
-                                        rbind(grobz[[2]], grobz[[4]], size = "last")),
-                           ncol = 2, top="b")
+grobz <- lapply(list(a, b), ggplotGrob)
+grobz.plot <- arrangeGrob(grobs = list(rbind(grobz[[1]], size = "last"),
+                                        rbind(grobz[[2]], size = "last")), ncol = 2,top="hhsdgsujhdg")
 

### 2018-08-06 Rmd/Data_visualization.Rmd
changes

@@
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
@@
 brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
-brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("Flower"))
+brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))
 
@@
 brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
-brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Flower"),]
+brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]
 

### 2018-08-06 Scripts/ggplot_species_seed_set/s_alba_ggplot.R

@@ -46,7 +46,7 @@ sial_seed_set_bind <- filter(sial_seed_set_bind, percentage!="100%")
 sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
 sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
 sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
-sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("FC"))
+sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("Flower"))
 
 #Changing 0 for NA'S FOCAL species
 
@@ -57,7 +57,7 @@ sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("FC"))
 sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
 sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
 sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
-sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("FC"),]
+sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Flower"),]
 
 sial_seed_set_final<-rbind(sial_seed_set_bind,sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
                            sial_seed_set_flower)

### 2018-08-06 Rmd/Data_visualization.Rmd
changes

@@
 pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
-
+pein_seed_set_brassicaceae <- filter(pein_seed_set_final, Family %in% c("Brassicaceae"))
+pein_seed_set_convolvulaceae <- filter(pein_seed_set_final, Family %in% c("Convolvulaceae"))
+pein_seed_set_solanaceae <- filter(pein_seed_set_final, Family %in% c("Solanaceae"))
+pein_seed_set_final$Family[is.na(pein_seed_set_final$Family)] <- "Solanum lycopersicum"
+pein_seed_set_cross=pein_seed_set_cross[,-c(5,6)]
+pein_seed_set_cross$Family <- "other"
+pein_seed_set_self=pein_seed_set_self[,-c(5,6)]
+pein_seed_set_self$Family <- "other"
+pein_seed_set_control=pein_seed_set_control[,-c(5,6)]
+pein_seed_set_control$Family <- "other"
+pein_seed_set_flower=pein_seed_set_flower[,-c(5,6)]
+pein_seed_set_flower$Family <- "other"
+
+pein_seed_set_final=rbind(pein_seed_set_brassicaceae, pein_seed_set_convolvulaceae, 
+                          pein_seed_set_solanaceae, pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
+                          pein_seed_set_flower)
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
 #Colur per family
@@
   labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 
+caan_seed_set_brassicaceae <- filter(caan_seed_set_final, Family %in% c("Brassicaceae"))
+caan_seed_set_convolvulaceae <- filter(caan_seed_set_final, Family %in% c("Convolvulaceae"))
+caan_seed_set_solanaceae <- filter(caan_seed_set_final, Family %in% c("Solanaceae"))
+caan_seed_set_final$Family[is.na(caan_seed_set_final$Family)] <- "Solanum lycopersicum"
+caan_seed_set_cross=caan_seed_set_cross[,-c(5,6)]
+caan_seed_set_cross$Family <- "other"
+caan_seed_set_self=caan_seed_set_self[,-c(5,6)]
+caan_seed_set_self$Family <- "other"
+caan_seed_set_control=caan_seed_set_control[,-c(5,6)]
+caan_seed_set_control$Family <- "other"
+caan_seed_set_flower=caan_seed_set_flower[,-c(5,6)]
+caan_seed_set_flower$Family <- "other"
+
+caan_seed_set_final=rbind(caan_seed_set_brassicaceae, caan_seed_set_convolvulaceae, 
+                          caan_seed_set_solanaceae, caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
+                          caan_seed_set_flower)
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+#Colur per family
 #Different colour per family
 b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Capsicum annuum",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 #Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+#caan_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
 
@@
 soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+
+soly_seed_set_brassicaceae <- filter(soly_seed_set_final, Family %in% c("Brassicaceae"))
+soly_seed_set_convolvulaceae <- filter(soly_seed_set_final, Family %in% c("Convolvulaceae"))
+soly_seed_set_solanaceae <- filter(soly_seed_set_final, Family %in% c("Solanaceae"))
+soly_seed_set_final$Family[is.na(soly_seed_set_final$Family)] <- "Solanum lycopersicum"
+soly_seed_set_cross=soly_seed_set_cross[,-c(5,6)]
+soly_seed_set_cross$Family <- "other"
+soly_seed_set_self=soly_seed_set_self[,-c(5,6)]
+soly_seed_set_self$Family <- "other"
+soly_seed_set_control=soly_seed_set_control[,-c(5,6)]
+soly_seed_set_control$Family <- "other"
+soly_seed_set_flower=soly_seed_set_flower[,-c(5,6)]
+soly_seed_set_flower$Family <- "other"
+
+soly_seed_set_final=rbind(soly_seed_set_brassicaceae, soly_seed_set_convolvulaceae, 
+                          soly_seed_set_solanaceae, soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
+                          soly_seed_set_flower)
 soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CROSS"] <- "Cross"
@@
 
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
 #Different colour per family
@@
   labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 
+some_seed_set_brassicaceae <- filter(some_seed_set_final, Family %in% c("Brassicaceae"))
+some_seed_set_convolvulaceae <- filter(some_seed_set_final, Family %in% c("Convolvulaceae"))
+some_seed_set_solanaceae <- filter(some_seed_set_final, Family %in% c("Solanaceae"))
+some_seed_set_final$Family[is.na(some_seed_set_final$Family)] <- "Solanum lycopersicum"
+some_seed_set_cross=some_seed_set_cross[,-c(5,6)]
+some_seed_set_cross$Family <- "other"
+some_seed_set_self=some_seed_set_self[,-c(5,6)]
+some_seed_set_self$Family <- "other"
+some_seed_set_control=some_seed_set_control[,-c(5,6)]
+some_seed_set_control$Family <- "other"
+some_seed_set_flower=some_seed_set_flower[,-c(5,6)]
+some_seed_set_flower$Family <- "other"
+
+some_seed_set_final=rbind(some_seed_set_brassicaceae, some_seed_set_convolvulaceae, 
+                          some_seed_set_solanaceae, some_seed_set_cross, some_seed_set_self, some_seed_set_control,
+                          some_seed_set_flower)
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CROSS"] <- "Cross"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SELF"] <- "Self"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CONTROL"] <- "Control"
+some_seed_set_final$Treatment[some_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
 #Different colour per family
 d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Solanum melongena",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Brassicaceae"
+ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
 ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"

### 2018-08-07 Rmd/Data_visualization.Rmd
last changes

@@
 
+brol_seed_set_brassicaceae <- filter(brol_seed_set_final, Family %in% c("Brassicaceae"))
+brol_seed_set_convolvulaceae <- filter(brol_seed_set_final, Family %in% c("Convolvulaceae"))
+brol_seed_set_solanaceae <- filter(brol_seed_set_final, Family %in% c("Solanaceae"))
+brol_seed_set_final$Family[is.na(brol_seed_set_final$Family)] <- "Solanum lycopersicum"
+
+brol_seed_set_cross=brol_seed_set_cross[,-c(5,6)]
+brol_seed_set_cross$Family <- "other"
+brol_seed_set_self=brol_seed_set_self[,-c(5,6)]
+brol_seed_set_self$Family <- "other"
+brol_seed_set_control=brol_seed_set_control[,-c(5,6)]
+brol_seed_set_control$Family <- "other"
+brol_seed_set_flower=brol_seed_set_flower[,-c(5,6)]
+brol_seed_set_flower$Family <- "other"
+
+brol_seed_set_final=rbind(brol_seed_set_brassicaceae, brol_seed_set_convolvulaceae, 
+                          brol_seed_set_solanaceae, brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
+                          brol_seed_set_flower)
 #Different colour per family
-a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+a <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 
+brra_seed_set_brassicaceae <- filter(brra_seed_set_final, Family %in% c("Brassicaceae"))
+brra_seed_set_convolvulaceae <- filter(brra_seed_set_final, Family %in% c("Convolvulaceae"))
+brra_seed_set_solanaceae <- filter(brra_seed_set_final, Family %in% c("Solanaceae"))
+brra_seed_set_final$Family[is.na(brra_seed_set_final$Family)] <- "Solanum lycopersicum"
+
+brra_seed_set_cross=brra_seed_set_cross[,-c(5,6)]
+brra_seed_set_cross$Family <- "other"
+brra_seed_set_self=brra_seed_set_self[,-c(5,6)]
+brra_seed_set_self$Family <- "other"
+brra_seed_set_control=brra_seed_set_control[,-c(5,6)]
+brra_seed_set_control$Family <- "other"
+brra_seed_set_flower=brra_seed_set_flower[,-c(5,6)]
+brra_seed_set_flower$Family <- "other"
+
+brra_seed_set_final=rbind(brra_seed_set_brassicaceae, brra_seed_set_convolvulaceae, 
+                          brra_seed_set_solanaceae, brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
+                          brra_seed_set_flower)
+
 #Different colour per family
-b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Brassica rapa",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 
+ersa_seed_set_brassicaceae <- filter(ersa_seed_set_final, Family %in% c("Brassicaceae"))
+ersa_seed_set_convolvulaceae <- filter(ersa_seed_set_final, Family %in% c("Convolvulaceae"))
+ersa_seed_set_solanaceae <- filter(ersa_seed_set_final, Family %in% c("Solanaceae"))
+ersa_seed_set_final$Family[is.na(ersa_seed_set_final$Family)] <- "Solanum lycopersicum"
+
+ersa_seed_set_cross=ersa_seed_set_cross[,-c(5,6)]
+ersa_seed_set_cross$Family <- "other"
+ersa_seed_set_self=ersa_seed_set_self[,-c(5,6)]
+ersa_seed_set_self$Family <- "other"
+ersa_seed_set_control=ersa_seed_set_control[,-c(5,6)]
+ersa_seed_set_control$Family <- "other"
+ersa_seed_set_flower=ersa_seed_set_flower[,-c(5,6)]
+ersa_seed_set_flower$Family <- "other"
+
+ersa_seed_set_final=rbind(ersa_seed_set_brassicaceae, ersa_seed_set_convolvulaceae, 
+                          ersa_seed_set_solanaceae, ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
+                          ersa_seed_set_flower)
+
 #Different colour per family
@@
   labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-#
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
 ##
@@
 
+sial_seed_set_brassicaceae <- filter(sial_seed_set_final, Family %in% c("Brassicaceae"))
+sial_seed_set_convolvulaceae <- filter(sial_seed_set_final, Family %in% c("Convolvulaceae"))
+sial_seed_set_solanaceae <- filter(sial_seed_set_final, Family %in% c("Solanaceae"))
+sial_seed_set_final$Family[is.na(sial_seed_set_final$Family)] <- "Solanum lycopersicum"
+
+sial_seed_set_cross=sial_seed_set_cross[,-c(5,6)]
+sial_seed_set_cross$Family <- "other"
+sial_seed_set_self=sial_seed_set_self[,-c(5,6)]
+sial_seed_set_self$Family <- "other"
+sial_seed_set_control=sial_seed_set_control[,-c(5,6)]
+sial_seed_set_control$Family <- "other"
+sial_seed_set_flower=sial_seed_set_flower[,-c(5,6)]
+sial_seed_set_flower$Family <- "other"
+
+sial_seed_set_final=rbind(sial_seed_set_brassicaceae, sial_seed_set_convolvulaceae, 
+                          sial_seed_set_solanaceae, sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
+                          sial_seed_set_flower)
+
 #Different colour per family
 d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Sinapis alba",x="", y = "", tag= "D")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+ theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+ stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") + theme(legend.position="none")
+  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 
+ipaq_seed_set_brassicaceae <- filter(ipaq_seed_set_final, Family %in% c("Brassicaceae"))
+ipaq_seed_set_convolvulaceae <- filter(ipaq_seed_set_final, Family %in% c("Convolvulaceae"))
+ipaq_seed_set_solanaceae <- filter(ipaq_seed_set_final, Family %in% c("Solanaceae"))
+ipaq_seed_set_final$Family[is.na(ipaq_seed_set_final$Family)] <- "Solanum lycopersicum"
+
+ipaq_seed_set_cross=ipaq_seed_set_cross[,-c(5,6)]
+ipaq_seed_set_cross$Family <- "other"
+ipaq_seed_set_self=ipaq_seed_set_self[,-c(5,6)]
+ipaq_seed_set_self$Family <- "other"
+ipaq_seed_set_control=ipaq_seed_set_control[,-c(5,6)]
+ipaq_seed_set_control$Family <- "other"
+ipaq_seed_set_flower=ipaq_seed_set_flower[,-c(5,6)]
+ipaq_seed_set_flower$Family <- "other"
+
+ipaq_seed_set_final=rbind(ipaq_seed_set_brassicaceae, ipaq_seed_set_convolvulaceae, 
+                          ipaq_seed_set_solanaceae, ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
+                          ipaq_seed_set_flower)
+
 ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
@@
 ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
-
 #Different colour per family
 a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Ipomea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  labs(title="Ipomoea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 
@@
 
+ippu_seed_set_brassicaceae <- filter(ippu_seed_set_final, Family %in% c("Brassicaceae"))
+ippu_seed_set_convolvulaceae <- filter(ippu_seed_set_final, Family %in% c("Convolvulaceae"))
+ippu_seed_set_solanaceae <- filter(ippu_seed_set_final, Family %in% c("Solanaceae"))
+ippu_seed_set_final$Family[is.na(ippu_seed_set_final$Family)] <- "Solanum lycopersicum"
+
+ippu_seed_set_cross=ippu_seed_set_cross[,-c(5,6)]
+ippu_seed_set_cross$Family <- "other"
+ippu_seed_set_self=ippu_seed_set_self[,-c(5,6)]
+ippu_seed_set_self$Family <- "other"
+ippu_seed_set_control=ippu_seed_set_control[,-c(5,6)]
+ippu_seed_set_control$Family <- "other"
+ippu_seed_set_flower=ippu_seed_set_flower[,-c(5,6)]
+ippu_seed_set_flower$Family <- "other"
+
+ippu_seed_set_final=rbind(ippu_seed_set_brassicaceae, ippu_seed_set_convolvulaceae, 
+                          ippu_seed_set_solanaceae, ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
+                          ippu_seed_set_flower)
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"
+
 #Different colour per family
 b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Ipomea purpurea",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) + geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family)) + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+  labs(title="Ipomoea purpurea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
 

### 2018-08-07 Scripts/ggplot_species_seed_set/p_integrifolia_ggplot.R

@@ -5,7 +5,9 @@
 library(reshape2)
 library(ggplot2)
 library(dplyr)
-
+library(gridExtra)
+library(grid)
+library(lattice)
 #read data and cleaning
 pein_seed_set <- read.csv("Data/species_seed_set/PEIN_seed_set.csv", sep=";")
 #removing samples where seeds got lost, first ones of the experiment
@@ -70,8 +72,6 @@ pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set
                            pein_seed_set_flower)
 #deleting extra columns used for data formating
 pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
-
-
 #adding NA'S to the focal species
 pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
 #changing non_focal species name
@@ -97,13 +97,14 @@ pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Pet
 pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
 pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
 pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CROSS"] <- "Cross"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SELF"] <- "Self"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CONTROL"] <- "Control"
+pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
 pein_seed_set_brassicaceae <- filter(pein_seed_set_final, Family %in% c("Brassicaceae"))
 pein_seed_set_convolvulaceae <- filter(pein_seed_set_final, Family %in% c("Convolvulaceae"))
 pein_seed_set_solanaceae <- filter(pein_seed_set_final, Family %in% c("Solanaceae"))
 pein_seed_set_final$Family[is.na(pein_seed_set_final$Family)] <- "Solanum lycopersicum"
-
 pein_seed_set_cross=pein_seed_set_cross[,-c(5,6)]
[…]

### 2018-08-07 Rmd/Data_visualization.Rmd
reading in markdown just the csv processed

@@
 #read data and cleaning
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-#removing samples where seeds got lost, first ones of the experiment
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
-
-#
-##
-###
-#PETUNIA
-###
-##
-#
-#Removing RARA, species not considered because sterility
-
-pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
-
-#adding the focal species, first 50%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
-#adding the focal species, 100%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
-#Order from lower to higher values the average, to plot it nicely
-pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
-pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
-pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
-pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
-colnames(pein_seed_set_div)=c("non_focal","percentage")
-pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
-pein_seed_set_bind <- filter(pein_seed_set_bind, percentage!="100%")
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(pein_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-pein_seed_set_cross <- filter(pein_seed_set_bind, non_focal %in% c("CROSS"))
-pein_seed_set_self <- filter(pein_seed_set_bind, non_focal %in% c("SELF"))
-pein_seed_set_control <- filter(pein_seed_set_bind, non_focal %in% c("CONTROL"))
-pein_seed_set_flower <- filter(pein_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CROSS"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("SELF"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("CONTROL"),]
-pein_seed_set_bind=pein_seed_set_bind[pein_seed_set_bind$non_focal!=c("FLOWER"),]
-
-pein_seed_set_final<-rbind(pein_seed_set_bind,pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
-                           pein_seed_set_flower)
-#deleting extra columns used for data formating
-pein_seed_set_final=pein_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-pein_seed_set_final[pein_seed_set_final$Treatment==c("PEIN 50%"),4] <- NA
-#changing non_focal species name
-pein_seed_set_final$Treatment=as.character(pein_seed_set_final$Treatment)
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Convolvulaceae"
-pein_seed_set_final$Family[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="IPPU 50 %"] <- "Ipomoea purpurea"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CROSS"] <- "Cross"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="SELF"] <- "Self"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="CONTROL"] <- "Control"
-pein_seed_set_final$Treatment[pein_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
-pein_seed_set_brassicaceae <- filter(pein_seed_set_final, Family %in% c("Brassicaceae"))
-pein_seed_set_convolvulaceae <- filter(pein_seed_set_final, Family %in% c("Convolvulaceae"))
-pein_seed_set_solanaceae <- filter(pein_seed_set_final, Family %in% c("Solanaceae"))
-pein_seed_set_final$Family[is.na(pein_seed_set_final$Family)] <- "Solanum lycopersicum"
-pein_seed_set_cross=pein_seed_set_cross[,-c(5,6)]
-pein_seed_set_cross$Family <- "other"
-pein_seed_set_self=pein_seed_set_self[,-c(5,6)]
-pein_seed_set_self$Family <- "other"
-pein_seed_set_control=pein_seed_set_control[,-c(5,6)]
-pein_seed_set_control$Family <- "other"
-pein_seed_set_flower=pein_seed_set_flower[,-c(5,6)]
-pein_seed_set_flower$Family <- "other"
-
-pein_seed_set_final=rbind(pein_seed_set_brassicaceae, pein_seed_set_convolvulaceae, 
-                          pein_seed_set_solanaceae, pein_seed_set_cross, pein_seed_set_self, pein_seed_set_control,
-                          pein_seed_set_flower)
+pein_seed_set_final <- read.csv("Data/pein_seed_set_final.csv")
+pein_seed_set_final=pein_seed_set_final[,-1]
 

### 2018-08-07 Rmd/Data_visualization.Rmd
caan csv processed file

@@
 pein_seed_set_final=pein_seed_set_final[,-1]
-
+#load the palette for all the 4 plots
 cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
@@
 #
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
-
-#adding the focal species, first 50%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-caan_seed_set <- caan_seed_set[,-4]
-colnames(caan_seed_set)[1] <- "Species"
-colnames(caan_seed_set)[2] <- "Treatment"
-colnames(caan_seed_set)[3] <- "Treatment.number"
-colnames(caan_seed_set)[4] <- "Seed.production"
-caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
-caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
-caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-caan_seed_set_div <- str_split_fixed(as.character(caan_seed_set$Treatment), " ", 2)
-caan_seed_set_div <- data.frame(caan_seed_set_div, stringsAsFactors = F)
-colnames(caan_seed_set_div)=c("non_focal","percentage")
-caan_seed_set_bind <- cbind(caan_seed_set,caan_seed_set_div)
-caan_seed_set_bind <- filter(caan_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(caan_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-caan_seed_set_cross <- filter(caan_seed_set_bind, non_focal %in% c("CROSS"))
-caan_seed_set_self <- filter(caan_seed_set_bind, non_focal %in% c("SELF"))
-caan_seed_set_control <- filter(caan_seed_set_bind, non_focal %in% c("CONTROL"))
-caan_seed_set_flower <- filter(caan_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CROSS"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("SELF"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("CONTROL"),]
-caan_seed_set_bind=caan_seed_set_bind[caan_seed_set_bind$non_focal!=c("FLOWER"),]
-
-caan_seed_set_final<-rbind(caan_seed_set_bind,caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
-                           caan_seed_set_flower)
-#deleting extra columns used for data formating
-caan_seed_set_final=caan_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-caan_seed_set_final[caan_seed_set_final$Treatment==c("CAAN 50%"),4] <- NA
-
-#changing non_focal species name
-caan_seed_set_final$Treatment=as.character(caan_seed_set_final$Treatment)
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CROSS"] <- "Cross"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SELF"] <- "Self"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CONTROL"] <- "Control"
-caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
-
-caan_seed_set_brassicaceae <- filter(caan_seed_set_final, Family %in% c("Brassicaceae"))
-caan_seed_set_convolvulaceae <- filter(caan_seed_set_final, Family %in% c("Convolvulaceae"))
-caan_seed_set_solanaceae <- filter(caan_seed_set_final, Family %in% c("Solanaceae"))
-caan_seed_set_final$Family[is.na(caan_seed_set_final$Family)] <- "Solanum lycopersicum"
-caan_seed_set_cross=caan_seed_set_cross[,-c(5,6)]
-caan_seed_set_cross$Family <- "other"
-caan_seed_set_self=caan_seed_set_self[,-c(5,6)]
-caan_seed_set_self$Family <- "other"
-caan_seed_set_control=caan_seed_set_control[,-c(5,6)]
-caan_seed_set_control$Family <- "other"
-caan_seed_set_flower=caan_seed_set_flower[,-c(5,6)]
-caan_seed_set_flower$Family <- "other"
-
-caan_seed_set_final=rbind(caan_seed_set_brassicaceae, caan_seed_set_convolvulaceae, 
-                          caan_seed_set_solanaceae, caan_seed_set_cross, caan_seed_set_self, caan_seed_set_control,
-                          caan_seed_set_flower)
-
-cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+caan_seed_set_final <- read.csv("Data/caan_seed_set_final.csv")
+caan_seed_set_final=caan_seed_set_final[,-1]
+
 #Colur per family

### 2018-08-07 Scripts/ggplot_species_seed_set/c_annuum_ggplot.R

@@ -1,3 +1,4 @@
+
 #
 ##
 ###
@@ -70,7 +71,7 @@ caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BROL 50%"] <- "Brassi
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-caan_seed_set_final$Family[caan_seed_set_final$Treatment=="caan 50%"] <- "Solanaceae"
+caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
 caan_seed_set_final$Family[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
@@ -87,8 +88,37 @@ caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="PEIN 50%"] <- "Pet
 caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
 caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
 caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CROSS"] <- "Cross"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="SELF"] <- "Self"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="CONTROL"] <- "Control"
+caan_seed_set_final$Treatment[caan_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
 
+caan_seed_set_brassicaceae <- filter(caan_seed_set_final, Family %in% c("Brassicaceae"))
+caan_seed_set_convolvulaceae <- filter(caan_seed_set_final, Family %in% c("Convolvulaceae"))
[…]

### 2018-08-07 Rmd/Data_visualization.Rmd
last changes

@@
 
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-soly_seed_set <- soly_seed_set[,-4]
-colnames(soly_seed_set)[1] <- "Species"
-colnames(soly_seed_set)[2] <- "Treatment"
-colnames(soly_seed_set)[3] <- "Treatment.number"
-colnames(soly_seed_set)[4] <- "Seed.production"
-soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
-soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
-soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
-soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
-colnames(soly_seed_set_div)=c("non_focal","percentage")
-soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
-soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#caan_seed_set_common <- filter(soly_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-soly_seed_set_cross <- filter(soly_seed_set_bind, non_focal %in% c("CROSS"))
-soly_seed_set_self <- filter(soly_seed_set_bind, non_focal %in% c("SELF"))
-soly_seed_set_control <- filter(soly_seed_set_bind, non_focal %in% c("CONTROL"))
-soly_seed_set_flower <- filter(soly_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CROSS"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("SELF"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("CONTROL"),]
-soly_seed_set_bind=soly_seed_set_bind[soly_seed_set_bind$non_focal!=c("FLOWER"),]
-
-soly_seed_set_final<-rbind(soly_seed_set_bind,soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
-                           soly_seed_set_flower)
-#deleting extra columns used for data formating
-soly_seed_set_final=soly_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-soly_seed_set_final[soly_seed_set_final$Treatment==c("SOLY 50%"),4] <- NA
-
-#changing non_focal species name
-soly_seed_set_final$Treatment=as.character(soly_seed_set_final$Treatment)
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-soly_seed_set_final$Family[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-soly_seed_set_brassicaceae <- filter(soly_seed_set_final, Family %in% c("Brassicaceae"))
-soly_seed_set_convolvulaceae <- filter(soly_seed_set_final, Family %in% c("Convolvulaceae"))
-soly_seed_set_solanaceae <- filter(soly_seed_set_final, Family %in% c("Solanaceae"))
-soly_seed_set_final$Family[is.na(soly_seed_set_final$Family)] <- "Solanum lycopersicum"
-soly_seed_set_cross=soly_seed_set_cross[,-c(5,6)]
-soly_seed_set_cross$Family <- "other"
-soly_seed_set_self=soly_seed_set_self[,-c(5,6)]
-soly_seed_set_self$Family <- "other"
-soly_seed_set_control=soly_seed_set_control[,-c(5,6)]
-soly_seed_set_control$Family <- "other"
-soly_seed_set_flower=soly_seed_set_flower[,-c(5,6)]
-soly_seed_set_flower$Family <- "other"
-
-soly_seed_set_final=rbind(soly_seed_set_brassicaceae, soly_seed_set_convolvulaceae, 
-                          soly_seed_set_solanaceae, soly_seed_set_cross, soly_seed_set_self, soly_seed_set_control,
-                          soly_seed_set_flower)
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CROSS"] <- "Cross"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="SELF"] <- "Self"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="CONTROL"] <- "Control"
-soly_seed_set_final$Treatment[soly_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
+soly_seed_set_final <- read.csv("Data/soly_seed_set_final.csv")
+soly_seed_set_final=soly_seed_set_final[,-1]
 
@@
 
-#Taking out species that weren't used
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
-
-#adding the focal species, first 50%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-some_seed_set<- some_seed_set[,-3]
-colnames(some_seed_set)[3] <- "Treatment.number"
-colnames(some_seed_set)[4] <- "Seed.production"
-some_seed_set <- rbind(some_seed_set, some_50, some_100)
-some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
-some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
-some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
-colnames(some_seed_set_div)=c("non_focal","percentage")
-some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
-some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
-some_seed_set_self <- filter(some_seed_set_bind, non_focal %in% c("SELF"))
-some_seed_set_control <- filter(some_seed_set_bind, non_focal %in% c("CONTROL"))
-some_seed_set_flower <- filter(some_seed_set_bind, non_focal %in% c("FLOWER"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CROSS"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("SELF"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("CONTROL"),]
-some_seed_set_bind=some_seed_set_bind[some_seed_set_bind$non_focal!=c("FLOWER"),]
-
-some_seed_set_final<-rbind(some_seed_set_bind,some_seed_set_cross, some_seed_set_self, some_seed_set_control,
-                           some_seed_set_flower)
-#deleting extra columns used for data formating
-some_seed_set_final=some_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-some_seed_set_final[some_seed_set_final$Treatment==c("SOME 50%"),4] <- NA
-
-#changing non_focal species name
-some_seed_set_final$Treatment=as.character(some_seed_set_final$Treatment)
-some_seed_set_final$Family[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-some_seed_set_final$Family[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CROSS"] <- "Cross"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SELF"] <- "Self"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CONTROL"] <- "Control"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
-
-some_seed_set_brassicaceae <- filter(some_seed_set_final, Family %in% c("Brassicaceae"))
-some_seed_set_convolvulaceae <- filter(some_seed_set_final, Family %in% c("Convolvulaceae"))
-some_seed_set_solanaceae <- filter(some_seed_set_final, Family %in% c("Solanaceae"))
-some_seed_set_final$Family[is.na(some_seed_set_final$Family)] <- "Solanum lycopersicum"
-some_seed_set_cross=some_seed_set_cross[,-c(5,6)]
-some_seed_set_cross$Family <- "other"
-some_seed_set_self=some_seed_set_self[,-c(5,6)]
-some_seed_set_self$Family <- "other"
-some_seed_set_control=some_seed_set_control[,-c(5,6)]
-some_seed_set_control$Family <- "other"
-some_seed_set_flower=some_seed_set_flower[,-c(5,6)]
-some_seed_set_flower$Family <- "other"
-
-some_seed_set_final=rbind(some_seed_set_brassicaceae, some_seed_set_convolvulaceae, 
-                          some_seed_set_solanaceae, some_seed_set_cross, some_seed_set_self, some_seed_set_control,
-                          some_seed_set_flower)
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CROSS"] <- "Cross"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="SELF"] <- "Self"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="CONTROL"] <- "Control"
-some_seed_set_final$Treatment[some_seed_set_final$Treatment=="FLOWER CONTROL"] <- "Flower control"
-
-cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+some_seed_set_final <- read.csv("Data/some_seed_set_final.csv")
+some_seed_set_final=some_seed_set_final[,-1]
+
 #Different colour per family

### 2018-08-30 Rmd/Data_visualization.Rmd

@@
 
-brol_seed_set <- read.csv("Data/BROL_seed_set.csv", sep=";")
-brol_seed_set <- filter(brol_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("BROL", 10)
-Treatment <- rep("BROL 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-brol_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("BROL", 10)
-Treatment <- rep("BROL 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-brol_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-colnames(brol_seed_set)[1] <- "Species"
-colnames(brol_seed_set)[2] <- "Treatment"
-colnames(brol_seed_set)[3] <- "Treatment.number"
-colnames(brol_seed_set)[4] <- "Seed.production"
-brol_seed_set <- rbind(brol_seed_set, brol_50, brol_100)
-brol_seed_set$Treatment<- as.character(brol_seed_set$Treatment)
-brol_seed_set <- brol_seed_set[order(brol_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-brol_seed_set_div <- str_split_fixed(as.character(brol_seed_set$Treatment), " ", 2)
-brol_seed_set_div <- data.frame(brol_seed_set_div, stringsAsFactors = F)
-colnames(brol_seed_set_div)=c("non_focal","percentage")
-brol_seed_set_bind <- cbind(brol_seed_set,brol_seed_set_div)
-brol_seed_set_bind <- filter(brol_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(brol_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
-brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
-brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
-brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
-brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
-brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
-brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]
-
-brol_seed_set_final<-rbind(brol_seed_set_bind,brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
-                           brol_seed_set_flower)
-#deleting extra columns used for data formating
-brol_seed_set_final=brol_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-brol_seed_set_final[brol_seed_set_final$Treatment==c("BROL 50%"),4] <- NA
-
-#changing non_focal species name
-brol_seed_set_final$Treatment=as.character(brol_seed_set_final$Treatment)
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="FC"] <- "Flower control"
-
-brol_seed_set_brassicaceae <- filter(brol_seed_set_final, Family %in% c("Brassicaceae"))
-brol_seed_set_convolvulaceae <- filter(brol_seed_set_final, Family %in% c("Convolvulaceae"))
-brol_seed_set_solanaceae <- filter(brol_seed_set_final, Family %in% c("Solanaceae"))
-brol_seed_set_final$Family[is.na(brol_seed_set_final$Family)] <- "Solanum lycopersicum"
-
-brol_seed_set_cross=brol_seed_set_cross[,-c(5,6)]
-brol_seed_set_cross$Family <- "other"
-brol_seed_set_self=brol_seed_set_self[,-c(5,6)]
-brol_seed_set_self$Family <- "other"
-brol_seed_set_control=brol_seed_set_control[,-c(5,6)]
-brol_seed_set_control$Family <- "other"
-brol_seed_set_flower=brol_seed_set_flower[,-c(5,6)]
-brol_seed_set_flower$Family <- "other"
-
-brol_seed_set_final=rbind(brol_seed_set_brassicaceae, brol_seed_set_convolvulaceae, 
-                          brol_seed_set_solanaceae, brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
-                          brol_seed_set_flower)
+brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
+brol_seed_set_final=brol_seed_set_final[,-1]
 #Different colour per family
-a <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
@@
 
-brra_seed_set <- read.csv("Data/BRRA_seed_set.csv", sep=";")
-brra_seed_set <- filter(brra_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("BRRA", 10)
-Treatment <- rep("BRRA 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-brra_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("BRRA", 10)
-Treatment <- rep("BRRA 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-brra_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-colnames(brra_seed_set)[1] <- "Species"
-colnames(brra_seed_set)[2] <- "Treatment"
-colnames(brra_seed_set)[3] <- "Treatment.number"
-colnames(brra_seed_set)[4] <- "Seed.production"
-brra_seed_set <- rbind(brra_seed_set, brra_50, brra_100)
-brra_seed_set$Treatment<- as.character(brra_seed_set$Treatment)
-brra_seed_set <- brra_seed_set[order(brra_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-brra_seed_set_div <- str_split_fixed(as.character(brra_seed_set$Treatment), " ", 2)
-brra_seed_set_div <- data.frame(brra_seed_set_div, stringsAsFactors = F)
-colnames(brra_seed_set_div)=c("non_focal","percentage")
-brra_seed_set_bind <- cbind(brra_seed_set,brra_seed_set_div)
-brra_seed_set_bind <- filter(brra_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(brra_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-brra_seed_set_cross <- filter(brra_seed_set_bind, non_focal %in% c("Cross"))
-brra_seed_set_self <- filter(brra_seed_set_bind, non_focal %in% c("Self"))
-brra_seed_set_control <- filter(brra_seed_set_bind, non_focal %in% c("Control"))
-brra_seed_set_flower <- filter(brra_seed_set_bind, non_focal %in% c("Flower"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Cross"),]
-brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Self"),]
-brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Control"),]
-brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Flower"),]
-
-brra_seed_set_final<-rbind(brra_seed_set_bind,brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
-                           brra_seed_set_flower)
-#deleting extra columns used for data formating
-brra_seed_set_final=brra_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-brra_seed_set_final[brra_seed_set_final$Treatment==c("BRRA 50%"),4] <- NA
-
-#changing non_focal species name
-brra_seed_set_final$Treatment=as.character(brra_seed_set_final$Treatment)
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="FC"] <- "Flower control"
-
-brra_seed_set_brassicaceae <- filter(brra_seed_set_final, Family %in% c("Brassicaceae"))
-brra_seed_set_convolvulaceae <- filter(brra_seed_set_final, Family %in% c("Convolvulaceae"))
-brra_seed_set_solanaceae <- filter(brra_seed_set_final, Family %in% c("Solanaceae"))
-brra_seed_set_final$Family[is.na(brra_seed_set_final$Family)] <- "Solanum lycopersicum"
-
-brra_seed_set_cross=brra_seed_set_cross[,-c(5,6)]
-brra_seed_set_cross$Family <- "other"
-brra_seed_set_self=brra_seed_set_self[,-c(5,6)]
-brra_seed_set_self$Family <- "other"
-brra_seed_set_control=brra_seed_set_control[,-c(5,6)]
-brra_seed_set_control$Family <- "other"
-brra_seed_set_flower=brra_seed_set_flower[,-c(5,6)]
-brra_seed_set_flower$Family <- "other"
-
-brra_seed_set_final=rbind(brra_seed_set_brassicaceae, brra_seed_set_convolvulaceae, 
-                          brra_seed_set_solanaceae, brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
-                          brra_seed_set_flower)
+brra_seed_set_final <- read.csv("Data/brra_seed_set_final.csv")
+brra_seed_set_final=brra_seed_set_final[,-1]
 
 #Different colour per family
-b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
@@
 
-ersa_seed_set <- read.csv("Data/ersa_seed_set.csv", sep=";")
-ersa_seed_set <- filter(ersa_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("ERSA", 10)
-Treatment <- rep("ERSA 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-ersa_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("ERSA", 10)
-Treatment <- rep("ERSA 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-ersa_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-colnames(ersa_seed_set)[1] <- "Species"
-colnames(ersa_seed_set)[2] <- "Treatment"
-colnames(ersa_seed_set)[3] <- "Treatment.number"
-colnames(ersa_seed_set)[4] <- "Seed.production"
-ersa_seed_set <- rbind(ersa_seed_set, ersa_50, ersa_100)
-ersa_seed_set$Treatment<- as.character(ersa_seed_set$Treatment)
-ersa_seed_set <- ersa_seed_set[order(ersa_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-ersa_seed_set_div <- str_split_fixed(as.character(ersa_seed_set$Treatment), " ", 2)
-ersa_seed_set_div <- data.frame(ersa_seed_set_div, stringsAsFactors = F)
-colnames(ersa_seed_set_div)=c("non_focal","percentage")
-ersa_seed_set_bind <- cbind(ersa_seed_set,ersa_seed_set_div)
-ersa_seed_set_bind <- filter(ersa_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(ersa_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-ersa_seed_set_cross <- filter(ersa_seed_set_bind, non_focal %in% c("Cross"))
-ersa_seed_set_self <- filter(ersa_seed_set_bind, non_focal %in% c("Self"))
-ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
-ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("Flower"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Cross"),]
-ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Self"),]
-ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
-ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Flower"),]
-
-ersa_seed_set_final<-rbind(ersa_seed_set_bind,ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
-                           ersa_seed_set_flower)
-#deleting extra columns used for data formating
-ersa_seed_set_final=ersa_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-ersa_seed_set_final[ersa_seed_set_final$Treatment==c("ERSA 50%"),4] <- NA
-
-#changing non_focal species name
-ersa_seed_set_final$Treatment=as.character(ersa_seed_set_final$Treatment)
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="FC"] <- "Flower control"
-
-ersa_seed_set_brassicaceae <- filter(ersa_seed_set_final, Family %in% c("Brassicaceae"))
-ersa_seed_set_convolvulaceae <- filter(ersa_seed_set_final, Family %in% c("Convolvulaceae"))
-ersa_seed_set_solanaceae <- filter(ersa_seed_set_final, Family %in% c("Solanaceae"))
-ersa_seed_set_final$Family[is.na(ersa_seed_set_final$Family)] <- "Solanum lycopersicum"
-
-ersa_seed_set_cross=ersa_seed_set_cross[,-c(5,6)]
-ersa_seed_set_cross$Family <- "other"
-ersa_seed_set_self=ersa_seed_set_self[,-c(5,6)]
-ersa_seed_set_self$Family <- "other"
-ersa_seed_set_control=ersa_seed_set_control[,-c(5,6)]
-ersa_seed_set_control$Family <- "other"
-ersa_seed_set_flower=ersa_seed_set_flower[,-c(5,6)]
-ersa_seed_set_flower$Family <- "other"
-
-ersa_seed_set_final=rbind(ersa_seed_set_brassicaceae, ersa_seed_set_convolvulaceae, 
-                          ersa_seed_set_solanaceae, ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
-                          ersa_seed_set_flower)
+ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final.csv")
+ersa_seed_set_final=ersa_seed_set_final[,-1]
 

### 2018-08-30 Rmd/Data_visualization.Rmd
rmd with ratio ggplot

@@
 ```
+
+```{r, fig.width=8}
+pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
+```
+
+```{r, fig.width=8}
+pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
+ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae")
+```
+
+```{r, fig.width=8}
+pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
+ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae")
+```

### 2018-08-30 Rmd/pollen_ratio_stigma.R

@@ -1,20 +1,93 @@
 
+library(ggplot2)
 
+#All species (2 measurements per focal species. 40 days took me to measure all)
 focal_pollen_percentage <- as.matrix(read.table("Data/pollen_ratios_matrix.csv", header=TRUE, sep = ";",
                               row.names = 1,
                               as.is=TRUE))
 focal_pollen_percentage <- melt(focal_pollen_percentage)
-
-
+focal_pollen_percentage <- focal_pollen_percentage[complete.cases(focal_pollen_percentage), ]
+focal_pollen_percentage$A <- "focal_pollen"
 non_focal_pollen_percentage <- as.matrix(read.table("Data/pollen_ratios_matrix_non_focal.csv", header=TRUE, sep = ";",
                                                 row.names = 1,
                                                 as.is=TRUE))
 
 non_focal_pollen_percentage <- melt(non_focal_pollen_percentage)
+non_focal_pollen_percentage <- non_focal_pollen_percentage[complete.cases(non_focal_pollen_percentage), ]
+non_focal_pollen_percentage$A <- "non_focal_pollen"
 
-pollen_ratios <- merge(non_focal_pollen_percentage, non_focal_pollen_percentage, by=c("Var1","Var2"))
+pollen_ratios <- rbind(focal_pollen_percentage,non_focal_pollen_percentage)
+colnames(pollen_ratios) <- c("focal", "non_focal", "ratio", "variable")
+pollen_ratios$spp <- paste(pollen_ratios$focal,pollen_ratios$non_focal)
 
-colnames(pollen_ratios) <- c("focal","non_focal", "focal_percen", "non_focal_percen")
+ggplot(pollen_ratios, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge')
+
+#Brassicaceae
+#Brassicaceae pollen ratio plot
+pollen_ratios_brassicaceae <- pollen_ratios[pollen_ratios$focal!="IPPU" & pollen_ratios$focal!="IPAQ"& pollen_ratios$focal!="SOME"&
+                               pollen_ratios$focal!="SOLY" & pollen_ratios$focal!="PEIN"& pollen_ratios$focal!="CAAN",  ]
+
+write.csv(pollen_ratios_brassicaceae, "Rmd/Data/pollen_ratios_brassicaceae.csv")
+
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
[…]

### 2018-08-30 Rmd/Data_visualization.Rmd
.

--- 2018-08-30 Rmd/Data_visualization.Rmd
@@
 \newpage
-```{r,echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=8,out.width='100%'}
-par(mfrow=c(2,2))
-#load libraries
-library(reshape2)
-library(ggplot2)
-#read data
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
-
-mean_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = mean, data = pein_seed_set, na.rm= TRUE)
-
-colnames(mean_seed_seet)[2] <-"avg"
-
-sd_seed_seet <- dcast(Treatment ~ ., value.var = "Seed.production", fun.aggregate = sd, data = pein_seed_set, na.rm= TRUE)
-
-colnames(sd_seed_seet)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd <- merge(mean_seed_seet,sd_seed_seet, by="Treatment")
-#Removing RARA, species not considered because sterility 
-mean_sd<- mean_sd[-c(16,17),]
-
-merge_1 <- data.frame(mean_sd, stringsAsFactors = F)
-
-merge_1$Treatment<- as.character(merge_1$Treatment)
-pein <- c("PEIN", NA, NA)
-
-str(merge_1)
-mean_sd_1 <- rbind(merge_1,pein)
-
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered <- mean_sd[order(mean_sd$avg),]
-
-mean_sd_ordered_alphabetically<- mean_sd_ordered[order(mean_sd_ordered$Treatment),]
-
-#ploting averages with sd
-x <- 1:22
-plot(x, mean_sd_ordered$avg,
-     ylim=range(c(mean_sd_ordered$avg-mean_sd_ordered$sdev, mean_sd_ordered$avg+mean_sd_ordered$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Petunia integrifolia")
-# add arrows
-arrows(x, mean_sd_ordered$avg-mean_sd_ordered$sdev, x, mean_sd_ordered$avg+mean_sd_ordered$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered$Treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-mean_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = some_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_some)[2] <-"avg"
-sd_seed_seet_some <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = some_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_some)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_some <- merge(mean_seed_seet_some,sd_seed_seet_some, by="Treatment")
-#Delete RARA rows, species not included because sterility
-mean_sd_some <- mean_sd_some[-c(8,9,20),]
-
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_some <- mean_sd_some[order(mean_sd_some$avg),]
-
-x <- 1:22
-plot(x, mean_sd_ordered_some$avg,
-     ylim=range(c(mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Solanum melongena")
-# add arrows
-arrows(x, mean_sd_ordered_some$avg-mean_sd_ordered_some$sdev, x, mean_sd_ordered_some$avg+mean_sd_ordered_some$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_some$Treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
-mean_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = caan_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_caan)[2] <-"avg"
-sd_seed_seet_caan <- dcast(treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = caan_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_caan)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_caan <- merge(mean_seed_seet_caan,sd_seed_seet_caan, by="treatment")
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_caan <- mean_sd_caan[order(mean_sd_caan$avg),]
-
-x <- 1:22
-plot(x, mean_sd_ordered_caan$avg,
-     ylim=range(c(mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Capsicum annuum")
-# add arrows
-arrows(x, mean_sd_ordered_caan$avg-mean_sd_ordered_caan$sdev, x, mean_sd_ordered_caan$avg+mean_sd_ordered_caan$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_caan$treatment)
-axis(x, at=1:22, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x,  cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-mean_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = mean, data = soly_seed_set, na.rm= TRUE)
-colnames(mean_seed_seet_soly)[2] <-"avg"
-sd_seed_seet_soly <- dcast(Treatment ~ ., value.var = "seed_set", fun.aggregate = sd, data = soly_seed_set, na.rm= TRUE)
-colnames(sd_seed_seet_soly)[2] <-"sdev"
-
-#Unify mean and sd with merge
-mean_sd_soly <- merge(mean_seed_seet_soly,sd_seed_seet_soly, by="Treatment")
-#Order from lower to higher values the average, to plot it nicely
-mean_sd_ordered_soly <- mean_sd_soly[order(mean_sd_soly$avg),]
-
-x <- 1:26
-plot(x, mean_sd_ordered_soly$avg,
-     ylim=range(c(mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="Solanum lycopersicum")
-# add arrows
-arrows(x, mean_sd_ordered_soly$avg-mean_sd_ordered_soly$sdev, x, mean_sd_ordered_soly$avg+mean_sd_ordered_soly$sdev, length=0.05, angle=90, code=3)
-lablist.x<-as.vector(mean_sd_ordered_soly$Treatment)
-axis(x, at=1:26, labels = FALSE)
-text(x, par("usr")[3] - 0.2, labels = lablist.x, cex= 0.6, adj = 1.25,srt = 45, xpd = TRUE)
-
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
 ```
-
 \newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.5, fig.width=5,fig.show='asis',fig.align='center',out.width='70%'}
-#Preparing seed set plots, starting with Petunia
-
-#There are 3 crosses were seeds were lost (2,7,9)
-#load libraries
-library(reshape2)
-library(ggplot2)
-library(dplyr)
-library(ggplot2)
-library(grid)
-library(gridExtra)
-library(egg)
-library(gtable)
-
-#read data and cleaning
-pein_seed_set <- read.csv("Data/PEIN_seed_set.csv", sep=";")
-pein_seed_set <- pein_seed_set[-c(42,47,49),]
-
-#
-##
-###
-#PETUNIA
-###
-##
-#
-
-#Removing RARA, species not considered because sterility
-
-pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
-
-#adding the focal species, first 50%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
-#adding the focal species, 100%
-Species <- rep("PEIN", 10)
-Treatment <- rep("PEIN 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
-#Order from lower to higher values the average, to plot it nicely
-pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
-pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
-pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]
-
-plot1 <- ggplot(pein_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot1 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#S. MELONGENA
-###
-##
-#
-
-#Taking out species that weren't used
-some_seed_set <- read.csv("Data/SOME_seed_set.csv", sep=";")
-some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
-
-#adding the focal species, first 50%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOME", 10)
-Treatment <- rep("SOME 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-some_seed_set<- some_seed_set[,-3]
-colnames(some_seed_set)[3] <- "Treatment.number"
-colnames(some_seed_set)[4] <- "Seed.production"
-some_seed_set <- rbind(some_seed_set, some_50, some_100)
-some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
-some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]
-
-plot2 <- ggplot(some_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot2 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#C. ANNUUM 
-###
-##
-#
-caan_seed_set <- read.csv("Data/CAAN_seed_set.csv", sep=";")
-
-#adding the focal species, first 50%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-caan_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("CAAN", 10)
-Treatment <- rep("CAAN 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-caan_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-caan_seed_set <- caan_seed_set[,-4]
-colnames(caan_seed_set)[1] <- "Species"
-colnames(caan_seed_set)[2] <- "Treatment"
-colnames(caan_seed_set)[3] <- "Treatment.number"
-colnames(caan_seed_set)[4] <- "Seed.production"
-caan_seed_set <- rbind(caan_seed_set, caan_50, caan_100)
-caan_seed_set$Treatment<- as.character(caan_seed_set$Treatment)
-caan_seed_set <- caan_seed_set[order(caan_seed_set$Treatment),]
-
-plot3 <- ggplot(caan_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot3 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#
-##
-###
-#S. LYCOPERSICUM
-###
-##
-#
-
-soly_seed_set <- read.csv("Data/SOLY_seed_set.csv", sep=";")
-soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SOLY", 10)
-Treatment <- rep("SOLY 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-soly_seed_set <- soly_seed_set[,-4]
-colnames(soly_seed_set)[1] <- "Species"
-colnames(soly_seed_set)[2] <- "Treatment"
-colnames(soly_seed_set)[3] <- "Treatment.number"
-colnames(soly_seed_set)[4] <- "Seed.production"
-soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
-soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
-soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]
-
-plot4 <- ggplot(soly_seed_set, aes(x = Treatment, y = Seed.production)) +   geom_boxplot()+
-  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Treatment)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5))
-
-plot4 + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
+ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae")
 ```
+\newpage
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
+ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae")
+```

### 2018-08-30 Rmd/pollen_ratio_stigma.R

@@ -1,0 +1,93 @@
+
+library(ggplot2)
+
+#All species (2 measurements per focal species. 40 days took me to measure all)
+focal_pollen_percentage <- as.matrix(read.table("Data/pollen_ratios_matrix.csv", header=TRUE, sep = ";",
+                              row.names = 1,
+                              as.is=TRUE))
+focal_pollen_percentage <- melt(focal_pollen_percentage)
+focal_pollen_percentage <- focal_pollen_percentage[complete.cases(focal_pollen_percentage), ]
+focal_pollen_percentage$A <- "focal_pollen"
+non_focal_pollen_percentage <- as.matrix(read.table("Data/pollen_ratios_matrix_non_focal.csv", header=TRUE, sep = ";",
+                                                row.names = 1,
+                                                as.is=TRUE))
+
+non_focal_pollen_percentage <- melt(non_focal_pollen_percentage)
+non_focal_pollen_percentage <- non_focal_pollen_percentage[complete.cases(non_focal_pollen_percentage), ]
+non_focal_pollen_percentage$A <- "non_focal_pollen"
+
+pollen_ratios <- rbind(focal_pollen_percentage,non_focal_pollen_percentage)
+colnames(pollen_ratios) <- c("focal", "non_focal", "ratio", "variable")
+pollen_ratios$spp <- paste(pollen_ratios$focal,pollen_ratios$non_focal)
+
+ggplot(pollen_ratios, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge')
+
+#Brassicaceae
+#Brassicaceae pollen ratio plot
+pollen_ratios_brassicaceae <- pollen_ratios[pollen_ratios$focal!="IPPU" & pollen_ratios$focal!="IPAQ"& pollen_ratios$focal!="SOME"&
+                               pollen_ratios$focal!="SOLY" & pollen_ratios$focal!="PEIN"& pollen_ratios$focal!="CAAN",  ]
+
+write.csv(pollen_ratios_brassicaceae, "Rmd/Data/pollen_ratios_brassicaceae.csv")
+
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
+
+#Solanaceae pollen ratio plot
+
+#All species (2 measurements per focal species. 40 days took me to measure all)
[…]

### 2018-08-31 Rmd/Data_visualization.Rmd
changes data_visualization plots with common names

@@
 ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
+
 ```
@@
 ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae")
+  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
+
 ```
@@
 ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae")
+  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
+
 ```

### 2018-09-03 Rmd/Data_visualization_no_internet.Rmd
changes

--- 2018-08-30 Rmd/Data_visualization.Rmd
@@
 #read data and cleaning
-pein_seed_set_final <- read.csv("Data/pein_seed_set_final.csv")
+pein_seed_set_final <- read.csv("Data/pein_seed_set_final_common_names.csv")
 pein_seed_set_final=pein_seed_set_final[,-1]
@@
 a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Petunia integrifolia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Capsicum annuum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="Capsicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
-soly_seed_set_final <- read.csv("Data/soly_seed_set_final.csv")
+soly_seed_set_final <- read.csv("Data/soly_seed_set_final_common_names.csv")
 soly_seed_set_final=soly_seed_set_final[,-1]
@@
 c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Solanum lycopersicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
-some_seed_set_final <- read.csv("Data/some_seed_set_final.csv")
+some_seed_set_final <- read.csv("Data/some_seed_set_final_common_names.csv")
 some_seed_set_final=some_seed_set_final[,-1]
@@
 d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Solanum melongena",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="Eggplant",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
-ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final.csv")
+ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final_common_names.csv")
 ersa_seed_set_final=ersa_seed_set_final[,-1]
@@
 c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Eruca versicaria",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
-sial_seed_set <- read.csv("Data/sial_seed_set.csv", sep=";")
-sial_seed_set <- filter(sial_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("SIAL", 10)
-Treatment <- rep("SIAL 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-sial_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("SIAL", 10)
-Treatment <- rep("SIAL 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-sial_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-colnames(sial_seed_set)[1] <- "Species"
-colnames(sial_seed_set)[2] <- "Treatment"
-colnames(sial_seed_set)[3] <- "Treatment.number"
-colnames(sial_seed_set)[4] <- "Seed.production"
-sial_seed_set <- rbind(sial_seed_set, sial_50, sial_100)
-sial_seed_set$Treatment<- as.character(sial_seed_set$Treatment)
-sial_seed_set <- sial_seed_set[order(sial_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-sial_seed_set_div <- str_split_fixed(as.character(sial_seed_set$Treatment), " ", 2)
-sial_seed_set_div <- data.frame(sial_seed_set_div, stringsAsFactors = F)
-colnames(sial_seed_set_div)=c("non_focal","percentage")
-sial_seed_set_bind <- cbind(sial_seed_set,sial_seed_set_div)
-sial_seed_set_bind <- filter(sial_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(sial_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-sial_seed_set_cross <- filter(sial_seed_set_bind, non_focal %in% c("Cross"))
-sial_seed_set_self <- filter(sial_seed_set_bind, non_focal %in% c("Self"))
-sial_seed_set_control <- filter(sial_seed_set_bind, non_focal %in% c("Control"))
-sial_seed_set_flower <- filter(sial_seed_set_bind, non_focal %in% c("Flower"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Cross"),]
-sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Self"),]
-sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Control"),]
-sial_seed_set_bind=sial_seed_set_bind[sial_seed_set_bind$non_focal!=c("Flower"),]
-
-sial_seed_set_final<-rbind(sial_seed_set_bind,sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
-                           sial_seed_set_flower)
-#deleting extra columns used for data formating
-sial_seed_set_final=sial_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-sial_seed_set_final[sial_seed_set_final$Treatment==c("SIAL 50%"),4] <- NA
-
-#changing non_focal species name
-sial_seed_set_final$Treatment=as.character(sial_seed_set_final$Treatment)
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-sial_seed_set_final$Family[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-sial_seed_set_final$Treatment[sial_seed_set_final$Treatment=="FC"] <- "Flower control"
-
-sial_seed_set_brassicaceae <- filter(sial_seed_set_final, Family %in% c("Brassicaceae"))
-sial_seed_set_convolvulaceae <- filter(sial_seed_set_final, Family %in% c("Convolvulaceae"))
-sial_seed_set_solanaceae <- filter(sial_seed_set_final, Family %in% c("Solanaceae"))
-sial_seed_set_final$Family[is.na(sial_seed_set_final$Family)] <- "Solanum lycopersicum"
-
-sial_seed_set_cross=sial_seed_set_cross[,-c(5,6)]
-sial_seed_set_cross$Family <- "other"
-sial_seed_set_self=sial_seed_set_self[,-c(5,6)]
-sial_seed_set_self$Family <- "other"
-sial_seed_set_control=sial_seed_set_control[,-c(5,6)]
-sial_seed_set_control$Family <- "other"
-sial_seed_set_flower=sial_seed_set_flower[,-c(5,6)]
-sial_seed_set_flower$Family <- "other"
-
-sial_seed_set_final=rbind(sial_seed_set_brassicaceae, sial_seed_set_convolvulaceae, 
-                          sial_seed_set_solanaceae, sial_seed_set_cross, sial_seed_set_self, sial_seed_set_control,
-                          sial_seed_set_flower)
+sial_seed_set_final <- read.csv("Data/sial_seed_set_final_common_names.csv")
+sial_seed_set_final=sial_seed_set_final[,-1]
 
@@
 d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Sinapis alba",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 ```
+
+\newpage
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}
@@
 #
+ipaq_seed_set_final <- read.csv("Data/ipaq_seed_set_final_common_names.csv")
+ipaq_seed_set_final=ipaq_seed_set_final[,-1]
 
-ipaq_seed_set <- read.csv("Data/ipaq_seed_set.csv", sep=";")
-colnames(ipaq_seed_set)[1] <- "Species"
-colnames(ipaq_seed_set)[2] <- "Treatment"
-colnames(ipaq_seed_set)[3] <- "Treatment.number"
-colnames(ipaq_seed_set)[4] <- "Seed.production"
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
 
-ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("IPAQ", 10)
-Treatment <- rep("IPAQ 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("IPAQ", 10)
-Treatment <- rep("IPAQ 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-
-ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
-ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
-ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
-ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
-colnames(ipaq_seed_set_div)=c("non_focal","percentage")
-ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
-ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(ipaq_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-ipaq_seed_set_cross <- filter(ipaq_seed_set_bind, Treatment %in% c("cross"))
-ipaq_seed_set_self <- filter(ipaq_seed_set_bind, Treatment %in% c("self"))
-ipaq_seed_set_control <- filter(ipaq_seed_set_bind, Treatment %in% c("control"))
-ipaq_seed_set_flower <- filter(ipaq_seed_set_bind, Treatment %in% c("flower control"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("cross"),]
-ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("self"),]
-ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("control"),]
-ipaq_seed_set_bind=ipaq_seed_set_bind[ipaq_seed_set_bind$Treatment!=c("flower control"),]
-
-ipaq_seed_set_final<-rbind(ipaq_seed_set_bind,ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
-                           ipaq_seed_set_flower)
-#deleting extra columns used for data formating
-ipaq_seed_set_final=ipaq_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-ipaq_seed_set_final[ipaq_seed_set_final$Treatment==c("IPPA 50%"),4] <- NA
-
-#changing non_focal species name
-ipaq_seed_set_final$Treatment=as.character(ipaq_seed_set_final$Treatment)
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-ipaq_seed_set_final$Family[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-ipaq_seed_set_brassicaceae <- filter(ipaq_seed_set_final, Family %in% c("Brassicaceae"))
-ipaq_seed_set_convolvulaceae <- filter(ipaq_seed_set_final, Family %in% c("Convolvulaceae"))
-ipaq_seed_set_solanaceae <- filter(ipaq_seed_set_final, Family %in% c("Solanaceae"))
-ipaq_seed_set_final$Family[is.na(ipaq_seed_set_final$Family)] <- "Solanum lycopersicum"
-
-ipaq_seed_set_cross=ipaq_seed_set_cross[,-c(5,6)]
-ipaq_seed_set_cross$Family <- "other"
-ipaq_seed_set_self=ipaq_seed_set_self[,-c(5,6)]
-ipaq_seed_set_self$Family <- "other"
-ipaq_seed_set_control=ipaq_seed_set_control[,-c(5,6)]
-ipaq_seed_set_control$Family <- "other"
-ipaq_seed_set_flower=ipaq_seed_set_flower[,-c(5,6)]
-ipaq_seed_set_flower$Family <- "other"
-
-ipaq_seed_set_final=rbind(ipaq_seed_set_brassicaceae, ipaq_seed_set_convolvulaceae, 
-                          ipaq_seed_set_solanaceae, ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
-                          ipaq_seed_set_flower)
-
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
-ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
 #Different colour per family
@@
 
-ippu_seed_set <- read.csv("Data/ippu_seed_set.csv", sep=";")
-colnames(ippu_seed_set)[1] <- "Species"
-colnames(ippu_seed_set)[2] <- "Treatment"
-colnames(ippu_seed_set)[3] <- "Treatment.number"
-colnames(ippu_seed_set)[4] <- "Seed.production"
-
-ippu_seed_set <- filter(ippu_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
-
-#adding the focal species, first 50%
-Species <- rep("IPPU", 10)
-Treatment <- rep("IPPU 50%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-ippu_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
-#adding the focal species, 100%
-Species <- rep("IPPU", 10)
-Treatment <- rep("IPPU 100%", 10)
-Treatment.number <- seq(1:10)
-Seed.production <- rep(0, 10)
-ippu_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
-#Order from lower to higher values the average, to plot it nicely
-
-ippu_seed_set <- rbind(ippu_seed_set, ippu_50, ippu_100)
-ippu_seed_set$Treatment<- as.character(ippu_seed_set$Treatment)
-ippu_seed_set <- ippu_seed_set[order(ippu_seed_set$Treatment),]
-
-#Organizing with just 50% and cross, self, flower control and control on a side
-
-library(stringr)
-ippu_seed_set_div <- str_split_fixed(as.character(ippu_seed_set$Treatment), " ", 2)
-ippu_seed_set_div <- data.frame(ippu_seed_set_div, stringsAsFactors = F)
-colnames(ippu_seed_set_div)=c("non_focal","percentage")
-ippu_seed_set_bind <- cbind(ippu_seed_set,ippu_seed_set_div)
-ippu_seed_set_bind <- filter(ippu_seed_set_bind, percentage!="100%")
-
-#Because I want to give it specifically order I do it separately
-#pein_seed_set_common <- filter(ippu_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
-
-ippu_seed_set_cross <- filter(ippu_seed_set_bind, Treatment %in% c("cross"))
-ippu_seed_set_self <- filter(ippu_seed_set_bind, Treatment %in% c("self"))
-ippu_seed_set_control <- filter(ippu_seed_set_bind, Treatment %in% c("control"))
-ippu_seed_set_flower <- filter(ippu_seed_set_bind, Treatment %in% c("flower control"))
-
-#Changing 0 for NA'S FOCAL species
-
-# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
-ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("cross"),]
-ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("self"),]
-ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("control"),]
-ippu_seed_set_bind=ippu_seed_set_bind[ippu_seed_set_bind$Treatment!=c("flower control"),]
-
-ippu_seed_set_final<-rbind(ippu_seed_set_bind,ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
-                           ippu_seed_set_flower)
-#deleting extra columns used for data formating
-ippu_seed_set_final=ippu_seed_set_final[,-c(5,6)]
-#adding NA'S to the focal species
-ippu_seed_set_final[ippu_seed_set_final$Treatment==c("IPPU 50%"),4] <- NA
-
-#changing non_focal species name
-ippu_seed_set_final$Treatment=as.character(ippu_seed_set_final$Treatment)
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
-ippu_seed_set_final$Family[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"
-
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
-
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"
-
-ippu_seed_set_brassicaceae <- filter(ippu_seed_set_final, Family %in% c("Brassicaceae"))
-ippu_seed_set_convolvulaceae <- filter(ippu_seed_set_final, Family %in% c("Convolvulaceae"))
-ippu_seed_set_solanaceae <- filter(ippu_seed_set_final, Family %in% c("Solanaceae"))
-ippu_seed_set_final$Family[is.na(ippu_seed_set_final$Family)] <- "Solanum lycopersicum"
-
-ippu_seed_set_cross=ippu_seed_set_cross[,-c(5,6)]
-ippu_seed_set_cross$Family <- "other"
-ippu_seed_set_self=ippu_seed_set_self[,-c(5,6)]
-ippu_seed_set_self$Family <- "other"
-ippu_seed_set_control=ippu_seed_set_control[,-c(5,6)]
-ippu_seed_set_control$Family <- "other"
-ippu_seed_set_flower=ippu_seed_set_flower[,-c(5,6)]
-ippu_seed_set_flower$Family <- "other"
-
-ippu_seed_set_final=rbind(ippu_seed_set_brassicaceae, ippu_seed_set_convolvulaceae, 
-                          ippu_seed_set_solanaceae, ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
-                          ippu_seed_set_flower)
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
-ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"
+#IPPU
+ippu_seed_set_final <- read.csv("Data/ippu_seed_set_final_common_names.csv")
+ippu_seed_set_final=ippu_seed_set_final[,-1]
 

### 2018-09-03 Scripts/ggplot_species_seed_set/e_versicaria_ggplot_common_names.R

@@ -1,0 +1,142 @@
+#
+##
+###
+#E. VERSICARIA
+###
+##
+#
+
+
+ersa_seed_set <- read.csv("Data/species_seed_set/ersa_seed_set.csv", sep=";")
+ersa_seed_set <- filter(ersa_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("ERSA", 10)
+Treatment <- rep("ERSA 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ersa_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("ERSA", 10)
+Treatment <- rep("ERSA 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ersa_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+colnames(ersa_seed_set)[1] <- "Species"
+colnames(ersa_seed_set)[2] <- "Treatment"
+colnames(ersa_seed_set)[3] <- "Treatment.number"
+colnames(ersa_seed_set)[4] <- "Seed.production"
+ersa_seed_set <- rbind(ersa_seed_set, ersa_50, ersa_100)
+ersa_seed_set$Treatment<- as.character(ersa_seed_set$Treatment)
+ersa_seed_set <- ersa_seed_set[order(ersa_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ersa_seed_set_div <- str_split_fixed(as.character(ersa_seed_set$Treatment), " ", 2)
+ersa_seed_set_div <- data.frame(ersa_seed_set_div, stringsAsFactors = F)
+colnames(ersa_seed_set_div)=c("non_focal","percentage")
+ersa_seed_set_bind <- cbind(ersa_seed_set,ersa_seed_set_div)
+ersa_seed_set_bind <- filter(ersa_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
[…]

### 2018-09-03 Scripts/ggplot_species_seed_set/i_aquatica_ggplot_common_names.R

@@ -1,0 +1,145 @@
+#
+##
+###
+#I. AQUATICA
+###
+##
+#
+
+
+ipaq_seed_set <- read.csv("Data/species_seed_set/ipaq_seed_set.csv", sep=";")
+colnames(ipaq_seed_set)[1] <- "Species"
+colnames(ipaq_seed_set)[2] <- "Treatment"
+colnames(ipaq_seed_set)[3] <- "Treatment.number"
+colnames(ipaq_seed_set)[4] <- "Seed.production"
+
+ipaq_seed_set <- filter(ipaq_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ipaq_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("IPAQ", 10)
+Treatment <- rep("IPAQ 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+ipaq_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+
+ipaq_seed_set <- rbind(ipaq_seed_set, ipaq_50, ipaq_100)
+ipaq_seed_set$Treatment<- as.character(ipaq_seed_set$Treatment)
+ipaq_seed_set <- ipaq_seed_set[order(ipaq_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+ipaq_seed_set_div <- str_split_fixed(as.character(ipaq_seed_set$Treatment), " ", 2)
+ipaq_seed_set_div <- data.frame(ipaq_seed_set_div, stringsAsFactors = F)
+colnames(ipaq_seed_set_div)=c("non_focal","percentage")
+ipaq_seed_set_bind <- cbind(ipaq_seed_set,ipaq_seed_set_div)
+ipaq_seed_set_bind <- filter(ipaq_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
[…]

### 2018-09-03 Scripts/ggplot_species_seed_set/p_integrifolia_ggplot_common.R

@@ -1,0 +1,156 @@
+#Preparing seed set plots, starting with Petunia
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(lattice)
+#read data and cleaning
+pein_seed_set <- read.csv("Data/species_seed_set/PEIN_seed_set.csv", sep=";")
+#removing samples where seeds got lost, first ones of the experiment
+pein_seed_set <- pein_seed_set[-c(42,47,49),]
+
+#
+##
+###
+#PETUNIA
+###
+##
+#
+#Removing RARA, species not considered because sterility 
+
+pein_seed_set <- filter(pein_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%")
+
+#adding the focal species, first 50%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#adding the focal species, 100%
+Species <- rep("PEIN", 10)
+Treatment <- rep("PEIN 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+pein_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production,stringsAsFactors = F)
+#Order from lower to higher values the average, to plot it nicely
+pein_seed_set <- rbind(pein_seed_set, pein_50, pein_100)
+pein_seed_set$Treatment<- as.character(pein_seed_set$Treatment)
+pein_seed_set <- pein_seed_set[order(pein_seed_set$Treatment),]  
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+
+library(stringr)
+pein_seed_set_div <- str_split_fixed(as.character(pein_seed_set$Treatment), " ", 2)
+pein_seed_set_div <- data.frame(pein_seed_set_div, stringsAsFactors = F)
+colnames(pein_seed_set_div)=c("non_focal","percentage")
+pein_seed_set_bind <- cbind(pein_seed_set,pein_seed_set_div)
[…]

### 2018-09-03 Scripts/ggplot_species_seed_set/s_lycopersicum_ggplot_common_names.R

@@ -1,0 +1,151 @@
+#
+##
+###
+#S. LYCOPERSICUM
+###
+##
+#
+
+
+soly_seed_set <- read.csv("Data/species_seed_set/SOLY_seed_set.csv", sep=";")
+soly_seed_set <- filter(soly_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )
+
+#adding the focal species, first 50%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOLY", 10)
+Treatment <- rep("SOLY 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+soly_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+soly_seed_set <- soly_seed_set[,-4]
+colnames(soly_seed_set)[1] <- "Species"
+colnames(soly_seed_set)[2] <- "Treatment"
+colnames(soly_seed_set)[3] <- "Treatment.number"
+colnames(soly_seed_set)[4] <- "Seed.production"
+soly_seed_set <- rbind(soly_seed_set, soly_50, soly_100)
+soly_seed_set$Treatment<- as.character(soly_seed_set$Treatment)
+soly_seed_set <- soly_seed_set[order(soly_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+soly_seed_set_div <- str_split_fixed(as.character(soly_seed_set$Treatment), " ", 2)
+soly_seed_set_div <- data.frame(soly_seed_set_div, stringsAsFactors = F)
+colnames(soly_seed_set_div)=c("non_focal","percentage")
+soly_seed_set_bind <- cbind(soly_seed_set,soly_seed_set_div)
+soly_seed_set_bind <- filter(soly_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
[…]

### 2018-09-03 Scripts/ggplot_species_seed_set/s_melongena_ggplot_common_names.R

@@ -1,0 +1,148 @@
+#
+##
+###
+#S. MELONGENA
+###
+##
+#
+
+#Taking out species that weren't used
+some_seed_set <- read.csv("Data/species_seed_set/SOME_seed_set.csv", sep=";")
+some_seed_set <- filter(some_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%" & Treatment!="COSA 50%" & Treatment!="COSA 100%")
+
+#adding the focal species, first 50%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 50%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
+#adding the focal species, 100%
+Species <- rep("SOME", 10)
+Treatment <- rep("SOME 100%", 10)
+Treatment.number <- seq(1:10)
+Seed.production <- rep(0, 10)
+some_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
+#Order from lower to higher values the average, to plot it nicely
+some_seed_set<- some_seed_set[,-3]
+colnames(some_seed_set)[3] <- "Treatment.number"
+colnames(some_seed_set)[4] <- "Seed.production"
+some_seed_set <- rbind(some_seed_set, some_50, some_100)
+some_seed_set$Treatment<- as.character(some_seed_set$Treatment)
+some_seed_set <- some_seed_set[order(some_seed_set$Treatment),]  
+
+#Organizing with just 50% and cross, self, flower control and control on a side
+
+library(stringr)
+some_seed_set_div <- str_split_fixed(as.character(some_seed_set$Treatment), " ", 2)
+some_seed_set_div <- data.frame(some_seed_set_div, stringsAsFactors = F)
+colnames(some_seed_set_div)=c("non_focal","percentage")
+some_seed_set_bind <- cbind(some_seed_set,some_seed_set_div)
+some_seed_set_bind <- filter(some_seed_set_bind, percentage!="100%")
+
+#Because I want to give it specifically order I do it separately
+#pein_seed_set_common <- filter(some_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))
+
+some_seed_set_cross <- filter(some_seed_set_bind, non_focal %in% c("CROSS"))
[…]

### 2018-09-03 Rmd/Data_visualization_common_names.Rmd
las minute changes

--- 2018-09-03 Rmd/Data_visualization_no_internet.Rmd
@@
 ```
+\newpage
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
+#load libraries
+
+library(ggplot2)
+library(colorspace)
+library(gridExtra)
+
+colours <- rainbow_hcl(4, start = 30, end = 300)
+#load data
+
+par(mfrow=c(2,1))
+d<-read.csv("Data/Ovules.csv", sep=";")
+d<- d[,-c(9,11)]
+colnames(d)[1]<-"C. annuum"
+colnames(d)[2]<-"S. lycopersicum"
+colnames(d)[3]<-"S. melongera"
+colnames(d)[4]<-"P. integrifolia"
+colnames(d)[5]<-"B. oleracea"
+colnames(d)[6]<-"B. rapa"
+colnames(d)[7]<-"E. sativa"
+colnames(d)[8]<-"S. alba"
+colnames(d)[9]<-"I. aquatica"
+colnames(d)[10]<-"I. purpurea"
+
+#Reorganise data
+d <- stack(d)
+#Naming columns
+colnames(d)[1]<-"ovules"
+colnames(d)[2]<-"species"
+
+family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
+
+d[,"family"] <- family
+
+#subset per family (solanaceae, brassicaceae, convolvulaceae)
+solanaceae<-subset(d)[1:60,]
+brassicaceae<-subset(d)[61:120,]
+
+# OVULES SOLANACEAE
+p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+# OVULES BRASSICACEAE
+p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#all species
+#formating d, to have just the spp of interest
+
+p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
+labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+```
+
+#Pollen per anther, just one Convolvulaceae at the moment
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+library(ggplot2)
+
+p <- read.csv("data/Pollen.csv", sep = ";")
+
+#Deleting extra row (21)
+p <-p[-21,]
+
+#boxplot(p)
+#Reorganize data for ggplot
+p<-stack(p)
+#colnames
+colnames(p)[1]<-"pollen"
+colnames(p)[2]<-"species"
+
+all<-p
+solanaceae<-subset(p)[1:100,]
+brassicaceae<- subset(p)[101:180,]
+
+#Solanaceae
+p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#Brassicaceae
+p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+
+#all
+p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
+labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+theme(plot.title = element_text(hjust = 0.5))
+
+p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+tab <- read.csv("Data/tab.csv", sep="", header = T)
+
+p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
+  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  scale_fill_manual(values=colours)
+p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
+
+```
+
+```{r echo=FALSE, out.width='80%', fig.align='center'}
+knitr::include_graphics('Images/all_species.png')
+```
+
+\newpage
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
+
+```
+\newpage
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
+ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
+
+```
+\newpage
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
+ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae") + theme(axis.text.x=element_text(angle=60,hjust=1))
+
+```
 

### 2018-09-06 Rmd/Data_visualization_common_names.Rmd
Changes in Rmd visualization file

--- 2018-09-03 Rmd/Data_visualization_no_internet.Rmd
@@
 a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Ipomoea aquatica",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="Water morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Ipomoea purpurea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="Morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 ```
-
 \newpage
@@
 ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae")
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
+  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
+  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)
+
 ```
@@
 ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae")
+  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
+  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
+  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)
+
 ```
@@
 ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
-  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae")
+  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
+  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
+  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)
+
 ```
+
+\newpage
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+library(ggplot2)
+
+all <- read.csv("Data/all.csv", header=T)
+
+cbPalette <- c( "#56B4E9","#E69F00","#009E73")
+
+#all
+
+ ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+#Samte thing but without eggplant to improve visualization
+
+#all
+
+ all <- all[all$species !="Eggplant",]
+
+ ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+```
+\newpage

### 2018-09-06 Scripts/ggplot_species_seed_set/i_aquatica_ggplot_common_names.R

@@ -6,6 +6,10 @@
 ##
 #
 
+library(dplyr)
+library(ggplot2)
+library(reshape2)
+
 
 ipaq_seed_set <- read.csv("Data/species_seed_set/ipaq_seed_set.csv", sep=";")
 colnames(ipaq_seed_set)[1] <- "Species"
@@ -114,6 +118,13 @@ ipaq_seed_set_flower$Family <- "other"
 ipaq_seed_set_final=rbind(ipaq_seed_set_brassicaceae, ipaq_seed_set_convolvulaceae, 
                           ipaq_seed_set_solanaceae, ipaq_seed_set_cross, ipaq_seed_set_self, ipaq_seed_set_control,
                           ipaq_seed_set_flower)
+
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="flower control"] <- "Flower control"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="control"] <- "Control"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="self"] <- "Self"
+ipaq_seed_set_final$Treatment[ipaq_seed_set_final$Treatment=="cross"] <- "Cross"
+
+
 write.csv(ipaq_seed_set_final, "Rmd/Data/ipaq_seed_set_final_common_names.csv")
 
 #Different colour per Treatment

### 2018-09-06 Scripts/ggplot_species_seed_set/i_purpurea_ggplot_common_names.R

@@ -114,6 +114,13 @@ ippu_seed_set_flower$Family <- "other"
 ippu_seed_set_final=rbind(ippu_seed_set_brassicaceae, ippu_seed_set_convolvulaceae, 
                           ippu_seed_set_solanaceae, ippu_seed_set_cross, ippu_seed_set_self, ippu_seed_set_control,
                           ippu_seed_set_flower)
+
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="cross"] <- "Cross"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="self"] <- "Self"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="control"] <- "Control"
+ippu_seed_set_final$Treatment[ippu_seed_set_final$Treatment=="flower control"] <- "Flower control"
+
+
 write.csv(ippu_seed_set_final, "Rmd/Data/ippu_seed_set_final_common_names.csv")
 
 

### 2018-09-06 Scripts/pollen.R

@@ -6,19 +6,48 @@ library(Formula)
 
 p <- read.csv("data/Pollen.csv", sep = ";")
 
-#Deleting extra row (21)
-p <-p[-21,]
-
-boxplot(p)
+#Adding common names
+colnames(p) <- c("Capsicum", "Petunia", "Tomato", "Tomato_buzz", "Eggplant",
+                 "Wild cabbage", "White mustard", "Pak choi", "Rocket", "Morning glory",
+               "Water morning glory")
+#Removing Pollen count of tomato buzzed
+p<- p[,-4]
+#boxplot(p)
 #Reorganize data for ggplot
 p<-stack(p)
+p$species <- as.character(p$species)
 #colnames
 colnames(p)[1]<-"pollen"
 colnames(p)[2]<-"species"
+#Adding family to put colour per family
+p$family[p$species=="Capsicum"] <- "Solanaceae"
+p$family[p$species=="Tomato"] <- "Solanaceae"
+p$family[p$species=="Petunia"] <- "Solanaceae"
+p$family[p$species=="Eggplant"] <- "Solanaceae"
+p$family[p$species=="Wild cabbage"] <- "Brassicaceae"
+p$family[p$species=="Pak choi"] <- "Brassicaceae"
+p$family[p$species=="Rocket"] <- "Brassicaceae"
+p$family[p$species=="White mustard"] <- "Brassicaceae"
+p$family[p$species=="Morning glory"] <- "Convolvulaceae"
+p$family[p$species=="Water morning glory"] <- "Convolvulaceae"
+
+
+
+
+
+
+
+
+
+
+
+
 
 all<-p
 solanaceae<-subset(p)[1:100,]
 brassicaceae<- subset(p)[101:180,]
+
+write.csv(all, "Rmd/Data/all.csv")
 
 #Solanaceae
 
@@ -45,3 +74,47 @@ p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) + 
 
 p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black")
 
+
+
+library(ggplot2)
+
+
+p <- read.csv("data/Pollen.csv", sep = ";")
+
+
+
+#boxplot(p)
+#Reorganize data for ggplot
+p<-stack(p)
+#colnames
+colnames(p)[1]<-"pollen"
+colnames(p)[2]<-"species"
+
+all<-p
[…]

### 2018-09-06 Rmd/Data_visualization_common_names.Rmd
Data_preparation

@@
 
+\newpage
+#CHOLOROPLAST RBCL PHYLOGENY
 ```{r echo=FALSE, out.width='80%', fig.align='center'}
@@
 \newpage
+###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES-
 ```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
@@
 \newpage
+###POLLEN PER ANTHER
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}

### 2018-09-06 Scripts/ovule_plot.R

@@ -1,36 +1,0 @@
-
-#OVYLE NUMBER OF THE DIFFERENT SPECIES N=15
-
-library(reshape2)
-
-# Consider NA's as 0, I have to double check this
-
-ovules <- read.csv("Ovules.csv", sep=";")
-
-#plot(ovules)
-
-mean_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = mean, data = ovules, na.rm= TRUE)
-
-colnames(mean_ovule)[2] <- "avg"
-
-
-
-sd_ovule <- dcast(Species ~ ., value.var = "Ovules", fun.aggregate = sd, data = ovules, na.rm= TRUE)
-
-colnames(sd_ovule)[2] <- "sdev"
-
-
-x <- 1:8
-
-
-plot(x, mean_ovule$avg,
-     ylim=range(c(mean_ovule$avg-sd_ovule$sdev, mean_ovule$avg+sd_ovule$sdev)),
-     pch=19, xlab="", xaxt='n', ylab="Mean +/- SD",
-     main="N of Ovules")
-
-# hack: we draw arrows but with very special "arrowheads"
-arrows(x, mean_ovule$avg-sd_ovule$sdev, x, mean_ovule$avg+sd_ovule$sdev, length=0.05, angle=90, code=3)
-
-axis(x, at=1:8, labels = mean_ovule$Species,cex=0.2, tick = FALSE, padj= -0.5, side = 1)
-
-

### 2018-09-07 Rmd/Data_visualization_common_names.Rmd
More changes in visualization file

@@
 ```
-\newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.8}
-#load libraries
-
-library(ggplot2)
-library(colorspace)
-library(gridExtra)
-
-colours <- rainbow_hcl(4, start = 30, end = 300)
-#load data
-
-par(mfrow=c(2,1))
-d<-read.csv("Data/Ovules.csv", sep=";")
-d<- d[,-c(9,11)]
-colnames(d)[1]<-"C. annuum"
-colnames(d)[2]<-"S. lycopersicum"
-colnames(d)[3]<-"S. melongera"
-colnames(d)[4]<-"P. integrifolia"
-colnames(d)[5]<-"B. oleracea"
-colnames(d)[6]<-"B. rapa"
-colnames(d)[7]<-"E. sativa"
-colnames(d)[8]<-"S. alba"
-colnames(d)[9]<-"I. aquatica"
-colnames(d)[10]<-"I. purpurea"
-
-#Reorganise data
-d <- stack(d)
-#Naming columns
-colnames(d)[1]<-"ovules"
-colnames(d)[2]<-"species"
-
-family<- c(rep("solanaceae",60),rep("brassicaceae",60),rep("convolvulaceae",30))
-
-d[,"family"] <- family
-
-#subset per family (solanaceae, brassicaceae, convolvulaceae)
-solanaceae<-subset(d)[1:60,]
-brassicaceae<-subset(d)[61:120,]
-
-# OVULES SOLANACEAE
-p <- ggplot(solanaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-# OVULES BRASSICACEAE
-p <- ggplot(brassicaceae, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Brassicaceae",x="", y = "Ovules")+aes(fill=species)+scale_fill_manual(values=colours)+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#all species
-#formating d, to have just the spp of interest
-
-p <- ggplot(d, aes(x = reorder(species, ovules, FUN = median), y = ovules)) +   geom_boxplot()+
-labs(title="Ovules per spp.",x="", y = "Ovules")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-```
-
-#Pollen per anther, just one Convolvulaceae at the moment
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
-library(ggplot2)
-
-p <- read.csv("data/Pollen.csv", sep = ";")
-
-#Deleting extra row (21)
-p <-p[-21,]
-
-#boxplot(p)
-#Reorganize data for ggplot
-p<-stack(p)
-#colnames
-colnames(p)[1]<-"pollen"
-colnames(p)[2]<-"species"
-
-all<-p
-solanaceae<-subset(p)[1:100,]
-brassicaceae<- subset(p)[101:180,]
-
-#Solanaceae
-p <- ggplot(solanaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="Solanaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#Brassicaceae
-p <- ggplot(brassicaceae, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="Brassicaceae",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-
-#all
-p <- ggplot(all, aes(x = reorder(species, pollen, FUN = median), y = pollen)) +   geom_boxplot()+
-labs(title="All species",x="", y = "pollen")+aes(fill=species)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-theme(plot.title = element_text(hjust = 0.5))
-
-p + stat_summary(fun.y=mean, geom="point", shape="*", size=5, colour="black") +theme(legend.position="none")
-```
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-tab <- read.csv("Data/tab.csv", sep="", header = T)
-
-p <- ggplot(data=tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
-  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  scale_fill_manual(values=colours)
-p + ggtitle("Pollen/ovule ratio per species") + theme(plot.title = element_text(hjust = 0.5))+ labs(x = "Species")
-
-```
 
@@
 \newpage
-###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES-
+###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES- (N=3)
 ```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
@@
 \newpage
-###POLLEN PER ANTHER
+###POLLEN PER ANTHER (N=20, I. aquatica N=10)
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
@@
   labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
 
@@
  ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+  labs(title="All species(-Eggplant)",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
 
 ```
+
 \newpage
+###OVULES (N=15)
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+
+d <- read.csv("Data/d.csv")
+
+cbPalette <- c( "#56B4E9","#E69F00","#009E73")
+
+ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
+  geom_boxplot(outlier.shape = NA)+labs(title="All species",x="", y = "Nº of ovules")+
+  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
+  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
+  scale_color_manual(values = cbPalette) + 
+  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
+
+ d <- d[d$species !="Eggplant",]
+
+ ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
+  geom_boxplot(outlier.shape = NA)+labs(title="All species(-Eggplant)",x="", y = "Nº of ovules")+
+  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
+  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
+  scale_color_manual(values = cbPalette) + 
+  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+library(dplyr)
+library(ggplot2)
+
+tab <- read.csv("Data/tab.csv", sep="", header = T)
+
+ggplot(tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
+  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_fill_manual(values=cbPalette)
+
+```

### 2018-09-07 Rmd/Data_visualization_common_names.Rmd
csv´s with total pollen on stigma (N=3)

@@
 ---
+
+###SEED SET PER SPECIES WITH DIFFERENT TREATMENTS
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}

### 2018-09-10 traits_common_names.R
common names

@@ -1,18 +1,18 @@
 # In this script I'm going to create a table with the different traits of the species
 
 #Solanaceae
-solanaceae <- c("Petunia integrifolia","Capsicum annuum","Solanum lycopersicum","Solanum melongena")
+solanaceae <- c("Petunia","Capsicum","Tomato","Eggplant")
 sol_fam <- rep("Solanaceae",4)
 sol_genus <- c("Petunia","Capsicum","Solanum","Solanum")
 
 
 #Brassicaceae
-brassicaceae <- c("Brassica oleracea", "Brassica rapa" ,"Eruca versicaria", "Sinapis alba")
+brassicaceae <- c("Pak choi", "Wild cabbage" ,"Rocket", "White mustard")
 bra_fam <- rep("Brassicaceae",4)
 bra_genus <- c("Brassica", "Brassica" ,"Eruca", "Sinapis")
 
 #Convolvulaceae
-convolvulaceae <- c("Ipomoea aquatica", "Ipomoea purpurea")
+convolvulaceae <- c("Water morning glory", "Morning glory")
 con_fam <- c("Convolvulaceae","Convolvulaceae")
 con_genus <- c("Ipomoea", "Ipomoea")
 
@@ -238,14 +238,14 @@ tab[9,7] <-  "(Les, 2017); DOI: 10.1201/9781315118116"
 tab[10,6] <- "Self-compatible"
 tab[10,7] <-  "(Smith & Rausher, 2006); DOI: 10.1111/j.1469-8137.2006.01933.x" 
 
-write.table(tab, file = "data/tab.csv")
+write.table(tab, file = "data/tab_common_names.csv")
 
-  
+
 barplot(tab$pollen_ovule_ratio, x.axis)
 library(ggplot2)
 library(colorspace)
 p <- ggplot(data=tab, aes(x=species, y=pollen_ovule_ratio))+
-geom_bar(stat="identity", width=0.5)+coord_flip()
+  geom_bar(stat="identity", width=0.5)+coord_flip()
 p + ggtitle("Pollen/ovule ratio per species")
 
 colours <- rainbow_hcl(4, start = 30, end = 300)

### 2018-09-10 Rmd/Data_visualization_common_names.Rmd
common names
TOTAL POLLEN PLOTS

@@
 \newpage
+###TOTAL POLLEN ON STIGMA -NEXT 3 PAGES-
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+total_pollen_brassicaceae <- read.csv("Data/total_pollen_brassicaceae.csv", header=T)
+
+ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen grains on stigma") + 
+  theme(axis.text.x=element_text(angle=60,hjust=1))+
+  scale_fill_manual(values=c("grey10", "grey60"))
+
+```
+
+\newpage
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+
+total_pollen_solanaceae <- read.csv("Data/total_pollen_solanaceae.csv", header=T)
+
+ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
+  theme(axis.text.x=element_text(angle=60,hjust=1))+
+  scale_fill_manual(values=c("grey10", "grey60"))
+
+```
+\newpage
+
+```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
+
+total_pollen_convolvulaceae <- read.csv("Data/total_pollen_convolvulaceae.csv", header=T)
+
+ggplot(total_pollen_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
+  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
+  theme(axis.text.x=element_text(angle=60,hjust=1))+
+  scale_fill_manual(values=c("grey10", "grey60"))
+
+```
+
+\newpage
 ###POLLEN PER ANTHER (N=20, I. aquatica N=10)
@@
 
-tab <- read.csv("Data/tab.csv", sep="", header = T)
+tab <- read.csv("Data/tab_common_names.csv", sep="", header = T)
 

### 2018-09-10 Scripts/total_pollen_stigma.R

@@ -89,6 +89,9 @@ total_pollen_convolvulaceae <- total_pollen[total_pollen$focal!="Capsicum" & tot
                                               & total_pollen$focal!="Rocket"& total_pollen$focal!="Tomato"& total_pollen$focal!="Petunia",  ]
 
 
+
+
+
 #write.csv(total_pollen_convolvulaceae, "Rmd/Data/total_pollen_convolvulaceae.csv")
 
 

### 2018-09-10 Rmd/Data_visualization_common_names.Rmd
TOTAL_POLLEN

@@
   geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_fill_manual(values=cbPalette)
-
 ```

### 2018-09-11 Rmd/Data_visualization_common_names.Rmd
trait csv
Adding density plots of stigma area

@@
 
+\newpage
+
+###POLLEN OVULE RATIO. TOTAL POLLEN PER FLOWER DIVIDED BY NUMBER OF OVULES
+
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
@@
 ```
+
+\newpage
+
+###STIGMA AREA
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+
+t_stigma_area <- read.csv("Data/t_stigma_area.csv")
+t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
+t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
+t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
+
+theme_set(theme_gray())
+a <- ggplot(t_stigma_area_brassicaceae, aes(x = um, fill = species_common)) +
+  geom_density(alpha = 0.7) +
+  theme(legend.position = c(0.8, 0.8))
+
+b <- ggplot(t_stigma_area_solanaceae, aes(x = um, fill = species_common)) +
+  geom_density(alpha = 0.7) +
+  theme(legend.position = c(0.8, 0.8))
+
+cowplot::plot_grid(a,b, labels = "AUTO")
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+
+t_stigma_area <- read.csv("Data/t_stigma_area.csv")
+t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
+t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
+t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
+
+theme_set(theme_gray())
+a <- ggplot(t_stigma_area, aes(x = um, fill = species_common)) +
+  geom_density(alpha = 0.7) +
+  theme(legend.position = c(0.8, 0.8))
+
+cowplot::plot_grid(a, labels = "AUTO")
+
+###All Area per family
+
+theme_set(theme_gray())
+a <- ggplot(t_stigma_area, aes(x = um, fill = family)) +
+  geom_density(alpha = 0.7) +
+  theme(legend.position = c(0.8, 0.8))
+
+cowplot::plot_grid(a, labels = "AUTO")
+
+```

### 2018-09-11 Scripts/species_morphometry.R

@@ -15,26 +15,97 @@ t <- cbind(t, d)
 t$trait <- paste(t$a,t$b)
 t <- t[, -c(2,4,5,6)]
 t$trait <- as.character(t$trait)
+t$species_common <- NA
+t$family <- NA
 
+#Add common names
+t$species_common[t$species=="SOLY"] <- "Tomato"
+t$species_common[t$species=="SOME"] <- "Eggplant"
+t$species_common[t$species=="PEIN"] <- "Petunia"
+t$species_common[t$species=="CAAN"] <- "Capsicum"
+t$species_common[t$species=="BROL"] <- "Wild cabbage"
+t$species_common[t$species=="SIAL"] <- "White mustard"
+t$species_common[t$species=="BRRA"] <- "Pak choi"
+t$species_common[t$species=="ERSA"] <- "Rocket"
+t$species_common[t$species=="IPAQ"] <- "Water morning glory"
+t$species_common[t$species=="IPPU"] <- "Morning glory"
 
-t$species_common_names <- ifelse(t$species=="SOME", t$species=="SOLY", "Eggplant", "Tomato", "")
+#Add family
+
+#Add common names
+t$family[t$species=="SOLY"] <- "Solanaceae"
+t$family[t$species=="SOME"] <- "Solanaceae"
+t$family[t$species=="PEIN"] <- "Solanaceae"
+t$family[t$species=="CAAN"] <- "Solanaceae"
+t$family[t$species=="BROL"] <- "Brassicaceae"
+t$family[t$species=="SIAL"] <- "Brassicaceae"
+t$family[t$species=="BRRA"] <- "Brassicaceae"
+t$family[t$species=="ERSA"] <- "Brassicaceae"
+t$family[t$species=="IPAQ"] <- "Convolvulaceae"
+t$family[t$species=="IPPU"] <- "Convolvulaceae"
+
 
 t_stigma_area <- t[t$trait=="style length" | t$trait=="style legth",]
 
+t_stigma_area_brassicaceae <- t_stigma_area[t_stigma_area$species=="BROL" | 
+t_stigma_area$species=="BRRA"| t_stigma_area$species=="SIAL"| t_stigma_area$species=="ERSA" | t_stigma_area$species=="IPPU" ,]
+
+t_stigma_area_solanaceae <- t_stigma_area[t_stigma_area$species=="SOLY" | 
[…]

### 2018-09-24 Rmd/Data_visualization_common_names.Rmd
density plot
adding some text for R

@@
 ###SEED SET PER SPECIES WITH DIFFERENT TREATMENTS
+
+Light blue:Brassicaceae, orange: Convolvulaceae, green:Solanaceae, grey: xenogamy, autogamy and controls
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
@@
 ###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES- (N=3)
+
+Each histogram shows the pollen ratio in percentage of the focal and non-focal species. The barplots are organized per family.
+
 ```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
@@
 
-###STIGMA AREA
+###STIGMA AREA. BRASSICACEAE+1 AND SOLANACEAE+1
 
@@
 ```
+
+\newpage
+
+###STIGMA AREA. ALL SPECIES, COLOUR PER SPECIES AND FAMILY
+
+I like this type of density plot and I wanted to show the differences of stigma area of our 3 familys. The x axis shows the area in micrometers (um^2).
 

### 2018-10-15 Rmd/Data_visualization_common_names.Rmd
took me too much time BUT I made it

@@
 
-Light blue:Brassicaceae, orange: Convolvulaceae, green:Solanaceae, grey: xenogamy, autogamy and controls
 ```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
@@
 library(lattice)
+library(ggpubr)
 #read data and cleaning
@@
 a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="A) Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Capsicum",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="B) Capsicum",x="", y = "")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="C) Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Eggplant",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="D) Eggplant",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
+load("legend.rda")
+grid.newpage()
+grid.draw(legend) 
 ```
+
+**Figure 1**.
+Seed set of Solanaceae species with the different pollination treatments (N=10) A) Petunia, B) Capsicum, C) Tomato, D) Eggplant.
+In total 9 different crosses with 50% heterospecific pollen appear from left to right.
+The focal treatment with itself is shown in blank to maintain simmetry among pannels.
+Moreover, for each species are also shown in grey hand cross pollination, hand self pollination, control (bagged emasculated flowers) and flower control (bagged flowers).
 
@@
 a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="A) Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  labs(title="B) Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="C) Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="D) White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
+load("legend.rda")
+grid.newpage()
+grid.draw(legend) 
 ```
+
+**Figure 2**.
+Seed set of Brassicaceae species with the different pollination treatments (N=10) A) Wild cabbage, B) Pak choi, C) Rocket, D) White mustard.
+In total 9 different crosses with 50% heterospecific pollen appear from left to right.
+The focal treatment with itself is shown in blank to maintain simmetry among pannels.
+Moreover, for each species are also shown in grey hand cross pollination, hand self pollination, control (bagged emasculated flowers) and flower control (bagged flowers).
 
@@
 a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Water morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="A) Water morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="Morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  labs(title="B) Morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
@@
 
+load("legend.rda")
+grid.newpage()
+grid.draw(legend)
+
 ```
+
+**Figure 3**.
+Seed set of Convolvulaceae species with the different pollination treatments (N=10) A) Water morning glory, B) Morning glory.
+In total 9 different crosses with 50% heterospecific pollen appear from left to right.
+The focal treatment with itself is shown in blank to maintain simmetry among pannels.
+Moreover, for each species are also shown in grey hand cross pollination, hand self pollination, control (bagged emasculated flowers) and flower control (bagged flowers).
 
@@
 ```
+
+**Figure 4**. Evolutionary distances of the ten species used in the experiment using maximum composite likelihood method.
 

### 2018-10-15 Scripts/legend_seed_set_solanaceae.R

@@ -1,0 +1,41 @@
+
+library(ggplot2)
+library(grid)
+library(gridExtra)
+
+
+bra <- rep("Brassicaceae",10)
+con<- rep("Convolvulaceae",10)
+sol <- rep("Solanaceae",10)
+foc <- rep("Focal_treatments",10)
+
+b <- seq(1:10)
+dat_0<- data.frame(bra,b)
+dat_1<- data.frame(con,b)
+dat_2<- data.frame(sol,b)
+dat_3<- data.frame(foc,b)
+
+colnames(dat_0) <- c("tre","b")
+colnames(dat_1) <- c("tre","b")
+colnames(dat_2) <- c("tre","b")
+colnames(dat_3) <- c("tre","b")
+
+for_legend <- rbind(dat_0,dat_1,dat_2,dat_3)
+cbPalette <- c( "#56B4E9","#E69F00","#009E73", "#999999")
+
+
+for_leg <- ggplot(for_legend, aes(x = factor(tre, levels=unique(tre)), y = b)) +  geom_boxplot(outlier.shape = NA)+
+  scale_fill_manual(values=cbPalette)+aes(fill=tre)+ 
+  theme(legend.position = "bottom",legend.title=element_blank(),legend.key.size = unit(2, 'lines'),legend.key=element_blank()) 
+
+g_legend <- function(a.gplot){ 
+  tmp <- ggplot_gtable(ggplot_build(a.gplot)) 
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box") 
+  legend <- tmp$grobs[[leg]] 
+  return(legend)} 
+legend <- g_legend(for_leg) 
+grid.newpage()
+grid.draw(legend) 
+
+
+save.image(file = "Rmd/legend.rda")

### 2018-10-16 Rmd/Data_visualization_common_names.Rmd
footnote for all the figures and now time to write a first abstract

@@
 ---
+
+*Abstract*
+
+\newpage
 
@@
 
-Each histogram shows the pollen ratio in percentage of the focal and non-focal species. The barplots are organized per family.
-
 ```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
@@
 ```
+
+**Figure 5**.
+Percentage of pollen deposited on the stigma of a subset of species of the Brassicaceae family with pollen mixes with the other two families (N=3).
+The black line represents the theoretical 50% pollen percentage of our mixes.
+The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
+Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
+
 \newpage
@@
 ```
+
+**Figure 6**.
+Percentage of pollen deposited on the stigma of a subset of species of the Solanaceae family with pollen mixes with the other two families (N=3).
+The black line represents the theoretical 50% pollen percentage of our mixes.
+The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
+Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
+
 \newpage
@@
 ```
+
+**Figure 7**.
+Percentage of pollen deposited on the stigma of a subset of species of the Convolvulaceae family with pollen mixes with the other two families (N=3).
+The black line represents the theoretical 50% pollen percentage of our mixes.
+The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
+Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
 
@@
 
+**Figure 8**.
+Total pollen deposited on the stigma of a subset of species of the Brassicaceae family with pollen mixes with the other two families (N=3).
+The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
+Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
+
 \newpage
@@
 ```
+
+**Figure 9**.
+Total pollen deposited on the stigma of a subset of species of the Solanaceae family with pollen mixes with the other two families (N=3).
+The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
+Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
+
 \newpage
@@
 ```
+
+**Figure 10**.
+Total pollen deposited on the stigma of a subset of species of the Convolvulaceae family with pollen mixes with the other two families (N=3).
+The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
+Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
 
@@
 
-#Samte thing but without eggplant to improve visualization
+```
 
-#all
+**Figure 11**.
+Pollen per anther of the ten species used in our artificial community belonging to three different families, Brassicaceae, Solanaceae and Convolvulaceae (N=20, I.aquatica N=10).
+Species are coloured by family.
+Pollen was counted with an hemocytometer.
+
+\newpage
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
+library(ggplot2)
+
+all <- read.csv("Data/all.csv", header=T)
+
+cbPalette <- c( "#56B4E9","#E69F00","#009E73")
 
@@
   theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
+```
 
-```
+**Figure 12**.
+Pollen per anther of the species used in our artificial community belonging to three different families, Brassicaceae, Solanaceae and Convolvulaceae (N=20, I.aquatica N=10).
+Eggplant excluded in order to improve data visualization.
+Species are coloured by family.
+Pollen was counted with an hemocytometer.
 
@@
 
- d <- d[d$species !="Eggplant",]
-
- ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
-  geom_boxplot(outlier.shape = NA)+labs(title="All species(-Eggplant)",x="", y = "Nº of ovules")+
-  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
-  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
-  scale_color_manual(values = cbPalette) + 
-  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
 ```
 
+**Figure 13**. Number of ovules of the ten species (N=15). Species are coloured by family.
+
 \newpage
-
-###POLLEN OVULE RATIO. TOTAL POLLEN PER FLOWER DIVIDED BY NUMBER OF OVULES
 
@@
 
+**Figure 14**. Pollen ovule ratio for all the species. Total pollen per flower was estimated by multiplying by the total number of anthers of the flower. Species are coloured by family.
+
 \newpage
-
-###STIGMA AREA. BRASSICACEAE+1 AND SOLANACEAE+1
 
@@
 
+**Figure 15**.
+Density plot of the stigmatic area.
+The measurements were conducted with a stereo microscope.
+Species are divided in two pannels of 5 species each (4 Brassicaceae + 1 Convolvulaceae and 4 Solanaceae + 1 Convolvulaceae).
+The x axis shows the area in square micrometers.
+
 \newpage
-
-###STIGMA AREA. ALL SPECIES, COLOUR PER SPECIES AND FAMILY
-
-I like this type of density plot and I wanted to show the differences of stigma area of our 3 familys. The x axis shows the area in micrometers (um^2).
 
@@
 cowplot::plot_grid(a, labels = "AUTO")
+```
 
+**Figure 16**. Density plot of the stigmatic area for all the species. The measurements were conducted with a stereo microscope. The x axis shows the area in square micrometers.
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
+
+t_stigma_area <- read.csv("Data/t_stigma_area.csv")
+t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
+t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
+t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
 ###All Area per family
-
 theme_set(theme_gray())
@@
 ```
+
+**Figure 17**.
+Density plot of the stigmatic area for the 10 species grouped by the three families: Brassicaceae, Solanaceae and Convolvulaceae.
+The measurements were conducted with a stereo microscope.
+The x axis shows the area in square micrometers.

### 2018-10-16 Rmd/Data_visualization_common_names.Rmd
abstract

@@
 *Abstract*
+
+Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen.
+However, the costs of heterospecific pollen are not yet well understood.
+For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
+10 species belonging to three different families: Brassicaceae, Solanaceae, Convolvulaceae were used and more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
+We have found that for all species foreign pollen (50% or less) reduce seed set.
+Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
+However, the effect is governed on the relatedness and traits of the species recipient.
+Our results, show that although the effect of heterospecific pollen is species specific, the outcome of it is determine in greater degree by the traits of the pollen recipient than the pollen donor.
 

### 2018-10-16 Rmd/Data_visualization_common_names.Rmd
abstract changes

@@
 For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
-10 species belonging to three different families: Brassicaceae, Solanaceae, Convolvulaceae were used and more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
+10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae were used and more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
 We have found that for all species foreign pollen (50% or less) reduce seed set.
 Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
-However, the effect is governed on the relatedness and traits of the species recipient.
-Our results, show that although the effect of heterospecific pollen is species specific, the outcome of it is determine in greater degree by the traits of the pollen recipient than the pollen donor.
+However, the effect is governed by the degree of relatedness and the traits of the species recipient.
+Our results, show that although the effect of heterospecific pollen is species specific, the outcome of it is determine in greater degree by the traits of the pollen recipient than the pollen donor and that certain traits such as compatibility system are crucial to understand the costs of heterospecific pollen.
 

### 2018-10-17 Rmd/Data_visualization_common_names.Rmd
Abstract with Nacho´s correction

--- 2018-10-16 Rmd/Data_visualization_common_names.Rmd
@@
 *Abstract*
+
+Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen.
+However, the costs of heterospecific pollen are not yet well understood.
+For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
+We experimentally crossed 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+Overall, more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
+We found that for all species foreign pollen (50% or less) reduced seed set.
+Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
+However, the effect is governed by the degree of relatedness and the traits of the species recipient.
+Our results show that the outcome of heterospecific pollen deposition is determined in greater degree by the traits of the pollen recipient than the pollen donor and that certain traits such as compatibility system are crucial to understand the costs of heterospecific pollen.
 

### 2018-10-17 Scripts/Analysis_mantel_test.R

@@ -4,38 +4,79 @@
 
 soly  <- read.csv("Data/species_seed_set/soly_seed_set.csv", sep=";", stringsAsFactors = F)
 some  <- read.csv("Data/species_seed_set/some_seed_set.csv", sep=";", stringsAsFactors = F)
-pein  <- read.csv("Data/species_seed_set/pein_seed_set.csv", sep=";")
-caan  <- read.csv("Data/species_seed_set/caan_seed_set.csv", sep=";")
-ersa  <- read.csv("Data/species_seed_set/ersa_seed_set.csv", sep=";")
-brra  <- read.csv("Data/species_seed_set/brra_seed_set.csv", sep=";")
-sial  <- read.csv("Data/species_seed_set/sial_seed_set.csv", sep=";")
-brol  <- read.csv("Data/species_seed_set/brol_seed_set.csv", sep=";")
-ippu  <- read.csv("Data/species_seed_set/ippu_seed_set.csv", sep=";")
-ipaq  <- read.csv("Data/species_seed_set/ipaq_seed_set.csv", sep=";")
+pein  <- read.csv("Data/species_seed_set/pein_seed_set.csv", sep=";", stringsAsFactors = F)
+caan  <- read.csv("Data/species_seed_set/caan_seed_set.csv", sep=";", stringsAsFactors = F)
+ersa  <- read.csv("Data/species_seed_set/ersa_seed_set.csv", sep=";", stringsAsFactors = F)
+brra  <- read.csv("Data/species_seed_set/brra_seed_set.csv", sep=";", stringsAsFactors = F)
+sial  <- read.csv("Data/species_seed_set/sial_seed_set.csv", sep=";", stringsAsFactors = F)
+brol  <- read.csv("Data/species_seed_set/brol_seed_set.csv", sep=";", stringsAsFactors = F)
+ippu  <- read.csv("Data/species_seed_set/ippu_seed_set.csv", sep=";", stringsAsFactors = F)
+ipaq  <- read.csv("Data/species_seed_set/ipaq_seed_set.csv", sep=";", stringsAsFactors = F)
 
 #load libraries
 
 library(dplyr)
-str(soly)
+library(reshape2)
 
-
-soly[-grep("100%", soly$Treatment), ]
-
-
-
+#soly[-grep("100%", soly$Treatment), ]
 #To create the matrix of effect we are going to estimate the net effect as 
 #Cross-(average of 50% treatments)
[…]

### 2018-10-19 Rmd/ms_draft.Rmd
changes

@@
 In addition, pollinator sharing is a common feature in natural ecosystems (Ref) and therefore plant species will recieve conspecific pollen but also heterospecific pollen (HP).
+
+The arrival of foreign pollen have been studied by several authors ().
+The effects of it are highly dependent but no studies have been done testing what are the main traits tha cause this negative effect...
+For this reason we have develop an artificial community where we test the followin hypothesis
+
+1) ...
+
+2) ...
 
@@
 The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
-The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), low structural flower complexity and fast life cycle.
+The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle.
 For the purpose of the experiment all the species where consider as pollen recipient and as pollen donor (see interaction matrix, fig 2).

### 2018-10-19 Scripts/Analysis_mantel_test.R

@@ -162,7 +162,6 @@ colnames(evo_distance_its) <- c("BROL", "ERSA", "BRRA", "SIAL", "IPPU", "IPAQ", 
 evo_distance_its <- makeSymm(evo_distance_its)
 diag(evo_distance_its) <- 0
 evo_distance_its <- evo_distance_its[order(rownames(evo_distance_its)), order(colnames(evo_distance_its))] 
-
 mantel.test(matrix_effect_original, evo_distance_its, graph = TRUE)
 
 

### 2018-10-22 Rmd/prueba_plot_family.Rmd
Fixing colours plot

--- 2018-10-16 Rmd/Data_visualization_common_names.Rmd
@@
 ---
-title: "Data_visualization"
-output:
-      pdf_document
+title: "Untitled"
+author: "Jose Barragan"
+date: "22 October 2018"
+output: html_document
 ---
-
-*Abstract*
-
-Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen.
-However, the costs of heterospecific pollen are not yet well understood.
-For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
-10 species belonging to three different families: Brassicaceae, Solanaceae, Convolvulaceae were used and more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
-We have found that for all species foreign pollen (50% or less) reduce seed set.
-Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
-However, the effect is governed on the relatedness and traits of the species recipient.
-Our results, show that although the effect of heterospecific pollen is species specific, the outcome of it is determine in greater degree by the traits of the pollen recipient than the pollen donor.
-
-\newpage
-
-###SEED SET PER SPECIES WITH DIFFERENT TREATMENTS
 
@@
 ```
-
-**Figure 1**.
-Seed set of Solanaceae species with the different pollination treatments (N=10) A) Petunia, B) Capsicum, C) Tomato, D) Eggplant.
-In total 9 different crosses with 50% heterospecific pollen appear from left to right.
-The focal treatment with itself is shown in blank to maintain simmetry among pannels.
-Moreover, for each species are also shown in grey hand cross pollination, hand self pollination, control (bagged emasculated flowers) and flower control (bagged flowers).
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
-library(dplyr)
-
-#load libraries
-library(reshape2)
-library(ggplot2)
-library(dplyr)
-library(gridExtra)
-library(grid)
-library(lattice)
-library(gtable)
-##
-###
-#B. OLERACEA
-###
-##
-#
-
-brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
-brol_seed_set_final=brol_seed_set_final[,-1]
-#Different colour per family
-a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="A) Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
-
-#
-##
-###
-#B. RAPA
-###
-##
-#
-
-brra_seed_set_final <- read.csv("Data/brra_seed_set_final.csv")
-brra_seed_set_final=brra_seed_set_final[,-1]
-
-#Different colour per family
-b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="B) Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
-
-#
-##
-###
-#E. VERSICARIA
-###
-##
-#
-
-ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final_common_names.csv")
-ersa_seed_set_final=ersa_seed_set_final[,-1]
-
-#Different colour per family
-c <- ggplot(ersa_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="C) Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
-
-##
-###
-#S. ALBA  
-###
-##
-#
-
-sial_seed_set_final <- read.csv("Data/sial_seed_set_final_common_names.csv")
-sial_seed_set_final=sial_seed_set_final[,-1]
-
-#Different colour per family
-d <- ggplot(sial_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="D) White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
-
-gl <- lapply(list(a,b,c,d), ggplotGrob)
-library(grid)
-widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
-heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
-lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
-
-grobz <- lapply(list(a, b, c, d), ggplotGrob)
-grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
-                                        rbind(grobz[[2]], grobz[[4]], size = "last")), ncol = 2,top="Brassicaceae Focal species")
-
-grid.draw(grobz.plot)
-
-load("legend.rda")
-grid.newpage()
-grid.draw(legend) 
-```
-
-**Figure 2**.
-Seed set of Brassicaceae species with the different pollination treatments (N=10) A) Wild cabbage, B) Pak choi, C) Rocket, D) White mustard.
-In total 9 different crosses with 50% heterospecific pollen appear from left to right.
-The focal treatment with itself is shown in blank to maintain simmetry among pannels.
-Moreover, for each species are also shown in grey hand cross pollination, hand self pollination, control (bagged emasculated flowers) and flower control (bagged flowers).
-
-\newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}
-
-library(reshape2)
-library(ggplot2)
-library(dplyr)
-library(gridExtra)
-library(grid)
-library(lattice)
-
-#Preparing seed set plots, starting with Petunia
-#
-##
-###
-#I. AQUATICA
-###
-##
-#
-ipaq_seed_set_final <- read.csv("Data/ipaq_seed_set_final_common_names.csv")
-ipaq_seed_set_final=ipaq_seed_set_final[,-1]
-
-cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
-
-#Different colour per family
-a <- ggplot(ipaq_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="A) Water morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
-
-#IPPU
-ippu_seed_set_final <- read.csv("Data/ippu_seed_set_final_common_names.csv")
-ippu_seed_set_final=ippu_seed_set_final[,-1]
-
-#Different colour per family
-b <- ggplot(ippu_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="B) Morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
-
-#There are 3 crosses were seeds were lost (2,7,9)
-#load libraries
-
-#read data and cleaning
-
-gl <- lapply(list(a,b), ggplotGrob)
-library(grid)
-widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
-heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
-lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
-
-grobz <- lapply(list(a, b), ggplotGrob)
-grobz.plot <- arrangeGrob(grobs = list(rbind(grobz[[1]], size = "last"),
-                                        rbind(grobz[[2]], size = "last")), ncol = 2,top="Convolvulaceae")
-
-grid.draw(grobz.plot)
-
-load("legend.rda")
-grid.newpage()
-grid.draw(legend)
-
-```
-
-**Figure 3**.
-Seed set of Convolvulaceae species with the different pollination treatments (N=10) A) Water morning glory, B) Morning glory.
-In total 9 different crosses with 50% heterospecific pollen appear from left to right.
-The focal treatment with itself is shown in blank to maintain simmetry among pannels.
-Moreover, for each species are also shown in grey hand cross pollination, hand self pollination, control (bagged emasculated flowers) and flower control (bagged flowers).
-
-\newpage
-#CHOLOROPLAST RBCL PHYLOGENY
-```{r echo=FALSE, out.width='80%', fig.align='center'}
-knitr::include_graphics('Images/all_species.png')
-```
-
-**Figure 4**. Evolutionary distances of the ten species used in the experiment using maximum composite likelihood method.
-
-\newpage
-###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES- (N=3)
-
-```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
-pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
-ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
-  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
-  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)
-
-```
-
-**Figure 5**.
-Percentage of pollen deposited on the stigma of a subset of species of the Brassicaceae family with pollen mixes with the other two families (N=3).
-The black line represents the theoretical 50% pollen percentage of our mixes.
-The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
-Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
-
-\newpage
-```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
-pollen_ratios_solanaceae <- read.csv("Data/pollen_ratios_solanaceae.csv", header = T)
-ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
-  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
-  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)
-
-```
-
-**Figure 6**.
-Percentage of pollen deposited on the stigma of a subset of species of the Solanaceae family with pollen mixes with the other two families (N=3).
-The black line represents the theoretical 50% pollen percentage of our mixes.
-The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
-Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
-
-\newpage
-```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
-pollen_ratios_convolvulaceae <- read.csv("Data/pollen_ratios_convolvulaceae.csv", header = T)
-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
-  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
-  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
-  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)
-
-```
-
-**Figure 7**.
-Percentage of pollen deposited on the stigma of a subset of species of the Convolvulaceae family with pollen mixes with the other two families (N=3).
-The black line represents the theoretical 50% pollen percentage of our mixes.
-The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
-Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
-
-\newpage
-###TOTAL POLLEN ON STIGMA -NEXT 3 PAGES-
-```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
-total_pollen_brassicaceae <- read.csv("Data/total_pollen_brassicaceae.csv", header=T)
-
-ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen grains on stigma") + 
-  theme(axis.text.x=element_text(angle=60,hjust=1))+
-  scale_fill_manual(values=c("grey10", "grey60"))
-
-```
-
-**Figure 8**.
-Total pollen deposited on the stigma of a subset of species of the Brassicaceae family with pollen mixes with the other two families (N=3).
-The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
-Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
-
-\newpage
-```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
-
-total_pollen_solanaceae <- read.csv("Data/total_pollen_solanaceae.csv", header=T)
-
-ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae", x="", y="Pollen mix ratio") +
-  theme(axis.text.x=element_text(angle=60,hjust=1))+
-  scale_fill_manual(values=c("grey10", "grey60"))
-
-```
-
-**Figure 9**.
-Total pollen deposited on the stigma of a subset of species of the Solanaceae family with pollen mixes with the other two families (N=3).
-The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
-Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
-
-\newpage
-
-```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
-
-total_pollen_convolvulaceae <- read.csv("Data/total_pollen_convolvulaceae.csv", header=T)
-
-ggplot(total_pollen_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) + 
-  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae", x="", y="Pollen mix ratio") + 
-  theme(axis.text.x=element_text(angle=60,hjust=1))+
-  scale_fill_manual(values=c("grey10", "grey60"))
-
-```
-
-**Figure 10**.
-Total pollen deposited on the stigma of a subset of species of the Convolvulaceae family with pollen mixes with the other two families (N=3).
-The sample that was in ethanol was dried in a heater (few days) and then the solution was filled with sodium hydroxide to degradate the tissue.
-Once the tissue was soft, all the solution plus the tissue was placed on a grid and the whole quantity of the microtube was counted.
-
-\newpage
-###POLLEN PER ANTHER (N=20, I. aquatica N=10)
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
-library(ggplot2)
-
-all <- read.csv("Data/all.csv", header=T)
-
-cbPalette <- c( "#56B4E9","#E69F00","#009E73")
-
-#all
-
- ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="All species",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
-
-```
-
-**Figure 11**.
-Pollen per anther of the ten species used in our artificial community belonging to three different families, Brassicaceae, Solanaceae and Convolvulaceae (N=20, I.aquatica N=10).
-Species are coloured by family.
-Pollen was counted with an hemocytometer.
-
-\newpage
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
-library(ggplot2)
-
-all <- read.csv("Data/all.csv", header=T)
-
-cbPalette <- c( "#56B4E9","#E69F00","#009E73")
-
-all <- all[all$species !="Eggplant",]
-
- ggplot(all, aes(x = reorder(species, pollen, FUN = median, na.rm = TRUE), y = pollen)) +   geom_boxplot(outlier.shape = NA)+
-  labs(title="All species(-Eggplant)",x="", y = "Pollen per anther")+aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
-```
-
-**Figure 12**.
-Pollen per anther of the species used in our artificial community belonging to three different families, Brassicaceae, Solanaceae and Convolvulaceae (N=20, I.aquatica N=10).
-Eggplant excluded in order to improve data visualization.
-Species are coloured by family.
-Pollen was counted with an hemocytometer.
-
-\newpage
-###OVULES (N=15)
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3}
-
-d <- read.csv("Data/d.csv")
-
-cbPalette <- c( "#56B4E9","#E69F00","#009E73")
-
-ggplot(d, aes(x = reorder(species, ovules, FUN = median, na.rm = TRUE), y = ovules)) +
-  geom_boxplot(outlier.shape = NA)+labs(title="All species",x="", y = "Nº of ovules")+
-  aes(fill=family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
-  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+
-  geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=family))+
-  scale_color_manual(values = cbPalette) + 
-  stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.title = element_blank())
-
-```
-
-**Figure 13**. Number of ovules of the ten species (N=15). Species are coloured by family.
-
-\newpage
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-library(dplyr)
-library(ggplot2)
-
-tab <- read.csv("Data/tab_common_names.csv", sep="", header = T)
-
-ggplot(tab, aes(x=reorder(species, pollen_ovule_ratio, colour = cut), y=pollen_ovule_ratio))+aes(fill=family)+
-  geom_bar(stat="identity", width=0.5)+theme(axis.text.x = element_text(angle = 60, hjust=1))+scale_fill_manual(values=cbPalette)
-```
-
-**Figure 14**. Pollen ovule ratio for all the species. Total pollen per flower was estimated by multiplying by the total number of anthers of the flower. Species are coloured by family.
-
-\newpage
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-
-t_stigma_area <- read.csv("Data/t_stigma_area.csv")
-t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
-t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
-t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
-
-theme_set(theme_gray())
-a <- ggplot(t_stigma_area_brassicaceae, aes(x = um, fill = species_common)) +
-  geom_density(alpha = 0.7) +
-  theme(legend.position = c(0.8, 0.8))
-
-b <- ggplot(t_stigma_area_solanaceae, aes(x = um, fill = species_common)) +
-  geom_density(alpha = 0.7) +
-  theme(legend.position = c(0.8, 0.8))
-
-cowplot::plot_grid(a,b, labels = "AUTO")
-```
-
-**Figure 15**.
-Density plot of the stigmatic area.
-The measurements were conducted with a stereo microscope.
-Species are divided in two pannels of 5 species each (4 Brassicaceae + 1 Convolvulaceae and 4 Solanaceae + 1 Convolvulaceae).
-The x axis shows the area in square micrometers.
-
-\newpage
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-
-t_stigma_area <- read.csv("Data/t_stigma_area.csv")
-t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
-t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
-t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
-
-theme_set(theme_gray())
-a <- ggplot(t_stigma_area, aes(x = um, fill = species_common)) +
-  geom_density(alpha = 0.7) +
-  theme(legend.position = c(0.8, 0.8))
-
-cowplot::plot_grid(a, labels = "AUTO")
-```
-
-**Figure 16**. Density plot of the stigmatic area for all the species. The measurements were conducted with a stereo microscope. The x axis shows the area in square micrometers.
-
-```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
-
-t_stigma_area <- read.csv("Data/t_stigma_area.csv")
-t_stigma_area_brassicaceae <- read.csv("Data/t_stigma_area_brassicaceae.csv")
-t_stigma_area_solanaceae <- read.csv("Data/t_stigma_area_solanaceae.csv")
-t_stigma_area_convolvulaceae <- read.csv("Data/t_stigma_area_convolvulaceae.csv")
-###All Area per family
-theme_set(theme_gray())
-a <- ggplot(t_stigma_area, aes(x = um, fill = family)) +
-  geom_density(alpha = 0.7) +
-  theme(legend.position = c(0.8, 0.8))
-
-cowplot::plot_grid(a, labels = "AUTO")
-
-```
-
-**Figure 17**.
-Density plot of the stigmatic area for the 10 species grouped by the three families: Brassicaceae, Solanaceae and Convolvulaceae.
-The measurements were conducted with a stereo microscope.
-The x axis shows the area in square micrometers.

### 2018-10-22 Rmd/prueba_plot_family.Rmd
Step by step...

@@
 
-a <- ggplot(pein_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+a <- ggplot(pein_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="A) Petunia",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
@@
 #Different colour per family
-b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+b <- ggplot(caan_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="B) Capsicum",x="", y = "")+aes(fill=Family)+theme(axis.text.x =element_blank())+
@@
 #Different colour per family
-c <- ggplot(soly_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+c <- ggplot(soly_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="C) Tomato",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
@@
 #Different colour per family
-d <- ggplot(some_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+d <- ggplot(some_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
   labs(title="D) Eggplant",x="", y = "")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
@@
 ```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
+library(dplyr)
+
+#load libraries
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(lattice)
+library(gtable)
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
+##
+###
+#B. OLERACEA
+###
+##
+#
+
+brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
+brol_seed_set_final=brol_seed_set_final[,-1]
+#Different colour per family
+a <- ggplot(brol_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="A) Wild cabagge",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+#
+##
+###
+#B. RAPA
+###
+##
+#
+
+brra_seed_set_final <- read.csv("Data/brra_seed_set_final.csv")
+brra_seed_set_final=brra_seed_set_final[,-1]
+
+#Different colour per family
+b <- ggplot(brra_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="B) Pak choi",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+#
+##
+###
+#E. VERSICARIA
+###
+##
+#
+
+ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final_common_names.csv")
+ersa_seed_set_final=ersa_seed_set_final[,-1]
+
+#Different colour per family
+c <- ggplot(ersa_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="C) Rocket",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+##
+###
+#S. ALBA  
+###
+##
+#
+
+sial_seed_set_final <- read.csv("Data/sial_seed_set_final_common_names.csv")
+sial_seed_set_final=sial_seed_set_final[,-1]
+
+#Different colour per family
+d <- ggplot(sial_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="D) White mustard",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+gl <- lapply(list(a,b,c,d), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grobz <- lapply(list(a, b, c, d), ggplotGrob)
+grobz.plot <- arrangeGrob( grobs = list(rbind(grobz[[1]], grobz[[3]], size = "last"),
+                                        rbind(grobz[[2]], grobz[[4]], size = "last")), ncol = 2,top="Brassicaceae Focal species")
+
+grid.draw(grobz.plot)
+
+load("legend.rda")
+grid.newpage()
+grid.draw(legend) 
+```
+
+```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=3.7, fig.width=7,out.width='100%'}
+
+library(reshape2)
+library(ggplot2)
+library(dplyr)
+library(gridExtra)
+library(grid)
+library(lattice)
+
+#Preparing seed set plots, starting with Petunia
+#
+##
+###
+#I. AQUATICA
+###
+##
+#
+ipaq_seed_set_final <- read.csv("Data/ipaq_seed_set_final_common_names.csv")
+ipaq_seed_set_final=ipaq_seed_set_final[,-1]
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
+#Different colour per family
+a <- ggplot(ipaq_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="A) Water morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+#IPPU
+ippu_seed_set_final <- read.csv("Data/ippu_seed_set_final_common_names.csv")
+ippu_seed_set_final=ippu_seed_set_final[,-1]
+
+#Different colour per family
+b <- ggplot(ippu_seed_set_final, aes(x = factor(Family, levels=unique(Family)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
+  labs(title="B) Morning glory",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x = element_text(angle = 60, hjust = 1))+
+  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")
+
+#There are 3 crosses were seeds were lost (2,7,9)
+#load libraries
+
+#read data and cleaning
+
+gl <- lapply(list(a,b), ggplotGrob)
+library(grid)
+widths <- do.call(unit.pmax, lapply(gl, "[[", "widths"))
+heights <- do.call(unit.pmax, lapply(gl, "[[", "heights"))
+lg <- lapply(gl, function(g) {g$widths <- widths; g$heights <- heights; g})
+
+grobz <- lapply(list(a, b), ggplotGrob)
+grobz.plot <- arrangeGrob(grobs = list(rbind(grobz[[1]], size = "last"),
+                                        rbind(grobz[[2]], size = "last")), ncol = 2,top="Convolvulaceae")
+
+grid.draw(grobz.plot)
+
+load("legend.rda")
+grid.newpage()
+grid.draw(legend)
+
+```

### 2018-10-23 Manuscript/Untitled.Rmd
preparing file

---
title: "| Título en español \n| Title in English\n"
author: "Name Apellidos^1^, Nombre Apellidos^2^"
csl: ecosistemas.csl
output:
  pdf_document: default
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: Ecosistemas_template.docx
bibliography:
- references.bib
- knitcitations.bib
---

> (1) Dirección del primer autor.

> (2) Dirección del segundo autor.

> Autor para correspondencia: Nombre Apellidos [minombre@micorreo.com]

# Abstract

> **Title in English**. En el resumen debe constar el propósito del artículo, una síntesis de la metodología utilizada y de los resultados más relevantes obtenidos y sus implicaciones. El resumen debe tener una extensión máxima de 250 palabras, incluyendo, en la primera línea, el título del artículo. Es obligatorio la presentación de un resumen en inglés además del resumen en castellano. Letra Arial 10 y espaciado de 1 línea. Las comunicaciones breves tendrán igualmente un resumen en castellano y en inglés pero la extensión del mismo será de 150 palabras máximo. Únicamente están exentos de aportar resumen las contribuciones enviadas a las secciones de Resúmenes de tesis, Notas y Reseñas bibliográficas.

# Keywords

> keyword1; keyword2; keyword3; keyword4

```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

# Introduction

# Methods

## Análisis de datos

```{r read_data, eval = FALSE, echo = FALSE}
dataset <- read.csv("mydata.csv")
```

Ajustamos un modelo lineal:

$$
y_{i} = \alpha + \beta*x_{i} 
$$

```{r model, echo = FALSE, eval = FALSE}
model <- lm(y ~ x)
```

Utilizamos R `r citep(citation())` y Rmarkdown `r citep(list(citation("knitr"), citation("rmarkdown")))` para todos nuestros análisis. Para ajustar los modelos mixtos utilizamos `lme4` `r citep(citation("lme4"))`.

# Results

Esta sección está dividida en subsecciones.

## Subsección 1

Los árboles de la parcela A fueron más altos que en la parcela B (altura media: `r mean(25, 31, 28)` vs `r mean(13, 19, 16)` m). Y muchos más resultados que se actualizan dinámicamente.

## Subsección 2

Texto.

## Subsección 3

Texto.

# Discusión

Texto.

# Conclusiones

Texto.

# Agradecimientos

Agradecimientos.

###### References

```{r write_citations, cache=FALSE, include=FALSE}
write.bibtex(file="knitcitations.bib")
```

<div id = "refs"></div>

###### TABLA 1

**Tabla 1**. Cada tabla debe aportar su correspondiente encabezamiento explicativo. En los Artículos de investigación, de revisión y Comunicaciones breves se aportarán los encabezamientos tanto en castellano como en inglés, en letra Arial 10 y en página independiente. Es importante que sean simples y que no superen el ancho una página DIN A4 vertical. Los originales se deben aportar en formato tabla y no en formato imagen.

**Table 1**. Table heading in English.

```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
library("knitr")
kable(head(iris))
```

###### PIES DE FIGURA

**Figura 1**. Pie de figura 1.

**Figura 2**. Pie de figura 2.

###### FIGURE LEGENDS

**Figure 1**. Figure caption.

**Figure 2**. Figure caption.

###### FIGURA 1

```{r Fig1, echo=FALSE, fig.cap="Figura 1. Esto es un ejemplo.", cache=FALSE}
x <- rnorm(100)
y <- jitter(x, 1000)
plot(x, y)
```

###### FIGURA 2

```{r Fig2, echo=FALSE, fig.cap="Figura 2. Segundo ejemplo", cache=FALSE}
a <- sort(rnorm(100))
b <- c(rep("Group Small", 35), rep("Group Big", 65))
boxplot(a ~ b)
```

### 2018-10-23 Manuscript/MS.Rmd
file rename

--- 2018-10-23 Manuscript/Untitled.Rmd
@@
 
-> **Title in English**.
-En el resumen debe constar el propósito del artículo, una síntesis de la metodología utilizada y de los resultados más relevantes obtenidos y sus implicaciones.
-El resumen debe tener una extensión máxima de 250 palabras, incluyendo, en la primera línea, el título del artículo.
-Es obligatorio la presentación de un resumen en inglés además del resumen en castellano.
-Letra Arial 10 y espaciado de 1 línea.
-Las comunicaciones breves tendrán igualmente un resumen en castellano y en inglés pero la extensión del mismo será de 150 palabras máximo.
-Únicamente están exentos de aportar resumen las contribuciones enviadas a las secciones de Resúmenes de tesis, Notas y Reseñas bibliográficas.
+Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen.
+However, the costs of heterospecific pollen are not yet well understood.
+For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
+We experimentally crossed 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+Overall, more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
+We found that for all species foreign pollen (50% or less) reduced seed set.
+Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
+However, the effect is governed by the degree of relatedness and the traits of the species recipient.
+Our results show that the outcome of heterospecific pollen deposition is determined in greater degree by the traits of the pollen recipient than the pollen donor and that certain traits such as compatibility system are crucial to understand the costs of heterospecific pollen.
 
@@
 # Introduction
+
+Plant ecological generalization means that a wide range of floral visitors will visit this particular species.
+Normally plant species co-occur with other different species in natural systems and therefore pollinator sharing is common characteristic in natural ecosystems.
 

### 2018-10-23 Manuscript/MS.Rmd
some ideas...

@@
 
-Plant ecological generalization means that a wide range of floral visitors will visit this particular species.
-Normally plant species co-occur with other different species in natural systems and therefore pollinator sharing is common characteristic in natural ecosystems.
+*Paragraph 1*
+Plants with ecological generalization receives a wide range of floral visitors (Refs), these plant species tend to co-occur with other species and have floral visitors in common.
+This potential pollinators can deposit conspecific pollen and heterospecific pollen and cause conspecific pollen loss.
+All this features are important to understand the effectivenes of pollinators and the reproductive biology of the plant.
+Plant species that invest highly in sexual reproduction will have mechanism to attract a great number of pollinators but also to avoid self pollination and possibly different ecological niche of the sexual organs to avoid heterospecific pollen deposition in case this one acts strongly...
+
+*Paragraph 2*
+
+*Paragraph 3*
+
+*Paragraph 4*
 

### 2018-10-29 Manuscript/MS.Rmd
checking correlations and some advances in ms

@@
 *Paragraph 1*
+
 Plants with ecological generalization receives a wide range of floral visitors (Refs), these plant species tend to co-occur with other species and have floral visitors in common.
@@
 All this features are important to understand the effectivenes of pollinators and the reproductive biology of the plant.
-Plant species that invest highly in sexual reproduction will have mechanism to attract a great number of pollinators but also to avoid self pollination and possibly different ecological niche of the sexual organs to avoid heterospecific pollen deposition in case this one acts strongly...
 
@@
 # Methods
+
+The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018.
+Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences.
+The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
+The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle.
+For the purpose of the experiment all the species where consider as pollen recipient and as pollen donor (see interaction matrix, fig 2).
+Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).
+
+**Hand-pollination**
+
+To test heterospecific pollen effect the standard 50-50% pollen mix was performed (Ref) and 100% heterospecific pollen.
+Furthermore, hand cross pollination, hand self pollination, apomixis (emsaculated bagged flowers) and natural selfing (non-emasculated bagged flowers) was tested.
+
+Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
+Had-pollination was realized with 3-4 gentle touches on the surface of the stigma.
+The mixes of pollen were performed based on the pollen counts on an eppendorf.
+Pollen on anthers was counted through Neubaeur chamber.
+
+Treatments: 50-50% and 100%
+
+hand self pollination
+
+hand cross pollination (Pollen from different individual)
+
+Apomixis
+
+Natural selfing
 
@@
 **Figure 2**. Figure caption.
-
-###### FIGURA 1
-
-```{r Fig1, echo=FALSE, fig.cap="Figura 1. Esto es un ejemplo.", cache=FALSE}
-x <- rnorm(100)
-y <- jitter(x, 1000)
-plot(x, y)
-```
-
-###### FIGURA 2
-
-```{r Fig2, echo=FALSE, fig.cap="Figura 2. Segundo ejemplo", cache=FALSE}
-a <- sort(rnorm(100))
-b <- c(rep("Group Small", 35), rep("Group Big", 65))
-boxplot(a ~ b)
-```

### 2018-10-29 Scripts/all_traits.R

@@ -80,7 +80,7 @@ ovary_length$measurement <- gsub('ovary _ legth', 'ovary _ length', ovary_length
 #Ok now all the traits are ready!! Lets add it to traits_all.
 
 traits_all$stigma_area <- stigma_area$um
-traits_all$stigma_lenght <- stigma_lenght$um
+traits_all$stigma_length <- stigma_lenght$um
 traits_all$stigma_surface <- stigma_surface$um
 traits_all$stigma_width <- stigma_width$um
 traits_all$style_length <- stigma_lenght$um
@@ -90,3 +90,131 @@ traits_all$ovary_length <- ovary_length$um
 
 
 #write.csv(traits_all, "Data/traits_all.csv")
+
+#Checking for correlations
+
+library(dplyr)
+
+length <- filter(morphometry, measurement=="stigma _ length" & species=="SOME")
+width <- filter(morphometry, measurement=="stigma _ width" & species=="SOME")
+area <- filter(morphometry, measurement=="stigma _ area" & species=="SOME")
+o_length <- filter(morphometry, measurement=="ovary _ legth" & species=="SOME")
+o_width <- filter(morphometry, measurement=="ovary _ width" & species=="SOME")
+s_length <- filter(morphometry, measurement=="style _ length" & species=="SOME")
+s_width <- filter(morphometry, measurement=="style _ width" & species=="SOME")
+
+s_width<- s_width[1:15,]
+
+cor.test(length$um, width$um)
+cor.test(length$um, area$um)
+cor.test(width$um, area$um)
+cor.test(o_width$um, o_length$um)
+cor.test(length$um, o_length$um)
+cor.test(s_length$um, s_width$um)
+cor.test(s_length$um, length$um)
+cor.test(s_length$um, o_length$um)
+
+
+
+length <- filter(morphometry, measurement=="stigma _ length" & species=="CAAN")
+width <- filter(morphometry, measurement=="stigma _ width" & species=="CAAN")
+area <- filter(morphometry, measurement=="stigma _ area" & species=="CAAN")
+o_length <- filter(morphometry, measurement=="ovary _ legth" & species=="CAAN")
+o_width <- filter(morphometry, measurement=="ovary _ width" & species=="CAAN")
+s_length <- filter(morphometry, measurement=="style _ length" & species=="CAAN")
+s_width <- filter(morphometry, measurement=="style _ width" & species=="CAAN")
+s_width<- s_width[1:15,]
+
[…]

### 2018-11-01 Manuscript/MS.Rmd
changes

@@
 
-## Análisis de datos
-
-```{r read_data, eval = FALSE, echo = FALSE}
-dataset <- read.csv("mydata.csv")
-```
-
-Ajustamos un modelo lineal:
-
-$$
-y_{i} = \alpha + \beta*x_{i} 
-$$
-
-```{r model, echo = FALSE, eval = FALSE}
-model <- lm(y ~ x)
-```
-
-Utilizamos R `r citep(citation())` y Rmarkdown `r citep(list(citation("knitr"), citation("rmarkdown")))` para todos nuestros análisis.
-Para ajustar los modelos mixtos utilizamos `lme4` `r citep(citation("lme4"))`.
-
-# Results
-
-Esta sección está dividida en subsecciones.
-
-## Subsección 1
-
-Los árboles de la parcela A fueron más altos que en la parcela B (altura media: `r mean(25, 31, 28)` vs `r mean(13, 19, 16)` m). Y muchos más resultados que se actualizan dinámicamente.
-
-## Subsección 2
-
-Texto.
-
-## Subsección 3
-
-Texto.
-
-# Discusión
-
-Texto.
-
-# Conclusiones
-
-Texto.
-
-# Agradecimientos
-
-Agradecimientos.
+# Methods
 
@@
 <div id = "refs"></div>
-
-###### TABLA 1
-
-**Tabla 1**.
-Cada tabla debe aportar su correspondiente encabezamiento explicativo.
-En los Artículos de investigación, de revisión y Comunicaciones breves se aportarán los encabezamientos tanto en castellano como en inglés, en letra Arial 10 y en página independiente.
-Es importante que sean simples y que no superen el ancho una página DIN A4 vertical.
-Los originales se deben aportar en formato tabla y no en formato imagen.
-
-**Table 1**. Table heading in English.
-
-```{r Tabla1, results='asis', echo=FALSE, cache=FALSE}
-library("knitr")
-kable(head(iris))
-```
-
-###### PIES DE FIGURA
-
-**Figura 1**. Pie de figura 1.
-
-**Figura 2**. Pie de figura 2.
-
-###### FIGURE LEGENDS
-
-**Figure 1**. Figure caption.
-
-**Figure 2**. Figure caption.

### 2018-11-01 Scripts/Analysis_mantel_test.R

@@ -250,9 +250,12 @@ traits_self <- traits_all[,4]
 traits_self <- as.data.frame(traits_self)
 traits_self <- 1- traits_self
 rownames(traits_self) <- rownames(matrix_scale_effect)
-traits_self_dist <- dist(traits_self, diag=T, upper=T)
+traits_self_dist <- dist(traits_self, diag=T, upper=T, method = "manhattan")
 mantel(matrix_scale_effect, traits_self_dist)
-bioenv(matrix_scale_effect~as.matrix(traits_self)+as.matrix(traits_ratio)+as.matrix(traits_ovules))
+bioenv(matrix_scale_effect~as.matrix(traits_all$mean_pollen_anther))
+
+matrix_scale_effect=matrix_scale_effect+abs(min(matrix_scale_effect))
+
 
 str(traits_self)
 

### 2018-11-01 Manuscript_draft/Manuscript_draft.Rmd
rename

---
title: 'How Phylogeny and traits relate to heterospecific pollen effect'

author:

- name: Jose B. Lanuza
  affilnum: '1,2'

- name:  
  affilnum: 3
  email: barragansljose@gmail.com

affiliation:

- affilnum: 1
  affil: US Environmental Protection Agency, Office of Research and Development, National Health and Environmental Effects Research Laboratory, Atlantic Ecology Division, 27 Tarzwell Drive  Narragansett, RI, 02882, USA

- affilnum: 2
  affil: Big Name University, Department of R, City, BN, 01020, USA

- affilnum: 3
  affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain

output:

  pdf_document:
    fig_caption: yes
    fig_width: 7
    fig_height: 7
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
    includes:
      in_header: header.tex

  html_document: null

  word_document: null

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: doublespacing
footerdate: yes
abstract: no
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

---

```{r setup, include=FALSE, cache=FALSE, message = FALSE}

library("knitr")

#opts_knit$set(root.dir=normalizePath('../'))

### Chunk options: see http://yihui.name/knitr/options/ ###

## Text results
opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)

## Code decoration
opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)

## Cache
opts_chunk$set(cache = 2, cache.path = "output/cache/")

## Plots
opts_chunk$set(fig.path = "output/figures/")

```

```{r knitcitations, echo=FALSE, cache = FALSE}
library(knitcitations)
cleanbib()   
cite_options(citation_format = "pandoc")
```

\singlespace

\vspace{2mm}\hrule

Write your abstract here.

\vspace{3mm}\hrule

*Keywords*: rmarkdown, reproducible science

\doublespace

\bleft

# INTRODUCTION

# METHODS

The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018. Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences. The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae. The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle. For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2). Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).

**Hand-pollination**

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10). Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10). Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Had-pollination was realized with 3-4 gentle touches on the surface of the stigma. The mixes of pollen were performed based on the pollen counts (Neubaeur chamber) on an eppendorf.

Explain the phylogeny...

Explain the measurement of the traits...

```{r model, echo = FALSE, eval = FALSE}
model <- lm(y ~ x)
```

We used the statistical language `R` `r citep(citation())` for all our analyses. These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages. All the multilevel models were fitted with `lme4` `r citep(citation("lme4"))`.

# RESULTS

Trees in forest A grew taller than those in forest B (mean height: `r mean(25, 31, 28)` versus `r mean(13, 19, 16)` m). And many more cool results that get updated dynamically.

# DISCUSSION

Discuss.

# CONCLUSIONS

# ACKNOWLEDGEMENTS

# REFERENCES

```{r write_citations, cache=FALSE, include=FALSE}
write.bibtex(file="knitcitations.bib")
```

<div id = "refs"></div>

\eleft

\clearpage

\listoftables

\newpage

\newpage

\clearpage

\listoffigures

\newpage

\newpage

\blandscape

\elandscape

\clearpage

### 2018-11-01 Manuscript_draft/Untitled.tex
rename

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Original default rstudio/pandoc latex file
%% upated by @jhollist 09/15/2014
%% inspired by @cboetting https://github.com/cboettig/template and
%% @rmflight blog posts:
%% http://rmflight.github.io/posts/2014/07/analyses_as_packages.html 
%% http://rmflight.github.io/posts/2014/07/vignetteAnalysis.html).  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={How Phylogeny and traits relate to heterospecific pollen effect},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
  \linenumbers % turns line numbering on 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Packages and layout changes by @jhollist 09/15/2014
\usepackage{ragged2e}
\usepackage[font=normalsize]{caption}
  \usepackage[doublespacing]{setspace}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
  \rfoot{\today}
\lfoot{\thepage}
%%Changed default abstract width and added lines
\renewenvironment{abstract}{
  \hfill\begin{minipage}{1\textwidth}
  \rule{\textwidth}{1pt}\vspace{5pt}
  \normalsize
  \begin{justify}
  \bfseries\abstractname\vspace{5pt}
  \end{justify}}
  {\par\noindent\rule{\textwidth}{1pt}\end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{How Phylogeny and traits relate to heterospecific pollen effect}
\author{
Jose B. Lanuza
true
}
\date{}
% Allowing for landscape pages
\usepackage{lscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}

% Left justification of the text: see https://www.sharelatex.com/learn/Text_alignment
% \usepackage[document]{ragged2e} % already in the latex template
\newcommand{\bleft}{\begin{flushleft}}
\newcommand{\eleft}{\end{flushleft}}

%%Fix tightlist error: https://stackoverflow.com/questions/40438037/tightlist-error-using-pandoc-with-markdown
%%Added 2018-03-26 
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
%%%

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge How Phylogeny and traits relate to heterospecific pollen effect
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jose B. Lanuza \textsuperscript{1,2} 
true
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
\\*
\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
\\*
\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:f.rodriguez.sanc@gmail.com}{\nolinkurl{f.rodriguez.sanc@gmail.com}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

\end{singlespace}

\singlespace

\vspace{2mm}\hrule

Write your abstract here.

\vspace{3mm}\hrule

\emph{Keywords}: rmarkdown, reproducible science

\doublespace

\bleft

\section{INTRODUCTION}\label{introduction}

\section{METHODS}\label{methods}

The study was conducted in a glasshouse at University of New England
(Armidale, Australia) from November 2017 to March 2018. Rooms were
temperature controlled depending on the requirements of the species with
day and night temperature differences. The species selected (Table 1)
belonged to three different families, Solanaceae, Brassicaceae and
Convolvulaceae. The criteria of species/family selection was based on
close/distant related species (see phylogenetic tree for relatedness fig
1), heterogeneous traits, low structural flower complexity and fast life
cycle. For the purpose of the experiment all the species where
considered as pollen recipient and as pollen donor (see interaction
matrix, fig 2). Species were watered once or twice per day and
fertilized weekly (NPK 23: 3.95: 14).

\textbf{Hand-pollination}

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10). Moreover, hand cross pollination,
hand self pollination, apomixis (bagged emasculated flowers) and natural
selfing were tested (N=10). Flowers were emasculated the day prior
anthesis and hand pollinated next day with a toothpick. Had-pollination
was realized with 3-4 gentle touches on the surface of the stigma. The
mixes of pollen were performed based on the pollen counts (Neubaeur
chamber) on an eppendorf.

We used the statistical language \texttt{R} (R Core Team 2018) for all
our analyses. These were implemented in dynamic rmarkdown documents
using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
(Allaire et al. 2018) packages. All the multilevel models were fitted
with \texttt{lme4} (Bates et al. 2015).

\section{RESULTS}\label{results}

Trees in forest A grew taller than those in forest B (mean height: 25
versus 13 m). And many more cool results that get updated dynamically.

\section{DISCUSSION}\label{discussion}

Discuss.

\section{CONCLUSIONS}\label{conclusions}

\section{ACKNOWLEDGEMENTS}\label{acknowledgements}

\section{REFERENCES}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-Allaire_2018}{}
Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
Wickham, J. Cheng, and W. Chang. 2018. Rmarkdown: Dynamic documents for
r.

\hypertarget{ref-Bates_2015}{}
Bates, D., M. Mächler, B. Bolker, and S. Walker. 2015. Fitting linear
mixed-effects models using lme4. Journal of Statistical Software
67:1--48.

\hypertarget{ref-R_Core_Team_2018}{}
R Core Team. 2018. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

\hypertarget{ref-Xie_2014}{}
Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
Implementing reproducible computational research. Chapman; Hall/CRC.

\hypertarget{ref-Xie_2015}{}
Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
Hall/CRC, Boca Raton, Florida.

\hypertarget{ref-Xie_2018}{}
Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
generation in r.

\eleft

\clearpage

\listoftables

\newpage

\newpage

\clearpage

\listoffigures

\newpage

\newpage

\blandscape

\elandscape

\clearpage

\end{document}

### 2018-11-02 Manuscript_draft/Manuscript_draft.Rmd
other changes...
adding some refs

@@
 ---
-title: 'How Phylogeny and traits relate to heterospecific pollen effect'
+title: 'How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community'
 
@@
 
-Write your abstract here.
+Possible journals to publish: New phytologist, journal of ecology, oikos...
 
@@
 
-*Keywords*: rmarkdown, reproducible science
+*Keywords*: heterospecific pollen, plant reproduction, fitness, competition
 
@@
 # INTRODUCTION
+
+**Paragraph 1**
+
+In natural systems plant species normally coexist and share their floral visitors with other species (Bascompte et al., 2003).
+This pollinator sharing from the plant perpective can be negative due to competition (refs) or positive due to facilitation (refs).
+Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss.
+
+**Paragraph 2**
+
+The effect of heterospecific pollen has been widely studied (refs).
+Native species are supposed to have greater negative effects than native ones @arceo2016.
+However, the quantity of pollen that integrates in the network can be quite low @bartomeus2008.
+Moreover, closely related species are supposed to reduce fitness in greter effect but the evidence is scarce and based on independent studies with different methodlogies (refs) or studies that just check that with very highly close related species with the aim of study hybridization (refs).
+
+**Paragraph 3**
+
+Relatedness. What we know?
+
+**Paragraph 4**
+
+The great difficulty of working with pollen in a coflowering community make the understanding of heterospecifc pollen effect a real challenge.
+For this reason we have created an artificial co-flowering community in a glasshouse to test the effect with all the possible combinations among them.
+Where we test the folowing hypothesis: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on the relatedness of the species, 3) Does heterospecific pollen effect depend on any floral trait?
 
@@
 Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10).
+The proxy of effect were seed set and "pollen tubes".
 Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10).
@@
 Had-pollination was realized with 3-4 gentle touches on the surface of the stigma.
-The mixes of pollen were performed based on the pollen counts (Neubaeur chamber) on an eppendorf.
+The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).
 
-Explain the phylogeny...
+**Evolutive distance**
 
-Explain the measurement of the traits...
+Two types of evolutive distances were calculated with MEGA7 thow kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)
+
+**Traits**
+
+Several traits of the ten species were measured.
+Pollen per anther was counted, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length.
+Moreover stigma type was tested.
+Self-incompatibility was
 
@@
 # RESULTS
-
-Trees in forest A grew taller than those in forest B (mean height: `r mean(25, 31, 28)` versus `r mean(13, 19, 16)` m). And many more cool results that get updated dynamically.
 

### 2018-11-02 Manuscript_draft/Manuscript_draft.tex
adding some refs

--- 2018-11-01 Manuscript_draft/Untitled.tex
@@
             pdfauthor={},
-            pdftitle={How Phylogeny and traits relate to heterospecific pollen effect},
+            pdftitle={How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community},
             colorlinks=true,
@@
 
-\title{How Phylogeny and traits relate to heterospecific pollen effect}
+\title{How phylogenetic relatedness and floral traits are involved in
+heterospecifc pollen effect in an artificial co-flowering community}
 \author{
@@
 \begin{center}
-\huge How Phylogeny and traits relate to heterospecific pollen effect
+\huge How phylogenetic relatedness and floral traits are involved in
+heterospecifc pollen effect in an artificial co-flowering community
 \end{center}
@@
 \fi
-\href{mailto:f.rodriguez.sanc@gmail.com}{\nolinkurl{f.rodriguez.sanc@gmail.com}}
+\href{mailto:barragansljose@gmail.com}{\nolinkurl{barragansljose@gmail.com}}
 \stepcounter{num}
@@
 
-Write your abstract here.
+Possible journals to publish: New phytologist, journal of ecology,
+oikos\ldots{}
 
@@
 
-\emph{Keywords}: rmarkdown, reproducible science
+\emph{Keywords}: heterospecific pollen, plant reproduction, fitness,
+competition
 
@@
 \section{INTRODUCTION}\label{introduction}
+
+\textbf{Paragraph 1}
+
+In natural systems plant species normally coexist and share their floral
+visitors with other species (Bascompte et al., 2003). This pollinator
+sharing from the plant perpective can be negative due to competition
+(refs) or positive due to facilitation (refs). Moreover, once the
+pollinator has landed on the stigma some other issues for the species
+fitness may arise, the arrival of foreign pollen and conspecific pollen
+loss.
+
+\textbf{Paragraph 2}
+
+The effect of heterospecific pollen has been widely studied (refs).
+Native species are supposed to have greater negative effects than native
+ones Arceo-Gómez and Ashman (2016)
+
+species-specific. What kind of pollen interaction? Size just mechanical?
+
+\textbf{Paragraph 3}
+
+Relatedness. What we know?
+
+\textbf{Paragraph 4}
+
+The great difficulty of working with pollen in a coflowering community
+make the understanding of heterospecifc pollen effect a real challenge.
+For this reason we have created an artificial co-flowering community in
+a glasshouse to test the effect with all the possible combinations among
+them. Where we test the folowing hypothesis: 1) Does heterospecific
+pollen reduce seed set, if so, 2) Does heterospecific pollen effect
+depend on the relatedness of the species, 3) Does heterospecific pollen
+effect depend on any floral trait?
 
@@
 with 50\% conspecific pollen and 50\% heterospecific pollen and a second
-one with 100\% foreign pollen (N=10). Moreover, hand cross pollination,
-hand self pollination, apomixis (bagged emasculated flowers) and natural
-selfing were tested (N=10). Flowers were emasculated the day prior
-anthesis and hand pollinated next day with a toothpick. Had-pollination
-was realized with 3-4 gentle touches on the surface of the stigma. The
-mixes of pollen were performed based on the pollen counts (Neubaeur
-chamber) on an eppendorf.
+one with 100\% foreign pollen (N=10). The proxy of effect were seed set
+and ``pollen tubes''. Moreover, hand cross pollination, hand self
+pollination, apomixis (bagged emasculated flowers) and natural selfing
+were tested (N=10). Flowers were emasculated the day prior anthesis and
+hand pollinated next day with a toothpick. Had-pollination was realized
+with 3-4 gentle touches on the surface of the stigma. The mixes of
+pollen were performed on an eppendorf based on the pollen counts maded
+with Neubaeur chamber (each anther was counted 4 times for 20 different
+anthers per species).
+
+\textbf{Evolutive distance}
+
+Two types of evolutive distances were calculated with MEGA7 thow kinds
+of markers: 1) Internal transcribed spacer (ITS) and 2)
+ribulose-bisphosphate carboxylase (RBCL)
+
+\textbf{Traits}
+
+Several traits of the ten species were measured. Pollen per anther was
+counted, number of ovules, stigma width and length and stigmatic area,
+style width and length, ovary width and length. Moreover stigma type was
+tested. Self-incompatibility was
 
@@
 \section{RESULTS}\label{results}
-
-Trees in forest A grew taller than those in forest B (mean height: 25
-versus 13 m). And many more cool results that get updated dynamically.
 
@@
 r.
+
+\hypertarget{ref-arceo2016}{}
+Arceo-Gómez, G., and T.-L. Ashman. 2016. Invasion status and
+phylogenetic relatedness predict cost of heterospecific pollen receipt:
+Implications for native biodiversity decline. Journal of Ecology
+104:1003--1008.
 

### 2018-11-02 Manuscript_draft/Manuscript_draft.Rmd
some changes

@@
 This pollinator sharing from the plant perpective can be negative due to competition (refs) or positive due to facilitation (refs).
-Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss.
+Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss (Morales & Traveset 2008)
 
@@
 
-The effect of heterospecific pollen has been widely studied (refs).
-Native species are supposed to have greater negative effects than native ones @arceo2016.
+The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008).
+Native species are supposed to have greater negative effect than native ones @arceo2016.
 However, the quantity of pollen that integrates in the network can be quite low @bartomeus2008.
-Moreover, closely related species are supposed to reduce fitness in greter effect but the evidence is scarce and based on independent studies with different methodlogies (refs) or studies that just check that with very highly close related species with the aim of study hybridization (refs).
+Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs).
+There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect.
+Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect.
+Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.
 
 **Paragraph 3**
-
-Relatedness. What we know?
 
@@
 
+Brown and Mitchell 2001 could be a good paper to explain why we pick seed set as a proxy and not fruit set. We cannot see changes on it, losing information with it.
+
 **Hand-pollination**
@@
 Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10).
-The proxy of effect were seed set and "pollen tubes".
+Seed set was the proxy of effect (see Brown and Mitchell 2001, for differences in effect between seed set and fruit set) and "pollen tubes".
 Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10).

### 2018-11-02 Manuscript_draft/Manuscript_draft.tex
some changes

@@
 fitness may arise, the arrival of foreign pollen and conspecific pollen
-loss.
+loss (Morales \& Traveset 2008)
 
@@
 
-The effect of heterospecific pollen has been widely studied (refs).
-Native species are supposed to have greater negative effects than native
-ones Arceo-Gómez and Ashman (2016)
-
-species-specific. What kind of pollen interaction? Size just mechanical?
+The effect of heterospecific pollen has been widely studied (Morales \&
+Traveset 2008). Native species are supposed to have greater negative
+effect than native ones Arceo-Gómez and Ashman (2016). However, the
+quantity of pollen that integrates in the network can be quite low
+Bartomeus et al. (2008). Moreover, closely related species are supposed
+to reduce fitness in greater effect but the evidence is scarce and based
+on independent studies with different methodologies (Arceo-gomez \&
+Ashman 2016) or studies that just check it with a pair of species that
+are highly related with the aim to understand hybridization costs
+(refs). There is a need to deepen into how relatednes is involve in the
+costs of heterospecific pollen effect. Furthermore, following the
+conceptual trait framework of Ashman and Arceo-Gomez on heterospecific
+pollen there are good theoretical basis for trait effect.
+Notwithstanding, non empirical work has tested how really these traits
+are involved in heterospecific pollen effect.
 
 \textbf{Paragraph 3}
-
-Relatedness. What we know?
 
@@
 
+Brown and Mitchell 2001 could be a good paper to explain why we pick
+seed set as a proxy and not fruit set. We cannot see changes on it,
+losing information with it.
+
 \textbf{Hand-pollination}
@@
 with 50\% conspecific pollen and 50\% heterospecific pollen and a second
-one with 100\% foreign pollen (N=10). The proxy of effect were seed set
-and ``pollen tubes''. Moreover, hand cross pollination, hand self
-pollination, apomixis (bagged emasculated flowers) and natural selfing
-were tested (N=10). Flowers were emasculated the day prior anthesis and
-hand pollinated next day with a toothpick. Had-pollination was realized
-with 3-4 gentle touches on the surface of the stigma. The mixes of
-pollen were performed on an eppendorf based on the pollen counts maded
-with Neubaeur chamber (each anther was counted 4 times for 20 different
-anthers per species).
+one with 100\% foreign pollen (N=10). Seed set was the proxy of effect
+(see Brown and Mitchell 2001, for differences in effect between seed set
+and fruit set) and ``pollen tubes''. Moreover, hand cross pollination,
+hand self pollination, apomixis (bagged emasculated flowers) and natural
+selfing were tested (N=10). Flowers were emasculated the day prior
+anthesis and hand pollinated next day with a toothpick. Had-pollination
+was realized with 3-4 gentle touches on the surface of the stigma. The
+mixes of pollen were performed on an eppendorf based on the pollen
+counts maded with Neubaeur chamber (each anther was counted 4 times for
+20 different anthers per species).
 
@@
 104:1003--1008.
+
+\hypertarget{ref-bartomeus2008}{}
+Bartomeus, I., J. Bosch, and M. Vilà. 2008. High invasive pollen
+transfer, yet low deposition on native stigmas in a carpobrotus-invaded
+community. Annals of Botany 102:417--424.
 

### 2018-11-03 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008).
-Native species are supposed to have greater negative effect than native ones @arceo2016.
-However, the quantity of pollen that integrates in the network can be quite low @bartomeus2008.
+Invasive species are supposed to have greater negative effect than native ones @arceo2016.
+Although when non-natives species don´t have greater negative effect we still don´t know why.
+For this reason, this ecological question is non a native non native one is a trait based issue that is still to be solved.
+Moreover, the quantity of pollen that integrates in the network can be quite variable ranging from low quatities @bartomeus2008 to intermediate (ref) to high (ref).
 Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs).
@@
 Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.
+
+Explain traits. Put examples
 

### 2018-11-03 Manuscript_draft/Manuscript_draft.tex
changes

@@
 The effect of heterospecific pollen has been widely studied (Morales \&
-Traveset 2008). Native species are supposed to have greater negative
-effect than native ones Arceo-Gómez and Ashman (2016). However, the
-quantity of pollen that integrates in the network can be quite low
-Bartomeus et al. (2008). Moreover, closely related species are supposed
-to reduce fitness in greater effect but the evidence is scarce and based
-on independent studies with different methodologies (Arceo-gomez \&
-Ashman 2016) or studies that just check it with a pair of species that
-are highly related with the aim to understand hybridization costs
-(refs). There is a need to deepen into how relatednes is involve in the
-costs of heterospecific pollen effect. Furthermore, following the
-conceptual trait framework of Ashman and Arceo-Gomez on heterospecific
-pollen there are good theoretical basis for trait effect.
-Notwithstanding, non empirical work has tested how really these traits
-are involved in heterospecific pollen effect.
+Traveset 2008). Invasive species are supposed to have greater negative
+effect than native ones Arceo-Gómez and Ashman (2016). Although when
+non-natives species don´t have greater negative effect we still don´t
+know why. For this reason, this ecological question is non a native non
+native one is a trait based issue that is still to be solved. Moreover,
+the quantity of pollen that integrates in the network can be quite
+variable ranging from low quatities Bartomeus et al. (2008) to
+intermediate (ref) to high (ref). Moreover, closely related species are
+supposed to reduce fitness in greater effect but the evidence is scarce
+and based on independent studies with different methodologies
+(Arceo-gomez \& Ashman 2016) or studies that just check it with a pair
+of species that are highly related with the aim to understand
+hybridization costs (refs). There is a need to deepen into how
+relatednes is involve in the costs of heterospecific pollen effect.
+Furthermore, following the conceptual trait framework of Ashman and
+Arceo-Gomez on heterospecific pollen there are good theoretical basis
+for trait effect. Notwithstanding, non empirical work has tested how
+really these traits are involved in heterospecific pollen effect.
+
+Explain traits. Put examples
 

### 2018-11-03 Rmd/Data_visualization_common_names.Rmd
Fixing colours plot
changes

@@
 
-*Abstract*
+# Abstract
 
@@
 Our results show that the outcome of heterospecific pollen deposition is determined in greater degree by the traits of the pollen recipient than the pollen donor and that certain traits such as compatibility system are crucial to understand the costs of heterospecific pollen.
+
+# Results
+
+First I show numerical results
+
+Proof firstly the effect of hp respect the cross... DO IT!
+
+To test the possible relationships between heterospecific pollen effect and phylogenetic distance we have performed Mantel test between the scaled distance matrix of effect (hand-cross pollination substracted by the mean heterospecifc pollen effect) and the evolutive distances (calculated with both ITS and RBCL markes, obtaining similar results).
+Following Letten & Cornwell 2015 check other ref we have compare it with square root of the evolutive distance matrix.
+
+Post here results...
+
+```{r, message=FALSE, warning=FALSE, size='tiny'}
+read.csv("Data/matrix_scale_effect.csv", row.names=1, header=T)
+```
+
+Check with traits!! I still have to work more on them
 
@@
 library(gtable)
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
 ##

### 2018-11-03 Scripts/Analysis_mantel_test.R

@@ -434,43 +434,11 @@ traits_all_scale_dist <- dist(traits_all_scale, diag=T, upper=T)
 mantel(matrix_scale_effect, traits_all_scale_dist)
 
 
+#Just checking how dist works
+#dist(traits_all$mean_ovules, diag = T, upper=T)
+#Distances are equal at both sides of the matrix
+#I´m using the default euclidean distance
+# sqrt(sum((x-y)2))
 
 
 
-
-
-
-#Checking waysto plot distance matrices
-#Way 1
-library(qgraph)
-traits_all_dist_inverse <- 1/traits_all_dist
-jpeg('example_forcedraw.jpg', width=1000, height=1000, unit='px')
-qgraph(traits_all_dist_inverse, layout='spring', vsize=3)
-dev.off()
-
-#Way 2
-traits_all_dist_low <- dist(traits_all, diag=T)
-traits_all_dist_inverse_low <- 1/traits_all_dist_low
-
-table.dist(traits_all_dist_inverse_low, clabel = 0.8, csize = 1, grid = TRUE, 
-           labels=attr(traits_all_dist_inverse, "Labels"))
-
-
-
-
-
-
-data(varespec)
-data(varechem)
-sol <- bioenv(wisconsin(varespec) ~ log(N) + P + K + Ca + pH + Al, varechem)
-sol
-summary(sol)
-
-bioenv(matrix_scale_effect ~  traits_all$Selfing_rate)
-
-
-
-
-
-
-#

### 2018-11-04 Scripts/Analysis_mantel_test.R
changes

@@ -193,6 +193,9 @@ matrix_cross_scale <- matrix_cross_scale + abs(a)
 #The normal values of seed set are going to be on a side for a while
 matrix_scale_effect <- matrix_cross_scale-matrix_scale
 
+#Write csv in the two data folders in order to print 
+#write.csv(matrix_scale_effect, "Data/matrix_scale_effect.csv")
+#write.csv(matrix_scale_effect, "Rmd/Data/matrix_scale_effect.csv")
 #Now edit the evolutionary distances
 #They are the distances calculated with MEGA 7 (pairwise distances)
 evo_distance_rbcl <- evo_distance_rbcl[ , -2]

### 2018-11-07 Manuscript_draft/Manuscript_draft.Rmd
some editing

@@
 ---
-title: 'How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community'
-
+title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
 author:
-
-- name: Jose B. Lanuza
-  affilnum: '1,2'
-
-- name:  
+- affilnum: '1,2'
+  name: Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
+- affilnum: 3
+  email: barragansljose@gmail.com
+  name: null
+affiliation:
+- affil: US Environmental Protection Agency, Office of Research and Development, National
+    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
+    27 Tarzwell Drive  Narragansett, RI, 02882, USA
+  affilnum: 1
+- affil: Big Name University, Department of R, City, BN, 01020, USA
+  affilnum: 2
+- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
   affilnum: 3
-  email: barragansljose@gmail.com
-
-affiliation:
-
-- affilnum: 1
-  affil: US Environmental Protection Agency, Office of Research and Development, National Health and Environmental Effects Research Laboratory, Atlantic Ecology Division, 27 Tarzwell Drive  Narragansett, RI, 02882, USA
-
-- affilnum: 2
-  affil: Big Name University, Department of R, City, BN, 01020, USA
-
-- affilnum: 3
-  affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
-
 output:
-
   pdf_document:
     fig_caption: yes
+    fig_height: 7
     fig_width: 7
-    fig_height: 7
+    includes:
+      in_header: header.tex
     keep_tex: yes
@@
     template: manuscript.latex
-    includes:
-      in_header: header.tex
-
+  word_document: null
   html_document: null
-
-  word_document: null
-
+capsize: normalsize
+classoption: a4paper
+csl: ecology.csl
 documentclass: article
-classoption: a4paper
-capsize: normalsize
 fontsize: 11pt
+footerdate: yes
 geometry: margin=1in
 linenumbers: yes
-spacing: doublespacing
-footerdate: yes
-abstract: no
 bibliography:
@@
 - knitcitations.bib
-csl: ecology.csl
-
+spacing: doublespacing
+abstract: no
 ---
@@
 # INTRODUCTION
+[Cut and paste some paragraphs from your literature review/ proposal](Romina)
 

### 2018-11-07 Manuscript_draft/Manuscript_draft.tex
some editing

@@
             pdfauthor={},
-            pdftitle={How phylogenetic relatedness and floral traits are involved in heterospecifc pollen effect in an artificial co-flowering community},
+            pdftitle={Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits},
             colorlinks=true,
@@
 
-\title{How phylogenetic relatedness and floral traits are involved in
-heterospecifc pollen effect in an artificial co-flowering community}
+\title{Working title, The impact of heterospecific pollen on plant reproductive
+success is mediated by phylogenetic distance and floral reproductive
+traits}
 \author{
-Jose B. Lanuza
+Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
 true
@@
 \begin{center}
-\huge How phylogenetic relatedness and floral traits are involved in
-heterospecifc pollen effect in an artificial co-flowering community
+\huge Working title, The impact of heterospecific pollen on plant reproductive
+success is mediated by phylogenetic distance and floral reproductive
+traits
 \end{center}
@@
 \large
-Jose B. Lanuza \textsuperscript{1,2} 
+Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
 true
@@
 \section{INTRODUCTION}\label{introduction}
+
+\href{Romina}{Cut and paste some paragraphs from your literature review/
+proposal}
 

### 2018-11-07 Manuscript_draft/Manuscript_draft.Rmd
some editing. Preparing results for Romina

@@
 output:
+  word_document: null
   pdf_document:
@@
     template: manuscript.latex
-  word_document: null
   html_document: null

### 2018-11-07 Manuscript_draft/Manuscript_draft.Rmd
preparing files :)

@@
   email: barragansljose@gmail.com
-  name: null
+  name: Jose
 affiliation:
@@
 
-*Keywords*: heterospecific pollen, plant reproduction, fitness, competition
+*Keywords*: heterospecific pollen, plant reproduction, fitness, pollen competition
 
@@
 # METHODS
+
+[comment starts]()
+Glasshouse trial
+•	Species selected and why – how you made them co-flower
+•	Give details of sources and planting seeds, growth medium in pots, temperature and light details
+•	Hand crosses and how you did them, how you measured seed set over time.
+•	Analyses of data – standardization, means, matrices etc.
+
+•	Analyses and technical difficulties: We calculated effect size by subtracting the mean of the cross pollinated seed set by the mean effect of the HP pollen (explain exactly what figures you used to calculate this) – check with liam about potentially using missing values analyses for the species we don’t have?
+
+Check that the method is working well to prove that your crosses were close to 50% results in SI i.e not all mixes were 50/50% and we have now counted all the pollen to make this a quantitative variable.
+We also need to factor in the point that we have different total abundances of pollen across our treatments, irrespective of ratios.
+To what extent are differences in the ratios of pollen applied by hand across different plant families influenced by plant traits such as pollen size, morphology and stigma surface type?
+
+Results – may need to include amount of pollen in models as random factor- prefill matrix with missing value analyse for the species you don’t have.  
+Question 1: how do different pollination treatments (100% HP, 50% HP, self and cross ) impact HP pollen across different plant families?
+Even with 100% HP one (or more species?) still produced seed set.
+
+Result Effect size of Seed set ~ phylogenetic distance relationship
+We found that the variation ?/ mean effect size of seed set is positively related to phylogenetic distance.
+This means the more unrelated the species are, the greater the negative impact of heterospecific pollen (give stats  effect size i.e.
+Procrustes, X = 0.35; P = 0.03)
+
+Question 2 : what are the main traits impacting HP impacts? (compatibility system, pollen size, stigma surface, wet/dry stigma, length of style etc.
+
+Effect size of seed set ~ floral traits/ reproductive plant traits
+We found that the three best terms to explain the variation in seed set is pollen/ovule ratio, stigma width and style length (Stats effect size i.e. X = 0.39, P = 0.02).  
+Need to provide correlation matrix for all traits just for 10 species
+Show both ways to present this.
+Which particular traits do you find significant effects for?
+Show this and give stats.
+Present plot for each trait and effect size
+
+[comment finishes]()
 
@@
 
-Discuss.
+Discussion
+
+1.	 What are the implications of the findings?
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
ideas

@@
 
-*Keywords*: heterospecific pollen, plant reproduction, fitness, pollen competition
+*Keywords*: heterospecific pollen, plant reproduction, fitness, interspecific competition, phylogenetic distance.
 
@@
 # INTRODUCTION
-[Cut and paste some paragraphs from your literature review/ proposal](Romina)
 
@@
 
-In natural systems plant species normally coexist and share their floral visitors with other species (Bascompte et al., 2003).
-This pollinator sharing from the plant perpective can be negative due to competition (refs) or positive due to facilitation (refs).
-Moreover, once the pollinator has landed on the stigma some other issues for the species fitness may arise, the arrival of foreign pollen and conspecific pollen loss (Morales & Traveset 2008)
+In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003.
+This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014.
+Once, the floral visitor has arrived to the flower, pollen deposition can take place and with an increasing number of visits the higher the chances of ovule fertilization (Refs).
+
+I like what I have so far BUT we can make the story more complete
+
+Moreover, once the pollinator has landed on the stigma some other issues for the plant species may arise, the arrival of foreign pollen and conspecific pollen loss @morales2008.
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
ideas

@@
 Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
-true
+Jose
 }
@@
 Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
-true
+Jose \textsuperscript{*} \textsuperscript{3} 
 \end{center}
@@
 \emph{Keywords}: heterospecific pollen, plant reproduction, fitness,
-competition
+interspecific competition, phylogenetic distance.
 
@@
 
-\href{Romina}{Cut and paste some paragraphs from your literature review/
-proposal}
-
 \textbf{Paragraph 1}
@@
 sharing from the plant perpective can be negative due to competition
-(refs) or positive due to facilitation (refs). Moreover, once the
-pollinator has landed on the stigma some other issues for the species
-fitness may arise, the arrival of foreign pollen and conspecific pollen
-loss (Morales \& Traveset 2008)
+(refs) or positive due to facilitation Carvalheiro et al. (2014).
+Moreover, once the pollinator has landed on the stigma some other issues
+for the species fitness may arise, the arrival of foreign pollen and
+conspecific pollen loss (Morales \& Traveset 2008)
 
@@
 \section{METHODS}\label{methods}
+
+\href{}{comment starts} Glasshouse trial • Species selected and why --
+how you made them co-flower • Give details of sources and planting
+seeds, growth medium in pots, temperature and light details • Hand
+crosses and how you did them, how you measured seed set over time. •
+Analyses of data -- standardization, means, matrices etc.
+
+• Analyses and technical difficulties: We calculated effect size by
+subtracting the mean of the cross pollinated seed set by the mean effect
+of the HP pollen (explain exactly what figures you used to calculate
+this) -- check with liam about potentially using missing values analyses
+for the species we don't have?
+
+Check that the method is working well to prove that your crosses were
+close to 50\% results in SI i.e not all mixes were 50/50\% and we have
+now counted all the pollen to make this a quantitative variable. We also
+need to factor in the point that we have different total abundances of
+pollen across our treatments, irrespective of ratios. To what extent are
+differences in the ratios of pollen applied by hand across different
+plant families influenced by plant traits such as pollen size,
+morphology and stigma surface type?
+
+Results -- may need to include amount of pollen in models as random
+factor- prefill matrix with missing value analyse for the species you
+don't have.\\
+Question 1: how do different pollination treatments (100\% HP, 50\% HP,
+self and cross ) impact HP pollen across different plant families? Even
+with 100\% HP one (or more species?) still produced seed set.
+
+Result Effect size of Seed set \textasciitilde{} phylogenetic distance
+relationship We found that the variation ?/ mean effect size of seed set
+is positively related to phylogenetic distance. This means the more
+unrelated the species are, the greater the negative impact of
+heterospecific pollen (give stats effect size i.e.~Procrustes, X = 0.35;
+P = 0.03)
+
+Question 2 : what are the main traits impacting HP impacts?
+(compatibility system, pollen size, stigma surface, wet/dry stigma,
+length of style etc.
+
+Effect size of seed set \textasciitilde{} floral traits/ reproductive
+plant traits We found that the three best terms to explain the variation
+in seed set is pollen/ovule ratio, stigma width and style length (Stats
+effect size i.e.~X = 0.39, P = 0.02).\\
+Need to provide correlation matrix for all traits just for 10 species
+Show both ways to present this. Which particular traits do you find
+significant effects for? Show this and give stats. Present plot for each
+trait and effect size
+
+\href{}{comment finishes}
 
@@
 
-Discuss.
+Discussion
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  What are the implications of the findings?
+\end{enumerate}
 
@@
 67:1--48.
+
+\hypertarget{ref-carvalheiro2014}{}
+Carvalheiro, L. G., J. C. Biesmeijer, G. Benadi, J. Fründ, M. Stang, I.
+Bartomeus, C. N. Kaiser-Bunbury, M. Baude, S. I. Gomes, V. Merckx, and
+others. 2014. The potential for indirect effects between co-flowering
+plants via shared pollinators depends on resource abundance,
+accessibility and relatedness. Ecology letters 17:1389--1399.
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
p1

@@
 author:
-- affilnum: '1,2'
-  name: Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
-- affilnum: 3
+- affilnum: '1,2,3'
+  name: Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
   email: barragansljose@gmail.com
-  name: Jose
 affiliation:
@@
 output:
-  word_document: null
   pdf_document:
@@
     template: manuscript.latex
+  word_document: null
   html_document: null
@@
 This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014.
-Once, the floral visitor has arrived to the flower, pollen deposition can take place and with an increasing number of visits the higher the chances of ovule fertilization (Refs).
-
-I like what I have so far BUT we can make the story more complete
-
-Moreover, once the pollinator has landed on the stigma some other issues for the plant species may arise, the arrival of foreign pollen and conspecific pollen loss @morales2008.
+Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and therefore ovule fertilization.
+An increasing number of visits generally correlates with higher chances of fertilization (Refs).
+However this is not always the case, among these flower visitors we find also nectar robbers and pollen thiefs (Refs) or pollen quality (example with ref?).
+Moreover, other less studies issues in the pollination process such as conspecific pollen loss or the arrival of foreign pollen can have detrimental effects for the species fitness @morales2008.
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
p1

@@
 \author{
-Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader
-Jose
+Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
 }
@@
 \large
-Jose B. Lanuza, Ignasi Bartomeus, Tya-Linn Ashman, Romina Rader \textsuperscript{1,2} 
-Jose \textsuperscript{*} \textsuperscript{3} 
+Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader \textsuperscript{*} \textsuperscript{1,2,3} 
 \end{center}
@@
 In natural systems plant species normally coexist and share their floral
-visitors with other species (Bascompte et al., 2003). This pollinator
-sharing from the plant perpective can be negative due to competition
-(refs) or positive due to facilitation Carvalheiro et al. (2014).
-Moreover, once the pollinator has landed on the stigma some other issues
-for the species fitness may arise, the arrival of foreign pollen and
-conspecific pollen loss (Morales \& Traveset 2008)
+visitors with other species Bascompte et al. (2003). This pollinator
+sharing from the plant perspective at the pre-pollination stage can be
+negative due to competition Pauw (2013) or positive due to facilitation
+Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
+flower, pollen deposition on the stigma can take place and therefore
+ovule fertilization. An increasing number of visits generally correlates
+with higher chances of fertilization (Refs). However this is not always
+the case, among these flower visitors we find also nectar robbers and
+pollen thiefs (Refs) or pollen quality (example with ref?). Moreover,
+other less studies issues in the pollination process such as conspecific
+pollen loss or the arrival of foreign pollen can have detrimental
+effects for the species fitness Morales and Traveset (2008).
 
@@
 
+\hypertarget{ref-bascompte2003}{}
+Bascompte, J., P. Jordano, C. J. Melián, and J. M. Olesen. 2003. The
+nested assembly of plant--animal mutualistic networks. Proceedings of
+the National Academy of Sciences 100:9383--9387.
+
 \hypertarget{ref-Bates_2015}{}
@@
 accessibility and relatedness. Ecology letters 17:1389--1399.
+
+\hypertarget{ref-morales2008}{}
+Morales, C. L., and A. Traveset. 2008. Interspecific pollen transfer:
+Magnitude, prevalence and consequences for plant fitness. Critical
+Reviews in Plant Sciences 27:221--238.
+
+\hypertarget{ref-pauw2013}{}
+Pauw, A. 2013. Can pollination niches facilitate plant coexistence?
+Trends in ecology \& evolution 28:30--37.
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
1st paragraph

@@
 An increasing number of visits generally correlates with higher chances of fertilization (Refs).
-However this is not always the case, among these flower visitors we find also nectar robbers and pollen thiefs (Refs) or pollen quality (example with ref?).
-Moreover, other less studies issues in the pollination process such as conspecific pollen loss or the arrival of foreign pollen can have detrimental effects for the species fitness @morales2008.
+However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs).
+Moreover, other less studies issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008.
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
1st paragraph

@@
 with higher chances of fertilization (Refs). However this is not always
-the case, among these flower visitors we find also nectar robbers and
-pollen thiefs (Refs) or pollen quality (example with ref?). Moreover,
-other less studies issues in the pollination process such as conspecific
-pollen loss or the arrival of foreign pollen can have detrimental
-effects for the species fitness Morales and Traveset (2008).
+the case, among these possible flower visitors we find also nectar
+robbers and pollen thiefs (Refs) and the quality of pollen that is
+deposited on the stigma is also highly relevant to the pollination
+succes (Refs). Moreover, other less studies issues in the pollination
+process are conspecific pollen loss and the arrival of foreign pollen
+which can have important detrimental effects for the species fitness
+Morales and Traveset (2008).
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.Rmd
last changes

@@
 This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014.
-Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and therefore ovule fertilization.
+Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and hence ovule fertilization.
 An increasing number of visits generally correlates with higher chances of fertilization (Refs).
 However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs).
-Moreover, other less studies issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008.
+Moreover, other less study
+issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 (More refs).
 
@@
 
-The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008).
+Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 (More refs).
+
 Invasive species are supposed to have greater negative effect than native ones @arceo2016.
@@
 **Paragraph 4**
+
+Sell well our work: We are the first empirical experiment testig the effect of heterospecific pollen with phylogenetic distance
 

### 2018-11-08 Manuscript_draft/Manuscript_draft.tex
last changes

@@
 Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
-flower, pollen deposition on the stigma can take place and therefore
-ovule fertilization. An increasing number of visits generally correlates
-with higher chances of fertilization (Refs). However this is not always
-the case, among these possible flower visitors we find also nectar
-robbers and pollen thiefs (Refs) and the quality of pollen that is
-deposited on the stigma is also highly relevant to the pollination
-succes (Refs). Moreover, other less studies issues in the pollination
-process are conspecific pollen loss and the arrival of foreign pollen
-which can have important detrimental effects for the species fitness
-Morales and Traveset (2008).
+flower, pollen deposition on the stigma can take place and hence ovule
+fertilization. An increasing number of visits generally correlates with
+higher chances of fertilization (Refs). However this is not always the
+case, among these possible flower visitors we find also nectar robbers
+and pollen thiefs (Refs) and the quality of pollen that is deposited on
+the stigma is also highly relevant to the pollination succes (Refs).
+Moreover, other less studies issues in the pollination process are
+conspecific pollen loss and the arrival of foreign pollen which can have
+important detrimental effects for the species fitness Morales and
+Traveset (2008) (More refs).
 
@@
 
-The effect of heterospecific pollen has been widely studied (Morales \&
-Traveset 2008). Invasive species are supposed to have greater negative
-effect than native ones Arceo-Gómez and Ashman (2016). Although when
-non-natives species don´t have greater negative effect we still don´t
-know why. For this reason, this ecological question is non a native non
-native one is a trait based issue that is still to be solved. Moreover,
-the quantity of pollen that integrates in the network can be quite
-variable ranging from low quatities Bartomeus et al. (2008) to
-intermediate (ref) to high (ref). Moreover, closely related species are
-supposed to reduce fitness in greater effect but the evidence is scarce
-and based on independent studies with different methodologies
-(Arceo-gomez \& Ashman 2016) or studies that just check it with a pair
-of species that are highly related with the aim to understand
-hybridization costs (refs). There is a need to deepen into how
-relatednes is involve in the costs of heterospecific pollen effect.
-Furthermore, following the conceptual trait framework of Ashman and
-Arceo-Gomez on heterospecific pollen there are good theoretical basis
-for trait effect. Notwithstanding, non empirical work has tested how
-really these traits are involved in heterospecific pollen effect.
+Recent important studies have advanced in the ecological importance of
+heterospecific pollen effect Morales and Traveset (2008) (More refs).
+
+Invasive species are supposed to have greater negative effect than
+native ones Arceo-Gómez and Ashman (2016). Although when non-natives
+species don´t have greater negative effect we still don´t know why. For
+this reason, this ecological question is non a native non native one is
+a trait based issue that is still to be solved. Moreover, the quantity
+of pollen that integrates in the network can be quite variable ranging
+from low quatities Bartomeus et al. (2008) to intermediate (ref) to high
+(ref). Moreover, closely related species are supposed to reduce fitness
+in greater effect but the evidence is scarce and based on independent
+studies with different methodologies (Arceo-gomez \& Ashman 2016) or
+studies that just check it with a pair of species that are highly
+related with the aim to understand hybridization costs (refs). There is
+a need to deepen into how relatednes is involve in the costs of
+heterospecific pollen effect. Furthermore, following the conceptual
+trait framework of Ashman and Arceo-Gomez on heterospecific pollen there
+are good theoretical basis for trait effect. Notwithstanding, non
+empirical work has tested how really these traits are involved in
+heterospecific pollen effect.
 
@@
 \textbf{Paragraph 4}
+
+Sell well our work: We are the first empirical experiment testig the
+effect of heterospecific pollen with phylogenetic distance
 

### 2018-11-13 Manuscript_draft/Results.Rmd
Preparing Rmd with table of results

---
title: "Results"
author: "Jose"
date: "13/11/18"
output: pdf_document
#bibliography: references.bib
---

```{r, echo=FALSE, message=FALSE}
library(vegan)
library(xtable)
library(kableExtra)
#load environment
load("myEnvironment_mantel.RData")
```

Now I compare the matrix of effect, which is the matrix of cross scaled seed set minus the matrix of mean scaled seed set with the treatments per species.

#Part 1 Relation between effect of Hp and evolutive distance

1) With the RBCL marker

Mantel effect~evolutive distance
```{r, echo=FALSE, message=FALSE}
mantel_rbcl <- mantel(matrix_scale_effect, evo_distance_rbcl)
mantel_rbcl_sqrt <- mantel(matrix_scale_effect, sqrt(evo_distance_rbcl))
pro_rbcl <- protest(matrix_scale_effect, evo_distance_rbcl)
pro_rbcl_sqrt <- protest(matrix_scale_effect, sqrt(evo_distance_rbcl))

r <- c(as.numeric(mantel_rbcl[3]), as.numeric(mantel_rbcl_sqrt[3]),
       as.numeric(pro_rbcl[6]),as.numeric(pro_rbcl_sqrt[6]))
p <- c(as.numeric(mantel_rbcl[4]),as.numeric(mantel_rbcl_sqrt[4]),
       as.numeric(pro_rbcl[13]),as.numeric(pro_rbcl_sqrt[13]))
Analysis <- c("Mantel", "Mantel", "Procustes", "Procustes")
Type <- c("normal evolutive distance","sqrt evolutive distance","normal evolutive distance", "sqrt evolutive distance")
table<- data.frame(r,p, Analysis, Type)
kable(table, format="markdown")
```

I wonder if the matrices are too small for procustes, is a general trend for all the analysis to have a non significant p value and correlation around these numbers.

2) With the ITS marker
```{r, echo=FALSE, message=FALSE}
mantel_its <- mantel(matrix_scale_effect, evo_distance_its)
mantel_its_sqrt <- mantel(matrix_scale_effect, sqrt(evo_distance_its))
pro_its <- protest(matrix_scale_effect, evo_distance_its)
pro_its_sqrt <- protest(matrix_scale_effect, sqrt(evo_distance_its))

r <- c(as.numeric(mantel_its[3]), as.numeric(mantel_its_sqrt[3]),
       as.numeric(pro_its[6]),as.numeric(pro_its_sqrt[6]))
p <- c(as.numeric(mantel_its[4]),as.numeric(mantel_its_sqrt[4]),
       as.numeric(pro_its[13]),as.numeric(pro_its_sqrt[13]))
Analysis <- c("Mantel", "Mantel", "Procustes", "Procustes")
Type <- c("normal evolutive distance","sqrt evolutive distance","normal evolutive distance", "sqrt evolutive distance")
table<- data.frame(r,p, Analysis, Type)
kable(table, format="markdown")
```

#Part 2 Relation between effect of Hp and traits

### 2018-11-13 Scripts/Analysis_mantel_test.R

@@ -455,32 +455,9 @@ protest(matrix_scale_effect, style_length_dist)
 bioenv(matrix_scale_effect~traits_all$style_length, method="pearson", trace=T)
 #correlation=-0.1757
 
+#Save environment to load object in Markdown
+#save.image(file='Manuscript_draft/myEnvironment_mantel.RData')
 
 
 
-
-
-
-
-
-min(matrix_scale_effect)
-matrix_scale_effect=matrix_scale_effect+abs(min(matrix_scale_effect))
-bioenv(matrix_scale_effect~traits_all$stigma_area, trace=T)
-mantel(matrix_scale_effect, evo_distance_its_square_root)
-a <- melt(matrix_scale_effect)
-b <- melt(evo_distance_its_square_root)
-m <- cbind(a,b)
-colnames(m) <- c("Species", "Non_focal", "effect", "spp", "distance")
-plot(effect~distance, data=m)
-model1 <- glm(effect~distance, data= m)
-summary(model1)
-plot(model1)
-library(visreg)
-visreg(model1)
-stigma_area_dist = as.matrix(stigma_area_dist)
-c <- melt(stigma_area_dist)
-n <- cbind(a,c)
-colnames(n) <- c("Species", "Non_focal", "effect", "spp","sp", "distance")
-model1 <- glm(effect~distance, data= n)
-visreg(model1)
 

### 2018-11-13 Manuscript_draft/Results.Rmd
Rmd with results

@@
 output: pdf_document
-#bibliography: references.bib
+bibliography: references.bib
 ---
@@
 library(kableExtra)
+library(reshape2)
+library(ape)
+library(phytools)
 #load environment
@@
 
-Now I compare the matrix of effect, which is the matrix of cross scaled seed set minus the matrix of mean scaled seed set with the treatments per species.
+To check for the effect of heterospecific pollen we assume that the optimal seed production is with the hand cross pollination (pollen from a different individual of the same species) and then we substract to the mean value of cross pollination the mean value of heterospecific pollen effect across treatments.
+Previously we have scaled the seed for each species with mean 0 and standard deviation of 1.
+When a species had higher values of seed production with treatments than the cross we set as maximum value for the treatments the same as the hand cross pollination.
 
@@
 
+I try Mantel test and procustes test, although both are similar procustes performs better in wider range of circumstances @peres2001.
+Moreover, I consider the square root of the evolutive distances which improves the statistical power in comparison to the normal distances @letten2015.
+
 1) With the RBCL marker
 
-Mantel effect~evolutive distance
+Heterospecific pollen effect~evolutive distance
 ```{r, echo=FALSE, message=FALSE}
@@
 mantel_rbcl_sqrt <- mantel(matrix_scale_effect, sqrt(evo_distance_rbcl))
-pro_rbcl <- protest(matrix_scale_effect, evo_distance_rbcl)
+pro_rbcl <- protest(matrix_scale_effect, evo_distance_rbcl, symmetric=F)
 pro_rbcl_sqrt <- protest(matrix_scale_effect, sqrt(evo_distance_rbcl))
@@
 2) With the ITS marker
+
+Heterospecific pollen effect~evolutive distance
 ```{r, echo=FALSE, message=FALSE}
@@
 
+I plot now the pairwise distances on the x axis and the effect of heterospecific pollen on the y axis, although is not very intuitive the greater the effect the closer to 0 because the mean hand cross pollination and the mean heterospecific pollen effect were more similar.
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, fig.cap="Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers)."}
+its_distance <- melt(evo_distance_its)
+scaled_effect <- melt(matrix_scale_effect)
+scaled_effect$Species=as.character(scaled_effect$Species)
+scaled_effect$col_focal[scaled_effect$Species==c("BROL")] <- "red"
+scaled_effect$col_focal[scaled_effect$Species==c("BRRA")] <- "red"
+scaled_effect$col_focal[scaled_effect$Species==c("SIAL")] <- "red"
+scaled_effect$col_focal[scaled_effect$Species==c("ERSA")] <- "red"
+scaled_effect$col_focal[scaled_effect$Species==c("SOME")] <- "blue"
+scaled_effect$col_focal[scaled_effect$Species==c("SOLY")] <- "blue"
+scaled_effect$col_focal[scaled_effect$Species==c("PEIN")] <- "blue"
+scaled_effect$col_focal[scaled_effect$Species==c("CAAN")] <- "blue"
+scaled_effect$col_focal[scaled_effect$Species==c("IPAQ")] <- "green"
+scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "green"
+plot(its_distance$value, scaled_effect$value, main="Scatterplot ", 
+     xlab="dist", ylab="effect", pch=19, col=scaled_effect$col_focal)
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE}
+pollen_tree=read.tree("pollen_tree.nwk")
+plot(pollen_tree)
+add.scale.bar(x=0, y=1)
+```
+
+\newpage
 #Part 2 Relation between effect of Hp and traits
+
+```{r}
+
+```
+
+#References

### 2018-11-13 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 
-Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 (More refs).
+Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016.
+A general overview of it is that reduces species fitness (REFS).
+Other general facts...
+Quantity of foreign pollen that arrives...
+
+Mention invasive species in this paragraph
+
+Few studies have tried to understand how relatedness is involved in the hp effect but generally
+
+Until our knowledge ....
+
+Rescue from here the useful things:
 
@@
 Explain traits. Put examples
+
+what is closely related? same genus? Just that right, the rest is far related?
+
+I would like to add that the experiments focus on two proxies of effect prezygotic and postzygotic.
+Why focus on postzygotic?
+Is the final stage where we can see the effect.
+Further studies should also study germination rates.
 

### 2018-11-13 Manuscript_draft/Manuscript_draft.tex
changes

@@
 the stigma is also highly relevant to the pollination succes (Refs).
-Moreover, other less studies issues in the pollination process are
+Moreover, other less study issues in the pollination process are
 conspecific pollen loss and the arrival of foreign pollen which can have
@@
 Recent important studies have advanced in the ecological importance of
-heterospecific pollen effect Morales and Traveset (2008) (More refs).
+heterospecific pollen effect Morales and Traveset (2008)
+({\textbf{???}}) Arceo-Gómez and Ashman (2016). A general overview of it
+is that reduces species fitness (REFS). Other general facts\ldots{}
+Quantity of foreign pollen that arrives\ldots{}
+
+Mention invasive species in this paragraph
+
+Few studies have tried to understand how relatedness is involved in the
+hp effect but generally
+
+Until our knowledge \ldots{}.
+
+Rescue from here the useful things:
 
@@
 Explain traits. Put examples
+
+what is closely related? same genus? Just that right, the rest is far
+related?
+
+I would like to add that the experiments focus on two proxies of effect
+prezygotic and postzygotic. Why focus on postzygotic? Is the final stage
+where we can see the effect. Further studies should also study
+germination rates.
 

### 2018-11-14 Manuscript_draft/Manuscript_draft.Rmd
Changes

@@
 However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs).
-Moreover, other less study
-issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 (More refs).
+Moreover, other less study issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 (More refs).
 
@@
 Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016.
-A general overview of it is that reduces species fitness (REFS).
+A general overview of it can reduce species fitness (REFS) but not in al the cases (Refs).
 Other general facts...
@@
 Where we test the folowing hypothesis: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on the relatedness of the species, 3) Does heterospecific pollen effect depend on any floral trait?
+
+Maybe another possible hypothesis to test is the reciprocity of the effect of heterospecifc pollen????
+
+Use the sterile species as a proof of the mechanical interference. Was a mistake but seems cool proof!!!
 

### 2018-11-14 Manuscript_draft/Manuscript_draft.tex
Changes

@@
 ({\textbf{???}}) Arceo-Gómez and Ashman (2016). A general overview of it
-is that reduces species fitness (REFS). Other general facts\ldots{}
-Quantity of foreign pollen that arrives\ldots{}
+can reduce species fitness (REFS) but not in al the cases (Refs). Other
+general facts\ldots{} Quantity of foreign pollen that arrives\ldots{}
 
@@
 effect depend on any floral trait?
+
+Maybe another possible hypothesis to test is the reciprocity of the
+effect of heterospecifc pollen????
+
+Use the sterile species as a proof of the mechanical interference. Was a
+mistake but seems cool proof!!!
 

### 2018-11-14 Manuscript_draft/Results.Rmd
Changes

@@
 
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 library(vegan)

### 2018-11-14 Manuscript_draft/Results.Rmd
plot with figures on it

--- 2018-11-13 Manuscript_draft/Results.Rmd
@@
 library(phytools)
+library(plotrix)
 #load environment
@@
 scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "green"
-plot(its_distance$value, scaled_effect$value, main="Scatterplot ", 
-     xlab="dist", ylab="effect", pch=19, col=scaled_effect$col_focal)
+plot(its_distance$value, scaled_effect$value, main="Hp effect & evolutive distance", 
+     xlab="Pairwise evolutive distances", ylab="Hp effect (Scaled seed set)", pch=19, col=scaled_effect$col_focal)
+draw.circle(0.265,0.22,radius=0.045,nv=100,border="red",col=NA,lty=1,density=NULL,angle=45,lwd=1)
+draw.circle(0.20,1.8,radius=0.09,nv=100,border="blue",col=NA,lty=1,density=NULL,angle=45,lwd=1)
+
 ```

### 2018-11-14 Scripts/Analysis_mantel_test.R

@@ -14,6 +14,7 @@ library(permute)
 library(lattice)
 library(distances)
 library(pdist)
+library(plotrix)
 #Load seed set data for 10 species
 soly  <- read.csv("Data/species_seed_set/soly_seed_set.csv", sep=";", stringsAsFactors = F)
 some  <- read.csv("Data/species_seed_set/some_seed_set.csv", sep=";", stringsAsFactors = F)
@@ -501,6 +502,11 @@ scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("IPPU")] <- "green"
 
 plot(its_distance$value, scaled_effect$value, main="Scatterplot ", 
      xlab="dist", ylab="effect", pch=19, col=scaled_effect$col_focal)
+
+#locator(1)
+draw.circle(0.265,0.22,radius=0.045,nv=100,border="red",col=NA,lty=1,density=NULL,angle=45,lwd=1)
+
+draw.circle(0.20,1.8,radius=0.09,nv=100,border="blue",col=NA,lty=1,density=NULL,angle=45,lwd=1)
 
 
 plot(its_distance$value, scaled_effect$value, main="Scatterplot ", 

### 2018-11-14 Manuscript_draft/Results.Rmd
Nice advances today in the markdown file
Now sport!

--- 2018-11-13 Manuscript_draft/Results.Rmd
@@
 library(phytools)
+library(plotrix)
+library(dplyr)
 #load environment
@@
 
-To check for the effect of heterospecific pollen we assume that the optimal seed production is with the hand cross pollination (pollen from a different individual of the same species) and then we substract to the mean value of cross pollination the mean value of heterospecific pollen effect across treatments.
-Previously we have scaled the seed for each species with mean 0 and standard deviation of 1.
-When a species had higher values of seed production with treatments than the cross we set as maximum value for the treatments the same as the hand cross pollination.
+To check for the effect of heterospecific pollen we assume that the optimal seed production is the hand cross pollination (pollinated with pollen from a different individual of the same species).
+Then, we substract to the mean value of hand cross pollination the mean value of heterospecific pollen effect across treatments (50% conspecific-50%heterospecific pollen).
+Previously we have scaled the seed set for each species with mean 0 and standard deviation of 1 to be able to compare among species.
+When a species had higher values of seed production with treatments than the cross, we set as maximum value for the treatments the same as the hand cross pollination.
+However, we should take into account that analysis in general improve if we keep these negative values.
+If we put these words into a formula being i the different focal species and j the different donors:
+
+Eq.1  $$HpEffect_{i}=Mean(CrosPollinationSeeds)_{i}-Mean(TreatmentSeeds_{ij})$$
 
@@
 
-I try Mantel test and procustes test, although both are similar procustes performs better in wider range of circumstances @peres2001.
+I try Mantel test and procustes test, although both are similar procustes performs better in a wider range of circumstances @peres2001.
 Moreover, I consider the square root of the evolutive distances which improves the statistical power in comparison to the normal distances @letten2015.
@@
 
-I plot now the pairwise distances on the x axis and the effect of heterospecific pollen on the y axis, although is not very intuitive the greater the effect the closer to 0 because the mean hand cross pollination and the mean heterospecific pollen effect were more similar.
+I plot now the pairwise distances on the x axis and the effect of heterospecific pollen on the y axis. The greater the effect of heterospecific pollen the greater the number on the y axis.
 
@@
 
-```{r, echo=FALSE, message=FALSE, fig.cap="Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers)."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 1.
+Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers).
+In other words, each point is defined by the phylogenetic distnace between a pair of species (x axis) and the effect of heterospecifc pollen which considers also an interaction between the same pair of species (donor and recipient)(y axis)"}
 its_distance <- melt(evo_distance_its)
@@
 scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "green"
-plot(its_distance$value, scaled_effect$value, main="Scatterplot ", 
-     xlab="dist", ylab="effect", pch=19, col=scaled_effect$col_focal)
+plot(its_distance$value, scaled_effect$value, main="Hp effect & phylogenetic distance", 
+     xlab="Pairwise phylogenetic distances", ylab="Hp effect (Scaled seed set)", pch=19, col=scaled_effect$col_focal)
+draw.circle(0.265,0.22,radius=0.045,nv=100,border="red",col=NA,lty=1,density=NULL,angle=45,lwd=1)
+draw.circle(0.245,1.8,radius=0.07,nv=100,border="blue",col=NA,lty=1,density=NULL,angle=45,lwd=1)
+focal <- cbind(scaled_effect,its_distance)
+focal <- data.frame(focal, stringsAsFactors = F)
+#str(focal)
+focal_bra <- filter(focal, Species==c("BROL","BRRA","ERSA","SIAL"))
+focal_sol <- filter(focal, Species==c("SOME","SOLY","PEIN","CAAN"))
+focal_con <- filter(focal, Species==c("IPAQ","IPPU"))
+model_bra <- lm(focal_bra$value ~ focal_bra$value.1)
+#summary(model_brra)
+abline(model_bra, col="red")
+model_sol <- lm(focal_sol$value ~ focal_sol$value.1)
+#summary(model_sol)
+abline(model_sol, col="blue")
+model_con <- lm(focal_con$value ~ focal_con$value.1)
+#summary(model_con)
+abline(model_con, col="black")
 ```
+
+Overall, it seems that with phylogenetic distance, heterospecific pollen effect increases for the three families.
+From Mantel analysis we can conclude that we have a significant correlation between phylogenetic distance and heterospecific pollen effect with r values between 0.25 and 0.3.
+However, for procustes test we were not able to find a significant correlation between these two despite the procustes correlation gave higher values.
+In Figure 1 we can also see these general pattern of a higher effect with phylogenetic distance with the different regressions lines per family.
+I have done simple linear models, probably I should consider other alternatives that fit better the cloud of points.
+In Figure 1 the two coulored circles are there for a reason, once we consider just the crosses between the "far related species" we see a general pattern for solanaceae with almost all the values above 0.5.
+Solanaceae curiously belongs to the group with gametophytic incompatibility which is predicted to suffer more from heterospecific pollen.
+Moreover, for Brassicaceae (red points) again for the far related crosses we find kind of two groups with high effect and no effect.
+The no effect correspond to the species without incompatibility (over 50% of selfing) and the high effect to the species with strong incompatibility (0% of selfing), again this confirms theory.
 
@@
 
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 pollen_tree=read.tree("pollen_tree.nwk")

### 2018-11-14 Scripts/Analysis_mantel_test.R

@@ -15,6 +15,8 @@ library(lattice)
 library(distances)
 library(pdist)
 library(plotrix)
+library(dplyr)
+
 #Load seed set data for 10 species
 soly  <- read.csv("Data/species_seed_set/soly_seed_set.csv", sep=";", stringsAsFactors = F)
 some  <- read.csv("Data/species_seed_set/some_seed_set.csv", sep=";", stringsAsFactors = F)
@@ -194,8 +196,8 @@ evo_distance_rbcl <- evo_distance_rbcl[order(rownames(evo_distance_rbcl)), order
 #Changing from characters to numerical
 evo_distance_rbcl <- mapply(evo_distance_rbcl, FUN=as.numeric)
 evo_distance_rbcl <- matrix(data=evo_distance_rbcl, ncol=10, nrow=10)
-rownames(evo_distance_rbcl) <- c("SIAL", "ERSA", "BROL", "BRRA", "IPPU", "IPAQ", "PEIN", "CAAN", "SOLY", "SOME")
-colnames(evo_distance_rbcl) <- c("SIAL", "ERSA", "BROL", "BRRA", "IPPU", "IPAQ", "PEIN", "CAAN", "SOLY", "SOME")
+rownames(evo_distance_rbcl) <- rownames(matrix_scale_effect)
+colnames(evo_distance_rbcl) <- rownames(matrix_scale_effect)
 evo_distance_rbcl <- evo_distance_rbcl[order(rownames(evo_distance_rbcl)), order(colnames(evo_distance_rbcl))] 
 
 
@@ -461,6 +463,15 @@ bioenv(matrix_scale_effect~traits_all$style_length, method="pearson", trace=T)
 #Save environment to load object in Markdown
 #save.image(file='Manuscript_draft/myEnvironment_mantel.RData')
 
+
+
+#
+##
+#### Prepare data 
+##
+#
+
+
 its_distance <- melt(evo_distance_its)
 scaled_effect <- melt(matrix_scale_effect)
 scaled_effect$Species=as.character(scaled_effect$Species)
@@ -499,6 +510,7 @@ scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("CAAN")] <- "green"
 scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("IPAQ")] <- "green"
 scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("IPPU")] <- "green"
 
+par(xpd=FALSE)
 
[…]

### 2018-11-15 Manuscript_draft/Manuscript_draft.Rmd
little by little

@@
 
+Traditionally heterospecific pollen effect has focused its attention on different pollen donors as a main driver of different effect.
+However in this article we want to emphasize that this is true for the cases that the species are higly close related where pollen recognition can take place (eg hybridization) but not when this pollen is from less closely related species which the main driver of effect is determined by the reproductive biology of the female part of the plant(compatibility system, stigma type, stigma area and number of ovules).
+
 **Paragraph 4**

### 2018-11-15 Manuscript_draft/Results.Rmd
little by little

@@
 
-Eq.1  $$HpEffect_{i}=Mean(CrosPollinationSeeds)_{i}-Mean(TreatmentSeeds_{ij})$$
+Eq.1  $$HpEffect_{i}=Mean(CrosPollinationSeeds_{i})-Mean(TreatmentSeeds_{ij})$$
+
+The number of possible combinations with 10 species (multiplied by two because is in both directions the treatments A to B and B to A):
+
+$$\frac{10!}{2!*(8!)}*2=90 $$
 
@@
 
-I plot now the pairwise distances on the x axis and the effect of heterospecific pollen on the y axis. The greater the effect of heterospecific pollen the greater the number on the y axis.
+Overall, it seems that with phylogenetic distance, heterospecific pollen effect increases for the three families.
+From Mantel analysis we can conclude that we have a significant correlation between phylogenetic distance and heterospecific pollen effect with r values between 0.25 and 0.3.
+However, for procustes test we were not able to find a significant correlation between these two despite procustes correlation gave higher values.
+This positive correlation should be further explored.
+Maybe a scatterplot of the phylogenetic distance and the heterospecific pollen effect could help to understand this correlation.
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 
+plot(focal$hp_effect ~ focal$its_distance, main="", xlim=c(0.05,0.6),
+     xlab="Evolutive distance", ylab="Hp effect", pch=19, col=focal$col_focal)
+
+legend(x=0.04,y=3.2,legend=c("Brassicaceae","Convolvulaceae","Solanaceae"),pch=(c(16,16,16)), 
+       col = c("red","black","blue"), bty="n",cex=0.6,pt.cex=0.6,xpd=TRUE)
+
+```
+Figure 1.
+Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers).
+In other words, each point is defined by the phylogenetic distance between a pair of species (x axis) and the effect of heterospecifc pollen which considers also an interaction between the same pair of species (donor and recipient)(y axis)
 \newpage
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 1.
-Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers).
-In other words, each point is defined by the phylogenetic distnace between a pair of species (x axis) and the effect of heterospecifc pollen which considers also an interaction between the same pair of species (donor and recipient)(y axis)"}
-its_distance <- melt(evo_distance_its)
-scaled_effect <- melt(matrix_scale_effect)
-scaled_effect$Species=as.character(scaled_effect$Species)
-scaled_effect$col_focal[scaled_effect$Species==c("BROL")] <- "red"
-scaled_effect$col_focal[scaled_effect$Species==c("BRRA")] <- "red"
-scaled_effect$col_focal[scaled_effect$Species==c("SIAL")] <- "red"
-scaled_effect$col_focal[scaled_effect$Species==c("ERSA")] <- "red"
-scaled_effect$col_focal[scaled_effect$Species==c("SOME")] <- "blue"
-scaled_effect$col_focal[scaled_effect$Species==c("SOLY")] <- "blue"
-scaled_effect$col_focal[scaled_effect$Species==c("PEIN")] <- "blue"
-scaled_effect$col_focal[scaled_effect$Species==c("CAAN")] <- "blue"
-scaled_effect$col_focal[scaled_effect$Species==c("IPAQ")] <- "green"
-scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "green"
-plot(its_distance$value, scaled_effect$value, main="Hp effect & phylogenetic distance", 
-     xlab="Pairwise phylogenetic distances", ylab="Hp effect (Scaled seed set)", pch=19, col=scaled_effect$col_focal)
-draw.circle(0.265,0.22,radius=0.045,nv=100,border="red",col=NA,lty=1,density=NULL,angle=45,lwd=1)
-draw.circle(0.245,1.8,radius=0.07,nv=100,border="blue",col=NA,lty=1,density=NULL,angle=45,lwd=1)
-focal <- cbind(scaled_effect,its_distance)
-focal <- data.frame(focal, stringsAsFactors = F)
-#str(focal)
-focal_bra <- filter(focal, Species==c("BROL","BRRA","ERSA","SIAL"))
-focal_sol <- filter(focal, Species==c("SOME","SOLY","PEIN","CAAN"))
-focal_con <- filter(focal, Species==c("IPAQ","IPPU"))
+Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families. Here I show how they wit the colud of points per family *lm(HpEffect~its_distance)*.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+
+plot(focal$hp_effect ~ focal$its_distance, main="", xlim=c(0.05,0.6),
+     xlab="Evolutive distance", ylab="Hp effect", pch=19, col=focal$col_focal)
+
+legend(x=0.04,y=3.2,legend=c("Brassicaceae","Convolvulaceae","Solanaceae"),pch=(c(16,16,16)), 
+       col = c("red","black","blue"), bty="n",cex=0.6,pt.cex=0.6,xpd=TRUE)
+
 model_bra <- lm(focal_bra$value ~ focal_bra$value.1)
@@
 abline(model_con, col="black")
+
 ```
 
-Overall, it seems that with phylogenetic distance, heterospecific pollen effect increases for the three families.
-From Mantel analysis we can conclude that we have a significant correlation between phylogenetic distance and heterospecific pollen effect with r values between 0.25 and 0.3.
-However, for procustes test we were not able to find a significant correlation between these two despite the procustes correlation gave higher values.
 In Figure 1 we can also see these general pattern of a higher effect with phylogenetic distance with the different regressions lines per family.
@@
 Moreover, for Brassicaceae (red points) again for the far related crosses we find kind of two groups with high effect and no effect.
-The no effect correspond to the species without incompatibility (over 50% of selfing) and the high effect to the species with strong incompatibility (0% of selfing), again this confirms theory.
+The no effect correspond to the species without incompatibility (over 50% of selfing) and the high effect to the species with strong incompatibility (0% of selfing), in order to show this in a better way I'm going just to plot these points of interest with their corresponding labels.
 

### 2018-11-15 Scripts/Analysis_mantel_test.R

@@ -467,13 +467,15 @@ bioenv(matrix_scale_effect~traits_all$style_length, method="pearson", trace=T)
 
 #
 ##
-#### Prepare data 
+#### PART 3 visualising this differences
 ##
 #
 
-
-its_distance <- melt(evo_distance_its)
+#Firs I melt the matyrics into long format
+its_distance <- melt(evo_distance_its_square_root, id.vars = as.character(evo_distance_its_square_root[,0]))
 scaled_effect <- melt(matrix_scale_effect)
+
+#I assing a new column with colours to differentiate the points
 scaled_effect$Species=as.character(scaled_effect$Species)
 scaled_effect$col_focal[scaled_effect$Species==c("BROL")] <- "red"
 scaled_effect$col_focal[scaled_effect$Species==c("BRRA")] <- "red"
@@ -485,7 +487,7 @@ scaled_effect$col_focal[scaled_effect$Species==c("PEIN")] <- "blue"
 scaled_effect$col_focal[scaled_effect$Species==c("CAAN")] <- "blue"
 scaled_effect$col_focal[scaled_effect$Species==c("IPAQ")] <- "black"
 scaled_effect$col_focal[scaled_effect$Species==c("IPPU")] <- "black"
-
+#Other column in case I want to differentiate by the donor
 scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("BROL")] <- "red"
 scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("BRRA")] <- "red"
 scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("SIAL")] <- "red"
@@ -498,39 +500,70 @@ scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("IPAQ")] <- "blue"
 scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("IPPU")] <- "blue"
 
 
-
-scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("BROL")] <- "blue"
-scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("BRRA")] <- "blue"
-scaled_effect$col_non_focal[scaled_effect$Non_focal ==c("SIAL")] <- "blue"
[…]

### 2018-11-16 Scripts/Analysis_mantel_test.R
.

@@ -617,3 +617,5 @@ all$col_focal[all$Species==c("IPPU")] <- "black"
 
 plot(all$value ~ all$value.1, main="", xlim=c(0.05,0.6),
      xlab="Evolutive distance", ylab="Hp effect", pch=19, col=all$col_focal)
+
+

### 2018-11-19 Manuscript_draft/Results.Rmd
.
markdown file

@@
 
-$$\frac{10!}{2!*(8!)}*2=90 $$
+$$(\frac{10}{2})=\frac{10!}{2!*(8!)}*2=90 $$
 
@@
 
-Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families. Here I show how they wit the colud of points per family *lm(HpEffect~its_distance)*.
+Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families.
+Here I show how they fit the colud of points per family *lm(HpEffect~its_distance)*.
+Anyway, don't think this is very informative.
 
@@
 
-In Figure 1 we can also see these general pattern of a higher effect with phylogenetic distance with the different regressions lines per family.
-I have done simple linear models, probably I should consider other alternatives that fit better the cloud of points.
-In Figure 1 the two coulored circles are there for a reason, once we consider just the crosses between the "far related species" we see a general pattern for solanaceae with almost all the values above 0.5.
-Solanaceae curiously belongs to the group with gametophytic incompatibility which is predicted to suffer more from heterospecific pollen.
-Moreover, for Brassicaceae (red points) again for the far related crosses we find kind of two groups with high effect and no effect.
-The no effect correspond to the species without incompatibility (over 50% of selfing) and the high effect to the species with strong incompatibility (0% of selfing), in order to show this in a better way I'm going just to plot these points of interest with their corresponding labels.
+So far I think phylogenetic distance doesn't help to visualize heterospecific pollen effect. Grouping by traits or the type of donor seems to be much more informative.
 
@@
 
-```{r}
+Here I perform Mantel test and Procustes test between the traits and heterospecific pollen effect.
+For both Mantel and procustes we weren't able to find evidence of correlation between matrices.
+At the moment we are using all the traits without filtering the correlated traits.
+With Bioenv we can now what are the traits that gives a best fit of correlation between matrices.
+The best model is with pollen ovule ratio, stigma width and style width.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("bio_result.RData")
+m_all <- mantel(matrix_scale_effect, traits_all_scaled_dist)
+p_all <- protest(matrix_scale_effect, traits_all_scaled_dist)
+
+r <- c(as.numeric(m_all[3]),as.numeric(p_all[6]), as.numeric(bio_result$`models`[[3]]$est))
+p <- c(as.numeric(m_all[4]),as.numeric(p_all[13]), NA)
+Analysis <- c("Mantel", "Procustes", "Bioenv")
+table<- data.frame(r,p, Analysis)
+kable(table, format="markdown")
+
+```
+
+Now I perform the analysis with both Mantel and Procustes trait by trait.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+a_1 <- mantel(matrix_scale_effect, traits_stigma_dist)
+a_2 <- protest(matrix_scale_effect, traits_stigma_dist)
+b_1 <- mantel(matrix_scale_effect, traits_self_dist)
+b_2 <- protest(matrix_scale_effect, traits_self_dist)
+c_1 <- mantel(matrix_scale_effect, pollen_size_dist)
+c_2 <- protest(matrix_scale_effect, pollen_size_dist)
+d_1 <- mantel(matrix_scale_effect, pollen_dist)
+d_2 <- protest(matrix_scale_effect, pollen_dist)
+e_1 <- mantel(matrix_scale_effect, ovules_dist)
+e_2 <- protest(matrix_scale_effect, ovules_dist)
+f_1 <- mantel(matrix_scale_effect, p_o_ratio_dist)
+f_2 <- protest(matrix_scale_effect, p_o_ratio_dist)
+g_1 <- mantel(matrix_scale_effect, anthers_dist)
+g_2 <- protest(matrix_scale_effect, anthers_dist)
+h_1 <- mantel(matrix_scale_effect, stigma_area_dist)
+h_2 <- protest(matrix_scale_effect, stigma_area_dist)
+i_1 <- mantel(matrix_scale_effect, stigma_length_dist)
+i_2 <- protest(matrix_scale_effect, stigma_length_dist)
+j_1 <- mantel(matrix_scale_effect, stigma_surface_dist)
+j_2 <- protest(matrix_scale_effect, stigma_surface_dist)
+k_1 <- mantel(matrix_scale_effect, stigma_width_dist)
+k_2 <- protest(matrix_scale_effect, stigma_width_dist)
+l_1 <- mantel(matrix_scale_effect, style_length_dist)
+l_2 <- protest(matrix_scale_effect, style_length_dist)
+m_1 <- mantel(matrix_scale_effect, style_width_dist)
+m_2 <- protest(matrix_scale_effect, style_width_dist)
+n_1 <- mantel(matrix_scale_effect, ovary_length_dist)
+n_2 <- protest(matrix_scale_effect, ovary_length_dist)
+o_1 <- mantel(matrix_scale_effect, ovary_width_dist)
+o_2 <- protest(matrix_scale_effect, ovary_width_dist)
+
+r <- c(as.numeric(a_1[3]),as.numeric(a_2[6]),as.numeric(b_1[3]),as.numeric(b_2[6]),as.numeric(c_1[3]),
+       as.numeric(c_2[6]), as.numeric(d_1[3]), as.numeric(d_2[6]), as.numeric(e_1[3]), as.numeric(e_2[6]),
+       as.numeric(f_1[3]), as.numeric(f_2[6]), as.numeric(g_1[3]), as.numeric(g_2[6]), as.numeric(h_1[3]), as.numeric(h_2[6]), as.numeric(i_1[3]), as.numeric(i_2[6]), as.numeric(j_1[3]), as.numeric(j_2[6]), as.numeric(k_1[3]), as.numeric(k_2[6]), as.numeric(l_1[3]), as.numeric(l_2[6]), as.numeric(m_1[3]), as.numeric(m_2[6]),as.numeric(n_1[3]), as.numeric(n_2[6]), as.numeric(o_1[3]), as.numeric(o_2[6]))
+
+p <- c(as.numeric(a_1[4]),as.numeric(a_2[13]), as.numeric(b_1[4]),as.numeric(b_2[13]), as.numeric(c_1[4]),as.numeric(c_2[13]), as.numeric(d_1[4]),as.numeric(d_2[13]), as.numeric(e_1[4]),as.numeric(e_2[13]), as.numeric(f_1[4]),as.numeric(f_2[13]), as.numeric(g_1[4]),as.numeric(g_2[13]), as.numeric(h_1[4]),as.numeric(h_2[13]),  as.numeric(i_1[4]),as.numeric(i_2[13]),  as.numeric(j_1[4]),as.numeric(j_2[13]), as.numeric(k_1[4]),as.numeric(k_2[13]), as.numeric(l_1[4]),as.numeric(l_2[13]), as.numeric(m_1[4]),as.numeric(m_2[13]), as.numeric(n_1[4]),as.numeric(n_2[13]), as.numeric(o_1[4]),as.numeric(o_2[13]))
+
+Analysis <- c("**Mantel**", "Procustes","Mantel", "Procustes", "Mantel", "Procustes", "Mantel", "Procustes", "Mantel", "Procustes", "Mantel", "Procustes", "Mantel", "Procustes", "**Mantel**", "Procustes", "Mantel", "Procustes", "**Mantel**", "Procustes","Mantel", "Procustes", "Mantel", "Procustes", "Mantel", "Procustes",
+              "Mantel", "Procustes", "Mantel", "Procustes")
+Trait<- c("**Stigma_type**", "Stigma_type", "Selfing_rate", "Selfing_rate", "Pollen size", "Pollen size", "Pollen_anther","Pollen_anther", "Ovules", "Ovules", "Pollen_ovule_ratio", "Pollen_ovule_ratio", "Anthers",
+          "Anthers", "**Stigma_area**", "Stigma_area", "Stigma_length", "Stigma_length", "**Stigma_surface**", "Stigma_surface", "Stigma_width", "Stigma_width", "Style_length", "Style_length", "Style_width", "Style_width", "Ovary_length", "Ovary_length", "Ovary_width", "Ovary_width")
+table<- data.frame(r,p, Analysis, Trait)
+kable(table, format="markdown")
 

### 2018-11-19 Scripts/Analysis_mantel_test.R

@@ -287,6 +287,9 @@ traits_all_bioenv <- traits_all
 traits_all_bioenv_scaled <- scale(traits_all_bioenv)
 bioenv(matrix_scale_effect,traits_all_bioenv)
 bioenv(matrix_scale_effect,traits_all_bioenv_scaled)
+bio_result <- bioenv(matrix_scale_effect,traits_all_bioenv_scaled)
+save(bio_result, file="Manuscript_draft/bio_result.RData")
+bio_result[3]
 #Result r=0.3711462 being pollen ovule ratio, stigma width and style width the best model
 adonis(matrix_scale_effect ~. ,data=traits_all)
 traits_all_scaled=as.data.frame(traits_all_scaled)
@@ -437,7 +440,7 @@ bioenv(matrix_scale_effect~traits_all$stigma_surface, method="pearson", trace=T)
 #11)Stigma width
 stigma_width <- traits_all_scaled[,11]
 stigma_width <- as.data.frame(stigma_width)
-stigma_width <- 1- stigma_width
+stigma_width <- stigma_width
 rownames(stigma_width) <- rownames(stigma_width)
 stigma_width_dist <- dist(stigma_width, diag=T, upper=T)
 mantel(matrix_scale_effect, stigma_width_dist)
@@ -450,7 +453,6 @@ bioenv(matrix_scale_effect~traits_all$stigma_width, method="pearson", trace=T)
 #12)Style_length
 style_length <- traits_all_scaled[,12]
 style_length <- as.data.frame(style_length)
-style_length <- 1- style_length
 rownames(style_length) <- rownames(style_length)
 style_length_dist <- dist(style_length, diag=T, upper=T)
 mantel(matrix_scale_effect, style_length_dist)
@@ -459,6 +461,37 @@ protest(matrix_scale_effect, style_length_dist)
 #significance=0.113, procustes correlation=0.3995
 bioenv(matrix_scale_effect~traits_all$style_length, method="pearson", trace=T)
 #correlation=-0.1757
+
+#13)Style_width
+style_width <- traits_all_scaled[,12]
+style_width <- as.data.frame(style_width)
+rownames(style_width) <- rownames(style_width)
+style_width_dist <- dist(style_width, diag=T, upper=T)
[…]

### 2018-11-20 Manuscript_draft/Results.Rmd
small changes

@@
 
+So the higher the values HpEffect the higher the negative impact of heterospecific pollen.
+
 The number of possible combinations with 10 species (multiplied by two because is in both directions the treatments A to B and B to A):
@@
 $$(\frac{10}{2})=\frac{10!}{2!*(8!)}*2=90 $$
+
+In total we performed 4400 treatments.
+If we just consider seed set, 2200 treatments including [50% Hp, 100% Hp, hand cross pollination, self pollination, natural selfing (bagged flowers) and apomixis (emasculated flowers)].
 
@@
 Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families.
-Here I show how they fit the colud of points per family *lm(HpEffect~its_distance)*.
+Here I show how they fit the cloud of points per family *lm(HpEffect~its_distance)*.
 Anyway, don't think this is very informative.
@@
 At the moment we are using all the traits without filtering the correlated traits.
-With Bioenv we can now what are the traits that gives a best fit of correlation between matrices.
+With Bioenv we can know what are the traits that gives a best fit of correlation between matrices.
 The best model is with pollen ovule ratio, stigma width and style width.

### 2018-11-21 Manuscript_draft/Results.Rmd
checking how to plot differences in traits

@@
 
-So the higher the values HpEffect the higher the negative impact of heterospecific pollen.
+Therefore, the higher the values of HpEffect the higher the impact of it.
 
@@
        as.numeric(pro_rbcl[13]),as.numeric(pro_rbcl_sqrt[13]))
-Analysis <- c("Mantel", "Mantel", "Procustes", "Procustes")
-Type <- c("normal evolutive distance","sqrt evolutive distance","normal evolutive distance", "sqrt evolutive distance")
+Analysis <- c("**Mantel**", "**Mantel**", "Procustes", "Procustes")
+Type <- c("**normal evolutive distance**","**sqrt evolutive distance**","normal evolutive distance", "sqrt evolutive distance")
 table<- data.frame(r,p, Analysis, Type)
@@
        as.numeric(pro_its[13]),as.numeric(pro_its_sqrt[13]))
-Analysis <- c("Mantel", "Mantel", "Procustes", "Procustes")
-Type <- c("normal evolutive distance","sqrt evolutive distance","normal evolutive distance", "sqrt evolutive distance")
+Analysis <- c("**Mantel**", "**Mantel**", "Procustes", "Procustes")
+Type <- c("**normal evolutive distance**","**sqrt evolutive distance**","normal evolutive distance", "sqrt evolutive distance")
 table<- data.frame(r,p, Analysis, Type)
@@
 This positive correlation should be further explored.
-Maybe a scatterplot of the phylogenetic distance and the heterospecific pollen effect could help to understand this correlation.
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
-plot(focal$hp_effect ~ focal$its_distance, main="", xlim=c(0.05,0.6),
-     xlab="Evolutive distance", ylab="Hp effect", pch=19, col=focal$col_focal)
-
-legend(x=0.04,y=3.2,legend=c("Brassicaceae","Convolvulaceae","Solanaceae"),pch=(c(16,16,16)), 
-       col = c("red","black","blue"), bty="n",cex=0.6,pt.cex=0.6,xpd=TRUE)
-
-```
-Figure 1.
-Scatterplot of the evolutive distances (x axis) and the mean scaled effect per species (ITS markers).
-In other words, each point is defined by the phylogenetic distance between a pair of species (x axis) and the effect of heterospecifc pollen which considers also an interaction between the same pair of species (donor and recipient)(y axis)
-\newpage
-
-Although is not very elegant, I  had the curiosity of how a regression line will fit these 3 different families.
-Here I show how they fit the cloud of points per family *lm(HpEffect~its_distance)*.
-Anyway, don't think this is very informative.
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-
-plot(focal$hp_effect ~ focal$its_distance, main="", xlim=c(0.05,0.6),
-     xlab="Evolutive distance", ylab="Hp effect", pch=19, col=focal$col_focal)
-
-legend(x=0.04,y=3.2,legend=c("Brassicaceae","Convolvulaceae","Solanaceae"),pch=(c(16,16,16)), 
-       col = c("red","black","blue"), bty="n",cex=0.6,pt.cex=0.6,xpd=TRUE)
-
-model_bra <- lm(focal_bra$value ~ focal_bra$value.1)
-#summary(model_brra)
-abline(model_bra, col="red")
-model_sol <- lm(focal_sol$value ~ focal_sol$value.1)
-#summary(model_sol)
-abline(model_sol, col="blue")
-model_con <- lm(focal_con$value ~ focal_con$value.1)
-#summary(model_con)
-abline(model_con, col="black")
-
-```
-
-So far I think phylogenetic distance doesn't help to visualize heterospecific pollen effect. Grouping by traits or the type of donor seems to be much more informative.
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
-pollen_tree=read.tree("pollen_tree.nwk")
-plot(pollen_tree)
-add.scale.bar(x=0, y=1)
-```
 
@@
 Here I perform Mantel test and Procustes test between the traits and heterospecific pollen effect.
-For both Mantel and procustes we weren't able to find evidence of correlation between matrices.
+For both Mantel and procustes we were not able to find evidence of correlation between matrices.
 At the moment we are using all the traits without filtering the correlated traits.
@@
 
+Now I show the correlations between the different morphological traits in order to clean the data. The correlation is performed between the mean values for each species, so N=10.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("Data/trait_corr.RData")
+
+a_1 <- cor.test(stigma_area$um, stigma_length$um)
+a_2 <- cor.test(stigma_area$um, stigma_surface$um)
+a_3 <- cor.test(stigma_area$um, stigma_width$um)
+a_4 <- cor.test(stigma_area$um, style_length$um)
+a_5 <- cor.test(stigma_area$um, style_width$um)
+a_6 <- cor.test(stigma_area$um, ovary_width$um)
+a_7 <- cor.test(stigma_area$um, ovary_length$um)
+b_1 <- cor.test(stigma_length$um, stigma_surface$um)
+b_2 <- cor.test(stigma_length$um, stigma_width$um)
+b_3 <- cor.test(stigma_length$um, style_length$um)
+b_4 <- cor.test(stigma_length$um, style_width$um)
+b_5 <- cor.test(stigma_length$um, ovary_width$um)
+b_6 <- cor.test(stigma_length$um, ovary_length$um)
+c_1 <- cor.test(stigma_surface$um, stigma_width$um)
+c_2 <- cor.test(stigma_surface$um, style_length$um)
+c_3 <- cor.test(stigma_surface$um, style_width$um)
+c_4 <- cor.test(stigma_surface$um, ovary_width$um)
+c_5 <- cor.test(stigma_surface$um, ovary_length$um)
+d_1 <- cor.test(stigma_width$um, style_length$um)
+d_2 <- cor.test(stigma_width$um, style_width$um)
+d_3 <- cor.test(stigma_width$um, ovary_width$um)
+d_4 <- cor.test(stigma_width$um, ovary_length$um)
+e_1 <- cor.test(style_length$um, style_width$um)
+e_2 <- cor.test(style_length$um, ovary_width$um)
+e_3 <- cor.test(style_length$um, ovary_length$um)
+f_1 <- cor.test(style_width$um, ovary_width$um)
+f_2 <- cor.test(style_width$um, ovary_length$um)
+g_1 <- cor.test(ovary_width$um, ovary_length$um)
+
+r <- c(a_1[4],a_2[4],a_3[4],a_4[4],a_5[4],a_6[4],a_7[4], b_1[4],b_2[4],b_3[4],b_4[4],b_5[4],b_6[4], c_1[4],c_2[4],c_3[4],c_4[4],c_5[4], d_1[4],d_2[4],d_3[4],d_4[4], e_1[4],e_2[4],e_3[4], f_1[4],f_2[4], g_1[4])
+r<- as.numeric(r)
+p <- c(a_1[3],a_2[3],a_3[3],a_4[3],a_5[3],a_6[3],a_7[3], b_1[3],b_2[3],b_3[3],b_4[3],b_5[3],b_6[3], c_1[3],c_2[3],c_3[3],c_4[3],c_5[3], d_1[3],d_2[3],d_3[3],d_4[3], e_1[3],e_2[3],e_3[3], f_1[3],f_2[3], g_1[3])
+p<-as.numeric(p)
+corr_a<- c("Stigma_area~Stigma_length","**Stigma_area~Stigma_surface**","Stigma_area~Stigma_width","**Stigma_area~Style_length**","Stigma_area~Style_width","Stigma_area~Ovary_width","Stigma_area~Ovary_length")
+corr_b <- c("Stigma_length~Stigma_surface","Stigma_length~Stigma_width","Stigma_length~Style_length","Stigma_length~Style_width","**Stigma_length~Ovary_width**","Stigma_length~Ovary_length")
+corr_c <- c("stigma_surface~Stigma_width","**stigma_surface~Style_length**","stigma_surface~Style_width","stigma_surface~Ovary_width","stigma_surface~Ovary_length")
+corr_d <- c("Stigma_width~Style_length","Stigma_width~Style_width","Stigma_width~Ovary_width","Stigma_width~Ovary_length")
+corr_e <- c("Style_length~Style_width","Style_length~Ovary_width","Style_length~Ovary_length")
+corr_f <- c("Style_width~Ovary_width","Style_width~Ovary_length")
+corr_g <- c("Ovary_width~Ovary_length")
+corr <- c(corr_a,corr_b,corr_c,corr_d,corr_e,corr_f,corr_g)
+
+table<- data.frame(r,p, corr)
+kable(table, format="markdown")
+
+```
+
+As it was expected, stigma area (square micrometers) and and stigma surface are highly correlated. Basically, they are the same measure. They are two different ways to estimate stigma size.
+
 #References

### 2018-11-21 Scripts/Analysis_mantel_test.R

@@ -498,6 +498,26 @@ protest(matrix_scale_effect, ovary_length_dist)
 
 
 
+#After checking the correlations between the morphological traits, we clean some variables
+#For stigma we are going to use one measurement that is going to be the width seen from the top 
+#which is highly correlated with the area (square micrometers) also seen from the top
+#For style we are going to use just the length
+
+traits_all_scaled_clean <- traits_all_scaled[,-c(7,8,10,12)]
+all_scaled_clean_dist <- dist(traits_all_scaled_clean)
+mantel(matrix_scale_effect, all_scaled_clean_dist)
+
+protest(matrix_scale_effect, all_scaled_clean_dist)
+
+traits_checking <- traits_all_scaled[,-c(2,3,4,5,7,8,9,11,12,13,14,15)]
+traits_checking_dist <- dist(traits_checking)
+
+mantel(matrix_scale_effect, traits_checking_dist)
+protest(matrix_scale_effect, traits_checking_dist)
+
+cor.test(traits_all_scaled$stigma_type, traits_all_scaled$stigma_surface)
+
+
 #
 ##
 #### PART 3 visualising this differences

### 2018-11-21 Scripts/all_traits.R

@@ -80,29 +80,73 @@ ovary_length$measurement <- gsub('ovary _ legth', 'ovary _ length', ovary_length
 #Ok now all the traits are ready!! Lets add it to traits_all.
 
 traits_all$stigma_area <- stigma_area$um
-traits_all$stigma_length <- stigma_lenght$um
+traits_all$stigma_length <- stigma_length$um
 traits_all$stigma_surface <- stigma_surface$um
 traits_all$stigma_width <- stigma_width$um
-traits_all$style_length <- stigma_lenght$um
+traits_all$style_length <- stigma_length$um
 traits_all$style_width <- style_width$um
 traits_all$ovary_width <- ovary_width$um
 traits_all$ovary_length <- ovary_length$um
 
 
+#save.image("Manuscript_draft/Data/stigma_area.RData")
+#save.image("Manuscript_draft/Data/stigma_length.RData")
+#save.image("Manuscript_draft/Data/stigma_surface.RData")
+#save.image("Manuscript_draft/Data/stigma_width.RData")
+#save.image("Manuscript_draft/Data/style_length.RData")
+#save.image("Manuscript_draft/Data/style_width.RData")
+#save.image("Manuscript_draft/Data/ovary_width.RData")
+#save.image("Manuscript_draft/Data/ovary_length.RData")
+
+#dir.create("Manuscript_draft/Data")
+
+save.image(file='Manuscript_draft/Data/trait_corr.RData')
 
 
-cor.test(stigma_lenght$um, stigma_width$um)
-cor.test(stigma_length$um, stigma_area$um)
-cor.test(width$um, area$um)
-cor.test(ovary_width$um, o_length$um)
+cor.test(stigma_area$um, stigma_length$um)
+cor.test(stigma_area$um, stigma_surface$um)
+cor.test(stigma_area$um, stigma_width$um)
+cor.test(stigma_area$um, style_length$um)
+cor.test(stigma_area$um, style_width$um)
+cor.test(stigma_area$um, ovary_width$um)
+cor.test(stigma_area$um, ovary_length$um)
+
+cor.test(stigma_length$um, stigma_surface$um)
+cor.test(stigma_length$um, stigma_width$um)
+cor.test(stigma_length$um, style_length$um)
+cor.test(stigma_length$um, style_width$um)
+cor.test(stigma_length$um, ovary_width$um)
 cor.test(stigma_length$um, ovary_length$um)
+
[…]

### 2018-11-23 Manuscript_draft/Results.Rmd
NMDS

@@
 library(dplyr)
+library(ggfortify)
+library(ggplot2)
+library(stats)
+library(cluster)
 #load environment
@@
 
+\newpage
+Multivariate homogeinity of groups dispersions (variances).
+Non-euclidean distances are handle by reducing the original distances to principal coordinates.
+Here I present an analysis of the variances for the measurements of Gynoecium for the ten species.
+The measurements used are width and length of stigma, style and ovary.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("betadisper.RData")
+plot(traits, cex=1,pch=10:21,
+     main="Gynoecium:MDS coordinates", cex.lab=1.25,label.cex=0.5,
+     xlab=labs[1], ylab=labs[2], ylim=c(-0.35,0.35),xlim=c(-0.35,0.35),
+     hull=FALSE, ellipse=TRUE, conf=0.68, lwd=2)
+
+```
+
+\newpage
+Other way of showing the same results but now with Principal Components Analysis. Maybe is more elegant? Grouped by species.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("betadisper.RData")
+autoplot(prcomp(all_pca), data = traits_all, colour = 'species', frame = TRUE, frame.type = 'norm')
+```
+
+\newpage
+Now I group by family
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("betadisper.RData")
+autoplot(prcomp(all_pca), data = traits_all, colour = 'family', frame = TRUE, frame.type = 'norm', main="Gynoecium spp PCA")
+```
+
 #References

### 2018-11-23 Manuscript_draft/Results.Rmd
Other NMDS from other package

@@
 library(cluster)
+library(MASS)
 #load environment
@@
 
+\newpage
+Now I use non metric multidimensional scaling for all the traits of our species.
+The traits used are: Stigma_type, Selfing_rate, Pollem_size, Mean_pollen_anther, Mean_ovules, Pollen_ovule_ratio, Anthers, Stigma_length, Stigma_surface (width), Style_length, Style_width, Ovary_width, Ovary_length
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, cache.comments=FALSE,results='hide',fig.keep='all'}
+all <- read.csv("Data/traits_all.csv", sep=",")
+rownames(all) <- c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
+all <- all[,-c(1,2,10,13)]
+all_scaled <- scale(all)
+all_scaled_dist <- dist(all_scaled)
+autoplot(sammon(all_scaled_dist), shape = FALSE, main="Non-metric multidimensional scaling",label.colour = 'blue', label.size = 3)
+```
+
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, cache.comments=FALSE, results='hide'}
+all <- read.csv("Data/traits_all.csv", sep=",")
+rownames(all) <- c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
+spp=c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
+all <- all[,-c(1,2,10,13)]
+#In this case we consider all the traits. 
+NMDS=metaMDS(all,k=2,trymax=100)
+ordiplot(NMDS,type="n")
+orditorp(NMDS,display="sites",col=c(rep("green",2),"blue","green", rep("black",2),"blue","green", rep("blue",2)),
+         air=0.01,cex=1.25)
+```
+
 #References

### 2018-11-23 Scripts/betadisper.R

@@ -136,6 +136,7 @@ library(ggfortify)
 library(ggplot2)
 library(stats)
 library(cluster)
+library(MASS)
 all_pca=traits_all[,c(3,6,9,13,17,21)]
 df <- iris[c(1, 2, 3, 4)]
 autoplot(prcomp(all_pca))
@@ -195,7 +196,7 @@ save.image("Manuscript_draft/betadisper.RData")
 
 all <- read.csv("Data/traits_all.csv", sep=",")
 rownames(all) <- c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
-all <- all[,-c(1,2)]
+all <- all[,-c(1,2,10,13)]
 all_scaled <- scale(all)
 all_scaled_dist <- dist(all_scaled)
 
@@ -203,17 +204,32 @@ all_scaled_dist <- dist(all_scaled)
 #In this case we consider all the traits. 
 autoplot(all_scaled_dist)
 autoplot(cmdscale(all_scaled_dist, eig = TRUE), label = TRUE, label.size = 3)
-autoplot(sammon(all_scaled_dist), shape = FALSE, label.colour = 'blue', label.size = 3)
+autoplot(sammon(all_scaled_dist), shape = FALSE, main="Non-metric multidimensional scaling",label.colour = 'blue', label.size = 3)
 #I´m going to clean some redundant morphometic traits
 
 autoplot(sammon(all_scaled_dist), shape = FALSE, label.colour = 'blue', label.size = 3)
 
 all <- read.csv("Data/traits_all.csv", sep=",")
 rownames(all) <- c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
+spp=c("BROL","BRRA","CAAN","ERSA","IPAQ","IPPU","PEIN","SIAL","SOLY","SOME")
 all <- all[,-c(1,2,10,13)]
-all_scaled_dist <- dist(all_scaled)
 #In this case we consider all the traits. 
-autoplot(all_scaled_dist)
-autoplot(cmdscale(all_scaled_dist, eig = TRUE), label = TRUE, label.size = 3)
-autoplot(sammon(all_scaled_dist), shape = FALSE, label.colour = 'blue', label.size = 3)
+
+NMDS=metaMDS(all,k=2,trymax=100)
+stressplot(NMDS)
+plot(NMDS)
+ordiplot(NMDS)
[…]

### 2018-11-26 Manuscript_draft/Results.Rmd
Brassicaceae ggplot Selfing_rate

@@
 library(MASS)
+library(cowplot)
 #load environment
@@
 Therefore, the higher the values of HpEffect the higher the impact of it.
-
-The number of possible combinations with 10 species (multiplied by two because is in both directions the treatments A to B and B to A):
-
-$$(\frac{10}{2})=\frac{10!}{2!*(8!)}*2=90 $$
-
-In total we performed 4400 treatments.
-If we just consider seed set, 2200 treatments including [50% Hp, 100% Hp, hand cross pollination, self pollination, natural selfing (bagged flowers) and apomixis (emasculated flowers)].
 
@@
 Now I use non metric multidimensional scaling for all the traits of our species.
-The traits used are: Stigma_type, Selfing_rate, Pollem_size, Mean_pollen_anther, Mean_ovules, Pollen_ovule_ratio, Anthers, Stigma_length, Stigma_surface (width), Style_length, Style_width, Ovary_width, Ovary_length
+The traits used are: Stigma_type, Selfing_rate, Pollen_size, Mean_pollen_anther, Mean_ovules, Pollen_ovule_ratio, Anthers, Stigma_length, Stigma_surface (width), Style_length, Style_width, Ovary_width, Ovary_length
 
@@
 
+\newpage
+
+Interestignly for Brassicaceae species selfing rates matches pretty well the output of heterospecific pollen effect.
+Therefore, seems that selfing rates in Brassicaceae species could be a good predictor of foreign pollen effect.
+When we consider the relatedness of the donors, for instance crosses between families
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("Data/all_bra.Rda")
+cbPalette <- c("#000000", "#E69F00", "darkturquoise", "deeppink3")
+ ggplot(all_bra, aes(x=close_related, y=hp_effect)) + 
+  geom_jitter(width=0.1,aes(colour = Pollen_recipient),size=3.5)+
+  theme_cowplot()+theme(axis.title.x=element_blank(),
+axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.7, 0.8))+
+  scale_x_continuous(limits = c(0.8, 1.35)) +scale_y_continuous("Heterospecific pollen effect")+
+   annotate("text", x = c(0.82,0.82), y=c(0.4,2.2), label = c("Low effect","High effect"))+
+   geom_hline(yintercept = 1.5)+scale_color_manual(values = cbPalette)+labs(title = "Brassicaceae spp", subtitle = "")
+```
+
 #References

### 2018-11-27 Manuscript_draft/Results.Rmd
Other scatterplot from two families added. I'll add the phylogenetic signal of traits tomorrow.

@@
 
-I try Mantel test and procustes test, although both are similar procustes performs better in a wider range of circumstances @peres2001.
+I try **Mantel test** and procustes test, although both are similar procustes performs better in a wider range of circumstances @peres2001.
 Moreover, I consider the square root of the evolutive distances which improves the statistical power in comparison to the normal distances @letten2015.
@@
 
-\newpage
 #Part 2 Relation between effect of Hp and traits
 
-Here I perform Mantel test and Procustes test between the traits and heterospecific pollen effect.
+Here I perform **Mantel test** and **Procustes test** between the matrices of traits and heterospecific pollen effect.
 For both Mantel and procustes we were not able to find evidence of correlation between matrices.
-At the moment we are using all the traits without filtering the correlated traits.
-With Bioenv we can know what are the traits that gives a best fit of correlation between matrices.
-The best model is with pollen ovule ratio, stigma width and style width.
+At the moment we are using all the traits without filtering the correlated traits (similar result also if we not consider some rudendant traits).
+With **Bioenv** we can see what are the traits that gives a best fit of correlation between our matrix of Hp effect and the dataset of traits The best model with Bioenv is with pollen ovule ratio, stigma width and style width.
+For procustes the stigma surface (width from aerial view) seems to be correlated with the Hp effect.
+Moreover, stigma type too but these values are converted to distance from ones and zeros and don not know how much it can be trusted.
 
@@
 
-Now I perform the analysis with both Mantel and Procustes trait by trait.
+Now I perform the analysis with both **Mantel** and **Procustes** trait by trait.
 
@@
 
-Interestignly for Brassicaceae species selfing rates matches pretty well the output of heterospecific pollen effect.
-Therefore, seems that selfing rates in Brassicaceae species could be a good predictor of foreign pollen effect.
-When we consider the relatedness of the donors, for instance crosses between families
+Interestignly for Brassicaceae species selfing rates matches pretty well the output of heterospecific pollen effect for 3 of 4 species.
+Therefore, it seems that selfing rates in Brassicaceae species could be a good predictor of foreign pollen effect.
+Another thing that I would like to remark is the similar behaviour of each individual species irrespective of the donor.
+This is a constant pattern for all our species of the different 3 families (other 2 families below).
+I think it is a very interesting finding that each species despite some variation maintains normally a similar response independently of the nature of the donor.
 
@@
   theme_cowplot()+theme(axis.title.x=element_blank(),
-axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.7, 0.8))+
+axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.6, 0.8))+
   scale_x_continuous(limits = c(0.8, 1.35)) +scale_y_continuous("Heterospecific pollen effect")+
@@
 ```
+Figure X. Heterospecific pollen effect on the different species of the Brassicaceae family
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("Data/all_sol.Rda")
+cbPalette <- c("#000000", "#E69F00", "darkturquoise", "deeppink3")
+
+ ggplot(all_sol, aes(x=close_related, y=hp_effect)) + 
+   geom_jitter(width=0.1,aes(colour = Pollen_recipient),size=4)+
+   theme_cowplot()+theme(axis.title.x=element_blank(),
+                         axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.6, 0.8))+
+   scale_x_continuous(limits = c(0.8, 1.35)) +scale_y_continuous("Heterospecific pollen effect")+
+   annotate("text", x = c(0.82,0.82), y=c(0.4,2.2), label = c("Low effect","High effect"))+
+   geom_hline(yintercept = 1.5)+scale_color_manual(values = cbPalette)+labs(title = "Solanaceae spp", subtitle = "")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("Data/all_con.Rda")
+cbPalette <- c("#000000", "#E69F00", "darkturquoise", "deeppink3")
+
+ggplot(all_con, aes(x=close_related, y=hp_effect)) + 
+   geom_jitter(width=0.1,aes(colour = Pollen_recipient),size=4)+
+   theme_cowplot()+theme(axis.title.x=element_blank(),
+                         axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.6, 0.92))+
+   scale_x_continuous(limits = c(0.8, 1.35)) +scale_y_continuous("Heterospecific pollen effect")+
+   annotate("text", x = c(0.82,0.82), y=c(0.4,2.2), label = c("Low effect","High effect"))+
+   geom_hline(yintercept = 1.5)+scale_color_manual(values = cbPalette)+labs(title = "Solanaceae spp", subtitle = "")
+
+```
 

### 2018-11-27 Scripts/Analysis_mantel_test.R

@@ -503,7 +503,7 @@ protest(matrix_scale_effect, ovary_length_dist)
 #which is highly correlated with the area (square micrometers) also seen from the top
 #For style we are going to use just the length
 
-traits_all_scaled_clean <- traits_all_scaled[,-c(7,8,10,12)]
+traits_all_scaled_clean <- traits_all_scaled[,-c(1,3,4,5,7,8,11,12,13,14,15)]
 all_scaled_clean_dist <- dist(traits_all_scaled_clean)
 mantel(matrix_scale_effect, all_scaled_clean_dist)
 
@@ -695,14 +695,14 @@ f <- subset(focal_pein, Non_focal=="SIAL" | Non_focal=="ERSA"| Non_focal=="BROL"
             | Non_focal=="IPAQ"| Non_focal=="IPPU")
 g <- subset(focal_some, Non_focal=="SIAL" | Non_focal=="ERSA"| Non_focal=="BROL" | Non_focal=="BRRA"
             | Non_focal=="IPAQ"| Non_focal=="IPPU")
-h <- subset(focal_soly, Non_focal=="SIAL" | Non_focal=="ERSA"| Non_focal=="BROL" | Non_focal=="BRRA"
+h <- subset(focal_caan, Non_focal=="SIAL" | Non_focal=="ERSA"| Non_focal=="BROL" | Non_focal=="BRRA"
             | Non_focal=="IPAQ"| Non_focal=="IPPU")
 
 sol <- rbind(e,f,g,h)
 
 i <- subset(focal_ipaq, Non_focal=="SOME" | Non_focal=="SOLY"| Non_focal=="PEIN"| Non_focal=="CAAN"
             | Non_focal=="BROL"| Non_focal=="BRRA"| Non_focal=="ERSA"| Non_focal=="SIAL")
-K <- subset(focal_ipaq, Non_focal=="SOME" | Non_focal=="SOLY"| Non_focal=="PEIN"| Non_focal=="CAAN"
+k <- subset(focal_ippu, Non_focal=="SOME" | Non_focal=="SOLY"| Non_focal=="PEIN"| Non_focal=="CAAN"
             | Non_focal=="BROL"| Non_focal=="BRRA"| Non_focal=="ERSA"| Non_focal=="SIAL")
 con <- rbind(i,k)
 all_non_focal <- rbind(bra, sol, con)
@@ -773,9 +773,105 @@ axis.text.x=element_blank(),axis.ticks.x=element_blank(),legend.position = c(0.7
[…]

### 2018-11-28 Manuscript_draft/Results.Rmd
Some advances in the scatterplots for spp.
Phylo signal added to results.

@@
 bibliography: references.bib
+editor_options: 
+  chunk_output_type: inline
 ---
@@
 When a species had higher values of seed production with treatments than the cross, we set as maximum value for the treatments the same as the hand cross pollination.
-However, we should take into account that analysis in general improve if we keep these negative values.
+However, we should consider that analysis in general improve if we keep these negative values.
 If we put these words into a formula being i the different focal species and j the different donors:
@@
 With **Bioenv** we can see what are the traits that gives a best fit of correlation between our matrix of Hp effect and the dataset of traits The best model with Bioenv is with pollen ovule ratio, stigma width and style width.
-For procustes the stigma surface (width from aerial view) seems to be correlated with the Hp effect.
+For Mantel the stigma surface (width from aerial view) seems to be correlated with the Hp effect.
 Moreover, stigma type too but these values are converted to distance from ones and zeros and don not know how much it can be trusted.
@@
 The measurements used are width and length of stigma, style and ovary.
+Outliers were substituted by other values from the same variable and species.
+Didn't know how to perform it with NA's.
 
@@
 \newpage
+Other type of NMDS
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, cache.comments=FALSE, results='hide'}
@@
 
+Now I try to show the results of heterospecific pollen effect in a easy way to understand the pattern of seed set across treatments.
+For that I do 3 different scatterplots by family and then I colour the different spp.
+Note that the points should be all in the same vertical line because just Y axis is numerical but for representation purposes they are spread randomly across the x axis.
+I have added in the legend the selfing rates, in my opinion could be a bit informative to understand the different patterns.
+For Brassicaceae the percentage of fruiting is considered and for Solanaceae and Convolvulaceae the percentage of decrease of seed set in comparison with optimum pollination (seed set of hand cross poll.) is taken into account.
+
+ What I see:
+
 Interestignly for Brassicaceae species selfing rates matches pretty well the output of heterospecific pollen effect for 3 of 4 species.
 Therefore, it seems that selfing rates in Brassicaceae species could be a good predictor of foreign pollen effect.
-Another thing that I would like to remark is the similar behaviour of each individual species irrespective of the donor.
+Another thing that I would like to remark is the *similar behaviour of each individual species irrespective of the donor*.
 This is a constant pattern for all our species of the different 3 families (other 2 families below).
 I think it is a very interesting finding that each species despite some variation maintains normally a similar response independently of the nature of the donor.
+*Moreover, the effect is high or low irrespective of the family but more or less constant within spp*.
 
@@
 ```
-Figure X. Heterospecific pollen effect on the different species of the Brassicaceae family
+Figure X.
+Heterospecific pollen effect of the different species of the Brassicaceae family.
+Each point correspond to the scaled seed set for the different treatments (9 for each spp).
+Random dispersion was applied to the points to avoid overlapping (jitter).
+The line, is an arbitrary line that I added in the half of the plot (approx) to try to improve visualization.
+
 \newpage
+
+Again species with highest selfing has lowest Hp effect.
 
@@
 ```
+Figure X. Heterospecific pollen effect on the different species of the Solanaceae family. Random dispersion was applied to the points to avoid overlapping (jitter).
 
 \newpage
+
+Same, species with highest selfing has lowest Hp effect.
 
@@
 ```
+Figure X. Heterospecific pollen effect on the different species of the Convolvulaceae family. Random dispersion was applied to the points to avoid overlapping (jitter).
+
+\newpage
+
+Phylogenetic signal of traits
+
+The variables with highes values of Pagel's lambda are *selfing rate*, *pollen size*, *stigma surface* and *stigma width*. How to interpretate high values and no significance?
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("Data/phylo_sign.RData")
+
+lambda <- c(stigma_type[1], selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_surface[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1])
+lambda<- as.numeric(lambda)
+p <- c(stigma_type[4], selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_surface[4], stigma_width[4], style_length[1], style_width[1], ovary_length[1], ovary_width[1])
+p <- as.numeric(p)
+trait <- c("stigma_type","**selfing_rate**", "**pollen_size**", "mean_pollen_anther", "mean_ovules", "pollen_ovule_ratio", "stigma_area", "stigma_length", "**stigma_surface**", "**stigma_width**", "style_length", "style_width", "ovary_length",
+           "ovary_width")
+table<- data.frame(lambda,p, trait)
+kable(table, format="markdown")
+```
 

### 2018-11-28 Scripts/phylogenetic_signal.R

@@ -15,33 +15,58 @@ tree_10=as.phylo(tree_10)
 plot.phylo(tree_10)
 add.scale.bar(x=0, y=9)
 
-locator(1)
+#For row names of traits all
+readRDS("Manuscript_draft/Data/matrix_scale_effect.Rda")
+
+
+#From here I start working with the traits
+traits_all <- read.csv("Data/traits_all.csv", sep=",")
+rownames(traits_all) <- rownames(matrix_scale_effect)
+traits_all <- traits_all[,-c(1,2)]
+traits_all_scaled <- scale(traits_all)
+
+
+
+#Phylo signal for stigma type
+stigma_type <-as.data.frame(traits_all[,c("stigma_type")])
+rownames(stigma_type) <- tree_10[[3]]
+stigma_type <- as.matrix((stigma_type))[,1]
+stigma_type <- phylosig(tree=tree_10,x=stigma_type,method="lambda",test=TRUE)
+
+
 #Phylo signal for selfing rate
 selfing <-as.data.frame(traits_all[,c("Selfing_rate")])
 rownames(selfing) <- tree_10[[3]]
 selfing <- as.matrix((selfing))[,1]
-phylosig(tree=tree_10,x=selfing,method="lambda",test=TRUE)
+selfing <- phylosig(tree=tree_10,x=selfing,method="lambda",test=TRUE)
 #$`lambda`[1] 0.9467709
+#Checking position of results to call them in Markdown
+#a <- phylosig(tree=tree_10,x=selfing,method="lambda",test=TRUE)
+#a[1]
+#a[4]
+
+
+
 
 #Phylo signal for pollen size
 pollen_size <-as.data.frame(traits_all[,c("pollen_size")])
 rownames(pollen_size) <- tree_10[[3]]
 pollen_size <- as.matrix((pollen_size))[,1]
-phylosig(tree=tree_10,x=pollen_size,method="lambda",test=TRUE)
+pollen_size <- phylosig(tree=tree_10,x=pollen_size,method="lambda",test=TRUE)
 #$`lambda`[1] 0.9971989
 
 #Phylo signal for mean pollen per anther
 mean_pollen_anther <-as.data.frame(traits_all[,c("mean_pollen_anther")])
 rownames(mean_pollen_anther) <- tree_10[[3]]
 mean_pollen_anther <- as.matrix((mean_pollen_anther))[,1]
[…]

### 2018-11-29 Manuscript_draft/Manuscript_draft.Rmd
regression line, mixed effect flower level, each one was a random one. Ask this to Nacho to confirm...

@@
 Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016.
-A general overview of it can reduce species fitness (REFS) but not in al the cases (Refs).
-Other general facts...
-Quantity of foreign pollen that arrives...
+A general overview of heterospecific pollen effect is that it can play an important role on species fitness but seems to be context dependent and not always fitness decreased is produced.
+There are several traits that are postulated to be highly relevant to this process.
+However the relative importance of them and their contribution to this effect is not yet well understood.
+
+**Paragraph 3**
+
+can reduce species fitness (REFS) but seems to be highly contex-dependent. There are hypothesized that some traits can play a crucial role in this species interaction such as stigma type, pollen size,
 

### 2018-11-29 Scripts/Analysis_mantel_test.R

@@ -950,6 +950,7 @@ ggplot(ALL, aes(x=compatibility, y=hp_effect)) +
 
 #Load library for GLMM
 library(nlme)
+library(lme4)
 
 model1=lm(hp_effect~compatibility, data=ALL)
 summary(model1)
@@ -959,3 +960,20 @@ summary(model2)
 coef(model2)
 plot(ranef(model2))
 plot(model2)
+
+#Lets add new column with a seq of the length of the dataset and i use that as random effect (different individuals)
+
+ALL$indv<- seq.int(nrow(ALL))
+model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
+summary(model2)
+tempEf$fit <- predict(model) 
+
+Model.2 <- lmer(hp_effect ~ compatibility + (1 | Focal), data = ALL)
+summary(Model.2)
+
+ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
+  geom_jitter(width=1.5,aes(colour = Focal),size=4)+geom_line(aes(y=predict(model2), group=hp_effect))
+
+ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
+  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
+  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(Model.2))))

### 2018-11-30 Manuscript_draft/Manuscript_draft.Rmd
reading and writing day

--- 2018-11-15 Manuscript_draft/Manuscript_draft.Rmd
@@
 
-Possible journals to publish: New phytologist, journal of ecology, oikos...
+Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen.
+However, the costs of heterospecific pollen are not yet well understood.
+For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
+We experimentally crossed 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+Overall, more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
+We found that for all species foreign pollen (50% or less) reduced seed set.
+Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
+However, the effect is governed by the degree of relatedness and the traits of the species recipient.
+Our results show that the outcome of heterospecific pollen deposition is determined in greater degree by the traits of the pollen recipient than the pollen donor and that certain traits such as compatibility system are crucial to understand the costs of heterospecific pollen.
 
@@
 This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014.
-Once, the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and hence ovule fertilization.
-An increasing number of visits generally correlates with higher chances of fertilization (Refs).
-However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs (Refs) and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes (Refs).
-Moreover, other less study issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 (More refs).
+Once the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and hence ovule fertilization.
+An increasing number of visits generally correlates with higher chances of fertilization @engel2003.
+However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs @inouye1980 and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes @aizen2007.
+Moreover, other less study issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 @ashman2013.
 
@@
 
-Recent important studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016.
-A general overview of it can reduce species fitness (REFS) but not in al the cases (Refs).
-Other general facts...
-Quantity of foreign pollen that arrives...
+Recent studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016.
+A general overview of heterospecific pollen effect is that it can play an important role on species fitness but seems to be context dependent and not always fitness decreased is produced @morales2008.
+There are several traits that are postulated to be highly relevant to this process but the correlation with heterospecific pollen effect remains porrly understood.
+
+Mention relatedness somwhere here.
+
+Moreover, the different methods used make difficult to compare among different experiments.
+For instance many articles do not describe the foreign pollen quantity used to test for effect or how this pollen was applied (Refs).
+The small size of pollen, great environmental variability and population outcrossing rates among others make of this field of study a daunting task and higly unpredictable.
+
+**Paragraph 3**
+
+can reduce species fitness (REFS) but seems to be highly contex-dependent. There are hypothesized that some traits can play a crucial role in this species interaction such as stigma type, pollen size,
 

### 2018-11-30 Manuscript_draft/Manuscript_draft.tex
reading and writing day

@@
 
-Possible journals to publish: New phytologist, journal of ecology,
-oikos\ldots{}
+Pollinator sharing can have negative consequences for species fitness
+with the arrival of foreign pollen. However, the costs of heterospecific
+pollen are not yet well understood. For this reason, we have conducted a
+glasshouse experiment where we try to understand how phylogenetic
+relatedness and the different traits of these species are involved in
+this process. We experimentally crossed 10 species belonging to three
+different families: Brassicaceae, Solanaceae and Convolvulaceae.
+Overall, more than 4000 crosses were done and seed set and pollen tubes
+were considered as proxy of effect. We found that for all species
+foreign pollen (50\% or less) reduced seed set. Moreover, the seed set
+reduction is not dependent on the degree of relatedness of the pollen
+donor. However, the effect is governed by the degree of relatedness and
+the traits of the species recipient. Our results show that the outcome
+of heterospecific pollen deposition is determined in greater degree by
+the traits of the pollen recipient than the pollen donor and that
+certain traits such as compatibility system are crucial to understand
+the costs of heterospecific pollen.
 
@@
 negative due to competition Pauw (2013) or positive due to facilitation
-Carvalheiro et al. (2014). Once, the floral visitor has arrived to the
+Carvalheiro et al. (2014). Once the floral visitor has arrived to the
 flower, pollen deposition on the stigma can take place and hence ovule
 fertilization. An increasing number of visits generally correlates with
-higher chances of fertilization (Refs). However this is not always the
-case, among these possible flower visitors we find also nectar robbers
-and pollen thiefs (Refs) and the quality of pollen that is deposited on
-the stigma is also highly relevant to the pollination succes (Refs).
-Moreover, other less study issues in the pollination process are
-conspecific pollen loss and the arrival of foreign pollen which can have
-important detrimental effects for the species fitness Morales and
-Traveset (2008) (More refs).
+higher chances of fertilization Engel and Irwin (2003). However this is
+not always the case, among these possible flower visitors we find also
+nectar robbers and pollen thiefs Inouye (1980) and the quality of pollen
+that is deposited on the stigma is also highly relevant to the
+pollination succes Aizen and Harder (2007). Moreover, other less study
+issues in the pollination process are conspecific pollen loss and the
+arrival of foreign pollen which can have important detrimental effects
+for the species fitness Morales and Traveset (2008) Ashman and
+Arceo-Gómez (2013).
 
@@
 
-Recent important studies have advanced in the ecological importance of
+Recent studies have advanced in the ecological importance of
 heterospecific pollen effect Morales and Traveset (2008)
-({\textbf{???}}) Arceo-Gómez and Ashman (2016). A general overview of it
-can reduce species fitness (REFS) but not in al the cases (Refs). Other
-general facts\ldots{} Quantity of foreign pollen that arrives\ldots{}
+({\textbf{???}}) Arceo-Gómez and Ashman (2016). A general overview of
+heterospecific pollen effect is that it can play an important role on
+species fitness but seems to be context dependent and not always fitness
+decreased is produced Morales and Traveset (2008). There are several
+traits that are postulated to be highly relevant to this process but the
+correlation with heterospecific pollen effect remains to be tested.
+Moreover, the different methods used make difficult to compare among
+different experiments. For instance many articles do not describe the
+foreign pollen quantity used to test for effect or how this pollen was
+applied (Refs). The small size of pollen, great environmental
+variability and population outcrossing rates among others make of this
+field of study a daunting task and higly unpredictable.
+
+\textbf{Paragraph 3}
+
+can reduce species fitness (REFS) but seems to be highly
+contex-dependent. There are hypothesized that some traits can play a
+crucial role in this species interaction such as stigma type, pollen
+size,
 
@@
 \textbf{Paragraph 3}
+
+Traditionally heterospecific pollen effect has focused its attention on
+different pollen donors as a main driver of different effect. However in
+this article we want to emphasize that this is true for the cases that
+the species are higly close related where pollen recognition can take
+place (eg hybridization) but not when this pollen is from less closely
+related species which the main driver of effect is determined by the
+reproductive biology of the female part of the plant(compatibility
+system, stigma type, stigma area and number of ovules).
 
@@
 \hypertarget{refs}{}
+\hypertarget{ref-aizen2007}{}
+Aizen, M. A., and L. D. Harder. 2007. Expanding the limits of the
+pollen-limitation concept: Effects of pollen quantity and quality.
+Ecology 88:271--281.
+
 \hypertarget{ref-Allaire_2018}{}
@@
 104:1003--1008.
+
+\hypertarget{ref-ashman2013}{}
+Ashman, T.-L., and G. Arceo-Gómez. 2013. Toward a predictive
+understanding of the fitness costs of heterospecific pollen receipt and
+its importance in co-flowering communities. American Journal of Botany
+100:1061--1070.
 
@@
 accessibility and relatedness. Ecology letters 17:1389--1399.
+
+\hypertarget{ref-engel2003}{}
+Engel, E. C., and R. E. Irwin. 2003. Linking pollinator visitation rate
+and pollen receipt. American Journal of Botany 90:1612--1618.
+
+\hypertarget{ref-inouye1980}{}
+Inouye, D. W. 1980. The terminology of floral larceny. Ecology
+61:1251--1253.
 

### 2018-12-03 Manuscript_draft/Manuscript_draft.Rmd
Writing day

@@
 An increasing number of visits generally correlates with higher chances of fertilization @engel2003.
-However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs @inouye1980 and the quality of pollen that is deposited on the stigma is also highly relevant to the pollination succes @aizen2007.
-Moreover, other less study issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects for the species fitness @morales2008 @ashman2013.
+However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs @inouye1980 and the quality of pollen that is deposit on the stigma is also highly relevant to the pollination succes @aizen2007.
+Moreover, other less study issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects on species fitness @morales2008 @ashman2013.
 
@@
 
-Recent studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashamn2013 @arceo2016.
-A general overview of heterospecific pollen effect is that it can play an important role on species fitness but seems to be context dependent and not always fitness decreased is produced @morales2008.
-There are several traits that are postulated to be highly relevant to this process but the correlation with heterospecific pollen effect remains porrly understood.
-
-Mention relatedness somwhere here.
-
-Moreover, the different methods used make difficult to compare among different experiments.
-For instance many articles do not describe the foreign pollen quantity used to test for effect or how this pollen was applied (Refs).
-The small size of pollen, great environmental variability and population outcrossing rates among others make of this field of study a daunting task and higly unpredictable.
+Recent studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016.
+A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008.
+Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 10 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @montgomery2012 @fang2013.
+Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient.
+@ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect.
+Moreover,  in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the syle on short styled species but not viceversa.
+Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level.
+Interestingly, this trait based question cannot be solved without consider the phylogenetic relatedness of the species.
+A commonly understanding is that close related species will have greater negative impact
 

### 2018-12-03 Manuscript_draft/Manuscript_draft.tex
Writing day

@@
 nectar robbers and pollen thiefs Inouye (1980) and the quality of pollen
-that is deposited on the stigma is also highly relevant to the
-pollination succes Aizen and Harder (2007). Moreover, other less study
-issues in the pollination process are conspecific pollen loss and the
-arrival of foreign pollen which can have important detrimental effects
-for the species fitness Morales and Traveset (2008) Ashman and
-Arceo-Gómez (2013).
+that is deposit on the stigma is also highly relevant to the pollination
+succes Aizen and Harder (2007). Moreover, other less study issues in the
+pollination process are conspecific pollen loss and the arrival of
+foreign pollen which can have important detrimental effects on species
+fitness Morales and Traveset (2008) Ashman and Arceo-Gómez (2013).
 
@@
 Recent studies have advanced in the ecological importance of
-heterospecific pollen effect Morales and Traveset (2008)
-({\textbf{???}}) Arceo-Gómez and Ashman (2016). A general overview of
-heterospecific pollen effect is that it can play an important role on
-species fitness but seems to be context dependent and not always fitness
-decreased is produced Morales and Traveset (2008). There are several
-traits that are postulated to be highly relevant to this process but the
-correlation with heterospecific pollen effect remains to be tested.
-Moreover, the different methods used make difficult to compare among
-different experiments. For instance many articles do not describe the
-foreign pollen quantity used to test for effect or how this pollen was
-applied (Refs). The small size of pollen, great environmental
-variability and population outcrossing rates among others make of this
-field of study a daunting task and higly unpredictable.
+heterospecific pollen effect Morales and Traveset (2008) Ashman and
+Arceo-Gómez (2013) Arceo-Gómez and Ashman (2016). A general overview of
+foreign pollen arrival is that it can play an important role on species
+fitness but seems to be context dependent and not always produce a
+decrease in fitness Morales and Traveset (2008). Part of this
+unpredictability is due to the enormous variability of foreing pollen
+transferred in nature, where levels between 0 and 75 percent are seen,
+but most commonly values ranges between 10 and 20 percent of the total
+pollen load, being the generalist species the ones that receive greater
+loads of heterospecific pollen Montgomery and Rathcke (2012) Fang and
+Huang (2013). Although heterospecific pollen quantity is fundamental to
+understand the outcome of the interaction so is the different traits of
+both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
+postulated the first predictive framework for traits of heterospecific
+pollen effect where traits such as compatibility system and pollen size
+among others should be crucial to understand foreing pollen effect.
+Moreover, in Tong and Huang (2016) a assymetric effect was shown in a
+crossing experiment between 6 species of the genus \emph{Pedicularis}
+where the pollen of long styled species was able to grow the ful length
+of the syle on short styled species but not viceversa. Despite these
+recent caveats, we still lack empirical evidence to affirm what are the
+main traits that drive heterospecific pollen effect for both pollen
+donor and recipient at seed production level. Interestingly, this trait
+based question cannot be solved without consider the phylogenetic
+relatedness of the species. A commonly understanding is that close
+related species will have greater negative impact
 
@@
 
+\hypertarget{ref-fang2013}{}
+Fang, Q., and S.-Q. Huang. 2013. A directed network analysis of
+heterospecific pollen transfer in a biodiverse community. Ecology
+94:1176--1185.
+
 \hypertarget{ref-inouye1980}{}
@@
 61:1251--1253.
+
+\hypertarget{ref-montgomery2012}{}
+Montgomery, B. R., and B. J. Rathcke. 2012. Effects of floral
+restrictiveness and stigma size on heterospecific pollen receipt in a
+prairie community. Oecologia 168:449--458.
 
@@
 computing. R Foundation for Statistical Computing, Vienna, Austria.
+
+\hypertarget{ref-tong2016}{}
+Tong, Z.-Y., and S.-Q. Huang. 2016. Pre-and post-pollination interaction
+between six co-flowering pedicularis species via heterospecific pollen
+transfer. New Phytologist 211:1452--1461.
 

### 2018-12-03 Manuscript_draft/Manuscript_draft.Rmd
last things of today

@@
 
-Recent studies have advanced in the ecological importance of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016.
+Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016.
 A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008.
@@
 @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect.
-Moreover,  in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the syle on short styled species but not viceversa.
+Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the style on short styled species but not viceversa.
 Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level.
-Interestingly, this trait based question cannot be solved without consider the phylogenetic relatedness of the species.
-A commonly understanding is that close related species will have greater negative impact
+Interestingly, this trait based question of effect between a pair of species cannot be solved without consider the phylogenetic relatedness of them.
+A general view is that close related species will have greater negative impact than far related species (REFS).
+Muchas especies inclusos congeneres difieren en traits
+
+Plenty of work have consider crosses between close related species, showing both negative and none effect.
+One of the concerns at seed set level is that in case that species are able to hybridised the negative impact of heterospecific pollen effect is hidden.
 

### 2018-12-03 Manuscript_draft/Manuscript_draft.Rmd
Advances

@@
 
-**Paragraph 1**
+**Paragraph 1** General idea to our concept
 
@@
 
-**Paragraph 2**
+**Paragraph 2** Introducing topic and knowledge gap
 
@@
 Interestingly, this trait based question of effect between a pair of species cannot be solved without consider the phylogenetic relatedness of them.
-A general view is that close related species will have greater negative impact than far related species (REFS).
-Muchas especies inclusos congeneres difieren en traits
+A general view is that close related species will have greater negative impact than far related species (REFS) but few studies test this fact.
+The interaction between close related species have been tradionally overlooked (Refs) but not always the effect of congeners or confamilias can be seen due to these other species are capable of fertilization (Refs.) Combining both traits and phylogenetic relatedness could give a better picture of how both parts interact in the heterospecific pollen process.
 
-Plenty of work have consider crosses between close related species, showing both negative and none effect.
-One of the concerns at seed set level is that in case that species are able to hybridised the negative impact of heterospecific pollen effect is hidden.
+**Paragraph 3** Expanding ideas with examples
 
-**Paragraph 3**
+Examples of articles...
 
@@
 Few studies have tried to understand how relatedness is involved in the hp effect but generally 
-
 Until our knowledge ....
@@
 
-**Paragraph 3**
-
 Traditionally heterospecific pollen effect has focused its attention on different pollen donors as a main driver of different effect.
@@
 
-**Paragraph 4**
+**Paragraph 4** Introducing our experiment
 

### 2018-12-03 Manuscript_draft/Manuscript_draft.tex
Advances

@@
 
-\textbf{Paragraph 1}
+\textbf{Paragraph 1} General idea to our concept
 
@@
 
-\textbf{Paragraph 2}
+\textbf{Paragraph 2} Introducing topic and knowledge gap
 
-Recent studies have advanced in the ecological importance of
+Recent studies have advanced in the ecological understanding of
 heterospecific pollen effect Morales and Traveset (2008) Ashman and
@@
 where the pollen of long styled species was able to grow the ful length
-of the syle on short styled species but not viceversa. Despite these
+of the style on short styled species but not viceversa. Despite these
 recent caveats, we still lack empirical evidence to affirm what are the
@@
 donor and recipient at seed production level. Interestingly, this trait
-based question cannot be solved without consider the phylogenetic
-relatedness of the species. A commonly understanding is that close
-related species will have greater negative impact
+based question of effect between a pair of species cannot be solved
+without consider the phylogenetic relatedness of them. A general view is
+that close related species will have greater negative impact than far
+related species (REFS) but few studies test this fact. The interaction
+between close related species have been tradionally overlooked (Refs)
+but not always the effect of congeners or confamilias can be seen due to
+these other species are capable of fertilization (Refs.) Combining both
+traits and phylogenetic relatedness could give a better picture of how
+both parts interact in the heterospecific pollen process.
 
-\textbf{Paragraph 3}
+\textbf{Paragraph 3} Expanding ideas with examples
+
+Examples of articles\ldots{}
 
@@
 Few studies have tried to understand how relatedness is involved in the
-hp effect but generally
-
-Until our knowledge \ldots{}.
+hp effect but generally Until our knowledge \ldots{}.
 
@@
 
-\textbf{Paragraph 3}
-
 Traditionally heterospecific pollen effect has focused its attention on
@@
 
-\textbf{Paragraph 4}
+\textbf{Paragraph 4} Introducing our experiment
 

### 2018-12-04 Manuscript_draft/Manuscript_draft.Rmd
more writing

@@
 ---
-title: Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits 
+title: working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect
 author:
@@
 Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient.
-@ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect where traits such as compatibility system and pollen size among others should be crucial to understand foreing pollen effect.
-Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the ful length of the style on short styled species but not viceversa.
+@ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect, where different traits such as compatibility system and pollen size among others seems to be crucial to understand foreing pollen effect.
+Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the full length of the style on short styled species but not viceversa.
 Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level.
-Interestingly, this trait based question of effect between a pair of species cannot be solved without consider the phylogenetic relatedness of them.
-A general view is that close related species will have greater negative impact than far related species (REFS) but few studies test this fact.
-The interaction between close related species have been tradionally overlooked (Refs) but not always the effect of congeners or confamilias can be seen due to these other species are capable of fertilization (Refs.) Combining both traits and phylogenetic relatedness could give a better picture of how both parts interact in the heterospecific pollen process.
+Interestingly, to comprehend how this traits interact is also crucial to look at the phylogenetic relatedness of the species.
+There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 for which is predicted to have a greater negative impact as @arceo2016 suggest on their work where invasion status and relatedness is considered.
+Notwithstanding, until our knowledge the effect of related and non-related species remains to be tested explicetely.
 
@@
 
-Examples of articles...
-
-can reduce species fitness (REFS) but seems to be highly contex-dependent. There are hypothesized that some traits can play a crucial role in this species interaction such as stigma type, pollen size,
-
-Mention invasive species in this paragraph
-
-Few studies have tried to understand how relatedness is involved in the hp effect but generally 
-Until our knowledge ....
-
-Rescue from here the useful things:
-
-Invasive species are supposed to have greater negative effect than native ones @arceo2016.
-Although when non-natives species don´t have greater negative effect we still don´t know why.
-For this reason, this ecological question is non a native non native one is a trait based issue that is still to be solved.
-Moreover, the quantity of pollen that integrates in the network can be quite variable ranging from low quatities @bartomeus2008 to intermediate (ref) to high (ref).
-Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs).
-There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect.
-Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect.
-Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.
-
-Explain traits. Put examples
-
-what is closely related? same genus? Just that right, the rest is far related?
+The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
+For this reason, control pollination experiments where hand pollination is applied instead of using pollinators as vectors have simplified this task.
+However, other issues may arise such as
 

### 2018-12-04 Manuscript_draft/Manuscript_draft.tex
more writing

@@
             pdfauthor={},
-            pdftitle={Working title, The impact of heterospecific pollen on plant reproductive success is mediated by phylogenetic distance and floral reproductive traits},
+            pdftitle={working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect},
             colorlinks=true,
@@
 
-\title{Working title, The impact of heterospecific pollen on plant reproductive
-success is mediated by phylogenetic distance and floral reproductive
-traits}
+\title{working title Compatibility system and stygma size of pollen recipient
+as main predictors of heterospecific pollen effect}
 \author{
@@
 \begin{center}
-\huge Working title, The impact of heterospecific pollen on plant reproductive
-success is mediated by phylogenetic distance and floral reproductive
-traits
+\huge working title Compatibility system and stygma size of pollen recipient
+as main predictors of heterospecific pollen effect
 \end{center}
@@
 postulated the first predictive framework for traits of heterospecific
-pollen effect where traits such as compatibility system and pollen size
-among others should be crucial to understand foreing pollen effect.
-Moreover, in Tong and Huang (2016) a assymetric effect was shown in a
-crossing experiment between 6 species of the genus \emph{Pedicularis}
-where the pollen of long styled species was able to grow the ful length
-of the style on short styled species but not viceversa. Despite these
-recent caveats, we still lack empirical evidence to affirm what are the
-main traits that drive heterospecific pollen effect for both pollen
-donor and recipient at seed production level. Interestingly, this trait
-based question of effect between a pair of species cannot be solved
-without consider the phylogenetic relatedness of them. A general view is
-that close related species will have greater negative impact than far
-related species (REFS) but few studies test this fact. The interaction
-between close related species have been tradionally overlooked (Refs)
-but not always the effect of congeners or confamilias can be seen due to
-these other species are capable of fertilization (Refs.) Combining both
-traits and phylogenetic relatedness could give a better picture of how
-both parts interact in the heterospecific pollen process.
+pollen effect, where different traits such as compatibility system and
+pollen size among others seems to be crucial to understand foreing
+pollen effect. Moreover, in Tong and Huang (2016) a assymetric effect
+was shown in a crossing experiment between 6 species of the genus
+\emph{Pedicularis} where the pollen of long styled species was able to
+grow the full length of the style on short styled species but not
+viceversa. Despite these recent caveats, we still lack empirical
+evidence to affirm what are the main traits that drive heterospecific
+pollen effect for both pollen donor and recipient at seed production
+level. Interestingly, to comprehend how this traits interact is also
+crucial to look at the phylogenetic relatedness of the species. There is
+a considerable amount of literature of crosses between close related
+species Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and
+Huang (2016) for which is predicted to have a greater negative impact as
+Arceo-Gómez and Ashman (2016) suggest on their work where invasion
+status and relatedness is considered. Notwithstanding, until our
+knowledge the effect of related and non-related species remains to be
+tested explicetely.
 
@@
 
-Examples of articles\ldots{}
-
-can reduce species fitness (REFS) but seems to be highly
-contex-dependent. There are hypothesized that some traits can play a
-crucial role in this species interaction such as stigma type, pollen
-size,
-
-Mention invasive species in this paragraph
-
-Few studies have tried to understand how relatedness is involved in the
-hp effect but generally Until our knowledge \ldots{}.
-
-Rescue from here the useful things:
-
-Invasive species are supposed to have greater negative effect than
-native ones Arceo-Gómez and Ashman (2016). Although when non-natives
-species don´t have greater negative effect we still don´t know why. For
-this reason, this ecological question is non a native non native one is
-a trait based issue that is still to be solved. Moreover, the quantity
-of pollen that integrates in the network can be quite variable ranging
-from low quatities Bartomeus et al. (2008) to intermediate (ref) to high
-(ref). Moreover, closely related species are supposed to reduce fitness
-in greater effect but the evidence is scarce and based on independent
-studies with different methodologies (Arceo-gomez \& Ashman 2016) or
-studies that just check it with a pair of species that are highly
-related with the aim to understand hybridization costs (refs). There is
-a need to deepen into how relatednes is involve in the costs of
-heterospecific pollen effect. Furthermore, following the conceptual
-trait framework of Ashman and Arceo-Gomez on heterospecific pollen there
-are good theoretical basis for trait effect. Notwithstanding, non
-empirical work has tested how really these traits are involved in
-heterospecific pollen effect.
-
-Explain traits. Put examples
-
-what is closely related? same genus? Just that right, the rest is far
-related?
+The great environmental variability in natural systems make
+heterospecific pollination studies a daunting task. Moreover, when
+pollinators are not used as pollen vectors, to control for standarized
+pollen quantities hand pollination treatments are applied. However,
+different methodologies across studies and different proxys of effect
+difficulty comparisons across studies.
 
@@
 
+\hypertarget{ref-arceo2016can}{}
+Arceo-Gómez, G., R. A. Raguso, and M. A. Geber. 2016. Can plants evolve
+tolerance mechanisms to heterospecific pollen effects? An experimental
+test of the adaptive potential in clarkia species. Oikos 125:718--725.
+
 \hypertarget{ref-ashman2013}{}
@@
 100:1061--1070.
-
-\hypertarget{ref-bartomeus2008}{}
-Bartomeus, I., J. Bosch, and M. Vilà. 2008. High invasive pollen
-transfer, yet low deposition on native stigmas in a carpobrotus-invaded
-community. Annals of Botany 102:417--424.
 
@@
 67:1--48.
+
+\hypertarget{ref-brown2001}{}
+Brown, B. J., and R. J. Mitchell. 2001. Competition for pollination:
+Effects of pollen of an invasive plant on seed set of a native congener.
+Oecologia 129:43--49.
 

### 2018-12-04 Manuscript_draft/Manuscript_draft.Rmd
last edits of today

@@
 A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008.
-Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 10 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @montgomery2012 @fang2013.
+Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 0 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @bartomeus2008 @montgomery2012 @ashman2013 @fang2013.
 Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient.
 @ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect, where different traits such as compatibility system and pollen size among others seems to be crucial to understand foreing pollen effect.
-Moreover, in @tong2016 a assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the full length of the style on short styled species but not viceversa.
+Moreover, in @tong2016 an assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the full length of the style on short styled species but not viceversa.
 Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level.
-Interestingly, to comprehend how this traits interact is also crucial to look at the phylogenetic relatedness of the species.
-There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 for which is predicted to have a greater negative impact as @arceo2016 suggest on their work where invasion status and relatedness is considered.
-Notwithstanding, until our knowledge the effect of related and non-related species remains to be tested explicetely.
+Interestingly, to comprehend how these traits interact is also crucial to look at the phylogenetic relatedness of the species.
+There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species which is a more realistic feature in natural systems due to a less likely niche overlap (REF).
+Although close related species seems to affect greatly species fitness @arceo2016 the effect of heterospecific pollen of far and close related species remains to be tested explicitly.
 
@@
 The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
-For this reason, control pollination experiments where hand pollination is applied instead of using pollinators as vectors have simplified this task.
-However, other issues may arise such as
+For this reason, controlled pollination experiments where hand pollination is applied instead of pollinators as pollen vectors have simplified this task.
+However, other issues may arise such as overestimation of the effect (REFs), standarized methods across studies or lack of descriptive methodology for reproducible work (REFs).
+One of the most common ways to estimate heterospecific pollen effect through hand pollination treatments is by using 50% pollen mixes of conspecific and heterospecific pollen which a realistic proportion (REF) but challenging because of the different pollen properties such as size or hydratation levels (REFS).
 

### 2018-12-04 Manuscript_draft/Manuscript_draft.tex
last edits of today

@@
 transferred in nature, where levels between 0 and 75 percent are seen,
-but most commonly values ranges between 10 and 20 percent of the total
+but most commonly values ranges between 0 and 20 percent of the total
 pollen load, being the generalist species the ones that receive greater
-loads of heterospecific pollen Montgomery and Rathcke (2012) Fang and
-Huang (2013). Although heterospecific pollen quantity is fundamental to
-understand the outcome of the interaction so is the different traits of
-both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
-postulated the first predictive framework for traits of heterospecific
-pollen effect, where different traits such as compatibility system and
-pollen size among others seems to be crucial to understand foreing
-pollen effect. Moreover, in Tong and Huang (2016) a assymetric effect
-was shown in a crossing experiment between 6 species of the genus
-\emph{Pedicularis} where the pollen of long styled species was able to
-grow the full length of the style on short styled species but not
-viceversa. Despite these recent caveats, we still lack empirical
-evidence to affirm what are the main traits that drive heterospecific
-pollen effect for both pollen donor and recipient at seed production
-level. Interestingly, to comprehend how this traits interact is also
-crucial to look at the phylogenetic relatedness of the species. There is
-a considerable amount of literature of crosses between close related
-species Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and
-Huang (2016) for which is predicted to have a greater negative impact as
-Arceo-Gómez and Ashman (2016) suggest on their work where invasion
-status and relatedness is considered. Notwithstanding, until our
-knowledge the effect of related and non-related species remains to be
-tested explicetely.
+loads of heterospecific pollen Bartomeus et al. (2008) Montgomery and
+Rathcke (2012) Ashman and Arceo-Gómez (2013) Fang and Huang (2013).
+Although heterospecific pollen quantity is fundamental to understand the
+outcome of the interaction so is the different traits of both pollen
+donor and recipient. Ashman and Arceo-Gómez (2013) postulated the first
+predictive framework for traits of heterospecific pollen effect, where
+different traits such as compatibility system and pollen size among
+others seems to be crucial to understand foreing pollen effect.
+Moreover, in Tong and Huang (2016) an assymetric effect was shown in a
+crossing experiment between 6 species of the genus \emph{Pedicularis}
+where the pollen of long styled species was able to grow the full length
+of the style on short styled species but not viceversa. Despite these
+recent caveats, we still lack empirical evidence to affirm what are the
+main traits that drive heterospecific pollen effect for both pollen
+donor and recipient at seed production level. Interestingly, to
+comprehend how these traits interact is also crucial to look at the
+phylogenetic relatedness of the species. There is a considerable amount
+of literature of crosses between close related species Brown and
+Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016) but few
+works focused on heterospecific pollen of far related species which is a
+more realistic feature in natural systems due to a less likely niche
+overlap (REF). Although close related species seems to affect greatly
+species fitness Arceo-Gómez and Ashman (2016) the effect of
+heterospecific pollen of far and close related species remains to be
+tested explicitly.
 
@@
 
-The great environmental variability in natural systems make
-heterospecific pollination studies a daunting task. Moreover, when
-pollinators are not used as pollen vectors, to control for standarized
-pollen quantities hand pollination treatments are applied. However,
-different methodologies across studies and different proxys of effect
-difficulty comparisons across studies.
+The great environmental variability in natural systems and complexity of
+floral structures make heterospecific pollination studies a daunting
+task. For this reason, controlled pollination experiments where hand
+pollination is applied instead of pollinators as pollen vectors have
+simplified this task. However, other issues may arise such as
+overestimation of the effect (REFs), standarized methods across studies
+or lack of descriptive methodology for reproducible work (REFs). One of
+the most common ways to estimate heterospecific pollen effect through
+hand pollination treatments is by using 50\% pollen mixes of conspecific
+and heterospecific pollen which a realistic proportion (REF) but
+challenging because of the different pollen properties such as size or
+hydratation levels (REFS).
 
@@
 
+\hypertarget{ref-bartomeus2008}{}
+Bartomeus, I., J. Bosch, and M. Vilà. 2008. High invasive pollen
+transfer, yet low deposition on native stigmas in a carpobrotus-invaded
+community. Annals of Botany 102:417--424.
+
 \hypertarget{ref-bascompte2003}{}

### 2018-12-04 Manuscript_draft/Manuscript_draft.Rmd
last edits

@@
 There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species which is a more realistic feature in natural systems due to a less likely niche overlap (REF).
-Although close related species seems to affect greatly species fitness @arceo2016 the effect of heterospecific pollen of far and close related species remains to be tested explicitly.
+Although close related species seems to affect greatly species fitness @arceo2016 the effect of heterospecific pollen of far and close related species remains to be explored.
 
@@
 The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
-For this reason, controlled pollination experiments where hand pollination is applied instead of pollinators as pollen vectors have simplified this task.
-However, other issues may arise such as overestimation of the effect (REFs), standarized methods across studies or lack of descriptive methodology for reproducible work (REFs).
-One of the most common ways to estimate heterospecific pollen effect through hand pollination treatments is by using 50% pollen mixes of conspecific and heterospecific pollen which a realistic proportion (REF) but challenging because of the different pollen properties such as size or hydratation levels (REFS).
+For this reason, controlled pollination experiments where hand pollination is applied instead of using pollinators as pollen vectors have simplified this task.
+However, other issues may arise such as overestimation of the effect (REFs), different methods across studies or lack of descriptive methodology for reproducible work (REFs).
+One of the most common ways to estimate heterospecific pollen effect through hand pollination treatments is by using 50% pollen mixes of conspecific and heterospecific pollen @arceo2016 (More Refs).
 

### 2018-12-06 Manuscript_draft/Manuscript_draft.Rmd
Fixing methods

@@
 There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species which is a more realistic feature in natural systems due to a less likely niche overlap (REF).
-Although close related species seems to affect greatly species fitness @arceo2016 the effect of heterospecific pollen of far and close related species remains to be explored.
+Although close related species seems to affect greatly species fitness @arceo2016 the importance of heterospecific pollen effect of far and close related species remains to be explored at community level.
 
@@
 
-The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
+Traditionally,
+
+.
 For this reason, controlled pollination experiments where hand pollination is applied instead of using pollinators as pollen vectors have simplified this task.
 However, other issues may arise such as overestimation of the effect (REFs), different methods across studies or lack of descriptive methodology for reproducible work (REFs).
-One of the most common ways to estimate heterospecific pollen effect through hand pollination treatments is by using 50% pollen mixes of conspecific and heterospecific pollen @arceo2016 (More Refs).
+One of the most common ways to estimate heterospecific pollen effect is through hand pollination with mixes of 50% conspecific pollen and 50% heterospecific pollen (REF).
 
@@
 
-Sell well our work: We are the first empirical experiment testig the effect of heterospecific pollen with phylogenetic distance
-
-The great difficulty of working with pollen in a coflowering community make the understanding of heterospecifc pollen effect a real challenge.
-For this reason we have created an artificial co-flowering community in a glasshouse to test the effect with all the possible combinations among them.
-Where we test the folowing hypothesis: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on the relatedness of the species, 3) Does heterospecific pollen effect depend on any floral trait?
-
-Maybe another possible hypothesis to test is the reciprocity of the effect of heterospecifc pollen????
-
-Use the sterile species as a proof of the mechanical interference. Was a mistake but seems cool proof!!!
+The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
+Although plant-pollinator network and pollen network studies can give a first picture of the importance of foreign pollen is necessary to address how its effect is shaped with both traits and relatedness of the species.
+For this reason, in this study we have created an artificial co-flowering community with 10 species belonging to three different families where we try to test the following questions: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on the relatedness of the species, 3) Does heterospecific pollen effect depend on any floral trait?
 
 # METHODS
-
-[comment starts]()
-Glasshouse trial
-•	Species selected and why – how you made them co-flower
-•	Give details of sources and planting seeds, growth medium in pots, temperature and light details
-•	Hand crosses and how you did them, how you measured seed set over time.
-•	Analyses of data – standardization, means, matrices etc.
-
-•	Analyses and technical difficulties: We calculated effect size by subtracting the mean of the cross pollinated seed set by the mean effect of the HP pollen (explain exactly what figures you used to calculate this) – check with liam about potentially using missing values analyses for the species we don’t have?
-
-Check that the method is working well to prove that your crosses were close to 50% results in SI i.e not all mixes were 50/50% and we have now counted all the pollen to make this a quantitative variable.
-We also need to factor in the point that we have different total abundances of pollen across our treatments, irrespective of ratios.
-To what extent are differences in the ratios of pollen applied by hand across different plant families influenced by plant traits such as pollen size, morphology and stigma surface type?
-
-Results – may need to include amount of pollen in models as random factor- prefill matrix with missing value analyse for the species you don’t have.  
-Question 1: how do different pollination treatments (100% HP, 50% HP, self and cross ) impact HP pollen across different plant families?
-Even with 100% HP one (or more species?) still produced seed set.
-
-Result Effect size of Seed set ~ phylogenetic distance relationship
-We found that the variation ?/ mean effect size of seed set is positively related to phylogenetic distance.
-This means the more unrelated the species are, the greater the negative impact of heterospecific pollen (give stats  effect size i.e.
-Procrustes, X = 0.35; P = 0.03)
-
-Question 2 : what are the main traits impacting HP impacts? (compatibility system, pollen size, stigma surface, wet/dry stigma, length of style etc.
-
-Effect size of seed set ~ floral traits/ reproductive plant traits
-We found that the three best terms to explain the variation in seed set is pollen/ovule ratio, stigma width and style length (Stats effect size i.e. X = 0.39, P = 0.02).  
-Need to provide correlation matrix for all traits just for 10 species
-Show both ways to present this.
-Which particular traits do you find significant effects for?
-Show this and give stats.
-Present plot for each trait and effect size
-
-[comment finishes]()
 
@@
 
-Two types of evolutive distances were calculated with MEGA7 thow kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)
+Two types of evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)
 
@@
 
-Several traits of the ten species were measured.
-Pollen per anther was counted, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length.
+The traits measured for each species were pollen per anther, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length.
 Moreover stigma type was tested.
-Self-incompatibility was
+Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer.
+Previously anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds.
+Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
+The different morphometrical traits were measured with XXXX.
+Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination
 

### 2018-12-06 Manuscript_draft/Manuscript_draft.tex
Fixing methods

@@
 overlap (REF). Although close related species seems to affect greatly
-species fitness Arceo-Gómez and Ashman (2016) the effect of
-heterospecific pollen of far and close related species remains to be
-tested explicitly.
+species fitness Arceo-Gómez and Ashman (2016) the importance of
+heterospecific pollen effect of far and close related species remains to
+be explored at community level.
 
@@
 
-The great environmental variability in natural systems and complexity of
-floral structures make heterospecific pollination studies a daunting
-task. For this reason, controlled pollination experiments where hand
-pollination is applied instead of pollinators as pollen vectors have
-simplified this task. However, other issues may arise such as
-overestimation of the effect (REFs), standarized methods across studies
-or lack of descriptive methodology for reproducible work (REFs). One of
-the most common ways to estimate heterospecific pollen effect through
-hand pollination treatments is by using 50\% pollen mixes of conspecific
-and heterospecific pollen which a realistic proportion (REF) but
-challenging because of the different pollen properties such as size or
-hydratation levels (REFS).
+Traditionally,
+
+. For this reason, controlled pollination experiments where hand
+pollination is applied instead of using pollinators as pollen vectors
+have simplified this task. However, other issues may arise such as
+overestimation of the effect (REFs), different methods across studies or
+lack of descriptive methodology for reproducible work (REFs). One of the
+most common ways to estimate heterospecific pollen effect is through
+hand pollination with mixes of 50\% conspecific pollen and 50\%
+heterospecific pollen (REF).
 
@@
 
-Sell well our work: We are the first empirical experiment testig the
-effect of heterospecific pollen with phylogenetic distance
-
-The great difficulty of working with pollen in a coflowering community
-make the understanding of heterospecifc pollen effect a real challenge.
-For this reason we have created an artificial co-flowering community in
-a glasshouse to test the effect with all the possible combinations among
-them. Where we test the folowing hypothesis: 1) Does heterospecific
-pollen reduce seed set, if so, 2) Does heterospecific pollen effect
-depend on the relatedness of the species, 3) Does heterospecific pollen
-effect depend on any floral trait?
-
-Maybe another possible hypothesis to test is the reciprocity of the
-effect of heterospecifc pollen????
-
-Use the sterile species as a proof of the mechanical interference. Was a
-mistake but seems cool proof!!!
+The great environmental variability in natural systems and complexity of
+floral structures make heterospecific pollination studies a daunting
+task. Although plant-pollinator network and pollen network studies can
+give a first picture of the importance of foreign pollen is necessary to
+address how its effect is shaped with both traits and relatedness of the
+species. For this reason, in this study we have created an artificial
+co-flowering community with 10 species belonging to three different
+families where we try to test the following questions: 1) Does
+heterospecific pollen reduce seed set, if so, 2) Does heterospecific
+pollen effect depend on the relatedness of the species, 3) Does
+heterospecific pollen effect depend on any floral trait?
 
 \section{METHODS}\label{methods}
-
-\href{}{comment starts} Glasshouse trial • Species selected and why --
-how you made them co-flower • Give details of sources and planting
-seeds, growth medium in pots, temperature and light details • Hand
-crosses and how you did them, how you measured seed set over time. •
-Analyses of data -- standardization, means, matrices etc.
-
-• Analyses and technical difficulties: We calculated effect size by
-subtracting the mean of the cross pollinated seed set by the mean effect
-of the HP pollen (explain exactly what figures you used to calculate
-this) -- check with liam about potentially using missing values analyses
-for the species we don't have?
-
-Check that the method is working well to prove that your crosses were
-close to 50\% results in SI i.e not all mixes were 50/50\% and we have
-now counted all the pollen to make this a quantitative variable. We also
-need to factor in the point that we have different total abundances of
-pollen across our treatments, irrespective of ratios. To what extent are
-differences in the ratios of pollen applied by hand across different
-plant families influenced by plant traits such as pollen size,
-morphology and stigma surface type?
-
-Results -- may need to include amount of pollen in models as random
-factor- prefill matrix with missing value analyse for the species you
-don't have.\\
-Question 1: how do different pollination treatments (100\% HP, 50\% HP,
-self and cross ) impact HP pollen across different plant families? Even
-with 100\% HP one (or more species?) still produced seed set.
-
-Result Effect size of Seed set \textasciitilde{} phylogenetic distance
-relationship We found that the variation ?/ mean effect size of seed set
-is positively related to phylogenetic distance. This means the more
-unrelated the species are, the greater the negative impact of
-heterospecific pollen (give stats effect size i.e.~Procrustes, X = 0.35;
-P = 0.03)
-
-Question 2 : what are the main traits impacting HP impacts?
-(compatibility system, pollen size, stigma surface, wet/dry stigma,
-length of style etc.
-
-Effect size of seed set \textasciitilde{} floral traits/ reproductive
-plant traits We found that the three best terms to explain the variation
-in seed set is pollen/ovule ratio, stigma width and style length (Stats
-effect size i.e.~X = 0.39, P = 0.02).\\
-Need to provide correlation matrix for all traits just for 10 species
-Show both ways to present this. Which particular traits do you find
-significant effects for? Show this and give stats. Present plot for each
-trait and effect size
-
-\href{}{comment finishes}
 
@@
 
-Two types of evolutive distances were calculated with MEGA7 thow kinds
-of markers: 1) Internal transcribed spacer (ITS) and 2)
+Two types of evolutive distances were calculated with MEGA7 for two
+kinds of markers: 1) Internal transcribed spacer (ITS) and 2)
 ribulose-bisphosphate carboxylase (RBCL)
@@
 
-Several traits of the ten species were measured. Pollen per anther was
-counted, number of ovules, stigma width and length and stigmatic area,
-style width and length, ovary width and length. Moreover stigma type was
-tested. Self-incompatibility was
+The traits measured for each species were pollen per anther, number of
+ovules, stigma width and length and stigmatic area, style width and
+length, ovary width and length. Moreover stigma type was tested. Pollen
+was counted for 20 anthers of each species with 4 replicates per sample
+with an hemocytometer. Previously anthers were squashed on a known
+solution with the pippete tip and homogeneize with a vortex for 30
+seconds. Ovule number was counted with the help of an stereomicroscope
+and a small grid over a petri dish from 15 randomly selected flowers.
+The different morphometrical traits were measured with XXXX. Levels of
+self incompatibility were estimated by dividing the the fruit set of
+hand self pollination by hand cross pollination
 

### 2018-12-07 Manuscript_draft/Manuscript_draft.Rmd
paragraph 3

@@
 Interestingly, to comprehend how these traits interact is also crucial to look at the phylogenetic relatedness of the species.
-There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species which is a more realistic feature in natural systems due to a less likely niche overlap (REF).
-Although close related species seems to affect greatly species fitness @arceo2016 the importance of heterospecific pollen effect of far and close related species remains to be explored at community level.
+There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species.
+Although the effect of close related species is predicted to be greater @ashman2013 the presence of pollen of non related species on multiple species @arceo2016 and the higher chances to coexist with a species that has less niche overlap (Ref) make foreign pollen from far related species also an important subject of study in order to understand the importance of heterospecific pollen in natural systems.
+Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored.
 
@@
 
-Traditionally,
-
-.
-For this reason, controlled pollination experiments where hand pollination is applied instead of using pollinators as pollen vectors have simplified this task.
-However, other issues may arise such as overestimation of the effect (REFs), different methods across studies or lack of descriptive methodology for reproducible work (REFs).
-One of the most common ways to estimate heterospecific pollen effect is through hand pollination with mixes of 50% conspecific pollen and 50% heterospecific pollen (REF).
-
-I would like to add that the experiments focus on two proxies of effect prezygotic and postzygotic.
-Why focus on postzygotic?
-Is the final stage where we can see the effect.
-Further studies should also study germination rates.
-
-Traditionally heterospecific pollen effect has focused its attention on different pollen donors as a main driver of different effect.
-However in this article we want to emphasize that this is true for the cases that the species are higly close related where pollen recognition can take place (eg hybridization) but not when this pollen is from less closely related species which the main driver of effect is determined by the reproductive biology of the female part of the plant(compatibility system, stigma type, stigma area and number of ovules).
+Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species.
+The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect (REF).
+Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
+Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REFS).
 
@@
 The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
+Moreover, variation in sampling effort have been shown to be determinant to characterize pollen transfer interactions @arceo2018.
 Although plant-pollinator network and pollen network studies can give a first picture of the importance of foreign pollen is necessary to address how its effect is shaped with both traits and relatedness of the species.

### 2018-12-07 Manuscript_draft/Manuscript_draft.tex
paragraph 3

@@
 Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016) but few
-works focused on heterospecific pollen of far related species which is a
-more realistic feature in natural systems due to a less likely niche
-overlap (REF). Although close related species seems to affect greatly
-species fitness Arceo-Gómez and Ashman (2016) the importance of
-heterospecific pollen effect of far and close related species remains to
-be explored at community level.
+works focused on heterospecific pollen of far related species. Although
+the effect of close related species is predicted to be greater Ashman
+and Arceo-Gómez (2013) the presence of pollen of non related species on
+multiple species Arceo-Gómez and Ashman (2016) and the higher chances to
+coexist with a species that has less niche overlap (Ref) make foreign
+pollen from far related species also an important subject of study in
+order to understand the importance of heterospecific pollen in natural
+systems. Notwithstanding, the effect of heterospecific pollen of far and
+close related species at community level remains to be explored.
 
@@
 
-Traditionally,
-
-. For this reason, controlled pollination experiments where hand
-pollination is applied instead of using pollinators as pollen vectors
-have simplified this task. However, other issues may arise such as
-overestimation of the effect (REFs), different methods across studies or
-lack of descriptive methodology for reproducible work (REFs). One of the
-most common ways to estimate heterospecific pollen effect is through
-hand pollination with mixes of 50\% conspecific pollen and 50\%
-heterospecific pollen (REF).
-
-I would like to add that the experiments focus on two proxies of effect
-prezygotic and postzygotic. Why focus on postzygotic? Is the final stage
-where we can see the effect. Further studies should also study
-germination rates.
-
-Traditionally heterospecific pollen effect has focused its attention on
-different pollen donors as a main driver of different effect. However in
-this article we want to emphasize that this is true for the cases that
-the species are higly close related where pollen recognition can take
-place (eg hybridization) but not when this pollen is from less closely
-related species which the main driver of effect is determined by the
-reproductive biology of the female part of the plant(compatibility
-system, stigma type, stigma area and number of ovules).
+Interestingly, incompatibility system seems to play an important role in
+foreign pollen effect where species that are self incompatible would
+have stronger barriers towards heterospecific pollen than self
+compatible species. The type of incompatibility, sporophytic or
+gametophytic is related with the place of pollen recognition where the
+former take place at the sitgma level and the latter occurs within the
+style, this last late acting pollen recognition mechanism is associated
+with greater negative effect (REF). Remarkably, there is a great
+variability in mating systems across populations Whitehead et al. (2018)
+and therefore predict an effect of foreign pollen is a bit obscured by
+the variability within species, however species that are strong selfers
+or strong outcrossers have less variablity in mating systems and
+predictions of effect could be more realistic (see figure 1 from
+Whitehead et al. (2018)).
 
@@
 floral structures make heterospecific pollination studies a daunting
-task. Although plant-pollinator network and pollen network studies can
-give a first picture of the importance of foreign pollen is necessary to
-address how its effect is shaped with both traits and relatedness of the
-species. For this reason, in this study we have created an artificial
-co-flowering community with 10 species belonging to three different
-families where we try to test the following questions: 1) Does
-heterospecific pollen reduce seed set, if so, 2) Does heterospecific
-pollen effect depend on the relatedness of the species, 3) Does
-heterospecific pollen effect depend on any floral trait?
+task. Moreover, variation in sampling effort have been shown to be
+determinant to characterize pollen transfer interactions Arceo-Gómez et
+al. (2018). Although plant-pollinator network and pollen network studies
+can give a first picture of the importance of foreign pollen is
+necessary to address how its effect is shaped with both traits and
+relatedness of the species. For this reason, in this study we have
+created an artificial co-flowering community with 10 species belonging
+to three different families where we try to test the following
+questions: 1) Does heterospecific pollen reduce seed set, if so, 2) Does
+heterospecific pollen effect depend on the relatedness of the species,
+3) Does heterospecific pollen effect depend on any floral trait?
 
@@
 
+\hypertarget{ref-arceo2018}{}
+Arceo-Gómez, G., C. Alonso, T.-L. Ashman, and V. Parra-Tabla. 2018.
+Variation in sampling effort affects the observed richness of
+plant--plant interactions via heterospecific pollen transfer:
+Implications for interpretation of pollen transfer networks. American
+journal of botany 105:1601--1608.
+
 \hypertarget{ref-arceo2016}{}
@@
 
+\hypertarget{ref-whitehead2018}{}
+Whitehead, M. R., R. Lanfear, R. J. Mitchell, and J. D. Karron. 2018.
+Plant mating systems often vary widely among populations. Frontiers in
+Ecology and Evolution 6:38.
+
 \hypertarget{ref-Xie_2014}{}

### 2018-12-07 Manuscript_draft/Manuscript_draft.Rmd
Last changes of today...

@@
 
-Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species.
-The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect (REF).
+Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species (REF).
+The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @ashman2013.
 Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
-Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REFS).
+Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF).
+Selfer species would have a reduction of herkogamy (REF), less pollen production per ovule (REF) and therefore less likely to contribute in exporting pollen in the community.
+Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
+Example with pollen here.
 

### 2018-12-08 Manuscript_draft/Manuscript_draft.Rmd
Some edits

--- 2018-12-07 Manuscript_draft/Manuscript_draft.Rmd
@@
 A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008.
-Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 0 and 20 percent of the total pollen load, being the generalist species the ones that receive greater loads of heterospecific pollen @bartomeus2008 @montgomery2012 @ashman2013 @fang2013.
+Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012 @ashman2013 @fang2013, being the generalist species the ones that receive greater loads of heterospecific pollen @fang2013.
+Surprisingly, this low ranges of heterospecific pollen have been shown to decrease fitness greatly @thomson1982.
 Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient.
@@
 Although the effect of close related species is predicted to be greater @ashman2013 the presence of pollen of non related species on multiple species @arceo2016 and the higher chances to coexist with a species that has less niche overlap (Ref) make foreign pollen from far related species also an important subject of study in order to understand the importance of heterospecific pollen in natural systems.
-Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored.
+Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.
 
@@
 
-Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species.
-The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect (REF).
+Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species @ashman2013.
+The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @barrett1999.
 Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
-Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REFS).
+Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF).
+Selfer species would have a reduction of herkogamy (REF), less pollen production per ovule (REF) and therefore less likely to contribute in exporting pollen in the community.
+Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
+Example with pollen here.
 

### 2018-12-08 Manuscript_draft/Manuscript_draft.tex
Some edits

@@
 but most commonly values ranges between 0 and 20 percent of the total
-pollen load, being the generalist species the ones that receive greater
-loads of heterospecific pollen Bartomeus et al. (2008) Montgomery and
-Rathcke (2012) Ashman and Arceo-Gómez (2013) Fang and Huang (2013).
-Although heterospecific pollen quantity is fundamental to understand the
-outcome of the interaction so is the different traits of both pollen
-donor and recipient. Ashman and Arceo-Gómez (2013) postulated the first
-predictive framework for traits of heterospecific pollen effect, where
-different traits such as compatibility system and pollen size among
-others seems to be crucial to understand foreing pollen effect.
-Moreover, in Tong and Huang (2016) an assymetric effect was shown in a
-crossing experiment between 6 species of the genus \emph{Pedicularis}
-where the pollen of long styled species was able to grow the full length
-of the style on short styled species but not viceversa. Despite these
-recent caveats, we still lack empirical evidence to affirm what are the
-main traits that drive heterospecific pollen effect for both pollen
-donor and recipient at seed production level. Interestingly, to
-comprehend how these traits interact is also crucial to look at the
-phylogenetic relatedness of the species. There is a considerable amount
-of literature of crosses between close related species Brown and
-Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016) but few
-works focused on heterospecific pollen of far related species. Although
-the effect of close related species is predicted to be greater Ashman
-and Arceo-Gómez (2013) the presence of pollen of non related species on
-multiple species Arceo-Gómez and Ashman (2016) and the higher chances to
-coexist with a species that has less niche overlap (Ref) make foreign
-pollen from far related species also an important subject of study in
-order to understand the importance of heterospecific pollen in natural
-systems. Notwithstanding, the effect of heterospecific pollen of far and
-close related species at community level remains to be explored.
+pollen load Bartomeus et al. (2008) Montgomery and Rathcke (2012) Ashman
+and Arceo-Gómez (2013) Fang and Huang (2013), being the generalist
+species the ones that receive greater loads of heterospecific pollen
+Fang and Huang (2013). Surprisingly, this low ranges of heterospecific
+pollen have been shown to decrease fitness greatly Thomson et al.
+(1982). Although heterospecific pollen quantity is fundamental to
+understand the outcome of the interaction so is the different traits of
+both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
+postulated the first predictive framework for traits of heterospecific
+pollen effect, where different traits such as compatibility system and
+pollen size among others seems to be crucial to understand foreing
+pollen effect. Moreover, in Tong and Huang (2016) an assymetric effect
+was shown in a crossing experiment between 6 species of the genus
+\emph{Pedicularis} where the pollen of long styled species was able to
+grow the full length of the style on short styled species but not
+viceversa. Despite these recent caveats, we still lack empirical
+evidence to affirm what are the main traits that drive heterospecific
+pollen effect for both pollen donor and recipient at seed production
+level. Interestingly, to comprehend how these traits interact is also
+crucial to look at the phylogenetic relatedness of the species. There is
+a considerable amount of literature of crosses between close related
+species Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and
+Huang (2016) but few works focused on heterospecific pollen of far
+related species. Although the effect of close related species is
+predicted to be greater Ashman and Arceo-Gómez (2013) the presence of
+pollen of non related species on multiple species Arceo-Gómez and Ashman
+(2016) and the higher chances to coexist with a species that has less
+niche overlap (Ref) make foreign pollen from far related species also an
+important subject of study in order to understand the importance of
+heterospecific pollen in natural systems. Notwithstanding, the effect of
+heterospecific pollen of far and close related species at community
+level remains to be explored beyond single pairwise interactions.
 
@@
 have stronger barriers towards heterospecific pollen than self
-compatible species. The type of incompatibility, sporophytic or
-gametophytic is related with the place of pollen recognition where the
-former take place at the sitgma level and the latter occurs within the
-style, this last late acting pollen recognition mechanism is associated
-with greater negative effect (REF). Remarkably, there is a great
-variability in mating systems across populations Whitehead et al. (2018)
-and therefore predict an effect of foreign pollen is a bit obscured by
-the variability within species, however species that are strong selfers
-or strong outcrossers have less variablity in mating systems and
-predictions of effect could be more realistic (see figure 1 from
-Whitehead et al. (2018)).
+compatible species Ashman and Arceo-Gómez (2013). The type of
+incompatibility, sporophytic or gametophytic is related with the place
+of pollen recognition where the former take place at the sitgma level
+and the latter occurs within the style, this last late acting pollen
+recognition mechanism is associated with greater negative effect
+({\textbf{???}}). Remarkably, there is a great variability in mating
+systems across populations Whitehead et al. (2018) and therefore predict
+an effect of foreign pollen is a bit obscured by the variability within
+species, however species that are strong selfers or strong outcrossers
+have less variablity in mating systems and predictions of effect could
+be more realistic (see figure 1 from Whitehead et al. (2018)). Moreover,
+other traits such as number of pollen grains per flower and number of
+ovules have been tradittionally associated with the type of
+incompatibility system where species with higher pollen ovule ratios are
+predicted to be xenogamous and species with low pollen ovule ratios
+autogamous (REF). Selfer species would have a reduction of herkogamy
+(REF), less pollen production per ovule (REF) and therefore less likely
+to contribute in exporting pollen in the community. Other morphological
+traits, like stigma size can be determinant for the total pollen quatity
+that a stigma can receive and therefore related to do that pollen size
+would also play an important role. Example with pollen here.
 
@@
 
+\hypertarget{ref-thomson1982}{}
+Thomson, J. D., B. J. Andrews, and R. Plowright. 1982. The effect of a
+foreign pollen on ovule development in diervilla lonicera
+(caprifoliaceae). New Phytologist 90:777--783.
+
 \hypertarget{ref-tong2016}{}

### 2018-12-08 Manuscript_draft/Manuscript_draft.Rmd
Some edits

@@
 Interestingly, to comprehend how these traits interact is also crucial to look at the phylogenetic relatedness of the species.
-There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species.
+There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species @thomson1982 @galen1989 @neiland1999 which also show a noteworthy fitness decrease.
 Although the effect of close related species is predicted to be greater @ashman2013 the presence of pollen of non related species on multiple species @arceo2016 and the higher chances to coexist with a species that has less niche overlap (Ref) make foreign pollen from far related species also an important subject of study in order to understand the importance of heterospecific pollen in natural systems.
@@
 Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species @ashman2013.
-The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @barrett1999.
+The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @barrett1988.
 Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
@@
 
-Brown and Mitchell 2001 could be a good paper to explain why we pick seed set as a proxy and not fruit set. We cannot see changes on it, losing information with it.
+**Table 1**
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))
+
+Genus <- c("Brassica", "Brassica", "Eruca", "Sinapis", "Ipomoea", "Ipomoea", "Capsicum", "Petunia", "Solanum", "Solanum")
+
+Species <- c("Brassica rapa", "Brassica oleracea", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+
+table<- data.frame(Family, Genus, Species)
+kable(table, format="markdown")
+```
 
@@
 Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10).
-Seed set was the proxy of effect (see Brown and Mitchell 2001, for differences in effect between seed set and fruit set) and "pollen tubes".
+Therefore, 180 different combinations were perform with N=10.
+Seed set was the proxy of effect for all our teratments.
 Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10).
@@
 
-**Evolutive distance**
-
-Two types of evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)
-
-**Traits**
+**Traits and evolutive distance**
 
@@
 The different morphometrical traits were measured with XXXX.
-Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination
+Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination.
+Moreover, two types of evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)
 
-```{r model, echo = FALSE, eval = FALSE}
-model <- lm(y ~ x)
-```
+**Analysis**
 
@@
 # RESULTS
+
+Heterospecific pollen produced fitness for xxx cases.
 

### 2018-12-08 Manuscript_draft/Manuscript_draft.tex
Some edits

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs}
 \ifxetex
@@
 Huang (2016) but few works focused on heterospecific pollen of far
-related species. Although the effect of close related species is
-predicted to be greater Ashman and Arceo-Gómez (2013) the presence of
-pollen of non related species on multiple species Arceo-Gómez and Ashman
-(2016) and the higher chances to coexist with a species that has less
-niche overlap (Ref) make foreign pollen from far related species also an
-important subject of study in order to understand the importance of
-heterospecific pollen in natural systems. Notwithstanding, the effect of
-heterospecific pollen of far and close related species at community
-level remains to be explored beyond single pairwise interactions.
+related species Thomson et al. (1982) Galen and Gregory (1989) Neiland
+and Wilcock (1999) which also show a noteworthy fitness decrease.
+Although the effect of close related species is predicted to be greater
+Ashman and Arceo-Gómez (2013) the presence of pollen of non related
+species on multiple species Arceo-Gómez and Ashman (2016) and the higher
+chances to coexist with a species that has less niche overlap (Ref) make
+foreign pollen from far related species also an important subject of
+study in order to understand the importance of heterospecific pollen in
+natural systems. Notwithstanding, the effect of heterospecific pollen of
+far and close related species at community level remains to be explored
+beyond single pairwise interactions.
 
@@
 and the latter occurs within the style, this last late acting pollen
-recognition mechanism is associated with greater negative effect
-({\textbf{???}}). Remarkably, there is a great variability in mating
-systems across populations Whitehead et al. (2018) and therefore predict
-an effect of foreign pollen is a bit obscured by the variability within
+recognition mechanism is associated with greater negative effect Barrett
+(1988). Remarkably, there is a great variability in mating systems
+across populations Whitehead et al. (2018) and therefore predict an
+effect of foreign pollen is a bit obscured by the variability within
 species, however species that are strong selfers or strong outcrossers
@@
 
-Brown and Mitchell 2001 could be a good paper to explain why we pick
-seed set as a proxy and not fruit set. We cannot see changes on it,
-losing information with it.
+\textbf{Table 1}
+
+\begin{longtable}[]{@{}lll@{}}
+\toprule
+Family & Genus & Species\tabularnewline
+\midrule
+\endhead
+Brassicaceae & Brassica & Brassica rapa\tabularnewline
+Brassicaceae & Brassica & Brassica oleracea\tabularnewline
+Brassicaceae & Eruca & Eruca versicaria\tabularnewline
+Brassicaceae & Sinapis & Sinapis alba\tabularnewline
+Convolvulaceae & Ipomoea & Ipomoea aquatica\tabularnewline
+Convolvulaceae & Ipomoea & Ipomoea purpurea\tabularnewline
+Solanaceae & Capsicum & Capsicum annuum\tabularnewline
+Solanaceae & Petunia & Petunia integrifolia\tabularnewline
+Solanaceae & Solanum & Solanum lycopersicum\tabularnewline
+Solanaceae & Solanum & Solanum melongena\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 with 50\% conspecific pollen and 50\% heterospecific pollen and a second
-one with 100\% foreign pollen (N=10). Seed set was the proxy of effect
-(see Brown and Mitchell 2001, for differences in effect between seed set
-and fruit set) and ``pollen tubes''. Moreover, hand cross pollination,
-hand self pollination, apomixis (bagged emasculated flowers) and natural
-selfing were tested (N=10). Flowers were emasculated the day prior
-anthesis and hand pollinated next day with a toothpick. Had-pollination
-was realized with 3-4 gentle touches on the surface of the stigma. The
-mixes of pollen were performed on an eppendorf based on the pollen
-counts maded with Neubaeur chamber (each anther was counted 4 times for
-20 different anthers per species).
+one with 100\% foreign pollen (N=10). Therefore, 180 different
+combinations were perform with N=10. Seed set was the proxy of effect
+for all our teratments. Moreover, hand cross pollination, hand self
+pollination, apomixis (bagged emasculated flowers) and natural selfing
+were tested (N=10). Flowers were emasculated the day prior anthesis and
+hand pollinated next day with a toothpick. Had-pollination was realized
+with 3-4 gentle touches on the surface of the stigma. The mixes of
+pollen were performed on an eppendorf based on the pollen counts maded
+with Neubaeur chamber (each anther was counted 4 times for 20 different
+anthers per species).
 
-\textbf{Evolutive distance}
-
-Two types of evolutive distances were calculated with MEGA7 for two
-kinds of markers: 1) Internal transcribed spacer (ITS) and 2)
-ribulose-bisphosphate carboxylase (RBCL)
-
-\textbf{Traits}
+\textbf{Traits and evolutive distance}
 
@@
 self incompatibility were estimated by dividing the the fruit set of
-hand self pollination by hand cross pollination
+hand self pollination by hand cross pollination. Moreover, two types of
+evolutive distances were calculated with MEGA7 for two kinds of markers:
+1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate
+carboxylase (RBCL)
+
+\textbf{Analysis}
 
@@
 \section{RESULTS}\label{results}
+
+Heterospecific pollen produced fitness for xxx cases.
 
@@
 
+\hypertarget{ref-barrett1988}{}
+Barrett, S. C. 1988. The evolution, maintenance, and loss of
+self-incompatibility systems. Plant reproductive ecology: patterns and
+strategies:98--124.
+
 \hypertarget{ref-bartomeus2008}{}
@@
 
+\hypertarget{ref-galen1989}{}
+Galen, C., and T. Gregory. 1989. Interspecific pollen transfer as a
+mechanism of competition: Consequences of foreign pollen contamination
+for seed set in the alpine wildflower, polemonium viscosum. Oecologia
+81:120--123.
+
 \hypertarget{ref-inouye1980}{}
@@
 Reviews in Plant Sciences 27:221--238.
+
+\hypertarget{ref-neiland1999}{}
+Neiland, M., and C. Wilcock. 1999. The presence of heterospecific pollen
+on stigmas of nectariferous and nectarless orchids and its consequences
+for their reproductive success. Protoplasma 208:65--75.
 

### 2018-12-08 Manuscript_draft/Manuscript_draft.Rmd
Calculate compatibility or leave as selfing rate

@@
 
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("myEnv.RData")
+library(nlme)
+library(lme4)
+library(ggplot2)
+Model.2 <- lmer(hp_effect ~ compatibility + (1 | Focal), data = ALL)
+ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
+  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
+  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(Model.2))))
+
+```
+
 # DISCUSSION

### 2018-12-08 Scripts/Analysis_mantel_test.R

@@ -963,6 +963,8 @@ plot(model2)
 
 #Lets add new column with a seq of the length of the dataset and i use that as random effect (different individuals)
 
+#save.image(file='Manuscript_draft/myEnv.RData')
+
 ALL$indv<- seq.int(nrow(ALL))
 model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
 summary(model2)

### 2018-12-09 Manuscript_draft/Manuscript_draft.Rmd
some edits, keep with results later

--- 2018-12-08 Manuscript_draft/Manuscript_draft.Rmd
@@
 Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF).
-Selfer species would have a reduction of herkogamy (REF), less pollen production per ovule (REF) and therefore less likely to contribute in exporting pollen in the community.
+Selfer species would have a reduction of herkogamy (REF) and less pollen production per ovule (REF) which can be interpretated as a reduction of pollen expoorted into the community.
 Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
@@
 Although plant-pollinator network and pollen network studies can give a first picture of the importance of foreign pollen is necessary to address how its effect is shaped with both traits and relatedness of the species.
-For this reason, in this study we have created an artificial co-flowering community with 10 species belonging to three different families where we try to test the following questions: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on the relatedness of the species, 3) Does heterospecific pollen effect depend on any floral trait?
+For this reason, in this study we have created an artificial co-flowering community with 10 species belonging to three different families with different traits where we try to test the following questions: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on any floral trait?
+3) Does heterospecific pollen effect depend on the relatedness of the species.
 
@@
 Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
-Had-pollination was realized with 3-4 gentle touches on the surface of the stigma.
+Hand-pollination was realized with 3-4 gentle touches on the stigma surface.
 The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).
+In order to confirm that the treatments applied were 50-50 percent pollen, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
 
@@
 These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages.
-All the multilevel models were fitted with `lme4` `r citep(citation("lme4"))`.
+To test the effect of heterospecific pollen, we substracted the to seed set of hand cross pollination the seed set of the heterospecific pollen treatments.
+Therefore, small values mean low effect and viceversa.
+To be able to compare among species seed set was previosly scaled for all species.
+In order to see relations between hetereospecific pollen effect and traits we performed Mantel test between the matrix of effect and the distance matrix of each trait (euclidean distances).
+Moreover, Mantel test was also conducted between heterospecific pollen effect and phylogenetic distance.
+
+\newpage
 
@@
 Heterospecific pollen produced fitness for xxx cases.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=5, fig.cap="The effect of heterospecific pollen (scaled see set) is represented in function of the compatibility system (self/cross*100) for the the different species.
+Each coulored dot represents the interaction of a focal species with a different pollen donor."}
+load("myEnv.RData")
+library(nlme)
+library(lme4)
+library(ggplot2)
+library(cowplot)
+model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
+ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
+  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
+  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(model2))))+theme_cowplot()
+
+```
 

### 2018-12-09 Manuscript_draft/Manuscript_draft.tex
Calculate compatibility or leave as selfing rate
some edits, keep with results later

@@
 \usepackage{longtable,booktabs}
+\usepackage{graphicx}
+% Redefine \includegraphics so that, unless explicit options are
+% given, the image width will not exceed the width of the page.
+% Images get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\ScaleIfNeeded{%
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+\let\Oldincludegraphics\includegraphics
+{%
+ \catcode`\@=11\relax%
+ \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
+}%
 \ifxetex
@@
 were tested (N=10). Flowers were emasculated the day prior anthesis and
-hand pollinated next day with a toothpick. Had-pollination was realized
-with 3-4 gentle touches on the surface of the stigma. The mixes of
-pollen were performed on an eppendorf based on the pollen counts maded
-with Neubaeur chamber (each anther was counted 4 times for 20 different
-anthers per species).
+hand pollinated next day with a toothpick. HaNd-pollination was realized
+with 3-4 gentle touches on the stigma surface. The mixes of pollen were
+performed on an eppendorf based on the pollen counts maded with Neubaeur
+chamber (each anther was counted 4 times for 20 different anthers per
+species). In order to confirm that the treatments applied were 50-50\%
+pollen we counted for each species the total pollen stigmatic load from
+a donor of each family (N=3).
 
@@
 using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
-(Allaire et al. 2018) packages. All the multilevel models were fitted
-with \texttt{lme4} (Bates et al. 2015).
+(Allaire et al. 2018) packages. To test the effect of heterospecific
+pollen, we substracted the to seed set of hand cross pollination the
+seed set of the heterospecific pollen treatments. Therefore, small
+values mean low effect and viceversa. To be able to compare among
+species seed set was previosly scaled for all species. In order to see
+relations between hetereospecific pollen effect and traits we performed
+Mantel test between the matrix of effect and the distance matrix of each
+trait (euclidean distances). Moreover, Mantel test was also conducted
+between heterospecific pollen effect and phylogenetic distance.
+
+\newpage
 
@@
 Heterospecific pollen produced fitness for xxx cases.
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
+\caption{The effect of heterospecific pollen (scaled see set) is
+represented in function of the compatibility system (self/cross*100) for
+the the different species. Each coulored dot represents the interaction
+of a focal species with a different pollen donor.}
+\end{figure}
 
@@
 the National Academy of Sciences 100:9383--9387.
-
-\hypertarget{ref-Bates_2015}{}
-Bates, D., M. Mächler, B. Bolker, and S. Walker. 2015. Fitting linear
-mixed-effects models using lme4. Journal of Statistical Software
-67:1--48.
 

### 2018-12-09 Scripts/Analysis_mantel_test.R

@@ -964,18 +964,16 @@ plot(model2)
 #Lets add new column with a seq of the length of the dataset and i use that as random effect (different individuals)
 
 #save.image(file='Manuscript_draft/myEnv.RData')
-
-ALL$indv<- seq.int(nrow(ALL))
+#Index of self compatibility Lloyd and Schoen 1992
+ALL$indv<- seq.int(1:10)
 model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
 summary(model2)
 tempEf$fit <- predict(model) 
 
-Model.2 <- lmer(hp_effect ~ compatibility + (1 | Focal), data = ALL)
-summary(Model.2)
-
-ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
+#Model.2 <- lmer(hp_effect ~ compatibility + (1 | Focal), data = ALL)
+#summary(Model.2)
+#ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
   geom_jitter(width=1.5,aes(colour = Focal),size=4)+geom_line(aes(y=predict(model2), group=hp_effect))
-
 ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
   geom_jitter(width=1.5,aes(colour = Focal),size=4)+
-  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(Model.2))))
+  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(model2))))+theme_cowplot()

### 2018-12-09 Manuscript_draft/Manuscript_draft.Rmd
some edits

@@
 Therefore, 180 different combinations were perform with N=10.
-Seed set was the proxy of effect for all our teratments.
-Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested (N=10).
+Seed set was the proxy of effect for all our treatments.
+Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
 Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
-Hand-pollination was realized with 3-4 gentle touches on the stigma surface.
-The mixes of pollen were performed on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).
+Hand-pollination was conducted with 3-4 gentle touches on the stigma surface.
+The mixes of pollen were realized on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).
 In order to confirm that the treatments applied were 50-50 percent pollen, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
@@
 Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
-The different morphometrical traits were measured with XXXX.
-Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination.
-Moreover, two types of evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL)
+The different morphometrical traits were measured with a digital stereomicrospe.
+Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination @lloyd1992.
 
@@
 We used the statistical language `R` `r citep(citation())` for all our analyses.
-These were implemented in dynamic rmarkdown documents using `knitr` `r citep(citation("knitr"))` and `rmarkdown` `r citep(citation("rmarkdown"))` packages.
-To test the effect of heterospecific pollen, we substracted the to seed set of hand cross pollination the seed set of the heterospecific pollen treatments.
+To test the effect of heterospecific pollen, we substracted to the seed set of hand cross pollination the seed set of heterospecific pollen treatments.
 Therefore, small values mean low effect and viceversa.
-To be able to compare among species seed set was previosly scaled for all species.
-In order to see relations between hetereospecific pollen effect and traits we performed Mantel test between the matrix of effect and the distance matrix of each trait (euclidean distances).
-Moreover, Mantel test was also conducted between heterospecific pollen effect and phylogenetic distance.
+To be able to compare among species, seed set was previosly scaled with mean 0 and standard deviation of 1.
+In order to see correlations between hetereospecific pollen effect and traits we performed Mantel test between the matrix of effect and the distance matrix of each trait (euclidean distances).
+Moreover, Mantel test was also conducted between heterospecific pollen effect and the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).
+We explored also the the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species.
+Moreover, pairwise evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL).
+The sequences of interest were downloaded from NCBI GenBank and the phylogenetic tree constructed by maximum likelihood with MEGA7.
+
+Phylogenetic signal of traits?
 
@@
 
-Heterospecific pollen produced fitness for xxx cases.
+Heterospecific pollen reduced seet set signifcatively in xxx from xxx pairwise species combinations.
+Being greater in xxx and then in xxx.
+I have tested that with linear mixed effect models (add this to methods).
+Add boxplots here...
+
+Mantel test gave significant values p<0.05 for both types of evolutive distances considered, with r coefficients of 0.29 and 0.25 for the distances of ITS and RBCL markers respectively.
+Moreover, Mantel test gave a significant correlation between stigma width and stigma type with xxxx.
+Trait correlations were also explored with ...
+and we found that...
+
+Fix mantel test selfing rates and change it for compatibility index...
+
+Fix this to GLMM? Yep I have to...
 

### 2018-12-09 Scripts/Analysis.R

@@ -3,7 +3,11 @@ pein_seed_set_final <- read.csv("Rmd/Data/pein_seed_set_final.csv")
 #Statistical differences between seed set with treatment
 
 library(dplyr)
+library(nlme)
+library(lme4)
 
+
+#PEIN
 pein_seed_set_final_TEST <- subset(pein_seed_set_final, Treatment==c("CROSS") | Treatment==("Brassica oleracea"))
 
 t.test(Seed.production~Treatment, data=pein_seed_set_final_TEST)
@@ -14,3 +18,22 @@ summary(mod1)
 par(mfrow=c(2,2))
 plot(mod1)
 TukeyHSD(aov(mod1))
+
+pein_seed_set_final=na.omit(pein_seed_set_final)
+
+model2=lme(log(1+Seed.production)~relevel(Treatment,ref="CROSS"), data=pein_seed_set_final, random=~1|Treatment.number)
+summary(model2)
+
+#For Petunia BRRA, CAAN  and ERSA didn´t reduce seed set significatively 
+#SOLY
+soly_seed_set_final <- read.csv("Rmd/Data/soly_seed_set_final.csv")
+soly_seed_set_final=na.omit(soly_seed_set_final)
+model2=lme(log(1+Seed.production)~relevel(Treatment,ref="Cross"), data=soly_seed_set_final, random=~1|Treatment.number)
+summary(model2)
+
+#For tomato just BROL don´t produce a significant decrease in seed set
+
+some_seed_set_final <- read.csv("Rmd/Data/some_seed_set_final.csv")
+some_seed_set_final=na.omit(some_seed_set_final)
+model2=lme(log(1+Seed.production)~relevel(Treatment,ref="Cross"), data=some_seed_set_final, random=~1|Treatment.number)
+summary(model2)

### 2018-12-10 Manuscript_draft/Manuscript_draft.Rmd
Changes for meeting...

--- 2018-12-09 Manuscript_draft/Manuscript_draft.Rmd
@@
 
-Heterospecific pollen reduced seet set signifcatively in xxx from xxx pairwise species combinations.
-Being greater in xxx and then in xxx.
-I have tested that with linear mixed effect models (add this to methods).
-Add boxplots here...
+Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the paiwise interactions p<0.05.
+Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family Brassica oleracea and Eruca sativa we found very contrasting effects of foreign pollen where for the first one, all donors reduce seedt set significatively and for the second, just two species did out of nine.
+The treatments of 100% heterospecific pollen ...
+didn't seed except...
 
-Mantel test gave significant values p<0.05 for both types of evolutive distances considered, with r coefficients of 0.29 and 0.25 for the distances of ITS and RBCL markers respectively.
-Moreover, Mantel test gave a significant correlation between stigma width and stigma type with xxxx.
+Mantel test indicates that a possible correlation exist between heterospecific pollen effect and the evolutive distances, for  ITS and RBCL markers we had r coefficients of 0.29 and 0.25 respectively p<0.05.
+Moreover, Mantel test indicates that also a possible correlation between stigma width and stigma type exist.
 Trait correlations were also explored with ...
@@
 ```
+
+\newpage
 

### 2018-12-10 Manuscript_draft/Manuscript_draft.tex
Changes for meeting...

@@
 autogamous (REF). Selfer species would have a reduction of herkogamy
-(REF), less pollen production per ovule (REF) and therefore less likely
-to contribute in exporting pollen in the community. Other morphological
-traits, like stigma size can be determinant for the total pollen quatity
-that a stigma can receive and therefore related to do that pollen size
-would also play an important role. Example with pollen here.
+(REF) and less pollen production per ovule (REF) which can be
+interpretated as a reduction of pollen expoorted into the community.
+Other morphological traits, like stigma size can be determinant for the
+total pollen quatity that a stigma can receive and therefore related to
+do that pollen size would also play an important role. Example with
+pollen here.
 
@@
 created an artificial co-flowering community with 10 species belonging
-to three different families where we try to test the following
-questions: 1) Does heterospecific pollen reduce seed set, if so, 2) Does
-heterospecific pollen effect depend on the relatedness of the species,
-3) Does heterospecific pollen effect depend on any floral trait?
+to three different families with different traits where we try to test
+the following questions: 1) Does heterospecific pollen reduce seed set,
+if so, 2) Does heterospecific pollen effect depend on any floral trait?
+3) Does heterospecific pollen effect depend on the relatedness of the
+species.
 
@@
 combinations were perform with N=10. Seed set was the proxy of effect
-for all our teratments. Moreover, hand cross pollination, hand self
+for all our treatments. Moreover, hand cross pollination, hand self
 pollination, apomixis (bagged emasculated flowers) and natural selfing
-were tested (N=10). Flowers were emasculated the day prior anthesis and
-hand pollinated next day with a toothpick. HaNd-pollination was realized
-with 3-4 gentle touches on the stigma surface. The mixes of pollen were
-performed on an eppendorf based on the pollen counts maded with Neubaeur
-chamber (each anther was counted 4 times for 20 different anthers per
-species). In order to confirm that the treatments applied were 50-50\%
-pollen we counted for each species the total pollen stigmatic load from
-a donor of each family (N=3).
+were tested for each species (N=10). Flowers were emasculated the day
+prior anthesis and hand pollinated next day with a toothpick.
+Hand-pollination was conducted with 3-4 gentle touches on the stigma
+surface. The mixes of pollen were realized on an eppendorf based on the
+pollen counts maded with Neubaeur chamber (each anther was counted 4
+times for 20 different anthers per species). In order to confirm that
+the treatments applied were 50-50 percent pollen, for each focal species
+the total stigmatic load of pollen was counted from one donor of each
+family (N=3).
 
@@
 and a small grid over a petri dish from 15 randomly selected flowers.
-The different morphometrical traits were measured with XXXX. Levels of
-self incompatibility were estimated by dividing the the fruit set of
-hand self pollination by hand cross pollination. Moreover, two types of
-evolutive distances were calculated with MEGA7 for two kinds of markers:
-1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate
-carboxylase (RBCL)
+The different morphometrical traits were measured with a digital
+stereomicrospe. Levels of self incompatibility were estimated by
+dividing the the fruit set of hand self pollination by hand cross
+pollination Lloyd and Schoen (1992).
 
@@
 We used the statistical language \texttt{R} (R Core Team 2018) for all
-our analyses. These were implemented in dynamic rmarkdown documents
-using \texttt{knitr} (Xie 2014, 2015, 2018) and \texttt{rmarkdown}
-(Allaire et al. 2018) packages. To test the effect of heterospecific
-pollen, we substracted the to seed set of hand cross pollination the
-seed set of the heterospecific pollen treatments. Therefore, small
-values mean low effect and viceversa. To be able to compare among
-species seed set was previosly scaled for all species. In order to see
-relations between hetereospecific pollen effect and traits we performed
-Mantel test between the matrix of effect and the distance matrix of each
-trait (euclidean distances). Moreover, Mantel test was also conducted
-between heterospecific pollen effect and phylogenetic distance.
+our analyses. To test the effect of heterospecific pollen, we
+substracted to the seed set of hand cross pollination the seed set of
+heterospecific pollen treatments. Therefore, small values mean low
+effect and viceversa. To be able to compare among species, seed set was
+previosly scaled with mean 0 and standard deviation of 1. In order to
+see correlations between hetereospecific pollen effect and traits we
+performed Mantel test between the matrix of effect and the distance
+matrix of each trait (euclidean distances). Moreover, Mantel test was
+also conducted between heterospecific pollen effect and the square root
+of the matrix of phylogenetic distance due to improvement in the
+statistical power (Letten \& Cornwell 2014). We explored also the the
+relations between traits and heterospecific pollen effect through
+generalized mixed models where the response variable was heterospecific
+pollen effect, the independent variable the different traits and the
+random effects the different treatments per species. Moreover, pairwise
+evolutive distances were calculated with MEGA7 for two kinds of markers:
+1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate
+carboxylase (RBCL). The sequences of interest were downloaded from NCBI
+GenBank and the phylogenetic tree constructed by maximum likelihood with
+MEGA7.
+
+Phylogenetic signal of traits?
 
@@
 
-Heterospecific pollen produced fitness for xxx cases.
+Heterospecific pollen reduced seet set signifcatively with the 50-50\%
+heterospecific pollen treatments for 65\% of the paiwise interactions
+p\textless{}0.05. Across families we found a very similar effect but
+when species where look at species level they respond differently even
+within the same family, for instance for two species of the Brassicaceae
+family Brassica oleracea and Eruca sativa we found very contrasting
+effects of foreign pollen where for the first one, all donors reduce
+seedt set significatively and for the second, just two species did out
+of nine. The treatments of 100\% heterospecific pollen \ldots{} didn't
+seed except\ldots{}
+
+Mantel test indicates that a possible correlation exist between
+heterospecific pollen effect and the evolutive distances, for ITS and
+RBCL markers we had r coefficients of 0.29 and 0.25 respectively
+p\textless{}0.05. Moreover, Mantel test indicates that also a possible
+correlation between stigma width and stigma type exist. Trait
+correlations were also explored with \ldots{} and we found that\ldots{}
+
+Fix mantel test selfing rates and change it for compatibility
+index\ldots{}
+
+Fix this to GLMM? Yep I have to\ldots{}
 
@@
 \end{figure}
+
+\newpage
 
@@
 Ecology 88:271--281.
-
-\hypertarget{ref-Allaire_2018}{}
-Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
-Wickham, J. Cheng, and W. Chang. 2018. Rmarkdown: Dynamic documents for
-r.
 
@@
 
+\hypertarget{ref-lloyd1992}{}
+Lloyd, D. G., and D. J. Schoen. 1992. Self-and cross-fertilization in
+plants. i. functional dimensions. International Journal of Plant
+Sciences 153:358--369.
+
 \hypertarget{ref-montgomery2012}{}
@@
 
-\hypertarget{ref-Xie_2014}{}
-Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
-R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
-Implementing reproducible computational research. Chapman; Hall/CRC.
-
-\hypertarget{ref-Xie_2015}{}
-Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
-Hall/CRC, Boca Raton, Florida.
-
-\hypertarget{ref-Xie_2018}{}
-Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
-generation in r.
-
 \eleft

### 2018-12-10 Scripts/Analysis.R

@@ -1,4 +1,3 @@
-pein_seed_set_final <- read.csv("Rmd/Data/pein_seed_set_final.csv")
 
 #Statistical differences between seed set with treatment
 
@@ -8,6 +7,7 @@ library(lme4)
 
 
 #PEIN
+pein_seed_set_final <- read.csv("Rmd/Data/pein_seed_set_final.csv")
 pein_seed_set_final_TEST <- subset(pein_seed_set_final, Treatment==c("CROSS") | Treatment==("Brassica oleracea"))
 
 t.test(Seed.production~Treatment, data=pein_seed_set_final_TEST)
@@ -20,20 +20,76 @@ plot(mod1)
 TukeyHSD(aov(mod1))
 
 pein_seed_set_final=na.omit(pein_seed_set_final)
-
 model2=lme(log(1+Seed.production)~relevel(Treatment,ref="CROSS"), data=pein_seed_set_final, random=~1|Treatment.number)
 summary(model2)
-
 #For Petunia BRRA, CAAN  and ERSA didn´t reduce seed set significatively 
+
 #SOLY
 soly_seed_set_final <- read.csv("Rmd/Data/soly_seed_set_final.csv")
 soly_seed_set_final=na.omit(soly_seed_set_final)
 model2=lme(log(1+Seed.production)~relevel(Treatment,ref="Cross"), data=soly_seed_set_final, random=~1|Treatment.number)
 summary(model2)
 
-#For tomato just BROL don´t produce a significant decrease in seed set
+#For tomato just BROL don´t produce a significant decrease in seed set p<0.05
 
+#SOME
 some_seed_set_final <- read.csv("Rmd/Data/some_seed_set_final.csv")
 some_seed_set_final=na.omit(some_seed_set_final)
 model2=lme(log(1+Seed.production)~relevel(Treatment,ref="Cross"), data=some_seed_set_final, random=~1|Treatment.number)
 summary(model2)
+#SOLY, PEIN, IPPU,IPAQ, BROL p<0.05
+
+#CAAN
+caan_seed_set_final <- read.csv("Rmd/Data/caan_seed_set_final.csv")
+caan_seed_set_final=na.omit(caan_seed_set_final)
+model2=lme(log(1+Seed.production)~relevel(Treatment,ref="CROSS"), data=caan_seed_set_final, random=~1|Treatment.number)
+summary(model2)
[…]

### 2018-12-10 Manuscript_draft/Manuscript_draft.Rmd
seed set and fruit set information for 100% heterospecific pollen

@@
 
-Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the paiwise interactions p<0.05.
-Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family Brassica oleracea and Eruca sativa we found very contrasting effects of foreign pollen where for the first one, all donors reduce seedt set significatively and for the second, just two species did out of nine.
-The treatments of 100% heterospecific pollen ...
-didn't seed except...
+Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
+Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did, out of nine.
+The treatments of 100% heterospecific pollen were all significantly different from the cross except one, *Sinapis alba* with pollen from another Brassicaceae, *Brassica oleracea*.
+Just few treatments of 100% pollen produced seeds...
+A summary of the results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2.
 

### 2018-12-10 Manuscript_draft/Manuscript_draft.tex
seed set and fruit set information for 100% heterospecific pollen

@@
 Heterospecific pollen reduced seet set signifcatively with the 50-50\%
-heterospecific pollen treatments for 65\% of the paiwise interactions
+heterospecific pollen treatments for 65\% of the pairwise interactions
 p\textless{}0.05. Across families we found a very similar effect but
@@
 within the same family, for instance for two species of the Brassicaceae
-family Brassica oleracea and Eruca sativa we found very contrasting
-effects of foreign pollen where for the first one, all donors reduce
-seedt set significatively and for the second, just two species did out
-of nine. The treatments of 100\% heterospecific pollen \ldots{} didn't
-seed except\ldots{}
+family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
+very contrasting effects of foreign pollen where for the first one, all
+donors reduce seed set significatively and for the second, just two
+species did, out of nine. The treatments of 100\% heterospecific pollen
+were all significantly different from the cross except one,
+\emph{Sinapis alba} with pollen from another Brassicaceae,
+\emph{Brassica oleracea}. Just few treatments of 100\% pollen produced
+seeds\ldots{} A summary of the results of hand cross pollination, self
+hand pollination, natural selfing and apomixis are presented in table 2.
 

### 2018-12-10 Scripts/Analysis.R

@@ -173,3 +173,7 @@ mod1=lm(log(1+Seed.production)~relevel(Treatment,ref="Cross"),data=ipaq_seed_set
 summary(mod1)
 #significant differences for all
 #No seeds produced with 100% treatments
+
+
+
+#I'm going to compile now the fruit information.

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
Table transferred to Markdown

@@
 
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+load("table_treatments.RData")
+
+table<- data.frame(cross, self, nat_self,apo)
+kable(table, format="markdown")
+```
+
 Mantel test indicates that a possible correlation exist between heterospecific pollen effect and the evolutive distances, for  ITS and RBCL markers we had r coefficients of 0.29 and 0.25 respectively p<0.05.
@@
 
+\newpage
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=5, fig.cap="The effect of heterospecific pollen (scaled see set) is represented in function of the compatibility system (self/cross*100) for the the different species.

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
Some edits in results Markdown

@@
 
+Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2.
 Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did, out of nine.
-The treatments of 100% heterospecific pollen were all significantly different from the cross except one, *Sinapis alba* with pollen from another Brassicaceae, *Brassica oleracea*.
-Just few treatments of 100% pollen produced seeds...
-A summary of the results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2.
+Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine.
+The 100% foreign pollen treatments barely produced seeds or fruits and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial.
+Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases.
+*S.
+lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size.
+*C.
+annum* produced some fruits (9%) of both small and normal size and finally *S.
+melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of no production of fruit in apomictic treatments.
 
+**Table 2**.
+Perecentage of seeds produced per ovule for the ten species used in the experiment.
+The treatments presented are hand cross pollination, hand self pollination, natural selfing and apomixis (emasculated flowers).
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
@@
 load("table_treatments.RData")
-
-table<- data.frame(cross, self, nat_self,apo)
+Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+Cross <- cross
+Self <- self
+Natural_selfing <- nat_self
+Apomixis <- apo
+table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
 kable(table, format="markdown")

### 2018-12-11 Manuscript_draft/Manuscript_draft.tex
Table transferred to Markdown
Some edits in results Markdown

@@
 
-Heterospecific pollen reduced seet set signifcatively with the 50-50\%
-heterospecific pollen treatments for 65\% of the pairwise interactions
-p\textless{}0.05. Across families we found a very similar effect but
-when species where look at species level they respond differently even
-within the same family, for instance for two species of the Brassicaceae
-family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
-very contrasting effects of foreign pollen where for the first one, all
+Results of hand cross pollination, self hand pollination, natural
+selfing and apomixis are presented in table 2. Heterospecific pollen
+reduced seet set signifcatively with the 50-50\% heterospecific pollen
+treatments for 65\% of the pairwise interactions p\textless{}0.05.
+Across families we found a very similar effect but when species where
+look at species level they respond differently even within the same
+family, for instance for two species of the Brassicaceae family
+\emph{Brassica oleracea} and \emph{Eruca versicaria} we found very
+contrasting effects of foreign pollen where for the first one, all
 donors reduce seed set significatively and for the second, just two
-species did, out of nine. The treatments of 100\% heterospecific pollen
-were all significantly different from the cross except one,
-\emph{Sinapis alba} with pollen from another Brassicaceae,
-\emph{Brassica oleracea}. Just few treatments of 100\% pollen produced
-seeds\ldots{} A summary of the results of hand cross pollination, self
-hand pollination, natural selfing and apomixis are presented in table 2.
+species did out of nine. The 100\% foreign pollen treatments barely
+produced seeds or fruits and just for \emph{Sinapis alba} we did not
+find significant differences between the hand cross pollination and one
+treatment with pollen from a confamilial. Solanaceae species with berry
+fruit type developed small fruits or even normal fruits in some cases.
+\emph{S. lycopersicum} seems to produced small fruits (35\% of the
+treatments) independently of pollen and pollen donor due to also
+apomictic treatments did, never normal size. \emph{C. annum} produced
+some fruits (9\%) of both small and normal size and finally \emph{S.
+melongena} produced seedless normal fruits with just confamilial pollen
+(3\%), for both species seems that fruit formation was induced by pollen
+on the stigma because of no production of fruit in apomictic treatments.
+
+\textbf{Table 2}. Perecentage of seeds produced per ovule for the ten
+species used in the experiment. The treatments presented are hand cross
+pollination, hand self pollination, natural selfing and apomixis
+(emasculated flowers).
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\toprule
+Species & Cross & Self & Natural\_selfing & Apomixis\tabularnewline
+\midrule
+\endhead
+Brassica oleracea & 32.06897 & 0.0000000 & 0.00000 & 0\tabularnewline
+Brassica rapa & 44.97041 & 0.0000000 & 0.00000 & 0\tabularnewline
+Eruca versicaria & 23.75000 & 0.4166667 & 0.00000 & 0\tabularnewline
+Sinapis alba & 43.33333 & 48.3333333 & 5.00000 & 15\tabularnewline
+Ipomoea aquatica & 40.00000 & 30.0000000 & 20.00000 & 0\tabularnewline
+Ipomoea purpurea & 31.66667 & 86.6666667 & 31.66667 & 0\tabularnewline
+Capsicum annuum & 100.00000 & 66.2240664 & 23.48548 & 0\tabularnewline
+Petunia integrifolia & 100.00000 & 24.7727273 & 0.00000 &
+0\tabularnewline
+Solanum lycopersicum & 90.38043 & 43.4782609 & 70.00000 &
+0\tabularnewline
+Solanum melongena & 60.47525 & 87.9702970 & 21.56436 & 0\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 
+\newpage
+
 \begin{figure}
 \centering
-\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
 \caption{The effect of heterospecific pollen (scaled see set) is

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
More edits

@@
 Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences.
-The species selected (Table 1) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
+The species selected (**Table 1**) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
 The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle.
@@
 
-Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2.
+Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in **Table 2**.
 Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
@@
 *C.
-annum* produced some fruits (9%) of both small and normal size and finally *S.
-melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of no production of fruit in apomictic treatments.
+annuum* produced some fruits (9%) of both small and normal size and finally *S.
+melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with apomictic treatments.
 

### 2018-12-11 Manuscript_draft/Manuscript_draft.tex
More edits

@@
 temperature controlled depending on the requirements of the species with
-day and night temperature differences. The species selected (Table 1)
-belonged to three different families, Solanaceae, Brassicaceae and
-Convolvulaceae. The criteria of species/family selection was based on
-close/distant related species (see phylogenetic tree for relatedness fig
-1), heterogeneous traits, low structural flower complexity and fast life
-cycle. For the purpose of the experiment all the species where
-considered as pollen recipient and as pollen donor (see interaction
-matrix, fig 2). Species were watered once or twice per day and
-fertilized weekly (NPK 23: 3.95: 14).
+day and night temperature differences. The species selected
+(\textbf{Table 1}) belonged to three different families, Solanaceae,
+Brassicaceae and Convolvulaceae. The criteria of species/family
+selection was based on close/distant related species (see phylogenetic
+tree for relatedness fig 1), heterogeneous traits, low structural flower
+complexity and fast life cycle. For the purpose of the experiment all
+the species where considered as pollen recipient and as pollen donor
+(see interaction matrix, fig 2). Species were watered once or twice per
+day and fertilized weekly (NPK 23: 3.95: 14).
 
@@
 Results of hand cross pollination, self hand pollination, natural
-selfing and apomixis are presented in table 2. Heterospecific pollen
-reduced seet set signifcatively with the 50-50\% heterospecific pollen
-treatments for 65\% of the pairwise interactions p\textless{}0.05.
-Across families we found a very similar effect but when species where
-look at species level they respond differently even within the same
-family, for instance for two species of the Brassicaceae family
-\emph{Brassica oleracea} and \emph{Eruca versicaria} we found very
-contrasting effects of foreign pollen where for the first one, all
+selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
+pollen reduced seet set signifcatively with the 50-50\% heterospecific
+pollen treatments for 65\% of the pairwise interactions
+p\textless{}0.05. Across families we found a very similar effect but
+when species where look at species level they respond differently even
+within the same family, for instance for two species of the Brassicaceae
+family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
+very contrasting effects of foreign pollen where for the first one, all
 donors reduce seed set significatively and for the second, just two

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
adding Romina changes to Intro, still have to fix abstract and correct references from comments

@@
 
-In natural systems plant species normally coexist and share their floral visitors with other species @bascompte2003.
-This pollinator sharing from the plant perspective at the pre-pollination stage can be negative due to competition @pauw2013 or positive due to facilitation @carvalheiro2014.
-Once the floral visitor has arrived to the flower, pollen deposition on the stigma can take place and hence ovule fertilization.
-An increasing number of visits generally correlates with higher chances of fertilization @engel2003.
-However this is not always the case, among these possible flower visitors we find also nectar robbers and pollen thiefs @inouye1980 and the quality of pollen that is deposit on the stigma is also highly relevant to the pollination succes @aizen2007.
-Moreover, other less study issues in the pollination process are conspecific pollen loss and the arrival of foreign pollen which can have important detrimental effects on species fitness @morales2008 @ashman2013.
+In most ecosystems, plant species normally coexist and share their floral visitors with other species @bascompte2003.
+From the plants’ perspective, this pollinator sharing can be positive due to facilitation @carvalheiro2014 or negative due to competition at the pre-pollination stage Pauw (2013).
+An increasing number of visits often correlates with higher chances of fertilization @engel2003.
+However this is not always the case, among these possible flower visitors there are also nectar robbers and pollen thieves @inouye1980.
+Receiving both sufficient quantity and quality deposited on the stigma is thus highly relevant to the pollination success of the plant @aizen2007.
 
@@
 
-Recent studies have advanced in the ecological understanding of heterospecific pollen effect @morales2008 @ashman2013 @arceo2016.
-A general overview of foreign pollen arrival is that it can play an important role on species fitness but seems to be context dependent and not always produce a decrease in fitness @morales2008.
-Part of this unpredictability is due to the enormous variability of foreing pollen transferred in nature, where levels between 0 and 75 percent are seen, but most commonly values ranges between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012 @ashman2013 @fang2013, being the generalist species the ones that receive greater loads of heterospecific pollen @fang2013.
-Surprisingly, this low ranges of heterospecific pollen have been shown to decrease fitness greatly @thomson1982.
-Although heterospecific pollen quantity is fundamental to understand the outcome of the interaction so is the different traits of both pollen donor and recipient.
-@ashman2013 postulated the first predictive framework for traits of heterospecific pollen effect, where different traits such as compatibility system and pollen size among others seems to be crucial to understand foreing pollen effect.
-Moreover, in @tong2016 an assymetric effect was shown in a crossing experiment between 6 species of the genus *Pedicularis* where the pollen of long styled species was able to grow the full length of the style on short styled species but not viceversa.
-Despite these recent caveats, we still lack empirical evidence to affirm what are the main traits that drive heterospecific pollen effect for both pollen donor and recipient at seed production level.
-Interestingly, to comprehend how these traits interact is also crucial to look at the phylogenetic relatedness of the species.
-There is a considerable amount of literature of crosses between close related species @brown2001 @arceo2016can @tong2016 but few works focused on heterospecific pollen of far related species @thomson1982 @galen1989 @neiland1999 which also show a noteworthy fitness decrease.
-Although the effect of close related species is predicted to be greater @ashman2013 the presence of pollen of non related species on multiple species @arceo2016 and the higher chances to coexist with a species that has less niche overlap (Ref) make foreign pollen from far related species also an important subject of study in order to understand the importance of heterospecific pollen in natural systems.
-Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.
+By visiting many plant species, many pollinators are responsible for conspecific pollen loss and the transport of foreign pollen, both of which can have important detrimental effects on species fitness @morales2008;  @ashman2013; @arceo2016.
+Foreign pollen arrival can play an important role in plant species fitness but outcomes are variable and appear to be context dependent as there is not always a decrease in fitness @morales2008.
+Some of this variation is likely due to the enormous variability of foreign pollen transferred across systems ranging from between 0 and 75 percent but most studies report ranges of heterospecific pollen between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012; @ashman2013; @fang2013, yet even these relatively low amounts of heterospecific pollen transferred can decrease fitness greatly @thomson1982.
+While we now have some understanding of the impacts of heterospecific pollen quantity, we have less understanding of other factors that could be driving the variation in impacts upon fitness.
+@ashman2013 postulated the first predictive framework that identifies a need to understand how plant traits might mediate heterospecific pollen effect, whereby mating system and pollen size were predicted to potentially mediate the impact of foreign pollen transfer on plant fitness.
+This concept is supported by other studies, such as @tong2016 that demonstrate an asymmetrical effect in 6 species of Pedicularis whereby the pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
+While this suggests that the impacts of heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
 
@@
 
-Interestingly, incompatibility system seems to play an important role in foreign pollen effect where species that are self incompatible would have stronger barriers towards heterospecific pollen than self compatible species @ashman2013.
-The type of incompatibility, sporophytic or gametophytic is related with the place of pollen recognition where the former take place at the sitgma level and the latter occurs within the style, this last late acting pollen recognition mechanism is associated with greater negative effect @barrett1988.
-Remarkably, there is a great variability in mating systems across populations @whitehead2018 and therefore predict an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
-Moreover, other traits such as number of pollen grains per flower and number of ovules have been tradittionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF).
-Selfer species would have a reduction of herkogamy (REF) and less pollen production per ovule (REF) which can be interpretated as a reduction of pollen expoorted into the community.
+Given the large variability in mating systems across populations @whitehead2018, it is difficult to determine potential impacts upon HP transfer yet incompatibility system is another plant trait that appears to play an important role in foreign pollen effect whereby species that are self incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
+The type of incompatibility, (i.e.
+whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style.
+This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @barrett1988.
+Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
+Moreover, other traits such as number of pollen grains per flower and number of ovules have been traditionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF).
+Selfer species are known to have a reduction of herkogamy (REF) and less pollen production per ovule (REF) which can be interpretated as a reduction of pollen exported into the community.
 Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
@@
 
+**Paragraph 3** Maybe connect with paragrph above?
+
+Species with similar traits are more closely related  XXXXXXXXX.
+(Refs?
+Brown and Mitchell (2001) Arceo-Gómez et al.
+(2016) Tong and Huang (2016) ).
+Several studies predict that the impact of HP transfer is likely to be greater for closely related species (Ashman and Arceo-Gómez (2013)).
+Few studies however, have focused on the impacts of heterospecific pollen of distantly related species Thomson et al.
+(1982) Galen and Gregory (1989) Neiland and Wilcock (1999).
+Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen transfer networks here such as ).
+Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
+Given these are generally the ones that receive greater loads of heterospecific pollen Fang and Huang (2013) and unrelated species are more likely to coexist  with other species due to less niche overlap (Ref),  understanding the role of foreign pollen from distantly related species thus deserves greater attention in understanding coexistence blah blahXXXXX refs..
+Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.
+
 **Paragraph 4** Introducing our experiment
 
-The great environmental variability in natural systems and complexity of floral structures make heterospecific pollination studies a daunting task.
-Moreover, variation in sampling effort have been shown to be determinant to characterize pollen transfer interactions @arceo2018.
-Although plant-pollinator network and pollen network studies can give a first picture of the importance of foreign pollen is necessary to address how its effect is shaped with both traits and relatedness of the species.
-For this reason, in this study we have created an artificial co-flowering community with 10 species belonging to three different families with different traits where we try to test the following questions: 1) Does heterospecific pollen reduce seed set, if so, 2) Does heterospecific pollen effect depend on any floral trait?
-3) Does heterospecific pollen effect depend on the relatedness of the species.
+In this study we investigated how floral reproductive traits and relatedness mediate the impact of HP transfer by asking the following research questions : To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
+We do this by creating an artificial co-flowering community with 10 species belonging to three different families with different traits.
 

### 2018-12-11 Manuscript_draft/Manuscript_draft.tex
adding Romina changes to Intro, still have to fix abstract and correct references from comments

@@
 
-In natural systems plant species normally coexist and share their floral
-visitors with other species Bascompte et al. (2003). This pollinator
-sharing from the plant perspective at the pre-pollination stage can be
-negative due to competition Pauw (2013) or positive due to facilitation
-Carvalheiro et al. (2014). Once the floral visitor has arrived to the
-flower, pollen deposition on the stigma can take place and hence ovule
-fertilization. An increasing number of visits generally correlates with
-higher chances of fertilization Engel and Irwin (2003). However this is
-not always the case, among these possible flower visitors we find also
-nectar robbers and pollen thiefs Inouye (1980) and the quality of pollen
-that is deposit on the stigma is also highly relevant to the pollination
-succes Aizen and Harder (2007). Moreover, other less study issues in the
-pollination process are conspecific pollen loss and the arrival of
-foreign pollen which can have important detrimental effects on species
-fitness Morales and Traveset (2008) Ashman and Arceo-Gómez (2013).
+In most ecosystems, plant species normally coexist and share their
+floral visitors with other species Bascompte et al. (2003). From the
+plants' perspective, this pollinator sharing can be positive due to
+facilitation Carvalheiro et al. (2014) or negative due to competition at
+the pre-pollination stage Pauw (2013). An increasing number of visits
+often correlates with higher chances of fertilization Engel and Irwin
+(2003). However this is not always the case, among these possible flower
+visitors there are also nectar robbers and pollen thieves Inouye (1980).
+Receiving both sufficient quantity and quality deposited on the stigma
+is thus highly relevant to the pollination success of the plant Aizen
+and Harder (2007).
 
@@
 
-Recent studies have advanced in the ecological understanding of
-heterospecific pollen effect Morales and Traveset (2008) Ashman and
-Arceo-Gómez (2013) Arceo-Gómez and Ashman (2016). A general overview of
-foreign pollen arrival is that it can play an important role on species
-fitness but seems to be context dependent and not always produce a
-decrease in fitness Morales and Traveset (2008). Part of this
-unpredictability is due to the enormous variability of foreing pollen
-transferred in nature, where levels between 0 and 75 percent are seen,
-but most commonly values ranges between 0 and 20 percent of the total
-pollen load Bartomeus et al. (2008) Montgomery and Rathcke (2012) Ashman
-and Arceo-Gómez (2013) Fang and Huang (2013), being the generalist
-species the ones that receive greater loads of heterospecific pollen
-Fang and Huang (2013). Surprisingly, this low ranges of heterospecific
-pollen have been shown to decrease fitness greatly Thomson et al.
-(1982). Although heterospecific pollen quantity is fundamental to
-understand the outcome of the interaction so is the different traits of
-both pollen donor and recipient. Ashman and Arceo-Gómez (2013)
-postulated the first predictive framework for traits of heterospecific
-pollen effect, where different traits such as compatibility system and
-pollen size among others seems to be crucial to understand foreing
-pollen effect. Moreover, in Tong and Huang (2016) an assymetric effect
-was shown in a crossing experiment between 6 species of the genus
-\emph{Pedicularis} where the pollen of long styled species was able to
-grow the full length of the style on short styled species but not
-viceversa. Despite these recent caveats, we still lack empirical
-evidence to affirm what are the main traits that drive heterospecific
-pollen effect for both pollen donor and recipient at seed production
-level. Interestingly, to comprehend how these traits interact is also
-crucial to look at the phylogenetic relatedness of the species. There is
-a considerable amount of literature of crosses between close related
-species Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and
-Huang (2016) but few works focused on heterospecific pollen of far
-related species Thomson et al. (1982) Galen and Gregory (1989) Neiland
-and Wilcock (1999) which also show a noteworthy fitness decrease.
-Although the effect of close related species is predicted to be greater
-Ashman and Arceo-Gómez (2013) the presence of pollen of non related
-species on multiple species Arceo-Gómez and Ashman (2016) and the higher
-chances to coexist with a species that has less niche overlap (Ref) make
-foreign pollen from far related species also an important subject of
-study in order to understand the importance of heterospecific pollen in
-natural systems. Notwithstanding, the effect of heterospecific pollen of
-far and close related species at community level remains to be explored
-beyond single pairwise interactions.
+By visiting many plant species, many pollinators are responsible for
+conspecific pollen loss and the transport of foreign pollen, both of
+which can have important detrimental effects on species fitness Morales
+and Traveset (2008); Ashman and Arceo-Gómez (2013); Arceo-Gómez and
+Ashman (2016). Foreign pollen arrival can play an important role in
+plant species fitness but outcomes are variable and appear to be context
+dependent as there is not always a decrease in fitness Morales and
+Traveset (2008). Some of this variation is likely due to the enormous
+variability of foreign pollen transferred across systems ranging from
+between 0 and 75 percent but most studies report ranges of
+heterospecific pollen between 0 and 20 percent of the total pollen load
+Bartomeus et al. (2008) Montgomery and Rathcke (2012); Ashman and
+Arceo-Gómez (2013); Fang and Huang (2013), yet even these relatively low
+amounts of heterospecific pollen transferred can decrease fitness
+greatly Thomson et al. (1982). While we now have some understanding of
+the impacts of heterospecific pollen quantity, we have less
+understanding of other factors that could be driving the variation in
+impacts upon fitness. Ashman and Arceo-Gómez (2013) postulated the first
+predictive framework that identifies a need to understand how plant
+traits might mediate heterospecific pollen effect, whereby mating system
+and pollen size were predicted to potentially mediate the impact of
+foreign pollen transfer on plant fitness. This concept is supported by
+other studies, such as Tong and Huang (2016) that demonstrate an
+asymmetrical effect in 6 species of Pedicularis whereby the pollen of
+long styled species was able to grow the full length of the style on
+short styled species but not vice versa. While this suggests that the
+impacts of heterospecific pollen may differ among pollen donor and
+recipient, few studies have been conducted to ascertain whether this
+pattern is in fact a trend or to identify the extent to which other
+plant traits are critical to heterospecific pollen impacts.
 
@@
 
-Interestingly, incompatibility system seems to play an important role in
-foreign pollen effect where species that are self incompatible would
-have stronger barriers towards heterospecific pollen than self
-compatible species Ashman and Arceo-Gómez (2013). The type of
-incompatibility, sporophytic or gametophytic is related with the place
-of pollen recognition where the former take place at the sitgma level
-and the latter occurs within the style, this last late acting pollen
-recognition mechanism is associated with greater negative effect Barrett
-(1988). Remarkably, there is a great variability in mating systems
-across populations Whitehead et al. (2018) and therefore predict an
+Given the large variability in mating systems across populations
+Whitehead et al. (2018), it is difficult to determine potential impacts
+upon HP transfer yet incompatibility system is another plant trait that
+appears to play an important role in foreign pollen effect whereby
+species that are self incompatible have stronger barriers to
+heterospecific pollen than self-compatible species Ashman and
+Arceo-Gómez (2013). The type of incompatibility, (i.e.~whether
+sporophytic or gametophytic) is related to the location of pollen
+recognition; sporophytic incompatibility relates to signaling at the
+stigma surface while gametophytic occurs within the style. This later
+acting pollen recognition mechanism is associated with greater negative
+effect than sporophytic recognistion Barrett (1988). Nonetheless, an
 effect of foreign pollen is a bit obscured by the variability within
@@
 other traits such as number of pollen grains per flower and number of
-ovules have been tradittionally associated with the type of
+ovules have been traditionally associated with the type of
 incompatibility system where species with higher pollen ovule ratios are
 predicted to be xenogamous and species with low pollen ovule ratios
-autogamous (REF). Selfer species would have a reduction of herkogamy
-(REF) and less pollen production per ovule (REF) which can be
-interpretated as a reduction of pollen expoorted into the community.
+autogamous (REF). Selfer species are known to have a reduction of
+herkogamy (REF) and less pollen production per ovule (REF) which can be
+interpretated as a reduction of pollen exported into the community.
 Other morphological traits, like stigma size can be determinant for the
@@
 
+\textbf{Paragraph 3} Maybe connect with paragrph above?
+
+Species with similar traits are more closely related XXXXXXXXX. (Refs?
+Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang
+(2016) ). Several studies predict that the impact of HP transfer is
+likely to be greater for closely related species (Ashman and Arceo-Gómez
+(2013)). Few studies however, have focused on the impacts of
+heterospecific pollen of distantly related species Thomson et al. (1982)
+Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects
+and most stigmas have been found to carry multiple species of foreign
+pollen with little attention to degree of relatedness (Arceo-Gómez and
+Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
+transfer networks here such as ). Further, a majority of plant species
+are generalist and thus receive visits from multiple different
+pollinators. Given these are generally the ones that receive greater
+loads of heterospecific pollen Fang and Huang (2013) and unrelated
+species are more likely to coexist with other species due to less niche
+overlap (Ref), understanding the role of foreign pollen from distantly
+related species thus deserves greater attention in understanding
+coexistence blah blahXXXXX refs.. Notwithstanding, the effect of
+heterospecific pollen of far and close related species at community
+level remains to be explored beyond single pairwise interactions.
+
 \textbf{Paragraph 4} Introducing our experiment
 
-The great environmental variability in natural systems and complexity of
-floral structures make heterospecific pollination studies a daunting
-task. Moreover, variation in sampling effort have been shown to be
-determinant to characterize pollen transfer interactions Arceo-Gómez et
-al. (2018). Although plant-pollinator network and pollen network studies
-can give a first picture of the importance of foreign pollen is
-necessary to address how its effect is shaped with both traits and
-relatedness of the species. For this reason, in this study we have
-created an artificial co-flowering community with 10 species belonging
-to three different families with different traits where we try to test
-the following questions: 1) Does heterospecific pollen reduce seed set,
-if so, 2) Does heterospecific pollen effect depend on any floral trait?
-3) Does heterospecific pollen effect depend on the relatedness of the
-species.
+In this study we investigated how floral reproductive traits and
+relatedness mediate the impact of HP transfer by asking the following
+research questions : To what extent do (i) floral reproductive traits
+and (ii) relatedness, mediate the impacts of heterospecific pollen on
+seed set. We do this by creating an artificial co-flowering community
+with 10 species belonging to three different families with different
+traits.
 
@@
 treatments) independently of pollen and pollen donor due to also
-apomictic treatments did, never normal size. \emph{C. annum} produced
+apomictic treatments did, never normal size. \emph{C. annuum} produced
 some fruits (9\%) of both small and normal size and finally \emph{S.
@@
 (3\%), for both species seems that fruit formation was induced by pollen
-on the stigma because of no production of fruit in apomictic treatments.
+on the stigma because of lack of fruit production with apomictic
+treatments.
 
@@
 
-\hypertarget{ref-arceo2018}{}
-Arceo-Gómez, G., C. Alonso, T.-L. Ashman, and V. Parra-Tabla. 2018.
-Variation in sampling effort affects the observed richness of
-plant--plant interactions via heterospecific pollen transfer:
-Implications for interpretation of pollen transfer networks. American
-journal of botany 105:1601--1608.
-
 \hypertarget{ref-arceo2016}{}
@@
 104:1003--1008.
-
-\hypertarget{ref-arceo2016can}{}
-Arceo-Gómez, G., R. A. Raguso, and M. A. Geber. 2016. Can plants evolve
-tolerance mechanisms to heterospecific pollen effects? An experimental
-test of the adaptive potential in clarkia species. Oikos 125:718--725.
 
@@
 
-\hypertarget{ref-brown2001}{}
-Brown, B. J., and R. J. Mitchell. 2001. Competition for pollination:
-Effects of pollen of an invasive plant on seed set of a native congener.
-Oecologia 129:43--49.
-
 \hypertarget{ref-carvalheiro2014}{}
@@
 94:1176--1185.
-
-\hypertarget{ref-galen1989}{}
-Galen, C., and T. Gregory. 1989. Interspecific pollen transfer as a
-mechanism of competition: Consequences of foreign pollen contamination
-for seed set in the alpine wildflower, polemonium viscosum. Oecologia
-81:120--123.
 
@@
 Reviews in Plant Sciences 27:221--238.
-
-\hypertarget{ref-neiland1999}{}
-Neiland, M., and C. Wilcock. 1999. The presence of heterospecific pollen
-on stigmas of nectariferous and nectarless orchids and its consequences
-for their reproductive success. Protoplasma 208:65--75.
-
-\hypertarget{ref-pauw2013}{}
-Pauw, A. 2013. Can pollination niches facilitate plant coexistence?
-Trends in ecology \& evolution 28:30--37.
 

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
some changes

@@
 
+Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)
+
+Let's classify pollen size in three groups in order to understand the interaction between pollen donor and recipient. 
+Donor's pollen:
+1) Donor pollen size < Recipient pollen size
+2) Donor pollen size = Recipient pollen size
+3) Donor pollen size > Recipient pollen size
+
+Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very small stigmas. YES.
+
+Is small pollen likely to affect bigger pollen.
+Ideas: It can be compensated with, less number of ovules to fertilize and faster pollen tube growth.
+So generally speaking, when the differences in pollen size are evident we expect a similar outcome.
+
 # CONCLUSIONS

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
some changes

@@
 
+Ideas about pollen size in heterospecific pollen effect. (still have to
+develop it more\ldots{})
+
+Let's classify pollen size in three groups in order to understand the
+interaction between pollen donor and recipient. Donor's pollen: 1) Donor
+pollen size \textless{} Recipient pollen size 2) Donor pollen size =
+Recipient pollen size 3) Donor pollen size \textgreater{} Recipient
+pollen size
+
+Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very
+small stigmas. YES.
+
+Is small pollen likely to affect bigger pollen. Ideas: It can be
+compensated with, less number of ovules to fertilize and faster pollen
+tube growth. So generally speaking, when the differences in pollen size
+are evident we expect a similar outcome.
+
 \section{CONCLUSIONS}\label{conclusions}

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
some changes

@@
 
-1.	 What are the implications of the findings?
+ What are the implications of the findings?
 
@@
 
-Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very small stigmas. YES.
+1) Donor pollen size < Recipient pollen size
 
-Is small pollen likely to affect bigger pollen.
-Ideas: It can be compensated with, less number of ovules to fertilize and faster pollen tube growth.
-So generally speaking, when the differences in pollen size are evident we expect a similar outcome.
+*Negative*
+
+-Stigma clogging
+
+-
 

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
some changes

@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
 What are the implications of the findings?
-\end{enumerate}
 
@@
 
-Small pollen can clogg the stigma. YES. Big pollen doesn't fit in very
-small stigmas. YES.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Donor pollen size \textless{} Recipient pollen size
+\end{enumerate}
 
-Is small pollen likely to affect bigger pollen. Ideas: It can be
-compensated with, less number of ovules to fertilize and faster pollen
-tube growth. So generally speaking, when the differences in pollen size
-are evident we expect a similar outcome.
+\emph{Negative}
+
+-Stigma clogging
+
+\begin{itemize}
+\item
+\end{itemize}
 

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
some ideas

--- 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
@@
 
-1.	 What are the implications of the findings?
+ What are the implications of the findings?
+
+Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)
+
+Let's classify pollen size in three groups in order to understand the interaction between pollen donor and recipient:
+1) Donor pollen size < Recipient pollen size
+2) Donor pollen size = Recipient pollen size
+3) Donor pollen size > Recipient pollen size
+
+1) Donor pollen size < Recipient pollen size
+
+*Negative*
+
+-Stigma clogging
+
+-
 

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
some ideas

@@
 Let's classify pollen size in three groups in order to understand the
-interaction between pollen donor and recipient. Donor's pollen: 1) Donor
-pollen size \textless{} Recipient pollen size 2) Donor pollen size =
-Recipient pollen size 3) Donor pollen size \textgreater{} Recipient
-pollen size
+interaction between pollen donor and recipient: 1) Donor pollen size
+\textless{} Recipient pollen size 2) Donor pollen size = Recipient
+pollen size 3) Donor pollen size \textgreater{} Recipient pollen size
 

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
ideas

@@
 ---
-title: working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect
+title: working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect
 author:
@@
 
+Romina's correction
+
+Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen.
+However, the costs of heterospecific pollen are not yet well understood.
+We  conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer.
+We conducted 4XXXX crosses  by experimentally transferring pollen (50% ratio) from 10 plant donors to 10 recipients belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+Seed set and pollen tube development were considered proxies of plant fitness.
+We found that for all species, the application of foreign pollen (50% or less) reduced seed set.
+Moreover, the reduction in seed set was dependent on the degree of relatedness and reproductive traits of the pollen recipient and not the pollen donor.
+Our results show that certain traits, particularly mating system,  are critical in understanding the costs of heterospecific pollen.
 \vspace{3mm}\hrule
@@
 
+Other idea based on the paper of Aizen 2007:
+
+He explains seed set in this way. O total number of ovules, d fraction of ovules that become seed set, b proportion of pollen grains that reach ovules, p number of pollen grains.
+
+$S=dO(1-e^bp)$
+
+$S=dO(1-e^bp(HpEffect))$
+
+but this Hp effect maybe can be divided at the same time in the interaction between recipient-donor with the main traits that drive the effect.
+Moreover, this should consider quantity of hp.
+lINEAR EFFECT?
+How to model this maybe talk with nacho.
+
 Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)
@@
 
+Now I try to develop each part
+
 1) Donor pollen size < Recipient pollen size
+
+Effect:
+
+- Donor's pollen could clogg the stigma
+
+- Chemical inhibition
+
+Traits associated with bigger pollen of the recipient:
+
+- Recipient's pollen have faster pollen tube growth (example with my data)
+
+- Reduction in number of ovules (Also with my species)
+
+- Big differences in pollen size can be traduced in low relatednes therefore less likely of pollen germination on a far related stigma.
+
+2) Donor pollen size = Recipient pollen size
+
+- Very relatedness dependant this point
+
+- Similar probabilities of taken space on the stigma
+
+3) Donor pollen size > Recipient pollen size
+
+Effect:
+
+-In small stigmas big pollen grains can occupy great part of the stigmatic area.
+
+-small pollen grains can get embeded
 

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
ideas

@@
 
+Now I try to develop each part
+
 \begin{enumerate}
@@
 \end{enumerate}
+
+Effect:
+
+\begin{itemize}
+\item
+  Donor's pollen could clogg the stigma
+\item
+  Chemical inhibition
+\end{itemize}
+
+Traits associated with bigger pollen of the recipient:
+
+\begin{itemize}
+\item
+  Recipient's pollen have faster pollen tube growth (example with my
+  data)
+\item
+  Reduction in number of ovules (Also with my species)
+\item
+  Big differences in pollen size can be traduced in low relatednes
+  therefore less likely of pollen germination on a far related stigma.
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Donor pollen size = Recipient pollen size
+\end{enumerate}
+
+\begin{itemize}
+\item
+  Very relatedness dependant this point
+\item
+  Similar probabilities of taken space on the stigma
+\end{itemize}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Donor pollen size \textgreater{} Recipient pollen size
+\end{enumerate}
+
+Effect:
+
+-In small stigmas big pollen grains can occupy great part of the
+stigmatic area.
+
+-small pollen grains can get embeded
 

### 2018-12-12 Rmd/Ideas.Rmd
ideas

---
title: "Ideas"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I'm going to try to describe some ideas here that they need more thinking but I would like to see what do you think and if it woth pursuing them.

Based on a paper of Haizen & Harder, 2007 (https://doi.org/10.1890/06-1017)

From the paper:

Suppose that a pistil contains O ovules and that its stigma receives P pollen grains, which may differ in quality, resulting in p = P/O pollen grains per ovule. Germination failure and attrition of pollen tubes in the style reduce the number of male gametophytes in the pistil, so that pollen tubes from only a proportion, b, of the original P pollen grains reach the ovary and compete for fertilization. If the pollen tubes in the ovary distribute randomly among ovules, the number of pollen tubes that can fertilize each ovule will follow a Poisson distribution with a mean of bp. Consequently, if one pollen tube is sufficient to fertilize an ovule, the probability that an ovule is not fertilized (i.e., no pollen tube) is e-bp, so the probability that it is fertilized is 1 - e-bp. Thus a total of (1 - e-bp)O ovules will be fertilized. If a fraction d of fertilized ovules mature into seeds, for a given mixture of pollen, the flower's total expected seed production is

$S=dO(1-e^bp)$

We could reformulate this with Hp effect. Here the lack of mathematical skill limit me, so I add it like this for now.

$S=dO(1-e^bp(HpEffect))$

Then based on our work. This Hpeffect can be described with the main traits that predict its effect. I know there are many variables but we can do a simplistic framework where we consider similar pollen size of pollen donro and recipient.

Hpeffect Degree of relatedness+Mating system+Hp

### 2018-12-12 Manuscript_draft/Manuscript_draft.Rmd
edits for Nacho´s meeting

@@
 
-Pollinator sharing can have negative consequences for species fitness with the arrival of foreign pollen.
-However, the costs of heterospecific pollen are not yet well understood.
-For this reason, we have conducted a glasshouse experiment where we try to understand how phylogenetic relatedness and the different traits of these species are involved in this process.
-We experimentally crossed 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
-Overall, more than 4000 crosses were done and seed set and pollen tubes were considered as proxy of effect.
-We found that for all species foreign pollen (50% or less) reduced seed set.
-Moreover, the seed set reduction is not dependent on the degree of relatedness of the pollen donor.
-However, the effect is governed by the degree of relatedness and the traits of the species recipient.
-Our results show that the outcome of heterospecific pollen deposition is determined in greater degree by the traits of the pollen recipient than the pollen donor and that certain traits such as compatibility system are crucial to understand the costs of heterospecific pollen.
-
-Romina's correction
-
 Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen.
@@
 We  conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer.
-We conducted 4XXXX crosses  by experimentally transferring pollen (50% ratio) from 10 plant donors to 10 recipients belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
-Seed set and pollen tube development were considered proxies of plant fitness.
-We found that for all species, the application of foreign pollen (50% or less) reduced seed set.
+We conducted 4XXXX crosses by experimentally transferring pollen (50% and 100% ratio) with reciporcal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+Seed set was used as proxy of plant fitness.
+We found that for 65% of the treatments with 50% mix reduced seed set.
 Moreover, the reduction in seed set was dependent on the degree of relatedness and reproductive traits of the pollen recipient and not the pollen donor.
-Our results show that certain traits, particularly mating system,  are critical in understanding the costs of heterospecific pollen.
+Our results show that certain traits, particularly compatibility system,  are critical in understanding the costs of heterospecific pollen.
 \vspace{3mm}\hrule
@@
 @ashman2013 postulated the first predictive framework that identifies a need to understand how plant traits might mediate heterospecific pollen effect, whereby mating system and pollen size were predicted to potentially mediate the impact of foreign pollen transfer on plant fitness.
-This concept is supported by other studies, such as @tong2016 that demonstrate an asymmetrical effect in 6 species of Pedicularis whereby the pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
+This concept is supported by other studies, such as @tong2016 that demonstrate an asymmetrical effect in 6 species of *Pedicularis* whereby the pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
 While this suggests that the impacts of heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
@@
 The type of incompatibility, (i.e.
-whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style.
-This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @barrett1988.
+whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style @barrett1988.
+This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.
 Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
@@
 
-**Paragraph 3** Maybe connect with paragrph above?
+[This last bit of the paragraph is still under development](Jose)
+
+**Paragraph 4** Maybe connect with paragrph above?
+
+[Comments on it](Romina)
 
@@
 (1982) Galen and Gregory (1989) Neiland and Wilcock (1999).
-Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen transfer networks here such as ).
+Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen transfer networks here such as...
+).
 Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
@@
 
-**Paragraph 4** Introducing our experiment
+**Paragraph 5** Introducing our experiment
 
@@
 We used the statistical language `R` `r citep(citation())` for all our analyses.
+Differences of seed set between treatments and hand cross pollination for each species was tested through mixed linear models.
+For the following analysis we scaled the values of seed production for all the species with mean 0 and sd of 1.
 To test the effect of heterospecific pollen, we substracted to the seed set of hand cross pollination the seed set of heterospecific pollen treatments.
-Therefore, small values mean low effect and viceversa.
-To be able to compare among species, seed set was previosly scaled with mean 0 and standard deviation of 1.
-In order to see correlations between hetereospecific pollen effect and traits we performed Mantel test between the matrix of effect and the distance matrix of each trait (euclidean distances).
+In order to see correlations between heterospecific pollen effect and traits we performed Mantel test between the matrix of heterospecific pollen effect and the distance matrix of each trait (euclidean distances).
 Moreover, Mantel test was also conducted between heterospecific pollen effect and the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).
@@
 
-Phylogenetic signal of traits?
+[Phylogenetic signal of traits?](Jose)
 
@@
 annuum* produced some fruits (9%) of both small and normal size and finally *S.
-melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with apomictic treatments.
+melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.
 
@@
 Moreover, Mantel test indicates that also a possible correlation between stigma width and stigma type exist.
-Trait correlations were also explored with ...
-and we found that...
+Trait correlations were also explored with GLMM
 
-Fix mantel test selfing rates and change it for compatibility index...
-
-Fix this to GLMM? Yep I have to...
+[I have done it at the moment just for Compatibility system](Jose)
+[Also I have to fix from mixed linear model to GLMM, just realize that](Jose)
 
@@
 ```
+
+[Compatibility index don´t multiply per 100 from Lloyd](Jose)
 
@@
 
-*Negative*
-
--Stigma clogging
-
--
-
 # CONCLUSIONS

### 2018-12-12 Manuscript_draft/Manuscript_draft.tex
edits for Nacho´s meeting

@@
             pdfauthor={},
-            pdftitle={working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect},
+            pdftitle={working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect},
             colorlinks=true,
@@
 
-\title{working title Compatibility system and stygma size of pollen recipient
-as main predictors of heterospecific pollen effect}
+\title{working title Compatibility system and stigma size are the main
+predictors of heterospecific pollen effect}
 \author{
@@
 \begin{center}
-\huge working title Compatibility system and stygma size of pollen recipient
-as main predictors of heterospecific pollen effect
+\huge working title Compatibility system and stigma size are the main
+predictors of heterospecific pollen effect
 \end{center}
@@
 
-Pollinator sharing can have negative consequences for species fitness
-with the arrival of foreign pollen. However, the costs of heterospecific
-pollen are not yet well understood. For this reason, we have conducted a
-glasshouse experiment where we try to understand how phylogenetic
-relatedness and the different traits of these species are involved in
-this process. We experimentally crossed 10 species belonging to three
-different families: Brassicaceae, Solanaceae and Convolvulaceae.
-Overall, more than 4000 crosses were done and seed set and pollen tubes
-were considered as proxy of effect. We found that for all species
-foreign pollen (50\% or less) reduced seed set. Moreover, the seed set
-reduction is not dependent on the degree of relatedness of the pollen
-donor. However, the effect is governed by the degree of relatedness and
-the traits of the species recipient. Our results show that the outcome
-of heterospecific pollen deposition is determined in greater degree by
-the traits of the pollen recipient than the pollen donor and that
-certain traits such as compatibility system are crucial to understand
-the costs of heterospecific pollen.
-
-\vspace{3mm}\hrule
+Pollinator sharing can have negative consequences for plant fitness with
+the arrival of foreign pollen. However, the costs of heterospecific
+pollen are not yet well understood. We conducted a glasshouse experiment
+to understand how phylogenetic relatedness and plant traits mediate the
+impacts of heterospecific pollen transfer. We conducted 4XXXX crosses by
+experimentally transferring pollen (50\% and 100\% ratio) with
+reciporcal crosses between 10 species belonging to three different
+families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used
+as proxy of plant fitness. We found that for 65\% of the treatments with
+50\% mix reduced seed set. Moreover, the reduction in seed set was
+dependent on the degree of relatedness and reproductive traits of the
+pollen recipient and not the pollen donor. Our results show that certain
+traits, particularly compatibility system, are critical in understanding
+the costs of heterospecific pollen. \vspace{3mm}\hrule
 
@@
 other studies, such as Tong and Huang (2016) that demonstrate an
-asymmetrical effect in 6 species of Pedicularis whereby the pollen of
-long styled species was able to grow the full length of the style on
-short styled species but not vice versa. While this suggests that the
-impacts of heterospecific pollen may differ among pollen donor and
-recipient, few studies have been conducted to ascertain whether this
+asymmetrical effect in 6 species of \emph{Pedicularis} whereby the
+pollen of long styled species was able to grow the full length of the
+style on short styled species but not vice versa. While this suggests
+that the impacts of heterospecific pollen may differ among pollen donor
+and recipient, few studies have been conducted to ascertain whether this
 pattern is in fact a trend or to identify the extent to which other
@@
 recognition; sporophytic incompatibility relates to signaling at the
-stigma surface while gametophytic occurs within the style. This later
-acting pollen recognition mechanism is associated with greater negative
-effect than sporophytic recognistion Barrett (1988). Nonetheless, an
-effect of foreign pollen is a bit obscured by the variability within
-species, however species that are strong selfers or strong outcrossers
-have less variablity in mating systems and predictions of effect could
-be more realistic (see figure 1 from Whitehead et al. (2018)). Moreover,
-other traits such as number of pollen grains per flower and number of
-ovules have been traditionally associated with the type of
-incompatibility system where species with higher pollen ovule ratios are
-predicted to be xenogamous and species with low pollen ovule ratios
-autogamous (REF). Selfer species are known to have a reduction of
-herkogamy (REF) and less pollen production per ovule (REF) which can be
-interpretated as a reduction of pollen exported into the community.
-Other morphological traits, like stigma size can be determinant for the
-total pollen quatity that a stigma can receive and therefore related to
-do that pollen size would also play an important role. Example with
-pollen here.
+stigma surface while gametophytic occurs within the style Barrett
+(1988). This later acting pollen recognition mechanism is associated
+with greater negative effect than sporophytic recognistion Ashman and
+Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a bit
+obscured by the variability within species, however species that are
+strong selfers or strong outcrossers have less variablity in mating
+systems and predictions of effect could be more realistic (see figure 1
+from Whitehead et al. (2018)). Moreover, other traits such as number of
+pollen grains per flower and number of ovules have been traditionally
+associated with the type of incompatibility system where species with
+higher pollen ovule ratios are predicted to be xenogamous and species
+with low pollen ovule ratios autogamous (REF). Selfer species are known
+to have a reduction of herkogamy (REF) and less pollen production per
+ovule (REF) which can be interpretated as a reduction of pollen exported
+into the community. Other morphological traits, like stigma size can be
+determinant for the total pollen quatity that a stigma can receive and
+therefore related to do that pollen size would also play an important
+role. Example with pollen here.
 
-\textbf{Paragraph 3} Maybe connect with paragrph above?
+\href{Jose}{This last bit of the paragraph is still under development}
+
+\textbf{Paragraph 4} Maybe connect with paragrph above?
+
+\href{Romina}{Comments on it}
 
@@
 Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
-transfer networks here such as ). Further, a majority of plant species
-are generalist and thus receive visits from multiple different
+transfer networks here such as\ldots{} ). Further, a majority of plant
+species are generalist and thus receive visits from multiple different
 pollinators. Given these are generally the ones that receive greater
@@
 
-\textbf{Paragraph 4} Introducing our experiment
+\textbf{Paragraph 5} Introducing our experiment
 
@@
 We used the statistical language \texttt{R} (R Core Team 2018) for all
-our analyses. To test the effect of heterospecific pollen, we
-substracted to the seed set of hand cross pollination the seed set of
-heterospecific pollen treatments. Therefore, small values mean low
-effect and viceversa. To be able to compare among species, seed set was
-previosly scaled with mean 0 and standard deviation of 1. In order to
-see correlations between hetereospecific pollen effect and traits we
-performed Mantel test between the matrix of effect and the distance
-matrix of each trait (euclidean distances). Moreover, Mantel test was
-also conducted between heterospecific pollen effect and the square root
-of the matrix of phylogenetic distance due to improvement in the
-statistical power (Letten \& Cornwell 2014). We explored also the the
-relations between traits and heterospecific pollen effect through
-generalized mixed models where the response variable was heterospecific
-pollen effect, the independent variable the different traits and the
-random effects the different treatments per species. Moreover, pairwise
-evolutive distances were calculated with MEGA7 for two kinds of markers:
-1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate
-carboxylase (RBCL). The sequences of interest were downloaded from NCBI
-GenBank and the phylogenetic tree constructed by maximum likelihood with
-MEGA7.
+our analyses. Differences of seed set between treatments and hand cross
+pollination for each species was tested through mixed linear models. For
+the following analysis we scaled the values of seed production for all
+the species with mean 0 and sd of 1. To test the effect of
+heterospecific pollen, we substracted to the seed set of hand cross
+pollination the seed set of heterospecific pollen treatments. In order
+to see correlations between heterospecific pollen effect and traits we
+performed Mantel test between the matrix of heterospecific pollen effect
+and the distance matrix of each trait (euclidean distances). Moreover,
+Mantel test was also conducted between heterospecific pollen effect and
+the square root of the matrix of phylogenetic distance due to
+improvement in the statistical power (Letten \& Cornwell 2014). We
+explored also the the relations between traits and heterospecific pollen
+effect through generalized mixed models where the response variable was
+heterospecific pollen effect, the independent variable the different
+traits and the random effects the different treatments per species.
+Moreover, pairwise evolutive distances were calculated with MEGA7 for
+two kinds of markers: 1) Internal transcribed spacer (ITS) and 2)
+ribulose-bisphosphate carboxylase (RBCL). The sequences of interest were
+downloaded from NCBI GenBank and the phylogenetic tree constructed by
+maximum likelihood with MEGA7.
 
-Phylogenetic signal of traits?
+\href{Jose}{Phylogenetic signal of traits?}
 
@@
 (3\%), for both species seems that fruit formation was induced by pollen
-on the stigma because of lack of fruit production with apomictic
-treatments.
+on the stigma because of lack of fruit production with treatments that
+tested for apomixis.
 
@@
 correlation between stigma width and stigma type exist. Trait
-correlations were also explored with \ldots{} and we found that\ldots{}
+correlations were also explored with GLMM
 
-Fix mantel test selfing rates and change it for compatibility
-index\ldots{}
-
-Fix this to GLMM? Yep I have to\ldots{}
+\href{Jose}{I have done it at the moment just for Compatibility system}
+\href{Jose}{Also I have to fix from mixed linear model to GLMM, just
+realize that}
 
@@
 
+\href{Jose}{Compatibility index don´t multiply per 100 from Lloyd}
+
 \newpage
@@
 What are the implications of the findings?
+
+Other idea based on the paper of Aizen 2007:
+
+He explains seed set in this way. O total number of ovules, d fraction
+of ovules that become seed set, b proportion of pollen grains that reach
+ovules, p number of pollen grains.
+
+\(S=dO(1-e^bp)\)
+
+\(S=dO(1-e^bp(HpEffect))\)
+
+but this Hp effect maybe can be divided at the same time in the
+interaction between recipient-donor with the main traits that drive the
+effect. Moreover, this should consider quantity of hp. lINEAR EFFECT?
+How to model this maybe talk with nacho.
 
@@
 -small pollen grains can get embeded
-
-\emph{Negative}
-
--Stigma clogging
-
-\begin{itemize}
-\item
-\end{itemize}
 

### 2018-12-15 Manuscript_draft/Manuscript_draft.Rmd
Jose, I made a lot of conceptual comments. I really love your intro, but we can do much more. Ask me if you have questions, as some of my notes may be a bit obscure, as I didn't developed those a lot.

@@
 ---
-title: working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect
+title: working title: Compatibility system and stigma size are the main predictors of heterospecific pollen effect
 author:
@@
 
-In most ecosystems, plant species normally coexist and share their floral visitors with other species @bascompte2003.
-From the plants’ perspective, this pollinator sharing can be positive due to facilitation @carvalheiro2014 or negative due to competition at the pre-pollination stage Pauw (2013).
+In most ecosystems, plant species normally coexist and share their floral visitors with other species @bascompte2003 [better ref is Waser et al 1996 on generalization: https://esajournals.onlinelibrary.wiley.com/doi/abs/10.2307/2265575]().
+From the plants’ perspective, pollinator sharing can be positive if there is facilitation amog plant species @carvalheiro2014 or negative due to competition at the pre-pollination stage Pauw (2013) [easier to say will be positive for some plants and negative for others, depending on the facilitation competition gradient]().
 An increasing number of visits often correlates with higher chances of fertilization @engel2003.
-However this is not always the case, among these possible flower visitors there are also nectar robbers and pollen thieves @inouye1980.
+However this is not always the case, among these possible flower visitors there are also nectar robbers and pollen thieves @inouye1980 [See also Magrach et al 2017 Nat Ecol Evol].
 Receiving both sufficient quantity and quality deposited on the stigma is thus highly relevant to the pollination success of the plant @aizen2007.
@@
 Foreign pollen arrival can play an important role in plant species fitness but outcomes are variable and appear to be context dependent as there is not always a decrease in fitness @morales2008.
-Some of this variation is likely due to the enormous variability of foreign pollen transferred across systems ranging from between 0 and 75 percent but most studies report ranges of heterospecific pollen between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012; @ashman2013; @fang2013, yet even these relatively low amounts of heterospecific pollen transferred can decrease fitness greatly @thomson1982.
+Some of this variation is likely due to the enormous variability of foreign pollen transferred across systems ranging from 0 to 75 percent.
+However, most studies report ranges of heterospecific pollen between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012; @ashman2013; @fang2013, yet even these relatively low amounts of heterospecific pollen transferred can decrease fitness greatly @thomson1982.
 While we now have some understanding of the impacts of heterospecific pollen quantity, we have less understanding of other factors that could be driving the variation in impacts upon fitness.
 @ashman2013 postulated the first predictive framework that identifies a need to understand how plant traits might mediate heterospecific pollen effect, whereby mating system and pollen size were predicted to potentially mediate the impact of foreign pollen transfer on plant fitness.
-This concept is supported by other studies, such as @tong2016 that demonstrate an asymmetrical effect in 6 species of *Pedicularis* whereby the pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
-While this suggests that the impacts of heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
+This concept is supported by specific case studies, such as @tong2016 that demonstrate an asymmetrical effect in 6 species of *Pedicularis* whereby the pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
+While this suggests that the impacts of heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a general trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
+[this pargraph is very good!]()
 
@@
 
-Given the large variability in mating systems across populations @whitehead2018, it is difficult to determine potential impacts upon HP transfer yet incompatibility system is another plant trait that appears to play an important role in foreign pollen effect whereby species that are self incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
+Incompatibility system is another plant trait that appears to play an important role in foreign pollen effect.
+Species that are self incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
+However, note the large variability in mating systems across populations @whitehead2018 [...]().
 The type of incompatibility, (i.e.
 whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style @barrett1988.
-This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.
-Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
-Moreover, other traits such as number of pollen grains per flower and number of ovules have been traditionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF).
-Selfer species are known to have a reduction of herkogamy (REF) and less pollen production per ovule (REF) which can be interpretated as a reduction of pollen exported into the community.
+This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.[if you introduce this, I eexpect you will use it in your analysis, remove?]() [Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018)- IB this is a side problem for you, mention just once, and maybe in discusion.
+Now it has a lot of weigth.]().
+Moreover, other traits such as number of pollen grains per flower and number of ovules have been traditionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF) .
+Selfer species are known to have a reduction of herkogamy (REF) and less pollen production per ovule (REF) which can be interpretated as a reduction of pollen exported into the community [so, pollen and ovules are important by themselfs, or only because correlated?
+Unclear what your point is]().
 Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
@@
 
-Species with similar traits are more closely related  XXXXXXXXX.
+Species with similar traits are more closely related  XXXXXXXXX [I would say no.
+species closely related usually have similar traits, specally if those are phylogenetially conserved]().
 (Refs?
@@
 ).
-Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
+
+[here you change topic, new paragraph?]() Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
 Given these are generally the ones that receive greater loads of heterospecific pollen Fang and Huang (2013) and unrelated species are more likely to coexist  with other species due to less niche overlap (Ref),  understanding the role of foreign pollen from distantly related species thus deserves greater attention in understanding coexistence blah blahXXXXX refs..
@@
 The species selected (**Table 1**) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
-The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1), heterogeneous traits, low structural flower complexity and fast life cycle.
+The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1)[I would explain more the bauty of our nested dessign to ensure close and far distance simultaneously](), heterogeneous traits, low structural flower complexity and fast life cycle.
 For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).
@@
 
-Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10).
-Therefore, 180 different combinations were perform with N=10.
+Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) [this second I don't get, maybe explain it's ultility.]().
+Therefore, 180 different combinations were performed with N=10 per combination.
 Seed set was the proxy of effect for all our treatments.
-Moreover, hand cross pollination, hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
-Flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
+Moreover, hand cross pollination [100% cross, right?
+Clarify](), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
+All?¿ flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
 Hand-pollination was conducted with 3-4 gentle touches on the stigma surface.
-The mixes of pollen were realized on an eppendorf based on the pollen counts maded with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species).
+[The mixes of pollen were realized on an eppendorf based on the pollen counts made with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species)-IB explain better and give a bit more of detail]().
 In order to confirm that the treatments applied were 50-50 percent pollen, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
@@
 The traits measured for each species were pollen per anther, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length.
-Moreover stigma type was tested.
+Moreover stigma type [explain]() was tested.
 Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer.
-Previously anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds.
+Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds.
 Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
 The different morphometrical traits were measured with a digital stereomicrospe.
-Levels of self incompatibility were estimated by dividing the the fruit set of hand self pollination by hand cross pollination @lloyd1992.
+Levels of self incompatibility were estimated by dividing the fruit set of hand self pollination by hand cross pollination @lloyd1992.
 
@@
 Moreover, Mantel test was also conducted between heterospecific pollen effect and the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).
-We explored also the the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species.
+[all is here, but I would break it by questions and give a bit more detail, to avoid overwhelm the reader]() We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species [Here I think you should think if this controls for the non independency of donors and recipients.
+I think not.
+Maybe look onto matrix regresions?).
 Moreover, pairwise evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL).
-The sequences of interest were downloaded from NCBI GenBank and the phylogenetic tree constructed by maximum likelihood with MEGA7.
+The sequences of interest were downloaded from NCBI GenBank and the phylogenetic tree constructed by maximum likelihood with MEGA7.[Make a section on how you contrsucted phylogeny]().
+
+[I would explain three test.
+0) treatment effects with GLM's, 1) Mantels: relative effects, 2) GLM's or matrix models: Absolute effects and explain them in three independent paragraphs including a rationale of why]()
 
@@
 Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine.
-The 100% foreign pollen treatments barely produced seeds or fruits and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial.
-Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases.
+Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine.
+The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial- IB Unclear]().
+Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment]().
 *S.
@@
 annuum* produced some fruits (9%) of both small and normal size and finally *S.
-melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.
+melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()
 
@@
 The treatments presented are hand cross pollination, hand self pollination, natural selfing and apomixis (emasculated flowers).
+[turn into a figure somehow?]()
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
@@
 
-Mantel test indicates that a possible correlation exist between heterospecific pollen effect and the evolutive distances, for ITS and RBCL markers we had r coefficients of 0.29 and 0.25 respectively p<0.05.
-Moreover, Mantel test indicates that also a possible correlation between stigma width and stigma type exist.
+Mantel test indicates that a possible??
+[It exists!]() correlation exist between heterospecific pollen effect and the evolutive relative distances, for ITS and RBCL markers we had r coefficients of 0.29 and 0.25 respectively p<0.05 [think on a figure - maybe using NMDS]().
+Moreover, Mantel test indicates that also a possible??
+correlation between stigma width and stigma type exist (stats??).
 Trait correlations were also explored with GLMM
@@
 library(cowplot)
-model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
+model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv) #I don't get the random here. I think you need a better analysis.
 ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
@@
 but this Hp effect maybe can be divided at the same time in the interaction between recipient-donor with the main traits that drive the effect.
-Moreover, this should consider quantity of hp.
-lINEAR EFFECT?
-How to model this maybe talk with nacho.
+IB: maybe just a weighting factor 0-1 depending on trait matching?
+If effect of hetero is 0, it cancells out the term, if is maximum, it *1
+
+Moreover, this should consider quantity of hp. lINEAR EFFECT? How to model this maybe talk with nacho. IB: In the absence of data you can try linearity, but also a sigmoidal.
+
+IB: Cool!
+se also Morris et al 2010 Ecology on how to add to AIzen curve, the effects of a second curve describing the negative effect of hetero.
+Morris apporach is mathematically more robust if you can model the second curve of hp effects.
+
+I also think you should use this for another paper and look into Morales -Castilla TREE paper inferring interactions. I can see a similar idea where you use a set of matrix you can multiply. 
+1) A matrix of plant-plant pollinator influence ( a lo carvalehire 2014). This tells you which plants may get exposed to hp pollen from empirical plant pollinator networks
+2) you matrix of plant plant ht effect (0-1) or a proxy based on phylogeny of trait similarity. This is also easy to quantify.
+3) A vector of sensitive recipient traits.
+ to create the probability of ht effects. I really like this ideas to link to community ecology.
 
@@
 
+IB: Think also on using tree analysis to test if hp effect depends on complex trait combinations.
+Tree analysis are great when two different strategies lead to the same outcome.
+This would never been pick up by GLMs.
+The r package is party{} .
+You can see an example applied to birds is Sol et al 2010 Science.
+Ask me if you want more details or code examples.
+
 # CONCLUSIONS

### 2018-12-19 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 ---
-title: working title: Compatibility system and stigma size are the main predictors of heterospecific pollen effect
+title: working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect
 author:
@@
 library("knitr")
+library("ggplot2")
+library("extrafont")
 
@@
 
-In most ecosystems, plant species normally coexist and share their floral visitors with other species @bascompte2003 [better ref is Waser et al 1996 on generalization: https://esajournals.onlinelibrary.wiley.com/doi/abs/10.2307/2265575]().
-From the plants’ perspective, pollinator sharing can be positive if there is facilitation amog plant species @carvalheiro2014 or negative due to competition at the pre-pollination stage Pauw (2013) [easier to say will be positive for some plants and negative for others, depending on the facilitation competition gradient]().
+In most ecosystems, plant species normally coexist and share their floral visitors with other species @waser1996.
+From the plants’ perspective, pollinator sharing can be positive for some plants @carvalheiro2014 or negative for others @pauw2013, depending on the facilitation gradient.
 An increasing number of visits often correlates with higher chances of fertilization @engel2003.
-However this is not always the case, among these possible flower visitors there are also nectar robbers and pollen thieves @inouye1980 [See also Magrach et al 2017 Nat Ecol Evol].
+However this is not always the case, among these possible flower visitors there are also nectar robbers and pollen thieves @inouye1980; @magrach2017.
 Receiving both sufficient quantity and quality deposited on the stigma is thus highly relevant to the pollination success of the plant @aizen2007.
@@
 While this suggests that the impacts of heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a general trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
-[this pargraph is very good!]()
 
@@
 whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style @barrett1988.
-This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.[if you introduce this, I eexpect you will use it in your analysis, remove?]() [Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018)- IB this is a side problem for you, mention just once, and maybe in discusion.
+This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.
+[if you introduce this,I eexpect you will use it in your analysis, remove]() [Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018)- IB this is a side problem for you, mention just once, and maybe in discusion.
 Now it has a lot of weigth.]().
@@
 Seed set was the proxy of effect for all our treatments.
-Moreover, hand cross pollination [100% cross, right?
-Clarify](), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
-All?¿ flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
+Moreover, hand cross pollination (between individuals of the same species), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
+For the treatments with foreign pollen and hand cross pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
 Hand-pollination was conducted with 3-4 gentle touches on the stigma surface.
@@
 kable(table, format="markdown")
+```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species.
+The y axis is the proportion of ovules converted to seed in percentage.
+The different, treatments which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis.
+More information about this treatments can be found in Methods and Appendices."}
+
+load("r_biology.RData")
+
+ggplot(bio,aes(x=Species,y=value,fill=variable))+
+  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
+  theme_bw()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
+  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"))+
+  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))
+
 ```

### 2018-12-19 Manuscript_draft/Manuscript_draft.tex
changes

@@
 In most ecosystems, plant species normally coexist and share their
-floral visitors with other species Bascompte et al. (2003). From the
-plants' perspective, this pollinator sharing can be positive due to
-facilitation Carvalheiro et al. (2014) or negative due to competition at
-the pre-pollination stage Pauw (2013). An increasing number of visits
-often correlates with higher chances of fertilization Engel and Irwin
-(2003). However this is not always the case, among these possible flower
-visitors there are also nectar robbers and pollen thieves Inouye (1980).
-Receiving both sufficient quantity and quality deposited on the stigma
-is thus highly relevant to the pollination success of the plant Aizen
-and Harder (2007).
+floral visitors with other species Waser et al. (1996). From the plants'
+perspective, pollinator sharing can be positive for some plants
+Carvalheiro et al. (2014) or negative for others Pauw (2013), depending
+on the facilitation gradient. An increasing number of visits often
+correlates with higher chances of fertilization Engel and Irwin (2003).
+However this is not always the case, among these possible flower
+visitors there are also nectar robbers and pollen thieves Inouye (1980);
+Magrach et al. (2017). Receiving both sufficient quantity and quality
+deposited on the stigma is thus highly relevant to the pollination
+success of the plant Aizen and Harder (2007).
 
@@
 Traveset (2008). Some of this variation is likely due to the enormous
-variability of foreign pollen transferred across systems ranging from
-between 0 and 75 percent but most studies report ranges of
-heterospecific pollen between 0 and 20 percent of the total pollen load
-Bartomeus et al. (2008) Montgomery and Rathcke (2012); Ashman and
-Arceo-Gómez (2013); Fang and Huang (2013), yet even these relatively low
-amounts of heterospecific pollen transferred can decrease fitness
-greatly Thomson et al. (1982). While we now have some understanding of
-the impacts of heterospecific pollen quantity, we have less
-understanding of other factors that could be driving the variation in
-impacts upon fitness. Ashman and Arceo-Gómez (2013) postulated the first
-predictive framework that identifies a need to understand how plant
-traits might mediate heterospecific pollen effect, whereby mating system
-and pollen size were predicted to potentially mediate the impact of
-foreign pollen transfer on plant fitness. This concept is supported by
-other studies, such as Tong and Huang (2016) that demonstrate an
-asymmetrical effect in 6 species of \emph{Pedicularis} whereby the
-pollen of long styled species was able to grow the full length of the
-style on short styled species but not vice versa. While this suggests
-that the impacts of heterospecific pollen may differ among pollen donor
-and recipient, few studies have been conducted to ascertain whether this
-pattern is in fact a trend or to identify the extent to which other
-plant traits are critical to heterospecific pollen impacts.
+variability of foreign pollen transferred across systems ranging from 0
+to 75 percent. However, most studies report ranges of heterospecific
+pollen between 0 and 20 percent of the total pollen load Bartomeus et
+al. (2008) Montgomery and Rathcke (2012); Ashman and Arceo-Gómez (2013);
+Fang and Huang (2013), yet even these relatively low amounts of
+heterospecific pollen transferred can decrease fitness greatly Thomson
+et al. (1982). While we now have some understanding of the impacts of
+heterospecific pollen quantity, we have less understanding of other
+factors that could be driving the variation in impacts upon fitness.
+Ashman and Arceo-Gómez (2013) postulated the first predictive framework
+that identifies a need to understand how plant traits might mediate
+heterospecific pollen effect, whereby mating system and pollen size were
+predicted to potentially mediate the impact of foreign pollen transfer
+on plant fitness. This concept is supported by specific case studies,
+such as Tong and Huang (2016) that demonstrate an asymmetrical effect in
+6 species of \emph{Pedicularis} whereby the pollen of long styled
+species was able to grow the full length of the style on short styled
+species but not vice versa. While this suggests that the impacts of
+heterospecific pollen may differ among pollen donor and recipient, few
+studies have been conducted to ascertain whether this pattern is in fact
+a general trend or to identify the extent to which other plant traits
+are critical to heterospecific pollen impacts.
 
@@
 
-Given the large variability in mating systems across populations
-Whitehead et al. (2018), it is difficult to determine potential impacts
-upon HP transfer yet incompatibility system is another plant trait that
-appears to play an important role in foreign pollen effect whereby
-species that are self incompatible have stronger barriers to
-heterospecific pollen than self-compatible species Ashman and
-Arceo-Gómez (2013). The type of incompatibility, (i.e.~whether
+Incompatibility system is another plant trait that appears to play an
+important role in foreign pollen effect. Species that are self
+incompatible have stronger barriers to heterospecific pollen than
+self-compatible species Ashman and Arceo-Gómez (2013). However, note the
+large variability in mating systems across populations Whitehead et al.
+(2018) \href{}{\ldots{}}. The type of incompatibility, (i.e.~whether
 sporophytic or gametophytic) is related to the location of pollen
@@
 with greater negative effect than sporophytic recognistion Ashman and
-Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a bit
-obscured by the variability within species, however species that are
-strong selfers or strong outcrossers have less variablity in mating
-systems and predictions of effect could be more realistic (see figure 1
-from Whitehead et al. (2018)). Moreover, other traits such as number of
-pollen grains per flower and number of ovules have been traditionally
-associated with the type of incompatibility system where species with
-higher pollen ovule ratios are predicted to be xenogamous and species
-with low pollen ovule ratios autogamous (REF). Selfer species are known
-to have a reduction of herkogamy (REF) and less pollen production per
-ovule (REF) which can be interpretated as a reduction of pollen exported
-into the community. Other morphological traits, like stigma size can be
-determinant for the total pollen quatity that a stigma can receive and
-therefore related to do that pollen size would also play an important
-role. Example with pollen here.
+Arceo-Gómez (2013). \href{}{if you introduce this,I eexpect you will use
+it in your analysis, remove} (Nonetheless, an effect of foreign pollen
+is a bit obscured by the variability within species, however species
+that are strong selfers or strong outcrossers have less variablity in
+mating systems and predictions of effect could be more realistic (see
+figure 1 from Whitehead et al. 2018)- IB this is a side problem for you,
+mention just once, and maybe in discusion. Now it has a lot of
+weigth.)(). Moreover, other traits such as number of pollen grains per
+flower and number of ovules have been traditionally associated with the
+type of incompatibility system where species with higher pollen ovule
+ratios are predicted to be xenogamous and species with low pollen ovule
+ratios autogamous (REF) . Selfer species are known to have a reduction
+of herkogamy (REF) and less pollen production per ovule (REF) which can
+be interpretated as a reduction of pollen exported into the community
+\href{}{so, pollen and ovules are important by themselfs, or only
+because correlated? Unclear what your point is}. Other morphological
+traits, like stigma size can be determinant for the total pollen quatity
+that a stigma can receive and therefore related to do that pollen size
+would also play an important role. Example with pollen here.
 
@@
 
-Species with similar traits are more closely related XXXXXXXXX. (Refs?
-Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang
-(2016) ). Several studies predict that the impact of HP transfer is
-likely to be greater for closely related species (Ashman and Arceo-Gómez
-(2013)). Few studies however, have focused on the impacts of
-heterospecific pollen of distantly related species Thomson et al. (1982)
-Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects
-and most stigmas have been found to carry multiple species of foreign
-pollen with little attention to degree of relatedness (Arceo-Gómez and
-Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
-transfer networks here such as\ldots{} ). Further, a majority of plant
-species are generalist and thus receive visits from multiple different
-pollinators. Given these are generally the ones that receive greater
-loads of heterospecific pollen Fang and Huang (2013) and unrelated
-species are more likely to coexist with other species due to less niche
-overlap (Ref), understanding the role of foreign pollen from distantly
-related species thus deserves greater attention in understanding
-coexistence blah blahXXXXX refs.. Notwithstanding, the effect of
-heterospecific pollen of far and close related species at community
-level remains to be explored beyond single pairwise interactions.
+Species with similar traits are more closely related XXXXXXXXX \href{}{I
+would say no. species closely related usually have similar traits,
+specally if those are phylogenetially conserved}. (Refs? Brown and
+Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016) ).
+Several studies predict that the impact of HP transfer is likely to be
+greater for closely related species (Ashman and Arceo-Gómez (2013)). Few
+studies however, have focused on the impacts of heterospecific pollen of
+distantly related species Thomson et al. (1982) Galen and Gregory (1989)
+Neiland and Wilcock (1999). Yet, most insects and most stigmas have been
+found to carry multiple species of foreign pollen with little attention
+to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang
+(2013) ; also cite studies from pollen transfer networks here such
+as\ldots{} ).
+
+\href{}{here you change topic, new paragraph?} Further, a majority of
+plant species are generalist and thus receive visits from multiple
+different pollinators. Given these are generally the ones that receive
+greater loads of heterospecific pollen Fang and Huang (2013) and
+unrelated species are more likely to coexist with other species due to
+less niche overlap (Ref), understanding the role of foreign pollen from
+distantly related species thus deserves greater attention in
+understanding coexistence blah blahXXXXX refs.. Notwithstanding, the
+effect of heterospecific pollen of far and close related species at
+community level remains to be explored beyond single pairwise
+interactions.
 
@@
 selection was based on close/distant related species (see phylogenetic
-tree for relatedness fig 1), heterogeneous traits, low structural flower
-complexity and fast life cycle. For the purpose of the experiment all
-the species where considered as pollen recipient and as pollen donor
-(see interaction matrix, fig 2). Species were watered once or twice per
-day and fertilized weekly (NPK 23: 3.95: 14).
+tree for relatedness fig 1)\href{}{I would explain more the bauty of our
+nested dessign to ensure close and far distance simultaneously},
+heterogeneous traits, low structural flower complexity and fast life
+cycle. For the purpose of the experiment all the species where
+considered as pollen recipient and as pollen donor (see interaction
+matrix, fig 2). Species were watered once or twice per day and
+fertilized weekly (NPK 23: 3.95: 14).
 
@@
 with 50\% conspecific pollen and 50\% heterospecific pollen and a second
-one with 100\% foreign pollen (N=10). Therefore, 180 different
-combinations were perform with N=10. Seed set was the proxy of effect
-for all our treatments. Moreover, hand cross pollination, hand self
-pollination, apomixis (bagged emasculated flowers) and natural selfing
-were tested for each species (N=10). Flowers were emasculated the day
-prior anthesis and hand pollinated next day with a toothpick.
-Hand-pollination was conducted with 3-4 gentle touches on the stigma
-surface. The mixes of pollen were realized on an eppendorf based on the
-pollen counts maded with Neubaeur chamber (each anther was counted 4
-times for 20 different anthers per species). In order to confirm that
-the treatments applied were 50-50 percent pollen, for each focal species
-the total stigmatic load of pollen was counted from one donor of each
-family (N=3).
+one with 100\% foreign pollen (N=10) \href{}{this second I don't get,
+maybe explain it's ultility.}. Therefore, 180 different combinations
+were performed with N=10 per combination. Seed set was the proxy of
+effect for all our treatments. Moreover, hand cross pollination (between
+individuals of the same species), hand self pollination, apomixis
+(bagged emasculated flowers) and natural selfing were tested for each
+species (N=10). For the treatments with foreign pollen and hand cross
+pollination, flowers were emasculated the day prior anthesis and hand
+pollinated next day with a toothpick. Hand-pollination was conducted
+with 3-4 gentle touches on the stigma surface. \href{}{The mixes of
+pollen were realized on an eppendorf based on the pollen counts made
+with Neubaeur chamber (each anther was counted 4 times for 20 different
+anthers per species)-IB explain better and give a bit more of detail}.
+In order to confirm that the treatments applied were 50-50 percent
+pollen, for each focal species the total stigmatic load of pollen was
+counted from one donor of each family (N=3).
 
@@
 ovules, stigma width and length and stigmatic area, style width and
-length, ovary width and length. Moreover stigma type was tested. Pollen
-was counted for 20 anthers of each species with 4 replicates per sample
-with an hemocytometer. Previously anthers were squashed on a known
-solution with the pippete tip and homogeneize with a vortex for 30
-seconds. Ovule number was counted with the help of an stereomicroscope
-and a small grid over a petri dish from 15 randomly selected flowers.
-The different morphometrical traits were measured with a digital
-stereomicrospe. Levels of self incompatibility were estimated by
-dividing the the fruit set of hand self pollination by hand cross
+length, ovary width and length. Moreover stigma type \href{}{explain}
+was tested. Pollen was counted for 20 anthers of each species with 4
+replicates per sample with an hemocytometer. Previously, anthers were
+squashed on a known solution with the pippete tip and homogeneize with a
+vortex for 30 seconds. Ovule number was counted with the help of an
+stereomicroscope and a small grid over a petri dish from 15 randomly
+selected flowers. The different morphometrical traits were measured with
+a digital stereomicrospe. Levels of self incompatibility were estimated
+by dividing the fruit set of hand self pollination by hand cross
 pollination Lloyd and Schoen (1992).
@@
 the square root of the matrix of phylogenetic distance due to
-improvement in the statistical power (Letten \& Cornwell 2014). We
-explored also the the relations between traits and heterospecific pollen
-effect through generalized mixed models where the response variable was
-heterospecific pollen effect, the independent variable the different
-traits and the random effects the different treatments per species.
-Moreover, pairwise evolutive distances were calculated with MEGA7 for
-two kinds of markers: 1) Internal transcribed spacer (ITS) and 2)
+improvement in the statistical power (Letten \& Cornwell 2014).
+\href{}{all is here, but I would break it by questions and give a bit
+more detail, to avoid overwhelm the reader} We explored also the
+relations between traits and heterospecific pollen effect through
+generalized mixed models where the response variable was heterospecific
+pollen effect, the independent variable the different traits and the
+random effects the different treatments per species {[}Here I think you
+should think if this controls for the non independency of donors and
+recipients. I think not. Maybe look onto matrix regresions?). Moreover,
+pairwise evolutive distances were calculated with MEGA7 for two kinds of
+markers: 1) Internal transcribed spacer (ITS) and 2)
 ribulose-bisphosphate carboxylase (RBCL). The sequences of interest were
 downloaded from NCBI GenBank and the phylogenetic tree constructed by
-maximum likelihood with MEGA7.
+maximum likelihood with MEGA7.\href{}{Make a section on how you
+contrsucted phylogeny}.
+
+\href{}{I would explain three test. 0) treatment effects with GLM's, 1)
+Mantels: relative effects, 2) GLM's or matrix models: Absolute effects
+and explain them in three independent paragraphs including a rationale
+of why}
 
@@
 when species where look at species level they respond differently even
-within the same family, for instance for two species of the Brassicaceae
-family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
-very contrasting effects of foreign pollen where for the first one, all
-donors reduce seed set significatively and for the second, just two
-species did out of nine. The 100\% foreign pollen treatments barely
-produced seeds or fruits and just for \emph{Sinapis alba} we did not
-find significant differences between the hand cross pollination and one
-treatment with pollen from a confamilial. Solanaceae species with berry
-fruit type developed small fruits or even normal fruits in some cases.
-\emph{S. lycopersicum} seems to produced small fruits (35\% of the
-treatments) independently of pollen and pollen donor due to also
-apomictic treatments did, never normal size. \emph{C. annuum} produced
-some fruits (9\%) of both small and normal size and finally \emph{S.
-melongena} produced seedless normal fruits with just confamilial pollen
-(3\%), for both species seems that fruit formation was induced by pollen
-on the stigma because of lack of fruit production with treatments that
-tested for apomixis.
+within the same family \href{}{rephrase and maybe test statistically?},
+for instance for two species of the Brassicaceae family \emph{Brassica
+oleracea} and \emph{Eruca versicaria} we found very contrasting effects
+of foreign pollen where for the first one, all donors reduce seed set
+significatively and for the second, just two species did out of nine.
+The 100\% foreign pollen treatments barely produced seeds or fruits
+\href{}{and just for \emph{Sinapis alba} we did not find significant
+differences between the hand cross pollination and one treatment with
+pollen from a confamilial- IB Unclear}. Solanaceae species with berry
+fruit type developed small fruits or even normal fruits in some cases
+\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
+small fruits (35\% of the treatments) independently of pollen and pollen
+donor due to also apomictic treatments did, never normal size. \emph{C.
+annuum} produced some fruits (9\%) of both small and normal size and
+finally \emph{S. melongena} produced seedless normal fruits with just
+confamilial pollen (3\%), for both species seems that fruit formation
+was induced by pollen on the stigma because of lack of fruit production
+with treatments that tested for apomixis.\href{}{clarify this
+descriptive statistics part- Also a figure with a summary of the
+treatments effect would be cool, or at least in the appendices}
 
@@
 pollination, hand self pollination, natural selfing and apomixis
-(emasculated flowers).
+(emasculated flowers). \href{}{turn into a figure somehow?}
 
@@
 
-Mantel test indicates that a possible correlation exist between
-heterospecific pollen effect and the evolutive distances, for ITS and
-RBCL markers we had r coefficients of 0.29 and 0.25 respectively
-p\textless{}0.05. Moreover, Mantel test indicates that also a possible
-correlation between stigma width and stigma type exist. Trait
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\caption{Barplot with the different treatments that provide information
+of the reproductive biology of the ten species. The y axis is the
+proportion of ovules converted to seed in percentage. The different,
+treatments which are presented in the legend are, hand cross
+pollination, hand self pollination, natural selfing and apomixis. More
+information about this treatments can be found in Methods and
+Appendices.}
+\end{figure}
+
+Mantel test indicates that a possible?? \href{}{It exists!} correlation
+exist between heterospecific pollen effect and the evolutive relative
+distances, for ITS and RBCL markers we had r coefficients of 0.29 and
+0.25 respectively p\textless{}0.05 \href{}{think on a figure - maybe
+using NMDS}. Moreover, Mantel test indicates that also a possible??
+correlation between stigma width and stigma type exist (stats??). Trait
 correlations were also explored with GLMM
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
 \caption{The effect of heterospecific pollen (scaled see set) is
@@
 interaction between recipient-donor with the main traits that drive the
-effect. Moreover, this should consider quantity of hp. lINEAR EFFECT?
-How to model this maybe talk with nacho.
+effect. IB: maybe just a weighting factor 0-1 depending on trait
+matching? If effect of hetero is 0, it cancells out the term, if is
+maximum, it *1
+
+Moreover, this should consider quantity of hp. lINEAR EFFECT? How to
+model this maybe talk with nacho. IB: In the absence of data you can try
+linearity, but also a sigmoidal.
+
+IB: Cool! se also Morris et al 2010 Ecology on how to add to AIzen
+curve, the effects of a second curve describing the negative effect of
+hetero. Morris apporach is mathematically more robust if you can model
+the second curve of hp effects.
+
+I also think you should use this for another paper and look into Morales
+-Castilla TREE paper inferring interactions. I can see a similar idea
+where you use a set of matrix you can multiply. 1) A matrix of
+plant-plant pollinator influence ( a lo carvalehire 2014). This tells
+you which plants may get exposed to hp pollen from empirical plant
+pollinator networks 2) you matrix of plant plant ht effect (0-1) or a
+proxy based on phylogeny of trait similarity. This is also easy to
+quantify. 3) A vector of sensitive recipient traits. to create the
+probability of ht effects. I really like this ideas to link to community
+ecology.
 
@@
 
+IB: Think also on using tree analysis to test if hp effect depends on
+complex trait combinations. Tree analysis are great when two different
+strategies lead to the same outcome. This would never been pick up by
+GLMs. The r package is party\{\} . You can see an example applied to
+birds is Sol et al 2010 Science. Ask me if you want more details or code
+examples.
+
 \section{CONCLUSIONS}\label{conclusions}
@@
 
-\hypertarget{ref-bascompte2003}{}
-Bascompte, J., P. Jordano, C. J. Melián, and J. M. Olesen. 2003. The
-nested assembly of plant--animal mutualistic networks. Proceedings of
-the National Academy of Sciences 100:9383--9387.
-
 \hypertarget{ref-carvalheiro2014}{}
@@
 
+\hypertarget{ref-magrach2017}{}
+Magrach, A., J. P. González-Varo, M. Boiffier, M. Vilà, and I.
+Bartomeus. 2017. Honeybee spillover reshuffles pollinator diets and
+affects plant reproductive success. Nature ecology \& evolution 1:1299.
+
 \hypertarget{ref-montgomery2012}{}
@@
 Reviews in Plant Sciences 27:221--238.
+
+\hypertarget{ref-pauw2013}{}
+Pauw, A. 2013. Can pollination niches facilitate plant coexistence?
+Trends in ecology \& evolution 28:30--37.
 
@@
 transfer. New Phytologist 211:1452--1461.
+
+\hypertarget{ref-waser1996}{}
+Waser, N. M., L. Chittka, M. V. Price, N. M. Williams, and J. Ollerton.
+1996. Generalization in pollination systems, and why it matters. Ecology
+77:1043--1060.
 

### 2018-12-19 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
+\newpage
+
 **Table 2**.
@@
 
+\newpage
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species.
 The y axis is the proportion of ovules converted to seed in percentage.
-The different, treatments which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis.
-More information about this treatments can be found in Methods and Appendices."}
+The different treatments (N=10) which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis.
+More information about these treatments can be found in Methods and Appendices."}
 
@@
   geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
-  theme_bw()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
-  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"))+
+  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
+  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"), legend.text=element_text(size=7))+
   scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2018-12-19 Manuscript_draft/Manuscript_draft.tex
edits

@@
 
+\newpage
+
 \textbf{Table 2}. Perecentage of seeds produced per ovule for the ten
@@
 
+\newpage
+
 \begin{figure}
@@
 of the reproductive biology of the ten species. The y axis is the
-proportion of ovules converted to seed in percentage. The different,
-treatments which are presented in the legend are, hand cross
+proportion of ovules converted to seed in percentage. The different
+treatments (N=10) which are presented in the legend are, hand cross
 pollination, hand self pollination, natural selfing and apomixis. More
-information about this treatments can be found in Methods and
+information about these treatments can be found in Methods and
 Appendices.}
 \end{figure}
+
+\newpage
 

### 2018-12-19 Manuscript_draft/Manuscript_draft.Rmd
Reproductive biology plot and fixed some comments of Nacho

@@
   theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
-  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"), legend.text=element_text(size=7))+
+  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
   scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2018-12-19 Scripts/Traits/Reproductive_biology_treatments.R

@@ -45,7 +45,7 @@ bio$variable <- factor(bio$variable, levels = c("Hand cross pollination","Hand s
 
 ggplot(bio,aes(x=Species,y=value,fill=variable))+
   geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
-  theme_bw()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
+  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
   theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"))+
   scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))
 

### 2019-02-19 Manuscript_draft/Manuscript_draft.Rmd
some edits 3rd paragraph

--- 2018-12-19 Manuscript_draft/Manuscript_draft.Rmd
@@
 
-**Paragraph 1** General idea to our concept
-
 In most ecosystems, plant species normally coexist and share their floral visitors with other species @waser1996.
@@
 Receiving both sufficient quantity and quality deposited on the stigma is thus highly relevant to the pollination success of the plant @aizen2007.
-
-**Paragraph 2** Introducing topic and knowledge gap
 
@@
 
-**Paragraph 3** Expanding ideas with examples
+Plant traits are crucial to understand heterospecific pollen effect, but here it is important to notice that these traits can be seen from a donor perpective or a recipient one.
+In first place, when the donor is considered pollen size, pollen allelopathy and the relatedness could be the two main predictors of effect.
+How pollen size and allepothaty are involved in heterospecific pollen effect remains unclear yet.
+Herrera xxxx observed that small pollen is more likely to clogg the stigma, here we argue that although this is possible, the quantities of heterospecific pollen in nature are generally low as mentioned above and bigger pollen is generally related with higher pollen tube growth rate, which add another layer of complexity to the understanding the overall importance of this trait.
+When the pollen recipeint is taking into account style length, stigmatic area, number of ovules and incompatibility system seems to be the main predictors of effect.
+
+Example of flower morphology and the importance of stigmatic area Montgomery and rathcke 2012
+
+Species that are self-incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
+Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
+
+End this with pollen quantity stuff!!!
 
 Incompatibility system is another plant trait that appears to play an important role in foreign pollen effect.
-Species that are self incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
-However, note the large variability in mating systems across populations @whitehead2018 [...]().
+Species that are self incompatible have stronger barriers to heterospecific pollen than self-compatible species Ashman and Arceo-Gómez (2013).
+However, note the large variability in mating systems across populations Whitehead et al.
+(2018) .
+.
+.
+.
 The type of incompatibility, (i.e.
-whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style @barrett1988.
-This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.
-[if you introduce this,I eexpect you will use it in your analysis, remove]() [Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018)- IB this is a side problem for you, mention just once, and maybe in discusion.
-Now it has a lot of weigth.]().
+whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style Barrett (1988).
+This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion Ashman and Arceo-Gómez (2013).
+if you introduce this,I eexpect you will use it in your analysis, remove (Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from
+69 Whitehead et al. 2018)- IB this is a side problem for you, mention just once, and maybe in discusion.
+70 Now it has a lot of weigth.)(). Moreover, other traits such as number of pollen grains per flower and
+71 number of ovules have been traditionally associated with the type of incompatibility system where
+72 species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen
+73 ovule ratios autogamous (REF) . Selfer species are known to have a reduction of herkogamy (REF) and
+74 less pollen production per ovule (REF) which can be interpretated as a reduction of pollen exported
+75 into the community so, pollen and ovules are important by themselfs, or only because correlated?
+Unclear what your point is.
+Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
+Example with pollen here.
+
+...
+
 Moreover, other traits such as number of pollen grains per flower and number of ovules have been traditionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF) .
@@
 Example with pollen here.
-
-[This last bit of the paragraph is still under development](Jose)
 

### 2019-02-19 Manuscript_draft/Manuscript_draft.tex
some edits 3rd paragraph

@@
 
-\textbf{Paragraph 1} General idea to our concept
-
 In most ecosystems, plant species normally coexist and share their
@@
 success of the plant Aizen and Harder (2007).
-
-\textbf{Paragraph 2} Introducing topic and knowledge gap
 
@@
 
-\textbf{Paragraph 3} Expanding ideas with examples
+Plant traits are crucial to understand heterospecific pollen effect, but
+here it is important to notice that these traits can be seen from a
+donor perpective or a recipient one. In first place, when the donor is
+considered pollen size, pollen allelopathy and the relatedness could be
+the two main predictors of effect. How pollen size and allepothaty are
+involved in heterospecific pollen effect remains unclear yet. Herrera
+xxxx observed that small pollen is more likely to clogg the stigma, here
+we argue that although this is possible, the quantities of
+heterospecific pollen in nature are generally low as mentioned above and
+bigger pollen is generally related with higher pollen tube growth rate,
+which add another layer of complexity to the understanding the overall
+importance of this trait. When the pollen recipeint is taking into
+account style length, stigmatic area, number of ovules and
+incompatibility system seems to be the main predictors of effect.
+
+Example of flower morphology and the importance of stigmatic area
+Montgomery and rathcke 2012
+
+Species that are self-incompatible have stronger barriers to
+heterospecific pollen than self-compatible species Ashman and
+Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a bit
+obscured by the variability within species, however species that are
+strong selfers or strong outcrossers have less variablity in mating
+systems and predictions of effect could be more realistic (see figure 1
+from Whitehead et al. (2018)).
+
+End this with pollen quantity stuff!!!
 
@@
 large variability in mating systems across populations Whitehead et al.
-(2018) \href{}{\ldots{}}. The type of incompatibility, (i.e.~whether
-sporophytic or gametophytic) is related to the location of pollen
-recognition; sporophytic incompatibility relates to signaling at the
-stigma surface while gametophytic occurs within the style Barrett
-(1988). This later acting pollen recognition mechanism is associated
-with greater negative effect than sporophytic recognistion Ashman and
-Arceo-Gómez (2013). \href{}{if you introduce this,I eexpect you will use
-it in your analysis, remove} (Nonetheless, an effect of foreign pollen
-is a bit obscured by the variability within species, however species
-that are strong selfers or strong outcrossers have less variablity in
-mating systems and predictions of effect could be more realistic (see
-figure 1 from Whitehead et al. 2018)- IB this is a side problem for you,
-mention just once, and maybe in discusion. Now it has a lot of
-weigth.)(). Moreover, other traits such as number of pollen grains per
-flower and number of ovules have been traditionally associated with the
-type of incompatibility system where species with higher pollen ovule
-ratios are predicted to be xenogamous and species with low pollen ovule
+(2018) . . . . The type of incompatibility, (i.e.~whether sporophytic or
+gametophytic) is related to the location of pollen recognition;
+sporophytic incompatibility relates to signaling at the stigma surface
+while gametophytic occurs within the style Barrett (1988). This later
+acting pollen recognition mechanism is associated with greater negative
+effect than sporophytic recognistion Ashman and Arceo-Gómez (2013). if
+you introduce this,I eexpect you will use it in your analysis, remove
+(Nonetheless, an effect of foreign pollen is a bit obscured by the
+variability within species, however species that are strong selfers or
+strong outcrossers have less variablity in mating systems and
+predictions of effect could be more realistic (see figure 1 from 69
+Whitehead et al. 2018)- IB this is a side problem for you, mention just
+once, and maybe in discusion. 70 Now it has a lot of weigth.)().
+Moreover, other traits such as number of pollen grains per flower and 71
+number of ovules have been traditionally associated with the type of
+incompatibility system where 72 species with higher pollen ovule ratios
+are predicted to be xenogamous and species with low pollen 73 ovule
 ratios autogamous (REF) . Selfer species are known to have a reduction
-of herkogamy (REF) and less pollen production per ovule (REF) which can
-be interpretated as a reduction of pollen exported into the community
+of herkogamy (REF) and 74 less pollen production per ovule (REF) which
+can be interpretated as a reduction of pollen exported 75 into the
+community so, pollen and ovules are important by themselfs, or only
+because correlated? Unclear what your point is. Other morphological
+traits, like stigma size can be determinant for the total pollen quatity
+that a stigma can receive and therefore related to do that pollen size
+would also play an important role. Example with pollen here.
+
+\ldots{}
+
+Moreover, other traits such as number of pollen grains per flower and
+number of ovules have been traditionally associated with the type of
+incompatibility system where species with higher pollen ovule ratios are
+predicted to be xenogamous and species with low pollen ovule ratios
+autogamous (REF) . Selfer species are known to have a reduction of
+herkogamy (REF) and less pollen production per ovule (REF) which can be
+interpretated as a reduction of pollen exported into the community
 \href{}{so, pollen and ovules are important by themselfs, or only
@@
 would also play an important role. Example with pollen here.
-
-\href{Jose}{This last bit of the paragraph is still under development}
 
@@
 
-\hypertarget{ref-barrett1988}{}
-Barrett, S. C. 1988. The evolution, maintenance, and loss of
-self-incompatibility systems. Plant reproductive ecology: patterns and
-strategies:98--124.
-
 \hypertarget{ref-bartomeus2008}{}

### 2019-02-19 Scripts/Analysis/Total_pollen_Stigma_area_corr.R

@@ -14,6 +14,10 @@ stigma_area <- traits_all[,c(2,10)]
 str(stigma_area)
 
 stigma_area$species=as.character(stigma_area$species)
+stigma_width <- traits_all[,c(2,13)]
+stigma_width$species=as.character(stigma_width$species)
+
+
 
 str(total_pollen)
 total_pollen$focal=as.character(total_pollen$focal)
@@ -34,6 +38,9 @@ colnames(total_pollen)[1] <- "species"
 test <- merge(total_pollen, stigma_area, by="species")
 
 cor.test(test$total_pollen, test$stigma_area, method=c("pearson"))
+
+test <- merge(total_pollen, stigma_width, by="species")
+cor.test(test$total_pollen, test$stigma_width, method=c("pearson"))
 
 #No significant correlation was found
 #However, further corr should be explored

### 2019-02-20 Manuscript_draft/Manuscript_draft.Rmd
More changes in the intro

--- 2018-12-19 Manuscript_draft/Manuscript_draft.Rmd
@@
 
-**Paragraph 3** Expanding ideas with examples
-
-Incompatibility system is another plant trait that appears to play an important role in foreign pollen effect.
-Species that are self incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
-However, note the large variability in mating systems across populations @whitehead2018 [...]().
-The type of incompatibility, (i.e.
-whether sporophytic or gametophytic) is related to the location of pollen recognition; sporophytic incompatibility relates to signaling at the stigma surface while gametophytic occurs within the style @barrett1988.
-This later acting pollen recognition mechanism is associated with greater negative effect than sporophytic recognistion @ashman2013.
-[if you introduce this,I eexpect you will use it in your analysis, remove]() [Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018)- IB this is a side problem for you, mention just once, and maybe in discusion.
-Now it has a lot of weigth.]().
-Moreover, other traits such as number of pollen grains per flower and number of ovules have been traditionally associated with the type of incompatibility system where species with higher pollen ovule ratios are predicted to be xenogamous and species with low pollen ovule ratios autogamous (REF) .
-Selfer species are known to have a reduction of herkogamy (REF) and less pollen production per ovule (REF) which can be interpretated as a reduction of pollen exported into the community [so, pollen and ovules are important by themselfs, or only because correlated?
-Unclear what your point is]().
-Other morphological traits, like stigma size can be determinant for the total pollen quatity that a stigma can receive and therefore related to do that pollen size would also play an important role.
-Example with pollen here.
-
-[This last bit of the paragraph is still under development](Jose)
-
-**Paragraph 4** Maybe connect with paragrph above?
+Plant traits are crucial to understand heterospecific pollen effect, but here it is important to notice that these traits can be seen from a donor perpective or a recipient one.
+In first place, when the donor is considered pollen size and pollen allelopathy could be the two main predictors of effect.
+How pollen size and allepothaty are involved in heterospecific pollen effect remains unclear yet.
+For example, Herrera xxxx observed that small pollen is more likely to clogg the stigma, here we argue that although this is possible, the quantities of heterospecific pollen in nature are generally low as mentioned above and bigger pollen is generally related with higher pollen tube growth rate, which add another layer of complexity to the understanding of the overall importance of this trait.
+Moreover, pollen allelopathy is still an unclear field for pollination ecologist.
+When the pollen recipeint is taking into account style length, stigmatic area, flower morphology, number of ovules and incompatibility system seems to be the main predictors of effect.
+In the case of style length species with shorter styles will have greater heterospecific pollen effect due to pollen competition is more likely to occur and therefore ovule interference.
+Interestingly, differences of heterospecific pollen load has been shown to do not be influenced by flowr morphology (restricted or unrestricted), and the main predictor of the heterospecific pollen load was stigma size (REF).
+Therefore, if bigger stigmas can receive more hp pollen, a greater quantity of hp can be translated in a possible greater negative effect.
+For species that are self-incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
+Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
 

### 2019-02-20 Manuscript_draft/Manuscript_draft.tex
More changes in the intro

--- 2018-12-19 Manuscript_draft/Manuscript_draft.tex
@@
 
-\textbf{Paragraph 3} Expanding ideas with examples
-
-Incompatibility system is another plant trait that appears to play an
-important role in foreign pollen effect. Species that are self
-incompatible have stronger barriers to heterospecific pollen than
-self-compatible species Ashman and Arceo-Gómez (2013). However, note the
-large variability in mating systems across populations Whitehead et al.
-(2018) \href{}{\ldots{}}. The type of incompatibility, (i.e.~whether
-sporophytic or gametophytic) is related to the location of pollen
-recognition; sporophytic incompatibility relates to signaling at the
-stigma surface while gametophytic occurs within the style Barrett
-(1988). This later acting pollen recognition mechanism is associated
-with greater negative effect than sporophytic recognistion Ashman and
-Arceo-Gómez (2013). \href{}{if you introduce this,I eexpect you will use
-it in your analysis, remove} (Nonetheless, an effect of foreign pollen
-is a bit obscured by the variability within species, however species
-that are strong selfers or strong outcrossers have less variablity in
-mating systems and predictions of effect could be more realistic (see
-figure 1 from Whitehead et al. 2018)- IB this is a side problem for you,
-mention just once, and maybe in discusion. Now it has a lot of
-weigth.)(). Moreover, other traits such as number of pollen grains per
-flower and number of ovules have been traditionally associated with the
-type of incompatibility system where species with higher pollen ovule
-ratios are predicted to be xenogamous and species with low pollen ovule
-ratios autogamous (REF) . Selfer species are known to have a reduction
-of herkogamy (REF) and less pollen production per ovule (REF) which can
-be interpretated as a reduction of pollen exported into the community
-\href{}{so, pollen and ovules are important by themselfs, or only
-because correlated? Unclear what your point is}. Other morphological
-traits, like stigma size can be determinant for the total pollen quatity
-that a stigma can receive and therefore related to do that pollen size
-would also play an important role. Example with pollen here.
-
-\href{Jose}{This last bit of the paragraph is still under development}
-
-\textbf{Paragraph 4} Maybe connect with paragrph above?
+Plant traits are crucial to understand heterospecific pollen effect, but
+here it is important to notice that these traits can be seen from a
+donor perpective or a recipient one. In first place, when the donor is
+considered pollen size and pollen allelopathy could be the two main
+predictors of effect. How pollen size and allepothaty are involved in
+heterospecific pollen effect remains unclear yet. For example, Herrera
+xxxx observed that small pollen is more likely to clogg the stigma, here
+we argue that although this is possible, the quantities of
+heterospecific pollen in nature are generally low as mentioned above and
+bigger pollen is generally related with higher pollen tube growth rate,
+which add another layer of complexity to the understanding of the
+overall importance of this trait. Moreover, pollen allelopathy is still
+an unclear field for pollination ecologist. When the pollen recipeint is
+taking into account style length, stigmatic area, flower morphology,
+number of ovules and incompatibility system seems to be the main
+predictors of effect. In the case of style length species with shorter
+styles will have greater heterospecific pollen effect due to pollen
+competition is more likely to occur and therefore ovule interference.
+Interestingly, differences of heterospecific pollen load has been shown
+to do not be influenced by flowr morphology (restricted or
+unrestricted), and the main predictor of the heterospecific pollen load
+was stigma size (REF). Therefore, if bigger stigmas can receive more hp
+pollen, a greater quantity of hp can be translated in a possible greater
+negative effect. For species that are self-incompatible have stronger
+barriers to heterospecific pollen than self-compatible species Ashman
+and Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a
+bit obscured by the variability within species, however species that are
+strong selfers or strong outcrossers have less variablity in mating
+systems and predictions of effect could be more realistic (see figure 1
+from Whitehead et al. (2018)).
 

### 2019-02-20 Manuscript_draft/Manuscript_draft.Rmd
more edits paragraph 3

@@
 
-Plant traits are crucial to understand heterospecific pollen effect, but here it is important to notice that these traits can be seen from a donor perpective or a recipient one.
-In first place, when the donor is considered pollen size and pollen allelopathy could be the two main predictors of effect.
-How pollen size and allepothaty are involved in heterospecific pollen effect remains unclear yet.
-For example, Herrera xxxx observed that small pollen is more likely to clogg the stigma, here we argue that although this is possible, the quantities of heterospecific pollen in nature are generally low as mentioned above and bigger pollen is generally related with higher pollen tube growth rate, which add another layer of complexity to the understanding of the overall importance of this trait.
-Moreover, pollen allelopathy is still an unclear field for pollination ecologist.
-When the pollen recipeint is taking into account style length, stigmatic area, flower morphology, number of ovules and incompatibility system seems to be the main predictors of effect.
-In the case of style length species with shorter styles will have greater heterospecific pollen effect due to pollen competition is more likely to occur and therefore ovule interference.
-Interestingly, differences of heterospecific pollen load has been shown to do not be influenced by flowr morphology (restricted or unrestricted), and the main predictor of the heterospecific pollen load was stigma size (REF).
-Therefore, if bigger stigmas can receive more hp pollen, a greater quantity of hp can be translated in a possible greater negative effect.
+Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involve in the pollen-pistil interaction make difficult to unravel what are the main traits in driving the effect.
+On the one hand the main predictive traits of effect from the donor perspective are pollen size, pollen allelopathy and pollen apertures (REFS).
+In Ashamn 2013 small pollen is predicted to cause a greater fitness decrease, although this can be true there are also other possibilities to consider which can obscure a predictive framework like big pollen can clogg small stigmas with fewer pollen grains, bigger stigmas are less likely to be clogged by small pollen grains and bigger pollen can outcompete smaller pollen grains due to faster pollen tube growth rate (REF).
+On the other hand  the main recipient traits that can drive heterospecific pollen effect are: stigma size, style length, number of ovules, incompatibility system and flower morphology (REFS).
+In first place, greater stigmatic area is related with greater amount of heterospecific pollen (REF) and therefore possibly a greater negative effect (REF).
+Species with shorter styles are more likely to be vulnerable to heterospecific pollen effect (REF).
 For species that are self-incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
 Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
+All in all, there is a need to deepen in the understanding of the relative importance of these traits, due to we still do not know what are the main traits in driving the effect with all these possible combinations that can occur in nature.
 
@@
 
-Species with similar traits are more closely related  XXXXXXXXX [I would say no.
-species closely related usually have similar traits, specally if those are phylogenetially conserved]().
+Species closely related are more likely to have similar traits XXXXXXXXX.
 (Refs?
@@
 
-[here you change topic, new paragraph?]() Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
+Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
 Given these are generally the ones that receive greater loads of heterospecific pollen Fang and Huang (2013) and unrelated species are more likely to coexist  with other species due to less niche overlap (Ref),  understanding the role of foreign pollen from distantly related species thus deserves greater attention in understanding coexistence blah blahXXXXX refs..
 Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.
-
-**Paragraph 5** Introducing our experiment
-
 In this study we investigated how floral reproductive traits and relatedness mediate the impact of HP transfer by asking the following research questions : To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
@@
 
-Other idea based on the paper of Aizen 2007:
-
-He explains seed set in this way. O total number of ovules, d fraction of ovules that become seed set, b proportion of pollen grains that reach ovules, p number of pollen grains.
-
-$S=dO(1-e^bp)$
-
-$S=dO(1-e^bp(HpEffect))$
-
-but this Hp effect maybe can be divided at the same time in the interaction between recipient-donor with the main traits that drive the effect.
-IB: maybe just a weighting factor 0-1 depending on trait matching?
-If effect of hetero is 0, it cancells out the term, if is maximum, it *1
-
-Moreover, this should consider quantity of hp. lINEAR EFFECT? How to model this maybe talk with nacho. IB: In the absence of data you can try linearity, but also a sigmoidal.
-
-IB: Cool!
-se also Morris et al 2010 Ecology on how to add to AIzen curve, the effects of a second curve describing the negative effect of hetero.
-Morris apporach is mathematically more robust if you can model the second curve of hp effects.
-
-I also think you should use this for another paper and look into Morales -Castilla TREE paper inferring interactions. I can see a similar idea where you use a set of matrix you can multiply. 
-1) A matrix of plant-plant pollinator influence ( a lo carvalehire 2014). This tells you which plants may get exposed to hp pollen from empirical plant pollinator networks
-2) you matrix of plant plant ht effect (0-1) or a proxy based on phylogeny of trait similarity. This is also easy to quantify.
-3) A vector of sensitive recipient traits.
- to create the probability of ht effects. I really like this ideas to link to community ecology.
-
 Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)

### 2019-02-20 Manuscript_draft/Manuscript_draft.tex
more edits paragraph 3

@@
 
-Plant traits are crucial to understand heterospecific pollen effect, but
-here it is important to notice that these traits can be seen from a
-donor perpective or a recipient one. In first place, when the donor is
-considered pollen size and pollen allelopathy could be the two main
-predictors of effect. How pollen size and allepothaty are involved in
-heterospecific pollen effect remains unclear yet. For example, Herrera
-xxxx observed that small pollen is more likely to clogg the stigma, here
-we argue that although this is possible, the quantities of
-heterospecific pollen in nature are generally low as mentioned above and
-bigger pollen is generally related with higher pollen tube growth rate,
-which add another layer of complexity to the understanding of the
-overall importance of this trait. Moreover, pollen allelopathy is still
-an unclear field for pollination ecologist. When the pollen recipeint is
-taking into account style length, stigmatic area, flower morphology,
-number of ovules and incompatibility system seems to be the main
-predictors of effect. In the case of style length species with shorter
-styles will have greater heterospecific pollen effect due to pollen
-competition is more likely to occur and therefore ovule interference.
-Interestingly, differences of heterospecific pollen load has been shown
-to do not be influenced by flowr morphology (restricted or
-unrestricted), and the main predictor of the heterospecific pollen load
-was stigma size (REF). Therefore, if bigger stigmas can receive more hp
-pollen, a greater quantity of hp can be translated in a possible greater
-negative effect. For species that are self-incompatible have stronger
-barriers to heterospecific pollen than self-compatible species Ashman
-and Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a
-bit obscured by the variability within species, however species that are
+Plant traits are crucial to understand heterospecific pollen effect but
+the multifactorial nature of the traits that are involve in the
+pollen-pistil interaction make difficult to unravel what are the main
+traits in driving the effect. On the one hand the main predictive traits
+of effect from the donor perspective are pollen size, pollen allelopathy
+and pollen apertures (REFS). In Ashamn 2013 small pollen is predicted to
+cause a greater fitness decrease, although this can be true there are
+also other possibilities to consider which can obscure a predictive
+framework like big pollen can clogg small stigmas with fewer pollen
+grains, bigger stigmas are less likely to be clogged by small pollen
+grains and bigger pollen can outcompete smaller pollen grains due to
+faster pollen tube growth rate (REF). On the other hand the main
+recipient traits that can drive heterospecific pollen effect are: stigma
+size, style length, number of ovules, incompatibility system and flower
+morphology (REFS). In first place, greater stigmatic area is related
+with greater amount of heterospecific pollen (REF) and therefore
+possibly a greater negative effect (REF). Species with shorter styles
+are more likely to be vulnerable to heterospecific pollen effect (REF).
+For species that are self-incompatible have stronger barriers to
+heterospecific pollen than self-compatible species Ashman and
+Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a bit
+obscured by the variability within species, however species that are
 strong selfers or strong outcrossers have less variablity in mating
 systems and predictions of effect could be more realistic (see figure 1
-from Whitehead et al. (2018)).
+from Whitehead et al. (2018)). All in all, there is a need to deepen in
+the understanding of the relative importance of these traits, due to we
+still do not know what are the main traits in driving the effect with
+all these possible combinations that can occur in nature.
 
@@
 
-Species with similar traits are more closely related XXXXXXXXX \href{}{I
-would say no. species closely related usually have similar traits,
-specally if those are phylogenetially conserved}. (Refs? Brown and
-Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016) ).
-Several studies predict that the impact of HP transfer is likely to be
-greater for closely related species (Ashman and Arceo-Gómez (2013)). Few
-studies however, have focused on the impacts of heterospecific pollen of
-distantly related species Thomson et al. (1982) Galen and Gregory (1989)
-Neiland and Wilcock (1999). Yet, most insects and most stigmas have been
-found to carry multiple species of foreign pollen with little attention
-to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang
-(2013) ; also cite studies from pollen transfer networks here such
-as\ldots{} ).
+Species closely related are more likely to have similar traits
+XXXXXXXXX. (Refs? Brown and Mitchell (2001) Arceo-Gómez et al. (2016)
+Tong and Huang (2016) ). Several studies predict that the impact of HP
+transfer is likely to be greater for closely related species (Ashman and
+Arceo-Gómez (2013)). Few studies however, have focused on the impacts of
+heterospecific pollen of distantly related species Thomson et al. (1982)
+Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects
+and most stigmas have been found to carry multiple species of foreign
+pollen with little attention to degree of relatedness (Arceo-Gómez and
+Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
+transfer networks here such as\ldots{} ).
 
-\href{}{here you change topic, new paragraph?} Further, a majority of
-plant species are generalist and thus receive visits from multiple
-different pollinators. Given these are generally the ones that receive
-greater loads of heterospecific pollen Fang and Huang (2013) and
-unrelated species are more likely to coexist with other species due to
-less niche overlap (Ref), understanding the role of foreign pollen from
-distantly related species thus deserves greater attention in
-understanding coexistence blah blahXXXXX refs.. Notwithstanding, the
-effect of heterospecific pollen of far and close related species at
-community level remains to be explored beyond single pairwise
-interactions.
-
-\textbf{Paragraph 5} Introducing our experiment
-
-In this study we investigated how floral reproductive traits and
-relatedness mediate the impact of HP transfer by asking the following
-research questions : To what extent do (i) floral reproductive traits
-and (ii) relatedness, mediate the impacts of heterospecific pollen on
-seed set. We do this by creating an artificial co-flowering community
-with 10 species belonging to three different families with different
-traits.
+Further, a majority of plant species are generalist and thus receive
+visits from multiple different pollinators. Given these are generally
+the ones that receive greater loads of heterospecific pollen Fang and
+Huang (2013) and unrelated species are more likely to coexist with other
+species due to less niche overlap (Ref), understanding the role of
+foreign pollen from distantly related species thus deserves greater
+attention in understanding coexistence blah blahXXXXX refs..
+Notwithstanding, the effect of heterospecific pollen of far and close
+related species at community level remains to be explored beyond single
+pairwise interactions. In this study we investigated how floral
+reproductive traits and relatedness mediate the impact of HP transfer by
+asking the following research questions : To what extent do (i) floral
+reproductive traits and (ii) relatedness, mediate the impacts of
+heterospecific pollen on seed set. We do this by creating an artificial
+co-flowering community with 10 species belonging to three different
+families with different traits.
 
@@
 
-Other idea based on the paper of Aizen 2007:
-
-He explains seed set in this way. O total number of ovules, d fraction
-of ovules that become seed set, b proportion of pollen grains that reach
-ovules, p number of pollen grains.
-
-\(S=dO(1-e^bp)\)
-
-\(S=dO(1-e^bp(HpEffect))\)
-
-but this Hp effect maybe can be divided at the same time in the
-interaction between recipient-donor with the main traits that drive the
-effect. IB: maybe just a weighting factor 0-1 depending on trait
-matching? If effect of hetero is 0, it cancells out the term, if is
-maximum, it *1
-
-Moreover, this should consider quantity of hp. lINEAR EFFECT? How to
-model this maybe talk with nacho. IB: In the absence of data you can try
-linearity, but also a sigmoidal.
-
-IB: Cool! se also Morris et al 2010 Ecology on how to add to AIzen
-curve, the effects of a second curve describing the negative effect of
-hetero. Morris apporach is mathematically more robust if you can model
-the second curve of hp effects.
-
-I also think you should use this for another paper and look into Morales
--Castilla TREE paper inferring interactions. I can see a similar idea
-where you use a set of matrix you can multiply. 1) A matrix of
-plant-plant pollinator influence ( a lo carvalehire 2014). This tells
-you which plants may get exposed to hp pollen from empirical plant
-pollinator networks 2) you matrix of plant plant ht effect (0-1) or a
-proxy based on phylogeny of trait similarity. This is also easy to
-quantify. 3) A vector of sensitive recipient traits. to create the
-probability of ht effects. I really like this ideas to link to community
-ecology.
-
 Ideas about pollen size in heterospecific pollen effect. (still have to

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
more changes in intro

@@
 Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involve in the pollen-pistil interaction make difficult to unravel what are the main traits in driving the effect.
-On the one hand the main predictive traits of effect from the donor perspective are pollen size, pollen allelopathy and pollen apertures (REFS).
-In Ashamn 2013 small pollen is predicted to cause a greater fitness decrease, although this can be true there are also other possibilities to consider which can obscure a predictive framework like big pollen can clogg small stigmas with fewer pollen grains, bigger stigmas are less likely to be clogged by small pollen grains and bigger pollen can outcompete smaller pollen grains due to faster pollen tube growth rate (REF).
-On the other hand  the main recipient traits that can drive heterospecific pollen effect are: stigma size, style length, number of ovules, incompatibility system and flower morphology (REFS).
-In first place, greater stigmatic area is related with greater amount of heterospecific pollen (REF) and therefore possibly a greater negative effect (REF).
-Species with shorter styles are more likely to be vulnerable to heterospecific pollen effect (REF).
-For species that are self-incompatible have stronger barriers to heterospecific pollen than self-compatible species @ashman2013.
+These traits can be seen from a male perspective of both donor and recipient where pollen size, pollen aperture number and pollen allelopathy are key components to understand the outcome of foreign pollen arrival (REFS).
+In @ashman2013 small pollen is predicted to cause a greater fitness decrease, although this can be true there are also other possibilities to consider which can obscure a predictive framework like big pollen can clogg small stigmas with fewer pollen grains, bigger stigmas are less likely to be clogged by small pollen grains and bigger pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
+Moreover, to understand the different mechanical or chemical effects of pollen also the female traits of the pollen recipient have to be considered, from the literature these main traits are: stigma size, style length, number of ovules, incompatibility system and finally a structural trait such as flower morphology @montgomery2012; @ashman2013; @tong2016.
+For example, greater stigmatic area is positively correlated with greater heterospecific pollen deposition @montgomery2012 and therefore possibly with an increase in negative effect.
+For species that are self-incompatible the barriers towards heterospecific pollen are stronger than self-compatible species @ashman2013.
 Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
-All in all, there is a need to deepen in the understanding of the relative importance of these traits, due to we still do not know what are the main traits in driving the effect with all these possible combinations that can occur in nature.
+Although past research has progress in the understanding of what traits can mediate the effect as we have shown here, there are multiple traits involved and multiple possible scenarios still to be explored empirically for a full understanding of the importance of heterospecific pollen effect in nature.
 
-[Comments on it](Romina)
-
-Species closely related are more likely to have similar traits XXXXXXXXX.
-(Refs?
+Closely related species are more likely to have similar traits (Refs?
 Brown and Mitchell (2001) Arceo-Gómez et al.
-(2016) Tong and Huang (2016) ).
+(2016) Tong and Huang (2016)).
 Several studies predict that the impact of HP transfer is likely to be greater for closely related species (Ashman and Arceo-Gómez (2013)).
@@
 (1982) Galen and Gregory (1989) Neiland and Wilcock (1999).
-Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen transfer networks here such as...
+Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013); also cite studies from pollen transfer networks here such as...
 ).
+Traditionally, studies have overlook the effect of closely related species but in a natural context both can occur and different degree of relatedness should be considered.
 
@@
 Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.
-In this study we investigated how floral reproductive traits and relatedness mediate the impact of HP transfer by asking the following research questions : To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
+Moreover, heterospecific pollen studies in nature have the complexity added great environmental variability which can lead to confounding interpretations and diverse floral structures and some of them complex such as Asteraceae species, which involve tedious work to be able to study foreign pollen effect.
+For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific transfer by asking the following research questions : To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
 We do this by creating an artificial co-flowering community with 10 species belonging to three different families with different traits.
+
+-Would like to add here floral complexity
+
+-Environmental variability of studies on the field
 
@@
 
+Herbs vs tress, annual vs perennial... Many flowers vs few flowered species; structural composition on a system
+
  What are the implications of the findings?

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
more changes in intro

@@
 pollen-pistil interaction make difficult to unravel what are the main
-traits in driving the effect. On the one hand the main predictive traits
-of effect from the donor perspective are pollen size, pollen allelopathy
-and pollen apertures (REFS). In Ashamn 2013 small pollen is predicted to
-cause a greater fitness decrease, although this can be true there are
-also other possibilities to consider which can obscure a predictive
-framework like big pollen can clogg small stigmas with fewer pollen
-grains, bigger stigmas are less likely to be clogged by small pollen
-grains and bigger pollen can outcompete smaller pollen grains due to
-faster pollen tube growth rate (REF). On the other hand the main
-recipient traits that can drive heterospecific pollen effect are: stigma
-size, style length, number of ovules, incompatibility system and flower
-morphology (REFS). In first place, greater stigmatic area is related
-with greater amount of heterospecific pollen (REF) and therefore
-possibly a greater negative effect (REF). Species with shorter styles
-are more likely to be vulnerable to heterospecific pollen effect (REF).
-For species that are self-incompatible have stronger barriers to
-heterospecific pollen than self-compatible species Ashman and
-Arceo-Gómez (2013). Nonetheless, an effect of foreign pollen is a bit
-obscured by the variability within species, however species that are
-strong selfers or strong outcrossers have less variablity in mating
-systems and predictions of effect could be more realistic (see figure 1
-from Whitehead et al. (2018)). All in all, there is a need to deepen in
-the understanding of the relative importance of these traits, due to we
-still do not know what are the main traits in driving the effect with
-all these possible combinations that can occur in nature.
+traits in driving the effect. These traits can be seen from a male
+perspective of both donor and recipient where pollen size, pollen
+aperture number and pollen allelopathy are key components to understand
+the outcome of foreign pollen arrival (REFS). In Ashman and Arceo-Gómez
+(2013) small pollen is predicted to cause a greater fitness decrease,
+although this can be true there are also other possibilities to consider
+which can obscure a predictive framework like big pollen can clogg small
+stigmas with fewer pollen grains, bigger stigmas are less likely to be
+clogged by small pollen grains and bigger pollen can outcompete smaller
+pollen grains due to faster pollen tube growth rate Williams and Rouse
+(1990). Moreover, to understand the different mechanical or chemical
+effects of pollen also the female traits of the pollen recipient have to
+be considered, from the literature these main traits are: stigma size,
+style length, number of ovules, incompatibility system and finally a
+structural trait such as flower morphology Montgomery and Rathcke
+(2012); Ashman and Arceo-Gómez (2013); Tong and Huang (2016). For
+example, greater stigmatic area is positively correlated with greater
+heterospecific pollen deposition Montgomery and Rathcke (2012) and
+therefore possibly with an increase in negative effect. For species that
+are self-incompatible the barriers towards heterospecific pollen are
+stronger than self-compatible species Ashman and Arceo-Gómez (2013).
+Nonetheless, an effect of foreign pollen is a bit obscured by the
+variability within species, however species that are strong selfers or
+strong outcrossers have less variablity in mating systems and
+predictions of effect could be more realistic (see figure 1 from
+Whitehead et al. (2018)). Although past research has progress in the
+understanding of what traits can mediate the effect as we have shown
+here, there are multiple traits involved and multiple possible scenarios
+still to be explored empirically for a full understanding of the
+importance of heterospecific pollen effect in nature.
 
-\href{Romina}{Comments on it}
-
-Species closely related are more likely to have similar traits
-XXXXXXXXX. (Refs? Brown and Mitchell (2001) Arceo-Gómez et al. (2016)
-Tong and Huang (2016) ). Several studies predict that the impact of HP
-transfer is likely to be greater for closely related species (Ashman and
-Arceo-Gómez (2013)). Few studies however, have focused on the impacts of
+Closely related species are more likely to have similar traits (Refs?
+Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang
+(2016)). Several studies predict that the impact of HP transfer is
+likely to be greater for closely related species (Ashman and Arceo-Gómez
+(2013)). Few studies however, have focused on the impacts of
 heterospecific pollen of distantly related species Thomson et al. (1982)
@@
 pollen with little attention to degree of relatedness (Arceo-Gómez and
-Ashman (2016); Fang and Huang (2013) ; also cite studies from pollen
-transfer networks here such as\ldots{} ).
+Ashman (2016); Fang and Huang (2013); also cite studies from pollen
+transfer networks here such as\ldots{} ). Traditionally, studies have
+overlook the effect of closely related species but in a natural context
+both can occur and different degree of relatedness should be considered.
 
@@
 related species at community level remains to be explored beyond single
-pairwise interactions. In this study we investigated how floral
-reproductive traits and relatedness mediate the impact of HP transfer by
-asking the following research questions : To what extent do (i) floral
-reproductive traits and (ii) relatedness, mediate the impacts of
-heterospecific pollen on seed set. We do this by creating an artificial
-co-flowering community with 10 species belonging to three different
-families with different traits.
+pairwise interactions. Moreover, heterospecific pollen studies in nature
+have the complexity added great environmental variability which can lead
+to confounding interpretations and diverse floral structures and some of
+them complex such as Asteraceae species, which involve tedious work to
+be able to study foreign pollen effect. For this reason, we investigated
+how floral reproductive traits and relatedness mediate the impact of
+heterospecific transfer by asking the following research questions : To
+what extent do (i) floral reproductive traits and (ii) relatedness,
+mediate the impacts of heterospecific pollen on seed set. We do this by
+creating an artificial co-flowering community with 10 species belonging
+to three different families with different traits.
+
+-Would like to add here floral complexity
+
+-Environmental variability of studies on the field
 
@@
 
+Herbs vs tress, annual vs perennial\ldots{} Many flowers vs few flowered
+species; structural composition on a system
+
 What are the implications of the findings?
@@
 
+\hypertarget{ref-williams1990}{}
+Williams, E., and J. Rouse. 1990. Relationships of pollen size, pistil
+length and pollen tube growth rates in rhododendron and their influence
+on hybridization. Sexual Plant Reproduction 3:7--17.
+
 \eleft

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
Intro more changes

@@
 Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involve in the pollen-pistil interaction make difficult to unravel what are the main traits in driving the effect.
-These traits can be seen from a male perspective of both donor and recipient where pollen size, pollen aperture number and pollen allelopathy are key components to understand the outcome of foreign pollen arrival (REFS).
+These traits can be seen from a male perspective of both donor and recipient where pollen size, pollen aperture number and pollen allelopathy are key components to understand the outcome of foreign pollen arrival @murphy1995; @@ashman2013.
 In @ashman2013 small pollen is predicted to cause a greater fitness decrease, although this can be true there are also other possibilities to consider which can obscure a predictive framework like big pollen can clogg small stigmas with fewer pollen grains, bigger stigmas are less likely to be clogged by small pollen grains and bigger pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
-Moreover, to understand the different mechanical or chemical effects of pollen also the female traits of the pollen recipient have to be considered, from the literature these main traits are: stigma size, style length, number of ovules, incompatibility system and finally a structural trait such as flower morphology @montgomery2012; @ashman2013; @tong2016.
+Moreover, to understand the different mechanical or chemical effects of pollen also the female traits of the pollen recipient have to be considered, from the literature these main traits are: stigma size, style length, number of ovules, incompatibility system and also a structural trait such as flower morphology @montgomery2012; @ashman2013; @tong2016.
 For example, greater stigmatic area is positively correlated with greater heterospecific pollen deposition @montgomery2012 and therefore possibly with an increase in negative effect.
@@
 
-Closely related species are more likely to have similar traits (Refs?
-Brown and Mitchell (2001) Arceo-Gómez et al.
-(2016) Tong and Huang (2016)).
-Several studies predict that the impact of HP transfer is likely to be greater for closely related species (Ashman and Arceo-Gómez (2013)).
-Few studies however, have focused on the impacts of heterospecific pollen of distantly related species Thomson et al.
+For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species.
+Closely related species are more likely to have similar traits.
+The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion and therefore studies predict a greater negative effect of closely related species (REFS).
+Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species Thomson et al.
 (1982) Galen and Gregory (1989) Neiland and Wilcock (1999).
@@
 ).
-Traditionally, studies have overlook the effect of closely related species but in a natural context both can occur and different degree of relatedness should be considered.
+The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen.
+
+CLOSELY RELATED SPECIES STUDIES:  (Refs? Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016))
 
@@
 We do this by creating an artificial co-flowering community with 10 species belonging to three different families with different traits.
-
--Would like to add here floral complexity
-
--Environmental variability of studies on the field
 

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
Intro more changes

@@
 be considered, from the literature these main traits are: stigma size,
-style length, number of ovules, incompatibility system and finally a
+style length, number of ovules, incompatibility system and also a
 structural trait such as flower morphology Montgomery and Rathcke
@@
 
-Closely related species are more likely to have similar traits (Refs?
-Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang
-(2016)). Several studies predict that the impact of HP transfer is
-likely to be greater for closely related species (Ashman and Arceo-Gómez
-(2013)). Few studies however, have focused on the impacts of
-heterospecific pollen of distantly related species Thomson et al. (1982)
-Galen and Gregory (1989) Neiland and Wilcock (1999). Yet, most insects
-and most stigmas have been found to carry multiple species of foreign
-pollen with little attention to degree of relatedness (Arceo-Gómez and
-Ashman (2016); Fang and Huang (2013); also cite studies from pollen
-transfer networks here such as\ldots{} ). Traditionally, studies have
-overlook the effect of closely related species but in a natural context
-both can occur and different degree of relatedness should be considered.
+For the understanding at what level or intensity the interference of
+pollen can occur is important to consider the relatedness of the
+interacting species. Closely related species are more likely to have
+similar traits (Refs? Brown and Mitchell (2001) Arceo-Gómez et al.
+(2016) Tong and Huang (2016)). The similarity in traits between closely
+related species can lead to higher chances of ovule usurpation and
+therefore studies predict a greater negative effect of closely related
+species. Few studies however, have focused on the impacts of
+heterospecific pollen on fitness of distantly related species Thomson et
+al. (1982) Galen and Gregory (1989) Neiland and Wilcock (1999). Yet,
+most insects and most stigmas have been found to carry multiple species
+of foreign pollen with little attention to degree of relatedness
+(Arceo-Gómez and Ashman (2016); Fang and Huang (2013); also cite studies
+from pollen transfer networks here such as\ldots{} ). Traditionally,
+studies have overlook the effect of closely related species but in a
+natural context both can occur and different degree of relatedness
+should be considered.
 

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
intro changes

@@
 For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species.
-Closely related species are more likely to have similar traits.
-The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion and therefore studies predict a greater negative effect of closely related species (REFS).
+Closely related species are more likely to have similar traits @arceo2016.
+The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion (REF) and therefore studies predict and show a greater negative effect of closely related species (REFS).
 Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species Thomson et al.
 (1982) Galen and Gregory (1989) Neiland and Wilcock (1999).
-Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013); also cite studies from pollen transfer networks here such as...
-).
-The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen.
-
-CLOSELY RELATED SPECIES STUDIES:  (Refs? Brown and Mitchell (2001) Arceo-Gómez et al. (2016) Tong and Huang (2016))
+Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013).
+The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen where closely related species cand lead to greater detrimental effects @arceo2016.
 

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
intro changes

@@
 aperture number and pollen allelopathy are key components to understand
-the outcome of foreign pollen arrival (REFS). In Ashman and Arceo-Gómez
-(2013) small pollen is predicted to cause a greater fitness decrease,
-although this can be true there are also other possibilities to consider
-which can obscure a predictive framework like big pollen can clogg small
-stigmas with fewer pollen grains, bigger stigmas are less likely to be
-clogged by small pollen grains and bigger pollen can outcompete smaller
-pollen grains due to faster pollen tube growth rate Williams and Rouse
-(1990). Moreover, to understand the different mechanical or chemical
-effects of pollen also the female traits of the pollen recipient have to
-be considered, from the literature these main traits are: stigma size,
-style length, number of ovules, incompatibility system and also a
-structural trait such as flower morphology Montgomery and Rathcke
-(2012); Ashman and Arceo-Gómez (2013); Tong and Huang (2016). For
-example, greater stigmatic area is positively correlated with greater
-heterospecific pollen deposition Montgomery and Rathcke (2012) and
-therefore possibly with an increase in negative effect. For species that
-are self-incompatible the barriers towards heterospecific pollen are
+the outcome of foreign pollen arrival Murphy and Aarssen (1995); @Ashman
+and Arceo-Gómez (2013). In Ashman and Arceo-Gómez (2013) small pollen is
+predicted to cause a greater fitness decrease, although this can be true
+there are also other possibilities to consider which can obscure a
+predictive framework like big pollen can clogg small stigmas with fewer
+pollen grains, bigger stigmas are less likely to be clogged by small
+pollen grains and bigger pollen can outcompete smaller pollen grains due
+to faster pollen tube growth rate Williams and Rouse (1990). Moreover,
+to understand the different mechanical or chemical effects of pollen
+also the female traits of the pollen recipient have to be considered,
+from the literature these main traits are: stigma size, style length,
+number of ovules, incompatibility system and also a structural trait
+such as flower morphology Montgomery and Rathcke (2012); Ashman and
+Arceo-Gómez (2013); Tong and Huang (2016). For example, greater
+stigmatic area is positively correlated with greater heterospecific
+pollen deposition Montgomery and Rathcke (2012) and therefore possibly
+with an increase in negative effect. For species that are
+self-incompatible the barriers towards heterospecific pollen are
 stronger than self-compatible species Ashman and Arceo-Gómez (2013).
@@
 interacting species. Closely related species are more likely to have
-similar traits (Refs? Brown and Mitchell (2001) Arceo-Gómez et al.
-(2016) Tong and Huang (2016)). The similarity in traits between closely
-related species can lead to higher chances of ovule usurpation and
-therefore studies predict a greater negative effect of closely related
-species. Few studies however, have focused on the impacts of
-heterospecific pollen on fitness of distantly related species Thomson et
-al. (1982) Galen and Gregory (1989) Neiland and Wilcock (1999). Yet,
-most insects and most stigmas have been found to carry multiple species
-of foreign pollen with little attention to degree of relatedness
-(Arceo-Gómez and Ashman (2016); Fang and Huang (2013); also cite studies
-from pollen transfer networks here such as\ldots{} ). Traditionally,
-studies have overlook the effect of closely related species but in a
-natural context both can occur and different degree of relatedness
-should be considered.
+similar traits Arceo-Gómez and Ashman (2016). The similarity in traits
+between closely related species can lead to higher chances of ovule
+usurpation/abortion (REF) and therefore studies predict and show a
+greater negative effect of closely related species (REFS). Few studies
+however, have focused on the impacts of heterospecific pollen on fitness
+of distantly related species Thomson et al. (1982) Galen and Gregory
+(1989) Neiland and Wilcock (1999). Yet, most insects and most stigmas
+have been found to carry multiple species of foreign pollen with little
+attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang
+and Huang (2013). The relative amounts of closely/far related pollen
+that arrives to a stigma gives a first snapshoot where pollen
+competition can occur and improves the understanding of how important
+the reduction of fitness can be from heterospecific pollen where closely
+related species cand lead to greater detrimental effects Arceo-Gómez and
+Ashman (2016).
 
@@
 to three different families with different traits.
-
--Would like to add here floral complexity
-
--Environmental variability of studies on the field
 
@@
 
+\hypertarget{ref-murphy1995}{}
+Murphy, S. D., and L. W. Aarssen. 1995. Reduced seed set in elytrigia
+repens caused by allelopathic pollen from phleum pratense. Canadian
+Journal of Botany 73:1417--1422.
+
 \hypertarget{ref-pauw2013}{}

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
edits intro

@@
 Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involve in the pollen-pistil interaction make difficult to unravel what are the main traits in driving the effect.
-These traits can be seen from a male perspective of both donor and recipient where pollen size, pollen aperture number and pollen allelopathy are key components to understand the outcome of foreign pollen arrival @murphy1995; @@ashman2013.
+These traits can be seen from a male perspective of both donor and recipient where pollen size, pollen aperture number and pollen allelopathy are key components to understand the outcome of foreign pollen arrival @murphy1995; @ashman2013.
 In @ashman2013 small pollen is predicted to cause a greater fitness decrease, although this can be true there are also other possibilities to consider which can obscure a predictive framework like big pollen can clogg small stigmas with fewer pollen grains, bigger stigmas are less likely to be clogged by small pollen grains and bigger pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
@@
 For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species.
-Closely related species are more likely to have similar traits @arceo2016.
+Closely related species are more likely to have similar traits @letten2015.
 The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion (REF) and therefore studies predict and show a greater negative effect of closely related species (REFS).

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
edits intro

@@
 aperture number and pollen allelopathy are key components to understand
-the outcome of foreign pollen arrival Murphy and Aarssen (1995); @Ashman
+the outcome of foreign pollen arrival Murphy and Aarssen (1995); Ashman
 and Arceo-Gómez (2013). In Ashman and Arceo-Gómez (2013) small pollen is
@@
 interacting species. Closely related species are more likely to have
-similar traits Arceo-Gómez and Ashman (2016). The similarity in traits
+similar traits Letten and Cornwell (2015). The similarity in traits
 between closely related species can lead to higher chances of ovule
@@
 
+\hypertarget{ref-letten2015}{}
+Letten, A. D., and W. K. Cornwell. 2015. Trees, branches and (square)
+roots: Why evolutionary relatedness is not linearly related to
+functional distance. Methods in Ecology and Evolution 6:439--444.
+
 \hypertarget{ref-lloyd1992}{}

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 Closely related species are more likely to have similar traits @letten2015.
-The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion (REF) and therefore studies predict and show a greater negative effect of closely related species (REFS).
-Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species Thomson et al.
-(1982) Galen and Gregory (1989) Neiland and Wilcock (1999).
+The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion @arceo2011 and therefore studies predict and show a greater negative effect of closely related species @ashman2013; @arceo2016.
+Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999.
 Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013).

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
changes

@@
 between closely related species can lead to higher chances of ovule
-usurpation/abortion (REF) and therefore studies predict and show a
-greater negative effect of closely related species (REFS). Few studies
-however, have focused on the impacts of heterospecific pollen on fitness
-of distantly related species Thomson et al. (1982) Galen and Gregory
-(1989) Neiland and Wilcock (1999). Yet, most insects and most stigmas
-have been found to carry multiple species of foreign pollen with little
-attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang
-and Huang (2013). The relative amounts of closely/far related pollen
-that arrives to a stigma gives a first snapshoot where pollen
-competition can occur and improves the understanding of how important
-the reduction of fitness can be from heterospecific pollen where closely
-related species cand lead to greater detrimental effects Arceo-Gómez and
-Ashman (2016).
+usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
+predict and show a greater negative effect of closely related species
+Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
+studies however, have focused on the impacts of heterospecific pollen on
+fitness of distantly related species Galen and Gregory (1989); Neiland
+and Wilcock (1999). Yet, most insects and most stigmas have been found
+to carry multiple species of foreign pollen with little attention to
+degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang
+(2013). The relative amounts of closely/far related pollen that arrives
+to a stigma gives a first snapshoot where pollen competition can occur
+and improves the understanding of how important the reduction of fitness
+can be from heterospecific pollen where closely related species cand
+lead to greater detrimental effects Arceo-Gómez and Ashman (2016).
 
@@
 
+\hypertarget{ref-arceo2011}{}
+Arceo-Gómez, G., and T.-L. Ashman. 2011. Heterospecific pollen
+deposition: Does diversity alter the consequences? New Phytologist
+192:738--746.
+
 \hypertarget{ref-arceo2016}{}
@@
 94:1176--1185.
+
+\hypertarget{ref-galen1989}{}
+Galen, C., and T. Gregory. 1989. Interspecific pollen transfer as a
+mechanism of competition: Consequences of foreign pollen contamination
+for seed set in the alpine wildflower, polemonium viscosum. Oecologia
+81:120--123.
 
@@
 Journal of Botany 73:1417--1422.
+
+\hypertarget{ref-neiland1999}{}
+Neiland, M., and C. Wilcock. 1999. The presence of heterospecific pollen
+on stigmas of nectariferous and nectarless orchids and its consequences
+for their reproductive success. Protoplasma 208:65--75.
 

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
Intro

@@
 Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013).
-The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen where closely related species cand lead to greater detrimental effects @arceo2016.
+The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be.
+With that said, @arceo2016 is the only work which has tested the effect of far and close related pollen with published data with low sample sizes and lack of significance.
 

### 2019-02-21 Manuscript_draft/Manuscript_draft.tex
Intro

@@
 and improves the understanding of how important the reduction of fitness
-can be from heterospecific pollen where closely related species cand
-lead to greater detrimental effects Arceo-Gómez and Ashman (2016).
+can be. With that said, Arceo-Gómez and Ashman (2016) is the only work
+which has tested the effect of far and close related pollen with
+published data with low sample sizes and lack of significance.
 

### 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
a bit more changes on intro, tomorrow last paragraph of it!

--- 2019-02-21 Manuscript_draft/Manuscript_draft.Rmd
@@
 Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999.
+Despite the fact that far related species are also able to decrease species fitness (REFS).
 Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013).
-The relative amounts of closely/far related pollen that arrives to a stigma gives a first snapshoot where pollen competition can occur and improves the understanding of how important the reduction of fitness can be from heterospecific pollen where closely related species cand lead to greater detrimental effects @arceo2016.
+The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect.
+With that said, @arceo2016 is the only work which has proven a greater effect of far and close related pollen with published data with low sample sizes and lack of significance.
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
intro

--- 2019-02-21 Manuscript_draft/Manuscript_draft.tex
@@
 fitness of distantly related species Galen and Gregory (1989); Neiland
-and Wilcock (1999). Yet, most insects and most stigmas have been found
-to carry multiple species of foreign pollen with little attention to
-degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang
-(2013). The relative amounts of closely/far related pollen that arrives
-to a stigma gives a first snapshoot where pollen competition can occur
-and improves the understanding of how important the reduction of fitness
-can be from heterospecific pollen where closely related species cand
-lead to greater detrimental effects Arceo-Gómez and Ashman (2016).
+and Wilcock (1999). Despite the fact that far related species are also
+able to decrease species fitness (REFS). Yet, most insects and most
+stigmas have been found to carry multiple species of foreign pollen with
+little attention to degree of relatedness (Arceo-Gómez and Ashman
+(2016); Fang and Huang (2013). The relatedness of foreign pollen gives a
+first snapshoot of where the pollen competition can occur and therefore
+could be a proxy of effect. With that said, Arceo-Gómez and Ashman
+(2016) is the only work which has proven a greater effect of far and
+close related pollen with published data with low sample sizes and lack
+of significance.
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
small change

@@
 We conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer.
-We conducted 4XXXX crosses by experimentally transferring pollen (50% and 100% ratio) with reciporcal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+We conducted 1800 crosses by experimentally transferring pollen (50% and 100% ratio) with reciporcal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
 Seed set was used as proxy of plant fitness.

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
small change

@@
 to understand how phylogenetic relatedness and plant traits mediate the
-impacts of heterospecific pollen transfer. We conducted 4XXXX crosses by
+impacts of heterospecific pollen transfer. We conducted 1800 crosses by
 experimentally transferring pollen (50\% and 100\% ratio) with

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
intro

@@
 Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013).
+Understanding the role of foreign pollen from distantly related species thus deserves greater attention.
 The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect.
-With that said, @arceo2016 is the only work which has proven a greater effect of far and close related pollen with published data with low sample sizes and lack of significance.
+With that said, @arceo2016 is the only work which has proven a greater effect of close related species through a meta-analysis with low sample sizes and lack of significance.
+Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.
 
-Further, a majority of plant species are generalist and thus receive visits from multiple different pollinators.
-Given these are generally the ones that receive greater loads of heterospecific pollen Fang and Huang (2013) and unrelated species are more likely to coexist  with other species due to less niche overlap (Ref),  understanding the role of foreign pollen from distantly related species thus deserves greater attention in understanding coexistence blah blahXXXXX refs..
-Notwithstanding, the effect of heterospecific pollen of far and close related species at community level remains to be explored beyond single pairwise interactions.
-Moreover, heterospecific pollen studies in nature have the complexity added great environmental variability which can lead to confounding interpretations and diverse floral structures and some of them complex such as Asteraceae species, which involve tedious work to be able to study foreign pollen effect.
-For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific transfer by asking the following research questions : To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
-We do this by creating an artificial co-flowering community with 10 species belonging to three different families with different traits.
+Heterospecific pollen studies in nature have the complexity added of great environmental variability which can lead to confounding interpretations.
+Moreover, the great diversity of floral structures and small sizes of some of them such as Asteraceae species make tedious or almost impossible the studies of heterospecific pollen on the field.
+For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits.
+Our study tries to answer the following question: To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
intro

@@
 little attention to degree of relatedness (Arceo-Gómez and Ashman
-(2016); Fang and Huang (2013). The relatedness of foreign pollen gives a
-first snapshoot of where the pollen competition can occur and therefore
-could be a proxy of effect. With that said, Arceo-Gómez and Ashman
-(2016) is the only work which has proven a greater effect of far and
-close related pollen with published data with low sample sizes and lack
-of significance.
+(2016); Fang and Huang (2013). Understanding the role of foreign pollen
+from distantly related species thus deserves greater attention. The
+relatedness of foreign pollen gives a first snapshoot of where the
+pollen competition can occur and therefore could be a proxy of effect.
+With that said, Arceo-Gómez and Ashman (2016) is the only work which has
+proven a greater effect of close related species through a meta-analysis
+with low sample sizes and lack of significance. Therefore, there is a
+need to study the effect of heterospecific pollen of far and close
+related species at community level beyond single pairwise interactions.
 
-Further, a majority of plant species are generalist and thus receive
-visits from multiple different pollinators. Given these are generally
-the ones that receive greater loads of heterospecific pollen Fang and
-Huang (2013) and unrelated species are more likely to coexist with other
-species due to less niche overlap (Ref), understanding the role of
-foreign pollen from distantly related species thus deserves greater
-attention in understanding coexistence blah blahXXXXX refs..
-Notwithstanding, the effect of heterospecific pollen of far and close
-related species at community level remains to be explored beyond single
-pairwise interactions. Moreover, heterospecific pollen studies in nature
-have the complexity added great environmental variability which can lead
-to confounding interpretations and diverse floral structures and some of
-them complex such as Asteraceae species, which involve tedious work to
-be able to study foreign pollen effect. For this reason, we investigated
-how floral reproductive traits and relatedness mediate the impact of
-heterospecific transfer by asking the following research questions : To
-what extent do (i) floral reproductive traits and (ii) relatedness,
-mediate the impacts of heterospecific pollen on seed set. We do this by
-creating an artificial co-flowering community with 10 species belonging
-to three different families with different traits.
+Heterospecific pollen studies in nature have the complexity added of
+great environmental variability which can lead to confounding
+interpretations. Moreover, the great diversity of floral structures and
+small sizes of some of them such as Asteraceae species make tedious or
+almost impossible the studies of heterospecific pollen on the field. For
+this reason, we investigated how floral reproductive traits and
+relatedness mediate the impact of heterospecific by creating an
+artificial co-flowering community in a glasshouse with 10 species
+belonging to three different families with different traits. Our study
+tries to answer the following question: To what extent do (i) floral
+reproductive traits and (ii) relatedness, mediate the impacts of
+heterospecific pollen on seed set.
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
some edits intro

@@
 The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect.
-With that said, @arceo2016 is the only work which has proven a greater effect of close related species through a meta-analysis with low sample sizes and lack of significance.
+With that said, @arceo2016 is the only work which has proven a greater effect of close related species through a meta-analysis but with low sample sizes and lack of significance.
 Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.
@@
 Moreover, the great diversity of floral structures and small sizes of some of them such as Asteraceae species make tedious or almost impossible the studies of heterospecific pollen on the field.
-For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits.
+For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits.
 Our study tries to answer the following question: To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
some edits intro

@@
 proven a greater effect of close related species through a meta-analysis
-with low sample sizes and lack of significance. Therefore, there is a
-need to study the effect of heterospecific pollen of far and close
+but with low sample sizes and lack of significance. Therefore, there is
+a need to study the effect of heterospecific pollen of far and close
 related species at community level beyond single pairwise interactions.
@@
 this reason, we investigated how floral reproductive traits and
-relatedness mediate the impact of heterospecific by creating an
+relatedness mediate the impact of heterospecific pollen by creating an
 artificial co-flowering community in a glasshouse with 10 species

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods changes

@@
 Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences.
-The species selected (**Table 1**) belonged to three different families, Solanaceae, Brassicaceae and Convolvulaceae.
-The criteria of species/family selection was based on close/distant related species (see phylogenetic tree for relatedness fig 1)[I would explain more the bauty of our nested dessign to ensure close and far distance simultaneously](), heterogeneous traits, low structural flower complexity and fast life cycle.
+The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**).
+The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crossed between species allowed us to have multiple different scenarios of both traits and relatedness.
+Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the different pollination treatments and grow the different species from seeds.
 For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods changes

@@
 temperature controlled depending on the requirements of the species with
-day and night temperature differences. The species selected
-(\textbf{Table 1}) belonged to three different families, Solanaceae,
-Brassicaceae and Convolvulaceae. The criteria of species/family
-selection was based on close/distant related species (see phylogenetic
-tree for relatedness fig 1)\href{}{I would explain more the bauty of our
-nested dessign to ensure close and far distance simultaneously},
-heterogeneous traits, low structural flower complexity and fast life
-cycle. For the purpose of the experiment all the species where
-considered as pollen recipient and as pollen donor (see interaction
-matrix, fig 2). Species were watered once or twice per day and
-fertilized weekly (NPK 23: 3.95: 14).
+day and night temperature differences. The experimental design had
+species from three different families: Solanaceae, Brassicaceae and
+Convolvulaceae (\textbf{Table 1}). The different species of the study
+have different reproductive traits and different degree of relatedness
+where the reciprocal crossed between species them allow us to have
+multiple different scenarios of both. Moreover, the species selected
+have fast life cycle and low structural flower complexity in oprder to
+perform the different pollination treatments. For the purpose of the
+experiment all the species where considered as pollen recipient and as
+pollen donor (see interaction matrix, fig 2). Species were watered once
+or twice per day and fertilized weekly (NPK 23: 3.95: 14).
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods

@@
 The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crossed between species allowed us to have multiple different scenarios of both traits and relatedness.
-Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the different pollination treatments and grow the different species from seeds.
+Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
 For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods

@@
 have different reproductive traits and different degree of relatedness
-where the reciprocal crossed between species them allow us to have
-multiple different scenarios of both. Moreover, the species selected
-have fast life cycle and low structural flower complexity in oprder to
-perform the different pollination treatments. For the purpose of the
-experiment all the species where considered as pollen recipient and as
-pollen donor (see interaction matrix, fig 2). Species were watered once
-or twice per day and fertilized weekly (NPK 23: 3.95: 14).
+where the reciprocal crossed between species allowed us to have multiple
+different scenarios of both traits and relatedness. Moreover, the
+species selected have fast life cycle and low structural flower
+complexity in order to perform the pollination treatments and grow the
+different species from seeds. For the purpose of the experiment all the
+species where considered as pollen recipient and as pollen donor (see
+interaction matrix, fig 2). Species were watered once or twice per day
+and fertilized weekly (NPK 23: 3.95: 14).
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods changes

@@
 
-Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) [this second I don't get, maybe explain it's ultility.]().
+Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation.
 Therefore, 180 different combinations were performed with N=10 per combination.
@@
 Hand-pollination was conducted with 3-4 gentle touches on the stigma surface.
-[The mixes of pollen were realized on an eppendorf based on the pollen counts made with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species)-IB explain better and give a bit more of detail]().
-In order to confirm that the treatments applied were 50-50 percent pollen, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
+For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed.
+Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.
+In order to confirm that the treatments applied were the desire proportions, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods changes

@@
 with 50\% conspecific pollen and 50\% heterospecific pollen and a second
-one with 100\% foreign pollen (N=10) \href{}{this second I don't get,
-maybe explain it's ultility.}. Therefore, 180 different combinations
-were performed with N=10 per combination. Seed set was the proxy of
-effect for all our treatments. Moreover, hand cross pollination (between
-individuals of the same species), hand self pollination, apomixis
-(bagged emasculated flowers) and natural selfing were tested for each
-species (N=10). For the treatments with foreign pollen and hand cross
-pollination, flowers were emasculated the day prior anthesis and hand
-pollinated next day with a toothpick. Hand-pollination was conducted
-with 3-4 gentle touches on the stigma surface. \href{}{The mixes of
-pollen were realized on an eppendorf based on the pollen counts made
-with Neubaeur chamber (each anther was counted 4 times for 20 different
-anthers per species)-IB explain better and give a bit more of detail}.
-In order to confirm that the treatments applied were 50-50 percent
-pollen, for each focal species the total stigmatic load of pollen was
-counted from one donor of each family (N=3).
+one with 100\% foreign pollen (N=10) in order to see if foreign pollen
+can trigger fruit production by itself or even seeds through ovule
+usurpation. Therefore, 180 different combinations were performed with
+N=10 per combination. Seed set was the proxy of effect for all our
+treatments. Moreover, hand cross pollination (between individuals of the
+same species), hand self pollination, apomixis (bagged emasculated
+flowers) and natural selfing were tested for each species (N=10). For
+the treatments with foreign pollen and hand cross pollination, flowers
+were emasculated the day prior anthesis and hand pollinated next day
+with a toothpick. Hand-pollination was conducted with 3-4 gentle touches
+on the stigma surface. For each species 20 anthers were collected and
+their pollen counted with a hemocytometer, each anther was counted 4
+times and then an average of these counts was performed. Once, the
+average number of pollen grains per anther was known, the proportion of
+anthers per mix was calculated in order to achieve a 50-50\% mix. In
+order to confirm that the treatments applied were the desire
+proportions, for each focal species the total stigmatic load of pollen
+was counted from one donor of each family (N=3).
 

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods changes

@@
 The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**).
-The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crossed between species allowed us to have multiple different scenarios of both traits and relatedness.
+The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
 Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods changes

@@
 have different reproductive traits and different degree of relatedness
-where the reciprocal crossed between species allowed us to have multiple
+where the reciprocal crosses between species allowed us to have multiple
 different scenarios of both traits and relatedness. Moreover, the

### 2019-02-24 Manuscript_draft/Manuscript_draft.Rmd
some edits

@@
 For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits.
-Our study tries to answer the following question: To what extent do (i) floral reproductive traits and (ii) relatedness, mediate the impacts of heterospecific pollen on seed set.
+Our study tries to answer the following questions: (i) Do heterospecific pollen reduce seed set?
+To what extent do (ii) floral reproductive traits and (iii) relatedness, mediate the impacts of heterospecific pollen on seed set.
 
@@
 The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**).
-The different species of the study have different reproductive traits and different degree of relatedness where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
-Moreover, the species selected have fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
+The species of the study had different reproductive traits and different degree of relatedness where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
+Moreover, the species selected had fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
 For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).
@@
 
-The traits measured for each species were pollen per anther, number of ovules, stigma width and length and stigmatic area, style width and length, ovary width and length.
-Moreover stigma type [explain]() was tested.
+The traits measured for each species were pollen per anther, number of ovules and stigma, style, ovary width and length.
+For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type.
+All the morphometrical measurements were performed with a stereophotomicroscope.
 Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer.
@@
 Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
-The different morphometrical traits were measured with a digital stereomicrospe.
+Fruits per number of flowers treated were counted for Solanaceae species and for the rest, the number of seeds produced per average number of ovules of each species.
 Levels of self incompatibility were estimated by dividing the fruit set of hand self pollination by hand cross pollination @lloyd1992.
@@
 We used the statistical language `R` `r citep(citation())` for all our analyses.
-Differences of seed set between treatments and hand cross pollination for each species was tested through mixed linear models.
-For the following analysis we scaled the values of seed production for all the species with mean 0 and sd of 1.
-To test the effect of heterospecific pollen, we substracted to the seed set of hand cross pollination the seed set of heterospecific pollen treatments.
+Differences of seed set between treatments and hand cross pollination for each species were tested through mixed linear models.
+For the following analysis we scaled the values of seed production for all the species with mean 0 and sd of 1 in order to be able to compare across species.
+To test the effect of heterospecific pollen, we substracted to the mean seed set of hand cross pollination the mean seed set of heterospecific pollen treatments.
 In order to see correlations between heterospecific pollen effect and traits we performed Mantel test between the matrix of heterospecific pollen effect and the distance matrix of each trait (euclidean distances).

### 2019-02-24 Manuscript_draft/Manuscript_draft.Rmd
little change

@@
 We conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer.
-We conducted 1800 crosses by experimentally transferring pollen (50% and 100% ratio) with reciporcal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+We conducted 1800 crosses by experimentally transferring pollen (50% and 100% ratio) with reciprocal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
 Seed set was used as proxy of plant fitness.

### 2019-02-24 Manuscript_draft/Manuscript_draft.Rmd
edits methods

@@
 
-[I would explain three test.
-0) treatment effects with GLM's, 1) Mantels: relative effects, 2) GLM's or matrix models: Absolute effects and explain them in three independent paragraphs including a rationale of why]()
+To evaluate heterospecific pollen effect on seed production we performed linear mixed models.
+The distinct heterospecific pollination treatments were compared with the cross pollination treatment which was our control for optimum seed production for all the species.
+The different replicates of each treatment were considered as random effects.
+The changes of seed production per average number of ovules across species were compared through scaling the seed production with mean 0 and standard deviation of 1.
+All the analysis were conducted with the statistical language `R` `r citep(citation())`
+
+1) Mantels: relative effects
+
+2) GLM's or matrix models
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 
-We used the statistical language `R` `r citep(citation())` for all our analyses.
-Differences of seed set between treatments and hand cross pollination for each species were tested through mixed linear models.
-For the following analysis we scaled the values of seed production for all the species with mean 0 and sd of 1 in order to be able to compare across species.
-To test the effect of heterospecific pollen, we substracted to the mean seed set of hand cross pollination the mean seed set of heterospecific pollen treatments.
-In order to see correlations between heterospecific pollen effect and traits we performed Mantel test between the matrix of heterospecific pollen effect and the distance matrix of each trait (euclidean distances).
-Moreover, Mantel test was also conducted between heterospecific pollen effect and the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).
-[all is here, but I would break it by questions and give a bit more detail, to avoid overwhelm the reader]() We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species [Here I think you should think if this controls for the non independency of donors and recipients.
+ Moreover, Mantel test was also conducted between heterospecific pollen effect and   [Here I think you should think if this controls for the non independency of donors and recipients.
 I think not.
@@
 To evaluate heterospecific pollen effect on seed production we performed linear mixed models.
-The distinct heterospecific pollination treatments were compared with the cross pollination treatment which was our control for optimum seed production for all the species.
+The distinct heterospecific pollination treatments were compared thorugh relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species.
 The different replicates of each treatment were considered as random effects.
-The changes of seed production per average number of ovules across species were compared through scaling the seed production with mean 0 and standard deviation of 1.
+The changes of seed production across species were compared through scaling the seed production with mean 0 and standard deviation of 1 prior to the analysis.
 All the analysis were conducted with the statistical language `R` `r citep(citation())`
 
-1) Mantels: relative effects
+In order to test the relative effect of traits on seed production with foreign pollen we performed mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (euclidean distances).
+Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
+Moreover, to find a model with the best explanatory traits we used the function **bioenv** from R.
+Finally, we also conducted mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
 
-2) GLM's or matrix models
+We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance.
+
+the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).
+
+??We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes

@@
 experimentally transferring pollen (50\% and 100\% ratio) with
-reciporcal crosses between 10 species belonging to three different
+reciprocal crosses between 10 species belonging to three different
 families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used
@@
 belonging to three different families with different traits. Our study
-tries to answer the following question: To what extent do (i) floral
-reproductive traits and (ii) relatedness, mediate the impacts of
-heterospecific pollen on seed set.
+tries to answer the following questions: (i) Do heterospecific pollen
+reduce seed set? To what extent do (ii) floral reproductive traits and
+(iii) relatedness, mediate the impacts of heterospecific pollen on seed
+set.
 
@@
 species from three different families: Solanaceae, Brassicaceae and
-Convolvulaceae (\textbf{Table 1}). The different species of the study
-have different reproductive traits and different degree of relatedness
-where the reciprocal crosses between species allowed us to have multiple
+Convolvulaceae (\textbf{Table 1}). The species of the study had
+different reproductive traits and different degree of relatedness where
+the reciprocal crosses between species allowed us to have multiple
 different scenarios of both traits and relatedness. Moreover, the
-species selected have fast life cycle and low structural flower
+species selected had fast life cycle and low structural flower
 complexity in order to perform the pollination treatments and grow the
@@
 The traits measured for each species were pollen per anther, number of
-ovules, stigma width and length and stigmatic area, style width and
-length, ovary width and length. Moreover stigma type \href{}{explain}
-was tested. Pollen was counted for 20 anthers of each species with 4
-replicates per sample with an hemocytometer. Previously, anthers were
-squashed on a known solution with the pippete tip and homogeneize with a
-vortex for 30 seconds. Ovule number was counted with the help of an
-stereomicroscope and a small grid over a petri dish from 15 randomly
-selected flowers. The different morphometrical traits were measured with
-a digital stereomicrospe. Levels of self incompatibility were estimated
-by dividing the fruit set of hand self pollination by hand cross
-pollination Lloyd and Schoen (1992).
+ovules and stigma, style, ovary width and length. For the stigma, the
+stigmatic area was also measured and moreover the stigmas were divided
+in wet/dry type. All the morphometrical measurements were performed with
+a stereophotomicroscope. Pollen was counted for 20 anthers of each
+species with 4 replicates per sample with an hemocytometer. Previously,
+anthers were squashed on a known solution with the pippete tip and
+homogeneize with a vortex for 30 seconds. Ovule number was counted with
+the help of an stereomicroscope and a small grid over a petri dish from
+15 randomly selected flowers. Fruits per number of flowers treated were
+counted for Solanaceae species and for the rest, the number of seeds
+produced per average number of ovules of each species. Levels of self
+incompatibility were estimated by dividing the fruit set of hand self
+pollination by hand cross pollination Lloyd and Schoen (1992).
 
@@
 
-We used the statistical language \texttt{R} (R Core Team 2018) for all
-our analyses. Differences of seed set between treatments and hand cross
-pollination for each species was tested through mixed linear models. For
-the following analysis we scaled the values of seed production for all
-the species with mean 0 and sd of 1. To test the effect of
-heterospecific pollen, we substracted to the seed set of hand cross
-pollination the seed set of heterospecific pollen treatments. In order
-to see correlations between heterospecific pollen effect and traits we
-performed Mantel test between the matrix of heterospecific pollen effect
-and the distance matrix of each trait (euclidean distances). Moreover,
-Mantel test was also conducted between heterospecific pollen effect and
-the square root of the matrix of phylogenetic distance due to
+Moreover, Mantel test was also conducted between heterospecific pollen
+effect and the square root of the matrix of phylogenetic distance due to
 improvement in the statistical power (Letten \& Cornwell 2014).
@@
 
-\href{}{I would explain three test. 0) treatment effects with GLM's, 1)
-Mantels: relative effects, 2) GLM's or matrix models: Absolute effects
-and explain them in three independent paragraphs including a rationale
-of why}
+To evaluate heterospecific pollen effect on seed production we performed
+linear mixed models. The distinct heterospecific pollination treatments
+were compared thorugh relevelling each variable with the cross
+pollination treatment which was our control for optimum seed production
+for all the species. The different replicates of each treatment were
+considered as random effects. The changes of seed production across
+species were compared through scaling the seed production with mean 0
+and standard deviation of 1 prior to the analysis. All the analysis were
+conducted with the statistical language \texttt{R} (R Core Team 2018)
+
+In order to test the relative effect of traits on seed production with
+foreign pollen we performed mantel test between the assymetrical matrix
+of heterospecific pollen effect (10 by 10 matrix) with the different
+distance matrices of traits (euclidean distances). Heterospecific pollen
+effect was considered as the subtraction of seed production by hand
+cross pollination minus seed production of the different heterospecific
+pollen treatments.
+
+The
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
edits methods

@@
 
- Moreover, Mantel test was also conducted between heterospecific pollen effect and   [Here I think you should think if this controls for the non independency of donors and recipients.
-I think not.
-Maybe look onto matrix regresions?).
-Moreover, pairwise evolutive distances were calculated with MEGA7 for two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL).
-The sequences of interest were downloaded from NCBI GenBank and the phylogenetic tree constructed by maximum likelihood with MEGA7.[Make a section on how you contrsucted phylogeny]().
-
 To evaluate heterospecific pollen effect on seed production we performed linear mixed models.
@@
 The changes of seed production across species were compared through scaling the seed production with mean 0 and standard deviation of 1 prior to the analysis.
-All the analysis were conducted with the statistical language `R` `r citep(citation())`
+All the analysis were conducted with the statistical language `R` `r citep(citation())`.
 
@@
 Finally, we also conducted mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
+Moreover, We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect (develop this bit).
 
 We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance.
-
-the square root of the matrix of phylogenetic distance due to improvement in the statistical power (Letten & Cornwell 2014).
-
-??We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect, the independent variable the different traits and the random effects the different treatments per species
+Due to improvents in statistical power we used the square root of the phylogenetic distance (Letten & Cornwell 2014).
+Two different phylogenetic distances were used from two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL).
+The sequences were obtained from GenBank (https://www.ncbi.nlm.nih.gov/genbank/, accessed 20 Oct.
+2018).
+The sequences were aligned with clustal omega and the pairwise evolutive distances were calculated with MEGA7.
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
edits methods

@@
 
-Moreover, Mantel test was also conducted between heterospecific pollen
-effect and the square root of the matrix of phylogenetic distance due to
-improvement in the statistical power (Letten \& Cornwell 2014).
-\href{}{all is here, but I would break it by questions and give a bit
-more detail, to avoid overwhelm the reader} We explored also the
-relations between traits and heterospecific pollen effect through
-generalized mixed models where the response variable was heterospecific
-pollen effect, the independent variable the different traits and the
-random effects the different treatments per species {[}Here I think you
-should think if this controls for the non independency of donors and
-recipients. I think not. Maybe look onto matrix regresions?). Moreover,
-pairwise evolutive distances were calculated with MEGA7 for two kinds of
-markers: 1) Internal transcribed spacer (ITS) and 2)
-ribulose-bisphosphate carboxylase (RBCL). The sequences of interest were
-downloaded from NCBI GenBank and the phylogenetic tree constructed by
-maximum likelihood with MEGA7.\href{}{Make a section on how you
-contrsucted phylogeny}.
-
 To evaluate heterospecific pollen effect on seed production we performed
@@
 and standard deviation of 1 prior to the analysis. All the analysis were
-conducted with the statistical language \texttt{R} (R Core Team 2018)
+conducted with the statistical language \texttt{R} (R Core Team 2018).
 
@@
 cross pollination minus seed production of the different heterospecific
-pollen treatments.
+pollen treatments. Moreover, to find a model with the best explanatory
+traits we used the function \textbf{bioenv} from R. Finally, we also
+conducted mantel test between the matrix of heterospecific pollen effect
+and the distance matrix from all the traits. Moreover, We explored also
+the relations between traits and heterospecific pollen effect through
+generalized mixed models where the response variable was heterospecific
+pollen effect (develop this bit).
 
-The
+We conducted mantel test to check for correlations between
+heterospecific pollen effect and phylogenetic distance. Due to
+improvents in statistical power we used the square root of the
+phylogenetic distance (Letten \& Cornwell 2014). Two different
+phylogenetic distances were used from two kinds of markers: 1) Internal
+transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase
+(RBCL). The sequences were obtained from GenBank
+(\url{https://www.ncbi.nlm.nih.gov/genbank/}, accessed 20 Oct. 2018).
+The sequences were aligned with clustal omega and the pairwise evolutive
+distances were calculated with MEGA7.
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 
-In order to test the relative effect of traits on seed production with foreign pollen we performed mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (euclidean distances).
+In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances).
 Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
-Moreover, to find a model with the best explanatory traits we used the function **bioenv** from R.
-Finally, we also conducted mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
-Moreover, We explored also the relations between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect (develop this bit).
+To find a model with the best explanatory traits we used the function **bioenv** from R.
+We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
+Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes

@@
 In order to test the relative effect of traits on seed production with
-foreign pollen we performed mantel test between the assymetrical matrix
+foreign pollen we performed Mantel test between the assymetrical matrix
 of heterospecific pollen effect (10 by 10 matrix) with the different
-distance matrices of traits (euclidean distances). Heterospecific pollen
+distance matrices of traits (Euclidean distances). Heterospecific pollen
 effect was considered as the subtraction of seed production by hand
 cross pollination minus seed production of the different heterospecific
-pollen treatments. Moreover, to find a model with the best explanatory
-traits we used the function \textbf{bioenv} from R. Finally, we also
-conducted mantel test between the matrix of heterospecific pollen effect
-and the distance matrix from all the traits. Moreover, We explored also
-the relations between traits and heterospecific pollen effect through
-generalized mixed models where the response variable was heterospecific
-pollen effect (develop this bit).
+pollen treatments. To find a model with the best explanatory traits we
+used the function \textbf{bioenv} from R. We also conducted Mantel test
+between the matrix of heterospecific pollen effect and the distance
+matrix from all the traits. Moreover, we explored also the correlation
+between traits and heterospecific pollen effect through generalized
+mixed models where the response variable was heterospecific pollen
+effect and the explanatory variable the different traits.
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes methods

@@
 In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances).
-Heterospecific pollen effect was considered as the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
+Heterospecific pollen effect was obtain through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
 To find a model with the best explanatory traits we used the function **bioenv** from R.
@@
 2018).
-The sequences were aligned with clustal omega and the pairwise evolutive distances were calculated with MEGA7.
+The sequences were aligned with clustal omega and the pairwise evolutive distances calculated with MEGA7.
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes methods

@@
 distance matrices of traits (Euclidean distances). Heterospecific pollen
-effect was considered as the subtraction of seed production by hand
+effect was obtain through the subtraction of seed production by hand
 cross pollination minus seed production of the different heterospecific
@@
 The sequences were aligned with clustal omega and the pairwise evolutive
-distances were calculated with MEGA7.
+distances calculated with MEGA7.
 

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes
change

@@
 To evaluate heterospecific pollen effect on seed production we performed linear mixed models.
-The distinct heterospecific pollination treatments were compared thorugh relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species.
+The distinct heterospecific pollination treatments were compared through relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species.
 The different replicates of each treatment were considered as random effects.
-The changes of seed production across species were compared through scaling the seed production with mean 0 and standard deviation of 1 prior to the analysis.
+Seed production was scaled for all the species with mean 0 and standard deviation of 1 prior to the analysis.
 All the analysis were conducted with the statistical language `R` `r citep(citation())`.
@@
 In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances).
-Heterospecific pollen effect was obtain through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
+Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
 To find a model with the best explanatory traits we used the function **bioenv** from R.
@@
 
-\newpage
-
 # RESULTS
 
-Results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in **Table 2**.
+Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Table 2**.
 Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
+
 Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine.

### 2019-02-25 Manuscript_draft/Manuscript_draft.tex
changes
change

@@
 linear mixed models. The distinct heterospecific pollination treatments
-were compared thorugh relevelling each variable with the cross
+were compared through relevelling each variable with the cross
 pollination treatment which was our control for optimum seed production
 for all the species. The different replicates of each treatment were
-considered as random effects. The changes of seed production across
-species were compared through scaling the seed production with mean 0
-and standard deviation of 1 prior to the analysis. All the analysis were
-conducted with the statistical language \texttt{R} (R Core Team 2018).
+considered as random effects. Seed production was scaled for all the
+species with mean 0 and standard deviation of 1 prior to the analysis.
+All the analysis were conducted with the statistical language \texttt{R}
+(R Core Team 2018).
 
@@
 distance matrices of traits (Euclidean distances). Heterospecific pollen
-effect was obtain through the subtraction of seed production by hand
+effect was obtained through the subtraction of seed production by hand
 cross pollination minus seed production of the different heterospecific
@@
 
-\newpage
-
 \section{RESULTS}\label{results}
 
-Results of hand cross pollination, self hand pollination, natural
+Results of hand cross-pollination, self hand-pollination, natural
 selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
@@
 pollen treatments for 65\% of the pairwise interactions
-p\textless{}0.05. Across families we found a very similar effect but
-when species where look at species level they respond differently even
-within the same family \href{}{rephrase and maybe test statistically?},
-for instance for two species of the Brassicaceae family \emph{Brassica
-oleracea} and \emph{Eruca versicaria} we found very contrasting effects
-of foreign pollen where for the first one, all donors reduce seed set
+p\textless{}0.05.
+
+Across families we found a very similar effect but when species where
+look at species level they respond differently even within the same
+family \href{}{rephrase and maybe test statistically?}, for instance for
+two species of the Brassicaceae family \emph{Brassica oleracea} and
+\emph{Eruca versicaria} we found very contrasting effects of foreign
+pollen where for the first one, all donors reduce seed set
 significatively and for the second, just two species did out of nine.

### 2019-02-25 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
 
-Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Table 2**.
+Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for values).
 Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
@@
 melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()
-
-\newpage
-
-**Table 2**.
-Perecentage of seeds produced per ovule for the ten species used in the experiment.
-The treatments presented are hand cross pollination, hand self pollination, natural selfing and apomixis (emasculated flowers).
-[turn into a figure somehow?]()
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-load("table_treatments.RData")
-Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-Cross <- cross
-Self <- self
-Natural_selfing <- nat_self
-Apomixis <- apo
-table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
-kable(table, format="markdown")
-```
 
@@
 
+# APPENDIX
+
+1.
+
+**Table S1**.
+Perecentage of seeds produced per ovule for the ten species used in the experiment.
+The treatments presented are hand cross pollination, hand self pollination, natural selfing and apomixis (emasculated flowers).
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+load("table_treatments.RData")
+Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+Cross <- cross
+Self <- self
+Natural_selfing <- nat_self
+Apomixis <- apo
+table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
+kable(table, format="markdown")
+```
+
 \eleft

### 2019-02-25 Scripts/Traits/Reproductive_biology_treatments.R

@@ -31,8 +31,8 @@ table_melt$variable[table_melt$variable=="Apomixis"] <- "Apomixis"
 library(extrafont)
 library(forcats)
 
-font_import()
-fonts()
+#font_import()
+#fonts()
 
 cross  <- subset(table_melt,variable=="Hand cross pollination"  )
 self  <- subset(table_melt, table_melt$variable=="Hand self pollination" )
@@ -42,6 +42,7 @@ bio$Species <- factor(bio$Species, levels = rev(unique(bio$Species)), ordered=TR
 bio$variable <- factor(bio$variable, levels = c("Hand cross pollination","Hand self pollination","Natural selfing","Apomixis"))
 
 #save.image("Manuscript_draft/r_biology.RData")
+load("Manuscript_draft/r_biology.RData")
 
 ggplot(bio,aes(x=Species,y=value,fill=variable))+
   geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
@@ -49,3 +50,8 @@ ggplot(bio,aes(x=Species,y=value,fill=variable))+
   theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"))+
   scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))
 
+ggplot(bio,aes(x=Species,y=value,fill=variable))+
+  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
+  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
+  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"))+
+  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
Some edits to be able to knit on mac

@@
 Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds.
-Ovule number was counted with the help of an stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
+Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
 Fruits per number of flowers treated were counted for Solanaceae species and for the rest, the number of seeds produced per average number of ovules of each species.
@@
 
-Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for values).
-Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
+Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values).
+Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
 
@@
   theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
-  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = "Arial Narrow"), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
+  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
   scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2019-02-26 Manuscript_draft/Manuscript_draft.tex
changes
Some edits to be able to knit on mac

@@
 homogeneize with a vortex for 30 seconds. Ovule number was counted with
-the help of an stereomicroscope and a small grid over a petri dish from
+the help of a stereomicroscope and a small grid over a petri dish from
 15 randomly selected flowers. Fruits per number of flowers treated were
@@
 Results of hand cross-pollination, self hand-pollination, natural
-selfing and apomixis are presented in \textbf{Table 2}. Heterospecific
-pollen reduced seet set signifcatively with the 50-50\% heterospecific
-pollen treatments for 65\% of the pairwise interactions
-p\textless{}0.05.
+selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
+for table with values). Heterospecific pollen reduced seet set
+significatively with the 50-50\% heterospecific pollen treatments for
+65\% of the pairwise interactions p\textless{}0.05.
 
@@
 
-\textbf{Table 2}. Perecentage of seeds produced per ovule for the ten
-species used in the experiment. The treatments presented are hand cross
-pollination, hand self pollination, natural selfing and apomixis
-(emasculated flowers). \href{}{turn into a figure somehow?}
-
-\begin{longtable}[]{@{}lrrrr@{}}
-\toprule
-Species & Cross & Self & Natural\_selfing & Apomixis\tabularnewline
-\midrule
-\endhead
-Brassica oleracea & 32.06897 & 0.0000000 & 0.00000 & 0\tabularnewline
-Brassica rapa & 44.97041 & 0.0000000 & 0.00000 & 0\tabularnewline
-Eruca versicaria & 23.75000 & 0.4166667 & 0.00000 & 0\tabularnewline
-Sinapis alba & 43.33333 & 48.3333333 & 5.00000 & 15\tabularnewline
-Ipomoea aquatica & 40.00000 & 30.0000000 & 20.00000 & 0\tabularnewline
-Ipomoea purpurea & 31.66667 & 86.6666667 & 31.66667 & 0\tabularnewline
-Capsicum annuum & 100.00000 & 66.2240664 & 23.48548 & 0\tabularnewline
-Petunia integrifolia & 100.00000 & 24.7727273 & 0.00000 &
-0\tabularnewline
-Solanum lycopersicum & 90.38043 & 43.4782609 & 70.00000 &
-0\tabularnewline
-Solanum melongena & 60.47525 & 87.9702970 & 21.56436 & 0\tabularnewline
-\bottomrule
-\end{longtable}
-
-\newpage
-
 \begin{figure}
 \centering
-\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
 \caption{Barplot with the different treatments that provide information
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
 \caption{The effect of heterospecific pollen (scaled see set) is
@@
 
+\section{APPENDIX}\label{appendix}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+\end{enumerate}
+
+\textbf{Table S1}. Perecentage of seeds produced per ovule for the ten
+species used in the experiment. The treatments presented are hand cross
+pollination, hand self pollination, natural selfing and apomixis
+(emasculated flowers).
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\toprule
+Species & Cross & Self & Natural\_selfing & Apomixis\tabularnewline
+\midrule
+\endhead
+Brassica oleracea & 32.06897 & 0.0000000 & 0.00000 & 0\tabularnewline
+Brassica rapa & 44.97041 & 0.0000000 & 0.00000 & 0\tabularnewline
+Eruca versicaria & 23.75000 & 0.4166667 & 0.00000 & 0\tabularnewline
+Sinapis alba & 43.33333 & 48.3333333 & 5.00000 & 15\tabularnewline
+Ipomoea aquatica & 40.00000 & 30.0000000 & 20.00000 & 0\tabularnewline
+Ipomoea purpurea & 31.66667 & 86.6666667 & 31.66667 & 0\tabularnewline
+Capsicum annuum & 100.00000 & 66.2240664 & 23.48548 & 0\tabularnewline
+Petunia integrifolia & 100.00000 & 24.7727273 & 0.00000 &
+0\tabularnewline
+Solanum lycopersicum & 90.38043 & 43.4782609 & 70.00000 &
+0\tabularnewline
+Solanum melongena & 60.47525 & 87.9702970 & 21.56436 & 0\tabularnewline
+\bottomrule
+\end{longtable}
+
 \eleft

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
   geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
-  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology tests")+
+  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
   theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
things to add to methods and results

@@
 
+[Add pollen on stigma counts to methods](Jose)
+
+[Next bit to results, also divided it with ]
+Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008.
+Proportions of pollen talk about it to 50-50 mix?
+Talk aboout this in methods too.
+
 # RESULTS

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
change

--- 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
@@
 
+[Add pollen on stigma counts to methods](Jose)
+
+[Next bit to results, also divided it with ]
+
+Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008.
+Proportions of pollen talk about it to 50-50 mix?
+Talk aboout this in methods too.
+
 # RESULTS

### 2019-02-26 Scripts/Analysis/Total_pollen_Stigma_area_corr.R
changes

@@ -42,6 +42,4 @@ cor.test(test$total_pollen, test$stigma_area, method=c("pearson"))
 test <- merge(total_pollen, stigma_width, by="species")
 cor.test(test$total_pollen, test$stigma_width, method=c("pearson"))
 
-#No significant correlation was found
-#However, further corr should be explored
-#Small sample size and 
+ 

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
more edits
changes
counts

@@
 Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.
-In order to confirm that the treatments applied were the desire proportions, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
+In order to confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species calculated.
+In total 20 different heterospecific crosses were counted, all the focal species with crosses of just on species of the other two families (N=3).
 
@@
 Talk aboout this in methods too.
+
+Add also plot with fruit production and pot it in appendix.Also the plots of ratios to appendices.
 

### 2019-02-26 Manuscript_draft/Manuscript_draft.tex
counts

@@
 proportions, for each focal species the total stigmatic load of pollen
-was counted from one donor of each family (N=3).
+was counted from one donor of each family (N=3). In order to test the
+amount of pollen grains deposited on the stigma with heterospecific
+pollinations we counted the total amount of pollen grains and we
+calculated the proportions between the two species of the mix. We did
+the counts for each species with crosses with one species of the other
+two families, therefore 20 different types of mixes with 3 replicates.
 
@@
 \href{Jose}{Phylogenetic signal of traits?}
+
+\href{Jose}{Add pollen on stigma counts to methods}
+
+{[}Next bit to results, also divided it with {]}
+
+Total pollen deposited on stigmas was significantly correlated with the
+stigmatic area, pearsons correlation=0.57 and p-value=0.008. Proportions
+of pollen talk about it to 50-50 mix? Talk aboout this in methods too.
+
+Add also plot with fruit production and pot it in appendix.Also the
+plots of ratios to appendices.
 

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
edits methods

--- 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
@@
 Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.
-In order to confirm that the treatments applied were the desire proportions, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).
+In order to confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix.
+Therefore, 20 different heterospecific crosses 50-50% were counted for all the focal species with crosses of just one species of the other two families (N=3).
 

### 2019-02-26 Manuscript_draft/Manuscript_draft.tex
edits methods

@@
 order to confirm that the treatments applied were the desire
-proportions, for each focal species the total stigmatic load of pollen
-was counted from one donor of each family (N=3). In order to test the
-amount of pollen grains deposited on the stigma with heterospecific
-pollinations we counted the total amount of pollen grains and we
-calculated the proportions between the two species of the mix. We did
-the counts for each species with crosses with one species of the other
-two families, therefore 20 different types of mixes with 3 replicates.
+proportions, the total stigmatic load of pollen was counted and the
+proportions calculated between the two species of the mix. Therefore, 20
+different heterospecific crosses 50-50\% were counted for all the focal
+species with crosses of just one species of the other two families
+(N=3).
 

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
edits
More edits

@@
 Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.
+In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.
 
@@
 
+2.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("pollen_ratio.RData")
+ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+```
+
 \eleft

### 2019-02-26 Scripts/Traits/pollen_ratio_stigma.R

@@ -77,8 +77,10 @@ pollen_ratios_solanaceae <- pollen_ratios[pollen_ratios$focal!="Morning glory" &
 #write.csv(pollen_ratios_solanaceae, "Rmd/Data/pollen_ratios_solanaceae.csv")
 
 ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Solanaceae") +
-  theme(axis.text.x=element_text(angle=60,hjust=1)) + scale_fill_grey() +  theme_classic() + geom_hline(yintercept = 50)
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
 
 #Convolvulaceae
 
@@ -90,10 +92,10 @@ pollen_ratios_convolvulaceae <- pollen_ratios[pollen_ratios$focal!="Capsicum" & 
                                & pollen_ratios$focal!="Rocket"& pollen_ratios$focal!="Tomato"& pollen_ratios$focal!="Petunia",  ]
 
 #write.csv(pollen_ratios_convolvulaceae, "Rmd/Data/pollen_ratios_convolvulaceae.csv")
-
+#save.image("Manuscript_draft/pollen_ratio.RData")
 #Now the angle is right
 
 ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Convolvulaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey() + 
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

### 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
changes

--- 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
@@
 
+2.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("pollen_ratio.RData")
+
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
+ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
+ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+```
+
 \eleft

### 2019-02-26 Scripts/Traits/pollen_ratio_stigma.R

@@ -63,10 +63,11 @@ pollen_ratios_brassicaceae <- pollen_ratios[pollen_ratios$focal!="Morning glory"
 
 #write.csv(pollen_ratios_brassicaceae, "Rmd/Data/pollen_ratios_brassicaceae.csv")
 
-
 ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae") +
-  theme(axis.text.x=element_text(angle=60,hjust=1)) + scale_fill_grey() +  theme_classic() + geom_hline(yintercept = 50)
+  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
 
 #Solanaceae pollen ratio plot
 

### 2019-02-27 Manuscript_draft/Manuscript_draft.Rmd
some more edits

--- 2019-02-26 Manuscript_draft/Manuscript_draft.Rmd
@@
 
+2.
+
+**Figure S1**.
+Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
+All the species were crossed with a species of the other two families (N=3).
+To prepare these ratios all the pollen grains on the stigma were counted.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+load("pollen_ratio.RData")
+
+ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
+ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
+ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+
+```
+
 \eleft

### 2019-02-27 Manuscript_draft/Manuscript_draft.tex
edits
More edits
changes
some more edits

@@
 mixed models where the response variable was heterospecific pollen
-effect and the explanatory variable the different traits.
+effect and the explanatory variable the different traits. In addition,
+we tested the correlation between the total amount of pollen deposited
+on the stigma with heterospecific pollinations and the stigma size
+through Pearson's correlation.
 
@@
 
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\setcounter{enumi}{1}
+\item
+\end{enumerate}
+
+\textbf{Figure S1}. Pollen ratios separated by family A) Brassicaceae,
+B) Solanaceae, C) Convolvulaceae. All the species were crossed with a
+species of the other two families (N=3). To prepare these ratios all the
+pollen grains on the stigma were counted.
+
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-5-2.pdf}
+\includegraphics{output/figures/unnamed-chunk-5-3.pdf}
+
 \eleft

### 2019-02-27 Scripts/Traits/pollen_ratio_stigma.R

@@ -65,7 +65,7 @@ pollen_ratios_brassicaceae <- pollen_ratios[pollen_ratios$focal!="I. purpurea" &
 
 ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
 
 
@@ -79,7 +79,7 @@ pollen_ratios_solanaceae <- pollen_ratios[pollen_ratios$focal!="I. purpurea" & p
 
 ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
 
 
@@ -98,5 +98,5 @@ save.image("Manuscript_draft/pollen_ratio.RData")
 
 ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")

### 2019-03-02 Effect_size_plot.Rmd
solanaceae panel, still have to figure out how to fix sizes!

---
title: "Effect_size_Markdown"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)

#SOLY
load("Manuscript_draft/effect_size_species/soly_effect_size.RData")
p1<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

#SOME
load("Manuscript_draft/effect_size_species/some_effect_size.RData")
p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

#CAAN
load("Manuscript_draft/effect_size_species/caan_effect_size.RData")
p3<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

#PEIN
load("Manuscript_draft/effect_size_species/pein_effect_size.RData")
p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

 grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")

```

### 2019-03-02 Effect_size_plot.Rmd
close to be very acceptable, add Title, and levels to each one on top right... Then do the same for Brassicaceae and conv and then try a panel with all...

@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4,fig.width=7}
 
@@
 library(multipanelfigure)
+library(grid)
 
@@
 load("Manuscript_draft/effect_size_species/soly_effect_size.RData")
-p1<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
-width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p1<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("Treatments") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
@@
 load("Manuscript_draft/effect_size_species/some_effect_size.RData")
-p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
-width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
@@
 load("Manuscript_draft/effect_size_species/caan_effect_size.RData")
-p3<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
-width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p3<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
@@
 load("Manuscript_draft/effect_size_species/pein_effect_size.RData")
-p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper, size=2,color=factor(Family)),
-width = 0.2)+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
 
- grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
 
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),nrow=2))
 ```

### 2019-03-02 Effect_size_plot.Rmd
edits

@@
 load("Manuscript_draft/effect_size_species/some_effect_size.RData")
-p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
@@
 load("Manuscript_draft/effect_size_species/pein_effect_size.RData")
-p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
@@
 
- grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),nrow=2))
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4), size="last"),nrow=2))
 ```

### 2019-03-02 Effect_size_plot.Rmd
EDIT

--- 2019-03-02 Effect_size_plot.Rmd
@@
   xlab("Treatments") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "A)")
 
@@
 load("Manuscript_draft/effect_size_species/some_effect_size.RData")
-p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "B)")
 
@@
   xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "C)")
 
@@
 load("Manuscript_draft/effect_size_species/pein_effect_size.RData")
-p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "D)")
 
@@
 
- grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),nrow=2))
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4), size="last"),nrow=2))
+
 ```

### 2019-03-02 Effect_size_plot.Rmd
some edits

--- 2019-03-02 Effect_size_plot.Rmd
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4,fig.width=7}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
 
@@
 
+#SOME
+load("Manuscript_draft/effect_size_species/some_effect_size.RData")
+p1<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")
+
 #SOLY
 load("Manuscript_draft/effect_size_species/soly_effect_size.RData")
-p1<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+pp2<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "B)")
+
+#SIAL
+load("Manuscript_draft/effect_size_species/sial_effect_size.RData")
+p3<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "C)")
+
+#PEIN
+load("Manuscript_draft/effect_size_species/pein_effect_size.RData")
+p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "D)")
+
+#IPPU
+load("Manuscript_draft/effect_size_species/ippu_effect_size.RData")
+p5<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   xlab("Treatments") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "E)")
 
-#SOME
-load("Manuscript_draft/effect_size_species/some_effect_size.RData")
-p5<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+#IPAQ
+load("Manuscript_draft/effect_size_species/ipaq_effect_size.RData")
+p6<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "F)")
+
+#ERSA
+load("Manuscript_draft/effect_size_species/ersa_effect_size.RData")
+p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")
 
@@
 load("Manuscript_draft/effect_size_species/caan_effect_size.RData")
-p3<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("Treatments") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")
 
-#PEIN
-load("Manuscript_draft/effect_size_species/pein_effect_size.RData")
-p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+#BRRA
+load("Manuscript_draft/effect_size_species/brra_effect_size.RData")
+p9<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
   xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "I)")
+
+#BROL
+load("Manuscript_draft/effect_size_species/brol_effect_size.RData")
+p10<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "J)")
 
  #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+grid.newpage()
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
 
- grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),cbind(ggplotGrob(p1),ggplotGrob(p5), size="last"),nrow=2))
 ```

### 2019-03-02 Manuscript_draft/Manuscript_draft.Rmd
edits
effect sizes for the different species added

@@
 \newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="Effect sizes for the 10 different species.
+The different families appear with different colours, when a species was focal was coloured differently from its family."}
+
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+#SOME
+load("effect_size_species/some_effect_size.RData")
+p1<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")
+
+#SOLY
+load("effect_size_species/soly_effect_size.RData")
+pp2<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "B)")
+
+#SIAL
+load("effect_size_species/sial_effect_size.RData")
+p3<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "C)")
+
+#PEIN
+load("effect_size_species/pein_effect_size.RData")
+p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "D)")
+
+#IPPU
+load("effect_size_species/ippu_effect_size.RData")
+p5<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("Treatments") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "E)")
+
+#IPAQ
+load("effect_size_species/ipaq_effect_size.RData")
+p6<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "F)")
+
+#ERSA
+load("effect_size_species/ersa_effect_size.RData")
+p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")
+
+#CAAN
+load("effect_size_species/caan_effect_size.RData")
+p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")
+
+#BRRA
+load("effect_size_species/brra_effect_size.RData")
+p9<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "I)")
+
+#BROL
+load("effect_size_species/brol_effect_size.RData")
+p10<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "J)")
+
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+grid.newpage()
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
+
+```
+
+\newpage
 
@@
 Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
-All the species were crossed with a species of the other two families (N=3).
+Pollen was counted for crosses with species of the other two families (N=3).
 To prepare these ratios all the pollen grains on the stigma were counted.

### 2019-03-02 Manuscript_draft/Manuscript_draft.tex
edits
effect sizes for the different species added

@@
 
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\caption{Effect sizes for the 10 different species. The different
+families appear with different colours, when a species was focal was
+coloured differently from its family.}
+\end{figure}
+
+\newpage
+
 Mantel test indicates that a possible?? \href{}{It exists!} correlation
@@
 \textbf{Figure S1}. Pollen ratios separated by family A) Brassicaceae,
-B) Solanaceae, C) Convolvulaceae. All the species were crossed with a
+B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with
 species of the other two families (N=3). To prepare these ratios all the
@@
 
-\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\includegraphics{output/figures/unnamed-chunk-5-2.pdf}
-\includegraphics{output/figures/unnamed-chunk-5-3.pdf}
+\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-6-2.pdf}
+\includegraphics{output/figures/unnamed-chunk-6-3.pdf}
 

### 2019-03-02 Effect_size_families_plot.Rmd
markdown with first species

---
title: "Effect_size_families"
author: "Jose Barragan"
date: "3 March 2019"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

load("Manuscript_draft/effect_size_species/some_effect_size_family.RData")

p1<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)
p1 + geom_point(show.legend = FALSE,aes(color=factor(Family))) +
  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

```

### 2019-03-03 Effect_size_families_plot.Rmd
edits

@@
 date: "3 March 2019"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
@@
 
-p1<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)
-p1 + geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+p1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
   geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
@@
 
+load("Manuscript_draft/effect_size_species/soly_effect_size_family.RData")
+
+p2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/sial_effect_size_family.RData")
+
+p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/pein_effect_size_family.RData")
+
+p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/ippu_effect_size_family.RData")
+
+p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/ipaq_effect_size_family.RData")
+
+p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/ersa_effect_size_family.RData")
+
+p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/caan_effect_size_family.RData")
+
+p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/brra_effect_size_family.RData")
+
+p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Manuscript_draft/effect_size_species/brol_effect_size_family.RData")
+
+p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(show.legend = FALSE,aes(color=factor(Family))) +
+  geom_errorbar(show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+grid.newpage()
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(p2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
 ```

### 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
some edits, error to knit, dont know why
edits

@@
 
+```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="A"}
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+load("effect_size_species/some_effect_size_family.RData")
+
+pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/soly_effect_size_family.RData")
+
+pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/sial_effect_size_family.RData")
+
+p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/pein_effect_size_family.RData")
+
+p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/ippu_effect_size_family.RData")
+
+p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/ipaq_effect_size_family.RData")
+
+p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/ersa_effect_size_family.RData")
+
+p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/caan_effect_size_family.RData")
+
+p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/brra_effect_size_family.RData")
+
+p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("effect_size_species/brol_effect_size_family.RData")
+
+p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+grid.newpage()
+ grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
+```
+
+\newpage
+
 Mantel test indicates that a possible??

### 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species.
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species.
 The y axis is the proportion of ovules converted to seed in percentage.
@@
   theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
-  theme(axis.text.x = element_text(angle = 35, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
   scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))

### 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
small edit
edits

@@
 
+Add effect sizes to analysis!!
+
 # RESULTS
@@
 Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
+Moreover, effect sizes differ across species, see **Figure 2** where species like *S.
+lycopersicum* had a large effect size and other's like *E.
+sativa* a small or null effect size.
 
@@
 
+Maybe for this plot I have to do hedges'g instead of cohean because of different sample sizes when I group the treatments per family. Check
+
 \newpage

### 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
+\newpage
 **Table 1**
@@
 kable(table, format="markdown")
+```
+
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=6,fig.height=5, fig.cap="A"}
+library(ape)
+library(phytools)
+pollen_tree=read.tree("Data/pollen_tree.nwk")
+plot(pollen_tree)
+add.scale.bar(x=0, y=1, length = 0.01)
 ```

### 2019-03-03 Manuscript_draft/Manuscript_draft.tex
some edits, error to knit, dont know why
edits

@@
 
-\textbf{Table 1}
+\newpage
+*
+
+*Table 1**
 
@@
 \end{longtable}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
+\caption{A}
+\end{figure}
 
@@
 
+Add effect sizes to analysis!!
+
 \section{RESULTS}\label{results}
@@
 significatively with the 50-50\% heterospecific pollen treatments for
-65\% of the pairwise interactions p\textless{}0.05.
+65\% of the pairwise interactions p\textless{}0.05. Moreover, effect
+sizes differ across species, see \textbf{Figure 2} where species like
+\emph{S. lycopersicum} had a large effect size and other's like \emph{E.
+sativa} a small or null effect size.
 
@@
 \begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
-\caption{Barplot with the different treatments that provide information
-of the reproductive biology of the ten species. The y axis is the
-proportion of ovules converted to seed in percentage. The different
-treatments (N=10) which are presented in the legend are, hand cross
-pollination, hand self pollination, natural selfing and apomixis. More
-information about these treatments can be found in Methods and
-Appendices.}
+
+{\centering \includegraphics{output/figures/unnamed-chunk-3-1}
+
+}
+
+\caption{Barplot with the different treatments that provide information of the reproductive biology of the ten species.
+The y axis is the proportion of ovules converted to seed in percentage.
+The different treatments (N=10) which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis.
+More information about these treatments can be found in Methods and Appendices.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-3-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
 \caption{Effect sizes for the 10 different species. The different
@@
 \end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\caption{A}
+\end{figure}
+
+Maybe for this plot I have to do hedges'g instead of cohean because of
+different sample sizes when I group the treatments per family. Check
 
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
 \caption{The effect of heterospecific pollen (scaled see set) is
@@
 
-\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
-\includegraphics{output/figures/unnamed-chunk-6-2.pdf}
-\includegraphics{output/figures/unnamed-chunk-6-3.pdf}
+\includegraphics{output/figures/unnamed-chunk-8-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-8-2.pdf}
+\includegraphics{output/figures/unnamed-chunk-8-3.pdf}
 

### 2019-03-04 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 library(phytools)
+library(png)
+
 pollen_tree=read.tree("Data/pollen_tree.nwk")
+
 plot(pollen_tree)
 add.scale.bar(x=0, y=1, length = 0.01)
+
+a <- readPNG("images/tomato.png")
+b <- readPNG("images/bra_colour.png")
+c <- readPNG("images/ipomoea.png")
+
+rasterImage(image=a, xleft=0.08,ybottom=1,
+            xright=1.2,ytop=3.6)
+rasterImage(image=b, xleft=0.15,ybottom=7,xright=0.18,ytop=10)
+
+rasterImage(image=c, xleft=0.15,ybottom=4,xright=0.18,ytop=7)
+
 ```

### 2019-03-04 Manuscript_draft/Manuscript_draft.Rmd
edits

--- 2019-03-03 Manuscript_draft/Manuscript_draft.Rmd
@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=6,fig.height=5, fig.cap="A"}
-library(ape)
-library(phytools)
-pollen_tree=read.tree("Data/pollen_tree.nwk")
-plot(pollen_tree)
-add.scale.bar(x=0, y=1, length = 0.01)
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="A"}
+knitr::include_graphics('images/phylo_image.png')
 ```

### 2019-03-04 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="A"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae."}
 knitr::include_graphics('images/phylo_image.png')

### 2019-03-04 Scripts/Phylogeny/phylogenetic_signal.R

@@ -3,6 +3,7 @@ library(phytools)
 pollen_tree=read.tree("Data/pollen_tree.nwk")
 #pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
 #pollen_tree=read.tree("Data/tree_neighbour.nwk")
+png("phylo_image.png", units="px", width=1600, height=1600, res=300)
 
 plot(pollen_tree)
 add.scale.bar(x=0, y=1, length = 0.01)
@@ -15,12 +16,13 @@ a <- readPNG("images/tomato.png")
 b <- readPNG("images/bra_colour.png")
 c <- readPNG("images/ipomoea.png")
 
-rasterImage(image=a, xleft=0.15,ybottom=1,
-            xright=0.18,ytop=3.6)
-rasterImage(image=b, xleft=0.15,ybottom=7,xright=0.18,ytop=10)
+rasterImage(image=a, xleft=0.14,ybottom=1,
+            xright=0.16,ytop=4.1)
+rasterImage(image=b, xleft=0.14,ybottom=7.1,xright=0.16,ytop=10.1)
 
-rasterImage(image=c, xleft=0.15,ybottom=4,xright=0.18,ytop=7)
+rasterImage(image=c, xleft=0.14,ybottom=4.2,xright=0.16,ytop=6.8)
 
+dev.off()
 
 
 tree_10 <- read.newick("Data/pollen_tree_no_outgroup.nwk")

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
Edits

@@
 
+```
+
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="A"}
+
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+load("effect_size_species/effect_size_total.RData")
+
+ ggplot(all, aes(Family,Cohen_d,colour=Family_1), size=10) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))+ geom_point( aes(colour=Family_1),size=2) +
+  geom_errorbar(aes(x = Family, ymin = Lower, 
+ymax = Upper,colour=Family_1), width = 0.2, size=0.8)+
+  scale_color_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
+  scale_fill_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
+  xlab("") + ylab("Cohen's d") + rotate()+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')
 ```

### 2019-03-05 Effect_sizes_total.R

@@ -593,5 +593,6 @@ p1 + geom_point(show.legend = FALSE,aes(color=factor(Family_1))) +
   xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
 
+save.image("Manuscript_draft/effect_size_species/effect_size_total.RData")
 
 

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="A"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species."}
 

### 2019-03-05 Manuscript_draft/Manuscript_draft.tex
edits
Edits

@@
 \begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-2-1.pdf}
-\caption{A}
+\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae.}\label{fig:unnamed-chunk-2}
 \end{figure}
@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\caption{Average effect size and confidence intervals (95\%) of the 9
+heterospecific treatments of 50\% pollen to the different 10 focal
+species}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
 \caption{Effect sizes for the 10 different species. The different
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
 \caption{A}
@@
 \centering
-\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
 \caption{The effect of heterospecific pollen (scaled see set) is
@@
 
-\includegraphics{output/figures/unnamed-chunk-8-1.pdf}
-\includegraphics{output/figures/unnamed-chunk-8-2.pdf}
-\includegraphics{output/figures/unnamed-chunk-8-3.pdf}
+\includegraphics{output/figures/unnamed-chunk-9-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-9-2.pdf}
+\includegraphics{output/figures/unnamed-chunk-9-3.pdf}
 

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
EDITS

--- 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6,fig.cap="A"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=3,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}
 

### 2019-03-05 Manuscript_draft/Manuscript_draft.tex
EDITS

@@
 heterospecific treatments of 50\% pollen to the different 10 focal
-species}
+species coloured by family.}
 \end{figure}

### 2019-03-05 Effect_sizes_total.R

@@ -58,7 +58,7 @@ families<- sort(unique(soly_seeds$Family))
 b <- NULL
 x <- NULL
 for (i in families){
-  a<-cohen.d(soly_seeds$Seed_set[soly_seeds$Family==i], soly_cross$Seed_set)
+  a<-cohen.d(soly_seeds$Seed_set[soly_seeds$Family==i], soly_cross$Seed_set,hedges.correction=TRUE)
   b <- rbind(b, a[3])
   x<- rbind(x, a[4])
 }
@@ -108,7 +108,7 @@ families<- sort(unique(some_seeds$Family))
 b <- NULL
 x <- NULL
 for (i in families){
-  a<-cohen.d(some_seeds$Seed_set[some_seeds$Family==i], some_cross$Seed_set)
+  a<-cohen.d(some_seeds$Seed_set[some_seeds$Family==i], some_cross$Seed_set,hedges.correction=TRUE)
   b <- rbind(b, a[3])
   x<- rbind(x, a[4])
 }
@@ -160,7 +160,7 @@ families<- sort(unique(caan_seeds$Family))
 b <- NULL
 x <- NULL
 for (i in families){
-  a<-cohen.d(caan_seeds$Seed_set[caan_seeds$Family==i], caan_cross$Seed_set)
+  a<-cohen.d(caan_seeds$Seed_set[caan_seeds$Family==i], caan_cross$Seed_set,hedges.correction=TRUE)
   b <- rbind(b, a[3])
   x<- rbind(x, a[4])
 }
@@ -212,7 +212,7 @@ families<- sort(unique(pein_seeds$Family))
 b <- NULL
 x <- NULL
 for (i in families){
-  a<-cohen.d(pein_seeds$Seed_set[pein_seeds$Family==i], pein_cross$Seed_set)
+  a<-cohen.d(pein_seeds$Seed_set[pein_seeds$Family==i], pein_cross$Seed_set,hedges.correction=TRUE)
   b <- rbind(b, a[3])
   x<- rbind(x, a[4])
 }
@@ -275,7 +275,7 @@ families<- sort(unique(brol_seeds$Family))
 b <- NULL
 x <- NULL
 for (i in families){
-  a<-cohen.d(brol_seeds$Seed_set[brol_seeds$Family==i], brol_cross$Seed_set)
[…]

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
   scale_fill_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
-  xlab("") + ylab("Cohen's d") + rotate()+
+  xlab("") + ylab("Hedges' g") + rotate()+
   geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')

### 2019-03-05 Effect_sizes_total.R

@@ -590,7 +590,7 @@ p1 + geom_point(show.legend = FALSE,aes(color=factor(Family_1))) +
                                        ymax = Upper, size=2,color=factor(Family_1)), width = 0.2)+
   scale_color_manual("Family",values=c( "#0072B2", "#009E73", "#D55E00"))+
   scale_fill_manual("Family",values=c( "#0072B2", "#009E73", "#D55E00"))+
-  xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
+  xlab("Treatments") + ylab("Hedges' g") + rotate()+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
 
 save.image("Manuscript_draft/effect_size_species/effect_size_total.RData")

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=3,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}
 

### 2019-03-05 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
   geom_errorbar(aes(x = Family, ymin = Lower, 
-ymax = Upper,colour=Family_1), width = 0.2, size=0.8)+
+ymax = Upper,colour=Family_1), width = 0.2, size=0.8, alpha=0.5)+
   scale_color_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
Edits

@@
 #SOME
-load("effect_size_species/some_effect_size.RData")
-p1<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+load("effect_size_species/all_effect_size.RData")
+
+#BROL
+load("effect_size_species/brol_effect_size.RData")
+p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = margin(t=0, l=0))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,0.5),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")
+
+#BRRA
+load("effect_size_species/brra_effect_size.RData")
+pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,0.5,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "B)")
+
+#ERSA
+load("effect_size_species/ersa_effect_size.RData")
+p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,0.5,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "C)")+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))
+
+#SIAL
+load("effect_size_species/sial_effect_size.RData")
+p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,0.5,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "D)")
+
+#IPAQ
+load("effect_size_species/ipaq_effect_size.RData")
+p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+geom_point(alpha=c(1,1,1,1,1,0.5,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "E)")
+
+#IPPU
+load("effect_size_species/ippu_effect_size.RData")
+p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
+  theme(axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,0.5,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "F)")
+
+#CAAN
+load("effect_size_species/caan_effect_size.RData")
+p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")
+
+#PEIN
+load("effect_size_species/pein_effect_size.RData")
+p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")
 
@@
 load("effect_size_species/soly_effect_size.RData")
-pp2<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
+p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,0.5,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "B)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "I)")
 
-#SIAL
-load("effect_size_species/sial_effect_size.RData")
-p3<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "C)")
+#SOME
+load("effect_size_species/some_effect_size.RData")
 
-#PEIN
-load("effect_size_species/pein_effect_size.RData")
-p4<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "D)")
-
-#IPPU
-load("effect_size_species/ippu_effect_size.RData")
-p5<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("Treatments") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "E)")
-
-#IPAQ
-load("effect_size_species/ipaq_effect_size.RData")
-p6<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "F)")
-
-#ERSA
-load("effect_size_species/ersa_effect_size.RData")
-p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")
-
-#CAAN
-load("effect_size_species/caan_effect_size.RData")
-p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")
-
-#BRRA
-load("effect_size_species/brra_effect_size.RData")
-p9<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "I)")
-
-#BROL
-load("effect_size_species/brol_effect_size.RData")
-p10<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#0072B2", "#009E73", "#E69F00", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "J)")
+p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,alpha=c(0.5,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "J)")
 

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")
@@
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "B)")
@@
 p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,0.5,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "I)")

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
changes

@@
   scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
@@
   scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**).
-The species of the study had different reproductive traits and different degree of relatedness where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
+The species of the study had different reproductive traits and different degree of relatedness (**Figure 1**) where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
 Moreover, the species selected had fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
@@
 \newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae."}
+knitr::include_graphics('images/phylo_image.png')
+```
+
+\newpage
+
 **Table 1**
@@
 
+\ref{Figure 1}
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae."}
-knitr::include_graphics('images/phylo_image.png')
-```
 

### 2019-03-06 Manuscript_draft/Manuscript_draft.tex
edits

@@
 Convolvulaceae (\textbf{Table 1}). The species of the study had
-different reproductive traits and different degree of relatedness where
-the reciprocal crosses between species allowed us to have multiple
-different scenarios of both traits and relatedness. Moreover, the
-species selected had fast life cycle and low structural flower
-complexity in order to perform the pollination treatments and grow the
-different species from seeds. For the purpose of the experiment all the
-species where considered as pollen recipient and as pollen donor (see
-interaction matrix, fig 2). Species were watered once or twice per day
-and fertilized weekly (NPK 23: 3.95: 14).
+different reproductive traits and different degree of relatedness
+(\textbf{Figure 1}) where the reciprocal crosses between species allowed
+us to have multiple different scenarios of both traits and relatedness.
+Moreover, the species selected had fast life cycle and low structural
+flower complexity in order to perform the pollination treatments and
+grow the different species from seeds. For the purpose of the experiment
+all the species where considered as pollen recipient and as pollen donor
+(see interaction matrix, fig 2). Species were watered once or twice per
+day and fertilized weekly (NPK 23: 3.95: 14).
 
 \newpage
-*
 
-*Table 1**
+\begin{figure}
+\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae.}\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\newpage
+
+\textbf{Table 1}
 
@@
 
-\newpage
-
-\begin{figure}
-\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae.}\label{fig:unnamed-chunk-2}
-\end{figure}
+\ref{Figure 1} \newpage
 

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
-\ref{Figure 1}
 \newpage
@@
 
-Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation.
-Therefore, 180 different combinations were performed with N=10 per combination.
+Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation.
+Therefore, we perfomed 180 different heterospecific treatments (N=10).
 Seed set was the proxy of effect for all our treatments.
-Moreover, hand cross pollination (between individuals of the same species), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
-For the treatments with foreign pollen and hand cross pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
+Moreover, hand cross-pollination (between individuals of the same species), hand self-pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
+For the treatments with foreign pollen and hand cross-pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
 Hand-pollination was conducted with 3-4 gentle touches on the stigma surface.

### 2019-03-06 Manuscript_draft/Manuscript_draft.tex
edits

@@
 
-\ref{Figure 1} \newpage
+\newpage
 
@@
 with 50\% conspecific pollen and 50\% heterospecific pollen and a second
-one with 100\% foreign pollen (N=10) in order to see if foreign pollen
-can trigger fruit production by itself or even seeds through ovule
-usurpation. Therefore, 180 different combinations were performed with
-N=10 per combination. Seed set was the proxy of effect for all our
-treatments. Moreover, hand cross pollination (between individuals of the
-same species), hand self pollination, apomixis (bagged emasculated
+one with 100\% foreign pollen in order to see if foreign pollen can
+trigger fruit production by itself or even seeds through ovule
+usurpation. Therefore, we perfomed 180 different heterospecific
+treatments (N=10). Seed set was the proxy of effect for all our
+treatments. Moreover, hand cross-pollination (between individuals of the
+same species), hand self-pollination, apomixis (bagged emasculated
 flowers) and natural selfing were tested for each species (N=10). For
-the treatments with foreign pollen and hand cross pollination, flowers
+the treatments with foreign pollen and hand cross-pollination, flowers
 were emasculated the day prior anthesis and hand pollinated next day

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.
-In order to confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix.
-Therefore, 20 different heterospecific crosses 50-50% were counted for all the focal species with crosses of just one species of the other two families (N=3).
+To confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix.
+Because pollen from the same family was difficult to distinguish, and we expected similar properties in mixing, we counted pollen from just one randomly selected species within each donor family different to the focal's family (N=3).
 

### 2019-03-06 Manuscript_draft/Manuscript_draft.tex
edits

@@
 average number of pollen grains per anther was known, the proportion of
-anthers per mix was calculated in order to achieve a 50-50\% mix. In
-order to confirm that the treatments applied were the desire
-proportions, the total stigmatic load of pollen was counted and the
-proportions calculated between the two species of the mix. Therefore, 20
-different heterospecific crosses 50-50\% were counted for all the focal
-species with crosses of just one species of the other two families
-(N=3).
+anthers per mix was calculated in order to achieve a 50-50\% mix. To
+confirm that the treatments applied were the desire proportions, the
+total stigmatic load of pollen was counted and the proportions
+calculated between the two species of the mix. Because pollen from the
+same family was difficult to distinguish, and we expected similar
+properties in mixing, we counted pollen from just one randomly selected
+species within each donor family different to the focal's family (N=3).
 

### 2019-03-06 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
-**Hand-pollination**
+**Hand pollination**
 
@@
 Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
-Fruits per number of flowers treated were counted for Solanaceae species and for the rest, the number of seeds produced per average number of ovules of each species.
-Levels of self incompatibility were estimated by dividing the fruit set of hand self pollination by hand cross pollination @lloyd1992.
+Fruits per number of flowers treated were counted for just Solanaceae species, we counted for all the species the number of seeds produced per average number of ovules.
+Levels of self-incompatibility were estimated by dividing the fruit set of hand self-pollination by hand cross pollination @lloyd1992.
 
@@
 In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances).
-Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross pollination minus seed production of the different heterospecific pollen treatments.
+Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
 To find a model with the best explanatory traits we used the function **bioenv** from R.
@@
 
-Results of hand cross-pollination, self hand-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values).
+Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values).
 Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
@@
 Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine.
-The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross pollination and one treatment with pollen from a confamilial- IB Unclear]().
+The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross-pollination and one treatment with pollen from a confamilial- IB Unclear]().
 Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment]().
@@
 The y axis is the proportion of ovules converted to seed in percentage.
-The different treatments (N=10) which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis.
+The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis.
 More information about these treatments can be found in Methods and Appendices."}
@@
 Perecentage of seeds produced per ovule for the ten species used in the experiment.
-The treatments presented are hand cross pollination, hand self pollination, natural selfing and apomixis (emasculated flowers).
+The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

### 2019-03-06 Manuscript_draft/Manuscript_draft.tex
edits

@@
 
-\textbf{Hand-pollination}
+\textbf{Hand pollination}
 
@@
 15 randomly selected flowers. Fruits per number of flowers treated were
-counted for Solanaceae species and for the rest, the number of seeds
-produced per average number of ovules of each species. Levels of self
-incompatibility were estimated by dividing the fruit set of hand self
-pollination by hand cross pollination Lloyd and Schoen (1992).
+counted for just Solanaceae species, we counted for all the species the
+number of seeds produced per average number of ovules. Levels of
+self-incompatibility were estimated by dividing the fruit set of hand
+self-pollination by hand cross pollination Lloyd and Schoen (1992).
 
@@
 effect was obtained through the subtraction of seed production by hand
-cross pollination minus seed production of the different heterospecific
+cross-pollination minus seed production of the different heterospecific
 pollen treatments. To find a model with the best explanatory traits we
@@
 
-Results of hand cross-pollination, self hand-pollination, natural
+Results of hand cross-pollination, hand self-pollination, natural
 selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
@@
 \href{}{and just for \emph{Sinapis alba} we did not find significant
-differences between the hand cross pollination and one treatment with
+differences between the hand cross-pollination and one treatment with
 pollen from a confamilial- IB Unclear}. Solanaceae species with berry
@@
 The y axis is the proportion of ovules converted to seed in percentage.
-The different treatments (N=10) which are presented in the legend are, hand cross pollination, hand self pollination, natural selfing and apomixis.
+The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis.
 More information about these treatments can be found in Methods and Appendices.}\label{fig:unnamed-chunk-3}
@@
 \textbf{Table S1}. Perecentage of seeds produced per ovule for the ten
-species used in the experiment. The treatments presented are hand cross
-pollination, hand self pollination, natural selfing and apomixis
+species used in the experiment. The treatments presented are hand
+cross-pollination, hand self-pollination, natural selfing and apomixis
 (emasculated flowers).

### 2019-03-08 Scripts/Analysis/Analysis_glm.R
Getting rid of outliers

@@ -79,6 +79,10 @@ z_caan <- (100-a_caan/b_caan*100)
 
 traits_all$si_index <- c(z_brol, z_brra, z_caan, z_ersa, z_ipaq, z_ippu, 
                          z_pein, z_sial, z_soly, z_some) 
+si_index <- c(z_brol, z_brra, z_caan, z_ersa, z_ipaq, z_ippu, 
+              z_pein, z_sial, z_soly, z_some) 
+
+saveRDS(si_index, "Data/si_index.RData")
 
 #colname to merge
 colnames(traits_all)[2] <- "Species"

### 2019-03-08 Scripts/Traits/all_traits.R

@@ -66,6 +66,8 @@ style <-morphometry[grep("style", morphometry$measurement),]
 style_length <-style[grep("length", style$measurement),] 
 #Style width
 style_width <-style[grep("width", style$measurement),] 
+boxplot(style_width$um)
+style_width[style_width$um>1500,]<- NA
 
 
 #Ovary
@@ -73,10 +75,13 @@ ovary <-morphometry[grep("ovary", morphometry$measurement),]
 
 #Ovary width
 ovary_width <-ovary[grep("width", ovary$measurement),] 
+ovary_width[ovary_width$um>2000,]<- NA
+boxplot(ovary_width$um)
+ovary_width[ovary_width$um>2000,]<- NA
 #Ovary width
 ovary_length <-ovary[grep("legth", ovary$measurement),] 
 ovary_length$measurement <- gsub('ovary _ legth', 'ovary _ length', ovary_length$measurement)
-
+boxplot(ovary_length$um)
 #Ok now all the traits are ready!! Lets add it to traits_all.
 #dir.create("Data/Morpho_RData")
 

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
Getting rid of outliers
edits

@@
 
+Mention that SI index is calculated (Schoen & Lloyd 1984)
+
 # RESULTS
@@
 Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values).
-Heterospecific pollen reduced seet set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Moreover, effect sizes differ across species, see **Figure 2** where species like *S.
-lycopersicum* had a large effect size and other's like *E.
-sativa* a small or null effect size.
+Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
+Moreover, average effect sizes differed across species and families, see **Figure 2**.
+Despite some variability in the effect of the different pollen donors per species, in general terms the effect per species was homogeneous (see **Figure 3**).
+When the donors were groped by family not big differences were seen, just for one species
 
-Across families we found a very similar effect but when species where look at species level they respond differently even within the same family [rephrase and maybe test statistically?](), for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did out of nine.
  The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross-pollination and one treatment with pollen from a confamilial- IB Unclear]().
@@
 load("effect_size_species/caan_effect_size.RData")
-p7<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
@@
 load("effect_size_species/pein_effect_size.RData")
-p8<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+

### 2019-03-09 Manuscript_draft/Manuscript_draft.tex
edits

@@
 
+Mention that SI index is calculated (Schoen \& Lloyd 1984)
+
 \section{RESULTS}\label{results}
@@
 selfing and apomixis are presented in \textbf{Figure 1} (see appendix 1
-for table with values). Heterospecific pollen reduced seet set
+for table with values). Heterospecific pollen reduced seed set
 significatively with the 50-50\% heterospecific pollen treatments for
-65\% of the pairwise interactions p\textless{}0.05. Moreover, effect
-sizes differ across species, see \textbf{Figure 2} where species like
-\emph{S. lycopersicum} had a large effect size and other's like \emph{E.
-sativa} a small or null effect size.
+65\% of the pairwise interactions p\textless{}0.05. Moreover, average
+effect sizes differed across species and families, see \textbf{Figure
+2}. Despite some variability in the effect of the different pollen
+donors per species, in general terms the effect per species was
+homogeneous (see \textbf{Figure 3}). When the donors were gropued by
+family not big differences were seen, just for one species
 
-Across families we found a very similar effect but when species where
-look at species level they respond differently even within the same
-family \href{}{rephrase and maybe test statistically?}, for instance for
-two species of the Brassicaceae family \emph{Brassica oleracea} and
-\emph{Eruca versicaria} we found very contrasting effects of foreign
-pollen where for the first one, all donors reduce seed set
-significatively and for the second, just two species did out of nine.
 The 100\% foreign pollen treatments barely produced seeds or fruits

### 2019-03-09 Analysis_traits.R

@@ -4,7 +4,9 @@ library(vegan)
 matrix_scale_effect <- readRDS("Data/matrix_scale_effect.Rda")
 
 traits_all <- read.csv("Data/traits_all.csv", sep=",")
-si_index <- readRDS("Data/si_index.RData")
+#si_index <- readRDS("Data/si_index.RData")
+si_index <- readRDS("Data/si_index_1.RData")
+
 traits_all$si_index <- si_index
 traits_all <- traits_all[,-c(1,2)]
 

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Moreover, average effect sizes differed across species and families, see **Figure 2**.
-Despite some variability in the effect of the different pollen donors per species, in general terms the effect per species was homogeneous (see **Figure 3**).
-When the donors were groped by family not big differences were seen, just for one species
+Moreover, average effect sizes differed across species and  within families, see **Figure 2**.
+Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments  per species was homogeneous (see **Figure 3**).
+When the donors were groped by family not big differences were seen, just for *S.
+lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap.
 

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
edits results

@@
 Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Moreover, average effect sizes differed across species and  within families, see **Figure 2**.
-Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments  per species was homogeneous (see **Figure 3**).
+Moreover, average effect sizes differed across species and across families, see **Figure 2**.
+Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just 4 species out of ten had only one donor with no overlap of the effect size confidence intervals.
+None of the donors had a clear stronger or weaker effect across species.
 When the donors were groped by family not big differences were seen, just for *S.

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 Moreover, average effect sizes differed across species and across families, see **Figure 2**.
-Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just 4 species out of ten had only one donor with no overlap of the effect size confidence intervals.
-None of the donors had a clear stronger or weaker effect across species.
+Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just for four species out of ten, just one donor did not overlap the confidence intervals with other donors.
+Therefore, none of the donors had a clear stronger or weaker effect across species.
 When the donors were groped by family not big differences were seen, just for *S.
 lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap.
+In addition,
+
+Now talk about the 100%, Make plot!!!!
 

### 2019-03-09 Manuscript_draft/Manuscript_draft.tex
edits

@@
 65\% of the pairwise interactions p\textless{}0.05. Moreover, average
-effect sizes differed across species and families, see \textbf{Figure
-2}. Despite some variability in the effect of the different pollen
-donors per species, in general terms the effect per species was
-homogeneous (see \textbf{Figure 3}). When the donors were gropued by
-family not big differences were seen, just for one species
+effect sizes differed across species and across families, see
+\textbf{Figure 2}. Despite some variability in the effect of the
+different pollen donors per species, in general terms the effect of
+heterospecific pollen from the distinct nine treatments per species was
+homogeneous (see \textbf{Figure 3}), just for four species out of ten,
+just one donor did not overlap the confidence intervals with other
+donors. Therefore, none of the donors had a clear stronger or weaker
+effect across species. When the donors were groped by family not big
+differences were seen, just for \emph{S. lycopersicum} the confidence
+intervals of Brassicaceae and Convolvulaceae did not overlap. In
+addition,
+
+Now talk about the 100\%, Make plot!!!!
 

### 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 When the donors were groped by family not big differences were seen, just for *S.
-lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap.
-In addition,
-
-Now talk about the 100%, Make plot!!!!
+lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**).
+In addition, for the 100% hetrospecific pollen treatment we did not find almost seed production.
+However, for just one species (*S.alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
 

### 2019-03-09 Manuscript_draft/Manuscript_draft.tex
edits

@@
 differences were seen, just for \emph{S. lycopersicum} the confidence
-intervals of Brassicaceae and Convolvulaceae did not overlap. In
-addition,
-
-Now talk about the 100\%, Make plot!!!!
+intervals of Brassicaceae and Convolvulaceae did not overlap (see
+\textbf{Figure 4}). In addition, for the 100\% hetrospecific pollen
+treatment we did not find almost seed production. However, for just one
+species (\emph{S.alba}) the control pollination and the heterospecific
+pollination with pollen from a confamilial had similar seed production.
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

--- 2019-03-09 Manuscript_draft/Manuscript_draft.Rmd
@@
 When the donors were groped by family not big differences were seen, just for *S.
-lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap.
-In addition,
-
-Now talk about the 100%, Make plot!!!!
-
- The 100% foreign pollen treatments barely produced seeds or fruits [and just for *Sinapis alba* we did not find significant differences between the hand cross-pollination and one treatment with pollen from a confamilial- IB Unclear]().
-Solanaceae species with berry fruit type developed small fruits or even normal fruits in some cases [under which treatment]().
-*S.
-lycopersicum* seems to produced small fruits (35% of the treatments) independently of pollen and pollen donor due to also apomictic treatments did, never normal size.
-*C.
-annuum* produced some fruits (9%) of both small and normal size and finally *S.
-melongena* produced seedless normal fruits with just confamilial pollen (3%), for both species seems that fruit formation was induced by pollen on the stigma because of lack of fruit production with treatments that tested for apomixis.[clarify this descriptive statistics part- Also a figure with a summary of the treatments effect would be cool, or at least in the appendices]()
+lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**).
+In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production.
+However, for just one species (*S.
+alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
+For both Solanaceae species *S.
+melongena* and *C.
+annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

--- 2019-03-09 Manuscript_draft/Manuscript_draft.tex
@@
 differences were seen, just for \emph{S. lycopersicum} the confidence
-intervals of Brassicaceae and Convolvulaceae did not overlap. In
-addition,
-
-Now talk about the 100\%, Make plot!!!!
-
-The 100\% foreign pollen treatments barely produced seeds or fruits
-\href{}{and just for \emph{Sinapis alba} we did not find significant
-differences between the hand cross-pollination and one treatment with
-pollen from a confamilial- IB Unclear}. Solanaceae species with berry
-fruit type developed small fruits or even normal fruits in some cases
-\href{}{under which treatment}. \emph{S. lycopersicum} seems to produced
-small fruits (35\% of the treatments) independently of pollen and pollen
-donor due to also apomictic treatments did, never normal size. \emph{C.
-annuum} produced some fruits (9\%) of both small and normal size and
-finally \emph{S. melongena} produced seedless normal fruits with just
-confamilial pollen (3\%), for both species seems that fruit formation
-was induced by pollen on the stigma because of lack of fruit production
-with treatments that tested for apomixis.\href{}{clarify this
-descriptive statistics part- Also a figure with a summary of the
-treatments effect would be cool, or at least in the appendices}
+intervals of Brassicaceae and Convolvulaceae did not overlap (see
+\textbf{Figure 4}). In addition, for the 100\% hetrospecific pollen
+treatments we did not find almost seed production. However, for just one
+species (\emph{S. alba}) the control pollination and the heterospecific
+pollination with pollen from a confamilial had similar seed production.
+For both Solanaceae species \emph{S. melongena} and \emph{C. annuum}
+100\% pollen treatments produced few seedles fruits (3\% and 9\%
+respectively) and they did not for the apomictic treatments.
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
-In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits (Euclidean distances).
+In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (Vegan package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
 Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
@@
 annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.
+
+Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a statistically clear correlation for both markers (p<0.05).
+The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

@@
 In order to test the relative effect of traits on seed production with
-foreign pollen we performed Mantel test between the assymetrical matrix
-of heterospecific pollen effect (10 by 10 matrix) with the different
-distance matrices of traits (Euclidean distances). Heterospecific pollen
-effect was obtained through the subtraction of seed production by hand
-cross-pollination minus seed production of the different heterospecific
-pollen treatments. To find a model with the best explanatory traits we
-used the function \textbf{bioenv} from R. We also conducted Mantel test
-between the matrix of heterospecific pollen effect and the distance
-matrix from all the traits. Moreover, we explored also the correlation
-between traits and heterospecific pollen effect through generalized
-mixed models where the response variable was heterospecific pollen
-effect and the explanatory variable the different traits. In addition,
-we tested the correlation between the total amount of pollen deposited
-on the stigma with heterospecific pollinations and the stigma size
-through Pearson's correlation.
+foreign pollen we performed Mantel test in R (Vegan package, Euclidean
+distance) between the assymetrical matrix of heterospecific pollen
+effect (10 by 10 matrix) with the different distance matrices of traits.
+Heterospecific pollen effect was obtained through the subtraction of
+seed production by hand cross-pollination minus seed production of the
+different heterospecific pollen treatments. To find a model with the
+best explanatory traits we used the function \textbf{bioenv} from R. We
+also conducted Mantel test between the matrix of heterospecific pollen
+effect and the distance matrix from all the traits. Moreover, we
+explored also the correlation between traits and heterospecific pollen
+effect through generalized mixed models where the response variable was
+heterospecific pollen effect and the explanatory variable the different
+traits. In addition, we tested the correlation between the total amount
+of pollen deposited on the stigma with heterospecific pollinations and
+the stigma size through Pearson's correlation.
 
@@
 respectively) and they did not for the apomictic treatments.
+
+Results of Mantel test between heterospecific pollen effect and
+phylogenetic distance gave a statistically clear correlation for both
+markers (p\textless{}0.05). The correlations with ITS and RBCL markers
+was respectively of 0.29 and 0.25.
 

### 2019-03-10 Scripts/Analysis/Analysis_mantel_test.R

@@ -262,6 +262,8 @@ mantel(matrix_scale_effect, evo_distance_its)
 #Based on Letten & Cornwell 2014
 evo_distance_its_square_root <- sqrt(evo_distance_its)
 mantel(matrix_scale_effect, evo_distance_its_square_root)
+mantel(matrix_scale_effect, evo_distance_its_square_root, permutations = 10000)
+
 #significance=0.028, r=0.2764
 p <- mantel.correlog(matrix_scale_effect, evo_distance_its_square_root) 
 plot(p)

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
-Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a statistically clear correlation for both markers (p<0.05).
+Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05).
 The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.
+
+add phylogenetic signal of traits...
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

@@
 Results of Mantel test between heterospecific pollen effect and
-phylogenetic distance gave a statistically clear correlation for both
-markers (p\textless{}0.05). The correlations with ITS and RBCL markers
-was respectively of 0.29 and 0.25.
+phylogenetic distance gave a positive statistically clear correlation
+for both markers (p\textless{}0.05). The correlations with ITS and RBCL
+markers was respectively of 0.29 and 0.25.
+
+add phylogenetic signal of traits\ldots{}
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
RESULTS

@@
 The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.
-
-add phylogenetic signal of traits...
+The phylogenetic signal of traits was significantly correlated with pollen size, stigma measurements and style length (p<0.05).
+Although with a lack of a significant correlation pagel's lambda values were also relatively high (>0.45) for incompatibility index, ovary length and levels of selfing.
+Moreover, Mantel test between heterospecific pollen effect and traits gave also a positive significant correlation with a  r value of 0.4.
+When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect (LOOK AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE OPPOSITE)
 

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
RESULTS

@@
 for both markers (p\textless{}0.05). The correlations with ITS and RBCL
-markers was respectively of 0.29 and 0.25.
-
-add phylogenetic signal of traits\ldots{}
+markers was respectively of 0.29 and 0.25. The phylogenetic signal of
+traits was significantly correlated with pollen size, stigma
+measurements and style length (p\textless{}0.05). Although with a lack
+of a significant correlation pagel's lambda values were also relatively
+high (\textgreater{}0.45) for incompatibility index, ovary length and
+levels of selfing. Moreover, Mantel test between heterospecific pollen
+effect and traits gave also a positive significant correlation with a r
+value of 0.4. When the effect was look trait by trait with Mantel test,
+stigma type and stigma measurements (length, width and area) gave a
+significant positive correlation with heterospecific pollen effect (LOOK
+AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE
+OPPOSITE)
 

### 2019-03-10 Scripts/Analysis/Analysis_mantel_test.R

@@ -299,6 +299,8 @@ apply(traits_all_scaled, 2, sd)
 #Now I apply Mantel
 traits_all_scaled_dist <- dist(traits_all_scaled)
 mantel(matrix_scale_effect, traits_all_scaled_dist)
+mantel(matrix_scale_effect, dist(traits_all))
+
 #significance=0.296, r=0.09
 protest(matrix_scale_effect, traits_all_scaled_dist)
 #significance=0.946, procustes correlation=0.5968

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 affiliation:
-- affil: US Environmental Protection Agency, Office of Research and Development, National
-    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
-    27 Tarzwell Drive  Narragansett, RI, 02882, USA
+- affil: University of New England (Australia)
   affilnum: 1
-- affil: Big Name University, Department of R, City, BN, 01020, USA
+- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
   affilnum: 2
-- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
+- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
   affilnum: 3

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits

@@
 \\*
-\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
-National Health and Environmental Effects Research Laboratory, Atlantic
-Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
+\textsuperscript{1}University of New England (Australia)\\*
 \\*
-\textsuperscript{2}Big Name University, Department of R, City, BN, 01020, USA\\*
+\textsuperscript{2}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
 \\*
-\textsuperscript{3}Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain\\*
+\textsuperscript{3}Department of Biological Sciences, University of Pittsburgh 4249 Fifth
+Avenue, Pittsburgh, Pennsylvania 15260-3929 USA\\*
 }

### 2019-03-10 Manuscript_draft/Manuscript_draft.Rmd
edits authors and affiliations

@@
 author:
-- affilnum: '1,2,3'
-  name: Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
+- name: Jose B. Lanuza
+  affilnum: 1
   email: barragansljose@gmail.com
+
+- name: Ignasi Bartomeus
+  affilnum: 2
+
+- name: Tia-Lynn Ashman  
+  affilnum: 3
+
+- name: Romina Rader
+  affilnum: 1
+
 affiliation:

### 2019-03-10 Manuscript_draft/Manuscript_draft.tex
edits authors and affiliations

@@
 \author{
-Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
+Jose B. Lanuza
+Ignasi Bartomeus
+Tia-Lynn Ashman
+Romina Rader
 }
@@
 \large
-Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader \textsuperscript{*} \textsuperscript{1,2,3} 
+Jose B. Lanuza \textsuperscript{*} \textsuperscript{1} 
+Ignasi Bartomeus \textsuperscript{2} 
+Tia-Lynn Ashman \textsuperscript{3} 
+Romina Rader \textsuperscript{1} 
 \end{center}

### 2019-03-11 Scripts/Analysis/Analysis_mantel_test.R
edits

@@ -165,6 +165,8 @@ diag(matrix_scale) <- diag(matrix_cross_scale)
 
 #Creating matrix of effect (mean cross spp x1-mean HP effect spp x1)
 matrix_scale_effect <- matrix_cross_scale-matrix_scale
+matrix_scale_reverted <- matrix_scale-matrix_cross_scale
+
 #We set our lower bound to 0
 #Maximum theoretical value is our cross, "no treatments could be greater than it"
 matrix_scale_effect[matrix_scale_effect<0]<- 0
@@ -271,6 +273,12 @@ protest(matrix_scale_effect, evo_distance_its_square_root)
 #significance=0.765, procustes corr=0.5259
 
 
+#load Effect sizes
+matrix_effect_size <- readRDS("Data/matrix_effect_size.RData")
+mantel(matrix_effect_size, sqrt(evo_distance_its))
+mantel(abs(matrix_effect_size), sqrt(evo_distance_rbcl))
+mantel(abs(matrix_scale_reverted), sqrt(evo_distance_rbcl))
+
 #
 ##
 ###
@@ -300,9 +308,14 @@ apply(traits_all_scaled, 2, sd)
 traits_all_scaled_dist <- dist(traits_all_scaled)
 mantel(matrix_scale_effect, traits_all_scaled_dist)
 mantel(matrix_scale_effect, dist(traits_all))
+mantel(matrix_effect_size, dist(traits_all))
+mantel(abs(matrix_effect_size), dist(traits_all))
+mantel(abs(matrix_scale_reverted), dist(traits_all))
 
 #significance=0.296, r=0.09
 protest(matrix_scale_effect, traits_all_scaled_dist)
+protest(matrix_effect_size,  dist(traits_all))
+
 #significance=0.946, procustes correlation=0.5968
 protest(matrix_scale_effect, traits_all_scaled)
 
@@ -336,6 +349,10 @@ traits_stigma_dist <- dist(traits_all_scaled_stigma, diag=T, upper=T)
 
 traits_si_index_dist <- dist(traits_all$si_index, diag=T, upper=T)
 mantel(matrix_scale_effect, traits_si_index_dist)
+mantel(matrix_effect_size, traits_si_index_dist)
+mantel(abs(matrix_effect_size), traits_si_index_dist)
+mantel(abs(matrix_scale_reverted), traits_si_index_dist)
+
 #significance=0.016, r=0.27
 protest(matrix_scale_effect, traits_si_index_dist)
[…]

### 2019-03-11 Scripts/Data_preparation/matrix_effect_size.R

@@ -1,0 +1,52 @@
+#Analysis mantel with effect sizes
+#I have to load first all the script of effect size of analysis to run this one
+
+soly_effect_size$Focal <- "SOLY"
+soly_effect_size<- soly_effect_size[-2,]
+
+some_effect_size$Focal <- "SOME"
+some_effect_size<- some_effect_size[-1,]
+
+pein_effect_size$Focal <- "PEIN"
+pein_effect_size<- pein_effect_size[-3,]
+
+caan_effect_size$Focal <- "CAAN"
+caan_effect_size<- caan_effect_size[-4,]
+
+brol_effect_size$Focal <- "BROL"
+brol_effect_size<- brol_effect_size[-10,]
+
+brra_effect_size$Focal <- "BRRA"
+brra_effect_size<- brra_effect_size[-9,]
+
+sial_effect_size$Focal <- "SIAL"
+sial_effect_size<- sial_effect_size[-7,]
+
+ersa_effect_size$Focal <- "ERSA"
+ersa_effect_size<- ersa_effect_size[-8,]
+
+ippu_effect_size$Focal <- "IPPU"
+ippu_effect_size<- ippu_effect_size[-5,]
+
+ipaq_effect_size$Focal <- "IPAQ"
+ipaq_effect_size<- ipaq_effect_size[-6,]
+
+e_size <- rbind(soly_effect_size,some_effect_size,pein_effect_size, caan_effect_size, brol_effect_size, brra_effect_size,
+      sial_effect_size, ersa_effect_size, ippu_effect_size, ipaq_effect_size)
+
+e_size <- e_size[,-c(2,3,5,6)]
+str(e_size)
+e_size$Species<- as.character(e_size$Species)
+
+
+e_size$Species <- gsub("50%", "", e_size$Species)
+e_size$le <- seq(1:90)
+e_size[22,1] <- e_size[4,1]
+e_size <- e_size[,-4]
+matrix_effect_size <- tapply(e_size$Cohen_d, e_size[c("Focal", "Species")], mean)
+matrix_effect_size <- matrix_effect_size[order(rownames(matrix_effect_size)), order(colnames(matrix_effect_size))] 
+diag(matrix_effect_size) <- 0
+matrix_effect_size[8,5]<- matrix_effect_size[8,6]
+matrix_effect_size[10,5]<- matrix_effect_size[10,6]
+
+saveRDS(matrix_effect_size, "Data/matrix_effect_size.RData")

### 2019-03-11 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae"}
 knitr::include_graphics('images/phylo_image.png')
@@
 alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
-For both Solanaceae species *S.
+For two Solanaceae species *S.
 melongena* and *C.
@@
 The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.
-The phylogenetic signal of traits was significantly correlated with pollen size, stigma measurements and style length (p<0.05).
+We found a significant phylogenetic signal of traits for pollen size, stigma measurements and style length (p<0.05).
 Although with a lack of a significant correlation pagel's lambda values were also relatively high (>0.45) for incompatibility index, ovary length and levels of selfing.
 Moreover, Mantel test between heterospecific pollen effect and traits gave also a positive significant correlation with a  r value of 0.4.
-When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect (LOOK AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE OPPOSITE)
+When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect.
 

### 2019-03-11 Scripts/Analysis/Analysis_glm.R

@@ -1,4 +1,9 @@
 #In this script I'm going to perform GLM between Hp effect and the traits
+library(vegan)
+library(lme4)
+library(nlme)
+library(cowplot)
+library(ggplot2)
 
 #load data
 matrix_scale_effect <- readRDS("Manuscript_draft/Data/matrix_scale_effect.Rda")
@@ -82,8 +87,8 @@ traits_all$si_index <- c(z_brol, z_brra, z_caan, z_ersa, z_ipaq, z_ippu,
 si_index <- c(z_brol, z_brra, z_caan, z_ersa, z_ipaq, z_ippu, 
               z_pein, z_sial, z_soly, z_some) 
 
-saveRDS(si_index, "Data/si_index.RData")
-saveRDS(si_index, "Data/si_index_1.RData")
+#saveRDS(si_index, "Data/si_index.RData")
+#saveRDS(si_index, "Data/si_index_1.RData")
 
 #colname to merge
 colnames(traits_all)[2] <- "Species"
@@ -106,147 +111,13 @@ traits_all$compatibility=as.numeric(traits_all$compatibility)
 hp_mean_sp <- dcast(Species ~ ., value.var = "value", fun.aggregate = mean, data = effect, na.rm= TRUE)
 colnames(hp_mean_sp) <- c("Species","hp_effect")
 
-
 data <- merge(hp_mean_sp, traits_all, by="Species")
 data <- data[,-c(3)]
-
-model1=lm(hp_effect~si_index, data=data)
-summary(model1)
-
-model1=lm(hp_effect~Selfing_rate, data=data)
-summary(model1)
-
-model1=lm(hp_effect~pollen_size, data=data)
-summary(model1)
-
-model1=lm(hp_effect~mean_pollen_anther, data=data)
-summary(model1)
-
-model1=lm(hp_effect~mean_ovules, data=data)
-summary(model1)
-
-model1=lm(hp_effect~pollen_ovule_ratio, data=data)
-summary(model1)
-
-model1=lm(hp_effect~stigma_area, data=data)
-summary(model1)
-
-model1=lm(hp_effect~stigma_length, data=data)
-summary(model1)
-
-model1=lm(hp_effect~stigma_surface, data=data)
-summary(model1)
-
-model1=lm(hp_effect~stigma_width, data=data)
-summary(model1)
-
-model1=lm(hp_effect~style_length, data=data)
-summary(model1)
-
-model1=lm(hp_effect~style_width, data=data)
[…]

### 2019-03-11 Manuscript_draft/Manuscript_draft.tex
edits

@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from bottom to top: Solanaceae, Convolvulaceae and Brassicaceae.}\label{fig:unnamed-chunk-1}
+\includegraphics[width=1\linewidth]{images/phylo_image} \caption{Phylogenetic tree of the ten species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae}\label{fig:unnamed-chunk-1}
 \end{figure}
@@
 pollination with pollen from a confamilial had similar seed production.
-For both Solanaceae species \emph{S. melongena} and \emph{C. annuum}
+For two Solanaceae species \emph{S. melongena} and \emph{C. annuum}
 100\% pollen treatments produced few seedles fruits (3\% and 9\%
@@
 for both markers (p\textless{}0.05). The correlations with ITS and RBCL
-markers was respectively of 0.29 and 0.25. The phylogenetic signal of
-traits was significantly correlated with pollen size, stigma
-measurements and style length (p\textless{}0.05). Although with a lack
-of a significant correlation pagel's lambda values were also relatively
-high (\textgreater{}0.45) for incompatibility index, ovary length and
-levels of selfing. Moreover, Mantel test between heterospecific pollen
-effect and traits gave also a positive significant correlation with a r
-value of 0.4. When the effect was look trait by trait with Mantel test,
-stigma type and stigma measurements (length, width and area) gave a
-significant positive correlation with heterospecific pollen effect (LOOK
-AT HOW I EXPRESS THIS IS VERY RELEVANT, HP EFFECT FOR ME IS THE
-OPPOSITE)
+markers was respectively of 0.29 and 0.25. We found a significant
+phylogenetic signal of traits for pollen size, stigma measurements and
+style length (p\textless{}0.05). Although with a lack of a significant
+correlation pagel's lambda values were also relatively high
+(\textgreater{}0.45) for incompatibility index, ovary length and levels
+of selfing. Moreover, Mantel test between heterospecific pollen effect
+and traits gave also a positive significant correlation with a r value
+of 0.4. When the effect was look trait by trait with Mantel test, stigma
+type and stigma measurements (length, width and area) gave a significant
+positive correlation with heterospecific pollen effect.
 

### 2019-03-11 Effect_sizes_total.R

@@ -1,13 +1,13 @@
 #In this script I'm going to calculate the effect sizes and plot them.
 #Moreover I will compare differences among species and among families
-dev.off()
-dev.off() 
+
 #loadlibrary
-#install.packages("effsize")
+#i#install.packages("effsize")
 library(effsize)
 library(dplyr)
 library(ggplot2)
 library(ggpubr)
+#install.packages("effsize")
 
 load("seed_set&scaled_seed_set.RData")
 
@@ -578,7 +578,7 @@ all_convolvulaceae <- all_convolvulaceae %>% arrange(desc(Family))
 all_brassicaceae <- all_brassicaceae %>% arrange(desc(Family))
 
 all<- rbind(all_solanaceae,all_convolvulaceae, all_brassicaceae)
-
+saveRDS(all, "Data/effect_size_all.RData")
 all$Family_1 <- "S"
 all$Family_1[1:4]<- "B" 
 all$Family_1[5:6]<- "C"
@@ -593,6 +593,55 @@ p1 + geom_point(show.legend = FALSE,aes(color=factor(Family_1))) +
   xlab("Treatments") + ylab("Hedges' g") + rotate()+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
 
-save.image("Manuscript_draft/effect_size_species/effect_size_total.RData")
+#save.image("Manuscript_draft/effect_size_species/effect_size_total.RData")
+traits_all <- read.csv("Data/traits_all.csv", sep=",")
+traits_all$species <- c("BROL", "BRRA", "CAAN", "ERSA", "IPAQ", "IPPU", 
+                        "PEIN", "SIAL", "SOLY", "SOME") 
+colnames(traits_all)[2] <- "Species"
+traits_all=traits_all[,-1]
+all$Family <- c("SOME", "SOLY", "PEIN", "CAAN", "IPPU", "IPAQ", "SIAL","ERSA", "BRRA", "BROL")
+colnames(all)[1] <- "Species"
+all <- all[order(all$Species),]
+all_t <-merge(all, traits_all, by="Species")
+si_index <- readRDS("Data/si_index.RData")
+str(all_t)
+all_t$si_index <- si_index
+all_t$stigma_type <- as.character(all_t$stigma_type)
+p1<- ggplot(all_t, aes(Species,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))
[…]

### 2019-03-11 Scripts/Analysis/phylosignal.R
edits

@@ -1,0 +1,24 @@
+#Phylosignal package
+#devtools::install_github("fkeck/phylosignal")
+
+library(ape)
+library(phylosignal)
+library(adephylo)
+library(phylobase)
+library(phylosignal)
+library(caret)
+library(ggplot2)
+library(seqHMM)
+data(carni19)
+
+
+tre <- read.tree(text=carni19$tre)
+dat <- list()
+dat$mass <- carni19$bm
+dat$random <- rnorm(19, sd = 10)
+dat$bm <- rTraitCont(tre)
+dat <- as.data.frame(dat)
+p4d <- phylo4d(tre, dat)
+barplot.phylo4d(p4d, tree.type = "phylo", tree.ladderize = TRUE)
+phyloSignal(p4d = p4d, method = "all")
+

### 2019-03-12 Manuscript_draft/Manuscript_draft.Rmd
edits
trying to do the phylo signal of hp effect

@@
 
-Maybe for this plot I have to do hedges'g instead of cohean because of different sample sizes when I group the treatments per family. Check
-
 \newpage
@@
 
-Discussion
+Although we have found a positive correlation between phylogenetic distance and heterospecific pollen effect, this results have to be treated carefully.
+From our results we want to highlight that also far related species can affect negatively fitness but the effect from close related is species can also have important detrimental effects.
+Moreover, the effect of close related species can be masked by the possibility of hibridization as it occure between two of our species of Brassica.
+Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors.
+These different traits will define how it will be the effect across the different species independently of the nature of the donor.
+Although traditionally the nature of the pollen donor have been very studied, the recipient...
 

### 2019-03-12 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=5, fig.cap="The effect of heterospecific pollen (scaled see set) is represented in function of the compatibility system (self/cross*100) for the the different species.
-Each coulored dot represents the interaction of a focal species with a different pollen donor."}
-load("myEnv.RData")
-library(nlme)
-library(lme4)
-library(ggplot2)
-library(cowplot)
-model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv) #I don't get the random here. I think you need a better analysis.
-ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
-  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
-  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(model2))))+theme_cowplot()
-
-```
-
-[Compatibility index don´t multiply per 100 from Lloyd](Jose)
-
-\newpage
 

### 2019-03-12 Manuscript_draft/Manuscript_draft.tex
edits

@@
 
-Maybe for this plot I have to do hedges'g instead of cohean because of
-different sample sizes when I group the treatments per family. Check
-
 \newpage
@@
 
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
-\caption{The effect of heterospecific pollen (scaled see set) is
-represented in function of the compatibility system (self/cross*100) for
-the the different species. Each coulored dot represents the interaction
-of a focal species with a different pollen donor.}
-\end{figure}
-
-\href{Jose}{Compatibility index don´t multiply per 100 from Lloyd}
-
-\newpage
-
 \section{DISCUSSION}\label{discussion}
 
-Discussion
+Although we have found a positive correlation between phylogenetic
+distance and heterospecific pollen effect, this results have to be
+treated carefully. From our results we want to highlight that also far
+related species can affect negatively fitness but the effect from close
+related is species can also have important detrimental effects.
+Moreover, the effect of close related species can be masked by the
+possibility of hibridization as it occure between two of our species of
+Brassica. Moreover, although different effect between distinct donors
+can occur we want to note the importance on the traits of the recipient
+that determine an homogeneous effect between donors. These different
+traits will define how it will be the effect across the different
+species independently of the nature of the donor. Although traditionally
+the nature of the pollen donor have been very studied, the
+recipient\ldots{}
 
@@
 
-\includegraphics{output/figures/unnamed-chunk-9-1.pdf}
-\includegraphics{output/figures/unnamed-chunk-9-2.pdf}
-\includegraphics{output/figures/unnamed-chunk-9-3.pdf}
+\includegraphics{output/figures/unnamed-chunk-8-1.pdf}
+\includegraphics{output/figures/unnamed-chunk-8-2.pdf}
+\includegraphics{output/figures/unnamed-chunk-8-3.pdf}
 

### 2019-03-12 Manuscript_draft/Manuscript_draft.Rmd
...

@@
 
+Open with the main results...
+
 Although we have found a positive correlation between phylogenetic distance and heterospecific pollen effect, this results have to be treated carefully.
@@
 Moreover, the effect of close related species can be masked by the possibility of hibridization as it occure between two of our species of Brassica.
-Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors.
-These different traits will define how it will be the effect across the different species independently of the nature of the donor.
+Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors as we have shown in figure xxx.
+These different traits will define how it will be the effect across the different species independently of the nature of the donor and also differently even between species of .
 Although traditionally the nature of the pollen donor have been very studied, the recipient...
@@
  What are the implications of the findings?
-
-Ideas about pollen size in heterospecific pollen effect. (still have to develop it more...)
-
-Let's classify pollen size in three groups in order to understand the interaction between pollen donor and recipient:
-1) Donor pollen size < Recipient pollen size
-2) Donor pollen size = Recipient pollen size
-3) Donor pollen size > Recipient pollen size
-
-Now I try to develop each part
-
-1) Donor pollen size < Recipient pollen size
-
-Effect:
-
-- Donor's pollen could clogg the stigma
-
-- Chemical inhibition
-
-Traits associated with bigger pollen of the recipient:
-
-- Recipient's pollen have faster pollen tube growth (example with my data)
-
-- Reduction in number of ovules (Also with my species)
-
-- Big differences in pollen size can be traduced in low relatednes therefore less likely of pollen germination on a far related stigma.
-
-2) Donor pollen size = Recipient pollen size
-
-- Very relatedness dependant this point
-
-- Similar probabilities of taken space on the stigma
-
-3) Donor pollen size > Recipient pollen size
-
-Effect:
-
--In small stigmas big pollen grains can occupy great part of the stigmatic area.
-
--small pollen grains can get embeded
-
-IB: Think also on using tree analysis to test if hp effect depends on complex trait combinations.
-Tree analysis are great when two different strategies lead to the same outcome.
-This would never been pick up by GLMs.
-The r package is party{} .
-You can see an example applied to birds is Sol et al 2010 Science.
-Ask me if you want more details or code examples.
 

### 2019-03-12 Scripts/Analysis/Analysis_glm.R

@@ -98,12 +98,12 @@ traits_all$compatibility[traits_all$Species=="BROL"] <- 0
 traits_all$compatibility[traits_all$Species=="BRRA"] <- 0
 traits_all$compatibility[traits_all$Species=="SIAL"] <- 100
 traits_all$compatibility[traits_all$Species=="ERSA"] <- 2
-traits_all$compatibility[traits_all$Focal=="CAAN"] <- 64
-traits_all$compatibility[traits_all$Focal=="SOLY"] <- 48
-traits_all$compatibility[traits_all$Focal=="SOME"] <- 100
-traits_all$compatibility[traits_all$Focal=="PEIN"] <- 26
-traits_all$compatibility[traits_all$Focal=="IPAQ"] <- 75
-traits_all$compatibility[traits_all$Focal=="IPPU"] <- 100
+traits_all$compatibility[traits_all$Species=="CAAN"] <- 64
+traits_all$compatibility[traits_all$Species=="SOLY"] <- 48
+traits_all$compatibility[traits_all$Species=="SOME"] <- 100
+traits_all$compatibility[traits_all$Species=="PEIN"] <- 26
+traits_all$compatibility[traits_all$Species=="IPAQ"] <- 75
+traits_all$compatibility[traits_all$Species=="IPPU"] <- 100
 
 traits_all$compatibility=as.numeric(traits_all$compatibility)
 

### 2019-03-12 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect.
-With that said, @arceo2016 is the only work which has proven a greater effect of close related species through a meta-analysis but with low sample sizes and lack of significance.
+With that said, @arceo2016 is the only work until our knowledge which has proven a greater effect of close related species through a meta-analysis but with low sample sizes and lack of significance.
 Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.
@@
 Moreover, the great diversity of floral structures and small sizes of some of them such as Asteraceae species make tedious or almost impossible the studies of heterospecific pollen on the field.
-For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with different traits.
+For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with heterogeneous reproductive traits.
 Our study tries to answer the following questions: (i) Do heterospecific pollen reduce seed set?
@@
 Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences.
-The experimental design had species from three different families: Solanaceae, Brassicaceae and Convolvulaceae (**Table 1**).
-The species of the study had different reproductive traits and different degree of relatedness (**Figure 1**) where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
+The experimental design had species from three different families: Brassicaceae, Convolvulaceae and Solanaceae (**Table 1**).
+The species of the study had different reproductive traits and different degree of relatedness (see phylogenetic tree, **Figure 1**) where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
 Moreover, the species selected had fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
 For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).
-Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14).
+Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14) and the rooms of the glasshouse were temperature controlled with temperature oscillations between day and night.
 
@@
 
-**Table 1**
+**Table 1** Species list with family and genus.
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
@@
 
-The traits measured for each species were pollen per anther, number of ovules and stigma, style, ovary width and length.
-For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type.
-All the morphometrical measurements were performed with a stereophotomicroscope.
+The traits measured for each species were pollen per anther, pollen size, number of ovules and stigma, style, ovary width and length.
+For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type with the help of the stereomicroscope.
+All the morphometrical measurements were performed with a stereophotomicroscope with the exception of pollen size that was carried out with a light microscope.
 Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer.
@@
 Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
-Fruits per number of flowers treated were counted for just Solanaceae species, we counted for all the species the number of seeds produced per average number of ovules.
+Fruits per number of flowers treated were counted for just Solanaceae species with fleshy fruit.
+For all the species we counted the number of seeds produced per average number of ovules.
 Levels of self-incompatibility were estimated by dividing the fruit set of hand self-pollination by hand cross pollination @lloyd1992.

### 2019-03-12 Manuscript_draft/Manuscript_draft.tex
edits

@@
 pollen competition can occur and therefore could be a proxy of effect.
-With that said, Arceo-Gómez and Ashman (2016) is the only work which has
-proven a greater effect of close related species through a meta-analysis
-but with low sample sizes and lack of significance. Therefore, there is
-a need to study the effect of heterospecific pollen of far and close
-related species at community level beyond single pairwise interactions.
+With that said, Arceo-Gómez and Ashman (2016) is the only work until our
+knowledge which has proven a greater effect of close related species
+through a meta-analysis but with low sample sizes and lack of
+significance. Therefore, there is a need to study the effect of
+heterospecific pollen of far and close related species at community
+level beyond single pairwise interactions.
 
@@
 artificial co-flowering community in a glasshouse with 10 species
-belonging to three different families with different traits. Our study
-tries to answer the following questions: (i) Do heterospecific pollen
-reduce seed set? To what extent do (ii) floral reproductive traits and
-(iii) relatedness, mediate the impacts of heterospecific pollen on seed
-set.
+belonging to three different families with heterogeneous reproductive
+traits. Our study tries to answer the following questions: (i) Do
+heterospecific pollen reduce seed set? To what extent do (ii) floral
+reproductive traits and (iii) relatedness, mediate the impacts of
+heterospecific pollen on seed set.
 
@@
 day and night temperature differences. The experimental design had
-species from three different families: Solanaceae, Brassicaceae and
-Convolvulaceae (\textbf{Table 1}). The species of the study had
-different reproductive traits and different degree of relatedness
-(\textbf{Figure 1}) where the reciprocal crosses between species allowed
-us to have multiple different scenarios of both traits and relatedness.
-Moreover, the species selected had fast life cycle and low structural
-flower complexity in order to perform the pollination treatments and
-grow the different species from seeds. For the purpose of the experiment
-all the species where considered as pollen recipient and as pollen donor
-(see interaction matrix, fig 2). Species were watered once or twice per
-day and fertilized weekly (NPK 23: 3.95: 14).
+species from three different families: Brassicaceae, Convolvulaceae and
+Solanaceae (\textbf{Table 1}). The species of the study had different
+reproductive traits and different degree of relatedness (see
+phylogenetic tree, \textbf{Figure 1}) where the reciprocal crosses
+between species allowed us to have multiple different scenarios of both
+traits and relatedness. Moreover, the species selected had fast life
+cycle and low structural flower complexity in order to perform the
+pollination treatments and grow the different species from seeds. For
+the purpose of the experiment all the species where considered as pollen
+recipient and as pollen donor (see interaction matrix, fig 2). Species
+were watered once or twice per day and fertilized weekly (NPK 23: 3.95:
+14) and the rooms of the glasshouse were temperature controlled with
+temperature oscillations between day and night.
 
@@
 
-\textbf{Table 1}
+\textbf{Table 1} Species list with family and genus.
 
@@
 
-The traits measured for each species were pollen per anther, number of
-ovules and stigma, style, ovary width and length. For the stigma, the
-stigmatic area was also measured and moreover the stigmas were divided
-in wet/dry type. All the morphometrical measurements were performed with
-a stereophotomicroscope. Pollen was counted for 20 anthers of each
-species with 4 replicates per sample with an hemocytometer. Previously,
-anthers were squashed on a known solution with the pippete tip and
-homogeneize with a vortex for 30 seconds. Ovule number was counted with
-the help of a stereomicroscope and a small grid over a petri dish from
-15 randomly selected flowers. Fruits per number of flowers treated were
-counted for just Solanaceae species, we counted for all the species the
-number of seeds produced per average number of ovules. Levels of
-self-incompatibility were estimated by dividing the fruit set of hand
-self-pollination by hand cross pollination Lloyd and Schoen (1992).
+The traits measured for each species were pollen per anther, pollen
+size, number of ovules and stigma, style, ovary width and length. For
+the stigma, the stigmatic area was also measured and moreover the
+stigmas were divided in wet/dry type with the help of the
+stereomicroscope. All the morphometrical measurements were performed
+with a stereophotomicroscope with the exception of pollen size that was
+carried out with a light microscope. Pollen was counted for 20 anthers
+of each species with 4 replicates per sample with an hemocytometer.
+Previously, anthers were squashed on a known solution with the pippete
+tip and homogeneize with a vortex for 30 seconds. Ovule number was
+counted with the help of a stereomicroscope and a small grid over a
+petri dish from 15 randomly selected flowers. Fruits per number of
+flowers treated were counted for just Solanaceae species with fleshy
+fruit. For all the species we counted the number of seeds produced per
+average number of ovules. Levels of self-incompatibility were estimated
+by dividing the fruit set of hand self-pollination by hand cross
+pollination Lloyd and Schoen (1992).
 
@@
 
+Open with the main results\ldots{}
+
 Although we have found a positive correlation between phylogenetic
@@
 can occur we want to note the importance on the traits of the recipient
-that determine an homogeneous effect between donors. These different
-traits will define how it will be the effect across the different
-species independently of the nature of the donor. Although traditionally
+that determine an homogeneous effect between donors as we have shown in
+figure xxx. These different traits will define how it will be the effect
+across the different species independently of the nature of the donor
+and also differently even between species of . Although traditionally
 the nature of the pollen donor have been very studied, the
@@
 What are the implications of the findings?
-
-Ideas about pollen size in heterospecific pollen effect. (still have to
-develop it more\ldots{})
-
-Let's classify pollen size in three groups in order to understand the
-interaction between pollen donor and recipient: 1) Donor pollen size
-\textless{} Recipient pollen size 2) Donor pollen size = Recipient
-pollen size 3) Donor pollen size \textgreater{} Recipient pollen size
-
-Now I try to develop each part
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\tightlist
-\item
-  Donor pollen size \textless{} Recipient pollen size
-\end{enumerate}
-
-Effect:
-
-\begin{itemize}
-\item
-  Donor's pollen could clogg the stigma
-\item
-  Chemical inhibition
-\end{itemize}
-
-Traits associated with bigger pollen of the recipient:
-
-\begin{itemize}
-\item
-  Recipient's pollen have faster pollen tube growth (example with my
-  data)
-\item
-  Reduction in number of ovules (Also with my species)
-\item
-  Big differences in pollen size can be traduced in low relatednes
-  therefore less likely of pollen germination on a far related stigma.
-\end{itemize}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Donor pollen size = Recipient pollen size
-\end{enumerate}
-
-\begin{itemize}
-\item
-  Very relatedness dependant this point
-\item
-  Similar probabilities of taken space on the stigma
-\end{itemize}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Donor pollen size \textgreater{} Recipient pollen size
-\end{enumerate}
-
-Effect:
-
--In small stigmas big pollen grains can occupy great part of the
-stigmatic area.
-
--small pollen grains can get embeded
-
-IB: Think also on using tree analysis to test if hp effect depends on
-complex trait combinations. Tree analysis are great when two different
-strategies lead to the same outcome. This would never been pick up by
-GLMs. The r package is party\{\} . You can see an example applied to
-birds is Sol et al 2010 Science. Ask me if you want more details or code
-examples.
 

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
progressing with the draft. Analysis.

@@
 All the analysis were conducted with the statistical language `R` `r citep(citation())`.
+
+To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD].
+We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.
 

### 2019-03-13 Manuscript_draft/Manuscript_draft.tex
progressing with the draft. Analysis.

@@
 
+To compare the magnitude of effect of heterospecific pollen across
+species we conducted standarized Hedges' d {[}(mean of mixed 50\% mix -
+mean of cross pollination)/pooled SD{]}. We did in three different ways:
+effect sizes of each donor per focal species; effect sizes per family of
+the different donors per focal species; effect sizes of all the donors
+grouped per focal species.
+
 In order to test the relative effect of traits on seed production with

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 For all the species we counted the number of seeds produced per average number of ovules.
-Levels of self-incompatibility were estimated by dividing the fruit set of hand self-pollination by hand cross pollination @lloyd1992.
+Levels of self-incompatibility were estimated by dividing the seed set of hand self-pollination by hand cross-pollination @lloyd1992.
 
@@
 
-To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD].
+To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD] with **effsize** package.
 We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.
-
-In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (Vegan package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
-Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
-To find a model with the best explanatory traits we used the function **bioenv** from R.
-We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
-Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.
-In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.
 
@@
 
+In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (**vegan** package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
+Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
+To find a model with the best explanatory traits we used the function **bioenv** from R.
+We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
+Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.
+In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.
+
 [Phylogenetic signal of traits?](Jose)
-
-[Add pollen on stigma counts to methods](Jose)
-
-[Next bit to results, also divided it with ]
 
@@
 Add also plot with fruit production and pot it in appendix.Also the plots of ratios to appendices.
-
-Add effect sizes to analysis!!
-
-Mention that SI index is calculated (Schoen & Lloyd 1984)
 

### 2019-03-13 Manuscript_draft/Manuscript_draft.tex
edits

@@
 average number of ovules. Levels of self-incompatibility were estimated
-by dividing the fruit set of hand self-pollination by hand cross
-pollination Lloyd and Schoen (1992).
+by dividing the seed set of hand self-pollination by hand
+cross-pollination Lloyd and Schoen (1992).
 
@@
 species we conducted standarized Hedges' d {[}(mean of mixed 50\% mix -
-mean of cross pollination)/pooled SD{]}. We did in three different ways:
-effect sizes of each donor per focal species; effect sizes per family of
-the different donors per focal species; effect sizes of all the donors
-grouped per focal species.
-
-In order to test the relative effect of traits on seed production with
-foreign pollen we performed Mantel test in R (Vegan package, Euclidean
-distance) between the assymetrical matrix of heterospecific pollen
-effect (10 by 10 matrix) with the different distance matrices of traits.
-Heterospecific pollen effect was obtained through the subtraction of
-seed production by hand cross-pollination minus seed production of the
-different heterospecific pollen treatments. To find a model with the
-best explanatory traits we used the function \textbf{bioenv} from R. We
-also conducted Mantel test between the matrix of heterospecific pollen
-effect and the distance matrix from all the traits. Moreover, we
-explored also the correlation between traits and heterospecific pollen
-effect through generalized mixed models where the response variable was
-heterospecific pollen effect and the explanatory variable the different
-traits. In addition, we tested the correlation between the total amount
-of pollen deposited on the stigma with heterospecific pollinations and
-the stigma size through Pearson's correlation.
+mean of cross pollination)/pooled SD{]} with \textbf{effsize} package.
+We did in three different ways: effect sizes of each donor per focal
+species; effect sizes per family of the different donors per focal
+species; effect sizes of all the donors grouped per focal species.
 
@@
 
+In order to test the relative effect of traits on seed production with
+foreign pollen we performed Mantel test in R (\textbf{vegan} package,
+Euclidean distance) between the assymetrical matrix of heterospecific
+pollen effect (10 by 10 matrix) with the different distance matrices of
+traits. Heterospecific pollen effect was obtained through the
+subtraction of seed production by hand cross-pollination minus seed
+production of the different heterospecific pollen treatments. To find a
+model with the best explanatory traits we used the function
+\textbf{bioenv} from R. We also conducted Mantel test between the matrix
+of heterospecific pollen effect and the distance matrix from all the
+traits. Moreover, we explored also the correlation between traits and
+heterospecific pollen effect through generalized mixed models where the
+response variable was heterospecific pollen effect and the explanatory
+variable the different traits. In addition, we tested the correlation
+between the total amount of pollen deposited on the stigma with
+heterospecific pollinations and the stigma size through Pearson's
+correlation.
+
 \href{Jose}{Phylogenetic signal of traits?}
-
-\href{Jose}{Add pollen on stigma counts to methods}
-
-{[}Next bit to results, also divided it with {]}
 
@@
 plots of ratios to appendices.
-
-Add effect sizes to analysis!!
-
-Mention that SI index is calculated (Schoen \& Lloyd 1984)
 

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
adding effect size of phylo to draft

@@
 
-Add also plot with fruit production and pot it in appendix.Also the plots of ratios to appendices.
+Also the plots of ratios to appendices.
+
+NMDS to appendix?
 
@@
 When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect.
+
+[add table with morphometrical traits to appendix]()
 
@@
 
+```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.cap="Phylogenetic signal of the average heterospecific pollen effect size per species"}
+library(ape)
+library(phylosignal)
+library(adephylo)
+library(phylobase)
+library(phylosignal)
+library(caret)
+library(ggplot2)
+library(seqHMM)
+library(dplyr)
+library(reshape2)
+pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
+effect_size_all <- readRDS( "Data/effect_size_all.RData")
+#Now rename species
+rownames(effect_size_all) <- c("Solanum_melongena","Solanum_lycopersicum","Petunia_integrifolia", "Capsicum_annuum","Ipomoea_purpurea","Ipomoea_aquatica","Sinapis_alba","Eruca_vesicaria","Brassica_rapa", "Brassica_oleracea")
+hp_mean_sp=effect_size_all[,-c(1,3,4)]
+p4d <- phylo4d(pollen_tree, hp_mean_sp)
+barplot.phylo4d(p4d, center = TRUE , scale = FALSE,trait.labels="Hp effect",bar.col = c(rep("#0072B2",4), rep("#009E73",2), rep("#D55E00",4)))
+```
+
+\newpage
+
 Mantel test indicates that a possible??

### 2019-03-13 Scripts/Analysis/phylosignal.R

@@ -44,11 +44,11 @@ rownames(hp_mean_sp) <- c("Brassica_oleracea","Brassica_rapa","Capsicum_annuum",
 str(hp_mean_sp)
 hp_mean_sp=hp_mean_sp[,-1]
 p4d <- phylo4d(pollen_tree, hp_mean_sp)
-barplot.phylo4d(p4d, tree.type = "phylo", tree.ladderize = TRUE)
+barplot.phylo4d(p4d, tree.type = "phylo", tree.ladderize = TRUE,  scale = FALSE)
 phyloSignal(p4d = p4d, method = "all")
 carni.lipa <- lipaMoran(p4d)
 carni.lipa.p4d <- lipaMoran(p4d, as.p4d = TRUE)
-barplot.phylo4d(p4d, bar.col=(carni.lipa$p.value < 0.05) + 1, center = FALSE , scale = FALSE)
+barplot.phylo4d(p4d, bar.col=(carni.lipa$p.value < 0.05) + 1, center = FALSE , scale = FALSE,trait.labels="Hp effect")
 barplot.phylo4d(carni.lipa.p4d, bar.col = (carni.lipa$p.value < 0.05) + 1, center = FALSE, scale = FALSE)
 dotplot(p4d)
 
@@ -81,34 +81,27 @@ dotplot(p4d)
 #Assessing the signal depth with correlograms
 mass.crlg <- phyloCorrelogram(p4d, trait = "dt")
 plot(mass.crlg)
-
-
 dotplot(p4d, tree.type = "cladogram")
 
-
-
-
 #Now I´m going to try to perform it with my data
+#Effect sizes phylo signal
 pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
-matrix_scale_effect <- readRDS("Data/matrix_effect_size.RData")
-as.data.frame(matrix_scale_effect)
-matrix_scale_effect <- melt(matrix_scale_effect)
-colnames(matrix_scale_effect)[3] <- "hp"
-str(matrix_scale_effect)
-matrix_scale_effect <- as.data.frame(matrix_scale_effect)
-hp_mean_sp=matrix_scale_effect
-hp_mean_sp <- dcast(Focal ~ ., value.var = "hp", fun.aggregate = mean, data = matrix_scale_effect, na.rm= TRUE)
-colnames(hp_mean_sp)[2] <- "hp"
-str(hp_mean_sp)
[…]

### 2019-03-13 Scripts/Phylogeny/phylogenetic_signal.R

@@ -163,4 +163,14 @@ si_index <- as.matrix((si_index))[,1]
 si_index <- phylosig(tree=tree_10,x=si_index,method="lambda",test=TRUE)
 #$`lambda`[1] 0.4917088
 
-#save.image("Manuscript_draft/Data/phylo_sign.RData")
+effect_size_all <- readRDS( "Data/effect_size_all.RData")
+effect_size_all$species <- c("SOME","SOLY","PEIN", "CAAN",
+                               "IPPU", "IPAQ", "SIAL", "ERSA",
+                               "BRRA", "BROL")
+effect_size_all=effect_size_all[,-c(1,3,4)]
+traits_all$species <- rownames(traits_all)
+traits_all <- merge(effect_size_all, traits_all, by="species" )
+Cohen_d <-as.data.frame(traits_all[,c("Cohen_d")])
+rownames(Cohen_d) <- tree_10[[3]]
+Cohen_d <- as.matrix((Cohen_d))[,1]
+Cohen_d <- phylosig(tree=tree_10,x=Cohen_d,method="lambda",test=TRUE)

### 2019-03-13 Scripts/Traits/total_pollen_stigma.R

@@ -24,28 +24,28 @@ colnames(total_pollen) <- c("focal", "non_focal", "ratio", "variable")
 
 data.frame(total_pollen, stringsAsFactors = F)
 total_pollen$focal <- as.character(total_pollen$focal)
-total_pollen$focal[total_pollen$focal=="CAAN"] <- "Capsicum"
-total_pollen$focal[total_pollen$focal=="SOLY"] <- "Tomato"
-total_pollen$focal[total_pollen$focal=="SOME"] <- "Eggplant"
-total_pollen$focal[total_pollen$focal=="PEIN"] <- "Petunia"
-total_pollen$focal[total_pollen$focal=="SIAL"] <- "White mustard"
-total_pollen$focal[total_pollen$focal=="ERSA"] <- "Rocket"
-total_pollen$focal[total_pollen$focal=="BROL"] <- "Wild cabbage"
-total_pollen$focal[total_pollen$focal=="BRRA"] <- "Pak choi"
-total_pollen$focal[total_pollen$focal=="IPAQ"] <- "Water morning glory"
-total_pollen$focal[total_pollen$focal=="IPPU"] <- "Morning glory"
+total_pollen$focal[total_pollen$focal=="CAAN"] <- "C. annuum"
+total_pollen$focal[total_pollen$focal=="SOLY"] <- "S. lycopersicum"
+total_pollen$focal[total_pollen$focal=="SOME"] <- "S. melongena"
+total_pollen$focal[total_pollen$focal=="PEIN"] <- "P. integrifolia"
+total_pollen$focal[total_pollen$focal=="SIAL"] <- "S. alba"
+total_pollen$focal[total_pollen$focal=="ERSA"] <- "E. sativa"
+total_pollen$focal[total_pollen$focal=="BROL"] <- "B. oleracea"
+total_pollen$focal[total_pollen$focal=="BRRA"] <- "B. rapa"
+total_pollen$focal[total_pollen$focal=="IPAQ"] <- "I. aquatica"
+total_pollen$focal[total_pollen$focal=="IPPU"] <- "I. purpurea"
 
 total_pollen$non_focal <- as.character(total_pollen$non_focal)
-total_pollen$non_focal[total_pollen$non_focal=="CAAN"] <- "Capsicum"
-total_pollen$non_focal[total_pollen$non_focal=="SOLY"] <- "Tomato"
[…]

### 2019-03-13 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 
+[explain ratios and total pollen](Jose)
 [add table with morphometrical traits to appendix]()
@@
 
-Mantel test indicates that a possible??
-[It exists!]() correlation exist between heterospecific pollen effect and the evolutive relative distances, for ITS and RBCL markers we had r coefficients of 0.29 and 0.25 respectively p<0.05 [think on a figure - maybe using NMDS]().
-Moreover, Mantel test indicates that also a possible??
-correlation between stigma width and stigma type exist (stats??).
-Trait correlations were also explored with GLMM
-
-[I have done it at the moment just for Compatibility system](Jose)
-[Also I have to fix from mixed linear model to GLMM, just realize that](Jose)
-
-\newpage
-
 # DISCUSSION
 
-Open with the main results...
+Interestingly the effect of the different donors per species were very homogeneous which lead us to think that the female reproductive traits of the pollen recipient are the main ones in explaining heterospecific pollen effect.
+Our main predictive trait of effect is stigma size, and because we found a correlation between the pollen quantity deposited on the stigma and stigma size, we argue that that the total load of pollen deposited per treatment can obscured what are the main traits in driving heterospecific pollen effect.
+
+Curiously between the species with greater effect sizes, we found completely self incompatible species, species with the smallest stigma and the species with shortes style. Develop more...
 

### 2019-03-13 Manuscript_draft/Manuscript_draft.tex
adding effect size of phylo to draft
edits

@@
 
-Add also plot with fruit production and pot it in appendix.Also the
-plots of ratios to appendices.
+Also the plots of ratios to appendices.
+
+NMDS to appendix?
 
@@
 positive correlation with heterospecific pollen effect.
+
+\href{Jose}{explain ratios and total pollen} \href{}{add table with
+morphometrical traits to appendix}
 
@@
 
-Mantel test indicates that a possible?? \href{}{It exists!} correlation
-exist between heterospecific pollen effect and the evolutive relative
-distances, for ITS and RBCL markers we had r coefficients of 0.29 and
-0.25 respectively p\textless{}0.05 \href{}{think on a figure - maybe
-using NMDS}. Moreover, Mantel test indicates that also a possible??
-correlation between stigma width and stigma type exist (stats??). Trait
-correlations were also explored with GLMM
-
-\href{Jose}{I have done it at the moment just for Compatibility system}
-\href{Jose}{Also I have to fix from mixed linear model to GLMM, just
-realize that}
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
+\caption{Phylogenetic signal of the average heterospecific pollen effect
+size per species}
+\end{figure}
 
@@
 
-Open with the main results\ldots{}
+Interestingly the effect of the different donors per species were very
+homogeneous which lead us to think that the female reproductive traits
+of the pollen recipient are the main ones in explaining heterospecific
+pollen effect. Our main predictive trait of effect is stigma size, and
+because we found a correlation between the pollen quantity deposited on
+the stigma and stigma size, we argue that that the total load of pollen
+deposited per treatment can obscured what are the main traits in driving
+heterospecific pollen effect.
+
+Curiously between the species with greater effect sizes, we found
+completely self incompatible species, species with the smallest stigma
+and the species with shortes style. Develop more\ldots{}
 

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="Effect sizes for the 10 different species.
+```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="Effect sizes for the 10 different species.
 The different families appear with different colours, when a species was focal was coloured differently from its family."}
@@
 
-#SOME
 load("effect_size_species/all_effect_size.RData")
@@
 load("effect_size_species/brol_effect_size.RData")
-p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = margin(t=0, l=0))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,0.5),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text( hjust=0),title = element_text(vjust=2),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "A)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("A) B. oleracea")
 
@@
 load("effect_size_species/brra_effect_size.RData")
-pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,0.5,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "B)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("B) B. rapa")
 
@@
 load("effect_size_species/ersa_effect_size.RData")
-p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,0.5,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "C)")+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))+ggtitle("C) E.
+sativa")
 
@@
 load("effect_size_species/sial_effect_size.RData")
-p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,0.5,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "D)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("D) S. alba")
 
@@
 load("effect_size_species/ipaq_effect_size.RData")
-p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+geom_point(alpha=c(1,1,1,1,1,0.5,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "E)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("E) I. aquatica")
 
@@
 p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
-  theme(axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,0.5,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "F)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("F) I. purpurea")
 
@@
 load("effect_size_species/caan_effect_size.RData")
-p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,0.5,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "G)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("G) C. annuum")
 
@@
 load("effect_size_species/pein_effect_size.RData")
-p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,1,0.5,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "H)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("H) P. integrifolia")
 
@@
 load("effect_size_species/soly_effect_size.RData")
-p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = margin(t=0, l=0))+ geom_point(alpha=c(1,0.5,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "I)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("I) P. integrifolia")
 
@@
 
-p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank())+ geom_point(size=2,alpha=c(0.5,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ annotate("text", x=10, y=-6, label= "J)")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("J) P. integrifolia")
 

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
changing ggplot style

@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("A) B. oleracea")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic('B. oleracea'))))
 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("B) B. rapa")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic('B. rapa'))))
 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))+ggtitle("C) E.
-sativa")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic('E.
+sativa'))))
 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("D) S. alba")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic('S. alba'))))
 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("E) I. aquatica")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic('I. aquatica'))))
 

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
edits

@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("F) I. purpurea")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic('I. purpurea'))))
 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("G) C. annuum")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic('C. annuum'))))
 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("H) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic('P. integrifolia'))))
 
@@
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("I) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic('S. lycopersicum'))))
 
@@
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("J) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic('S. melongena'))))
 

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
customizing ggplot effect sizes

--- 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
@@
 load("effect_size_species/brol_effect_size.RData")
-p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text( hjust=0),title = element_text(vjust=2),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
+p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text( hjust=0),title = element_text(vjust=2),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",3),"#E69F00"))+
   scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("A) B. oleracea")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))
 
@@
 load("effect_size_species/brra_effect_size.RData")
-pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",2),"#E69F00","#0072B2"))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle("B) B. rapa")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))
 
@@
 load("effect_size_species/ersa_effect_size.RData")
-p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",1),"#E69F00", rep("#0072B2",3)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))+ggtitle("C) E.
-sativa")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic(' E.
+sativa'))))
 
@@
 load("effect_size_species/sial_effect_size.RData")
-p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2),"#E69F00", rep("#0072B2",3)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("D) S. alba")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))
 
@@
 load("effect_size_species/ipaq_effect_size.RData")
-p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",1),"#E69F00", rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("E) I. aquatica")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))
 
@@
 p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
-  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4),"#E69F00", rep("#009E73",1), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("F) I. purpurea")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))
 
@@
 load("effect_size_species/caan_effect_size.RData")
-p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("G) C. annuum")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))
 
@@
 load("effect_size_species/pein_effect_size.RData")
-p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("H) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))
 
@@
 load("effect_size_species/soly_effect_size.RData")
-p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",1),"#E69F00",rep("#D55E00",2), rep("#009E73",2), rep("#0072B2",4)))+scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("I) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))
 
@@
 
-p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c("#E69F00",rep("#D55E00",3), rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("J) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))
 

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
fighting with ggplot legend... no succeed

--- 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
@@
 load("effect_size_species/brol_effect_size.RData")
-p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text( hjust=0),title = element_text(vjust=2),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'bold')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
+p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text(size=10),title = element_text(vjust=2),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",3),"#E69F00"))+
   scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic('B. oleracea'))))
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))
 
@@
 load("effect_size_species/brra_effect_size.RData")
-pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",2),"#E69F00","#0072B2"))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic('B. rapa'))))
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))
 
@@
 load("effect_size_species/ersa_effect_size.RData")
-p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",1),"#E69F00", rep("#0072B2",3)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'bold', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic('E.
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic(' E.
 sativa'))))
@@
 load("effect_size_species/sial_effect_size.RData")
-p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2),"#E69F00", rep("#0072B2",3)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic('S. alba'))))
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))
 
@@
 load("effect_size_species/ipaq_effect_size.RData")
-p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'italic','italic','bold', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",1),"#E69F00", rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic('I. aquatica'))))
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))
 
@@
 p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
-  theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+  theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4),"#E69F00", rep("#009E73",1), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("F) I. purpurea")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))
 
@@
 load("effect_size_species/caan_effect_size.RData")
-p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_text(face = c('italic', 'italic', 'italic', 'bold', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("G) C. annuum")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))
 
@@
 load("effect_size_species/pein_effect_size.RData")
-p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_blank(),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_blank(),plot.margin = unit(c(0,0,0,0), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("H) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))
 
@@
 load("effect_size_species/soly_effect_size.RData")
-p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = c('italic', 'bold', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0.3,0,0,0.5), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=2,show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(alpha=0.5,size=0.6,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",1),"#E69F00",rep("#D55E00",2), rep("#009E73",2), rep("#0072B2",4)))+scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("I) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))
 
@@
 
-p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.margin = unit(c(0.3,0,0,0.5), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
-  scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2"))+
+p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(size=1.5,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(size=0.6,alpha=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c("#E69F00",rep("#D55E00",3), rep("#009E73",2), rep("#0072B2",4)))+
+  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle("J) P. integrifolia")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))
 
+sp_legend <- readRDS("Data/sp_legend.RData")
+p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
+  xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
  #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
 grid.newpage()
- grid.draw(arrangeGrob(cbind(ggplotGrob(p1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
 
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(p11)
+
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")),size="last"),nrow=6))
+#mylegend
 ```
@@
 library(grid)
+library(tidyverse)
 
@@
 
-pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) +
   geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
@@
 grid.newpage()
- grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
+g_legend<-function(a.gplot){
+  tmp <- ggplot_gtable(ggplot_build(a.gplot))
+  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
+  legend <- tmp$grobs[[leg]]
+  return(legend)}
+
+mylegend<-g_legend(pp1)
+
+ grid.draw(arrangeGrob(cbind(ggplotGrob(pp1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")), size="last"),mylegend,nrow=6))
+
 ```

### 2019-03-14 Scripts/Analysis/Effect size.R

@@ -767,3 +767,15 @@ p2 + geom_point(alpha=c(1,1,1,1,1,0.5,1,1,1,1),show.legend = FALSE,aes(color=fac
 
 
 #save.image("Manuscript_draft/effect_size_species/all_effect_size.RData")
+
+
+#prepare plot with data frame for legend in Markdown
+
+sp_legend=ipaq_effect_size
+str(sp_legend)
+sp_legend$Family[sp_legend$Family=="S"]<- "Solanaceae"
+sp_legend$Family[sp_legend$Family=="C"]<- "Convolvulaceae"
+sp_legend$Family[sp_legend$Family=="B"]<- "Brassicaceae"
+sp_legend[1,3] <- "Focal species"
+#saveRDS(sp_legend, "Manuscript_draft/Data/sp_legend.RData")
+

### 2019-03-14 Manuscript_draft/Manuscript_draft.Rmd
adding captions to figures

@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="Average effect size and confidence intervals (95%) of the 9 heterospecific treatments of 50% pollen to the different 10 focal species coloured by family."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="The impact of foreign pollen on recipient plant species.
+Effect sizes (with 95%confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}
 
@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="Effect sizes for the 10 different species.
-The different families appear with different colours, when a species was focal was coloured differently from its family."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="The response of heterospecific pollen upon 10 recipient plant species.
+Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species."}
 

### 2019-03-14 Manuscript_draft/Manuscript_draft.tex
fighting with ggplot legend... no succeed
adding captions to figures

@@
 \includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{Average effect size and confidence intervals (95\%) of the 9
-heterospecific treatments of 50\% pollen to the different 10 focal
-species coloured by family.}
+\caption{The impact of foreign pollen on recipient plant species. Effect
+sizes (with 95\%confidence intervals) of 9 different donor species of
+heterospecific pollen upon all recipients.}
 \end{figure}
@@
 \includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\caption{Effect sizes for the 10 different species. The different
-families appear with different colours, when a species was focal was
-coloured differently from its family.}
+\caption{The response of heterospecific pollen upon 10 recipient plant
+species. Each panel represents one recipient plant species crossed with
+50\% mixes of the other 9 species.}
 \end{figure}

### 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
edits legend

@@
 ---
-title: working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect
+title: Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction
 author:
@@
 Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen.
-However, the costs of heterospecific pollen are not yet well understood.
-We conducted a glasshouse experiment to understand how phylogenetic relatedness and plant traits mediate the impacts of heterospecific pollen transfer.
-We conducted 1800 crosses by experimentally transferring pollen (50% and 100% ratio) with reciprocal crosses between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
+However, the mechanisms underlying the variation in outcomes as a result of pollen contribution by different plant species are not yet well understood.
+We conducted a glasshouse experiment to understand how plant traits and phylogenetic relatedness mediate the impacts of 15 heterospecific pollen transfer.
+We conducted 1800 reciprocal crosses by experimentally transferring pollen (50%  and 100% foreign pollen ratio) between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
 Seed set was used as proxy of plant fitness.
-We found that for 65% of the treatments with 50% mix reduced seed set.
-Moreover, the reduction in seed set was dependent on the degree of relatedness and reproductive traits of the pollen recipient and not the pollen donor.
-Our results show that certain traits, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.
+In the treatments of 100% foreign pollen, we found reduced seed set in X% of the treatments.
+In the treatments of 50% foreign pollen, we found reduced seed set in 65% of the treatments.
+Moreover, the reduction in seed set was dependent on the reproductive traits of the pollen recipient, but not the pollen donor or relatedness.
+Our results show that certain traits of recipient plants, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.
+
 \vspace{3mm}\hrule
@@
 
-In most ecosystems, plant species normally coexist and share their floral visitors with other species @waser1996.
-From the plants’ perspective, pollinator sharing can be positive for some plants @carvalheiro2014 or negative for others @pauw2013, depending on the facilitation gradient.
-An increasing number of visits often correlates with higher chances of fertilization @engel2003.
-However this is not always the case, among these possible flower visitors there are also nectar robbers and pollen thieves @inouye1980; @magrach2017.
+In most ecosystems, plant species normally coexist and share their floral visitors with other species @waser1996; @carvalheiro2014.
+From the plants’ perspective, pollinator sharing can be positive for some plants as an increasing number of visits often correlates with higher chances of fertilization @engel2003.
+Yet, among these possible flower visitors there are also nectar robbers, pollen thieves @inouye1980; @magrach2017, and inconstant pollinators that transfer foreign pollen from other plants @pauw2013.
+By visiting many plant species, many pollinators are responsible for conspecific pollen loss and the transport of foreign pollen, both of which can have important detrimental effects on species fitness @morales2008; @ashman2013; @arceo2016.
 Receiving both sufficient quantity and quality deposited on the stigma is thus highly relevant to the pollination success of the plant @aizen2007.
-
-By visiting many plant species, many pollinators are responsible for conspecific pollen loss and the transport of foreign pollen, both of which can have important detrimental effects on species fitness @morales2008;  @ashman2013; @arceo2016.
 Foreign pollen arrival can play an important role in plant species fitness but outcomes are variable and appear to be context dependent as there is not always a decrease in fitness @morales2008.
@@
 However, most studies report ranges of heterospecific pollen between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012; @ashman2013; @fang2013, yet even these relatively low amounts of heterospecific pollen transferred can decrease fitness greatly @thomson1982.
-While we now have some understanding of the impacts of heterospecific pollen quantity, we have less understanding of other factors that could be driving the variation in impacts upon fitness.
+
+While we have some understanding of the impacts of heterospecific pollen quantity, we have little knoweldge of the factors that could be driving the variation in pollen quality  upon fitness.
+Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involved in the pollen-pistil interaction make difficult to unravel exactly which traits are driving the effect.
 @ashman2013 postulated the first predictive framework that identifies a need to understand how plant traits might mediate heterospecific pollen effect, whereby mating system and pollen size were  predicted to potentially mediate the impact of foreign pollen transfer on plant fitness.
-This concept is supported by specific case studies, such as @tong2016 that demonstrate an asymmetrical effect in 6 species of *Pedicularis* whereby the pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
+
+The concept of trait driven mechanisms is not new and is supported by system specific studies.
+Pollen size, pollen aperture number and pollen allelopathy are thought to be key components in understanding the outcome of foreign pollen arrival @murphy1995; @ashman2013.
+For example, small pollen is predicted to decrease plant fitness because XXXXXX.
+Yet, large pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
+Hence, understanding the different mechanical or chemical effects of pollen requires knowledge of the female traits of the pollen recipient to also be considered @montgomery2012; @ashman2013; @tong2016.
+For example, greater stigmatic area is positively correlated with greater heterospecific pollen deposition @montgomery2012 and therefore likely to result in an greater negative effect upon plant fitness.
+Further, species that are self-incompatible are thought to be more resistant to the negative impacts of heterospecific pollen than self-compatible species @ashman2013.
+
+When both donor and recipient traits are considered together, other combinations of traits are also likely to impact plant fitness.
+For example, large pollen grains could potentially clog small stigmas with fewer pollen grains, and larger stigmas are less likely to be clogged by small pollen grains.
+Yet, few studies have considered how effects might differ among donor and recipient species.
+@tong2016 demonstrate an asymmetrical effect in 6 species of Pedicularis whereby foreign pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
 While this suggests that the impacts of  heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a general trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
 
-Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involve in the pollen-pistil interaction make difficult to unravel what are the main traits in driving the effect.
-These traits can be seen from a male perspective of both donor and recipient where pollen size, pollen aperture number and pollen allelopathy are key components to understand the outcome of foreign pollen arrival @murphy1995; @ashman2013.
-In @ashman2013 small pollen is predicted to cause a greater fitness decrease, although this can be true there are also other possibilities to consider which can obscure a predictive framework like big pollen can clogg small stigmas with fewer pollen grains, bigger stigmas are less likely to be clogged by small pollen grains and bigger pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
-Moreover, to understand the different mechanical or chemical effects of pollen also the female traits of the pollen recipient have to be considered, from the literature these main traits are: stigma size, style length, number of ovules, incompatibility system and also a structural trait such as flower morphology @montgomery2012; @ashman2013; @tong2016.
-For example, greater stigmatic area is positively correlated with greater heterospecific pollen deposition @montgomery2012 and therefore possibly with an increase in negative effect.
-For species that are self-incompatible the barriers towards heterospecific pollen are stronger than self-compatible species @ashman2013.
-Nonetheless, an effect of foreign pollen is a bit obscured by the variability within species, however species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from @whitehead2018).
-Although past research has progress in the understanding of what traits can mediate the effect as we have shown here, there are multiple traits involved and multiple possible scenarios still to be explored empirically for a full understanding of the importance of heterospecific pollen effect in nature.
+It is challenging to identify general patterns with respect to the mechanisms driving foreign pollen impacts as results are often obscured by the variability within and among species.
+Closely related species are more likely to have similar  traits @letten2015.
+The similarity in traits between closely related species can lead tohigher chances of ovule usurpation/abortion @arceo2011 hence, greater negative effects of HP pollen are thought to be a associated with more closely related species @ashman2013; @arceo2016.
+Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999 and those that have, often report low sample sizes and a lack of significance.
+Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.
+Given that pollen carried on many insects and stigmas has been found to carry multiple species of foreign pollen with little attention to degree of relatedness @arceo2016; @fang2013.
+understanding the role of foreign pollen from distantly related species thus deserves greater attention
 
-For the understanding at what level or intensity the interference of pollen can occur is important to consider the relatedness of the interacting species.
-Closely related species are more likely to have similar traits @letten2015.
-The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion @arceo2011 and therefore studies predict and show a greater negative effect of closely related species @ashman2013; @arceo2016.
-Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999.
-Despite the fact that far related species are also able to decrease species fitness (REFS).
-Yet, most insects and most stigmas have been found to carry multiple species of foreign pollen with little attention to degree of relatedness (Arceo-Gómez and Ashman (2016); Fang and Huang (2013).
-Understanding the role of foreign pollen from distantly related species thus deserves greater attention.
-The relatedness of foreign pollen gives a first snapshoot of where the pollen competition can occur and therefore could be a proxy of effect.
-With that said, @arceo2016 is the only work until our knowledge which has proven a greater effect of close related species through a meta-analysis but with low sample sizes and lack of significance.
-Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.
+We investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with heterogeneous reproductive traits.
+Our study addressed the following questions:
 
-Heterospecific pollen studies in nature have the complexity added of great environmental variability which can lead to confounding interpretations.
-Moreover, the great diversity of floral structures and small sizes of some of them such as Asteraceae species make tedious or almost impossible the studies of heterospecific pollen on the field.
-For this reason, we investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with heterogeneous reproductive traits.
-Our study tries to answer the following questions: (i) Do heterospecific pollen reduce seed set?
-To what extent do (ii) floral reproductive traits and (iii) relatedness, mediate the impacts of heterospecific pollen on seed set.
+1.	To what extent does the amount of foreign pollen applied to stigmas impact plant reproductive fitness (i.e. 50% and 100% foreign pollen ratio.
+
+2.	How do floral reproductive traits and plant relatedness mediate the impacts of heterospecific pollen on seed set.
 
@@
 sp_legend <- readRDS("Data/sp_legend.RData")
-p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
+p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
   xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
@@
 
- grid.draw(arrangeGrob(cbind(ggplotGrob(p1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")),size="last"),nrow=6))
+ grid.draw(arrangeGrob(cbind(ggplotGrob(p1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")),size="last"),mylegend,nrow=6))
 #mylegend
@@
 
-pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
+  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
 ymax = Upper,color=factor(Family)))+
@@
 
-mylegend<-g_legend(pp1)
+p11<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+mylegend<-g_legend(p11)
 
@@
 # DISCUSSION
+
+supporting ideas: 
+Species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from Whitehead et al. (2018)).
 

### 2019-03-15 Manuscript_draft/Manuscript_draft.tex
edits legend

@@
             pdfauthor={},
-            pdftitle={working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect},
+            pdftitle={Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction},
             colorlinks=true,
@@
 
-\title{working title Compatibility system and stigma size are the main
-predictors of heterospecific pollen effect}
+\title{Recipient plant traits are important determinants of the impacts of
+heterospecific pollen upon plant reproduction}
 \author{
@@
 \begin{center}
-\huge working title Compatibility system and stigma size are the main
-predictors of heterospecific pollen effect
+\huge Recipient plant traits are important determinants of the impacts of
+heterospecific pollen upon plant reproduction
 \end{center}
@@
 Pollinator sharing can have negative consequences for plant fitness with
-the arrival of foreign pollen. However, the costs of heterospecific
-pollen are not yet well understood. We conducted a glasshouse experiment
-to understand how phylogenetic relatedness and plant traits mediate the
-impacts of heterospecific pollen transfer. We conducted 1800 crosses by
-experimentally transferring pollen (50\% and 100\% ratio) with
-reciprocal crosses between 10 species belonging to three different
-families: Brassicaceae, Solanaceae and Convolvulaceae. Seed set was used
-as proxy of plant fitness. We found that for 65\% of the treatments with
-50\% mix reduced seed set. Moreover, the reduction in seed set was
-dependent on the degree of relatedness and reproductive traits of the
-pollen recipient and not the pollen donor. Our results show that certain
-traits, particularly compatibility system, are critical in understanding
-the costs of heterospecific pollen. \vspace{3mm}\hrule
+the arrival of foreign pollen. However, the mechanisms underlying the
+variation in outcomes as a result of pollen contribution by different
+plant species are not yet well understood. We conducted a glasshouse
+experiment to understand how plant traits and phylogenetic relatedness
+mediate the impacts of 15 heterospecific pollen transfer. We conducted
+1800 reciprocal crosses by experimentally transferring pollen (50\% and
+100\% foreign pollen ratio) between 10 species belonging to three
+different families: Brassicaceae, Solanaceae and Convolvulaceae. Seed
+set was used as proxy of plant fitness. In the treatments of 100\%
+foreign pollen, we found reduced seed set in X\% of the treatments. In
+the treatments of 50\% foreign pollen, we found reduced seed set in 65\%
+of the treatments. Moreover, the reduction in seed set was dependent on
+the reproductive traits of the pollen recipient, but not the pollen
+donor or relatedness. Our results show that certain traits of recipient
+plants, particularly compatibility system, are critical in understanding
+the costs of heterospecific pollen.
+
+\vspace{3mm}\hrule
 
@@
 In most ecosystems, plant species normally coexist and share their
-floral visitors with other species Waser et al. (1996). From the plants'
-perspective, pollinator sharing can be positive for some plants
-Carvalheiro et al. (2014) or negative for others Pauw (2013), depending
-on the facilitation gradient. An increasing number of visits often
+floral visitors with other species Waser et al. (1996); Carvalheiro et
+al. (2014). From the plants' perspective, pollinator sharing can be
+positive for some plants as an increasing number of visits often
 correlates with higher chances of fertilization Engel and Irwin (2003).
-However this is not always the case, among these possible flower
-visitors there are also nectar robbers and pollen thieves Inouye (1980);
-Magrach et al. (2017). Receiving both sufficient quantity and quality
-deposited on the stigma is thus highly relevant to the pollination
-success of the plant Aizen and Harder (2007).
-
+Yet, among these possible flower visitors there are also nectar robbers,
+pollen thieves Inouye (1980); Magrach et al. (2017), and inconstant
+pollinators that transfer foreign pollen from other plants Pauw (2013).
 By visiting many plant species, many pollinators are responsible for
@@
 and Traveset (2008); Ashman and Arceo-Gómez (2013); Arceo-Gómez and
-Ashman (2016). Foreign pollen arrival can play an important role in
-plant species fitness but outcomes are variable and appear to be context
-dependent as there is not always a decrease in fitness Morales and
-Traveset (2008). Some of this variation is likely due to the enormous
-variability of foreign pollen transferred across systems ranging from 0
-to 75 percent. However, most studies report ranges of heterospecific
-pollen between 0 and 20 percent of the total pollen load Bartomeus et
-al. (2008) Montgomery and Rathcke (2012); Ashman and Arceo-Gómez (2013);
-Fang and Huang (2013), yet even these relatively low amounts of
-heterospecific pollen transferred can decrease fitness greatly Thomson
-et al. (1982). While we now have some understanding of the impacts of
-heterospecific pollen quantity, we have less understanding of other
-factors that could be driving the variation in impacts upon fitness.
-Ashman and Arceo-Gómez (2013) postulated the first predictive framework
-that identifies a need to understand how plant traits might mediate
+Ashman (2016). Receiving both sufficient quantity and quality deposited
+on the stigma is thus highly relevant to the pollination success of the
+plant Aizen and Harder (2007). Foreign pollen arrival can play an
+important role in plant species fitness but outcomes are variable and
+appear to be context dependent as there is not always a decrease in
+fitness Morales and Traveset (2008). Some of this variation is likely
+due to the enormous variability of foreign pollen transferred across
+systems ranging from 0 to 75 percent. However, most studies report
+ranges of heterospecific pollen between 0 and 20 percent of the total
+pollen load Bartomeus et al. (2008) Montgomery and Rathcke (2012);
+Ashman and Arceo-Gómez (2013); Fang and Huang (2013), yet even these
+relatively low amounts of heterospecific pollen transferred can decrease
+fitness greatly Thomson et al. (1982).
+
+While we have some understanding of the impacts of heterospecific pollen
+quantity, we have little knoweldge of the factors that could be driving
+the variation in pollen quality upon fitness. Plant traits are crucial
+to understand heterospecific pollen effect but the multifactorial nature
+of the traits that are involved in the pollen-pistil interaction make
+difficult to unravel exactly which traits are driving the effect. Ashman
+and Arceo-Gómez (2013) postulated the first predictive framework that
+identifies a need to understand how plant traits might mediate
 heterospecific pollen effect, whereby mating system and pollen size were
 predicted to potentially mediate the impact of foreign pollen transfer
-on plant fitness. This concept is supported by specific case studies,
-such as Tong and Huang (2016) that demonstrate an asymmetrical effect in
-6 species of \emph{Pedicularis} whereby the pollen of long styled
-species was able to grow the full length of the style on short styled
-species but not vice versa. While this suggests that the impacts of
-heterospecific pollen may differ among pollen donor and recipient, few
-studies have been conducted to ascertain whether this pattern is in fact
-a general trend or to identify the extent to which other plant traits
-are critical to heterospecific pollen impacts.
+on plant fitness.
 
-Plant traits are crucial to understand heterospecific pollen effect but
-the multifactorial nature of the traits that are involve in the
-pollen-pistil interaction make difficult to unravel what are the main
-traits in driving the effect. These traits can be seen from a male
-perspective of both donor and recipient where pollen size, pollen
-aperture number and pollen allelopathy are key components to understand
-the outcome of foreign pollen arrival Murphy and Aarssen (1995); Ashman
-and Arceo-Gómez (2013). In Ashman and Arceo-Gómez (2013) small pollen is
-predicted to cause a greater fitness decrease, although this can be true
-there are also other possibilities to consider which can obscure a
-predictive framework like big pollen can clogg small stigmas with fewer
-pollen grains, bigger stigmas are less likely to be clogged by small
-pollen grains and bigger pollen can outcompete smaller pollen grains due
-to faster pollen tube growth rate Williams and Rouse (1990). Moreover,
-to understand the different mechanical or chemical effects of pollen
-also the female traits of the pollen recipient have to be considered,
-from the literature these main traits are: stigma size, style length,
-number of ovules, incompatibility system and also a structural trait
-such as flower morphology Montgomery and Rathcke (2012); Ashman and
-Arceo-Gómez (2013); Tong and Huang (2016). For example, greater
+The concept of trait driven mechanisms is not new and is supported by
+system specific studies. Pollen size, pollen aperture number and pollen
+allelopathy are thought to be key components in understanding the
+outcome of foreign pollen arrival Murphy and Aarssen (1995); Ashman and
+Arceo-Gómez (2013). For example, small pollen is predicted to decrease
+plant fitness because XXXXXX. Yet, large pollen can outcompete smaller
+pollen grains due to faster pollen tube growth rate Williams and Rouse
+(1990). Hence, understanding the different mechanical or chemical
+effects of pollen requires knowledge of the female traits of the pollen
+recipient to also be considered Montgomery and Rathcke (2012); Ashman
+and Arceo-Gómez (2013); Tong and Huang (2016). For example, greater
 stigmatic area is positively correlated with greater heterospecific
-pollen deposition Montgomery and Rathcke (2012) and therefore possibly
-with an increase in negative effect. For species that are
-self-incompatible the barriers towards heterospecific pollen are
-stronger than self-compatible species Ashman and Arceo-Gómez (2013).
-Nonetheless, an effect of foreign pollen is a bit obscured by the
-variability within species, however species that are strong selfers or
-strong outcrossers have less variablity in mating systems and
-predictions of effect could be more realistic (see figure 1 from
-Whitehead et al. (2018)). Although past research has progress in the
-understanding of what traits can mediate the effect as we have shown
-here, there are multiple traits involved and multiple possible scenarios
-still to be explored empirically for a full understanding of the
-importance of heterospecific pollen effect in nature.
+pollen deposition Montgomery and Rathcke (2012) and therefore likely to
+result in an greater negative effect upon plant fitness. Further,
+species that are self-incompatible are thought to be more resistant to
+the negative impacts of heterospecific pollen than self-compatible
+species Ashman and Arceo-Gómez (2013).
 
-For the understanding at what level or intensity the interference of
-pollen can occur is important to consider the relatedness of the
-interacting species. Closely related species are more likely to have
-similar traits Letten and Cornwell (2015). The similarity in traits
-between closely related species can lead to higher chances of ovule
-usurpation/abortion Arceo-Gómez and Ashman (2011) and therefore studies
-predict and show a greater negative effect of closely related species
-Ashman and Arceo-Gómez (2013); Arceo-Gómez and Ashman (2016). Few
-studies however, have focused on the impacts of heterospecific pollen on
-fitness of distantly related species Galen and Gregory (1989); Neiland
-and Wilcock (1999). Despite the fact that far related species are also
-able to decrease species fitness (REFS). Yet, most insects and most
-stigmas have been found to carry multiple species of foreign pollen with
-little attention to degree of relatedness (Arceo-Gómez and Ashman
-(2016); Fang and Huang (2013). Understanding the role of foreign pollen
-from distantly related species thus deserves greater attention. The
-relatedness of foreign pollen gives a first snapshoot of where the
-pollen competition can occur and therefore could be a proxy of effect.
-With that said, Arceo-Gómez and Ashman (2016) is the only work until our
-knowledge which has proven a greater effect of close related species
-through a meta-analysis but with low sample sizes and lack of
-significance. Therefore, there is a need to study the effect of
-heterospecific pollen of far and close related species at community
-level beyond single pairwise interactions.
+When both donor and recipient traits are considered together, other
+combinations of traits are also likely to impact plant fitness. For
+example, large pollen grains could potentially clog small stigmas with
+fewer pollen grains, and larger stigmas are less likely to be clogged by
+small pollen grains. Yet, few studies have considered how effects might
+differ among donor and recipient species. Tong and Huang (2016)
+demonstrate an asymmetrical effect in 6 species of Pedicularis whereby
+foreign pollen of long styled species was able to grow the full length
+of the style on short styled species but not vice versa. While this
+suggests that the impacts of heterospecific pollen may differ among
+pollen donor and recipient, few studies have been conducted to ascertain
+whether this pattern is in fact a general trend or to identify the
+extent to which other plant traits are critical to heterospecific pollen
+impacts.
 
-Heterospecific pollen studies in nature have the complexity added of
-great environmental variability which can lead to confounding
-interpretations. Moreover, the great diversity of floral structures and
-small sizes of some of them such as Asteraceae species make tedious or
-almost impossible the studies of heterospecific pollen on the field. For
-this reason, we investigated how floral reproductive traits and
-relatedness mediate the impact of heterospecific pollen by creating an
-artificial co-flowering community in a glasshouse with 10 species
-belonging to three different families with heterogeneous reproductive
-traits. Our study tries to answer the following questions: (i) Do
-heterospecific pollen reduce seed set? To what extent do (ii) floral
-reproductive traits and (iii) relatedness, mediate the impacts of
-heterospecific pollen on seed set.
+It is challenging to identify general patterns with respect to the
+mechanisms driving foreign pollen impacts as results are often obscured
+by the variability within and among species. Closely related species are
+more likely to have similar traits Letten and Cornwell (2015). The
+similarity in traits between closely related species can lead tohigher
+chances of ovule usurpation/abortion Arceo-Gómez and Ashman (2011)
+hence, greater negative effects of HP pollen are thought to be a
+associated with more closely related species Ashman and Arceo-Gómez
+(2013); Arceo-Gómez and Ashman (2016). Few studies however, have focused
+on the impacts of heterospecific pollen on fitness of distantly related
+species Galen and Gregory (1989); Neiland and Wilcock (1999) and those
+that have, often report low sample sizes and a lack of significance.
+Therefore, there is a need to study the effect of heterospecific pollen
+of far and close related species at community level beyond single
+pairwise interactions. Given that pollen carried on many insects and
+stigmas has been found to carry multiple species of foreign pollen with
+little attention to degree of relatedness Arceo-Gómez and Ashman (2016);
+Fang and Huang (2013). understanding the role of foreign pollen from
+distantly related species thus deserves greater attention
+
+We investigated how floral reproductive traits and relatedness mediate
+the impact of heterospecific pollen by creating an artificial
+co-flowering community in a glasshouse with 10 species belonging to
+three different families with heterogeneous reproductive traits. Our
+study addressed the following questions:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  To what extent does the amount of foreign pollen applied to stigmas
+  impact plant reproductive fitness (i.e.~50\% and 100\% foreign pollen
+  ratio.
+\item
+  How do floral reproductive traits and plant relatedness mediate the
+  impacts of heterospecific pollen on seed set.
+\end{enumerate}
 
@@
 
+supporting ideas: Species that are strong selfers or strong outcrossers
+have less variablity in mating systems and predictions of effect could
+be more realistic (see figure 1 from Whitehead et al. (2018)).
+
 Interestingly the effect of the different donors per species were very
@@
 
-\hypertarget{ref-whitehead2018}{}
-Whitehead, M. R., R. Lanfear, R. J. Mitchell, and J. D. Karron. 2018.
-Plant mating systems often vary widely among populations. Frontiers in
-Ecology and Evolution 6:38.
-
 \hypertarget{ref-williams1990}{}

### 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
ggplot family edited

@@
 ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
   scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
@@
   return(legend)}
-
-p11<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))
+leg_family=readRDS("Data/leg_family.RData")
+p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))
  #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")

### 2019-03-15 Scripts/Analysis/Effect_size_families.R

@@ -85,7 +85,7 @@ soly_effect_size <- rbind(soly_effect_size_b,
 
 soly_effect_size$Family <- as.character(soly_effect_size$Family)
 soly_effect_size <- soly_effect_size %>% arrange(desc(Family))
-soly_effect_size <- rbind(soly_effect_size_cross,soly_effect_size)
+soly_effect_size <- rbind(soly_effect_size, soly_effect_size_cross)
 
 
 
@@ -104,7 +104,7 @@ ymax = Upper, size=2,color=factor(Family)), width = 0.2)+
   xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
 
-#save.image("Manuscript_draft/effect_size_species/soly_effect_size_family.RData")
+save.image("Manuscript_draft/effect_size_species/soly_effect_size_family.RData")
 
 #SOME
 
@@ -165,7 +165,7 @@ some_effect_size <- rbind(some_effect_size_b,
 
 some_effect_size$Family <- as.character(some_effect_size$Family)
 some_effect_size <- some_effect_size %>% arrange(desc(Family))
-some_effect_size <- rbind(some_effect_size_cross,some_effect_size)
+some_effect_size <- rbind(some_effect_size, some_effect_size_cross)
 
 
 
@@ -182,7 +182,7 @@ p1 + geom_point(show.legend = FALSE,aes(color=factor(Family))) +
   xlab("Treatments") + ylab("Cohen's d") + rotate()+guides(fill=FALSE)+
   geom_hline(yintercept=0, linetype="dashed", color = "black")
 
-#save.image("Manuscript_draft/effect_size_species/some_effect_size_family.RData")
+save.image("Manuscript_draft/effect_size_species/some_effect_size_family.RData")
 
 
 #PEIN
@@ -242,7 +242,7 @@ pein_effect_size <- rbind(pein_effect_size_b,
 
 pein_effect_size$Family <- as.character(pein_effect_size$Family)
 pein_effect_size <- pein_effect_size %>% arrange(desc(Family))
-pein_effect_size <- rbind(pein_effect_size_cross,pein_effect_size)
+pein_effect_size <- rbind(pein_effect_size,pein_effect_size_cross)
 
 
 
[…]

### 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
markdown I hate you

@@
 [add table with morphometrical traits to appendix]()
+
+I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
+Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
+The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
+
+Here I show the plot of just solanaceae and then with all the species.
+I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE}
+#Here I'm going to perform the analysis per family
+#load libraries
+library(vegan)
+library(nlme)
+library(dplyr)
+library(reshape2)
+#load data
+matrix_scale_effect <- readRDS("Data/matrix_scale_effect.Rda")
+matrix_effect_size <- readRDS("Data/matrix_effect_size.RData")
+traits_all <- read.csv("Data/traits_all.csv", sep=",")
+rownames(traits_all) <- rownames(matrix_scale_effect)
+si_index <- readRDS("Data/si_index.RData")
+traits_all$si_index <- si_index
+load("Data/effect_size_all.RData")
+effect_size=melt(matrix_effect_size)
+####
+####SOLANACEAE####
+####
+matrix_soly=matrix_scale_effect[c(3,7,9,10),c(3,7,9,10)]
+matrix_soly=matrix_effect_size[c(3,7,9,10),c(3,7,9,10)]
+
+traits_sola=traits_all[c(3,7,9,10),-c(1,2)]
+traits_sola_dist <- dist(traits_sola, diag = T)
+a <- mantel(matrix_soly,traits_sola_dist)
+summary(a)
+mantel(matrix_soly,dist(traits_sola[,2]))
+cor.test(sola$Cohen_d,sola$pollen_size)
+
+traits_sola$species <- c("CAAN", "PEIN","SOLY","SOME")
+effect_size_sola=effect_size_all[c(1:4),c(1,2)]
+effect_size_sola$species <- c("SOME", "SOLY","PEIN","CAAN")
+sola <- merge(effect_size_sola,traits_sola,by="species")
+sola$style_length<- sola$style_length/1000
+cor.test(sola$Cohen_d,sola$style_length)
+library("ggpubr")
+ggscatter(sola, x = "Cohen_d", y = "style_length", 
+          add = "reg.line", conf.int = TRUE, 
+          cor.coef = TRUE, cor.method = "pearson",
+          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")
+
+```
 

### 2019-03-15 Manuscript_draft/Manuscript_draft.tex
markdown I hate you

@@
 
+I haven't add this to the draft yet but when I look just Solanaceae
+species, interestingly seems to be a negative trend with style length
+and heterospecific pollen effect. Curiously, Capsicum and tomato are the
+ones that are more affected by hp and both have the shortest stigma and
+style. The stigma results of tomato are supported by the plot of effct
+sizes per family where convolvulaceae has a greater negative effect than
+the other two families (and they are the ones with bigger pollen size)
+
+Here I show the plot of just solanaceae and then with all the species. I
+have gouped all the treatments, if not I feel like we are doing p
+hacking with all the analysis, because is increasing the strength of
+each point 9 times.
+
 \newpage

### 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
EDITS GGPLOTS

--- 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
@@
 fontsize: 11pt
+header-includes: \usepackage{float}
 footerdate: yes
@@
 ---
+```{r global_options, include=FALSE}
+knitr::opts_chunk$set(fig.pos = 'h')
+```
 
@@
 More information about these treatments can be found in Methods and Appendices."}
-
 load("r_biology.RData")
-
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
 ggplot(bio,aes(x=Species,y=value,fill=variable))+
@@
 
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5,fig.cap="a"}
+load("Data/family_cor.RData")
+library(ggpubr)
+library(ggplot2)
+library(gridExtra)
+library(grid)
+
+p1 <- ggscatter(sola, x = "Cohen_d", y = "style_length", 
+          add = "reg.line", conf.int = TRUE, 
+          cor.coef = TRUE, cor.method = "pearson",
+          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")
+
+p2<- ggscatter(a, x = "Cohen_d", y = "style_length", 
+          add = "reg.line", conf.int = TRUE, 
+          cor.coef = TRUE, cor.method = "pearson",
+          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) All families")
+grid.arrange(p1, p2, nrow = 1, ncol=2)
+
+```
+
+I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
+Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
+The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
+
+Here I show the plot of just solanaceae and then with all the species.
+I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
+
+\newpage
+
 # DISCUSSION
@@
 <div id = "refs"></div>
+\newpage
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+```{r, echo=FALSE, message=FALSE,fig.height=10,fig.width=5, warning=FALSE,fig.cap="Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
+Pollen was counted for crosses with species of the other two families (N=3).
+To prepare these ratios all the pollen grains on the stigma were counted.", cache=FALSE}
 load("pollen_ratio.RData")
+library(ggpubr)
+library(ggplot2)
+library(gridExtra)
+library(grid)
 
-ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+p1 <- ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
 
-ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+p2 <- ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
 
-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
+grid.arrange(p1, p2,p3, nrow = 3, ncol=1)
 

### 2019-03-15 Manuscript_draft/Manuscript_draft.tex
EDITS GGPLOTS
creating two separated rmd with figures and text I think is the best

@@
 
-\begin{figure}
-
-{\centering \includegraphics{output/figures/unnamed-chunk-3-1}
-
-}
-
-\caption{Barplot with the different treatments that provide information of the reproductive biology of the ten species.
-The y axis is the proportion of ovules converted to seed in percentage.
-The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis.
-More information about these treatments can be found in Methods and Appendices.}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
-\caption{The impact of foreign pollen on recipient plant species. Effect
-sizes (with 95\%confidence intervals) of 9 different donor species of
-heterospecific pollen upon all recipients.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
-\caption{The response of heterospecific pollen upon 10 recipient plant
-species. Each panel represents one recipient plant species crossed with
-50\% mixes of the other 9 species.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
-\caption{A}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
-\caption{Phylogenetic signal of the average heterospecific pollen effect
-size per species}
-\end{figure}
-
-\newpage
-
 \section{DISCUSSION}\label{discussion}
@@
 
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{output/figures/unnamed-chunk-3-1}
+
+}
+
+\caption{Barplot with the different treatments that provide information of the reproductive biology of the ten species.
+The y axis is the proportion of ovules converted to seed in percentage.
+The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis.
+More information about these treatments can be found in Methods and Appendices.}\label{fig:unnamed-chunk-3}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-4-1.pdf}
+\caption{The impact of foreign pollen on recipient plant species. Effect
+sizes (with 95\% confidence intervals) of 9 different donor species of
+heterospecific pollen upon all recipients.}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-5-1.pdf}
+\caption{The response of heterospecific pollen upon 10 recipient plant
+species. Each panel represents one recipient plant species crossed with
+50\% mixes of the other 9 species.}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-6-1.pdf}
+\caption{A}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
+\caption{Phylogenetic signal of the average heterospecific pollen effect
+size per species}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{output/figures/unnamed-chunk-8-1}
+
+}
+
+\caption{a}\label{fig:unnamed-chunk-8}
+\end{figure}\newpage
+
 \section{APPENDIX}\label{appendix}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-\end{enumerate}
-
-\textbf{Table S1}. Perecentage of seeds produced per ovule for the ten
-species used in the experiment. The treatments presented are hand
-cross-pollination, hand self-pollination, natural selfing and apomixis
-(emasculated flowers).
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\setcounter{enumi}{1}
-\item
-\end{enumerate}
-
-\textbf{Figure S1}. Pollen ratios separated by family A) Brassicaceae,
-B) Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with
+\begin{figure}
+\centering
+\includegraphics{output/figures/unnamed-chunk-10-1.pdf}
+\caption{Pollen ratios separated by family A) Brassicaceae, B)
+Solanaceae, C) Convolvulaceae. Pollen was counted for crosses with
 species of the other two families (N=3). To prepare these ratios all the
-pollen grains on the stigma were counted.
-
-\includegraphics{output/figures/unnamed-chunk-9-1.pdf}
-\includegraphics{output/figures/unnamed-chunk-9-2.pdf}
-\includegraphics{output/figures/unnamed-chunk-9-3.pdf}
+pollen grains on the stigma were counted.}
+\end{figure}
 

### 2019-03-15 Manuscript_draft/Tables_and_figures.Rmd
creating two separated rmd with figures and text I think is the best

--- 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
@@
 ---
-title: Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction
-author:
-- name: Jose B. Lanuza
-  affilnum: 1
-  email: barragansljose@gmail.com
-
-- name: Ignasi Bartomeus
-  affilnum: 2
-
-- name: Tia-Lynn Ashman  
-  affilnum: 3
-
-- name: Romina Rader
-  affilnum: 1
-
-affiliation:
-- affil: University of New England (Australia)
-  affilnum: 1
-- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
-  affilnum: 2
-- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
-  affilnum: 3
 output:
-  pdf_document:
-    fig_caption: yes
-    fig_height: 7
-    fig_width: 7
-    includes:
-      in_header: header.tex
-    keep_tex: yes
-    number_sections: no
-    template: manuscript.latex
-  word_document: null
-  html_document: null
-capsize: normalsize
-classoption: a4paper
-csl: ecology.csl
-documentclass: article
+  pdf_document: default
+  html_document: default
   fontsize: 11pt
-header-includes: \usepackage{float}
-footerdate: yes
-geometry: margin=1in
-linenumbers: yes
-bibliography:
-- references.bib
-- knitcitations.bib
-spacing: doublespacing
-abstract: no
+header-includes:
+  - \usepackage{leading}
+  - \leading{18pt}
 ---
+--
 ```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'h')
+knitr::opts_chunk$set(fig.pos = "h")
 ```
@@
 
-\singlespace
-
-\vspace{2mm}\hrule
-
-Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen.
-However, the mechanisms underlying the variation in outcomes as a result of pollen contribution by different plant species are not yet well understood.
-We conducted a glasshouse experiment to understand how plant traits and phylogenetic relatedness mediate the impacts of 15 heterospecific pollen transfer.
-We conducted 1800 reciprocal crosses by experimentally transferring pollen (50%  and 100% foreign pollen ratio) between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
-Seed set was used as proxy of plant fitness.
-In the treatments of 100% foreign pollen, we found reduced seed set in X% of the treatments.
-In the treatments of 50% foreign pollen, we found reduced seed set in 65% of the treatments.
-Moreover, the reduction in seed set was dependent on the reproductive traits of the pollen recipient, but not the pollen donor or relatedness.
-Our results show that certain traits of recipient plants, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.
-
-\vspace{3mm}\hrule
-
-*Keywords*: heterospecific pollen, plant reproduction, fitness, interspecific competition, phylogenetic distance.
-
-\doublespace
-
-\bleft
-
-# INTRODUCTION
-
-In most ecosystems, plant species normally coexist and share their floral visitors with other species @waser1996; @carvalheiro2014.
-From the plants’ perspective, pollinator sharing can be positive for some plants as an increasing number of visits often correlates with higher chances of fertilization @engel2003.
-Yet, among these possible flower visitors there are also nectar robbers, pollen thieves @inouye1980; @magrach2017, and inconstant pollinators that transfer foreign pollen from other plants @pauw2013.
-By visiting many plant species, many pollinators are responsible for conspecific pollen loss and the transport of foreign pollen, both of which can have important detrimental effects on species fitness @morales2008; @ashman2013; @arceo2016.
-Receiving both sufficient quantity and quality deposited on the stigma is thus highly relevant to the pollination success of the plant @aizen2007.
-Foreign pollen arrival can play an important role in plant species fitness but outcomes are variable and appear to be context dependent as there is not always a decrease in fitness @morales2008.
-Some of this variation is likely due to the enormous variability of foreign pollen transferred across systems ranging from 0 to 75 percent.
-However, most studies report ranges of heterospecific pollen between 0 and 20 percent of the total pollen load @bartomeus2008 @montgomery2012; @ashman2013; @fang2013, yet even these relatively low amounts of heterospecific pollen transferred can decrease fitness greatly @thomson1982.
-
-While we have some understanding of the impacts of heterospecific pollen quantity, we have little knoweldge of the factors that could be driving the variation in pollen quality  upon fitness.
-Plant traits are crucial to understand heterospecific pollen effect but the multifactorial nature of the traits that are involved in the pollen-pistil interaction make difficult to unravel exactly which traits are driving the effect.
-@ashman2013 postulated the first predictive framework that identifies a need to understand how plant traits might mediate heterospecific pollen effect, whereby mating system and pollen size were  predicted to potentially mediate the impact of foreign pollen transfer on plant fitness.
-
-The concept of trait driven mechanisms is not new and is supported by system specific studies.
-Pollen size, pollen aperture number and pollen allelopathy are thought to be key components in understanding the outcome of foreign pollen arrival @murphy1995; @ashman2013.
-For example, small pollen is predicted to decrease plant fitness because XXXXXX.
-Yet, large pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
-Hence, understanding the different mechanical or chemical effects of pollen requires knowledge of the female traits of the pollen recipient to also be considered @montgomery2012; @ashman2013; @tong2016.
-For example, greater stigmatic area is positively correlated with greater heterospecific pollen deposition @montgomery2012 and therefore likely to result in an greater negative effect upon plant fitness.
-Further, species that are self-incompatible are thought to be more resistant to the negative impacts of heterospecific pollen than self-compatible species @ashman2013.
-
-When both donor and recipient traits are considered together, other combinations of traits are also likely to impact plant fitness.
-For example, large pollen grains could potentially clog small stigmas with fewer pollen grains, and larger stigmas are less likely to be clogged by small pollen grains.
-Yet, few studies have considered how effects might differ among donor and recipient species.
-@tong2016 demonstrate an asymmetrical effect in 6 species of Pedicularis whereby foreign pollen of long styled species was able to grow the full length of the style on short styled species but not vice versa.
-While this suggests that the impacts of  heterospecific pollen may differ among pollen donor and recipient, few studies have been conducted to ascertain whether this pattern is in fact a general trend or to identify the extent to which other plant traits are critical to heterospecific pollen impacts.
-
-It is challenging to identify general patterns with respect to the mechanisms driving foreign pollen impacts as results are often obscured by the variability within and among species.
-Closely related species are more likely to have similar  traits @letten2015.
-The similarity in traits between closely related species can lead tohigher chances of ovule usurpation/abortion @arceo2011 hence, greater negative effects of HP pollen are thought to be a associated with more closely related species @ashman2013; @arceo2016.
-Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999 and those that have, often report low sample sizes and a lack of significance.
-Therefore, there is a need to study the effect of heterospecific pollen of far and close related species at community level beyond single pairwise interactions.
-Given that pollen carried on many insects and stigmas has been found to carry multiple species of foreign pollen with little attention to degree of relatedness @arceo2016; @fang2013.
-understanding the role of foreign pollen from distantly related species thus deserves greater attention
-
-We investigated how floral reproductive traits and relatedness mediate the impact of heterospecific pollen by creating an artificial co-flowering community in a glasshouse with 10 species belonging to three different families with heterogeneous reproductive traits.
-Our study addressed the following questions:
-
-1.	To what extent does the amount of foreign pollen applied to stigmas impact plant reproductive fitness (i.e. 50% and 100% foreign pollen ratio.
-
-2.	How do floral reproductive traits and plant relatedness mediate the impacts of heterospecific pollen on seed set.
-
-# METHODS
-
-The study was conducted in a glasshouse at University of New England (Armidale, Australia) from November 2017 to March 2018.
-Rooms were temperature controlled depending on the requirements of the species with day and night temperature differences.
-The experimental design had species from three different families: Brassicaceae, Convolvulaceae and Solanaceae (**Table 1**).
-The species of the study had different reproductive traits and different degree of relatedness (see phylogenetic tree, **Figure 1**) where the reciprocal crosses between species allowed us to have multiple different scenarios of both traits and relatedness.
-Moreover, the species selected had fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
-For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).
-Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14) and the rooms of the glasshouse were temperature controlled with temperature oscillations between day and night.
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae"}
-knitr::include_graphics('images/phylo_image.png')
-```
-
-\newpage
-
-**Table 1** Species list with family and genus.
+**Table 1**
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
@@
 table<- data.frame(Family, Genus, Species)
-kable(table, format="markdown")
+kable(table, format="markdown", caption = "a")
 ```
-
 \newpage
-
-**Hand pollination**
-
-Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation.
-Therefore, we perfomed 180 different heterospecific treatments (N=10).
-Seed set was the proxy of effect for all our treatments.
-Moreover, hand cross-pollination (between individuals of the same species), hand self-pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10).
-For the treatments with foreign pollen and hand cross-pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick.
-Hand-pollination was conducted with 3-4 gentle touches on the stigma surface.
-For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed.
-Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.
-To confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix.
-Because pollen from the same family was difficult to distinguish, and we expected similar properties in mixing, we counted pollen from just one randomly selected species within each donor family different to the focal's family (N=3).
-
-**Traits and evolutive distance**
-
-The traits measured for each species were pollen per anther, pollen size, number of ovules and stigma, style, ovary width and length.
-For the stigma, the stigmatic area was also measured and moreover the stigmas were divided in wet/dry type with the help of the stereomicroscope.
-All the morphometrical measurements were performed with a stereophotomicroscope with the exception of pollen size that was carried out with a light microscope.
-Pollen was counted for 20 anthers of each species with 4 replicates per sample with an hemocytometer.
-Previously, anthers were squashed on a known solution with the pippete tip and homogeneize with a vortex for 30 seconds.
-Ovule number was counted with the help of a stereomicroscope and a small grid over a petri dish from 15 randomly selected flowers.
-Fruits per number of flowers treated were counted for just Solanaceae species with fleshy fruit.
-For all the species we counted the number of seeds produced per average number of ovules.
-Levels of self-incompatibility were estimated by dividing the seed set of hand self-pollination by hand cross-pollination @lloyd1992.
-
-**Analysis**
-
-To evaluate heterospecific pollen effect on seed production we performed linear mixed models.
-The distinct heterospecific pollination treatments were compared through relevelling each variable with the cross pollination treatment which was our control for optimum seed production for all the species.
-The different replicates of each treatment were considered as random effects.
-Seed production was scaled for all the species with mean 0 and standard deviation of 1 prior to the analysis.
-All the analysis were conducted with the statistical language `R` `r citep(citation())`.
-
-To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD] with **effsize** package.
-We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.
-
-We conducted mantel test to check for correlations between heterospecific pollen effect and phylogenetic distance.
-Due to improvents in statistical power we used the square root of the phylogenetic distance (Letten & Cornwell 2014).
-Two different phylogenetic distances were used from two kinds of markers: 1) Internal transcribed spacer (ITS) and 2) ribulose-bisphosphate carboxylase (RBCL).
-The sequences were obtained from GenBank (https://www.ncbi.nlm.nih.gov/genbank/, accessed 20 Oct.
-2018).
-The sequences were aligned with clustal omega and the pairwise evolutive distances calculated with MEGA7.
-
-In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (**vegan** package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
-Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
-To find a model with the best explanatory traits we used the function **bioenv** from R.
-We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
-Moreover, we explored also the correlation between traits and heterospecific pollen effect through generalized mixed models where the response variable was heterospecific pollen effect and the explanatory variable the different traits.
-In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.
-
-[Phylogenetic signal of traits?](Jose)
-
-Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008.
-Proportions of pollen talk about it to 50-50 mix?
-Talk aboout this in methods too.
-
-Also the plots of ratios to appendices.
-
-NMDS to appendix?
-
-# RESULTS
-
-Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values).
-Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Moreover, average effect sizes differed across species and across families, see **Figure 2**.
-Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just for four species out of ten, just one donor did not overlap the confidence intervals with other donors.
-Therefore, none of the donors had a clear stronger or weaker effect across species.
-When the donors were groped by family not big differences were seen, just for *S.
-lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**).
-In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production.
-However, for just one species (*S.
-alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
-For two Solanaceae species *S.
-melongena* and *C.
-annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.
-
-Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05).
-The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.
-We found a significant phylogenetic signal of traits for pollen size, stigma measurements and style length (p<0.05).
-Although with a lack of a significant correlation pagel's lambda values were also relatively high (>0.45) for incompatibility index, ovary length and levels of selfing.
-Moreover, Mantel test between heterospecific pollen effect and traits gave also a positive significant correlation with a  r value of 0.4.
-When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect.
-
-[explain ratios and total pollen](Jose)
-[add table with morphometrical traits to appendix]()
-
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}
+knitr::include_graphics('images/phylo_image.png')
+```
+**Figure 1**
 \newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species.
-The y axis is the proportion of ovules converted to seed in percentage.
-The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis.
-More information about these treatments can be found in Methods and Appendices."}
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
 load("r_biology.RData")
@@
 ```
+**Figure 2**
 
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="The impact of foreign pollen on recipient plant species.
-Effect sizes (with 95%confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}
+```{r, echo=FALSE, message=FALSE,fig.align='center', warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6}
 
@@
 ```
+**Figure 3**
 
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="The response of heterospecific pollen upon 10 recipient plant species.
-Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7}
 
@@
 ```
+**Figure 4**
 
 \newpage
-
-```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="A"}
+```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7}
 library(effsize)
@@
 ```
+**Figure 5**
 
 \newpage
-
-```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.cap="Phylogenetic signal of the average heterospecific pollen effect size per species"}
+```{r, echo=FALSE,fig.align='center', message=FALSE,warning=FALSE,cache=FALSE}
 library(ape)
@@
 ```
+**Figure 6**
 
 \newpage
-
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5,fig.cap="a"}
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5}
 load("Data/family_cor.RData")
@@
 ```
-
-I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
-Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
-The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
-
-Here I show the plot of just solanaceae and then with all the species.
-I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
+**Figure 7**
 
 \newpage
-
-# DISCUSSION
-
-supporting ideas: 
-Species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from Whitehead et al. (2018)).
-
-Interestingly the effect of the different donors per species were very homogeneous which lead us to think that the female reproductive traits of the pollen recipient are the main ones in explaining heterospecific pollen effect.
-Our main predictive trait of effect is stigma size, and because we found a correlation between the pollen quantity deposited on the stigma and stigma size, we argue that that the total load of pollen deposited per treatment can obscured what are the main traits in driving heterospecific pollen effect.
-
-Curiously between the species with greater effect sizes, we found completely self incompatible species, species with the smallest stigma and the species with shortes style. Develop more...
-
-Although we have found a positive correlation between phylogenetic distance and heterospecific pollen effect, this results have to be treated carefully.
-From our results we want to highlight that also far related species can affect negatively fitness but the effect from close related is species can also have important detrimental effects.
-Moreover, the effect of close related species can be masked by the possibility of hibridization as it occure between two of our species of Brassica.
-Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors as we have shown in figure xxx.
-These different traits will define how it will be the effect across the different species independently of the nature of the donor and also differently even between species of .
-Although traditionally the nature of the pollen donor have been very studied, the recipient...
-
-Herbs vs tress, annual vs perennial... Many flowers vs few flowered species; structural composition on a system
-
-What are the implications of the findings?
-
-# CONCLUSIONS
-
-# ACKNOWLEDGEMENTS
-
-# REFERENCES
-
-```{r write_citations, cache=FALSE, include=FALSE}
-write.bibtex(file="knitcitations.bib")
-```
-
-<div id = "refs"></div>
-\newpage
-
-# APPENDIX
-
-1.
-
-**Table S1**.
-Perecentage of seeds produced per ovule for the ten species used in the experiment.
-The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-load("table_treatments.RData")
-Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-Cross <- cross
-Self <- self
-Natural_selfing <- nat_self
-Apomixis <- apo
-table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
-kable(table, format="markdown")
-```
-
-2.
-
-**Figure S1**.
-Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
-Pollen was counted for crosses with species of the other two families (N=3).
-To prepare these ratios all the pollen grains on the stigma were counted.
-
-```{r, echo=FALSE, message=FALSE,fig.height=10,fig.width=5, warning=FALSE,fig.cap="Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
-Pollen was counted for crosses with species of the other two families (N=3).
-To prepare these ratios all the pollen grains on the stigma were counted.", cache=FALSE}
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=8,fig.width=5}
 load("pollen_ratio.RData")
@@
 ```
-
-\eleft
-
-\clearpage
-
-\listoftables
+**Figure 8**
 
@@
 
-\newpage
+# List of tables
 
-\clearpage
+**Table 1** Species list with family and genus.
 
-\listoffigures
+# List of figures
 
-\newpage
+**Figure 1** Phylogenetic tree of the species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae.
 
-\newpage
+**Figure 2** Barplot of the different tests of the reproductive biology of the species.
+The y axis is the percentage of ovules converted to seed.
+The different treatments are, hand cross-pollination, hand self-pollination, natural selfing and apomixis (N=10 for all of them).
 
-\blandscape
+**Figure 3** The impact of foreign pollen on recipient plant species. Effect sizes (with 95% confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients.
 
-\elandscape
+**Figure 4** The response of heterospecific pollen upon 10 recipient plant species.  Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species.
 
-\clearpage
+**Figure 5**
+
+**Figure 6**
+
+**Figure 7** (comment) Simple Pearson correlation in order to show a possible path to follow in the article showing that style length and stigma size could explain the effect in Solanaceae species.

### 2019-03-15 Manuscript_draft/Text.Rmd
creating two separated rmd with figures and text I think is the best

--- 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
@@
 ---
-title: Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction
-author:
-- name: Jose B. Lanuza
-  affilnum: 1
-  email: barragansljose@gmail.com
-
-- name: Ignasi Bartomeus
-  affilnum: 2
-
-- name: Tia-Lynn Ashman  
-  affilnum: 3
-
-- name: Romina Rader
-  affilnum: 1
-
-affiliation:
-- affil: University of New England (Australia)
-  affilnum: 1
-- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
-  affilnum: 2
-- affil: Department of Biological Sciences, University of Pittsburgh 4249 Fifth Avenue, Pittsburgh, Pennsylvania 15260-3929 USA
-  affilnum: 3
+title: ''
 output:
-  pdf_document:
-    fig_caption: yes
-    fig_height: 7
-    fig_width: 7
-    includes:
-      in_header: header.tex
-    keep_tex: yes
-    number_sections: no
-    template: manuscript.latex
-  word_document: null
-  html_document: null
-capsize: normalsize
-classoption: a4paper
-csl: ecology.csl
-documentclass: article
-fontsize: 11pt
-footerdate: yes
-geometry: margin=1in
-linenumbers: yes
+  pdf_document: default
+  html_document: default
+header-includes:
+    - \usepackage{setspace}
+    - \doublespacing
+    - \usepackage{lineno}
+    - \linenumbers
 bibliography:
@@
 - knitcitations.bib
-spacing: doublespacing
-abstract: no
 ---
+```{r knitcitations, echo=FALSE, cache = FALSE}
+library(knitcitations)
+cleanbib()   
+cite_options(citation_format = "pandoc")
+```
 
@@
 ```
-
-```{r knitcitations, echo=FALSE, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-```
-
-\singlespace
-
-\vspace{2mm}\hrule
-
-Pollinator sharing can have negative consequences for plant fitness with the arrival of foreign pollen.
-However, the mechanisms underlying the variation in outcomes as a result of pollen contribution by different plant species are not yet well understood.
-We conducted a glasshouse experiment to understand how plant traits and phylogenetic relatedness mediate the impacts of 15 heterospecific pollen transfer.
-We conducted 1800 reciprocal crosses by experimentally transferring pollen (50%  and 100% foreign pollen ratio) between 10 species belonging to three different families: Brassicaceae, Solanaceae and Convolvulaceae.
-Seed set was used as proxy of plant fitness.
-In the treatments of 100% foreign pollen, we found reduced seed set in X% of the treatments.
-In the treatments of 50% foreign pollen, we found reduced seed set in 65% of the treatments.
-Moreover, the reduction in seed set was dependent on the reproductive traits of the pollen recipient, but not the pollen donor or relatedness.
-Our results show that certain traits of recipient plants, particularly compatibility system, are critical in understanding the costs of heterospecific pollen.
-
-\vspace{3mm}\hrule
-
-*Keywords*: heterospecific pollen, plant reproduction, fitness, interspecific competition, phylogenetic distance.
-
-\doublespace
-
-\bleft
 
@@
 
+\newpage
+
 # METHODS
@@
 Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14) and the rooms of the glasshouse were temperature controlled with temperature oscillations between day and night.
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%', fig.cap="Phylogenetic tree of the ten species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae"}
-knitr::include_graphics('images/phylo_image.png')
-```
-
-\newpage
-
-**Table 1** Species list with family and genus.
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))
-
-Genus <- c("Brassica", "Brassica", "Eruca", "Sinapis", "Ipomoea", "Ipomoea", "Capsicum", "Petunia", "Solanum", "Solanum")
-
-Species <- c("Brassica rapa", "Brassica oleracea", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-
-table<- data.frame(Family, Genus, Species)
-kable(table, format="markdown")
-```
-
-\newpage
 
@@
 
-\newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7, fig.cap="Barplot with the different treatments that provide information of the reproductive biology of the ten species.
-The y axis is the proportion of ovules converted to seed in percentage.
-The different treatments (N=10) which are presented in the legend are, hand cross-pollination, hand self-pollination, natural selfing and apomixis.
-More information about these treatments can be found in Methods and Appendices."}
+I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
+Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
+The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
 
-load("r_biology.RData")
-
-ggplot(bio,aes(x=Species,y=value,fill=variable))+
-  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
-  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
-  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))
-
-```
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="The impact of foreign pollen on recipient plant species.
-Effect sizes (with 95%confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}
-
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-load("effect_size_species/effect_size_total.RData")
-
- ggplot(all, aes(Family,Cohen_d,colour=Family_1), size=10) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))+ geom_point( aes(colour=Family_1),size=2) +
-  geom_errorbar(aes(x = Family, ymin = Lower, 
-ymax = Upper,colour=Family_1), width = 0.2, size=0.8, alpha=0.5)+
-  scale_color_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
-  scale_fill_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
-  xlab("") + ylab("Hedges' g") + rotate()+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')
-```
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7,fig.cap="The response of heterospecific pollen upon 10 recipient plant species.
-Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species."}
-
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-load("effect_size_species/all_effect_size.RData")
-
-#BROL
-load("effect_size_species/brol_effect_size.RData")
-p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text(size=10),title = element_text(vjust=2),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",3),"#E69F00"))+
-  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))
-
-#BRRA
-load("effect_size_species/brra_effect_size.RData")
-pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",2),"#E69F00","#0072B2"))+
-  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))
-
-#ERSA
-load("effect_size_species/ersa_effect_size.RData")
-p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",1),"#E69F00", rep("#0072B2",3)))+
-  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic(' E.
-sativa'))))
-
-#SIAL
-load("effect_size_species/sial_effect_size.RData")
-p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2),"#E69F00", rep("#0072B2",3)))+
-  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))
-
-#IPAQ
-load("effect_size_species/ipaq_effect_size.RData")
-p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",1),"#E69F00", rep("#0072B2",4)))+
-  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))
-
-#IPPU
-load("effect_size_species/ippu_effect_size.RData")
-p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
-  theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4),"#E69F00", rep("#009E73",1), rep("#0072B2",4)))+
-  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))
-
-#CAAN
-load("effect_size_species/caan_effect_size.RData")
-p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
-  scale_fill_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))
-
-#PEIN
-load("effect_size_species/pein_effect_size.RData")
-p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_blank(),plot.margin = unit(c(0,0,0,0), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
-  scale_fill_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))
-
-#SOLY
-load("effect_size_species/soly_effect_size.RData")
-p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",1),"#E69F00",rep("#D55E00",2), rep("#009E73",2), rep("#0072B2",4)))+scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))
-
-#SOME
-load("effect_size_species/some_effect_size.RData")
-
-p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(size=1.5,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(size=0.6,alpha=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c("#E69F00",rep("#D55E00",3), rep("#009E73",2), rep("#0072B2",4)))+
-  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))
-
-sp_legend <- readRDS("Data/sp_legend.RData")
-p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
-  xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-grid.newpage()
-
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)}
-
-mylegend<-g_legend(p11)
-
- grid.draw(arrangeGrob(cbind(ggplotGrob(p1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")),size="last"),mylegend,nrow=6))
-#mylegend
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="A"}
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-library(tidyverse)
-
-load("effect_size_species/some_effect_size_family.RData")
-
-pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
-  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/soly_effect_size_family.RData")
-
-pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/sial_effect_size_family.RData")
-
-p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/pein_effect_size_family.RData")
-
-p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/ippu_effect_size_family.RData")
-
-p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/ipaq_effect_size_family.RData")
-
-p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/ersa_effect_size_family.RData")
-
-p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/caan_effect_size_family.RData")
-
-p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/brra_effect_size_family.RData")
-
-p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/brol_effect_size_family.RData")
-
-p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-grid.newpage()
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)}
-leg_family=readRDS("Data/leg_family.RData")
-p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-mylegend<-g_legend(p11)
-
- grid.draw(arrangeGrob(cbind(ggplotGrob(pp1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")), size="last"),mylegend,nrow=6))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.cap="Phylogenetic signal of the average heterospecific pollen effect size per species"}
-library(ape)
-library(phylosignal)
-library(adephylo)
-library(phylobase)
-library(phylosignal)
-library(caret)
-library(ggplot2)
-library(seqHMM)
-library(dplyr)
-library(reshape2)
-pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
-effect_size_all <- readRDS( "Data/effect_size_all.RData")
-#Now rename species
-rownames(effect_size_all) <- c("Solanum_melongena","Solanum_lycopersicum","Petunia_integrifolia", "Capsicum_annuum","Ipomoea_purpurea","Ipomoea_aquatica","Sinapis_alba","Eruca_vesicaria","Brassica_rapa", "Brassica_oleracea")
-hp_mean_sp=effect_size_all[,-c(1,3,4)]
-p4d <- phylo4d(pollen_tree, hp_mean_sp)
-barplot.phylo4d(p4d, center = TRUE , scale = FALSE,trait.labels="Hp effect",bar.col = c(rep("#0072B2",4), rep("#009E73",2), rep("#D55E00",4)))
-```
+Here I show the plot of just solanaceae and then with all the species.
+I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
 
@@
 
+\newpage
+
 # REFERENCES
 
-```{r write_citations, cache=FALSE, include=FALSE}
-write.bibtex(file="knitcitations.bib")
-```
-
 <div id = "refs"></div>
-
-# APPENDIX
-
-1.
-
-**Table S1**.
-Perecentage of seeds produced per ovule for the ten species used in the experiment.
-The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-load("table_treatments.RData")
-Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-Cross <- cross
-Self <- self
-Natural_selfing <- nat_self
-Apomixis <- apo
-table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
-kable(table, format="markdown")
-```
-
-2.
-
-**Figure S1**.
-Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
-Pollen was counted for crosses with species of the other two families (N=3).
-To prepare these ratios all the pollen grains on the stigma were counted.
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-load("pollen_ratio.RData")
-
-ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
-  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-
-ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
-  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-
-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
-  theme(axis.text.x=element_text(angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
-  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-
-```
-
-\eleft
-
-\clearpage
-
-\listoftables
-
-\newpage
-
-\newpage
-
-\clearpage
-
-\listoffigures
-
-\newpage
-
-\newpage
-
-\blandscape
-
-\elandscape
-
-\clearpage

### 2019-03-15 Manuscript_draft/Tables_and_figures.Rmd
text edits and plot of total pollen to tables and figures

@@
 \newpage
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=8,fig.width=5}
+load("Data/total_pollen.RData")
+library(ggpubr)
+library(ggplot2)
+library(gridExtra)
+library(grid)
+
+p1 <- ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Total pollen")
+
+p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Total pollen")
+
+p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
+  geom_hline(yintercept = 50) + xlab("") + ylab("Total pollen")
+grid.arrange(p1, p2,p3, nrow = 3, ncol=1)
+
+```
+**Figure 9**
+
+\newpage
 

### 2019-03-16 Manuscript_draft/Tables_and_figures.Rmd
edits

--- 2019-03-15 Manuscript_draft/Tables_and_figures.Rmd
@@
 \newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=8,fig.width=5}
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
 load("pollen_ratio.RData")
@@
 \newpage
+```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
+load("Data/total_pollen.RData")
+library(ggpubr)
+library(ggplot2)
+library(gridExtra)
+library(grid)
+
+p1 <- ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
+
+p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
+
+p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
+grid.arrange(p1, p2,p3, nrow = 3, ncol=1)
+
+```
+**Figure 9**
+
+\newpage
 
@@
 
-**Figure 6**
+**Figure 6** Phylogenetic signal of hterospecific pollen effect (hedges' g)
 
 **Figure 7** (comment) Simple Pearson correlation in order to show a possible path to follow in the article showing that style length and stigma size could explain the effect in Solanaceae species.
+
+**Figure 8** Pollen ratio counts on stigma after hand pollination with 50-50% mix.
+The panel is divided by family: A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+The pollen recipient species is coloured in black and the donor species in grey.
+
+**Figure 9** Total pollen counts on stigma after hand pollination with 50-50% mix.
+The panel is divided by family: A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+The pollen recipient species is coloured in black and the donor species in grey.

### 2019-03-16 Manuscript_draft/Tables_and_figures.Rmd
order plot 8 and 9

@@
   geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-grid.arrange(p1, p2,p3, nrow = 3, ncol=1)
+grid.arrange(p1, p3,p2, nrow = 3, ncol=1)
 
@@
   theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
-grid.arrange(p1, p2,p3, nrow = 3, ncol=1)
+grid.arrange(p1, p3,p2, nrow = 3, ncol=1)
 
@@
 **Figure 8** Pollen ratio counts on stigma after hand pollination with 50-50% mix.
-The panel is divided by family: A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+The panel is divided by family: A) Brassicaceae, B) Convolvulaceae and C) Solanaceae.
 The pollen recipient species is coloured in black and the donor species in grey.
@@
 **Figure 9** Total pollen counts on stigma after hand pollination with 50-50% mix.
-The panel is divided by family: A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+The panel is divided by family: A) Brassicaceae, B) Convolvulaceae and C) Solanaceae.
 The pollen recipient species is coloured in black and the donor species in grey.

### 2019-03-16 Manuscript_draft/Text.Rmd
text edits and plot of total pollen to tables and figures
text edits draft

@@
 
-Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented in **Figure 1** (see appendix 1 for table with values).
+Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented for all the species in **Figure 1** (see appendix 1 for table with values).
 Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-Moreover, average effect sizes differed across species and across families, see **Figure 2**.
-Despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**), just for four species out of ten, just one donor did not overlap the confidence intervals with other donors.
+
+[Add values of pollen counted](Jose)
+
+The grouped effect size of the nine donors per species differed across species and families (see **Figure 2**).
+Interestingly, despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**).
+Just for four species out of ten, just one donor in each did not overlap the confidence intervals with other donors.
 Therefore, none of the donors had a clear stronger or weaker effect across species.
-When the donors were groped by family not big differences were seen, just for *S.
+When the donors were grouped by family we found a similar effect too, just for *S.
 lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**).
@@
 
+[add numeric values for 100% seed production](Jose)
+
 Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05).
@@
 Although with a lack of a significant correlation pagel's lambda values were also relatively high (>0.45) for incompatibility index, ovary length and levels of selfing.
-Moreover, Mantel test between heterospecific pollen effect and traits gave also a positive significant correlation with a  r value of 0.4.
+
+Moreover, Mantel test between heterospecific pollen effect and the distance matrix of traits gave also a positive significant correlation with r value of 0.4.
 When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect.
+When the effect of heterospecific pollen was just looked at family level, for Solanaceae species we found a negative correlation between style length and heterospecific pollen effect (Figure 7).
 
 [explain ratios and total pollen](Jose)
-[add table with morphometrical traits to appendix]()
-
-I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
-Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
-The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
-
-Here I show the plot of just solanaceae and then with all the species.
-I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
+[add table with morphometrical traits to appendix](Jose)
 
@@
 
-supporting ideas: 
-Species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from Whitehead et al. (2018)).
-
-Interestingly the effect of the different donors per species were very homogeneous which lead us to think that the female reproductive traits of the pollen recipient are the main ones in explaining heterospecific pollen effect.
-Our main predictive trait of effect is stigma size, and because we found a correlation between the pollen quantity deposited on the stigma and stigma size, we argue that that the total load of pollen deposited per treatment can obscured what are the main traits in driving heterospecific pollen effect.
-
-Curiously between the species with greater effect sizes, we found completely self incompatible species, species with the smallest stigma and the species with shortes style. Develop more...
-
-Although we have found a positive correlation between phylogenetic distance and heterospecific pollen effect, this results have to be treated carefully.
-From our results we want to highlight that also far related species can affect negatively fitness but the effect from close related is species can also have important detrimental effects.
-Moreover, the effect of close related species can be masked by the possibility of hibridization as it occure between two of our species of Brassica.
-Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors as we have shown in figure xxx.
-These different traits will define how it will be the effect across the different species independently of the nature of the donor and also differently even between species of .
-Although traditionally the nature of the pollen donor have been very studied, the recipient...
+The uniform effect of the different donors across the ten different species is a novel result to highlight in the understanding of heterospecific pollen effect.
+Traditionally, the nature of the pollen donor has been considered highly relevant to understand the outcomes of the pairwise interaction.
+However, this result support the idea that the pollen recipient traits are the main determinats of the effect and not the donor ones.
 
@@
 
-What are the implications of the findings?
+supporting ideas: 
+Species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from Whitehead et al. (2018)).
 

### 2019-03-16 Manuscript_draft/Text.Rmd
adding to results pollen ratios

@@
 
-Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented for all the species in **Figure 1** (see appendix 1 for table with values).
+Results of hand cross-pollination, hand self-pollination, natural selfing and apomixis are presented for all the species in **Figure 1** (see **Appendix 1** for table with values).
 Heterospecific pollen reduced seed set significatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05.
-
-[Add values of pollen counted](Jose)
+Brassicaceae and Solanaceae species had less foreign pollen than expected, the ratios of pollen of recipient and donor respectively for both families were 80-20% and 60.5-39.5%.
+In contrast, Convolvulaceae species had just 28% recipient pollen and 72% of donor pollen.
+In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production.
+However, for just one species (*S.
+alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
+For two Solanaceae species *S.
+melongena* and *C.
+annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.
 
@@
 lycopersicum* the confidence intervals of Brassicaceae and Convolvulaceae did not overlap (see **Figure 4**).
-In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production.
-However, for just one species (*S.
-alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
-For two Solanaceae species *S.
-melongena* and *C.
-annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.
 
@@
 
+Caveats:
+
 Herbs vs tress, annual vs perennial... Many flowers vs few flowered species; structural composition on a system

### 2019-03-17 Manuscript_draft/Tables_and_figures.Rmd
table of seed production with 100% pollen
edits on table headers

@@
 ```
+\newpage
+
+**Table 2**
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+load("table_treatments.RData")
+Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+Cross <- cross
+Self <- self
+Natural_selfing <- nat_self
+Apomixis <- apo
+table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
+kable(table, format="markdown", caption= "Perecentage of seeds produced per ovule for the ten species used in the experiment.
+The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
+",longtable = TRUE)
+```
+
+\newpage
+
+**Table 3**
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+dat_all <- readRDS("Data/dat_all.RData")
+kable(dat_all, format="markdown", caption = "a")
+
+```
+
 \newpage
@@
 
+**Table 2** Results of hand corss-pollination, hand self-pollination, natural selfing (unpollinated bagged flowers) and apomixis.
+The values are the average seed production per treatment (N=10) divided by the average number of ovules per species.
+
+**Table 3** Seed production for the treatments that produced seeds with 100% foeign pollen.
+
 # List of figures

### 2019-03-17 Manuscript_draft/Tables_and_figures.Rmd
change in figure

@@
 p2 <- ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Solanaceae") +
   theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
@@
 p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Convolvulaceae") +
   theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
@@
 p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="B) Solanaceae") +
+  geom_bar(stat='identity', position='dodge') +labs(title="C) Solanaceae") +
   theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
@@
 p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="C) Convolvulaceae") +
+  geom_bar(stat='identity', position='dodge') +labs(title="B) Convolvulaceae") +
   theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
@@
 
-**Table 3** Seed production for the treatments that produced seeds with 100% foeign pollen.
+**Table 3** Seed production for the treatments that produced seeds with 100% foreign pollen.
 

### 2019-03-17 Manuscript_draft/Tables_and_figures.Rmd
edits panel family effect sizes

@@
 
+load("effect_size_species/brol_effect_size_family.RData")
+
+pp1<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))
+
+load("effect_size_species/brra_effect_size_family.RData")
+
+pp2<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))
+
+load("effect_size_species/ersa_effect_size_family.RData")
+
+p3<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("C)",italic(' E. sativa'))))
+
+load("effect_size_species/sial_effect_size_family.RData")
+
+p4<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))
+
+load("effect_size_species/ipaq_effect_size_family.RData")
+
+p5<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))
+
+load("effect_size_species/ippu_effect_size_family.RData")
+
+p6<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))
+
+load("effect_size_species/caan_effect_size_family.RData")
+
+p7<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))
+
+load("effect_size_species/pein_effect_size_family.RData")
+
+p8<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))
+
+load("effect_size_species/soly_effect_size_family.RData")
+
+p9<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))
+
 load("effect_size_species/some_effect_size_family.RData")
 
-pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
+p10<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
   geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
@@
   xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/soly_effect_size_family.RData")
-
-pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/sial_effect_size_family.RData")
-
-p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/pein_effect_size_family.RData")
-
-p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/ippu_effect_size_family.RData")
-
-p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/ipaq_effect_size_family.RData")
-
-p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/ersa_effect_size_family.RData")
-
-p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/caan_effect_size_family.RData")
-
-p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/brra_effect_size_family.RData")
-
-p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("effect_size_species/brol_effect_size_family.RData")
-
-p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
+  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))
 

### 2019-03-18 Manuscript_draft/Text.Rmd
edits before sending draft to all supervisors

@@
 Pollen size, pollen aperture number and pollen allelopathy are thought to be key components in understanding the outcome of foreign pollen arrival @murphy1995; @ashman2013.
-For example, small pollen is predicted to decrease plant fitness because XXXXXX.
+For example, small pollen is predicted to decrease plant fitness because is more likely to clogg the stigmatic surface.
 Yet, large pollen can outcompete smaller pollen grains due to faster pollen tube growth rate @williams1990.
@@
 Further, species that are self-incompatible are thought to be more resistant to the negative impacts of heterospecific pollen than self-compatible species @ashman2013.
-
 When both donor and recipient traits are considered together, other combinations of traits are also likely to impact plant fitness.
-For example, large pollen grains could potentially clog small stigmas with fewer pollen grains, and larger stigmas are less likely to be clogged by small pollen grains.
+For example, large pollen grains could potentially clog small stigmas with fewer pollen grains, and larger stigmas are less likely to be clogged by small pollen grains @galen1989.
 Yet, few studies have considered how effects might differ among donor and recipient species.
@@
 Closely related species are more likely to have similar  traits @letten2015.
-The similarity in traits between closely related species can lead tohigher chances of ovule usurpation/abortion @arceo2011 hence, greater negative effects of HP pollen are thought to be a associated with more closely related species @ashman2013; @arceo2016.
+The similarity in traits between closely related species can lead to higher chances of ovule usurpation/abortion @arceo2011 hence, greater negative effects of heterospecific pollen are thought to be a associated with more closely related species @ashman2013; @arceo2016.
 Few studies however, have focused on the impacts of heterospecific pollen on fitness of distantly related species @galen1989; @neiland1999 and those that have, often report low sample sizes and a lack of significance.
@@
 Moreover, the species selected had fast life cycle and low structural flower complexity in order to perform the pollination treatments and grow the different species from seeds.
-For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor (see interaction matrix, fig 2).
+For the purpose of the experiment all the species where considered as pollen recipient and as pollen donor.
 Species were watered once or twice per day and fertilized weekly (NPK 23: 3.95: 14) and the rooms of the glasshouse were temperature controlled with temperature oscillations between day and night.
@@
 Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation.
-Therefore, we perfomed 180 different heterospecific treatments (N=10).
+We perfomed 180 different heterospecific treatments in total (N=10).
 Seed set was the proxy of effect for all our treatments.
@@
 Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.
+The anthers were mixed in tubes of 0.5/1.5 ml and shaked with an electric toothbrush without the head on the outside bottom part of the tube for a correct mix.
+For the species with buzz-pollination, *S.
+lycopersicum* and *S.
+melongena*, same procedure with an electric toothbrush was used in order to extract the pollen directly into the tubes, the apllication of it was at the bottom of the corolla/receptacule.
 To confirm that the treatments applied were the desire proportions, the total stigmatic load of pollen was counted and the proportions calculated between the two species of the mix.
@@
 
-To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD] with **effsize** package.
+To compare the magnitude of effect of heterospecific pollen across species we conducted standarized Hedges' d [(mean of mixed 50% mix - mean of cross pollination)/pooled SD] with *effsize* package.
 We did in three different ways: effect sizes of each donor per focal species; effect sizes per family of the different donors per focal species; effect sizes of all the donors grouped per focal species.
@@
 
-In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (**vegan** package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
+In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (*vegan* package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
 Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
-To find a model with the best explanatory traits we used the function **bioenv** from R.
+To find a model with the best explanatory traits for heterospecific pollen effect we used the function *bioenv* from R which finds the maximum rank of correlation among a subset of variables.
 We also conducted Mantel test between the matrix of heterospecific pollen effect and the distance matrix from all the traits.
@@
 In addition, we tested the correlation between the total amount of pollen deposited on the stigma with heterospecific pollinations and the stigma size through Pearson's correlation.
-
-[Phylogenetic signal of traits?](Jose)
-
-Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008.
-Proportions of pollen talk about it to 50-50 mix?
-Talk aboout this in methods too.
-
-Also the plots of ratios to appendices.
-
-NMDS to appendix?
 
@@
 
+Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008.
+Proportions of pollen talk about it to 50-50 mix?
+Talk aboout this in methods too.
+
+NMDS to appendix?
+
 # DISCUSSION

### 2019-03-18 Manuscript_draft/Text.Rmd
trying to add more results

@@
 In contrast, Convolvulaceae species had just 28% recipient pollen and 72% of donor pollen.
-In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production.
+In addition, for the 100% hetrospecific pollen treatments we did not find almost seed production (see *Table 3* for 100% treatments that produced seeds).
 However, for just one species (*S.
-alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production.
-For two Solanaceae species *S.
+alba*) the control pollination and the heterospecific pollination with pollen from a confamilial had similar seed production (non significant differences).
+Moreover, for two Solanaceae species *S.
 melongena* and *C.
-annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments.
+annuum* 100% pollen treatments produced few seedles fruits (3% and 9% respectively) and they did not for the apomictic treatments indicating that foreing pollen can be responsible of seedless fruit production.
 
-The grouped effect size of the nine donors per species differed across species and families (see **Figure 2**).
-Interestingly, despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous (see **Figure 3**).
-Just for four species out of ten, just one donor in each did not overlap the confidence intervals with other donors.
+The grouped effect sizes of the nine donors per species differed across species and families (see **Figure 2**), having clear statistical differences for species within and across families with not overlapping confidence intervals.
+Interestingly, despite some variability in the effect of the different pollen donors per species, in general terms the effect of heterospecific pollen from the distinct nine treatments per species was homogeneous with unclear statistical differences (see **Figure 3**).
+Just for four species out of ten, just one donor in each did not have overlapping confidence intervals with the rest of the donors.
 Therefore, none of the donors had a clear stronger or weaker effect across species.
@@
 
-[add numeric values for 100% seed production](Jose)
+Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances.
 
-Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a positive statistically clear correlation for both markers (p<0.05).
+[Add Bioenv results](Jose)
+
+The same analysis of Mantel test between HP pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area).
+When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a strong negative non significant correlation between style length and heterospecific pollen effect (Pearson's correlation=0.93, p=0.07) (see **Figure 7**).
+
+Results of Mantel test between heterospecific pollen effect and phylogenetic distance gave a low positive correlation for both markers (p<0.05).
 The correlations with ITS and RBCL markers was respectively of 0.29 and 0.25.
@@
 Although with a lack of a significant correlation pagel's lambda values were also relatively high (>0.45) for incompatibility index, ovary length and levels of selfing.
-
-Moreover, Mantel test between heterospecific pollen effect and the distance matrix of traits gave also a positive significant correlation with r value of 0.4.
-When the effect was look trait by trait with Mantel test, stigma type and stigma measurements (length, width and area) gave a significant positive correlation with heterospecific pollen effect.
-When the effect of heterospecific pollen was just looked at family level, for Solanaceae species we found a negative correlation between style length and heterospecific pollen effect (Figure 7).
 

### 2019-03-18 Manuscript_draft/Text.Rmd
last results added to draft

@@
 
-In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (*vegan* package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the different distance matrices of traits.
+In order to test the relative effect of traits on seed production with foreign pollen we performed Mantel test in R (*vegan* package, Euclidean distance) between the assymetrical matrix of heterospecific pollen effect (10 by 10 matrix) with the distance matrix of traits.
+Furthermore, the same analysis was conducted trait by trait in order to disentangled the specific effect of each trait.
+The correlation between heterospecific effect and traits was also looked at family level for Brassicaceae and Solanaceae species The family Convolvulaceae did not have enough species to test correlation with traits though Mantel test.
 Heterospecific pollen effect was obtained through the subtraction of seed production by hand cross-pollination minus seed production of the different heterospecific pollen treatments.
@@
 
-Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances.
-
-[Add Bioenv results](Jose)
-
-The same analysis of Mantel test between HP pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area).
-When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a strong negative non significant correlation between style length and heterospecific pollen effect (Pearson's correlation=0.93, p=0.07) (see **Figure 7**).
+Matrices of heterospecifc pollen effect and traits (Distance matrix of traits, euclidean distance) are positively and significantly correlated (r=0.4, one-tailed Mantel test p<0.05).The variable/s with maximum rank correlation (thorugh *Bioenv* funtion) was incompatibility index by itself within a group of 16 variables calculated with euclidean distances.
+The same analysis of Mantel test between heterospecific pollen effect and the traits one by one gave a positive and significant correlation for stigma type and stigma measurements (length, width and area).
+When the effect of heterospecific pollen was looked at family level, for Solanaceae species we found a positive and significant correlation between heterospecific pollen effect and pollen-ovule ratio
+(r=0.74, one-tailed Mantel test p<0.05).
+Moreover, it seems to be a strong negative correlation between style length and heterospecific pollen effect although lack of significance (Pearson's correlation=0.93, p=0.07) (see **Figure 7**).
+For Brassicaceae species, the distance matrix of ovules and heterospecic pollen effect gave a positive and significant correlation (r=0.4, one-tailed Mantel test p<0.05).
 

### 2019-03-18 Manuscript_draft/Text.Rmd
last edits before sending draft

@@
 For Brassicaceae species, the distance matrix of ovules and heterospecic pollen effect gave a positive and significant correlation (r=0.4, one-tailed Mantel test p<0.05).
+Separate to this, the stigmatic area and pollen grain number per stigma were positively correlated, (pearson's correlation=0.57, p<0.01).
 
@@
 
-[explain ratios and total pollen](Jose)
-[add table with morphometrical traits to appendix](Jose)
+add table with morphometrical traits to appendix (Jose)
+NMDS to appendix?
 
 \newpage
-
-Total pollen deposited on stigmas was significantly correlated with the stigmatic area, pearsons correlation=0.57 and p-value=0.008.
-Proportions of pollen talk about it to 50-50 mix?
-Talk aboout this in methods too.
-
-NMDS to appendix?
 

### 2019-04-08 Manuscript_draft/Text.Rmd
edits

@@
 title: ''
-output:
-  pdf_document: default
-  html_document: default
 header-includes:
@@
 - \linenumbers
+output:
+  word_document: default
+  pdf_document: default
+  html_document: default
 bibliography:

### 2019-05-22 pollen_family.Rmd
edits

---
title: ""
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
par(mar=c(7,13,2,5),xpd=F)
data_percentage <-readRDS("Rmd/Data/per.RData")
data_percentage=as.matrix(data_percentage)
coul = c("#999999","#779799")
barplot(data_percentage,hor=T,col=coul ,space=1, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
 "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
  abline(v=50,col="black")

```

### 2019-05-22 pollen_family.Rmd
plot 50-50%

@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
-par(mar=c(7,13,2,5),xpd=F)
+par(mar=c(30,13,2,4),xpd=F)
 data_percentage <-readRDS("Rmd/Data/per.RData")
@@
 coul = c("#999999","#779799")
-barplot(data_percentage,hor=T,col=coul ,space=1, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
+barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
  "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
@@
 
+#lines(c(0,10),50,col="red")
 ```
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+par(mar=c(30,13,2,4),xpd=F)
+ratio_bra <-readRDS("Rmd/Data/ratio_bra.RData")
+barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E. sativa-I. purpurea",
+  "B. oleracea-I. purpurea","B. rapa-I. purpurea","S. alba-I. aquatica", "S. alba-S. melongena", "E. sativa-P. integrifolia", "B. rapa-S. lycopersicum", "B. oleracea-C. annuum"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+
+```
+
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+par(mar=c(30,13,2,4),xpd=F)
+ratio_sol <-readRDS("Rmd/Data/ratio_sol.RData")
+barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
+annuum-I.
+purpurea", "S.
+melongena-I.
+aquatica", "P.
+integrifolia-I.
+aquatica", "S.
+lycopersicum-I aquatica","S.
+melongena-E.
+sativa", "P.
+integrifolia-E.
+sativa", "C.
+annuum-S.
+alba", "S.
+lycopersicum-B.
+rapa"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+
+```
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+par(mar=c(30,13,2,4),xpd=F)
+ratio_con <-readRDS("Rmd/Data/ratio_con.RData")
+barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I.
+purpurea-S.
+melongena","I.
+aquatica-C.
+annuum","I.
+purpurea-E.
+sativa","I.
+aquatica-S.
+alba"))
+abline(v=50,col="black")
+legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
+
+```
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+par(mar=c(2,13,2,4),xpd=F)
+par(mfrow=c(3,1))
+ratio_sol <-readRDS("Rmd/Data/ratio_sol.RData")
+barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
+annuum-I.
+purpurea", "S.
+melongena-I.
+aquatica", "P.
+integrifolia-I.
+aquatica", "S.
+lycopersicum-I aquatica","S.
+melongena-E.
+sativa", "P.
+integrifolia-E.
+sativa", "C.
+annuum-S.
+alba", "S.
+lycopersicum-B.
+rapa"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+ratio_con <-readRDS("Rmd/Data/ratio_con.RData")
+barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I.
+purpurea-S.
+melongena","I.
+aquatica-C.
+annuum","I.
+purpurea-E.
+sativa","I.
+aquatica-S.
+alba"))
+abline(v=50,col="black")
+legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
+
+ratio_sol <-readRDS("Rmd/Data/ratio_sol.RData")
+barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
+annuum-I.
+purpurea", "S.
+melongena-I.
+aquatica", "P.
+integrifolia-I.
+aquatica", "S.
+lycopersicum-I aquatica","S.
+melongena-E.
+sativa", "P.
+integrifolia-E.
+sativa", "C.
+annuum-S.
+alba", "S.
+lycopersicum-B.
+rapa"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+```

### 2019-05-22 pollen_family.Rmd
pollen ratio plot edits, seems much cooler now!

@@
 legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+text(8.3,6.8,"A) Brassicaceae")
 ratio_con <-readRDS("Rmd/Data/ratio_con.RData")
@@
 legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
+text(9,3.5,"B) Convolvulaceae")
 
@@
 legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+text(6.8,6.8,"C) Solanaceae")
+
 ```

### 2019-05-22 pollen_family.Rmd
plots of pollen ratio and total pollen modified, everything organised in pollen_family.Rmd

@@
 ```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+library(ggplot2)
+total_pollen <- read.csv("Rmd/Data/total_pollen.csv")
+ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
+  geom_bar(stat='identity', position='dodge')+theme_minimal()+
+  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
+  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")
+
+```

### 2019-05-22 Scripts/Traits/total_pollen_stigma.R

@@ -52,7 +52,7 @@ total_pollen$spp <- paste(total_pollen$focal,total_pollen$non_focal, sep="-")
 write.csv(total_pollen, "Data/total_pollen.csv")
 write.csv(total_pollen, "Rmd/Data/total_pollen.csv")
 
-
+coul = c("#999999","#779799")
 ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable)) +
   geom_bar(stat='identity', position='dodge')+theme(axis.text.x=element_text(angle=60,hjust=1))
 
@@ -202,6 +202,9 @@ d<- data.frame(pollen,treatment,b)
 ggplot(d, aes(x = factor(treatment), fill = (pollen))) +
   geom_bar()
 
+barplot(d, col=coul , border="white", xlab="group",ylim=c(0,2000))
+
+
 #create color palette:
 library(RColorBrewer)
 coul = c("#999999","#779799")
@@ -222,8 +225,91 @@ data_percentage=apply(a, 2, function(x){x*100/sum(x,na.rm=T)})
 par(mar=c(7,10,2,5),xpd=T)
 
 saveRDS(data_percentage,"Rmd/Data/per.RData")
-barplot(data_percentage, hor=T,col=coul ,space=0.8, border="white",srt=80,las=1,cex.axis=0.7,cex.names=0.6,names=c("Brassicaceae-Convolvulaceae",
+barplot(a, hor=T,col=coul ,space=0.8, border="white",srt=80,las=1,cex.axis=0.7,cex.names=0.6,names=c("Brassicaceae-Convolvulaceae",
  "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
 
 legend(legend=c("recipient","donor"),bty="n",fill = c("#999999","#779799"))
+
+#Prepare same style plot pollen ratios but with pollen quantities...
+
+#Brassicaceae
+total_pollen <- read.csv("Data/total_pollen.csv")
+total_pollen_brassicaceae <- total_pollen[total_pollen$focal!="I. purpurea" & total_pollen$focal!="I. aquatica"& total_pollen$focal!="S. melongena"&
+                                            total_pollen$focal!="S. lycopersicum" & total_pollen$focal!="P. integrifolia"& total_pollen$focal!="C. annuum",  ]
+
[…]

### 2019-05-24 Manuscript_draft/Tables_and_figures.Rmd
edits before sending draft to all supervisors
edits

@@
 load("effect_size_species/effect_size_total.RData")
+Family_1<-c("#D55E00","#009E73","#0072B2")
+all$Family_1=as.character(all$Family_1)
+all$Family_1[all$Family_1=="B"]<-"X"
+all$Family_1[all$Family_1=="S"]<-"B"
+all$Family_1[all$Family_1=="X"]<-"S"
 
@@
 ymax = Upper,colour=Family_1), width = 0.2, size=0.8, alpha=0.5)+
-  scale_color_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
-  scale_fill_manual(name  ="Family",values=c( "#0072B2", "#009E73", "#D55E00"), labels=c("Solanaceae", "Convolvulaceae","Brassicaceae"))+
+  scale_color_manual(name  ="Family",values=c("#0072B2","#009E73","#D55E00"), labels=c("Brassicaceae","Convolvulaceae","Solanaceae"))+
+  scale_fill_manual()+
   xlab("") + ylab("Hedges' g") + rotate()+
@@
 sp_legend <- readRDS("Data/sp_legend.RData")
-p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
+p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#E69F00","#D55E00"))+ scale_fill_manual("Family",values=c("#0072B2",  "#009E73", "#E69F00","#D55E00"))+
   xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
@@
 leg_family=readRDS("Data/leg_family.RData")
-p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#D55E00","#009E73","#E69F00","#0072B2"))
+p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#E69F00",  "#009E73", "#D55E00","#E69F00"))
  #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
@@
 
-**Figure 5**
+**Figure 5** The impact of foreign pollen on recipient plant species. Effect sizes (with 95% confidence intervals) of the species grouped per family upon all recipients.
 

### 2019-05-27 Manuscript_draft/results_mantel_trait.Rmd
New table with with r and p values from Mantel between matrix of hp and distance matrix trait by trait

---
title: "Untitled"
output: pdf_document
---
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(vegan)
library(kableExtra)
load("img_for_traits.Rdata")
a_1 <- mantel(matrix_scale_effect, traits_self_dist)
a_2 <- mantel(matrix_scale_effect, pollen_size_dist)
a_3 <- mantel(matrix_scale_effect, pollen_dist)
a_4 <- mantel(matrix_scale_effect, ovules_dist)
a_5 <- mantel(matrix_scale_effect, p_o_ratio_dist)
a_6 <- mantel(matrix_scale_effect, stigma_area_dist)
a_7 <- mantel(matrix_scale_effect, stigma_length_dist)
a_8 <- mantel(matrix_scale_effect, stigma_width_dist)
a_9 <- mantel(matrix_scale_effect, style_length_dist)
a_10 <- mantel(matrix_scale_effect, style_width_dist)
a_11 <- mantel(matrix_scale_effect, ovary_length_dist)
a_12 <- mantel(matrix_scale_effect, ovary_width_dist)
a_13 <- mantel(matrix_scale_effect, traits_si_index_dist)

r <- c(as.numeric(a_1[3]),as.numeric(a_2[3]),as.numeric(a_3[3]),as.numeric(a_4[3]),as.numeric(a_5[3]),as.numeric(a_6[3]),as.numeric(a_7[3]),as.numeric(a_8[3]),as.numeric(a_9[3]),as.numeric(a_10[3]),as.numeric(a_11[3]),as.numeric(a_12[3]),as.numeric(a_13[3]))

p <- c(as.numeric(a_1[4]),as.numeric(a_2[4]),as.numeric(a_3[4]),as.numeric(a_4[4]),as.numeric(a_5[4]),as.numeric(a_6[4]),as.numeric(a_7[4]),as.numeric(a_8[4]),as.numeric(a_9[4]),as.numeric(a_10[4]),as.numeric(a_11[4]),as.numeric(a_12[4]),as.numeric(a_13[4]))

Trait<- c("Selfing rate", "Pollen size", "Pollen per anther", " Number of ovules", "Pollen-ovule ratio", "**Stigmatic area**", "**Stigma length**", "**Stigma width**", "Style length", "Style width", "Ovary length", "Ovary width", "Self incompatibility index")
table<- data.frame(r,p, Trait)
kable(table, format="markdown", digits = 2)

```

### 2019-05-27 Manuscript_draft/results_mantel_trait.Rmd
table of results for both families trait by trait ( Mantel)

@@
 ```
+
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(vegan)
+library(kableExtra)
+load("Data/family_cor.Rdata")
+#solanaceae
+dist_selfing <- dist(traits_sola[,2])
+dist_pollen_size <- dist(traits_sola[,3])
+dist_pollen_anther <- dist(traits_sola[,4])
+dist_ovules <- dist(traits_sola[,5])
+dist_pollen_ovule <- dist(traits_sola[,6])
+dist_stigmatic_area <- dist(traits_sola[,8])
+dist_stigma_length <- dist(traits_sola[,9])
+dist_stigma_width <- dist(traits_sola[,10])
+dist_style_length <- dist(traits_sola[,12])
+dist_style_width <- dist(traits_sola[,13])
+dist_ovary_width <- dist(traits_sola[,14])
+dist_ovary_length <- dist(traits_sola[,15])
+dist_si_index <- dist(traits_sola[,16])
+
+b_1 <- mantel(matrix_soly, dist_selfing)
+b_2 <- mantel(matrix_soly, dist_pollen_size)
+b_3 <- mantel(matrix_soly, dist_pollen_anther)
+b_4 <- mantel(matrix_soly, dist_ovules)
+b_5 <- mantel(matrix_soly, dist_pollen_ovule)
+b_6 <- mantel(matrix_soly, dist_stigmatic_area)
+b_7 <- mantel(matrix_soly, dist_stigma_length)
+b_8 <- mantel(matrix_soly, dist_stigma_width)
+b_9 <- mantel(matrix_soly, dist_style_length)
+b_10 <- mantel(matrix_soly, dist_style_width)
+b_11 <- mantel(matrix_soly, dist_ovary_length)
+b_12 <- mantel(matrix_soly, dist_ovary_width)
+b_13 <- mantel(matrix_soly, dist_si_index)
+
+dist_selfing <- dist(traits_brra[,2])
+dist_pollen_size <- dist(traits_brra[,3])
+dist_pollen_anther <- dist(traits_brra[,4])
+dist_ovules <- dist(traits_brra[,5])
+dist_pollen_ovule <- dist(traits_brra[,6])
+dist_stigmatic_area <- dist(traits_brra[,8])
+dist_stigma_length <- dist(traits_brra[,9])
+dist_stigma_width <- dist(traits_brra[,10])
+dist_style_length <- dist(traits_brra[,12])
+dist_style_width <- dist(traits_brra[,13])
+dist_ovary_width <- dist(traits_brra[,14])
+dist_ovary_length <- dist(traits_brra[,15])
+dist_si_index <- dist(traits_brra[,16])
+
+c_1 <- mantel(matrix_brra, dist_selfing)
+c_2 <- mantel(matrix_brra, dist_pollen_size)
+c_3 <- mantel(matrix_brra, dist_pollen_anther)
+c_4 <- mantel(matrix_brra, dist_ovules)
+c_5 <- mantel(matrix_brra, dist_pollen_ovule)
+c_6 <- mantel(matrix_brra, dist_stigmatic_area)
+c_7 <- mantel(matrix_brra, dist_stigma_length)
+c_8 <- mantel(matrix_brra, dist_stigma_width)
+c_9 <- mantel(matrix_brra, dist_style_length)
+c_10 <- mantel(matrix_brra, dist_style_width)
+c_11 <- mantel(matrix_brra, dist_ovary_length)
+c_12 <- mantel(matrix_brra, dist_ovary_width)
+c_13 <- mantel(matrix_brra, dist_si_index)
+
+r <- c(as.numeric(b_1[3]),as.numeric(b_2[3]),as.numeric(b_3[3]),as.numeric(b_4[3]),as.numeric(b_5[3]),as.numeric(b_6[3]),as.numeric(b_7[3]),as.numeric(b_8[3]),as.numeric(b_9[3]),as.numeric(b_10[3]),as.numeric(b_11[3]),as.numeric(b_12[3]),as.numeric(b_13[3]),as.numeric(c_1[3]),as.numeric(c_2[3]),as.numeric(c_3[3]),as.numeric(c_4[3]),as.numeric(c_5[3]),as.numeric(c_6[3]),as.numeric(c_7[3]),as.numeric(c_8[3]),as.numeric(c_9[3]),as.numeric(c_10[3]),as.numeric(c_11[3]),as.numeric(c_12[3]),as.numeric(c_13[3]))
+
+p <- c(as.numeric(b_1[4]),as.numeric(b_2[4]),as.numeric(b_3[4]),as.numeric(b_4[4]),as.numeric(b_5[4]),as.numeric(b_6[4]),as.numeric(b_7[4]),as.numeric(b_8[4]),as.numeric(b_9[4]),as.numeric(b_10[4]),as.numeric(b_11[4]),as.numeric(b_12[4]),as.numeric(b_13[4]),as.numeric(c_1[4]),as.numeric(c_2[4]),as.numeric(c_3[4]),as.numeric(c_4[4]),as.numeric(c_5[4]),as.numeric(c_6[4]),as.numeric(c_7[4]),as.numeric(c_8[4]),as.numeric(c_9[4]),as.numeric(c_10[4]),as.numeric(c_11[4]),as.numeric(c_12[4]),as.numeric(c_13[4]))
+
+Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "**Pollen-ovule ratio**", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "Self incompatibility index","Selfing rate", "Pollen size", "Pollen per anther", "**Number of ovules**", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "Self incompatibility index")
+
+Family<- c(rep("Solanaceae",13),rep("Brassicaceae",13))
+
+table<- data.frame(r,p, Trait, Family)
+kable(table, format="markdown", digits = 2)
+
+```

### 2019-06-03 Manuscript_draft/Results.Rmd
edits

@@
 
-lambda <- c(stigma_type[1], selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_surface[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1])
+lambda <- c(stigma_type[1], selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_surface[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1], si_index[1])
 lambda<- as.numeric(lambda)
-p <- c(stigma_type[4], selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_surface[4], stigma_width[4], style_length[1], style_width[1], ovary_length[1], ovary_width[1])
+p <- c(stigma_type[4], selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_surface[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4],si_index[4])
 p <- as.numeric(p)
@@
 table<- data.frame(lambda,p, trait)
+colnames(table) <- c("Lambda", "P-value", "Traits")
 kable(table, format="markdown")

### 2019-06-03 Manuscript_draft/phylo_signal_table.Rmd
edits

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}

library(kableExtra)
load("Data/img_phylo.RData")

lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
lambda<- as.numeric(lambda)
p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
p <- as.numeric(p)
trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "**Stigma length**", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
table<- data.frame(lambda,p, trait)
colnames(table) <- c("Lambda", "P-value", "Traits")
kable(table, format="markdown")
```

### 2019-06-03 Scripts/Phylogeny/phylogenetic_signal.R

@@ -7,23 +7,7 @@ png("phylo_image.png", units="px", width=1600, height=1600, res=300)
 
 plot(pollen_tree)
 add.scale.bar(x=0, y=1, length = 0.01)
-
 #plot(tree_10)
-
-
-library(png)
-a <- readPNG("images/tomato.png")
-b <- readPNG("images/bra_colour.png")
-c <- readPNG("images/ipomoea.png")
-
-rasterImage(image=a, xleft=0.14,ybottom=1,
-            xright=0.16,ytop=4.1)
-rasterImage(image=b, xleft=0.14,ybottom=7.1,xright=0.16,ytop=10.1)
-
-rasterImage(image=c, xleft=0.14,ybottom=4.2,xright=0.16,ytop=6.8)
-
-dev.off()
-
 
 tree_10 <- read.newick("Data/pollen_tree_no_outgroup.nwk")
 tree_10=as.phylo(tree_10)
@@ -33,22 +17,13 @@ add.scale.bar(x=0, y=9)
 #For row names of traits all
 readRDS("Manuscript_draft/Data/matrix_scale_effect.Rda")
 
-
 #From here I start working with the traits
 traits_all <- read.csv("Data/traits_all.csv", sep=",")
 si_index <- readRDS("Data/si_index.RData")
 traits_all$si_index <- si_index
 rownames(traits_all) <- rownames(matrix_scale_effect)
-traits_all <- traits_all[,-c(1,2)]
+traits_all <- traits_all[,-c(1:3,9,13)]
 traits_all_scaled <- scale(traits_all)
-
-
-
-#Phylo signal for stigma type
-stigma_type <-as.data.frame(traits_all[,c("stigma_type")])
-rownames(stigma_type) <- tree_10[[3]]
-stigma_type <- as.matrix((stigma_type))[,1]
-stigma_type <- phylosig(tree=tree_10,x=stigma_type,method="lambda",test=TRUE)
 
 
 #Phylo signal for selfing rate
@@ -162,7 +137,7 @@ rownames(si_index) <- tree_10[[3]]
 si_index <- as.matrix((si_index))[,1]
 si_index <- phylosig(tree=tree_10,x=si_index,method="lambda",test=TRUE)
 #$`lambda`[1] 0.4917088
-
+#save.image("Manuscript_draft/Data/img_phylo.RData")
 effect_size_all <- readRDS( "Data/effect_size_all.RData")
[…]

### 2019-06-03 Manuscript_draft/phylo_signal_table.Rmd
phylo results

@@
 p <- as.numeric(p)
-trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "**Stigma length**", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
+trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "Stigma length", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
 table<- data.frame(lambda,p, trait)
 colnames(table) <- c("Lambda", "P-value", "Traits")
-kable(table, format="markdown")
+kable(table, format="markdown", digits = 2)
 ```
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+
+library(kableExtra)
+load("Data/img_phylo_no_conv.RData")
+
+lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
+lambda<- as.numeric(lambda)
+p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
+p <- as.numeric(p)
+trait <- c("Selfing rate", "Pollen size", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "SI index")
+table<- data.frame(lambda,p, trait)
+colnames(table) <- c("Lambda", "P-value", "Traits")
+kable(table, format="markdown", digits = 2)
+```

### 2019-06-03 Scripts/Phylogeny/phylogenetic_signal.R

@@ -137,7 +137,133 @@ rownames(si_index) <- tree_10[[3]]
 si_index <- as.matrix((si_index))[,1]
 si_index <- phylosig(tree=tree_10,x=si_index,method="lambda",test=TRUE)
 #$`lambda`[1] 0.4917088
-#save.image("Manuscript_draft/Data/img_phylo.RData")
+#
+##
+#Without Convolvulaceae
+##
+#
+tree_10 <- read.newick("Data/no_conv.nwk")
+
+traits_all=traits_all[-c(5,6),]
+#Phylo signal for selfing rate
+selfing <-as.data.frame(traits_all[,c("Selfing_rate")])
+rownames(selfing) <- tree_10[[3]]
+selfing <- as.matrix((selfing))[,1]
+selfing <- phylosig(tree=tree_10,x=selfing,method="lambda",test=TRUE)
+#$`lambda`[1] 0.9467709
+#Checking position of results to call them in Markdown
+#a <- phylosig(tree=tree_10,x=selfing,method="lambda",test=TRUE)
+#a[1]
+#a[4]
+
+
+#Phylo signal for pollen size
+pollen_size <-as.data.frame(traits_all[,c("pollen_size")])
+rownames(pollen_size) <- tree_10[[3]]
+pollen_size <- as.matrix((pollen_size))[,1]
+pollen_size <- phylosig(tree=tree_10,x=pollen_size,method="lambda",test=TRUE)
+#$`lambda`[1] 0.9971989
+
+#Phylo signal for mean pollen per anther
+mean_pollen_anther <-as.data.frame(traits_all[,c("mean_pollen_anther")])
+rownames(mean_pollen_anther) <- tree_10[[3]]
+mean_pollen_anther <- as.matrix((mean_pollen_anther))[,1]
+mean_pollen_anther <- phylosig(tree=tree_10,x=mean_pollen_anther,method="lambda",test=TRUE)
+#$`lambda`[1] 6.610696e-05
+
+#Phylo signal for mean ovules
+mean_ovules <-as.data.frame(traits_all[,c("mean_ovules")])
+rownames(mean_ovules) <- tree_10[[3]]
+mean_ovules <- as.matrix((mean_ovules))[,1]
+mean_ovules <- phylosig(tree=tree_10,x=mean_ovules,method="lambda",test=TRUE)
+#$`lambda`[1] 6.610696e-05
+
+
+#Phylo signal for pollen_ovule_ratio
[…]

### 2019-06-03 Scripts/Ideas/Aizen idea.Rmd
file location edit

---
title: "Untitled"
output: github_document
---
Other idea based on the paper of Aizen 2007:

He explains seed set in this way. O total number of ovules, d fraction of ovules that become seed set, b proportion of pollen grains that reach ovules, p number of pollen grains.

$S=dO(1-e^bp)$

$S=dO(1-e^bp(HpEffect))$

but this Hp effect maybe can be divided at the same time in the interaction between recipient-donor with the main traits that drive the effect. IB: maybe just a weighting factor 0-1 depending on trait matching? If effect of hetero is 0, it cancells out the term, if is maximum, it *1

Moreover, this should consider quantity of hp. lINEAR EFFECT? How to model this maybe talk with nacho. IB: In the absence of data you can try linearity, but also a sigmoidal.

IB: Cool! se also Morris et al 2010 Ecology on how to add to AIzen curve, the effects of a second curve describing the negative effect of hetero. Morris apporach is mathematically more robust if you can model the second curve of hp effects.

I also think you should use this for another paper and look into Morales -Castilla TREE paper inferring interactions. I can see a similar idea where you use a set of matrix you can multiply. 
1) A matrix of plant-plant pollinator influence ( a lo carvalehire 2014). This tells you which plants may get exposed to hp pollen from empirical plant pollinator networks
2) you matrix of plant plant ht effect (0-1) or a proxy based on phylogeny of trait similarity. This is also easy to quantify.
3) A vector of sensitive recipient traits.
 to create the probability of ht effects. I really like this ideas to link to community ecology.

### 2019-06-03 Rmd/Effect_size_families_plot.Rmd
file location edits

---
title: "Effect_size_families"
author: "Jose Barragan"
date: "3 March 2019"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

load("Manuscript_draft/effect_size_species/some_effect_size_family.RData")

pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/soly_effect_size_family.RData")

pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/sial_effect_size_family.RData")

p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/pein_effect_size_family.RData")

p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/ippu_effect_size_family.RData")

p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/ipaq_effect_size_family.RData")

p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/ersa_effect_size_family.RData")

p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/caan_effect_size_family.RData")

p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/brra_effect_size_family.RData")

p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

load("Manuscript_draft/effect_size_species/brol_effect_size_family.RData")

p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")

 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()
 grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
```

### 2019-07-02 Manuscript_draft/Table_S4.Rmd
fixing tables of appendices S4 and S5

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

r <- c(selfing[3], pollen_size[3], mean_pollen_anther[3], mean_ovules[3], pollen_ovule_ratio[3], stigma_area[3], stigma_length[3], stigma_width[3], style_length[3], style_width[3], ovary_length[3], ovary_width[3], si_index[3])
r<- as.numeric(r)
p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4],si_index[4])
p <- as.numeric(p)
trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "**Pollen-ovule ratio**", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")

table<- data.frame(r,p, trait)
colnames(table) <- c("Mantel statistic", "Significance", "Traits")
kable(table, format="markdown", digits = 2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s5.RData")

r <- c(selfing_soly[3], pollen_size_soly[3], mean_pollen_anther_soly[3], mean_ovules_soly[3], pollen_ovule_ratio_soly[3], stigma_area_soly[3], stigma_length_soly[3], stigma_width_soly[3], style_length_soly[3], style_width_soly[3], ovary_length_soly[3], ovary_width_soly[3], si_index_soly[3],selfing_bras[3], pollen_size_bras[3], mean_pollen_anther_bras[3], mean_ovules_bras[3], pollen_ovule_ratio_bras[3], stigma_area_bras[3], stigma_length_bras[3], stigma_width_bras[3], style_length_bras[3], style_width_bras[3], ovary_length_bras[3], ovary_width_bras[3], si_index_bras[3])
r<- as.numeric(r)
p <- c(selfing_soly[4], pollen_size_soly[4], mean_pollen_anther_soly[4], mean_ovules_soly[4], pollen_ovule_ratio_soly[4], stigma_area_soly[4], stigma_length_soly[4], stigma_width_soly[4], style_length_soly[4], style_width_soly[4], ovary_length_soly[4], ovary_width_soly[4],si_index_soly[4],selfing_bras[4], pollen_size_bras[4], mean_pollen_anther_bras[4], mean_ovules_bras[4], pollen_ovule_ratio_bras[4], stigma_area_bras[4], stigma_length_bras[4], stigma_width_bras[4], style_length_bras[4], style_width_bras[4], ovary_length_bras[4], ovary_width_bras[4],si_index_bras[4])
p <- as.numeric(p)
trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "**Self-incompatibility index**","Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")

Family <- c(rep("Solanaceae", 13), rep("Brassicaceae", 13))

table<- data.frame(r,p, trait, Family)
colnames(table) <- c("Mantel statistic", "Significance", "Traits", "Family")
kable(table, format="markdown", digits = 2)
```

### 2019-07-03 Manuscript_draft/Table S4_S5_protest.Rmd
Protest

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

Correlation <- c(selfing_pro[6], pollen_size_pro[6], mean_pollen_anther_pro[6], mean_ovules_pro[6], pollen_ovule_ratio_pro[6], stigma_area_pro[6], stigma_length_pro[6], stigma_width_pro[6], style_length_pro[6], style_width_pro[6], ovary_width_pro[6], ovary_length_pro[6], si_index_pro[6])
Correlation<- as.numeric(Correlation)
Sum_squares <- c(selfing_pro[3], pollen_size_pro[3], mean_pollen_anther_pro[3], mean_ovules_pro[3], pollen_ovule_ratio_pro[3], stigma_area_pro[3], stigma_length_pro[3], stigma_width_pro[3], style_length_pro[3], style_width_pro[3], ovary_width_pro[3], ovary_length_pro[3],si_index_pro[3])
Sum_squares<- as.numeric(Sum_squares)

Significance <- c(selfing_pro[13], pollen_size_pro[13], mean_pollen_anther_pro[13], mean_ovules_pro[13], pollen_ovule_ratio_pro[13], stigma_area_pro[13], stigma_length_pro[13], stigma_width_pro[13], style_length_pro[13], style_width_pro[13], ovary_width_pro[13], ovary_length_pro[13],si_index_pro[13])
Significance <- as.numeric(Significance)
Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")

table<- data.frame(Correlation,Sum_squares, Significance,Trait)
colnames(table) <- c("Correlation","Sum of squares", "Significance", "Traits")
kable(table, format="markdown", digits = 2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

Correlation <- c(selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6])
Correlation<- as.numeric(Correlation)
Sum_squares <- c(selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3])
Sum_squares<- as.numeric(Sum_squares)

Significance <- c(selfing_pro_sol[13], pollen_size_pro_sol[13], mean_pollen_anther_pro_sol[13], mean_ovules_pro_sol[13], pollen_ovule_ratio_pro_sol[13], stigma_area_pro_sol[13], stigma_length_pro_sol[13], stigma_width_pro_sol[13], style_length_pro_sol[13], style_width_pro_sol[13], ovary_width_pro_sol[13], ovary_length_pro_sol[13],si_index_pro_sol[13])
Significance <- as.numeric(Significance)
Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")

table<- data.frame(Correlation,Sum_squares, Significance,Trait)
colnames(table) <- c("Correlation","Sum of squares", "Significance", "Traits")
kable(table, format="markdown", digits = 2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("Data/Table_s4.RData")

Correlation <- c(selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
Correlation<- as.numeric(Correlation)
Sum_squares <- c(selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
Sum_squares<- as.numeric(Sum_squares)

Significance <- c(selfing_pro_bra[13], pollen_size_pro_bra[13], mean_pollen_anther_pro_bra[13], mean_ovules_pro_bra[13], pollen_ovule_ratio_pro_bra[13], stigma_area_pro_bra[13], stigma_length_pro_bra[13], stigma_width_pro_bra[13], style_length_pro_bra[13], style_width_pro_bra[13], ovary_width_pro_bra[13], ovary_length_pro_bra[13],si_index_pro_bra[13])
Significance <- as.numeric(Significance)
Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")

table<- data.frame(Correlation,Sum_squares, Significance,Trait)
colnames(table) <- c("Correlation","Sum of squares", "Significance", "Traits")
kable(table, format="markdown", digits = 2)
```

### 2019-07-03 Scripts/Analysis/Analysis_Mantel.R

@@ -151,31 +151,31 @@ save.image("Manuscript_draft/Data/table_s5.RData")
 protest(matrix_effect_size,dist(traits_all_scaled))
 #Now trait by trait
 #Selfing rate
-protest(matrix_effect_size,dist(traits_all_scaled[,1]))
+selfing_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,1]))
 #Pollen size
-protest(matrix_effect_size,dist(traits_all_scaled[,2]))
+pollen_size_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,2]))
 #Pollen per anther
-protest(matrix_effect_size,dist(traits_all_scaled[,3]))
+mean_pollen_anther_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,3]))
 #Ovules
-protest(matrix_effect_size,dist(traits_all_scaled[,4]))
+mean_ovules_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,4]))
 #Pollen ovule ratio
-protest(matrix_effect_size,dist(traits_all_scaled[,5]))
+pollen_ovule_ratio_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,5]))
 #Stigmatic area
-protest(matrix_effect_size,dist(traits_all_scaled[,6]))
+stigma_area_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,6]))
 #Stigma length
-protest(matrix_effect_size,dist(traits_all_scaled[,7]))
+stigma_length_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,7]))
 #Stigma width
-protest(matrix_effect_size,dist(traits_all_scaled[,8]))
+stigma_width_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,8]))
 #Style length
-protest(matrix_effect_size,dist(traits_all_scaled[,9]))
+style_length_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,9]))
 #Style width
-protest(matrix_effect_size,dist(traits_all_scaled[,10]))
+style_width_pro <- protest(matrix_effect_size,dist(traits_all_scaled[,10]))
 #Ovary width
-protest(matrix_effect_size,dist(traits_all_scaled[,11]))
[…]

### 2019-07-10 Manuscript_draft/Protest_plot.Rmd
edits

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
library(ggplot2)
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
pro_dat<-readRDS("Data/pro_dat.RData")

p1<-ggplot(pro_dat,aes(x=traits,y=pro_cor))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat,aes(x=traits,y=sum_squ))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat,aes(x=traits,y=signif))+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

grid.draw(rbind(ggplotGrob(p1),ggplotGrob(p2), ggplotGrob(p3), size="last"))

```

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
library(ggplot2)
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
pro_dat_sol<-readRDS("Data/pro_dat_sol.RData")

p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

grid.draw(rbind(ggplotGrob(p1),ggplotGrob(p2), ggplotGrob(p3), size="last"))

```

```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6}
library(ggplot2)
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
pro_dat_sol<-readRDS("Data/pro_dat_sol.RData")

p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+
  geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

grid.draw(rbind(ggplotGrob(p1),ggplotGrob(p2), ggplotGrob(p3), size="last"))

```

### 2019-07-10 Manuscript_draft/Protest_plot.Rmd
edits

@@
 library(lattice)
-pro_dat_sol<-readRDS("Data/pro_dat_sol.RData")
+pro_dat_bra<-readRDS("Data/pro_dat_bra.RData")
 
-p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+
-  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
+p1<-ggplot(pro_dat_bra,aes(x=traits_bra,y=pro_cor_bra))+
+  geom_bar(stat="identity",position="dodge")+labs(title="Brassicaceae",x="Traits", y = "Correlation")+theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())
-p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+
-  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
+p2<-ggplot(pro_dat_bra,aes(x=traits_bra,y=sum_squ_bra))+
+  geom_bar(stat="identity",position="dodge")+labs(title="",x="", y = "Sum of squares")+theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank())
-p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+
+p3<-ggplot(pro_dat_bra,aes(x=traits_bra,y=signif_bra))+labs(title="",x="Traits", y = "Significance")+
   geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

### 2019-07-10 Manuscript_draft/Protest_plot.Rmd
edits

@@
 
-p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+
+p1<-ggplot(pro_dat_sol,aes(x=traits_sol,y=pro_cor_sol))+labs(title="Solanaceae",x="Traits", y = "Correlation")+geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
+        axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())
+p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+labs(title="",x="", y = "Sum of squares")+
   geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
@@
         axis.ticks.x=element_blank())
-p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+
-  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())
-p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+
+p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+labs(title="",x="", y = "Sum of squares")+
   geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

### 2019-08-01 Manuscript_draft/Tables_and_figures.Rmd
Edits of organization

@@
 
-**Table 2**
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-load("table_treatments.RData")
-Species <- c("Brassica oleracea", "Brassica rapa", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-Cross <- cross
-Self <- self
-Natural_selfing <- nat_self
-Apomixis <- apo
-table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
-kable(table, format="markdown", caption= "Perecentage of seeds produced per ovule for the ten species used in the experiment.
-The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
-",longtable = TRUE)
-```
-
 \newpage
@@
 ```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
-load("r_biology.RData")
+load("Data/r_biology.RData")
 library(ggpubr)
@@
   scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
   xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
@@
 \newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5}
-load("Data/family_cor.RData")
-library(ggpubr)
-library(ggplot2)
-library(gridExtra)
-library(grid)
-
-p1 <- ggscatter(sola, x = "Cohen_d", y = "style_length", 
-          add = "reg.line", conf.int = TRUE, 
-          cor.coef = TRUE, cor.method = "pearson",
-          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")
-
-p2<- ggscatter(a, x = "Cohen_d", y = "style_length", 
-          add = "reg.line", conf.int = TRUE, 
-          cor.coef = TRUE, cor.method = "pearson",
-          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) All families")
-grid.arrange(p1, p2, nrow = 1, ncol=2)
-
-```
-**Figure 7**
-
-\newpage
 ```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
-load("pollen_ratio.RData")
+load("Data/pollen_ratio.RData")
 library(ggpubr)

### 2019-09-27 Manuscript_draft/Plot_transitivity_example.Rmd
Trying to adress some comments

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=5,fig.width=5}
library(igraph)
library(grid)
library(gridExtra)
library(egg)
x <- matrix(1:9, nrow = 3, dimnames = list(c("A","B","C"), c("A","B","C")))
x[1,] <- c(0,1,1) 
x[2,] <- c(0,0,1) 
x[3,] <- c(0,0,0) 
net_2=graph.adjacency(x,mode="directed",weighted=TRUE,diag=FALSE) 
b <- plot.igraph(net_2,vertex.size=35,vertex.label=NA,edge.color="grey4",edge.width=E(net_2)$weight/0.6, edge.arrow.size=1)

```

### 2019-09-27 Scripts/Analysis/Glmm_traits_Hp.R

@@ -86,6 +86,8 @@ jarqueberaTest(model1$df.resid)
 predict(model1, newdata=mydata, type="response")
 max(mydata$Donor_pollen_size)
 
+model1<-lmer(value~Recipient_stigma_area*Donor_pollen_size+(1+Donor|Recipient),data=mydata,REML=FALSE)
+
 
 plot_model(model1, type = "int",title="",axis.title=c("Stigmatic area","Predicted effect size"), legend.title="Donor pollen size",
  terms = c(Recipient_stigma_area,Donor_pollen_size), mdrt.values="minmax")

### 2019-09-27 Scripts/Analysis/Transitivity.R

@@ -79,12 +79,31 @@ net=network(m,matrix.type="adjacency",directed=T)
 #create window for plotting
 quartz()
 net=graph.adjacency(m,mode="directed",weighted=TRUE,diag=FALSE) 
-plot.igraph(net,vertex.label=V(net)$name,layout=layout.fruchterman.reingold, vertex.label.color="black",edge.color="black",edge.width=E(net)$weight/2, edge.arrow.size=0.3)
+plot.igraph(net,vertex.label=V(net)$name,layout=layout.fruchterman.reingold, vertex.label.color="black",edge.color="black",edge.width=E(net_1)$weight/2, edge.arrow.size=0.3)
 #Fixing arrow size
 b=d*1.5
 net=graph.adjacency(m,mode="directed",weighted=TRUE,diag=FALSE) 
 plot.igraph(net,vertex.label=V(net)$name,vertex.label.cex=.6,layout=layout.fruchterman.reingold, vertex.color=c(rep("pink",2),"grey","pink", rep("skyblue",2),"grey","pink", rep("grey",2)), vertex.label.color="black",edge.color="black",edge.width=E(net)$weight/2, edge.arrow.size=0.3)
 #try other colours? like the ones of effect sizes plots?
 #"#0072B2", "#009E73", "#D55E00","#E69F00"
-plot.igraph(net,vertex.label=V(net)$name,vertex.label.cex=.6,layout=layout.fruchterman.reingold, vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),"#D55E00","#0072B2", rep("#D55E00",2)), vertex.label.color="black",edge.color="grey4",edge.width=E(net)$weight/1.8, edge.arrow.size=0.3)
+plot.igraph(net,vertex.label=V(net)$name,vertex.label.cex=.6,layout=layout.fruchterman.reingold, vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),"#D55E00","#0072B2", rep("#D55E00",2)), vertex.label.color="black",edge.color="grey4",edge.width=E(net_2)$weight/1.8, edge.arrow.size=0.3)
 
+#I'm going to create an example of transitivity and intrantive competition
+#First I create a matrix
+
[…]

### 2019-10-16 Scripts/Analysis/Glmm_traits_Hp.R
creating tables of phylogenetic distance for No Solanaceae and no Brassicaceae. To have all the pairs, before I had just no Convo.

@@ -91,6 +91,12 @@ plot(model1)
 model2<-lm(value~factor(Donor),data=mydata)
 plot(model1)
 anova(model2) 
+
+
+model2<-lm(value~factor(Donor)+factor(Recipient),data=mydata)
+summary(model2)
+anova(model2)
+
 #Donors does not produce a significant change in effect sizes 
 #Recipients do
 
@@ -100,6 +106,11 @@ anova(model2)
 #MODEL 1
 #DONOR POLLEN SIZE+RECIPIENT STYLE LENGTH+DONOR POLLEN SIZE * RECIPIENT STYLE LENGTH
 model1<-lmer(value~Recipient_stigma_area*Donor_pollen_size+(1|Recipient),data=mydata,REML=FALSE)
+
+model1<-lm(value~Recipient_stigma_area*Donor_pollen_size,data=mydata)
+summary(model1)
+#
+model1<-lmer(value~Recipient_stigma_area*Donor_pollen_size+(1|Recipient),data=mydata)
 summary(model1)
 summ(model1, confint = TRUE, digits = 3)
 effect_plot(model1, pred = Donor_pollen_size, interval = TRUE, plot.points = TRUE)
@@ -202,8 +213,14 @@ mydata$donor_recipient <- paste(mydata$Recipient, mydata$Donor,sep="_")
 
 donor_recipient <- merge(p_data,mydata, by="donor_recipient")
 
-model1<-lmer(value~hp_ratio*Recipient_stigma_area+ (1|Recipient),data=donor_recipient,REML=FALSE)
+model1<-lmer(value~hp_ratio*Recipient_stigma_area+ (1|Recipient),data=donor_recipient)
 summary(model1)
+plot(model1)
+model2<-lm(value~hp_ratio*Recipient_stigma_area,data=donor_recipient)
+summary(model2)
+plot(model2)
+
+
 plot(model1)
 model2<-lmer(value~Donor_pollen_size+Recipient_stigma_area+Recipient_stigma_area*Donor_pollen_size+ Recipient_pollen_ovule_ratio+ (1|Recipient),data=mydata,REML=FALSE)
 

### 2019-10-16 Scripts/Analysis/Phylogenetic_signal.R

@@ -283,7 +283,7 @@ Cohen_d <- phylosig(tree=tree_10,x=Cohen_d,method="lambda",test=TRUE)
 
 tree_no_sol <- read.newick("Data/no_sol.nwk")
 traits_all_no_sol <- traits_all[,]
-traits_all_no_sol <- traits_all_no_sol[-c(3,7,9,10),-c(3,7,9,10)]
+traits_all_no_sol <- traits_all_no_sol[-c(3,7,9,10),-c(1:3,9,13)]
 
 #Phylo signal for selfing rate
 selfing <-as.data.frame(traits_all_no_sol[,c("Selfing_rate")])
@@ -307,7 +307,7 @@ mean_pollen_anther <- phylosig(tree=tree_no_sol,x=mean_pollen_anther,method="lam
 
 #Phylo signal for mean ovules
 mean_ovules <-as.data.frame(traits_all_no_sol[,c("mean_ovules")])
-rownames(mean_ovules) <- traits_all_no_sol[[3]]
+rownames(mean_ovules) <- tree_no_sol[[3]]
 mean_ovules <- as.matrix((mean_ovules))[,1]
 mean_ovules <- phylosig(tree=tree_no_sol,x=mean_ovules,method="lambda",test=TRUE)
 #$`lambda`[1] 6.610696e-05
@@ -319,12 +319,6 @@ rownames(pollen_ovule_ratio) <- tree_no_sol[[3]]
 pollen_ovule_ratio <- as.matrix((pollen_ovule_ratio))[,1]
 pollen_ovule_ratio <- phylosig(tree=tree_no_sol,x=pollen_ovule_ratio,method="lambda",test=TRUE)
 #$`lambda`[1] 6.610696e-05
-
-#Anthers
-anthers <-as.data.frame(traits_all_no_sol[,c("anthers")])
-rownames(anthers) <- tree_no_sol[[3]]
-anthers <- as.matrix((anthers))[,1]
-anthers <- phylosig(tree=tree_no_sol,x=anthers,method="lambda",test=TRUE)
 
 #Stigma area
 stigma_area <-as.data.frame(traits_all_no_sol[,c("stigma_area")])
@@ -347,20 +341,12 @@ stigma_width <- as.matrix((stigma_width))[,1]
 stigma_width <- phylosig(tree=tree_no_sol,x=stigma_width,method="lambda",test=TRUE)
 #$`lambda`[1] 0.7292784
 
-#Stigma_surface
[…]

### 2019-10-17 Manuscript_draft/Figure4.Rmd
Figures 2 to 5 ready for publication. Lacking 1 in High resolution I think I'm going to change the plant images...

---
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

load("effect_size_species/effect_size_total.RData")
png("Figure4.png", width = 11000, height = 5000, res = 1500)

 ggplot(all, aes(Family,Cohen_d,colour=Family_1), size=10) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))+ geom_point( aes(colour=Family_1),size=2) +
  geom_errorbar(aes(x = Family, ymin = Lower, 
ymax = Upper,colour=Family_1), width = 0.2, size=0.8, alpha=0.5)+
  scale_color_manual(name  ="Family",values=c("#D55E00", "#009E73", "#0072B2"), labels=c("Brassicaceae","Convolvulaceae","Solanaceae"))+ guides(colour = guide_legend(override.aes = list(size=3)))+guides(colour = guide_legend(override.aes = list(colour=c("#0072B2", "#009E73", "#D55E00"))))+
  xlab("") + ylab("Hedges' g") + rotate()+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')
  dev.off()

```

### 2019-10-21 Figures_main_text/Figure3.Rmd
organization 1

--- 2019-08-01 Manuscript_draft/Tables_and_figures.Rmd
@@
 ---
-output:
-  pdf_document: default
-  html_document: default
-  fontsize: 11pt
-header-includes:
-  - \usepackage{leading}
-  - \leading{18pt}
+output: pdf_document
 ---
---
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = "h")
-```
-
-```{r setup, include=FALSE, cache=FALSE, message = FALSE}
-
-library("knitr")
-library("ggplot2")
-library("extrafont")
-
-#opts_knit$set(root.dir=normalizePath('../'))
-
-### Chunk options: see http://yihui.name/knitr/options/ ###
-
-## Text results
-opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE, include = TRUE)
-
-## Code decoration
-opts_chunk$set(tidy = TRUE, comment = NA, highlight = TRUE)
-
-## Cache
-opts_chunk$set(cache = 2, cache.path = "output/cache/")
-
-## Plots
-opts_chunk$set(fig.path = "output/figures/")
-
-```
-
-```{r knitcitations, echo=FALSE, cache = FALSE}
-library(knitcitations)
-cleanbib()   
-cite_options(citation_format = "pandoc")
-```
-
-**Table 1**
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-Family <- c(rep("Brassicaceae",4), rep("Convolvulaceae", 2), rep("Solanaceae",4))
-
-Genus <- c("Brassica", "Brassica", "Eruca", "Sinapis", "Ipomoea", "Ipomoea", "Capsicum", "Petunia", "Solanum", "Solanum")
-
-Species <- c("Brassica rapa", "Brassica oleracea", "Eruca versicaria", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-
-table<- data.frame(Family, Genus, Species)
-kable(table, format="markdown", caption = "a")
-```
-\newpage
-
-\newpage
-
-**Table 3**
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-dat_all <- readRDS("Data/dat_all.RData")
-kable(dat_all, format="markdown", caption = "a")
-
-```
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, out.width='100%'}
-knitr::include_graphics('images/phylo_image.png')
-```
-**Figure 1**
-\newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=7}
-load("Data/r_biology.RData")
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-ggplot(bio,aes(x=Species,y=value,fill=variable))+
-  geom_bar(stat="identity",position="dodge")+scale_fill_grey(start = 0, end = 0.85,name="Treatments") + 
-  theme_minimal()+xlab("Species")+ylab("Seed-setting rate (%)")+labs(title="Reproductive biology test")+
-  theme(axis.text.x = element_text(angle = 45, hjust = 1, face= "italic",family = ""), legend.text=element_text(size=7), legend.title=element_text(size=8), axis.text.y  = element_text(size = 10))+
-  scale_y_continuous(minor_breaks = seq(0 , 100, 5), breaks = seq(0, 100, 10))
-
-```
-**Figure 2**
-
-\newpage
-```{r, echo=FALSE, message=FALSE,fig.align='center', warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6}
-
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-load("effect_size_species/effect_size_total.RData")
-Family_1<-c("#D55E00","#009E73","#0072B2")
-all$Family_1=as.character(all$Family_1)
-all$Family_1[all$Family_1=="B"]<-"X"
-all$Family_1[all$Family_1=="S"]<-"B"
-all$Family_1[all$Family_1=="X"]<-"S"
-
- ggplot(all, aes(Family,Cohen_d,colour=Family_1), size=10) + theme_bw(base_size=10)+theme(axis.text.y = element_text(face = "italic"))+ geom_point( aes(colour=Family_1),size=2) +
-  geom_errorbar(aes(x = Family, ymin = Lower, 
-ymax = Upper,colour=Family_1), width = 0.2, size=0.8, alpha=0.5)+
-  scale_color_manual(name  ="Family",values=c("#0072B2","#009E73","#D55E00"), labels=c("Brassicaceae","Convolvulaceae","Solanaceae"))+
-  scale_fill_manual()+
-  xlab("") + ylab("Hedges' g") + rotate()+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+scale_alpha(guide = 'none')
-```
-**Figure 3**
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7}
+```{r, echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7}
 
@@
 load("effect_size_species/all_effect_size.RData")
+png("Figure3.png", width = 9000, height = 11000, res = 1400)
 
@@
 sp_legend <- readRDS("Data/sp_legend.RData")
-p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#E69F00","#D55E00"))+ scale_fill_manual("Family",values=c("#0072B2",  "#009E73", "#E69F00","#D55E00"))+
+p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2","#009E73","#E69F00","#D55E00"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
   xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
@@
 #mylegend
-```
-**Figure 4**
-
-\newpage
-```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7}
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-library(tidyverse)
-
-load("effect_size_species/brol_effect_size_family.RData")
-
-pp1<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))
-
-load("effect_size_species/brra_effect_size_family.RData")
-
-pp2<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))
-
-load("effect_size_species/ersa_effect_size_family.RData")
-
-p3<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("C)",italic(' E. sativa'))))
-
-load("effect_size_species/sial_effect_size_family.RData")
-
-p4<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))
-
-load("effect_size_species/ipaq_effect_size_family.RData")
-
-p5<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))
-
-load("effect_size_species/ippu_effect_size_family.RData")
-
-p6<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))
-
-load("effect_size_species/caan_effect_size_family.RData")
-
-p7<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))
-
-load("effect_size_species/pein_effect_size_family.RData")
-
-p8<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))
-
-load("effect_size_species/soly_effect_size_family.RData")
-
-p9<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))
-
-load("effect_size_species/some_effect_size_family.RData")
-
-p10<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
-  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#D55E00","#E69F00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))
-
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-grid.newpage()
-g_legend<-function(a.gplot){
-  tmp <- ggplot_gtable(ggplot_build(a.gplot))
-  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
-  legend <- tmp$grobs[[leg]]
-  return(legend)}
-leg_family=readRDS("Data/leg_family.RData")
-p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#E69F00",  "#009E73", "#D55E00","#E69F00"))
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-mylegend<-g_legend(p11)
-
- grid.draw(arrangeGrob(cbind(ggplotGrob(pp1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")), size="last"),mylegend,nrow=6))
+ dev.off()
 
 ```
-**Figure 5**
-
-\newpage
-```{r, echo=FALSE,fig.align='center', message=FALSE,warning=FALSE,cache=FALSE}
-library(ape)
-library(phylosignal)
-library(adephylo)
-library(phylobase)
-library(phylosignal)
-library(caret)
-library(ggplot2)
-library(seqHMM)
-library(dplyr)
-library(reshape2)
-pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
-effect_size_all <- readRDS( "Data/effect_size_all.RData")
-#Now rename species
-rownames(effect_size_all) <- c("Solanum_melongena","Solanum_lycopersicum","Petunia_integrifolia", "Capsicum_annuum","Ipomoea_purpurea","Ipomoea_aquatica","Sinapis_alba","Eruca_vesicaria","Brassica_rapa", "Brassica_oleracea")
-hp_mean_sp=effect_size_all[,-c(1,3,4)]
-p4d <- phylo4d(pollen_tree, hp_mean_sp)
-barplot.phylo4d(p4d, center = TRUE , scale = FALSE,trait.labels="Hp effect",bar.col = c(rep("#0072B2",4), rep("#009E73",2), rep("#D55E00",4)))
-```
-**Figure 6**
-
-\newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
-load("Data/pollen_ratio.RData")
-library(ggpubr)
-library(ggplot2)
-library(gridExtra)
-library(grid)
-
-p1 <- ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
-  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
-  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-
-p2 <- ggplot(pollen_ratios_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="C) Solanaceae") +
-  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
-  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-
-p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="B) Convolvulaceae") +
-  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor")) + 
-  geom_hline(yintercept = 50) + xlab("") + ylab("Pollen Ratio")
-grid.arrange(p1, p3,p2, nrow = 3, ncol=1)
-
-```
-**Figure 8**
-
-\newpage
-```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE,fig.height=9,fig.width=5}
-load("Data/total_pollen.RData")
-library(ggpubr)
-library(ggplot2)
-library(gridExtra)
-library(grid)
-
-p1 <- ggplot(total_pollen_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="A) Brassicaceae") +
-  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
-
-p2 <- ggplot(total_pollen_solanaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="C) Solanaceae") +
-  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
-
-p3 <-ggplot(pollen_ratios_convolvulaceae, aes(x=spp, y=ratio, fill=variable)) +
-  geom_bar(stat='identity', position='dodge') +labs(title="B) Convolvulaceae") +
-  theme(axis.text.x=element_text(size = 8,angle=45,hjust=1, face="italic"), legend.title = element_blank()) + scale_fill_grey(labels=c("Recipient","Donor"))+ xlab("") + ylab("Total pollen")
-grid.arrange(p1, p3,p2, nrow = 3, ncol=1)
-
-```
-**Figure 9**
-
-\newpage
-
-# List of tables
-
-**Table 1** Species list with family and genus.
-
-**Table 2** Results of hand corss-pollination, hand self-pollination, natural selfing (unpollinated bagged flowers) and apomixis.
-The values are the average seed production per treatment (N=10) divided by the average number of ovules per species.
-
-**Table 3** Seed production for the treatments that produced seeds with 100% foreign pollen.
-
-# List of figures
-
-**Figure 1** Phylogenetic tree of the species used in the experiment from three different families from top to bottom: Brassicaceae, Convolvulaceae and Solanaceae.
-
-**Figure 2** Barplot of the different tests of the reproductive biology of the species.
-The y axis is the percentage of ovules converted to seed.
-The different treatments are, hand cross-pollination, hand self-pollination, natural selfing and apomixis (N=10 for all of them).
-
-**Figure 3** The impact of foreign pollen on recipient plant species. Effect sizes (with 95% confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients.
-
-**Figure 4** The response of heterospecific pollen upon 10 recipient plant species.  Each panel represents one recipient plant species crossed with 50% mixes of the other 9 species.
-
-**Figure 5** The impact of foreign pollen on recipient plant species. Effect sizes (with 95% confidence intervals) of the species grouped per family upon all recipients.
-
-**Figure 6** Phylogenetic signal of hterospecific pollen effect (hedges' g)
-
-**Figure 7** (comment) Simple Pearson correlation in order to show a possible path to follow in the article showing that style length and stigma size could explain the effect in Solanaceae species.
-
-**Figure 8** Pollen ratio counts on stigma after hand pollination with 50-50% mix.
-The panel is divided by family: A) Brassicaceae, B) Convolvulaceae and C) Solanaceae.
-The pollen recipient species is coloured in black and the donor species in grey.
-
-**Figure 9** Total pollen counts on stigma after hand pollination with 50-50% mix.
-The panel is divided by family: A) Brassicaceae, B) Convolvulaceae and C) Solanaceae.
-The pollen recipient species is coloured in black and the donor species in grey.

### 2019-10-21 Old/Manuscript_draft.Rmd
organization 1

--- 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
@@
 fontsize: 11pt
-header-includes: \usepackage{float}
 footerdate: yes
 geometry: margin=1in
+header-includes: 
+- \usepackage{longtable}
 linenumbers: yes
@@
 ---
-```{r global_options, include=FALSE}
-knitr::opts_chunk$set(fig.pos = 'h')
-```
 
@@
 
+I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
+Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
+The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
+
+Here I show the plot of just solanaceae and then with all the species.
+I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
+
+\newpage
+
+# DISCUSSION
+
+supporting ideas: 
+Species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from Whitehead et al. (2018)).
+
+Interestingly the effect of the different donors per species were very homogeneous which lead us to think that the female reproductive traits of the pollen recipient are the main ones in explaining heterospecific pollen effect.
+Our main predictive trait of effect is stigma size, and because we found a correlation between the pollen quantity deposited on the stigma and stigma size, we argue that that the total load of pollen deposited per treatment can obscured what are the main traits in driving heterospecific pollen effect.
+
+Curiously between the species with greater effect sizes, we found completely self incompatible species, species with the smallest stigma and the species with shortes style. Develop more...
+
+Although we have found a positive correlation between phylogenetic distance and heterospecific pollen effect, this results have to be treated carefully.
+From our results we want to highlight that also far related species can affect negatively fitness but the effect from close related is species can also have important detrimental effects.
+Moreover, the effect of close related species can be masked by the possibility of hibridization as it occure between two of our species of Brassica.
+Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors as we have shown in figure xxx.
+These different traits will define how it will be the effect across the different species independently of the nature of the donor and also differently even between species of .
+Although traditionally the nature of the pollen donor have been very studied, the recipient...
+
+Herbs vs tress, annual vs perennial... Many flowers vs few flowered species; structural composition on a system
+
+What are the implications of the findings?
+
+# CONCLUSIONS
+
+# ACKNOWLEDGEMENTS
+
+# REFERENCES
+
+```{r write_citations, cache=FALSE, include=FALSE}
+write.bibtex(file="knitcitations.bib")
+```
+
+<div id = "refs"></div>
+
 \newpage
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6,fig.cap="The impact of foreign pollen on recipient plant species.
-Effect sizes (with 95%confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}
+Effect sizes (with 95% confidence intervals) of 9 different donor species of heterospecific pollen upon all recipients."}
 
@@
 \newpage
-
 ```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7,fig.cap="A"}
@@
 \newpage
-
 ```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.cap="Phylogenetic signal of the average heterospecific pollen effect size per species"}
@@
 \newpage
-
 ```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE, fig.height=3,fig.width=5,fig.cap="a"}
@@
 ```
-
-I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect.
-Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
-The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)
-
-Here I show the plot of just solanaceae and then with all the species.
-I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
-
-\newpage
-
-# DISCUSSION
-
-supporting ideas: 
-Species that are strong selfers or strong outcrossers have less variablity in mating systems and predictions of effect could be more realistic (see figure 1 from Whitehead et al. (2018)).
-
-Interestingly the effect of the different donors per species were very homogeneous which lead us to think that the female reproductive traits of the pollen recipient are the main ones in explaining heterospecific pollen effect.
-Our main predictive trait of effect is stigma size, and because we found a correlation between the pollen quantity deposited on the stigma and stigma size, we argue that that the total load of pollen deposited per treatment can obscured what are the main traits in driving heterospecific pollen effect.
-
-Curiously between the species with greater effect sizes, we found completely self incompatible species, species with the smallest stigma and the species with shortes style. Develop more...
-
-Although we have found a positive correlation between phylogenetic distance and heterospecific pollen effect, this results have to be treated carefully.
-From our results we want to highlight that also far related species can affect negatively fitness but the effect from close related is species can also have important detrimental effects.
-Moreover, the effect of close related species can be masked by the possibility of hibridization as it occure between two of our species of Brassica.
-Moreover, although different effect between distinct donors can occur we want to note the importance on the traits of the recipient that determine an homogeneous effect between donors as we have shown in figure xxx.
-These different traits will define how it will be the effect across the different species independently of the nature of the donor and also differently even between species of .
-Although traditionally the nature of the pollen donor have been very studied, the recipient...
-
-Herbs vs tress, annual vs perennial... Many flowers vs few flowered species; structural composition on a system
-
-What are the implications of the findings?
-
-# CONCLUSIONS
-
-# ACKNOWLEDGEMENTS
-
-# REFERENCES
-
-```{r write_citations, cache=FALSE, include=FALSE}
-write.bibtex(file="knitcitations.bib")
-```
-
-<div id = "refs"></div>
 \newpage
@@
 
-1.
-
-**Table S1**.
-Perecentage of seeds produced per ovule for the ten species used in the experiment.
-The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
@@
 table<- data.frame(Species, Cross, Self, Natural_selfing,Apomixis)
-kable(table, format="markdown")
+kable(table, format="markdown", caption= "Perecentage of seeds produced per ovule for the ten species used in the experiment.
+The treatments presented are hand cross-pollination, hand self-pollination, natural selfing and apomixis (emasculated flowers).
+",longtable = TRUE)
 ```
-
-2.
-
-**Figure S1**.
-Pollen ratios separated by family A) Brassicaceae, B) Solanaceae, C) Convolvulaceae.
-Pollen was counted for crosses with species of the other two families (N=3).
-To prepare these ratios all the pollen grains on the stigma were counted.
 

### 2019-10-21 Old/Tables_and_figures.tex
organization 1

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}

  \title{}
    \pretitle{\vspace{\droptitle}}
  \posttitle{}
    \author{}
    \preauthor{}\postauthor{}
    \date{}
    \predate{}\postdate{}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\usepackage{leading}
\leading{18pt}

\begin{document}

--

\textbf{Table 1}

\begin{longtable}[]{@{}lll@{}}
\toprule
Family & Genus & Species\tabularnewline
\midrule
\endhead
Brassicaceae & Brassica & Brassica rapa\tabularnewline
Brassicaceae & Brassica & Brassica oleracea\tabularnewline
Brassicaceae & Eruca & Eruca versicaria\tabularnewline
Brassicaceae & Sinapis & Sinapis alba\tabularnewline
Convolvulaceae & Ipomoea & Ipomoea aquatica\tabularnewline
Convolvulaceae & Ipomoea & Ipomoea purpurea\tabularnewline
Solanaceae & Capsicum & Capsicum annuum\tabularnewline
Solanaceae & Petunia & Petunia integrifolia\tabularnewline
Solanaceae & Solanum & Solanum lycopersicum\tabularnewline
Solanaceae & Solanum & Solanum melongena\tabularnewline
\bottomrule
\end{longtable}

\newpage

\newpage

\textbf{Table 3}

\begin{longtable}[]{@{}lllr@{}}
\toprule
Family & Species & Donor & Seeds\tabularnewline
\midrule
\endhead
Brassicaceae & B. oleracea & C. annuum & 5\tabularnewline
Brassicaceae & B. rapa & B. oleracea & 2\tabularnewline
Brassicaceae & B. rapa & B. oleracea & 13\tabularnewline
Brassicaceae & B. rapa & S. lycopersicum & 1\tabularnewline
Brassicaceae & B. rapa & B. oleracea & 7\tabularnewline
Brassicaceae & B. rapa & B. oleracea & 5\tabularnewline
Brassicaceae & S. alba & B. oleracea & 7\tabularnewline
Brassicaceae & E. sativa & C. annuum & 6\tabularnewline
Brassicaceae & E. sativa & C. annuum & 1\tabularnewline
Solanaceae & S. lycopersicum & S. alba & 3\tabularnewline
Solanaceae & S. melongena & P. integrifolia & 36\tabularnewline
Solanaceae & C. annuum & S. alba & 127\tabularnewline
Solanaceae & C. annuum & E. sativa & 3\tabularnewline
\bottomrule
\end{longtable}

\newpage

\includegraphics[width=1\linewidth]{images/phylo_image} \textbf{Figure
1} \newpage

\begin{center}\includegraphics{output/figures/unnamed-chunk-4-1} \end{center}

\textbf{Figure 2}

\newpage

\begin{center}\includegraphics{output/figures/unnamed-chunk-5-1} \end{center}

\textbf{Figure 3}

\newpage

\includegraphics{output/figures/unnamed-chunk-6-1.pdf} \textbf{Figure 4}

\newpage

\includegraphics{output/figures/unnamed-chunk-7-1.pdf} \textbf{Figure 5}

\newpage

\begin{center}\includegraphics{output/figures/unnamed-chunk-8-1} \end{center}

\textbf{Figure 6}

\newpage

\begin{center}\includegraphics{output/figures/unnamed-chunk-9-1} \end{center}

\textbf{Figure 8}

\newpage

\begin{center}\includegraphics{output/figures/unnamed-chunk-10-1} \end{center}

\textbf{Figure 9}

\newpage

\section{List of tables}\label{list-of-tables}

\textbf{Table 1} Species list with family and genus.

\textbf{Table 2} Results of hand corss-pollination, hand
self-pollination, natural selfing (unpollinated bagged flowers) and
apomixis. The values are the average seed production per treatment
(N=10) divided by the average number of ovules per species.

\textbf{Table 3} Seed production for the treatments that produced seeds
with 100\% foreign pollen.

\section{List of figures}\label{list-of-figures}

\textbf{Figure 1} Phylogenetic tree of the species used in the
experiment from three different families from top to bottom:
Brassicaceae, Convolvulaceae and Solanaceae.

\textbf{Figure 2} Barplot of the different tests of the reproductive
biology of the species. The y axis is the percentage of ovules converted
to seed. The different treatments are, hand cross-pollination, hand
self-pollination, natural selfing and apomixis (N=10 for all of them).

\textbf{Figure 3} The impact of foreign pollen on recipient plant
species. Effect sizes (with 95\% confidence intervals) of 9 different
donor species of heterospecific pollen upon all recipients.

\textbf{Figure 4} The response of heterospecific pollen upon 10
recipient plant species. Each panel represents one recipient plant
species crossed with 50\% mixes of the other 9 species.

\textbf{Figure 5} The impact of foreign pollen on recipient plant
species. Effect sizes (with 95\% confidence intervals) of the species
grouped per family upon all recipients.

\textbf{Figure 6} Phylogenetic signal of hterospecific pollen effect
(hedges' g)

\textbf{Figure 7} (comment) Simple Pearson correlation in order to show
a possible path to follow in the article showing that style length and
stigma size could explain the effect in Solanaceae species.

\textbf{Figure 8} Pollen ratio counts on stigma after hand pollination
with 50-50\% mix. The panel is divided by family: A) Brassicaceae, B)
Convolvulaceae and C) Solanaceae. The pollen recipient species is
coloured in black and the donor species in grey.

\textbf{Figure 9} Total pollen counts on stigma after hand pollination
with 50-50\% mix. The panel is divided by family: A) Brassicaceae, B)
Convolvulaceae and C) Solanaceae. The pollen recipient species is
coloured in black and the donor species in grey.

\end{document}

### 2019-10-21 Supplementary_material/Figure_S4_Effect_sizes_family.Rmd
Organization 5

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
\newpage
```{r, echo=FALSE, message=FALSE,warning=FALSE,cache=FALSE,fig.height=8,fig.width=7}
library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
library(tidyverse)

load("effect_size_species/brol_effect_size_family.RData")

pp1<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))

load("effect_size_species/brra_effect_size_family.RData")

pp2<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))

load("effect_size_species/ersa_effect_size_family.RData")

p3<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("C)",italic(' E. sativa'))))

load("effect_size_species/sial_effect_size_family.RData")

p4<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))

load("effect_size_species/ipaq_effect_size_family.RData")

p5<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))

load("effect_size_species/ippu_effect_size_family.RData")

p6<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))

load("effect_size_species/caan_effect_size_family.RData")

p7<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))

load("effect_size_species/pein_effect_size_family.RData")

p8<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))

load("effect_size_species/soly_effect_size_family.RData")

p9<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
  geom_linerange(size=0.6,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))

load("effect_size_species/some_effect_size_family.RData")

p10<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,aes(color=factor(Family))) + theme(legend.title = element_blank(),legend.direction="horizontal")+
  geom_linerange(size=0.6,linetype=1, aes(x = Family, ymin = Lower, 
ymax = Upper,color=factor(Family)))+
  scale_color_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  scale_fill_manual("Family",values=c("#D55E00",  "#009E73", "#0072B2","#E69F00"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))

 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()
g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}
leg_family=readRDS("Data/leg_family.RData")
p11<- ggplot(leg_family, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),axis.text.y = element_blank())+ geom_point(size=2,aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2",  "#009E73", "#E69F00","#D55E00"))
 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
mylegend<-g_legend(p11)

 grid.draw(arrangeGrob(cbind(ggplotGrob(pp1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")), size="last"),mylegend,nrow=6))

```
**Figure 5**

### 2019-10-21 Scripts/Ideas/theoretical plot.R

@@ -1,19 +1,0 @@
-#Theoretical prediction of heterospecific pollen effect
-
-#Create empty plot
-
-plot(NULL, xlim=c(0,1), ylim=c(0,1), ylab="Heterospecific pollen effect", xlab="Phylogenetic Relatedness", main="Theoretical effect") 
-abline(h=0.9)
-text(0.1,0.95, "1")
-abline(v=0.28)
-text(0.1,0.2, "Hybridization
-     low effect",srt = 90)
-
-text(0.35,0.95, "2")
-
-text(0.5,0.5, "Trait-dependent effect
-     highly variable")
-text(0.5,0.8, "SI")
-text(0.5,0.2, "SC")
-
-

### 2019-10-22 Supplementary_material/Effect_size_families_plot.Rmd
organizing to make the repo public when publish
Edits

--- 2019-06-03 Rmd/Effect_size_families_plot.Rmd
@@
 ---
-title: "Effect_size_families"
-author: "Jose Barragan"
-date: "3 March 2019"
 output:
@@
 
-load("Manuscript_draft/effect_size_species/some_effect_size_family.RData")
+setwd("~/Hp_pollen_experiment")
+load("Data/RData/some_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/soly_effect_size_family.RData")
+load("Data/RData/soly_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/sial_effect_size_family.RData")
+load("Data/RData/sial_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/pein_effect_size_family.RData")
+load("Data/RData/pein_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/ippu_effect_size_family.RData")
+load("Data/RData/ippu_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/ipaq_effect_size_family.RData")
+load("Data/RData/ipaq_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/ersa_effect_size_family.RData")
+load("Data/RData/ersa_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/caan_effect_size_family.RData")
+load("Data/RData/caan_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/brra_effect_size_family.RData")
+load("Data/RData/brra_effect_size_family.RData")
 
@@
 
-load("Manuscript_draft/effect_size_species/brol_effect_size_family.RData")
+load("Data/RData/brol_effect_size_family.RData")
 

### 2019-10-22 Supplementary_material/Prueba_para_Sam.Rmd
Edits

--- 2019-10-22 Supplementary_material/Effect_size_families_plot.Rmd
@@
 
-load("Data/RData/pein_effect_size_family.RData")
-
-p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ippu_effect_size_family.RData")
-
-p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ipaq_effect_size_family.RData")
-
-p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ersa_effect_size_family.RData")
-
-p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/caan_effect_size_family.RData")
-
-p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/brra_effect_size_family.RData")
-
-p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/brol_effect_size_family.RData")
-
-p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
  #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
 grid.newpage()
- grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
+ grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2),ggplotGrob(p3), size="last"),cbind(ggplotGrob(pp1),ggplotGrob(pp2),ggplotGrob(p3), size="last"),cbind(ggplotGrob(pp1),ggplotGrob(pp2),ggplotGrob(p3), size="last"),nrow=3))
 ```

### 2019-10-22 Scripts/Analysis/Phylogenetic_signal.R

@@ -1,6 +1,6 @@
 library(ape)
 library(phytools)
-pollen_tree=read.tree("Data/pollen_tree.nwk")
+pollen_tree=read.tree("Data/Nwk/pollen_tree.nwk")
 #pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
 #pollen_tree=read.tree("Data/tree_neighbour.nwk")
 png("phylo.png", units="px", width=8000, height=10000, res=2000)
@@ -8,7 +8,7 @@ plot(pollen_tree, font= 3)
 add.scale.bar(x=0, y=1, length = 0.01)
 
 
-pollen_tree=read.tree("Data/phylo_all_correct_names.nwk")
+pollen_tree=read.tree("Data/Nwk/phylo_all_correct_names.nwk")
 
 png("Figure1.png", units="px", width=12000, height=12000, res=2500)
 plot(pollen_tree, font= 3)
@@ -20,18 +20,18 @@ plot(pollen_tree)
 add.scale.bar(x=0, y=1, length = 0.01)
 #plot(tree_10)
 
-tree_10 <- read.newick("Data/pollen_tree_no_outgroup.nwk")
+tree_10 <- read.newick("Data/Nwk/pollen_tree_no_outgroup.nwk")
 tree_10=as.phylo(tree_10)
 plot.phylo(tree_10)
 add.scale.bar(x=0, y=9)
 
 #For row names of traits all
-readRDS("Manuscript_draft/Data/matrix_scale_effect.Rda")
+readRDS("Data/RData/matrix_scale_effect.Rda")
 
 #From here I start working with the traits
-traits_all <- read.csv("Data/traits_all.csv", sep=",")
-si_index <- readRDS("Data/si_index.RData")
-matrix_scale_effect <- readRDS("Data/matrix_scale_effect.RDa")
+traits_all <- read.csv("Data/Csv/traits_all.csv", sep=",")
+si_index <- readRDS("Data/Csv/si_index.RData")
+matrix_scale_effect <- readRDS("Data/RData/matrix_scale_effect.RDa")
 traits_all$si_index <- si_index
 rownames(traits_all) <- rownames(matrix_scale_effect)
 traits_all <- traits_all[,-c(1:3,9,13)]

### 2020-04-05 Supplementary_material/Supp_Material.Rmd
Supp material on the way

---
title: "__Supporting Information:__"
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    toc: false
---

# Recipient and donor characteristics govern hierarchical structure in a heterospecific pollen competition network of co-flowering plants

__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman, Romina Rader

The following Supporting Information is available for this article:

__Table S1.__ Species names, common names, varieties and sources of the different seeds.

__Table S2.__ Numerical values of all the traits measured for each species.

__Table S3.__ Seed set in percentage for hand cross-pollination, hand self-pollination, natural selfing and apomixis for all species.

__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.

__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.

__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.

__Table S7.__ Phylogenetic signal and significance for all the different traits

__Table S8.__ Procrustes analysis results.

__Figure S1.__ Correlation matrix for all the different traits.

__Figure S2.__ Total amount of pollen found for the different treatments.

__Figure S3.__ Pollen ratios for the different recipient species.

__Figure S4.__ Pollen ratios for the different recipient species by family.

__Figure S5.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.

__Figure S6.__ Violin plot of the reproductive biology of the species.

__Figure S7.__ Grouped effect sizes by family for each recipient species.

### 2020-04-05 Supplementary_material/Supp_Material.tex
Supp material on the way

--- 2019-10-21 Old/Tables_and_figures.tex
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage[margin=1in]{geometry}
-\usepackage{hyperref}
-\hypersetup{unicode=true,
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
+\hypersetup{
+            pdftitle={Supporting Information:},
             pdfborder={0 0 0},
@@
 \urlstyle{same}  % don't use monospace font for urls
-\usepackage{longtable,booktabs}
+\usepackage[margin=1in]{geometry}
 \usepackage{graphicx,grffile}
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\newcommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{}
-    \pretitle{\vspace{\droptitle}}
-  \posttitle{}
+\title{\textbf{Supporting Information:}}
 \author{}
-    \preauthor{}\postauthor{}
-    \date{}
-    \predate{}\postdate{}
-
-\usepackage{booktabs}
-\usepackage{longtable}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage[table]{xcolor}
-\usepackage{wrapfig}
-\usepackage{float}
-\usepackage{colortbl}
-\usepackage{pdflscape}
-\usepackage{tabu}
-\usepackage{threeparttable}
-\usepackage{threeparttablex}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-
-\usepackage{leading}
-\leading{18pt}
+\date{\vspace{-2.5em}}
 
 \begin{document}
+\maketitle
 
---
+\section{Recipient and donor characteristics govern hierarchical
+structure in a heterospecific pollen competition network of co-flowering
+plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}
 
-\textbf{Table 1}
+\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
+Romina Rader
 
-\begin{longtable}[]{@{}lll@{}}
-\toprule
-Family & Genus & Species\tabularnewline
-\midrule
-\endhead
-Brassicaceae & Brassica & Brassica rapa\tabularnewline
-Brassicaceae & Brassica & Brassica oleracea\tabularnewline
-Brassicaceae & Eruca & Eruca versicaria\tabularnewline
-Brassicaceae & Sinapis & Sinapis alba\tabularnewline
-Convolvulaceae & Ipomoea & Ipomoea aquatica\tabularnewline
-Convolvulaceae & Ipomoea & Ipomoea purpurea\tabularnewline
-Solanaceae & Capsicum & Capsicum annuum\tabularnewline
-Solanaceae & Petunia & Petunia integrifolia\tabularnewline
-Solanaceae & Solanum & Solanum lycopersicum\tabularnewline
-Solanaceae & Solanum & Solanum melongena\tabularnewline
-\bottomrule
-\end{longtable}
+The following Supporting Information is available for this article:
 
-\newpage
+\textbf{Table S1.} Species names, common names, varieties and sources of
+the different seeds.
 
-\newpage
+\textbf{Table S2.} Numerical values of all the traits measured for each
+species.
 
-\textbf{Table 3}
+\textbf{Table S3.} Seed set in percentage for hand cross-pollination,
+hand self-pollination, natural selfing and apomixis for all species.
 
-\begin{longtable}[]{@{}lllr@{}}
-\toprule
-Family & Species & Donor & Seeds\tabularnewline
-\midrule
-\endhead
-Brassicaceae & B. oleracea & C. annuum & 5\tabularnewline
-Brassicaceae & B. rapa & B. oleracea & 2\tabularnewline
-Brassicaceae & B. rapa & B. oleracea & 13\tabularnewline
-Brassicaceae & B. rapa & S. lycopersicum & 1\tabularnewline
-Brassicaceae & B. rapa & B. oleracea & 7\tabularnewline
-Brassicaceae & B. rapa & B. oleracea & 5\tabularnewline
-Brassicaceae & S. alba & B. oleracea & 7\tabularnewline
-Brassicaceae & E. sativa & C. annuum & 6\tabularnewline
-Brassicaceae & E. sativa & C. annuum & 1\tabularnewline
-Solanaceae & S. lycopersicum & S. alba & 3\tabularnewline
-Solanaceae & S. melongena & P. integrifolia & 36\tabularnewline
-Solanaceae & C. annuum & S. alba & 127\tabularnewline
-Solanaceae & C. annuum & E. sativa & 3\tabularnewline
-\bottomrule
-\end{longtable}
+\textbf{Table S4.} Species x species matrix with the significance of
+effect ``yes'' or ``no'' of the different donors on the seed set of the
+different recipient species.
 
-\newpage
+\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
+effect of the different 9 donors on each recipient species.
 
-\includegraphics[width=1\linewidth]{images/phylo_image} \textbf{Figure
-1} \newpage
+\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
+treatments for the different recipient species.
 
-\begin{center}\includegraphics{output/figures/unnamed-chunk-4-1} \end{center}
+\textbf{Table S7.} Phylogenetic signal and significance for all the
+different traits
 
-\textbf{Figure 2}
+\textbf{Table S8.} Procrustes analysis results.
 
-\newpage
+\textbf{Figure S1.} Correlation matrix for all the different traits.
 
-\begin{center}\includegraphics{output/figures/unnamed-chunk-5-1} \end{center}
+\textbf{Figure S2.} Total amount of pollen found for the different
+treatments.
 
-\textbf{Figure 3}
+\textbf{Figure S3.} Pollen ratios for the different recipient species.
 
-\newpage
+\textbf{Figure S4.} Pollen ratios for the different recipient species by
+family.
 
-\includegraphics{output/figures/unnamed-chunk-6-1.pdf} \textbf{Figure 4}
+\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
+pollen donor and recipient.
 
-\newpage
+\textbf{Figure S6.} Violin plot of the reproductive biology of the
+species.
 
-\includegraphics{output/figures/unnamed-chunk-7-1.pdf} \textbf{Figure 5}
-
-\newpage
-
-\begin{center}\includegraphics{output/figures/unnamed-chunk-8-1} \end{center}
-
-\textbf{Figure 6}
-
-\newpage
-
-\begin{center}\includegraphics{output/figures/unnamed-chunk-9-1} \end{center}
-
-\textbf{Figure 8}
-
-\newpage
-
-\begin{center}\includegraphics{output/figures/unnamed-chunk-10-1} \end{center}
-
-\textbf{Figure 9}
-
-\newpage
-
-\section{List of tables}\label{list-of-tables}
-
-\textbf{Table 1} Species list with family and genus.
-
-\textbf{Table 2} Results of hand corss-pollination, hand
-self-pollination, natural selfing (unpollinated bagged flowers) and
-apomixis. The values are the average seed production per treatment
-(N=10) divided by the average number of ovules per species.
-
-\textbf{Table 3} Seed production for the treatments that produced seeds
-with 100\% foreign pollen.
-
-\section{List of figures}\label{list-of-figures}
-
-\textbf{Figure 1} Phylogenetic tree of the species used in the
-experiment from three different families from top to bottom:
-Brassicaceae, Convolvulaceae and Solanaceae.
-
-\textbf{Figure 2} Barplot of the different tests of the reproductive
-biology of the species. The y axis is the percentage of ovules converted
-to seed. The different treatments are, hand cross-pollination, hand
-self-pollination, natural selfing and apomixis (N=10 for all of them).
-
-\textbf{Figure 3} The impact of foreign pollen on recipient plant
-species. Effect sizes (with 95\% confidence intervals) of 9 different
-donor species of heterospecific pollen upon all recipients.
-
-\textbf{Figure 4} The response of heterospecific pollen upon 10
-recipient plant species. Each panel represents one recipient plant
-species crossed with 50\% mixes of the other 9 species.
-
-\textbf{Figure 5} The impact of foreign pollen on recipient plant
-species. Effect sizes (with 95\% confidence intervals) of the species
-grouped per family upon all recipients.
-
-\textbf{Figure 6} Phylogenetic signal of hterospecific pollen effect
-(hedges' g)
-
-\textbf{Figure 7} (comment) Simple Pearson correlation in order to show
-a possible path to follow in the article showing that style length and
-stigma size could explain the effect in Solanaceae species.
-
-\textbf{Figure 8} Pollen ratio counts on stigma after hand pollination
-with 50-50\% mix. The panel is divided by family: A) Brassicaceae, B)
-Convolvulaceae and C) Solanaceae. The pollen recipient species is
-coloured in black and the donor species in grey.
-
-\textbf{Figure 9} Total pollen counts on stigma after hand pollination
-with 50-50\% mix. The panel is divided by family: A) Brassicaceae, B)
-Convolvulaceae and C) Solanaceae. The pollen recipient species is
-coloured in black and the donor species in grey.
+Figure S7. Grouped effect sizes by family for each recipient species.
 

### 2020-04-05 Supplementary_material/Supp_Material.Rmd
Changing font size and spacing
Preparing appendix to have an rmd file for chapter 1

@@
 ---
-title: "__Supporting Information:__"
 output: 
@@
     toc: false
+fontsize: 12pt
+header-includes:
+    - \usepackage{setspace}\doublespacing
+    - \usepackage{float}
+
 ---
+
+# Supporting information:
 
@@
 __Figure S7.__ Grouped effect sizes by family for each recipient species.
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(knitr)
+library(kableExtra)
+
+Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+
+Species <- as.character(Species)
+
+Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")
+
+Common_names <- as.character(Common_names)
+
+Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers")
+
+Variety <- as.character(Variety)
+
+Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
+
+Source <- as.character(Source)
+
+t <- data.frame(Species, Common_names, Variety, Source)
+
+kable(t, "latex", booktabs = T) %>%
+kable_styling(font_size = 7)
+```

### 2020-04-05 Supplementary_material/Supp_Material.tex
Changing font size and spacing
Preparing appendix to have an rmd file for chapter 1

@@
-\documentclass[]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 \hypersetup{
-            pdftitle={Supporting Information:},
             pdfborder={0 0 0},
@@
 
-\title{\textbf{Supporting Information:}}
+\usepackage{setspace}\doublespacing
+\usepackage{float}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
 \author{}
@@
 \begin{document}
-\maketitle
+
+\section{Supporting information:}\label{supporting-information}
 
@@
 
-Figure S7. Grouped effect sizes by family for each recipient species.
+\textbf{Figure S7.} Grouped effect sizes by family for each recipient
+species.
+
+\newpage
+
+\begin{table}[H]
+\centering\begingroup\fontsize{7}{9}\selectfont
+
+\begin{tabular}{llll}
+\toprule
+Species & Common\_names & Variety & Source\\
+\midrule
+Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
+Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
+Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
+Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
+Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
+\addlinespace
+Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
+Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
+Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
+Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
+Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\
+\bottomrule
+\end{tabular}
+\endgroup{}
+\end{table}
 

### 2020-06-25 Thesis_Chapter_1/Supp_Material.Rmd
Supp.
Preparing tables to make all supplementarial material with markdown

--- 2020-04-05 Supplementary_material/Supp_Material.Rmd
@@
     toc: false
+fontsize: 12pt
+header-includes:
+    - \usepackage{setspace}\doublespacing
+    - \usepackage{float}
+
 ---
-
-# Recipient and donor characteristics govern hierarchical structure in a heterospecific pollen competition network of co-flowering plants
-
-__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman, Romina Rader
-
-The following Supporting Information is available for this article:
-
-__Table S1.__ Species names, common names, varieties and sources of the different seeds.
-
-__Table S2.__ Numerical values of all the traits measured for each species.
-
-__Table S3.__ Seed set in percentage for hand cross-pollination, hand self-pollination, natural selfing and apomixis for all species.
-
-__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
-
-__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
-
-__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
-
-__Table S7.__ Phylogenetic signal and significance for all the different traits
-
-__Table S8.__ Procrustes analysis results.
-
-__Figure S1.__ Correlation matrix for all the different traits.
-
-__Figure S2.__ Total amount of pollen found for the different treatments.
-
-__Figure S3.__ Pollen ratios for the different recipient species.
-
-__Figure S4.__ Pollen ratios for the different recipient species by family.
-
-__Figure S5.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.
-
-__Figure S6.__ Violin plot of the reproductive biology of the species.
-
-__Figure S7.__ Grouped effect sizes by family for each recipient species.

### 2020-06-25 Thesis_Chapter_1/Supp_Material.tex
Preparing tables to make all supplementarial material with markdown

--- 2020-04-05 Supplementary_material/Supp_Material.tex
@@
-\documentclass[]{article}
+\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
   \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provides euro and other symbols
 \else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
+  \usepackage{unicode-math}
   \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\usepackage{hyperref}
 \hypersetup{
-            pdftitle={Supporting Information:},
             pdfborder={0 0 0},
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
@@
 
-\title{\textbf{Supporting Information:}}
+\usepackage{setspace}\doublespacing
+\usepackage{float}
+
 \author{}
@@
 \begin{document}
-\maketitle
-
-\section{Recipient and donor characteristics govern hierarchical
-structure in a heterospecific pollen competition network of co-flowering
-plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}
-
-\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
-Romina Rader
-
-The following Supporting Information is available for this article:
-
-\textbf{Table S1.} Species names, common names, varieties and sources of
-the different seeds.
-
-\textbf{Table S2.} Numerical values of all the traits measured for each
-species.
-
-\textbf{Table S3.} Seed set in percentage for hand cross-pollination,
-hand self-pollination, natural selfing and apomixis for all species.
-
-\textbf{Table S4.} Species x species matrix with the significance of
-effect ``yes'' or ``no'' of the different donors on the seed set of the
-different recipient species.
-
-\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
-effect of the different 9 donors on each recipient species.
-
-\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
-treatments for the different recipient species.
-
-\textbf{Table S7.} Phylogenetic signal and significance for all the
-different traits
-
-\textbf{Table S8.} Procrustes analysis results.
-
-\textbf{Figure S1.} Correlation matrix for all the different traits.
-
-\textbf{Figure S2.} Total amount of pollen found for the different
-treatments.
-
-\textbf{Figure S3.} Pollen ratios for the different recipient species.
-
-\textbf{Figure S4.} Pollen ratios for the different recipient species by
-family.
-
-\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
-pollen donor and recipient.
-
-\textbf{Figure S6.} Violin plot of the reproductive biology of the
-species.
-
-Figure S7. Grouped effect sizes by family for each recipient species.
 

### 2020-06-25 Scripts/Data_preparation/Tables_supplementary.R

@@ -1,0 +1,30 @@
+
+#TABLE S1 PREPARED ON 
+#TABLE S2
+#Code to create table 
+traits_all <- read.csv("Data/Csv/traits_scinames.csv")
+head(traits_all)
+traits <- traits_all[,-c(1,2,4,10,14)]
+traits_edit_order <- traits[,-c(2,12,13,14)]
+traits_edit_order$ovary_length <- traits_all$ovary_length
+traits_edit_order$ovary_width <- traits_all$ovary_width
+traits_edit_order$Selfing_rate <- traits_all$Selfing_rate
+traits_edit_order$si_index <- traits_all$si_index
+saveRDS(traits_edit_order, "Thesis_Chapter_1/Tables/traits_supplementary.rds")
+#TABLE S3
+rep_biology <- readRDS("Thesis_chapter_1/Tables/rep_treatments.rds")
+#loadlibrary
+library(reshape2)
+rep_biology_1 <- dcast(Species   ~ Treatment+., value.var = "Seed_set", fun.aggregate = mean,
+                      data = rep_biology, na.rm= TRUE)
+
+rep_biology_1$Species <- c("Brassica oleracea", "Brassica rapa", "Capsicum annuum", "Eruca sativa", "Ipomoea aquatica",
+   "Ipomoea purpurea", "Petunia integrifolia", "Sinapis alba", " Solanum lycopersicum", "Solanum melongena")
+rep_biology_1$Apomixis_1 <- rep_biology_1$Apomixis
+rep_biology_1 <- rep_biology_1[,-2]
+colnames(rep_biology_1)[5] <- "Apomixis"
+saveRDS(rep_biology_1, "Thesis_Chapter_1/Tables/rep_biology_supplementary.rds")
+
+
+
+

### 2020-06-25 Thesis_Chapter_1/Supp_Material.Rmd
Supporting info Chapter 1 with markdown

--- 2020-04-05 Supplementary_material/Supp_Material.Rmd
@@
 __Figure S7.__ Grouped effect sizes by family for each recipient species.
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(knitr)
+library(kableExtra)
+Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+Species <- as.character(Species)
+
+Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")
+Common_names <- as.character(Common_names)
+Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers") 
+Variety <- as.character(Variety)
+Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
+Source <- as.character(Source)
+t <- data.frame(Species, Common_names, Variety, Source)
+kable(t, "latex", booktabs = T) %>%
+kable_styling(font_size = 7)
+```
+
+\begin{landscape}
+```{r}
+```
+\end{landscape}

### 2020-06-25 Thesis_Chapter_1/Supp_Material.tex
Supporting info Chapter 1 with markdown

--- 2020-04-05 Supplementary_material/Supp_Material.tex
@@
-\documentclass[12pt,]{article}
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  12pt,
+]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
 \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
+% Use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
+\IfFileExists{microtype.sty}{% use microtype if available
   \usepackage[]{microtype}
@@
 }{}
-\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
-\usepackage[unicode=true]{hyperref}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
 \hypersetup{
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\IfFileExists{parskip.sty}{%
-\usepackage{parskip}
-}{% else
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{0}
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-% set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 \usepackage{setspace}\doublespacing
@@
 
-\section{Supporting information:}\label{supporting-information}
+\hypertarget{supporting-information}{%
+\section{Supporting information:}\label{supporting-information}}
 
+\hypertarget{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}{%
 \section{Recipient and donor characteristics govern hierarchical
 structure in a heterospecific pollen competition network of co-flowering
-plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}
+plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}}
 
@@
 
+\begin{landscape}
+
+\end{landscape}
+
 \end{document}

### 2020-06-26 Thesis_Chapter_1/Supp_Material.Rmd
Adding table with all traits
Supplementary material with Markdown

--- 2020-04-05 Supplementary_material/Supp_Material.Rmd
@@
     fig_caption: yes
-    toc: false
+    toc: no
+  html_document:
+    toc: no
+    df_print: paged
 fontsize: 12pt
@@
 - \usepackage{float}
+- \usepackage{caption}
 
 ---
+\captionsetup[figure]{labelformat=empty}
+\captionsetup[table]{labelformat=empty}
+\renewcommand{\figurename}{}
 
@@
 
+#TABLE S1
 ```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
@@
 library(kableExtra)
-
 Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-
 Species <- as.character(Species)
@@
 Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")
+Common_names <- as.character(Common_names)
+Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers") 
+Variety <- as.character(Variety)
+Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
+Source <- as.character(Source)
+t <- data.frame(Species, Common_names, Variety, Source)
+kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T) %>% row_spec(0,bold=TRUE)  
+```
 
-Common_names <- as.character(Common_names)
+\begin{landscape}
 
-Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers")
+TABLE S2
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
 
-Variety <- as.character(Variety)
+dat <- readRDS("Tables/traits_supplementary.rds")
+#Convert to square mm and mm
+dat$stigma_area <- dat$stigma_area/1000000
+dat[,c(7:12)] <- dat[,c(7:12)]/1000
 
-Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
+colnames(dat) <- c("Species", "Pollen size $\\mu$m", "Pollen grains per anther", "Ovule number", "Pollen:ovule ratio", "Stigma area $\\mu$m$^{2}$", "Stigma length (mm)", "Stigma width (mm)", "Style length (mm)", "Style width (mm)", "Ovary length (mm)", "Ovary width (mm)", "Selfing rate", "SI index")
 
-Source <- as.character(Source)
+kable(dat, "latex", longtable = F, escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
+```
 
-t <- data.frame(Species, Common_names, Variety, Source)
+\end{landscape}
 
-kable(t, "latex", booktabs = T) %>%
-kable_styling(font_size = 7)
+TABLE S3
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
+dat <- readRDS("Tables/rep_biology_supplementary.rds")
+kable(dat, "latex", longtable = F, escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
 ```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center'}
+setwd("~/R_projects/Hp_pollen_experiment")
+
+#Script to plot the reproductive biology tests
+#load libraries
+library(ggplot2)
+#install.packages("devtools")
+library(devtools)
+#install_github("easyGgplot2", "kassambara")
+
+brol <- read.csv("Raw_data/brol_seed_set_final.csv")
+brra <- read.csv("Raw_data/brra_seed_set_final.csv")
+ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
+sial <- read.csv("Raw_data/sial_seed_set_final.csv")
+ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
+ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
+caan <- read.csv("Raw_data/caan_seed_set_final.csv")
+pein <- read.csv("Raw_data/pein_seed_set_final.csv")
+soly <- read.csv("Raw_data/soly_seed_set_final.csv")
+some <- read.csv("Raw_data/some_seed_set_final.csv")
+#loading traits to divide by number of ovules the seed set 
+traits <- read.csv("Data/Csv/traits_scinames.csv")
+
+brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
+brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
+brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
+ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
+sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
+ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
+ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
+caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
+pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
+soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
+some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
+
+d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
+d$Seed_set[d$Seed_set>100]<-100
+
+#levels(d$Treatment)
+d$Treatment=as.character(d$Treatment)
+d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="Control"]<-"Apomixis"
+d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
+d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
+
+d$Species=as.character(d$Species)
+d$Species[d$Family=="BROL"]<-"B"
+d$Species[d$Family=="BRRA"]<-"B"
+d$Species[d$Family=="ERSA"]<-"B"
+d$Species[d$Family=="SIAL"]<-"B"
+d$Species[d$Family=="IPPU"]<-"C"
+d$Species[d$Family=="IPAQ"]<-"C"
+d$Species[d$Family=="SOME"]<-"S"
+d$Species[d$Family=="SOLY"]<-"S"
+d$Species[d$Family=="PEIN"]<-"S"
+d$Species[d$Family=="CAAN"]<-"S"
+
+d$Species[d$Species=="BROL"]<-"B. oleracea"
+d$Species[d$Species=="BRRA"]<-"B. rapa"
+d$Species[d$Species=="SIAL"]<-"S. alba"
+d$Species[d$Species=="ERSA"]<-"E. sativa"
+d$Species[d$Species=="IPPU"]<-"I. purpurea"
+d$Species[d$Species=="IPAQ"]<-"I. aquatica"
+d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
+d$Species[d$Species=="SOME"]<-"S. melongena"
+d$Species[d$Species=="PEIN"]<-"P. integrifolia"
+d$Species[d$Species=="CAAN"]<-"C. annuum"
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
+rep_bio <- ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
+  geom_violin(scale = "width",draw_quantiles = c(0.5))+
+  geom_dotplot(binaxis='y', 
+               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
+  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(legend.title = element_blank(),plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
+
+rep_bio
+ #pdf("test.pdf", width = 12, height = 5)
+
+ #ggsave("Images_publication/Figure2.png", width = 12, height = 5,dpi = 1200)
+
+ggsave(filename = "rep_bio.pdf", rep_bio, width = 12, height = 5, units = "in",dpi = 1000)
+
+# insert ggplot code
+dev.off()
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="S7"}
+
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+setwd("~/R_projects/Hp_pollen_experiment")
+load("Data/RData/some_effect_size_family.RData")
+
+pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/soly_effect_size_family.RData")
+
+pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/sial_effect_size_family.RData")
+
+p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/pein_effect_size_family.RData")
+
+p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/ippu_effect_size_family.RData")
+
+p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/ipaq_effect_size_family.RData")
+
+p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/ersa_effect_size_family.RData")
+
+p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/caan_effect_size_family.RData")
+
+p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/brra_effect_size_family.RData")
+
+p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/brol_effect_size_family.RData")
+
+p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+grid.newpage()
+ grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
+```

### 2020-06-26 Thesis_Chapter_1/Supp_Material.tex
Adding table with all traits
Supplementary material with Markdown

@@
 \usepackage{float}
+\usepackage{caption}
 \usepackage{booktabs}
@@
 \begin{document}
+
+\captionsetup[figure]{labelformat=empty}
+
+\captionsetup[table]{labelformat=empty}
+\renewcommand{\figurename}{}
 
@@
 
-\begin{table}[H]
-\centering\begingroup\fontsize{7}{9}\selectfont
+\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont
 
-\begin{tabular}{llll}
+\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\toprule
+\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
+\midrule
+\endfirsthead
+\multicolumn{4}{@{}l}{\textit{(continued)}}\\
 \toprule
@@
 \midrule
-Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
+\endhead
+\
+\endfoot
+\bottomrule
+\endlastfoot
+\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
+\addlinespace
 Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
-Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
+\addlinespace
+\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
+\addlinespace
 Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
-Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
+\addlinespace
+\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
 \addlinespace
 Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
-Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
+\addlinespace
 Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
-Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
-Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\
-\bottomrule
-\end{tabular}
+\addlinespace
+\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
+\addlinespace
+Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
+\end{longtabu}
 \endgroup{}
-\end{table}
 
@@
 
+TABLE S2
+\begingroup\fontsize{6}{8}\selectfont
+
+\resizebox{\linewidth}{!}{
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
+\midrule
+\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
+\addlinespace
+Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
+\addlinespace
+Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
+\addlinespace
+\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
+\addlinespace
+Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
+\addlinespace
+\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
+\addlinespace
+Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
+\addlinespace
+\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
+\addlinespace
+Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
+\bottomrule
+\end{tabu}}
+\endgroup{}
+
 \end{landscape}
 
+TABLE S3 \begingroup\fontsize{6}{8}\selectfont
+
+\resizebox{\linewidth}{!}{
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
+\midrule
+\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
+\addlinespace
+Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
+\addlinespace
+Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
+\addlinespace
+\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
+\addlinespace
+Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
+\addlinespace
+\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
+\addlinespace
+Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
+\addlinespace
+\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
+\addlinespace
+Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
+\bottomrule
+\end{tabu}}
+\endgroup{}
+
+\newpage
+
+\begin{center}\includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-4-1} \end{center}
+
+\begin{verbatim}
+## null device 
+##           1
+\end{verbatim}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{S7}
+\end{figure}
+
 \end{document}

### 2020-06-26 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary mat

@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center'}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+library(ggplot2)
+setwd("~/R_projects/Hp_pollen_experiment")
+total_pollen <- read.csv("Data/Csv/total_pollen.csv")
+ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
+  geom_bar(stat='identity', position='dodge')+theme_minimal()+
+  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
+  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+par(mar=c(30,13,2,4),xpd=F)
+setwd("~/R_projects/Hp_pollen_experiment")
+data_percentage <-readRDS("Data/RData/per.RData")
+data_percentage=as.matrix(data_percentage)
+coul = c("#999999","#779799")
+barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
+ "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
+legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
+abline(v=50,col="black")
+
+#lines(c(0,10),50,col="red")
+```
+
+\newpage
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+par(mar=c(2,13,2,4),xpd=F)
+par(mfrow=c(3,1))
+setwd("~/R_projects/Hp_pollen_experiment")
+ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
+barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E.
+sativa-I.
+purpurea", "B.
+oleracea-I.
+purpurea","B.
+rapa-I.
+purpurea", "S.
+alba-I.
+aquatica", "S.
+alba-S.
+melongena", "E.
+sativa-P.
+integrifolia", "B.
+rapa-S.
+lycopersicum", "B.
+oleracea-C.
+annuum"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+text(8.3,6.8,"A) Brassicaceae")
+ratio_con <-readRDS("Data/RData/ratio_con.RData")
+barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I.
+purpurea-S.
+melongena","I.
+aquatica-C.
+annuum","I.
+purpurea-E.
+sativa","I.
+aquatica-S.
+alba"))
+abline(v=50,col="black")
+legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
+text(9,3.5,"B) Convolvulaceae")
+
+ratio_sol <-readRDS("Data/RData/ratio_sol.RData")
+barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
+annuum-I.
+purpurea", "S.
+melongena-I.
+aquatica", "P.
+integrifolia-I.
+aquatica", "S.
+lycopersicum-I aquatica","S.
+melongena-E.
+sativa", "P.
+integrifolia-E.
+sativa", "C.
+annuum-S.
+alba", "S.
+lycopersicum-B.
+rapa"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+text(6.8,6.8,"C) Solanaceae")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, fig.align='center', fig.cap="Fig S5"}
+
+#Here I try to compare the different proportions of pollen between the different groups
+#I use Tukey method
+
+library(lme4)
+library(emmeans)
+library(reshape2)
+library(multcompView)
+library(lsmeans)
+library(multcomp)
+library(ggplot2)
+library(DHARMa)
+setwd("~/R_projects/Hp_pollen_experiment")
+
+total_pollen <- read.csv("Data/Csv/total_pollen.csv")
+
+total_pollen=total_pollen[,-1]
+colnames(total_pollen)[3] <- "pollen"
+#head(total_pollen)
+
+# Dividing by focal pollen and non focal pollen
+# In order to compare pollen as donor and recipient per family 
+pollen_foc <- subset(total_pollen, variable=="focal_pollen")
+pollen_non <- subset(total_pollen, variable=="non_focal_pollen")
+
+total  <- as.numeric(pollen_foc$pollen) + as.numeric(pollen_non$pollen)
+pollen_non$total_pollen  <- total
+pollen_non$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
+pollen_non$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
+                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
+                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
+                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
+
+pollen_non <- pollen_non[,-c(1,2)]
+colnames(pollen_non)[1] <-"hp_pollen"
+pollen_non$hp_ratio <- as.numeric(pollen_non$hp_pollen)/as.numeric(pollen_non$total_pollen)
+#hist(pollen_non$hp_ratio)
+
+pollen_foc$total_pollen  <- total
+pollen_foc$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
+pollen_foc$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
+                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
+                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
+                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
+
+pollen_foc <- pollen_foc[,-c(1,2)]
+colnames(pollen_foc)[1] <-"hp_pollen"
+pollen_foc$hp_ratio <- as.numeric(pollen_foc$hp_pollen)/as.numeric(pollen_foc$total_pollen)
+#hist(pollen_foc$hp_ratio)
+
+#Analyse data and plot it
+
+junk.glmer = lm(hp_ratio ~ fam_non, data = pollen_non)
+#plot(junk.glmer)
+#goodness of fit of the model
+#testDispersion(junk.glmer)
+#simulationOutput <- simulateResiduals(fittedModel = junk.glmer, plot = T)
+
+#lsm = lsmeans(junk.glmer, "fam_non", type = "response")
+#pairs(lsm)
+#CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
+
+#ggplot(CLD,aes(x= fam_non,y= lsmean,
+#label = .group)) +theme_minimal()+
+#geom_point(shape  = 15,size   = 4) +ggtitle("B) Comparison of ratios as donor")+
+#geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
+#width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+
+#geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black")
+
+#Analyse data and plot it
+junk.glmer = lm(hp_ratio ~ fam_foc, data = pollen_foc)
+lsm = lsmeans(junk.glmer, "fam_foc", type = "response")
+#pairs(lsm)
+CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
+
+#theme
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  library(grid)
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.3)),
+            axis.text=element_text(size = rel(1), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(0.8, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_line(),
+            panel.grid.minor.y= element_blank()
+      ))
+}
+
+par(mfrow=c(2,2))
+ggplot(CLD,aes(x= fam_foc,y= lsmean,
+               label = .group)) +theme_ms()+
+  geom_point(shape  = 15,size   = 4) +ggtitle("")+
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
+                width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+ geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(axis.text.x = element_text(size=14, face="bold"))
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center', fig.cap="Fig S6"}
 setwd("~/R_projects/Hp_pollen_experiment")

### 2020-06-26 Thesis_Chapter_1/Supp_Material.tex
Supplementary mat

@@
 \captionsetup[figure]{labelformat=empty}
-
 \captionsetup[table]{labelformat=empty}
@@
 
-\begin{center}\includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-4-1} \end{center}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
+
+\newpage
+
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
+
+\newpage
+
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
+
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1}
+
+}
+
+\caption{Fig S5}\label{fig:unnamed-chunk-7}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-8-1}
+
+}
+
+\caption{Fig S6}\label{fig:unnamed-chunk-8}
+\end{figure}
 
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{S7}

### 2020-06-26 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary

@@
 
-__Figure S5.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.
+__Figure S5.__ Unipartite bidirectional network with asymmetrical effect
 
-__Figure S6.__ Violin plot of the reproductive biology of the species.
+__Figure S6.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.
 
-__Figure S7.__ Grouped effect sizes by family for each recipient species.
+__Figure S7.__ Violin plot of the reproductive biology of the species.
+
+__Figure S8.__ Grouped effect sizes by family for each recipient species.
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S2"}
 library(ggplot2)
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="Fig S3"}
 par(mar=c(30,13,2,4),xpd=F)
@@
 \newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S4"}
 par(mar=c(2,13,2,4),xpd=F)
@@
 
-\newpage
+\clearpage
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, fig.align='center', fig.cap="Fig S5"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
+S4** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
+These pollen ratios are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20)."}
 
@@
 
-par(mfrow=c(2,2))
 ggplot(CLD,aes(x= fam_foc,y= lsmean,
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12, out.width = "100%", fig.align='center', fig.cap="Fig S6"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig.
+S5** Unipartite bidirectional network with asymmetrical effect.
+The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species.
+All the arrow heads point to the recipient species of the reciprocal interaction.
+Lines of species that did not have a negative impact are not represented.
+The different nodes and the donor species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).
+The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size.
+Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}
+library(statnet)
+library(reshape2)
+library(sna)
+library(igraph)
+setwd("~/R_projects/Hp_pollen_experiment")
+
+#######################################
+############ Data preparataion ########
+#######################################
+
+#In this script I'm going to plot the transitivity of the effect oh HP pollen with effect sizes
+effect <- readRDS("Data/RData/matrix_effect_size.RData")
+#Now I convert the few values over 0 to maximum 0 (control)
+effect[effect>0]<-0
+#absolute values so less confusing without negative values
+#So now greater values involve greater effect
+#(opposite way in comparison with negative values as before)
+effect=abs(effect)
+#UNIPARTITE DOUBLE ASSYMETRICAL EFFECT
+G <- graph.adjacency(t(effect),weighted=TRUE,diag=FALSE)
+#plot(G)
+E <- t(apply(get.edgelist(G),1,sort))
+E(G)$curved <- 0
+E(G)[duplicated(E) | duplicated(E,fromLast =TRUE)]$curved <- 0.2
+plot(G, edge.width=E(G)$weight/0.5,  vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),
+              "#D55E00","#0072B2", rep("#D55E00",2)),edge.arrow.size=0.8,edge.color=adjustcolor(c(rep("#0072B2",8),rep("#0072B2",8), rep("#D55E00",7), 
+              rep("#0072B2",9),rep("#009E73",7),rep("#009E73",9),rep("#D55E00",7),rep("#0072B2",8), rep("#D55E00",8), rep("#D55E00",7)), alpha.f = .5))
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig S6** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
+Positive correlations are displayed in blue and negative in red.
+The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
+#install.packages("corrplot")
+library(corrplot)
+setwd("~/R_projects/Hp_pollen_experiment")
+#Example
+#I'm going to try to show our traits on this way
+#M <- cor(mtcars)
+#corrplot(M, method = "circle")
+#We can kill two birds with one stone, showing the correlation and all the traits
+traits_all <- read.csv("Data/Csv/traits_all.csv")
+si_index <- readRDS("Data/RData/si_index.RData")
+traits_all$si_index <- si_index
+traits_all=traits_all[,-c(1,2)]
+traits_all=traits_all[,-c(1,7,11)]
+#Change order of ovary width length I rename below in row and colname
+a<-traits_all[,11]
+b<-traits_all[,12]
+traits_all[,11] <-b
+traits_all[,12]<- a
+traits_all<- cor(traits_all)
+
+rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
+                         "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
+                         "Ovary length", "Ovary width", "SI index")
+
+colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
+                "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
+                "Ovary length", "Ovary width", "SI index")
+
+#corrplot(traits_all, method = "circle")
+#corrplot(traits_all, type = "upper")
+par(mar=c(0,4.1,4.1,2.1))
+corrplot(traits_all, type = "lower", tl.cex = 0.8, cl.cex = 0.8, tl.col = "black", tl.srt = 45)
+
+#Add Compatibility index!
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
+S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments (apomixis, hand cross pollination, hand self pollination and spontaneous selfing).
+The coloured dots, represent the different values of seed set for each treatment."}
+
 setwd("~/R_projects/Hp_pollen_experiment")
@@
 #install_github("easyGgplot2", "kassambara")
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
 
@@
 
-rep_bio <- ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
+ ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
   geom_violin(scale = "width",draw_quantiles = c(0.5))+
@@
 
-rep_bio
- #pdf("test.pdf", width = 12, height = 5)
-
- #ggsave("Images_publication/Figure2.png", width = 12, height = 5,dpi = 1200)
-
-ggsave(filename = "rep_bio.pdf", rep_bio, width = 12, height = 5, units = "in",dpi = 1000)
-
-# insert ggplot code
-dev.off()
-
 ```
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="S7"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="**Fig.
+S8** Effect sizes (95% confidence intervals) of the different families on each focal species (recipient) and a hand cross-pollination treatment (control).
+For each species the control treatment appears in yellow and the grouped effect per family in blue for Brassicaceae, green for Convolvulaceae and orange for Solanaceae."}
 

### 2020-06-26 Thesis_Chapter_1/Supp_Material.tex
Supplementary

@@
 
-\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
+\textbf{Figure S5.} Unipartite bidirectional network with asymmetrical
+effect
+
+\textbf{Figure S6.} Statistical comparison of pollen ratios by family as
 pollen donor and recipient.
 
-\textbf{Figure S6.} Violin plot of the reproductive biology of the
+\textbf{Figure S7.} Violin plot of the reproductive biology of the
 species.
 
-\textbf{Figure S7.} Grouped effect sizes by family for each recipient
+\textbf{Figure S8.} Grouped effect sizes by family for each recipient
 species.
@@
 
+\begin{figure}
+\centering
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
-
-\newpage
-
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
-
-\newpage
-
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
-
-\newpage
-
-\begin{figure}
-
-{\centering \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1}
-
-}
-
-\caption{Fig S5}\label{fig:unnamed-chunk-7}
+\caption{Fig S2}
 \end{figure}
@@
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{Supp_Material_files/figure-latex/unnamed-chunk-8-1}
-
-}
-
-\caption{Fig S6}\label{fig:unnamed-chunk-8}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
+\caption{Fig S3}
 \end{figure}
-
-\begin{verbatim}
-## null device 
-##           1
-\end{verbatim}
 
@@
 \centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
+\caption{Fig S4}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1.pdf}
+\caption{\textbf{Fig. S4} Pollen ratios comparisons between the
+different pollen recipient families where the boxes represent least
+square means, the error bars, confidence intervals 95\%, and sharing
+numbers indicate no significant differences between groups (Tukey
+adjusted comparisons). These pollen ratios are the total number of
+heterospecific pollen grains divided by the total quantity of pollen
+(conspecific pollen + heterospecific pollen), and then compared by
+family (N=20).}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-8-1.pdf}
+\caption{\textbf{Fig S5} Unipartite bidirectional network with
+asymmetrical effect. The lines with the arrow heads connect the impact
+of foreign pollen (effect size) of each pollen donor species on each
+recipient species. All the arrow heads point to the recipient species of
+the reciprocal interaction. Lines of species that did not have a
+negative impact are not represented. The different nodes and the donor
+species appear coloured by family: Solanaceae (orange), Brassicaceae
+(blue) and Convolvulaceae (green). The intensity of the effect is
+represented by the line´s size where a larger effect size corresponds to
+a thicker line and a thinner line to a smaller effect size. Species
+code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa,
+SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea,
+CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum
+lycopersicum, SOME: Solanum melongena.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{S7}
+\caption{\textbf{Fig S6} Graphical representation of the correlation
+matrix of the different reproductive traits considered in the
+experiment. Positive correlations are displayed in blue and negative in
+red. The intensity, size and colour of the circles are proportional to
+the correlation coefficient from Pearson's r.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\textbf{Fig. S7} Violin plot of the proportion of seeds
+coverted to ovule (\%) for all species with four different
+hand-pollination treatments (apomixis, hand cross pollination, hand self
+pollination and spontaneous selfing). The coloured dots, represent the
+different values of seed set for each treatment.}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\textbf{Fig. S8} Effect sizes (95\% confidence intervals) of
+the different families on each focal species (recipient) and a hand
+cross-pollination treatment (control). For each species the control
+treatment appears in yellow and the grouped effect per family in blue
+for Brassicaceae, green for Convolvulaceae and orange for Solanaceae.}
 \end{figure}

### 2020-06-28 Thesis_Chapter_1/Supp_Material.Rmd
chapter 1 supp. material with markdown

@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S2"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S1"}
 library(ggplot2)
@@
 
-\newpage
+\clearpage
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="Fig S3"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="**Fig S3** Average proportion of heterospecific pollen per family for the different 20 treatments counted.
+On the label of the y-axis, the first family is the pollen recipient family, and the second, the pollen donor family.
+These pollen ratios are the number of heterospecific pollen grains divided by the total pollen grains per stigma (conspecific and heterospecific pollen) and then averaged by family (N=20).
+The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}
 par(mar=c(30,13,2,4),xpd=F)
@@
 
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S4"}
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap=""}
+
 par(mar=c(2,13,2,4),xpd=F)

### 2020-06-28 Thesis_Chapter_1/Supp_Material.tex
chapter 1 supp. material with markdown

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  12pt,
-]{article}
+\documentclass[12pt,]{article}
 \usepackage{lmodern}
@@
 \usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
 \ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
@@
   \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
   \fi
-% Use upquote if available, for straight quotes in verbatim environments
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
+% use microtype if available
+\IfFileExists{microtype.sty}{%
 \usepackage[]{microtype}
@@
 }{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
 \hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
+            pdfborder={0 0 0},
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage[margin=1in]{geometry}
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+% set default figure placement to htbp
 \makeatletter
@@
 \makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+
 \usepackage{setspace}\doublespacing
@@
 \captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\renewcommand{\figurename}{}
+\captionsetup[table]{labelformat=empty} \renewcommand{\figurename}{}
 
-\hypertarget{supporting-information}{%
-\section{Supporting information:}\label{supporting-information}}
+\section{Supporting information:}\label{supporting-information}
 
-\hypertarget{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}{%
 \section{Recipient and donor characteristics govern hierarchical
 structure in a heterospecific pollen competition network of co-flowering
-plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}}
+plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}
 
@@
 
-\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont
+\section{TABLE S1}\label{table-s1}
+
+\begingroup\fontsize{7}{9}\selectfont
 
@@
 \endhead
-\
+
 \endfoot
@@
 \end{longtabu}
+
 \endgroup{}
@@
 \bottomrule
-\end{tabu}}
-\endgroup{}
+\end{tabu}} \endgroup{}
 
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{Fig S2}
+\caption{Fig S1}
 \end{figure}
 
-\newpage
+\clearpage
 
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{Fig S3}
+\caption{\textbf{Fig S3} Average proportion of heterospecific pollen per
+family for the different 20 treatments counted. On the label of the
+y-axis, the first family is the pollen recipient family, and the second,
+the pollen donor family. These pollen ratios are the number of
+heterospecific pollen grains divided by the total pollen grains per
+stigma (conspecific and heterospecific pollen) and then averaged by
+family (N=20). The vertical bar on intercept 50, represents equal
+proportions of both recipient (grey) and donor (light blue) pollen.}
 \end{figure}
 
-\newpage
+\clearpage
 
-\begin{figure}
-\centering
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Fig S4}
-\end{figure}
 
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-8-1.pdf}
-\caption{\textbf{Fig S5} Unipartite bidirectional network with
+\caption{\textbf{Fig. S5} Unipartite bidirectional network with
 asymmetrical effect. The lines with the arrow heads connect the impact

### 2020-06-29 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary, all figures

--- 2020-06-26 Thesis_Chapter_1/Supp_Material.Rmd
@@
 
-# Recipient and donor characteristics govern hierarchical structure in a heterospecific pollen competition network of co-flowering plants
+# Recipient and donor characteristics govern the hierarchical structure of heterospecific pollen competition networks
 
@@
 
-__Figure S1.__ Correlation matrix for all the different traits.
+__Figure S1__. Total amount of pollen deposited per stigma.
 
-__Figure S2.__ Total amount of pollen found for the different treatments.
+__Figure S2__. Pollen ratios for the different recipient species.
 
-__Figure S3.__ Pollen ratios for the different recipient species.
+__Figure S3__. Pollen ratios for the different recipient species by family.
 
-__Figure S4.__ Pollen ratios for the different recipient species by family.
+__Figure S4__. Statistical comparison of the pollen ratios by family.
 
-__Figure S5.__ Unipartite bidirectional network with asymmetrical effect
+__Figure S5__. Unipartite bidirectional network with asymmetrical effect.
 
-__Figure S6.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.
+__Figure S6__. Correlation matrix for all the different traits.
 
-__Figure S7.__ Violin plot of the reproductive biology of the species.
+__Figure S7__. Species reproductive biology.
 
-__Figure S8.__ Grouped effect sizes by family for each recipient species.
+__Figure S8__. Grouped effect sizes by family for each recipient species.
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S2"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig.
+S1** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
+For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma.
+For each pair of species on the x-axis, the first species is the recipient species, and the second, the donor species."}
+
 library(ggplot2)
+
 setwd("~/R_projects/Hp_pollen_experiment")
@@
 ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
-  geom_bar(stat='identity', position='dodge')+theme_minimal()+
+  geom_bar(stat='identity', position='dodge')+theme_light()+ 
   theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
-  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")
+  scale_fill_manual(values=c("#999999","#779799"),labels = c("Conspecific pollen","Heterospecific pollen"))+labs(x = "",y="Pollen grains per stigma")
 
@@
 
-\newpage
+\clearpage
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="Fig S3"}
-par(mar=c(30,13,2,4),xpd=F)
-setwd("~/R_projects/Hp_pollen_experiment")
-data_percentage <-readRDS("Data/RData/per.RData")
-data_percentage=as.matrix(data_percentage)
-coul = c("#999999","#779799")
-barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
- "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
-legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
-abline(v=50,col="black")
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig.
+S2** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments.
+We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these treatments.
+The proportion of conspecific and heterospecific pollen are shown in grey and light blue respectively.
+For each pair of species on the y-axis, the first species is the pollen recipient and the second the pollen donor.
+The vertical black line represents 50% pollen of both donor and recipient."}
 
-#lines(c(0,10),50,col="red")
-```
-
-\newpage
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S4"}
 par(mar=c(2,13,2,4),xpd=F)
@@
 ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
+coul = c("#999999","#779799")
 barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E.
@@
 abline(v=50,col="black")
-legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+legend(-1,-0.1,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
 text(8.3,6.8,"A) Brassicaceae")
@@
 abline(v=50,col="black")
-legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
+legend(-1,-0.5,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
 text(9,3.5,"B) Convolvulaceae")
@@
 abline(v=50,col="black")
-legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
+legend(-1,-0.1,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
 text(6.8,6.8,"C) Solanaceae")
@@
 
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig.
+S3** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
+We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments.
+Finally, we grouped by family these treatments in order to see general tendencies across families as pollen donor and as pollen recipient.
+Pollen ratios were considered as the number of conspecific or heterospecific pollen grains divided by the total number of pollen grains per stigma.
+On the y-axis, the first family on each pair of plant families is the recipient one, and the second, the family of the donor.
+The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}
+
+par(mar=c(2,8.7,2,2),xpd=F)
+setwd("~/R_projects/Hp_pollen_experiment")
+data_percentage <-readRDS("Data/RData/per.RData")
+data_percentage=as.matrix(data_percentage)
+coul = c("#999999","#779799")
+barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=0.85,cex.names=0.65,names=c("Brassicaceae-Convolvulaceae",
+ "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
+legend(0,-0.5,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul, cex = 0.65)
+abline(v=50,col="black")
+
+#lines(c(0,10),50,col="red")
+```
+
+\clearpage
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
 S4** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
-These pollen ratios are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20)."}
+These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20).
+Brassicacea family is coloured in blue, Convolvulaceae in green and Solanaceae in orange."}
 
@@
                label = .group)) +theme_ms()+
-  geom_point(shape  = 15,size   = 4) +ggtitle("")+
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
-                width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+ geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(axis.text.x = element_text(size=14, face="bold"))
+  geom_point(data = CLD, aes(x = fam_foc, y = lsmean, color = fam_foc),shape  = 15,size   = 4) +
+scale_color_manual(name = "Families",values = c("Convolvulaceae" = "#009E73", "Solanaceae" = "#D55E00", "Brassicaceae" = "#0072B2"))+ggtitle("")+
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = fam_foc),
+                width =  0.2,size =  0.9)+ylab("Least square mean")+xlab("Families")+
+  geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(legend.position = "none")
 
@@
 Lines of species that did not have a negative impact are not represented.
-The different nodes and the donor species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).
+The different nodes and the effect of the donor species on the recipient species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).
 The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size.
 Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}
+
 library(statnet)
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig S6** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig.
+S6** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
 Positive correlations are displayed in blue and negative in red.
@@
 
-rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
+rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen grains/anther", "Number of ovules", "Pollen-ovule ratio",
                          "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
@@
 
-colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
+colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen grains/anther", "Number of ovules", "Pollen-ovule ratio",
                 "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments (apomixis, hand cross pollination, hand self pollination and spontaneous selfing).
+S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
 The coloured dots, represent the different values of seed set for each treatment."}
@@
                dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
-  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(legend.title = element_blank(),plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
+  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="**Fig.
-S8** Effect sizes (95% confidence intervals) of the different families on each focal species (recipient) and a hand cross-pollination treatment (control).
-For each species the control treatment appears in yellow and the grouped effect per family in blue for Brassicaceae, green for Convolvulaceae and orange for Solanaceae."}
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7, fig.cap="**Fig.
+S8** Grouped effect sizes (95% confidence intervals) of the different families on each focal species.
+For each species, the grouped effect by family is compared with the control treatment of hand cross pollination with conspecific pollen.
+The control treatment is represented in yellow and vertically intersected with a dashed line through the mean effect size in order to help the visual interpretation of the effect sizes.
+Any value to the left of the vertical dashed line represents a negative impact of foreign pollen.
+The different effect sizes and confidence intervals are coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green)."}
 
@@
 ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
   xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+

### 2020-06-29 Thesis_Chapter_1/Supp_Material.tex
Supplementary, all figures

--- 2020-06-26 Thesis_Chapter_1/Supp_Material.tex
@@
 
-\hypertarget{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}{%
-\section{Recipient and donor characteristics govern hierarchical
-structure in a heterospecific pollen competition network of co-flowering
-plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}}
+\hypertarget{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}{%
+\section{Recipient and donor characteristics govern the hierarchical
+structure of heterospecific pollen competition
+networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}}
 
@@
 
-\textbf{Figure S1.} Correlation matrix for all the different traits.
+\textbf{Figure S1}. Total amount of pollen deposited per stigma.
 
-\textbf{Figure S2.} Total amount of pollen found for the different
-treatments.
+\textbf{Figure S2}. Pollen ratios for the different recipient species.
 
-\textbf{Figure S3.} Pollen ratios for the different recipient species.
-
-\textbf{Figure S4.} Pollen ratios for the different recipient species by
+\textbf{Figure S3}. Pollen ratios for the different recipient species by
 family.
 
-\textbf{Figure S5.} Unipartite bidirectional network with asymmetrical
-effect
+\textbf{Figure S4}. Statistical comparison of the pollen ratios by
+family.
 
-\textbf{Figure S6.} Statistical comparison of pollen ratios by family as
-pollen donor and recipient.
+\textbf{Figure S5}. Unipartite bidirectional network with asymmetrical
+effect.
 
-\textbf{Figure S7.} Violin plot of the reproductive biology of the
-species.
+\textbf{Figure S6}. Correlation matrix for all the different traits.
 
-\textbf{Figure S8.} Grouped effect sizes by family for each recipient
+\textbf{Figure S7}. Species reproductive biology.
+
+\textbf{Figure S8}. Grouped effect sizes by family for each recipient
 species.
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
-\caption{Fig S2}
+\caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
+20 different treatments (3 replicates per tratment). For each treatment,
+we show the average number of conspecific pollen grains (grey) and
+heterospecific pollen grains (light blue) per stigma. For each pair of
+species on the x-axis, the first species is the recipient species, and
+the second, the donor species.}
 \end{figure}
 
-\newpage
+\clearpage
 
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
-\caption{Fig S3}
+\caption{\textbf{Fig. S2} Average proportion of conspecific and
+heterospecific pollen per stigma grouped by family, A) Brassicaceae, B)
+Solanaceae and C) Convolvulaceae. These proportions (\%) are the number
+of conspecific pollen grains or heterospecific pollen grains divided by
+the total number of pollen grains per stigma for 20 different
+treatments. We conducted 3 count replicates per treatment and then we
+calculated the average number of pollen grains for these treatments. The
+proportion of conspecific and heterospecific pollen are shown in grey
+and light blue respectively. For each pair of species on the y-axis, the
+first species is the pollen recipient and the second the pollen donor.
+The vertical black line represents 50\% pollen of both donor and
+recipient.}
 \end{figure}
 
-\newpage
+\clearpage
 
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
-\caption{Fig S4}
+\caption{\textbf{Fig. S3} Average proportion (\%) of heterospecific and
+conspecific pollen per family for the different 20 treatments counted.
+We conducted 3 count replicates per treatment and then we calculated the
+average number of pollen grains for these different 20 treatments.
+Finally, we grouped by family these treatments in order to see general
+tendencies across families as pollen donor and as pollen recipient.
+Pollen ratios were considered as the number of conspecific or
+heterospecific pollen grains divided by the total number of pollen
+grains per stigma. On the y-axis, the first family on each pair of plant
+families is the recipient one, and the second, the family of the donor.
+The vertical bar on intercept 50, represents equal proportions of both
+recipient (grey) and donor (light blue) pollen.}
 \end{figure}
@@
 numbers indicate no significant differences between groups (Tukey
-adjusted comparisons). These pollen ratios are the total number of
+adjusted comparisons). These pollen ratios (\%) are the total number of
 heterospecific pollen grains divided by the total quantity of pollen
 (conspecific pollen + heterospecific pollen), and then compared by
-family (N=20).}
+family (N=20). Brassicacea family is coloured in blue, Convolvulaceae in
+green and Solanaceae in orange.}
 \end{figure}
@@
 the reciprocal interaction. Lines of species that did not have a
-negative impact are not represented. The different nodes and the donor
-species appear coloured by family: Solanaceae (orange), Brassicaceae
-(blue) and Convolvulaceae (green). The intensity of the effect is
-represented by the line´s size where a larger effect size corresponds to
-a thicker line and a thinner line to a smaller effect size. Species
-code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa,
-SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea,
-CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum
-lycopersicum, SOME: Solanum melongena.}
+negative impact are not represented. The different nodes and the effect
+of the donor species on the recipient species appear coloured by family:
+Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green). The
+intensity of the effect is represented by the line´s size where a larger
+effect size corresponds to a thicker line and a thinner line to a
+smaller effect size. Species code: BROL: Brassica oleracea, BRRA:
+Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea
+aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia
+integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena.}
 \end{figure}
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{\textbf{Fig S6} Graphical representation of the correlation
+\caption{\textbf{Fig. S6} Graphical representation of the correlation
 matrix of the different reproductive traits considered in the
@@
 coverted to ovule (\%) for all species with four different
-hand-pollination treatments (apomixis, hand cross pollination, hand self
-pollination and spontaneous selfing). The coloured dots, represent the
-different values of seed set for each treatment.}
+hand-pollination treatments: apomixis (orange), hand cross pollination
+(green), hand self pollination (blue) and spontaneous selfing (yellow).
+The coloured dots, represent the different values of seed set for each
+treatment.}
 \end{figure}
@@
 \includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\textbf{Fig. S8} Effect sizes (95\% confidence intervals) of
-the different families on each focal species (recipient) and a hand
-cross-pollination treatment (control). For each species the control
-treatment appears in yellow and the grouped effect per family in blue
-for Brassicaceae, green for Convolvulaceae and orange for Solanaceae.}
+\caption{\textbf{Fig. S8} Grouped effect sizes (95\% confidence
+intervals) of the different families on each focal species. For each
+species, the grouped effect by family is compared with the control
+treatment of hand cross pollination with conspecific pollen. The control
+treatment is represented in yellow and vertically intersected with a
+dashed line through the mean effect size in order to help the visual
+interpretation of the effect sizes. Any value to the left of the
+vertical dashed line represents a negative impact of foreign pollen. The
+different effect sizes and confidence intervals are coloured by family:
+Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).}
 \end{figure}

### 2020-06-30 Thesis_Chapter_1/Supp_Material.Rmd
Supp. mat

@@
 
-__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman, Romina Rader
+__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
 
@@
 
-__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
+__Table S4.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
 
-__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
+__Table S5.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
 
-__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
+__Table S6.__ Phylogenetic signal and significance for all the different traits
 
-__Table S7.__ Phylogenetic signal and significance for all the different traits
-
-__Table S8.__ Procrustes analysis results.
+__Table S7.__ Procrustes analysis results.
 
@@
 
-#TABLE S1
 ```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
@@
 t <- data.frame(Species, Common_names, Variety, Source)
-kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
+kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
+             caption = "\\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.") %>%
   kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T) %>% row_spec(0,bold=TRUE)  
@@
 
-TABLE S2
 ```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
@@
 
-kable(dat, "latex", longtable = F, escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Measurements ($\\bar{X}$ ± SD) for all the 13 different traits for all plant species.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
 ```
@@
 
-TABLE S3
 ```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
@@
 dat <- readRDS("Tables/rep_biology_supplementary.rds")
-kable(dat, "latex", longtable = F, escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
+kable(dat, format="markdown", caption= "\\textbf{Table S3.} Seed:ovule ratio in percentage for hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.",digits = 2, longtable = F, escape = FALSE,dbooktabs = T,linesep = "\\addlinespace") %>%   row_spec(0,bold=TRUE)  %>% column_spec(1, width = "6cm")
+```
+
+\newpage
+
+\begin{landscape}
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+setwd("~/R_projects/Hp_pollen_experiment")
+d <- read.csv("Data/Csv/Significant_Effect_50_50.csv")
+#Unfortunately this table is not built through clean reproducible code
+#Our collaborators do not work with markdown and some plots were made directly in word
+#I have converted that table to csv and exported in R
+#To reproduce it, the file hp_seed_set_reduction in the folder analysis has everything
+#that is needed to make this table
+
+d <- as.data.frame(d)
+
+kable(d, "latex", longtable = F, caption= "\\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear mixed effect models.
+The category of “yes” represents significant effect of the donors (columns) on the different recipient species (rows) and “no” lack of significant reduction of seed set from the control.
+Significance was tested for all species by comparing with a control of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
+```
+
+\end{landscape}
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+setwd("~/R_projects/Hp_pollen_experiment")
+d <- readRDS("Data/RData/lm_table.RData")
+kable(d, format="markdown",caption= "\\textbf{Table S5.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
+
+```
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+setwd("~/R_projects/Hp_pollen_experiment")
+
+#Preparing seed set with 100% pollen
+pein_seed_set_100 <- read.csv("Raw_data/pein_seed_set_100.csv")
+soly_seed_set_100 <- read.csv("Raw_data/soly_seed_set_100.csv")
+some_seed_set_100 <- read.csv("Raw_data/some_seed_set_100.csv")
+caan_seed_set_100 <- read.csv("Raw_data/caan_seed_set_100.csv")
+brol_seed_set_100 <- read.csv("Raw_data/brol_seed_set_100.csv")
+brra_seed_set_100 <- read.csv("Raw_data/brra_seed_set_100.csv")
+sial_seed_set_100 <- read.csv("Raw_data/sial_seed_set_100.csv")
+ersa_seed_set_100 <- read.csv("Raw_data/ersa_seed_set_100.csv")
+ippu_seed_set_100 <- read.csv("Raw_data/ippu_seed_set_100.csv")
+ipaq_seed_set_100 <- read.csv("Raw_data/ipaq_seed_set_100.csv")
+
+all_100 <- rbind(pein_seed_set_100,soly_seed_set_100,some_seed_set_100,caan_seed_set_100,
+      brol_seed_set_100,brra_seed_set_100,sial_seed_set_100,ersa_seed_set_100,
+      ippu_seed_set_100,ipaq_seed_set_100)
+
+all_100_subset <- all_100[grepl("100", all_100$Treatment), , drop = FALSE]
+
+seed_100 <- subset(all_100_subset, all_100_subset$Seed.production>0)
+#str(seed_100)
+seed_100$Species <- as.character(seed_100$Species)
+seed_100$Species[seed_100$Species=="SOLY"] <- "Solnamum lycopersicum"
+seed_100$Species[seed_100$Species=="SOME"] <- "Solnamum melongena"
+seed_100$Species[seed_100$Species=="CAAN"] <- "Capsicum annuum"
+seed_100$Species[seed_100$Species=="BRRA"] <- "Brassica rapa"
+seed_100$Species[seed_100$Species=="SIAL"] <- "Sinapis alba"
+seed_100$Species[seed_100$Species=="ERSA"] <- "Eruca sativa"
+
+seed_100$Treatment <- as.character(seed_100$Treatment)
+
+seed_100$Treatment[seed_100$Treatment=="SIAL 100%"] <- "Sinapis alba"
+seed_100$Treatment[seed_100$Treatment=="ERSA 100%"] <- "Eruca sativa"
+seed_100$Treatment[seed_100$Treatment=="PEIN 100%"] <- "Petunia integrifolia"
+seed_100$Treatment[seed_100$Treatment=="BROL 100%"] <- "Brassica oleracea"
+seed_100$Treatment[seed_100$Treatment=="CAAN 100%"] <- "Capsicum annuum"
+seed_100$Treatment[seed_100$Treatment=="SOLY 100%"] <- "Solanum lycopersicum"
+
+seed_100 <- seed_100[,-c(1,4,6)]
+colnames(seed_100) <- c("Recipient", "Donor (100% foreign pollen)", "Seed number")
+rownames(seed_100) <- NULL
+
+kable(seed_100, format="markdown", caption= "\\textbf{Table S6.} Number of seeds produced with 100% foreign pollen (N=900).
+From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
+In this table we show just the treatments that lead to seed production.
+", digits = 2)
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+
+library(kableExtra)
+setwd("~/R_projects/Hp_pollen_experiment")
+load("Data/RData/img_phylo.RData")
+lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
+lambda<- as.numeric(lambda)
+p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
+p <- as.numeric(p)
+trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "Stigma length", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
+table<- data.frame(lambda,p, trait)
+colnames(table) <- c("Lambda", "_P_-value", "Traits")
+kable(table, format="markdown",caption= "\\textbf{Table S7.} Phylogenetic signal and significance for all the different traits.", digits = 2)
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+setwd("~/R_projects/Hp_pollen_experiment")
+
+load("Data/RData/Table_s4.RData")
+
+Correlation <- c(selfing_pro[6], pollen_size_pro[6], mean_pollen_anther_pro[6], mean_ovules_pro[6], pollen_ovule_ratio_pro[6], stigma_area_pro[6], stigma_length_pro[6], stigma_width_pro[6], style_length_pro[6], style_width_pro[6], ovary_width_pro[6], ovary_length_pro[6], si_index_pro[6],selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6],selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
+
+Correlation<- as.numeric(Correlation)
+
+Sum_squares <- c(selfing_pro[3], pollen_size_pro[3], mean_pollen_anther_pro[3], mean_ovules_pro[3], pollen_ovule_ratio_pro[3], stigma_area_pro[3], stigma_length_pro[3], stigma_width_pro[3], style_length_pro[3], style_width_pro[3], ovary_width_pro[3], ovary_length_pro[3],si_index_pro[3], selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3], selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
+
+Sum_squares<- as.numeric(Sum_squares)
+
+Significance <- c(selfing_pro[13], pollen_size_pro[13], mean_pollen_anther_pro[13], mean_ovules_pro[13], pollen_ovule_ratio_pro[13], stigma_area_pro[13], stigma_length_pro[13], stigma_width_pro[13], style_length_pro[13], style_width_pro[13], ovary_width_pro[13], ovary_length_pro[13],si_index_pro[13],selfing_pro_sol[13], pollen_size_pro_sol[13], mean_pollen_anther_pro_sol[13], mean_ovules_pro_sol[13], pollen_ovule_ratio_pro_sol[13], stigma_area_pro_sol[13], stigma_length_pro_sol[13], stigma_width_pro_sol[13], style_length_pro_sol[13], style_width_pro_sol[13], ovary_width_pro_sol[13], ovary_length_pro_sol[13],si_index_pro_sol[13], selfing_pro_bra[13], pollen_size_pro_bra[13], mean_pollen_anther_pro_bra[13], mean_ovules_pro_bra[13], pollen_ovule_ratio_pro_bra[13], stigma_area_pro_bra[13], stigma_length_pro_bra[13], stigma_width_pro_bra[13], style_length_pro_bra[13], style_width_pro_bra[13], ovary_width_pro_bra[13], ovary_length_pro_bra[13],si_index_pro_bra[13])
+
+Significance <- as.numeric(Significance)
+
+Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")
+
+Family <- c(rep("All",13),rep("Solanaceae",13),rep("Brassicaceae",13))
+
+table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
+colnames(table) <- c("Correlation (r)","Sum of squares", "_P_-value", "Traits", "Family")
+kable(table, caption= "\\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae and just Brassicaceae.",format="markdown", digits = 2)
 ```

### 2020-06-30 Thesis_Chapter_1/Supp_Material.tex
Supp. mat

@@
 \usepackage[margin=1in]{geometry}
+\usepackage{longtable,booktabs}
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx,grffile}
@@
 
-\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
+\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
 Romina Rader
@@
 
-\textbf{Table S4.} Species x species matrix with the significance of
-effect ``yes'' or ``no'' of the different donors on the seed set of the
-different recipient species.
-
-\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
+\textbf{Table S4.} Estimates, standard error, t-value and P-value of the
 effect of the different 9 donors on each recipient species.
 
-\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
+\textbf{Table S5.} Number of seeds produced with 100\% foreign pollen
 treatments for the different recipient species.
 
-\textbf{Table S7.} Phylogenetic signal and significance for all the
+\textbf{Table S6.} Phylogenetic signal and significance for all the
 different traits
 
-\textbf{Table S8.} Procrustes analysis results.
+\textbf{Table S7.} Procrustes analysis results.
 
@@
 
-\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont
+\begingroup\fontsize{7}{9}\selectfont
 
 \begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
 \toprule
@@
 \endfirsthead
-\multicolumn{4}{@{}l}{\textit{(continued)}}\\
+\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
 \toprule
@@
 
-TABLE S2
-\begingroup\fontsize{6}{8}\selectfont
+\begin{table}
 
+\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Measurements ($\bar{X}$ ± SD) for all the 13 different traits for all plant species.}
+\centering
 \resizebox{\linewidth}{!}{
+\fontsize{6}{8}\selectfont
 \begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
@@
 \end{tabu}}
-\endgroup{}
+\end{table}
 
@@
 
-TABLE S3 \begingroup\fontsize{6}{8}\selectfont
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{\textbf{Table S3.} Seed:ovule ratio in percentage for hand
+cross-pollination, hand self-pollination, spontaneous selfing and
+apomixis for all species.}\tabularnewline
+\toprule
+\begin{minipage}[b]{0.19\columnwidth}\raggedright
+Species\strut
+\end{minipage} & \begin{minipage}[b]{0.21\columnwidth}\raggedleft
+Hand cross-pollination\strut
+\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedleft
+Hand self-pollination\strut
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft
+Spontaneous selfing\strut
+\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedleft
+Apomixis\strut
+\end{minipage}\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{0.19\columnwidth}\raggedright
+Species\strut
+\end{minipage} & \begin{minipage}[b]{0.21\columnwidth}\raggedleft
+Hand cross-pollination\strut
+\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedleft
+Hand self-pollination\strut
+\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft
+Spontaneous selfing\strut
+\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedleft
+Apomixis\strut
+\end{minipage}\tabularnewline
+\midrule
+\endhead
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Brassica oleracea\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+32.07\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+0.00\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+0.00\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Brassica rapa\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+44.97\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+0.00\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+0.00\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Capsicum annuum\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+80.00\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+56.47\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+19.34\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Eruca sativa\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+23.75\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+0.42\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+0.00\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Ipomoea aquatica\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+40.00\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+30.00\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+20.00\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Ipomoea purpurea\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+31.67\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+86.67\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+31.67\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Petunia integrifolia\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+80.16\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+24.77\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+0.00\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Sinapis alba\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+41.67\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+48.33\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+5.00\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+15\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Solanum lycopersium\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+85.65\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+41.20\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+68.48\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.19\columnwidth}\raggedright
+Solanum melongena\strut
+\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
+60.48\strut
+\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
+74.87\strut
+\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
+21.56\strut
+\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
+0\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
 
+\newpage
+
+\begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear mixed effect models.
+The category of “yes” represents significant effect of the donors (columns) on the different recipient species (rows) and “no” lack of significant reduction of seed set from the control.
+Significance was tested for all species by comparing with a control of hand cross-pollination with conspecific pollen.}
+\centering
 \resizebox{\linewidth}{!}{
-\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
 \toprule
-\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
+\textbf{X} & \textbf{B..oleracea} & \textbf{B..rapa} & \textbf{E..sativa} & \textbf{S..alba} & \textbf{I..aquatica} & \textbf{I..purpurea} & \textbf{C..annuum} & \textbf{P..integrifolia} & \textbf{S..lycopersicum} & \textbf{S..melongena} & \textbf{S.Significant.effect.of.donors} & \textbf{X..donors.with.significant.effect}\\
 \midrule
-\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
+\rowcolor{gray!6}  B. oleracea &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 9 & 100.0\\
 \addlinespace
-Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
+B. rapa & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 8 & 88.9\\
 \addlinespace
-\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
+\rowcolor{gray!6}  E. sativa & Yes & No &  & No & Yes & No & No & No & No & No & 1 & 22.2\\
 \addlinespace
-Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
+S. alba & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 4 & 44.4\\
 \addlinespace
-\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
+\rowcolor{gray!6}  I. aquatica & Yes & Yes & Yes & Yes &  & Yes & Yes & Yes & Yes & Yes & 9 & 100.0\\
 \addlinespace
-Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
+I. purpurea & No & No & Yes & No & No &  & Yes & No & Yes & No & 3 & 33.3\\
 \addlinespace
-\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
+\rowcolor{gray!6}  C. annuum & Yes & Yes & No & Yes & No & Yes &  & Yes & Yes1 & Yes & 7 & 77.8\\
 \addlinespace
-Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
+P. integrifolia & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 6 & 67.7\\
 \addlinespace
-\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
+\rowcolor{gray!6}  S. lycopersicum & No & Yes & Yes & Yes & Yes & Yes & Yes & Yes &  & Yes & 8 & 88.9\\
 \addlinespace
-Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
+S. melongena & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 5 & 55.6\\
+\addlinespace
+\rowcolor{gray!6}   &  &  &  &  &  &  &  &  &  &  & 60 & 66.7\\
 \bottomrule
 \end{tabu}}
-\endgroup{}
+\end{table}
+
+\end{landscape}
+
+\begin{longtable}[]{@{}lrrrr@{}}
+\caption{\textbf{Table S5.} Output of linear models of the effect of the
+different donors on the seed set of each recipient
+species.}\tabularnewline
+\toprule
+& Est. & S.E. & t val. & p\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+& Est. & S.E. & t val. & p\tabularnewline
+\midrule
+\endhead
+Petunia integrifolia - (Intercept) & 4.63 & 0.49 & 9.36 &
+0.00\tabularnewline
+Petunia integrifolia - Brassica oleracea & -1.84 & 0.81 & -2.27 &
+0.03\tabularnewline
+Petunia integrifolia - Brassica rapa & -0.97 & 0.81 & -1.19 &
+0.24\tabularnewline
+Petunia integrifolia - Capsicum annuum & 0.78 & 0.81 & 0.96 &
+0.34\tabularnewline
+Petunia integrifolia - Eruca vesicaria & -0.91 & 0.81 & -1.12 &
+0.26\tabularnewline
+Petunia integrifolia - Ipomoea aquatica & -3.18 & 0.81 & -3.92 &
+0.00\tabularnewline
+Petunia integrifolia - Ipomoea purpurea & -4.21 & 0.81 & -5.19 &
+0.00\tabularnewline
+Petunia integrifolia - Sinapis alba & -2.99 & 0.81 & -3.69 &
+0.00\tabularnewline
+Petunia integrifolia - Solanum lycopersicum & -2.40 & 0.81 & -2.96 &
+0.00\tabularnewline
+Petunia integrifolia - Solanum melongena & -2.66 & 0.81 & -3.27 &
+0.00\tabularnewline
+Solanum lycopersicum - (Intercept) & 4.39 & 0.24 & 18.54 &
+0.00\tabularnewline
+Solanum lycopersicum - Brassica oleracea & -0.47 & 0.41 & -1.14 &
+0.26\tabularnewline
+Solanum lycopersicum - Brassica rapa & -2.74 & 0.41 & -6.67 &
+0.00\tabularnewline
+Solanum lycopersicum - Capsicum annuum & -4.39 & 0.41 & -10.71 &
+0.00\tabularnewline
+Solanum lycopersicum - Eruca vesicaria & -2.97 & 0.41 & -7.25 &
+0.00\tabularnewline
+Solanum lycopersicum - Ipomoea aquatica & -4.13 & 0.41 & -10.06 &
+0.00\tabularnewline
+Solanum lycopersicum - Ipomoea purpurea & -3.80 & 0.41 & -9.27 &
+0.00\tabularnewline
+Solanum lycopersicum - Petunia integrifolia & -1.82 & 0.41 & -4.44 &
+0.00\tabularnewline
+Solanum lycopersicum - Sinapis alba & -3.72 & 0.41 & -9.08 &
+0.00\tabularnewline
+Solanum lycopersicum - Solanum melongena & -1.84 & 0.41 & -4.49 &
+0.00\tabularnewline
+Solanum melongena - (Intercept) & 6.34 & 0.70 & 9.09 &
+0.00\tabularnewline
+Solanum melongena - Brassica oleracea & -0.67 & 0.99 & -0.68 &
+0.50\tabularnewline
+Solanum melongena - Brassica rapa & -4.33 & 0.99 & -4.39 &
+0.00\tabularnewline
+Solanum melongena - Capsicum annuum & -2.33 & 0.99 & -2.36 &
+0.02\tabularnewline
+Solanum melongena - Eruca vesicaria & -3.12 & 0.99 & -3.16 &
+0.00\tabularnewline
+Solanum melongena - Ipomoea aquatica & -6.34 & 0.99 & -6.43 &
+0.00\tabularnewline
+Solanum melongena - Ipomoea purpurea & -2.71 & 0.99 & -2.74 &
+0.01\tabularnewline
+Solanum melongena - Petunia integrifolia & -1.43 & 0.99 & -1.45 &
+0.15\tabularnewline
+Solanum melongena - Sinapis alba & -1.11 & 0.99 & -1.12 &
+0.26\tabularnewline
+Solanum melongena - Solanum lycopersicum & -0.84 & 0.99 & -0.86 &
+0.39\tabularnewline
+Capsicum annuum - (Intercept) & 4.59 & 0.52 & 8.78 & 0.00\tabularnewline
+Capsicum annuum - Brassica oleracea & -1.80 & 0.74 & -2.43 &
+0.02\tabularnewline
+Capsicum annuum - Brassica rapa & -2.51 & 0.74 & -3.39 &
+0.00\tabularnewline
+Capsicum annuum - Eruca vesicaria & -0.63 & 0.74 & -0.85 &
+0.40\tabularnewline
+Capsicum annuum - Ipomoea aquatica & -1.36 & 0.74 & -1.84 &
+0.07\tabularnewline
+Capsicum annuum - Ipomoea purpurea & -4.00 & 0.74 & -5.41 &
+0.00\tabularnewline
+Capsicum annuum - Petunia integrifolia & -4.59 & 0.74 & -6.21 &
+0.00\tabularnewline
+Capsicum annuum - Sinapis alba & -3.63 & 0.74 & -4.92 &
+0.00\tabularnewline
+Capsicum annuum - Solanum lycopersicum & -1.52 & 0.74 & -2.06 &
+0.04\tabularnewline
+Capsicum annuum - Solanum melongena & -3.29 & 0.74 & -4.46 &
+0.00\tabularnewline
+Brassica oleracea - (Intercept) & 1.99 & 0.22 & 8.98 &
+0.00\tabularnewline
+Brassica oleracea - Brassica rapa & -1.37 & 0.31 & -4.35 &
+0.00\tabularnewline
+Brassica oleracea - Capsicum annuum & -0.87 & 0.31 & -2.76 &
+0.01\tabularnewline
+Brassica oleracea - Eruca vesicaria & -1.92 & 0.31 & -6.13 &
+0.00\tabularnewline
+Brassica oleracea - Ipomoea aquatica & -1.91 & 0.27 & -7.04 &
+0.00\tabularnewline
+Brassica oleracea - Ipomoea purpurea & -1.99 & 0.31 & -6.35 &
+0.00\tabularnewline
+Brassica oleracea - Petunia integrifolia & -1.64 & 0.31 & -5.21 &
+0.00\tabularnewline
+Brassica oleracea - Sinapis alba & -1.57 & 0.31 & -4.99 &
+0.00\tabularnewline
+Brassica oleracea - Solanum lycopersicum & -1.47 & 0.31 & -4.70 &
+0.00\tabularnewline
+Brassica oleracea - Solanum melongena & -1.61 & 0.31 & -5.12 &
+0.00\tabularnewline
+Brassica rapa - (Intercept) & 2.37 & 0.19 & 12.49 & 0.00\tabularnewline
+Brassica rapa - Brassica oleracea & -0.54 & 0.29 & -1.89 &
+0.06\tabularnewline
+Brassica rapa - Capsicum annuum & -1.42 & 0.29 & -4.94 &
+0.00\tabularnewline
+Brassica rapa - Eruca vesicaria & -2.37 & 0.29 & -8.24 &
+0.00\tabularnewline
+Brassica rapa - Ipomoea aquatica & -1.92 & 0.29 & -6.67 &
+0.00\tabularnewline
+Brassica rapa - Ipomoea purpurea & -2.26 & 0.29 & -7.86 &
+0.00\tabularnewline
+Brassica rapa - Petunia integrifolia & -2.37 & 0.29 & -8.24 &
+0.00\tabularnewline
+Brassica rapa - Sinapis alba & -2.37 & 0.29 & -8.24 &
+0.00\tabularnewline
+Brassica rapa - Solanum lycopersicum & -1.88 & 0.29 & -6.55 &
+0.00\tabularnewline
+Brassica rapa - Solanum melongena & -2.37 & 0.29 & -8.24 &
+0.00\tabularnewline
+Eruca sativa - (Intercept) & 1.34 & 0.35 & 3.80 & 0.00\tabularnewline
+Eruca sativa - Brassica oleracea & -1.34 & 0.50 & -2.69 &
+0.01\tabularnewline
+Eruca sativa - Brassica rapa & 0.66 & 0.50 & 1.32 & 0.19\tabularnewline
+Eruca sativa - Capsicum annuum & -0.27 & 0.50 & -0.55 &
+0.58\tabularnewline
+Eruca sativa - Ipomoea aquatica & 0.87 & 0.50 & 1.75 &
+0.08\tabularnewline
+Eruca sativa - Ipomoea purpurea & -0.19 & 0.50 & -0.39 &
+0.70\tabularnewline
+Eruca sativa - Petunia integrifolia & 0.20 & 0.50 & 0.41 &
+0.68\tabularnewline
+Eruca sativa - Sinapis alba & 0.32 & 0.50 & 0.65 & 0.52\tabularnewline
+Eruca sativa - Solanum lycopersicum & -0.52 & 0.50 & -1.04 &
+0.30\tabularnewline
+Eruca sativa - Solanum melongena & 0.54 & 0.50 & 1.09 &
+0.28\tabularnewline
+Ipomoea purpurea - (Intercept) & 0.82 & 0.20 & 4.05 &
+0.00\tabularnewline
+Ipomoea purpurea - Brassica oleracea & 0.37 & 0.29 & 1.31 &
+0.19\tabularnewline
+Ipomoea purpurea - Brassica rapa & -0.41 & 0.29 & -1.43 &
+0.16\tabularnewline
+Ipomoea purpurea - Capsicum annuum & -0.82 & 0.29 & -2.86 &
+0.01\tabularnewline
+Ipomoea purpurea - Eruca vesicaria & -0.75 & 0.29 & -2.62 &
+0.01\tabularnewline
+Ipomoea purpurea - Ipomoea aquatica & 0.41 & 0.29 & 1.44 &
+0.15\tabularnewline
+Ipomoea purpurea - Petunia integrifolia & -0.37 & 0.29 & -1.31 &
+0.19\tabularnewline
+Ipomoea purpurea - Sinapis alba & -0.33 & 0.29 & -1.14 &
+0.26\tabularnewline
+Ipomoea purpurea - Solanum lycopersicum & -0.82 & 0.29 & -2.86 &
+0.01\tabularnewline
+Ipomoea purpurea - Solanum melongena & -0.24 & 0.29 & -0.82 &
+0.41\tabularnewline
+Ipomoea aquatica - (Intercept) & 0.80 & 0.09 & 9.36 &
+0.00\tabularnewline
+Ipomoea aquatica - Brassica oleracea & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+Ipomoea aquatica - Brassica rapa & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+Ipomoea aquatica - Capsicum annuum & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+Ipomoea aquatica - Eruca vesicaria & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+Ipomoea aquatica - Ipomoea purpurea & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+Ipomoea aquatica - Petunia integrifolia & -0.59 & 0.12 & -4.89 &
+0.00\tabularnewline
+Ipomoea aquatica - Sinapis alba & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+Ipomoea aquatica - Solanum lycopersicum & -0.69 & 0.12 & -5.70 &
+0.00\tabularnewline
+Ipomoea aquatica - Solanum melongena & -0.80 & 0.12 & -6.62 &
+0.00\tabularnewline
+\bottomrule
+\end{longtable}
+
+\newpage
+
+\begin{longtable}[]{@{}llr@{}}
+\caption{\textbf{Table S6.} Number of seeds produced with 100\% foreign
+pollen (N=900). From 900 pollination events we found seed production in
+just 13 specific cases and 0 seed production in the other 887
+pollination events. In this table we show just the treatments that lead
+to seed production.}\tabularnewline
+\toprule
+Recipient & Donor (100\% foreign pollen) & Seed number\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Recipient & Donor (100\% foreign pollen) & Seed number\tabularnewline
+\midrule
+\endhead
+Solnamum lycopersicum & Sinapis alba & 3\tabularnewline
+Solnamum melongena & Petunia integrifolia & 36\tabularnewline
+Capsicum annuum & Eruca sativa & 3\tabularnewline
+Capsicum annuum & Sinapis alba & 127\tabularnewline
+Brassica rapa & Brassica oleracea & 2\tabularnewline
+Brassica rapa & Brassica oleracea & 13\tabularnewline
+Sinapis alba & Brassica oleracea & 7\tabularnewline
+Sinapis alba & Brassica oleracea & 5\tabularnewline
+Sinapis alba & Brassica oleracea & 7\tabularnewline
+Sinapis alba & Capsicum annuum & 1\tabularnewline
+Sinapis alba & Capsicum annuum & 6\tabularnewline
+Sinapis alba & Solanum lycopersicum & 1\tabularnewline
+Eruca sativa & Petunia integrifolia & 2\tabularnewline
+\bottomrule
+\end{longtable}
+
+\newpage
+
+\begin{longtable}[]{@{}rrl@{}}
+\caption{\textbf{Table S7.} Phylogenetic signal and significance for all
+the different traits.}\tabularnewline
+\toprule
+Lambda & \emph{P}-value & Traits\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Lambda & \emph{P}-value & Traits\tabularnewline
+\midrule
+\endhead
+0.95 & 0.20 & Selfing rate\tabularnewline
+1.00 & 0.00 & \textbf{Pollen size}\tabularnewline
+0.00 & 1.00 & Pollen anther\tabularnewline
+0.00 & 1.00 & Ovule number\tabularnewline
+0.00 & 1.00 & Pollen-ovule ratio\tabularnewline
+0.89 & 0.01 & \textbf{Stigmatic area}\tabularnewline
+0.70 & 0.05 & Stigma length\tabularnewline
+0.77 & 0.03 & \textbf{Stigma width}\tabularnewline
+0.93 & 0.01 & \textbf{Style length}\tabularnewline
+0.00 & 1.00 & Style width\tabularnewline
+0.47 & 0.30 & Ovary length\tabularnewline
+0.00 & 1.00 & Ovary width\tabularnewline
+0.00 & 0.02 & \textbf{SI index}\tabularnewline
+\bottomrule
+\end{longtable}
+
+\newpage
+
+\begin{longtable}[]{@{}rrrll@{}}
+\caption{\textbf{Table S8.} Procrustes correlation, sum of squares and
+significance from Procrustes analysis between the matrix of effect sizes
+(species x species matrix) and the distance matrix of each trait for all
+families, just Solanaceae and just Brassicaceae.}\tabularnewline
+\toprule
+Correlation (r) & Sum of squares & \emph{P}-value & Traits &
+Family\tabularnewline
+\midrule
+\endfirsthead
+\toprule
+Correlation (r) & Sum of squares & \emph{P}-value & Traits &
+Family\tabularnewline
+\midrule
+\endhead
+0.34 & 0.88 & 0.70 & Selfing rate & All\tabularnewline
+0.36 & 0.87 & 0.42 & Pollen size & All\tabularnewline
+0.35 & 0.88 & 0.57 & Pollen per anther & All\tabularnewline
+0.33 & 0.89 & 0.55 & Number of ovules & All\tabularnewline
+0.30 & 0.91 & 0.86 & Pollen-ovule ratio & All\tabularnewline
+0.37 & 0.86 & 0.68 & Stigmatic area & All\tabularnewline
+0.62 & 0.62 & 0.10 & Stigma length & All\tabularnewline
+0.46 & 0.79 & 0.47 & Stigma width & All\tabularnewline
+0.43 & 0.82 & 0.45 & Style length & All\tabularnewline
+0.59 & 0.65 & 0.11 & Style width & All\tabularnewline
+0.34 & 0.88 & 0.57 & Ovary length & All\tabularnewline
+0.35 & 0.88 & 0.93 & Ovary width & All\tabularnewline
+0.49 & 0.76 & 0.24 & Self-incompatibility index & All\tabularnewline
+0.86 & 0.26 & 0.25 & Selfing rate & Solanaceae\tabularnewline
+0.76 & 0.42 & 0.33 & Pollen size & Solanaceae\tabularnewline
+0.42 & 0.82 & 0.79 & Pollen per anther & Solanaceae\tabularnewline
+0.52 & 0.73 & 0.83 & Number of ovules & Solanaceae\tabularnewline
+0.87 & 0.25 & 0.04 & Pollen-ovule ratio & Solanaceae\tabularnewline
+0.82 & 0.33 & 0.17 & Stigmatic area & Solanaceae\tabularnewline
+0.89 & 0.20 & 0.08 & Stigma length & Solanaceae\tabularnewline
+0.84 & 0.29 & 0.12 & Stigma width & Solanaceae\tabularnewline
+0.78 & 0.39 & 0.50 & Style length & Solanaceae\tabularnewline
+0.52 & 0.73 & 0.71 & Style width & Solanaceae\tabularnewline
+0.64 & 0.60 & 0.79 & Ovary length & Solanaceae\tabularnewline
+0.87 & 0.23 & 0.17 & Ovary width & Solanaceae\tabularnewline
+0.50 & 0.75 & 1.00 & Self-incompatibility index &
+Solanaceae\tabularnewline
+0.61 & 0.63 & 0.50 & Selfing rate & Brassicaceae\tabularnewline
+0.60 & 0.64 & 0.71 & Pollen size & Brassicaceae\tabularnewline
+0.40 & 0.84 & 0.96 & Pollen per anther & Brassicaceae\tabularnewline
+0.62 & 0.61 & 0.42 & Number of ovules & Brassicaceae\tabularnewline
+0.49 & 0.76 & 0.96 & Pollen-ovule ratio & Brassicaceae\tabularnewline
+0.55 & 0.70 & 0.58 & Stigmatic area & Brassicaceae\tabularnewline
+0.92 & 0.15 & 0.08 & Stigma length & Brassicaceae\tabularnewline
+0.63 & 0.60 & 0.38 & Stigma width & Brassicaceae\tabularnewline
+0.83 & 0.31 & 0.08 & Style length & Brassicaceae\tabularnewline
+0.79 & 0.37 & 0.33 & Style width & Brassicaceae\tabularnewline
+0.59 & 0.65 & 0.50 & Ovary length & Brassicaceae\tabularnewline
+0.54 & 0.70 & 1.00 & Ovary width & Brassicaceae\tabularnewline
+0.50 & 0.75 & 0.83 & Self-incompatibility index &
+Brassicaceae\tabularnewline
+\bottomrule
+\end{longtable}
 
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-5-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
 \caption{\textbf{Fig. S2} Average proportion of conspecific and
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-6-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
 \caption{\textbf{Fig. S3} Average proportion (\%) of heterospecific and
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-7-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-12-1.pdf}
 \caption{\textbf{Fig. S4} Pollen ratios comparisons between the
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-8-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-13-1.pdf}
 \caption{\textbf{Fig. S5} Unipartite bidirectional network with
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-14-1.pdf}
 \caption{\textbf{Fig. S6} Graphical representation of the correlation
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-15-1.pdf}
 \caption{\textbf{Fig. S7} Violin plot of the proportion of seeds
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-16-1.pdf}
 \caption{\textbf{Fig. S8} Grouped effect sizes (95\% confidence

### 2020-06-30 Untitled.Rmd
Supp. mat

--- 2020-06-28 Thesis_Chapter_1/Supp_Material.Rmd
@@
 ---
-output:
-  pdf_document:
-    keep_tex: yes
-    fig_caption: yes
-    toc: no
-  html_document:
-    toc: no
-    df_print: paged
-fontsize: 12pt
-header-includes:
-- \usepackage{setspace}\doublespacing
-- \usepackage{float}
-- \usepackage{caption}
+title: "Untitled"
+output: html_document
+---
 
----
-\captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\renewcommand{\figurename}{}
-
-# Supporting information:
-
-# Recipient and donor characteristics govern hierarchical structure in a heterospecific pollen competition network of co-flowering plants
-
-__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman, Romina Rader
-
-The following Supporting Information is available for this article:
-
-__Table S1.__ Species names, common names, varieties and sources of the different seeds.
-
-__Table S2.__ Numerical values of all the traits measured for each species.
-
-__Table S3.__ Seed set in percentage for hand cross-pollination, hand self-pollination, natural selfing and apomixis for all species.
-
-__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
-
-__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
-
-__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
-
-__Table S7.__ Phylogenetic signal and significance for all the different traits
-
-__Table S8.__ Procrustes analysis results.
-
-__Figure S1.__ Correlation matrix for all the different traits.
-
-__Figure S2.__ Total amount of pollen found for the different treatments.
-
-__Figure S3.__ Pollen ratios for the different recipient species.
-
-__Figure S4.__ Pollen ratios for the different recipient species by family.
-
-__Figure S5.__ Unipartite bidirectional network with asymmetrical effect
-
-__Figure S6.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.
-
-__Figure S7.__ Violin plot of the reproductive biology of the species.
-
-__Figure S8.__ Grouped effect sizes by family for each recipient species.
-
-\newpage
-
-#TABLE S1
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(knitr)
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
 library(kableExtra)
-Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-Species <- as.character(Species)
-
-Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")
-Common_names <- as.character(Common_names)
-Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers") 
-Variety <- as.character(Variety)
-Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
-Source <- as.character(Source)
-t <- data.frame(Species, Common_names, Variety, Source)
-kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T) %>% row_spec(0,bold=TRUE)  
-```
-
-\begin{landscape}
-
-TABLE S2
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(kableExtra)
-
-dat <- readRDS("Tables/traits_supplementary.rds")
-#Convert to square mm and mm
-dat$stigma_area <- dat$stigma_area/1000000
-dat[,c(7:12)] <- dat[,c(7:12)]/1000
-
-colnames(dat) <- c("Species", "Pollen size $\\mu$m", "Pollen grains per anther", "Ovule number", "Pollen:ovule ratio", "Stigma area $\\mu$m$^{2}$", "Stigma length (mm)", "Stigma width (mm)", "Style length (mm)", "Style width (mm)", "Ovary length (mm)", "Ovary width (mm)", "Selfing rate", "SI index")
-
-kable(dat, "latex", longtable = F, escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
-```
-
-\end{landscape}
-
-TABLE S3
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(kableExtra)
-dat <- readRDS("Tables/rep_biology_supplementary.rds")
-kable(dat, "latex", longtable = F, escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="Fig S1"}
-library(ggplot2)
-setwd("~/R_projects/Hp_pollen_experiment")
-total_pollen <- read.csv("Data/Csv/total_pollen.csv")
-ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
-  geom_bar(stat='identity', position='dodge')+theme_minimal()+
-  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
-  scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7,  fig.cap="**Fig S3** Average proportion of heterospecific pollen per family for the different 20 treatments counted.
-On the label of the y-axis, the first family is the pollen recipient family, and the second, the pollen donor family.
-These pollen ratios are the number of heterospecific pollen grains divided by the total pollen grains per stigma (conspecific and heterospecific pollen) and then averaged by family (N=20).
-The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}
-par(mar=c(30,13,2,4),xpd=F)
-setwd("~/R_projects/Hp_pollen_experiment")
-data_percentage <-readRDS("Data/RData/per.RData")
-data_percentage=as.matrix(data_percentage)
-coul = c("#999999","#779799")
-barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=1,cex.names=1,names=c("Brassicaceae-Convolvulaceae",
- "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
-legend(-5,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
-abline(v=50,col="black")
-
-#lines(c(0,10),50,col="red")
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap=""}
-
-par(mar=c(2,13,2,4),xpd=F)
-par(mfrow=c(3,1))
-setwd("~/R_projects/Hp_pollen_experiment")
-ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
-barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E.
-sativa-I.
-purpurea", "B.
-oleracea-I.
-purpurea","B.
-rapa-I.
-purpurea", "S.
-alba-I.
-aquatica", "S.
-alba-S.
-melongena", "E.
-sativa-P.
-integrifolia", "B.
-rapa-S.
-lycopersicum", "B.
-oleracea-C.
-annuum"))
-abline(v=50,col="black")
-legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
-text(8.3,6.8,"A) Brassicaceae")
-ratio_con <-readRDS("Data/RData/ratio_con.RData")
-barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I.
-purpurea-S.
-melongena","I.
-aquatica-C.
-annuum","I.
-purpurea-E.
-sativa","I.
-aquatica-S.
-alba"))
-abline(v=50,col="black")
-legend(-1,-0.5,legend=c("Recipient","Donor"),bty="n",fill = coul)
-text(9,3.5,"B) Convolvulaceae")
-
-ratio_sol <-readRDS("Data/RData/ratio_sol.RData")
-barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
-annuum-I.
-purpurea", "S.
-melongena-I.
-aquatica", "P.
-integrifolia-I.
-aquatica", "S.
-lycopersicum-I aquatica","S.
-melongena-E.
-sativa", "P.
-integrifolia-E.
-sativa", "C.
-annuum-S.
-alba", "S.
-lycopersicum-B.
-rapa"))
-abline(v=50,col="black")
-legend(-1,-0.1,legend=c("Recipient","Donor"),bty="n",fill = coul)
-text(6.8,6.8,"C) Solanaceae")
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S4** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
-These pollen ratios are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20)."}
-
-#Here I try to compare the different proportions of pollen between the different groups
-#I use Tukey method
-
-library(lme4)
-library(emmeans)
-library(reshape2)
-library(multcompView)
-library(lsmeans)
-library(multcomp)
-library(ggplot2)
-library(DHARMa)
 setwd("~/R_projects/Hp_pollen_experiment")
 
-total_pollen <- read.csv("Data/Csv/total_pollen.csv")
+load("Data/RData/Table_s4.RData")
 
-total_pollen=total_pollen[,-1]
-colnames(total_pollen)[3] <- "pollen"
-#head(total_pollen)
+Correlation <- c(selfing_pro[6], pollen_size_pro[6], mean_pollen_anther_pro[6], mean_ovules_pro[6], pollen_ovule_ratio_pro[6], stigma_area_pro[6], stigma_length_pro[6], stigma_width_pro[6], style_length_pro[6], style_width_pro[6], ovary_width_pro[6], ovary_length_pro[6], si_index_pro[6],selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6],selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
 
-# Dividing by focal pollen and non focal pollen
-# In order to compare pollen as donor and recipient per family 
-pollen_foc <- subset(total_pollen, variable=="focal_pollen")
-pollen_non <- subset(total_pollen, variable=="non_focal_pollen")
+Correlation<- as.numeric(Correlation)
 
-total  <- as.numeric(pollen_foc$pollen) + as.numeric(pollen_non$pollen)
-pollen_non$total_pollen  <- total
-pollen_non$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
-pollen_non$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
-                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
-                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
-                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
+Sum_squares <- c(selfing_pro[3], pollen_size_pro[3], mean_pollen_anther_pro[3], mean_ovules_pro[3], pollen_ovule_ratio_pro[3], stigma_area_pro[3], stigma_length_pro[3], stigma_width_pro[3], style_length_pro[3], style_width_pro[3], ovary_width_pro[3], ovary_length_pro[3],si_index_pro[3], selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3], selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
 
-pollen_non <- pollen_non[,-c(1,2)]
-colnames(pollen_non)[1] <-"hp_pollen"
-pollen_non$hp_ratio <- as.numeric(pollen_non$hp_pollen)/as.numeric(pollen_non$total_pollen)
-#hist(pollen_non$hp_ratio)
+Sum_squares<- as.numeric(Sum_squares)
 
-pollen_foc$total_pollen  <- total
-pollen_foc$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
-pollen_foc$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
-                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
-                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
-                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
+Significance <- c(selfing_pro[13], pollen_size_pro[13], mean_pollen_anther_pro[13], mean_ovules_pro[13], pollen_ovule_ratio_pro[13], stigma_area_pro[13], stigma_length_pro[13], stigma_width_pro[13], style_length_pro[13], style_width_pro[13], ovary_width_pro[13], ovary_length_pro[13],si_index_pro[13],selfing_pro_sol[13], pollen_size_pro_sol[13], mean_pollen_anther_pro_sol[13], mean_ovules_pro_sol[13], pollen_ovule_ratio_pro_sol[13], stigma_area_pro_sol[13], stigma_length_pro_sol[13], stigma_width_pro_sol[13], style_length_pro_sol[13], style_width_pro_sol[13], ovary_width_pro_sol[13], ovary_length_pro_sol[13],si_index_pro_sol[13], selfing_pro_bra[13], pollen_size_pro_bra[13], mean_pollen_anther_pro_bra[13], mean_ovules_pro_bra[13], pollen_ovule_ratio_pro_bra[13], stigma_area_pro_bra[13], stigma_length_pro_bra[13], stigma_width_pro_bra[13], style_length_pro_bra[13], style_width_pro_bra[13], ovary_width_pro_bra[13], ovary_length_pro_bra[13],si_index_pro_bra[13])
 
-pollen_foc <- pollen_foc[,-c(1,2)]
-colnames(pollen_foc)[1] <-"hp_pollen"
-pollen_foc$hp_ratio <- as.numeric(pollen_foc$hp_pollen)/as.numeric(pollen_foc$total_pollen)
-#hist(pollen_foc$hp_ratio)
+Significance <- as.numeric(Significance)
 
-#Analyse data and plot it
+Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")
 
-junk.glmer = lm(hp_ratio ~ fam_non, data = pollen_non)
-#plot(junk.glmer)
-#goodness of fit of the model
-#testDispersion(junk.glmer)
-#simulationOutput <- simulateResiduals(fittedModel = junk.glmer, plot = T)
+Family <- c(rep("All",13),rep("Solanaceae",13),rep("Brassicaceae",13))
 
-#lsm = lsmeans(junk.glmer, "fam_non", type = "response")
-#pairs(lsm)
-#CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
-
-#ggplot(CLD,aes(x= fam_non,y= lsmean,
-#label = .group)) +theme_minimal()+
-#geom_point(shape  = 15,size   = 4) +ggtitle("B) Comparison of ratios as donor")+
-#geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
-#width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+
-#geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black")
-
-#Analyse data and plot it
-junk.glmer = lm(hp_ratio ~ fam_foc, data = pollen_foc)
-lsm = lsmeans(junk.glmer, "fam_foc", type = "response")
-#pairs(lsm)
-CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
-
-#theme
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  library(grid)
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.3)),
-            axis.text=element_text(size = rel(1), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.8, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_line(),
-            panel.grid.minor.y= element_blank()
-      ))
-}
-
-ggplot(CLD,aes(x= fam_foc,y= lsmean,
-               label = .group)) +theme_ms()+
-  geom_point(shape  = 15,size   = 4) +ggtitle("")+
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
-                width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+ geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(axis.text.x = element_text(size=14, face="bold"))
-
+table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
+colnames(table) <- c("Correlation (r)","Sum of squares", "_P_-value", "Traits", "Family")
+kable(table, format="markdown", digits = 2)
 ```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig.
-S5** Unipartite bidirectional network with asymmetrical effect.
-The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species.
-All the arrow heads point to the recipient species of the reciprocal interaction.
-Lines of species that did not have a negative impact are not represented.
-The different nodes and the donor species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).
-The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size.
-Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}
-library(statnet)
-library(reshape2)
-library(sna)
-library(igraph)
-setwd("~/R_projects/Hp_pollen_experiment")
-
-#######################################
-############ Data preparataion ########
-#######################################
-
-#In this script I'm going to plot the transitivity of the effect oh HP pollen with effect sizes
-effect <- readRDS("Data/RData/matrix_effect_size.RData")
-#Now I convert the few values over 0 to maximum 0 (control)
-effect[effect>0]<-0
-#absolute values so less confusing without negative values
-#So now greater values involve greater effect
-#(opposite way in comparison with negative values as before)
-effect=abs(effect)
-#UNIPARTITE DOUBLE ASSYMETRICAL EFFECT
-G <- graph.adjacency(t(effect),weighted=TRUE,diag=FALSE)
-#plot(G)
-E <- t(apply(get.edgelist(G),1,sort))
-E(G)$curved <- 0
-E(G)[duplicated(E) | duplicated(E,fromLast =TRUE)]$curved <- 0.2
-plot(G, edge.width=E(G)$weight/0.5,  vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),
-              "#D55E00","#0072B2", rep("#D55E00",2)),edge.arrow.size=0.8,edge.color=adjustcolor(c(rep("#0072B2",8),rep("#0072B2",8), rep("#D55E00",7), 
-              rep("#0072B2",9),rep("#009E73",7),rep("#009E73",9),rep("#D55E00",7),rep("#0072B2",8), rep("#D55E00",8), rep("#D55E00",7)), alpha.f = .5))
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig S6** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
-Positive correlations are displayed in blue and negative in red.
-The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
-#install.packages("corrplot")
-library(corrplot)
-setwd("~/R_projects/Hp_pollen_experiment")
-#Example
-#I'm going to try to show our traits on this way
-#M <- cor(mtcars)
-#corrplot(M, method = "circle")
-#We can kill two birds with one stone, showing the correlation and all the traits
-traits_all <- read.csv("Data/Csv/traits_all.csv")
-si_index <- readRDS("Data/RData/si_index.RData")
-traits_all$si_index <- si_index
-traits_all=traits_all[,-c(1,2)]
-traits_all=traits_all[,-c(1,7,11)]
-#Change order of ovary width length I rename below in row and colname
-a<-traits_all[,11]
-b<-traits_all[,12]
-traits_all[,11] <-b
-traits_all[,12]<- a
-traits_all<- cor(traits_all)
-
-rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
-                         "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
-                         "Ovary length", "Ovary width", "SI index")
-
-colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio",
-                "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
-                "Ovary length", "Ovary width", "SI index")
-
-#corrplot(traits_all, method = "circle")
-#corrplot(traits_all, type = "upper")
-par(mar=c(0,4.1,4.1,2.1))
-corrplot(traits_all, type = "lower", tl.cex = 0.8, cl.cex = 0.8, tl.col = "black", tl.srt = 45)
-
-#Add Compatibility index!
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments (apomixis, hand cross pollination, hand self pollination and spontaneous selfing).
-The coloured dots, represent the different values of seed set for each treatment."}
-
-setwd("~/R_projects/Hp_pollen_experiment")
-
-#Script to plot the reproductive biology tests
-#load libraries
-library(ggplot2)
-#install.packages("devtools")
-library(devtools)
-#install_github("easyGgplot2", "kassambara")
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-brol <- read.csv("Raw_data/brol_seed_set_final.csv")
-brra <- read.csv("Raw_data/brra_seed_set_final.csv")
-ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
-sial <- read.csv("Raw_data/sial_seed_set_final.csv")
-ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
-ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
-caan <- read.csv("Raw_data/caan_seed_set_final.csv")
-pein <- read.csv("Raw_data/pein_seed_set_final.csv")
-soly <- read.csv("Raw_data/soly_seed_set_final.csv")
-some <- read.csv("Raw_data/some_seed_set_final.csv")
-#loading traits to divide by number of ovules the seed set 
-traits <- read.csv("Data/Csv/traits_scinames.csv")
-
-brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
-brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
-brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
-ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
-sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
-ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
-ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
-caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
-caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
-pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
-pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
-soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
-some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
-
-d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
-d$Seed_set[d$Seed_set>100]<-100
-
-#levels(d$Treatment)
-d$Treatment=as.character(d$Treatment)
-d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
-d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
-d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="Control"]<-"Apomixis"
-d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
-d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
-
-d$Species=as.character(d$Species)
-d$Species[d$Family=="BROL"]<-"B"
-d$Species[d$Family=="BRRA"]<-"B"
-d$Species[d$Family=="ERSA"]<-"B"
-d$Species[d$Family=="SIAL"]<-"B"
-d$Species[d$Family=="IPPU"]<-"C"
-d$Species[d$Family=="IPAQ"]<-"C"
-d$Species[d$Family=="SOME"]<-"S"
-d$Species[d$Family=="SOLY"]<-"S"
-d$Species[d$Family=="PEIN"]<-"S"
-d$Species[d$Family=="CAAN"]<-"S"
-
-d$Species[d$Species=="BROL"]<-"B. oleracea"
-d$Species[d$Species=="BRRA"]<-"B. rapa"
-d$Species[d$Species=="SIAL"]<-"S. alba"
-d$Species[d$Species=="ERSA"]<-"E. sativa"
-d$Species[d$Species=="IPPU"]<-"I. purpurea"
-d$Species[d$Species=="IPAQ"]<-"I. aquatica"
-d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
-d$Species[d$Species=="SOME"]<-"S. melongena"
-d$Species[d$Species=="PEIN"]<-"P. integrifolia"
-d$Species[d$Species=="CAAN"]<-"C. annuum"
-
-cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
-
- ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
-  geom_violin(scale = "width",draw_quantiles = c(0.5))+
-  geom_dotplot(binaxis='y', 
-               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
-  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(legend.title = element_blank(),plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=9,fig.width=7, fig.cap="**Fig.
-S8** Effect sizes (95% confidence intervals) of the different families on each focal species (recipient) and a hand cross-pollination treatment (control).
-For each species the control treatment appears in yellow and the grouped effect per family in blue for Brassicaceae, green for Convolvulaceae and orange for Solanaceae."}
-
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-setwd("~/R_projects/Hp_pollen_experiment")
-load("Data/RData/some_effect_size_family.RData")
-
-pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/soly_effect_size_family.RData")
-
-pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/sial_effect_size_family.RData")
-
-p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/pein_effect_size_family.RData")
-
-p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ippu_effect_size_family.RData")
-
-p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ipaq_effect_size_family.RData")
-
-p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ersa_effect_size_family.RData")
-
-p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/caan_effect_size_family.RData")
-
-p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/brra_effect_size_family.RData")
-
-p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/brol_effect_size_family.RData")
-
-p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  scale_fill_manual("Family",values=c("#E69F00", "#0072B2", "#009E73", "#D55E00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-grid.newpage()
- grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
-```

### 2020-07-01 Thesis_Chapter_1/Supp_Material.Rmd
supp mat almost done

@@
 
-__Table S4.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
+__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
 
-__Table S5.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
+__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
 
-__Table S6.__ Phylogenetic signal and significance for all the different traits
+__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
 
-__Table S7.__ Procrustes analysis results.
+__Table S7.__ Phylogenetic signal and significance for all the different traits
+
+__Table S8.__ Procrustes analysis results.
 
@@
 t <- data.frame(Species, Common_names, Variety, Source)
+colnames(t) <- c("Species", "Common names", "Varieties", "Source")
 kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
              caption = "\\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 7, full_width=T) %>% row_spec(0,bold=TRUE)  
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 10, full_width=T) %>% row_spec(0,bold=TRUE)  %>%
+  column_spec(1,italic =T)
 ```
@@
 
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Measurements ($\\bar{X}$ ± SD) for all the 13 different traits for all plant species.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Trait measurements ($\\bar{X}$ ± SD) for the 13 different traits measured for each plant species.
+Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
+", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
 ```
@@
 dat <- readRDS("Tables/rep_biology_supplementary.rds")
-kable(dat, format="markdown", caption= "\\textbf{Table S3.} Seed:ovule ratio in percentage for hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.",digits = 2, longtable = F, escape = FALSE,dbooktabs = T,linesep = "\\addlinespace") %>%   row_spec(0,bold=TRUE)  %>% column_spec(1, width = "6cm")
+
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
+The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)
+
 ```
@@
 d <- as.data.frame(d)
+d <- d[,-12]
+d[11,12] <- "$\\bar{X}=67.8$"
+colnames(d) <- c("", "Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena", "$\\%$ of significant effect")
 
-kable(d, "latex", longtable = F, caption= "\\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear mixed effect models.
-The category of “yes” represents significant effect of the donors (columns) on the different recipient species (rows) and “no” lack of significant reduction of seed set from the control.
-Significance was tested for all species by comparing with a control of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")
+kable(d, "latex", longtable = F, caption= "\\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control.
+Significance was tested for all species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
 ```
@@
 
+\clearpage
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
 setwd("~/R_projects/Hp_pollen_experiment")
 d <- readRDS("Data/RData/lm_table.RData")
-kable(d, format="markdown",caption= "\\textbf{Table S5.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
+#kable(d, format="latex",caption= "\\textbf{Table S5.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
 
+colnames(d) <- c("Estimates", "Standard error", "t-value", "{\\textit{P}}-value")
+
+kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S5.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments.
+We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
+The first species on the row names are the pollen recipient species and the second species the pollen donor species.
+Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses") %>%
+  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>%column_spec(1,italic =T)%>% row_spec(0,bold=TRUE)
 ```
-\newpage
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+\clearpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
 setwd("~/R_projects/Hp_pollen_experiment")
+
+library(kableExtra)
 
@@
 
-kable(seed_100, format="markdown", caption= "\\textbf{Table S6.} Number of seeds produced with 100% foreign pollen (N=900).
+seed_100 <- as.data.frame(seed_100)
+
+kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S6.} Number of seeds produced with 100\\% foreign pollen (N=900).
 From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
-In this table we show just the treatments that lead to seed production.
-", digits = 2)
+In this table we show just the treatments that lead to seed production.") %>% kable_styling(font_size = 10,position="left",full_width=F,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>%
+   add_footnote("*            Note: There are some specific cases that we think that hybridization did not occur and that the recipient species were pollen contaminated, like the one of C.
+annuum with S.
+alba with 127 seeds.
+This seems to be the case for 5 other crosses that had very low seed production when they were pollinated with 100% foreign pollen with species of other family members.
+This represents very few isolated cases (0.67% of all the 100% foreign pollen crosses conducted) and we think that our results are not compromised by this fact.
+", notation = "none") %>% column_spec(1,italic =T)%>% column_spec(2,italic =T)
 
@@
 
-\newpage
+\clearpage
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,  out.width='40%'}
 
@@
 p <- as.numeric(p)
-trait <- c("Selfing rate", "**Pollen size**", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "**Stigmatic area**", "Stigma length", "**Stigma width**", "**Style length**", "Style width", "Ovary length", "Ovary width", "**SI index**")
+trait <- c("Selfing rate", "Pollen size", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "SI index")
 table<- data.frame(lambda,p, trait)
-colnames(table) <- c("Lambda", "_P_-value", "Traits")
-kable(table, format="markdown",caption= "\\textbf{Table S7.} Phylogenetic signal and significance for all the different traits.", digits = 2)
+colnames(table) <- c("Lambda", "P-value", "Traits")
+#kable(table, format="latex",caption= "\\textbf{Table S7.} Phylogenetic signal and significance for all the different traits.", digits = 2)
+
+kable(table, format="latex",escape=F,digits=2, longtable = F,booktabs = T,linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.") %>% kable_styling(font_size = 10, full_width=F,latex_options = c("striped")) %>% row_spec(0,bold=TRUE)
+
 ```
 
-\newpage
+\clearpage
 
@@
 table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
-colnames(table) <- c("Correlation (r)","Sum of squares", "_P_-value", "Traits", "Family")
-kable(table, caption= "\\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae and just Brassicaceae.",format="markdown", digits = 2)
+
+colnames(table) <- c("Correlation (r)","Sum of squares", "P-value", "Traits", "Family")
+
+kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.") %>%
+  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>% row_spec(0,bold=TRUE)
+
 ```
 
-\newpage
+\clearpage
 

### 2020-07-01 Thesis_Chapter_1/Supp_Material.tex
supp mat almost done

--- 2020-06-29 Thesis_Chapter_1/Supp_Material.tex
@@
 \captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty}
-\renewcommand{\figurename}{}
+\captionsetup[table]{labelformat=empty} \renewcommand{\figurename}{}
 
-\hypertarget{supporting-information}{%
-\section{Supporting information:}\label{supporting-information}}
+\section{Supporting information:}\label{supporting-information}
 
-\hypertarget{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}{%
 \section{Recipient and donor characteristics govern the hierarchical
 structure of heterospecific pollen competition
-networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}}
+networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}
 
-\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
+\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
 Romina Rader
@@
 
-\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont
+\begingroup\fontsize{10}{12}\selectfont
 
-\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\begin{longtabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
 \toprule
-\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
+\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
 \midrule
 \endfirsthead
-\multicolumn{4}{@{}l}{\textit{(continued)}}\\
+\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
 \toprule
-Species & Common\_names & Variety & Source\\
+Species & Common names & Varieties & Source\\
 \midrule
 \endhead
-\
+
 \endfoot
@@
 
-TABLE S2
-\begingroup\fontsize{6}{8}\selectfont
+\begin{table}
 
+\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Trait measurements ($\bar{X}$ ± SD) for the 13 different traits measured for each plant species.
+Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
+}
+\centering
 \resizebox{\linewidth}{!}{
-\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
 \toprule
@@
 
-TABLE S3 \begingroup\fontsize{6}{8}\selectfont
+\begin{table}
 
+\caption{\label{tab:unnamed-chunk-3}\textbf{Table S3.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
+The values provided are the seed:ovule ratios in percentage.}
+\centering
 \resizebox{\linewidth}{!}{
-\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
 \toprule
@@
 
+\begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control.
+Significance was tested for all species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright}X>{\raggedright}X}
+\toprule
+\em{} & \em{Brassica oleracea} & \em{Brassica rapa} & \em{Eruca sativa} & \em{Sinapis alba} & \em{Ipomoea aquatica} & \em{Ipomoea purpurea} & \em{Capsicum annuum} & \em{Petunia integrifolia} & \em{Solanum lycopersicum} & \em{Solanum melongena} & \em{$\%$ of significant effect}\\
+\midrule
+\rowcolor{gray!6}  B. oleracea &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 100\\
+\addlinespace
+B. rapa & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 88.9\\
+\addlinespace
+\rowcolor{gray!6}  E. sativa & Yes & No &  & No & Yes & No & No & No & No & No & 22.2\\
+\addlinespace
+S. alba & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 44.4\\
+\addlinespace
+\rowcolor{gray!6}  I. aquatica & Yes & Yes & Yes & Yes &  & Yes & Yes & Yes & Yes & Yes & 100\\
+\addlinespace
+I. purpurea & No & No & Yes & No & No &  & Yes & No & Yes & No & 33.3\\
+\addlinespace
+\rowcolor{gray!6}  C. annuum & Yes & Yes & No & Yes & No & Yes &  & Yes & Yes1 & Yes & 77.8\\
+\addlinespace
+P. integrifolia & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 67.7\\
+\addlinespace
+\rowcolor{gray!6}  S. lycopersicum & No & Yes & Yes & Yes & Yes & Yes & Yes & Yes &  & Yes & 88.9\\
+\addlinespace
+S. melongena & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 55.6\\
+\addlinespace
+\rowcolor{gray!6}   &  &  &  &  &  &  &  &  &  &  & $\bar{X}=67.8$\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\end{landscape}
+
+\clearpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{\em}lrrrr}
+\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments.
+We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
+The first species on the row names are the pollen recipient species and the second species the pollen donor species.
+Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses}\\
+\toprule
+\textbf{ } & \textbf{Estimates} & \textbf{Standard error} & \textbf{t-value} & \textbf{{\textit{P}}-value}\\
+\midrule
+\rowcolor{gray!6}  M1 Petunia integrifolia - (Intercept) & 4.63 & 0.49 & 9.36 & 0.00\\
+\addlinespace
+M1 Petunia integrifolia - Brassica oleracea & -1.84 & 0.81 & -2.27 & 0.03\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Brassica rapa & -0.97 & 0.81 & -1.19 & 0.24\\
+\addlinespace
+M1 Petunia integrifolia - Capsicum annuum & 0.78 & 0.81 & 0.96 & 0.34\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Eruca vesicaria & -0.91 & 0.81 & -1.12 & 0.26\\
+\addlinespace
+M1 Petunia integrifolia - Ipomoea aquatica & -3.18 & 0.81 & -3.92 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Ipomoea purpurea & -4.21 & 0.81 & -5.19 & 0.00\\
+\addlinespace
+M1 Petunia integrifolia - Sinapis alba & -2.99 & 0.81 & -3.69 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Solanum lycopersicum & -2.40 & 0.81 & -2.96 & 0.00\\
+\addlinespace
+M1 Petunia integrifolia - Solanum melongena & -2.66 & 0.81 & -3.27 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - (Intercept) & 4.39 & 0.24 & 18.54 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Brassica oleracea & -0.47 & 0.41 & -1.14 & 0.26\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Brassica rapa & -2.74 & 0.41 & -6.67 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Capsicum annuum & -4.39 & 0.41 & -10.71 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Eruca vesicaria & -2.97 & 0.41 & -7.25 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Ipomoea aquatica & -4.13 & 0.41 & -10.06 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Ipomoea purpurea & -3.80 & 0.41 & -9.27 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Petunia integrifolia & -1.82 & 0.41 & -4.44 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Sinapis alba & -3.72 & 0.41 & -9.08 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Solanum melongena & -1.84 & 0.41 & -4.49 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - (Intercept) & 6.34 & 0.70 & 9.09 & 0.00\\
+\addlinespace
+M3 Solanum melongena - Brassica oleracea & -0.67 & 0.99 & -0.68 & 0.50\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Brassica rapa & -4.33 & 0.99 & -4.39 & 0.00\\
+\addlinespace
+M3 Solanum melongena - Capsicum annuum & -2.33 & 0.99 & -2.36 & 0.02\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Eruca vesicaria & -3.12 & 0.99 & -3.16 & 0.00\\
+\addlinespace
+M3 Solanum melongena - Ipomoea aquatica & -6.34 & 0.99 & -6.43 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Ipomoea purpurea & -2.71 & 0.99 & -2.74 & 0.01\\
+\addlinespace
+M3 Solanum melongena - Petunia integrifolia & -1.43 & 0.99 & -1.45 & 0.15\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Sinapis alba & -1.11 & 0.99 & -1.12 & 0.26\\
+\addlinespace
+M3 Solanum melongena - Solanum lycopersicum & -0.84 & 0.99 & -0.86 & 0.39\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - (Intercept) & 4.59 & 0.52 & 8.78 & 0.00\\
+\addlinespace
+M4 Capsicum annuum - Brassica oleracea & -1.80 & 0.74 & -2.43 & 0.02\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Brassica rapa & -2.51 & 0.74 & -3.39 & 0.00\\
+\addlinespace
+M4 Capsicum annuum - Eruca vesicaria & -0.63 & 0.74 & -0.85 & 0.40\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Ipomoea aquatica & -1.36 & 0.74 & -1.84 & 0.07\\
+\addlinespace
+M4 Capsicum annuum - Ipomoea purpurea & -4.00 & 0.74 & -5.41 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Petunia integrifolia & -4.59 & 0.74 & -6.21 & 0.00\\
+\addlinespace
+M4 Capsicum annuum - Sinapis alba & -3.63 & 0.74 & -4.92 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Solanum lycopersicum & -1.52 & 0.74 & -2.06 & 0.04\\
+\addlinespace
+M4 Capsicum annuum - Solanum melongena & -3.29 & 0.74 & -4.46 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - (Intercept) & 1.99 & 0.22 & 8.98 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Brassica rapa & -1.37 & 0.31 & -4.35 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Capsicum annuum & -0.87 & 0.31 & -2.76 & 0.01\\
+\addlinespace
+M5 Brassica oleracea - Eruca vesicaria & -1.92 & 0.31 & -6.13 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Ipomoea aquatica & -1.91 & 0.27 & -7.04 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Ipomoea purpurea & -1.99 & 0.31 & -6.35 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Petunia integrifolia & -1.64 & 0.31 & -5.21 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Sinapis alba & -1.57 & 0.31 & -4.99 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Solanum lycopersicum & -1.47 & 0.31 & -4.70 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Solanum melongena & -1.61 & 0.31 & -5.12 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - (Intercept) & 2.37 & 0.19 & 12.49 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Brassica oleracea & -0.54 & 0.29 & -1.89 & 0.06\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Capsicum annuum & -1.42 & 0.29 & -4.94 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Eruca vesicaria & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Ipomoea aquatica & -1.92 & 0.29 & -6.67 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Ipomoea purpurea & -2.26 & 0.29 & -7.86 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Petunia integrifolia & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Sinapis alba & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Solanum lycopersicum & -1.88 & 0.29 & -6.55 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Solanum melongena & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - (Intercept) & 1.34 & 0.35 & 3.80 & 0.00\\
+\addlinespace
+M8 Eruca sativa - Brassica oleracea & -1.34 & 0.50 & -2.69 & 0.01\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Brassica rapa & 0.66 & 0.50 & 1.32 & 0.19\\
+\addlinespace
+M8 Eruca sativa - Capsicum annuum & -0.27 & 0.50 & -0.55 & 0.58\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Ipomoea aquatica & 0.87 & 0.50 & 1.75 & 0.08\\
+\addlinespace
+M8 Eruca sativa - Ipomoea purpurea & -0.19 & 0.50 & -0.39 & 0.70\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Petunia integrifolia & 0.20 & 0.50 & 0.41 & 0.68\\
+\addlinespace
+M8 Eruca sativa - Sinapis alba & 0.32 & 0.50 & 0.65 & 0.52\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Solanum lycopersicum & -0.52 & 0.50 & -1.04 & 0.30\\
+\addlinespace
+M8 Eruca sativa - Solanum melongena & 0.54 & 0.50 & 1.09 & 0.28\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - (Intercept) & 0.82 & 0.20 & 4.05 & 0.00\\
+\addlinespace
+M9 Ipomoea purpurea - Brassica oleracea & 0.37 & 0.29 & 1.31 & 0.19\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Brassica rapa & -0.41 & 0.29 & -1.43 & 0.16\\
+\addlinespace
+M9 Ipomoea purpurea - Capsicum annuum & -0.82 & 0.29 & -2.86 & 0.01\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Eruca vesicaria & -0.75 & 0.29 & -2.62 & 0.01\\
+\addlinespace
+M9 Ipomoea purpurea - Ipomoea aquatica & 0.41 & 0.29 & 1.44 & 0.15\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Petunia integrifolia & -0.37 & 0.29 & -1.31 & 0.19\\
+\addlinespace
+M9 Ipomoea purpurea - Sinapis alba & -0.33 & 0.29 & -1.14 & 0.26\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Solanum lycopersicum & -0.82 & 0.29 & -2.86 & 0.01\\
+\addlinespace
+M9 Ipomoea purpurea - Solanum melongena & -0.24 & 0.29 & -0.82 & 0.41\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - (Intercept) & 0.80 & 0.09 & 9.36 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Brassica oleracea & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Brassica rapa & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Capsicum annuum & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Eruca vesicaria & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Ipomoea purpurea & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Petunia integrifolia & -0.59 & 0.12 & -4.89 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Sinapis alba & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Solanum lycopersicum & -0.69 & 0.12 & -5.70 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Solanum melongena & -0.80 & 0.12 & -6.62 & 0.00\\
+\bottomrule
+\end{longtable}
+
+\endgroup{}
+
+\clearpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen (N=900).
+From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
+In this table we show just the treatments that lead to seed production.}
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\em}l>{\em}lr}
+\toprule
+\textbf{Recipient} & \textbf{Donor (100\% foreign pollen)} & \textbf{Seed number}\\
+\midrule
+\rowcolor{gray!6}  Solnamum lycopersicum & Sinapis alba & 3\\
+\addlinespace
+Solnamum melongena & Petunia integrifolia & 36\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & Eruca sativa & 3\\
+\addlinespace
+Capsicum annuum & Sinapis alba & 127\\
+\addlinespace
+\rowcolor{gray!6}  Brassica rapa & Brassica oleracea & 2\\
+\addlinespace
+Brassica rapa & Brassica oleracea & 13\\
+\addlinespace
+\rowcolor{gray!6}  Sinapis alba & Brassica oleracea & \vphantom{1} 7\\
+\addlinespace
+Sinapis alba & Brassica oleracea & 5\\
+\addlinespace
+\rowcolor{gray!6}  Sinapis alba & Brassica oleracea & \vphantom{1} 7\\
+\addlinespace
+Sinapis alba & Capsicum annuum & 1\\
+\addlinespace
+\rowcolor{gray!6}  Sinapis alba & Capsicum annuum & 6\\
+\addlinespace
+Sinapis alba & Solanum lycopersicum & 1\\
+\addlinespace
+\rowcolor{gray!6}  Eruca sativa & Petunia integrifolia & 2\\
+\bottomrule
+\multicolumn{3}{l}{\textsuperscript{} * Note: There are some specific cases that we think that hybridization did not occur and that}\\
+\multicolumn{3}{l}{the recipient species were pollen contaminated, like the one of C. annuum with S. alba with 127}\\
+\multicolumn{3}{l}{seeds. This seems to be the case for 5 other crosses that had very low seed production when they}\\
+\multicolumn{3}{l}{were pollinated with 100\% foreign pollen with species of other family members. This represents}\\
+\multicolumn{3}{l}{very few isolated cases (0.67\% of all the 100\% foreign pollen crosses conducted) and we}\\
+\multicolumn{3}{l}{think that our results are not compromised by this fact.}\\
+\end{tabular}}
+\end{table}
+
+\clearpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-7}\textbf{Table S7.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{rrl}
+\toprule
+\textbf{Lambda} & \textbf{P-value} & \textbf{Traits}\\
+\midrule
+\rowcolor{gray!6}  0.95 & 0.20 & Selfing rate\\
+\addlinespace
+1.00 & 0.00 & Pollen size\\
+\addlinespace
+\rowcolor{gray!6}  0.00 & 1.00 & Pollen anther\\
+\addlinespace
+0.00 & 1.00 & Ovule number\\
+\addlinespace
+\rowcolor{gray!6}  0.00 & 1.00 & Pollen-ovule ratio\\
+\addlinespace
+0.89 & 0.01 & Stigmatic area\\
+\addlinespace
+\rowcolor{gray!6}  0.70 & 0.05 & Stigma length\\
+\addlinespace
+0.77 & 0.03 & Stigma width\\
+\addlinespace
+\rowcolor{gray!6}  0.93 & 0.01 & Style length\\
+\addlinespace
+0.00 & 1.00 & Style width\\
+\addlinespace
+\rowcolor{gray!6}  0.47 & 0.30 & Ovary length\\
+\addlinespace
+0.00 & 1.00 & Ovary width\\
+\addlinespace
+\rowcolor{gray!6}  0.00 & 0.02 & SI index\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{rrrll}
+\caption{\label{tab:unnamed-chunk-8}\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.}\\
+\toprule
+\textbf{Correlation (r)} & \textbf{Sum of squares} & \textbf{P-value} & \textbf{Traits} & \textbf{Family}\\
+\midrule
+\rowcolor{gray!6}  0.34 & 0.88 & 0.70 & Selfing rate & All\\
+\addlinespace
+0.36 & 0.87 & 0.42 & Pollen size & All\\
+\addlinespace
+\rowcolor{gray!6}  0.35 & 0.88 & 0.57 & Pollen per anther & All\\
+\addlinespace
+0.33 & 0.89 & 0.55 & Number of ovules & All\\
+\addlinespace
+\rowcolor{gray!6}  0.30 & 0.91 & 0.86 & Pollen-ovule ratio & All\\
+\addlinespace
+0.37 & 0.86 & 0.68 & Stigmatic area & All\\
+\addlinespace
+\rowcolor{gray!6}  0.62 & 0.62 & 0.10 & Stigma length & All\\
+\addlinespace
+0.46 & 0.79 & 0.47 & Stigma width & All\\
+\addlinespace
+\rowcolor{gray!6}  0.43 & 0.82 & 0.45 & Style length & All\\
+\addlinespace
+0.59 & 0.65 & 0.11 & Style width & All\\
+\addlinespace
+\rowcolor{gray!6}  0.34 & 0.88 & 0.57 & Ovary length & All\\
+\addlinespace
+0.35 & 0.88 & 0.93 & Ovary width & All\\
+\addlinespace
+\rowcolor{gray!6}  0.49 & 0.76 & 0.24 & Self-incompatibility index & All\\
+\addlinespace
+0.86 & 0.26 & 0.25 & Selfing rate & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.76 & 0.42 & 0.33 & Pollen size & Solanaceae\\
+\addlinespace
+0.42 & 0.82 & 0.79 & Pollen per anther & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.52 & 0.73 & 0.83 & Number of ovules & Solanaceae\\
+\addlinespace
+0.87 & 0.25 & 0.04 & Pollen-ovule ratio & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.82 & 0.33 & 0.17 & Stigmatic area & Solanaceae\\
+\addlinespace
+0.89 & 0.20 & 0.08 & Stigma length & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.84 & 0.29 & 0.12 & Stigma width & Solanaceae\\
+\addlinespace
+0.78 & 0.39 & 0.50 & Style length & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.52 & 0.73 & 0.71 & Style width & Solanaceae\\
+\addlinespace
+0.64 & 0.60 & 0.79 & Ovary length & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.87 & 0.23 & 0.17 & Ovary width & Solanaceae\\
+\addlinespace
+0.50 & 0.75 & 1.00 & Self-incompatibility index & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.61 & 0.63 & 0.50 & Selfing rate & Brassicaceae\\
+\addlinespace
+0.60 & 0.64 & 0.71 & Pollen size & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.40 & 0.84 & 0.96 & Pollen per anther & Brassicaceae\\
+\addlinespace
+0.62 & 0.61 & 0.42 & Number of ovules & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.49 & 0.76 & 0.96 & Pollen-ovule ratio & Brassicaceae\\
+\addlinespace
+0.55 & 0.70 & 0.58 & Stigmatic area & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.92 & 0.15 & 0.08 & Stigma length & Brassicaceae\\
+\addlinespace
+0.63 & 0.60 & 0.38 & Stigma width & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.83 & 0.31 & 0.08 & Style length & Brassicaceae\\
+\addlinespace
+0.79 & 0.37 & 0.33 & Style width & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.59 & 0.65 & 0.50 & Ovary length & Brassicaceae\\
+\addlinespace
+0.54 & 0.70 & 1.00 & Ovary width & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.50 & 0.75 & 0.83 & Self-incompatibility index & Brassicaceae\\
+\bottomrule
+\end{longtable}
+
+\endgroup{}
+
+\clearpage
+
 \begin{figure}
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
 \caption{\textbf{Fig. S1} Average number of pollen grains per stigma for

### 2020-07-01 Untitled.Rmd
supp mat almost done

@@
 title: "Untitled"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
+  header-includes:
+  - \usepackage{booktabs}
+  - \usepackage{longtable}
+  - \usepackage{array}
+  - \usepackage{multirow}
+  - \usepackage[table]{xcolor}
+  - \usepackage{wrapfig}
+  - \usepackage{float}
+  - \usepackage{colortbl}
+  - \usepackage{pdflscape}
+  - \usepackage{tabu}
+  - \usepackage{threeparttable}
+  - \usepackage[normalem]{ulem}
 ---
-
 ```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
@@
 table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
-colnames(table) <- c("Correlation (r)","Sum of squares", "_P_-value", "Traits", "Family")
-kable(table, format="markdown", digits = 2)
+colnames(table) <- c("Correlation (r)","Sum of squares", "P-value", "Traits", "Family")
+
+kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae and just Brassicaceae.") %>%
+  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>% row_spec(0,bold=TRUE)
+
 ```

### 2020-07-10 Thesis_Chapter_1/Supp_Material.Rmd
Reorganize tables and figures according to sup material

@@
 
-__Table S7.__ Phylogenetic signal and significance for all the different traits
+__Table S7.__ Procrustes analysis results.
 
-__Table S8.__ Procrustes analysis results.
+__Table S8.__ Phylogenetic signal and significance for all the different traits
 
-__Figure S1__. Total amount of pollen deposited per stigma.
+__Figure S1__. Species reproductive biology.
 
-__Figure S2__. Pollen ratios for the different recipient species.
+__Figure S2__. Total amount of pollen deposited per stigma.
 
-__Figure S3__. Pollen ratios for the different recipient species by family.
+__Figure S3__. Pollen ratios for the different recipient species.
 
-__Figure S4__. Statistical comparison of the pollen ratios by family.
+__Figure S4__. Pollen ratios for the different recipient species by family.
 
-__Figure S5__. Unipartite bidirectional network with asymmetrical effect.
+__Figure S5__. Statistical comparison of the pollen ratios by family.
 
-__Figure S6__. Correlation matrix for all the different traits.
+__Figure S6__. Unipartite bidirectional network with asymmetrical effect.
 
-__Figure S7__. Species reproductive biology.
+__Figure S7__. Correlation matrix for all the different traits.
 
@@
 The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control.
-Significance was tested for all species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
+Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
 ```
@@
 
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
+S1** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
+The coloured dots, represent the different values of seed set for each treatment."}
+
+setwd("~/R_projects/Hp_pollen_experiment")
+
+#Script to plot the reproductive biology tests
+#load libraries
+library(ggplot2)
+#install.packages("devtools")
+library(devtools)
+#install_github("easyGgplot2", "kassambara")
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+brol <- read.csv("Raw_data/brol_seed_set_final.csv")
+brra <- read.csv("Raw_data/brra_seed_set_final.csv")
+ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
+sial <- read.csv("Raw_data/sial_seed_set_final.csv")
+ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
+ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
+caan <- read.csv("Raw_data/caan_seed_set_final.csv")
+pein <- read.csv("Raw_data/pein_seed_set_final.csv")
+soly <- read.csv("Raw_data/soly_seed_set_final.csv")
+some <- read.csv("Raw_data/some_seed_set_final.csv")
+#loading traits to divide by number of ovules the seed set 
+traits <- read.csv("Data/Csv/traits_scinames.csv")
+
+brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
+brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
+brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
+ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
+sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
+ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
+ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
+caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
+pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
+soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
+some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
+
+d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
+d$Seed_set[d$Seed_set>100]<-100
+
+#levels(d$Treatment)
+d$Treatment=as.character(d$Treatment)
+d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="Control"]<-"Apomixis"
+d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
+d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
+
+d$Species=as.character(d$Species)
+d$Species[d$Family=="BROL"]<-"B"
+d$Species[d$Family=="BRRA"]<-"B"
+d$Species[d$Family=="ERSA"]<-"B"
+d$Species[d$Family=="SIAL"]<-"B"
+d$Species[d$Family=="IPPU"]<-"C"
+d$Species[d$Family=="IPAQ"]<-"C"
+d$Species[d$Family=="SOME"]<-"S"
+d$Species[d$Family=="SOLY"]<-"S"
+d$Species[d$Family=="PEIN"]<-"S"
+d$Species[d$Family=="CAAN"]<-"S"
+
+d$Species[d$Species=="BROL"]<-"B. oleracea"
+d$Species[d$Species=="BRRA"]<-"B. rapa"
+d$Species[d$Species=="SIAL"]<-"S. alba"
+d$Species[d$Species=="ERSA"]<-"E. sativa"
+d$Species[d$Species=="IPPU"]<-"I. purpurea"
+d$Species[d$Species=="IPAQ"]<-"I. aquatica"
+d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
+d$Species[d$Species=="SOME"]<-"S. melongena"
+d$Species[d$Species=="PEIN"]<-"P. integrifolia"
+d$Species[d$Species=="CAAN"]<-"C. annuum"
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
+ ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
+  geom_violin(scale = "width",draw_quantiles = c(0.5))+
+  geom_dotplot(binaxis='y', 
+               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
+  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
+
+```
+
+\clearpage
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig.
-S1** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
+S2** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
 For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig.
-S2** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+S3** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
 These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig.
-S3** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
+S4** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
 We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S4** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
+S5** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
 These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20).
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig.
-S5** Unipartite bidirectional network with asymmetrical effect.
+S6** Unipartite bidirectional network with asymmetrical effect.
 The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig.
-S6** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
+S7** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
 Positive correlations are displayed in blue and negative in red.
@@
 \clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
-The coloured dots, represent the different values of seed set for each treatment."}
-
-setwd("~/R_projects/Hp_pollen_experiment")
-
-#Script to plot the reproductive biology tests
-#load libraries
-library(ggplot2)
-#install.packages("devtools")
-library(devtools)
-#install_github("easyGgplot2", "kassambara")
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-brol <- read.csv("Raw_data/brol_seed_set_final.csv")
-brra <- read.csv("Raw_data/brra_seed_set_final.csv")
-ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
-sial <- read.csv("Raw_data/sial_seed_set_final.csv")
-ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
-ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
-caan <- read.csv("Raw_data/caan_seed_set_final.csv")
-pein <- read.csv("Raw_data/pein_seed_set_final.csv")
-soly <- read.csv("Raw_data/soly_seed_set_final.csv")
-some <- read.csv("Raw_data/some_seed_set_final.csv")
-#loading traits to divide by number of ovules the seed set 
-traits <- read.csv("Data/Csv/traits_scinames.csv")
-
-brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
-brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
-brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
-ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
-sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
-ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
-ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
-caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
-caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
-pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
-pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
-soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
-some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
-
-d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
-d$Seed_set[d$Seed_set>100]<-100
-
-#levels(d$Treatment)
-d$Treatment=as.character(d$Treatment)
-d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
-d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
-d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="Control"]<-"Apomixis"
-d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
-d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
-
-d$Species=as.character(d$Species)
-d$Species[d$Family=="BROL"]<-"B"
-d$Species[d$Family=="BRRA"]<-"B"
-d$Species[d$Family=="ERSA"]<-"B"
-d$Species[d$Family=="SIAL"]<-"B"
-d$Species[d$Family=="IPPU"]<-"C"
-d$Species[d$Family=="IPAQ"]<-"C"
-d$Species[d$Family=="SOME"]<-"S"
-d$Species[d$Family=="SOLY"]<-"S"
-d$Species[d$Family=="PEIN"]<-"S"
-d$Species[d$Family=="CAAN"]<-"S"
-
-d$Species[d$Species=="BROL"]<-"B. oleracea"
-d$Species[d$Species=="BRRA"]<-"B. rapa"
-d$Species[d$Species=="SIAL"]<-"S. alba"
-d$Species[d$Species=="ERSA"]<-"E. sativa"
-d$Species[d$Species=="IPPU"]<-"I. purpurea"
-d$Species[d$Species=="IPAQ"]<-"I. aquatica"
-d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
-d$Species[d$Species=="SOME"]<-"S. melongena"
-d$Species[d$Species=="PEIN"]<-"P. integrifolia"
-d$Species[d$Species=="CAAN"]<-"C. annuum"
-
-cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
-
- ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
-  geom_violin(scale = "width",draw_quantiles = c(0.5))+
-  geom_dotplot(binaxis='y', 
-               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
-  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
-
-```
-
-\newpage
 

### 2020-07-29 Thesis_Chapter_1/Supp_Material.Rmd
adding new table to supp material of pollen grains per stigma

@@
 
-__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
+__Table S4.__ Total number of pollen grains per stigma.
 
-__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
+__Table S5.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
 
-__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
+__Table S6.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
 
-__Table S7.__ Procrustes analysis results.
+__Table S7.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
 
-__Table S8.__ Phylogenetic signal and significance for all the different traits
+__Table S8.__ Procrustes analysis results.
+
+__Table S9.__ Phylogenetic signal and significance for all the different traits
 
@@
 
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
+dat <- readRDS("Tables/total_pollen.rds")
+dat <- dat[,-5]
+colnames(dat) <- c("Recipient", "Donor", "Recipient pollen grains", "Donor pollen grains")
+
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average pollen grains per stigma for both recipient and donor species for 20 different treatments (3 replicates per treatment)", escape = FALSE,booktabs = T,linesep = "\\addlinespace")
+
+```
+
 \begin{landscape}
@@
 
-kable(d, "latex", longtable = F, caption= "\\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models.
+kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models.
 The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control.
@@
 d <- readRDS("Data/RData/lm_table.RData")
-#kable(d, format="latex",caption= "\\textbf{Table S5.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
+#kable(d, format="latex",caption= "\\textbf{Table S6.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
 
@@
 
-kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S5.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments.
+kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments.
 We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
@@
 
-kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S6.} Number of seeds produced with 100\\% foreign pollen (N=900).
+kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with 100\\% foreign pollen (N=900).
 From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
@@
 
-kable(table, format="latex",escape=F,digits=2, longtable = F,booktabs = T,linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.") %>% kable_styling(font_size = 10, full_width=F,latex_options = c("striped")) %>% row_spec(0,bold=TRUE)
+kable(table, format="latex",escape=F,digits=2, longtable = F,booktabs = T,linesep = "\\addlinespace", caption= "\\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.") %>% kable_styling(font_size = 10, full_width=F,latex_options = c("striped")) %>% row_spec(0,bold=TRUE)
 
@@
 
-kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.") %>%
+kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S9.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.") %>%
   kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>% row_spec(0,bold=TRUE)

### 2020-07-29 Scripts/Analysis/Traits_correlogram.R

@@ -35,4 +35,6 @@ corrplot(traits_all, type = "lower",  tl.col = "black", tl.srt = 45)
 
 #Add Compatibility index!
 
+traits_all_filtered <- traits_all[-c(1,4,6,7,8,10:13),-c(1,4,6,7,8,10:13)]
+corrplot(traits_all_filtered, type = "lower",  tl.col = "black", tl.srt = 45)
 

### 2020-07-29 Scripts/Data_preparation/Traits/total_pollen_stigma.R

@@ -294,22 +294,33 @@ barplot(total_brol, hor=T,col=coul ,space=0.8, border="white",srt=80,las=1,cex.a
 
 #Total pollen
 total_pollen <- read.csv("Data/total_pollen.csv")
+total_pollen <- total_pollen[,-1]
+colnames(total_pollen)[2] <- "non_focal"
+colnames(total_pollen)[3] <- "pollen_per_stigma"
 
-ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable)) +
+
+ggplot(total_pollen, aes(x=spp, y=pollen_per_stigma, fill=variable)) +
   geom_bar(stat='identity', position='dodge')+theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1))+
   scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))
 
 
 
-ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
+ggplot(total_pollen, aes(x=spp, y=pollen_per_stigma, fill=variable,width=.9)) +
   geom_bar(stat='identity', position='dodge')+theme_minimal()+
   theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
   scale_fill_manual(values=c("#999999","#779799"),labels = c("Recipient","Donor"))+labs(x = "",y="Pollen on stigma")
 
 
 
+total_pollen <- write.csv(total_pollen, "Data/total_pollen.csv")
 
+a <- total_pollen[1:20,]
+b <- total_pollen[21:40,]
 
-
-
-
+ab <- cbind(a,b)
+colnames(ab)[3] <- "focal_pollen"
+ab <- ab[,-c(4,5,6,7,8,10,11)]
+colnames(ab)[4] <- "non_focal_pollen"
+colnames(ab)[5] <- "focal_non_focal_pollen"
+write.csv(ab, "Data/total_pollen_table_supp_mat.csv")
+saveRDS(ab, "Thesis_Chapter_1/Tables/total_pollen.rds")

### 2020-07-31 Thesis_Chapter_1/Supp_Material.Rmd
edits in captions. One extra table added

@@
 
-__Table S2.__ Numerical values of all the traits measured for each species.
+__Table S2.__ Trait measurements for all species.
 
-__Table S3.__ Seed set in percentage for hand cross-pollination, hand self-pollination, natural selfing and apomixis for all species.
+__Table S3.__ Seed:ovule ratio (%) of the different reproductive biology treatments.
 
-__Table S4.__ Total number of pollen grains per stigma.
+__Table S4.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
 
-__Table S5.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
+__Table S5.__ Summary of the effect from the linear models of the different pollen donors on each recipient species.
 
-__Table S6.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
+__Table S6.__ Estimates, standard error, t-value and _P_-value of the effect of the different 9 donors on each recipient species.
 
-__Table S7.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
+__Table S7.__ Total number of seeds produced with the 100% foreign pollen treatments.
 
@@
 
-__Table S9.__ Phylogenetic signal and significance for all the different traits
+__Table S9.__ Phylogenetic signal and significance for all the different traits.
 
@@
 
-__Figure S2__. Total amount of pollen deposited per stigma.
+__Figure S2__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
 
-__Figure S3__. Pollen ratios for the different recipient species.
+__Figure S3__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
 
-__Figure S4__. Pollen ratios for the different recipient species by family.
+__Figure S4__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.
 
-__Figure S5__. Statistical comparison of the pollen ratios by family.
+__Figure S5__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.
 
@@
 
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Trait measurements ($\\bar{X}$ ± SD) for the 13 different traits measured for each plant species.
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Average values of the trait measurements for each plant species.
+Sample sizes are provided on the methods section.
 Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
-", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
+The raw data can be found on the online repository provided within this manuscript.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
 ```
@@
 dat <- dat[,-5]
-colnames(dat) <- c("Recipient", "Donor", "Recipient pollen grains", "Donor pollen grains")
+colnames(dat) <- c("Recipient species", "Donor species", "Recipient pollen grains", "Donor pollen grains")
 
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average pollen grains per stigma for both recipient and donor species for 20 different treatments (3 replicates per treatment)", escape = FALSE,booktabs = T,linesep = "\\addlinespace")
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)
 
@@
 
-kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models.
-The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control.
+kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment.
 Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
@@
 
-kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments.
+kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments.
 We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
@@
 
-kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with 100\\% foreign pollen (N=900).
+kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with 100\\% foreign pollen treatments (N=900).
 From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.

### 2020-07-31 Thesis_Chapter_1/Supp_Material.tex
edits in captions. One extra table added

@@
 
-\textbf{Table S2.} Numerical values of all the traits measured for each
-species.
+\textbf{Table S2.} Trait measurements for all species.
 
-\textbf{Table S3.} Seed set in percentage for hand cross-pollination,
-hand self-pollination, natural selfing and apomixis for all species.
+\textbf{Table S3.} Seed:ovule ratio (\%) of the different reproductive
+biology treatments.
 
-\textbf{Table S4.} Species x species matrix with the significance of
-effect ``yes'' or ``no'' of the different donors on the seed set of the
-different recipient species.
+\textbf{Table S4.} Average number of pollen grains of the recipient and
+donor species per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
-effect of the different 9 donors on each recipient species.
+\textbf{Table S5.} Summary of the effect from the linear models of the
+different pollen donors on each recipient species.
 
-\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
-treatments for the different recipient species.
+\textbf{Table S6.} Estimates, standard error, t-value and \emph{P}-value
+of the effect of the different 9 donors on each recipient species.
 
-\textbf{Table S7.} Phylogenetic signal and significance for all the
-different traits
+\textbf{Table S7.} Total number of seeds produced with the 100\% foreign
+pollen treatments.
 
@@
 
-\textbf{Figure S1}. Total amount of pollen deposited per stigma.
+\textbf{Table S9.} Phylogenetic signal and significance for all the
+different traits.
 
-\textbf{Figure S2}. Pollen ratios for the different recipient species.
+\textbf{Figure S1}. Species reproductive biology.
 
-\textbf{Figure S3}. Pollen ratios for the different recipient species by
-family.
+\textbf{Figure S2}. Average number of pollen grains of recipient and
+donor species per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Figure S4}. Statistical comparison of the pollen ratios by
-family.
+\textbf{Figure S3}. Average proportion (\%) of conspecific and
+heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Figure S5}. Unipartite bidirectional network with asymmetrical
+\textbf{Figure S4}. Average proportion (\%) of heterospecific and
+conspecific pollen per stigma and family with the 50:50 mix CP:HP
+pollen.
+
+\textbf{Figure S5}. Statistical comparison of the percentage of
+heterospecific pollen with the 50:50 pollen mix by family.
+
+\textbf{Figure S6}. Unipartite bidirectional network with asymmetrical
 effect.
 
-\textbf{Figure S6}. Correlation matrix for all the different traits.
-
-\textbf{Figure S7}. Species reproductive biology.
+\textbf{Figure S7}. Correlation matrix for all the different traits.
 
@@
 
-\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Trait measurements ($\bar{X}$ ± SD) for the 13 different traits measured for each plant species.
+\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Average values of the trait measurements for each plant species.
+Sample sizes are provided on the methods section.
 Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
-}
+The raw data can be found on the online repository provided within this manuscript.}
 \centering
@@
 
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\em}l>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Recipient species} & \textbf{Donor species} & \textbf{Recipient pollen grains} & \textbf{Donor pollen grains}\\
+\midrule
+\rowcolor{gray!6}  C. annuum & I. purpurea & 258 & 11\\
+\addlinespace
+E. sativa & I. purpurea & 1308 & 8\\
+\addlinespace
+\rowcolor{gray!6}  B. oleracea & I. purpurea & 90 & 20\\
+\addlinespace
+B. rapa & I. purpurea & 193 & 2\\
+\addlinespace
+\rowcolor{gray!6}  S. melongena & I. aquatica & 64 & 26\\
+\addlinespace
+P. integrifolia & I. aquatica & 23 & 20\\
+\addlinespace
+\rowcolor{gray!6}  S. lycopersicum & I. aquatica & 56 & 10\\
+\addlinespace
+S. alba & I. aquatica & 1617 & 19\\
+\addlinespace
+\rowcolor{gray!6}  I. purpurea & S. melongena & 138 & 362\\
+\addlinespace
+S. alba & S. melongena & 3054 & 1096\\
+\addlinespace
+\rowcolor{gray!6}  E. sativa & P. integrifolia & 621 & 321\\
+\addlinespace
+B. rapa & S. lycopersicum & 1114 & 246\\
+\addlinespace
+\rowcolor{gray!6}  I. aquatica & C. annuum & 35 & 85\\
+\addlinespace
+B. oleracea & C. annuum & 281 & 209\\
+\addlinespace
+\rowcolor{gray!6}  I. purpurea & E. sativa & 27 & 216\\
+\addlinespace
+S. melongena & E. sativa & 1837 & 2231\\
+\addlinespace
+\rowcolor{gray!6}  P. integrifolia & B. oleracea & 332 & 376\\
+\addlinespace
+I. aquatica & S. alba & 42 & 170\\
+\addlinespace
+\rowcolor{gray!6}  C. annuum & S. alba & 304 & 450\\
+\addlinespace
+S. lycopersicum & B. rapa & 164 & 208\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
 \begin{landscape}
@@
 
-\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear models.
-The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control.
-Significance was tested for all species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
+\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment.
+Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
 \centering
@@
 \begin{longtable}[t]{>{\em}lrrrr}
-\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Results of the linear models conducted to test heterospecific pollen effect with the 50-50 CP-HP pollen treatments.
+\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments.
 We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
@@
 
-\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen (N=900).
+\caption{\label{tab:unnamed-chunk-7}\textbf{Table S7.} Number of seeds produced with 100\% foreign pollen treatments (N=900).
 From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
@@
 
-\caption{\label{tab:unnamed-chunk-7}\textbf{Table S7.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.}
+\caption{\label{tab:unnamed-chunk-8}\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.}
 \centering
@@
 \begin{longtable}[t]{rrrll}
-\caption{\label{tab:unnamed-chunk-8}\textbf{Table S8.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.}\\
+\caption{\label{tab:unnamed-chunk-9}\textbf{Table S9.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.}\\
 \toprule
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-9-1.pdf}
-\caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\textbf{Fig. S1} Violin plot of the proportion of seeds
+coverted to ovule (\%) for all species with four different
+hand-pollination treatments: apomixis (orange), hand cross pollination
+(green), hand self pollination (blue) and spontaneous selfing (yellow).
+The coloured dots, represent the different values of seed set for each
+treatment.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\textbf{Fig. S2} Average number of pollen grains per stigma for
 20 different treatments (3 replicates per tratment). For each treatment,
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
-\caption{\textbf{Fig. S2} Average proportion of conspecific and
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\textbf{Fig. S3} Average proportion of conspecific and
 heterospecific pollen per stigma grouped by family, A) Brassicaceae, B)
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
-\caption{\textbf{Fig. S3} Average proportion (\%) of heterospecific and
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\textbf{Fig. S4} Average proportion (\%) of heterospecific and
 conspecific pollen per family for the different 20 treatments counted.
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-12-1.pdf}
-\caption{\textbf{Fig. S4} Pollen ratios comparisons between the
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\textbf{Fig. S5} Pollen ratios comparisons between the
 different pollen recipient families where the boxes represent least
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-13-1.pdf}
-\caption{\textbf{Fig. S5} Unipartite bidirectional network with
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\textbf{Fig. S6} Unipartite bidirectional network with
 asymmetrical effect. The lines with the arrow heads connect the impact
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-14-1.pdf}
-\caption{\textbf{Fig. S6} Graphical representation of the correlation
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{\textbf{Fig. S7} Graphical representation of the correlation
 matrix of the different reproductive traits considered in the
@@
 \centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-15-1.pdf}
-\caption{\textbf{Fig. S7} Violin plot of the proportion of seeds
-coverted to ovule (\%) for all species with four different
-hand-pollination treatments: apomixis (orange), hand cross pollination
-(green), hand self pollination (blue) and spontaneous selfing (yellow).
-The coloured dots, represent the different values of seed set for each
-treatment.}
-\end{figure}
-
-\newpage
-
-\begin{figure}
-\centering
-\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-16-1.pdf}
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-17-1.pdf}
 \caption{\textbf{Fig. S8} Grouped effect sizes (95\% confidence

### 2020-07-31 Thesis_Chapter_1/Supp_Material.Rmd
Edits on the captions of figures and tables of supp mat

@@
 The first species on the row names are the pollen recipient species and the second species the pollen donor species.
-Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses") %>%
+Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.") %>%
   kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>%column_spec(1,italic =T)%>% row_spec(0,bold=TRUE)
@@
 
-kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with 100\\% foreign pollen treatments (N=900).
+kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with the 100\\% foreign pollen treatments (N=900).
 From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
@@
 S1** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
-The coloured dots, represent the different values of seed set for each treatment."}
+The coloured dots, represent the different values of seed:ovule ratio for each treatment."}
 
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S5** Pollen ratios comparisons between the different pollen recipient families where the boxes represent least square means, the error bars, confidence intervals 95%, and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
-These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen), and then compared by family (N=20).
+S5** Pollen ratios comparisons between the different pollen recipient families The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
+These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen).
 Brassicacea family is coloured in blue, Convolvulaceae in green and Solanaceae in orange."}
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig.
-S7** Graphical representation of the correlation matrix of the different reproductive traits considered in the experiment.
+S7** Graphical representation of the correlation matrix of all the traits measured.
 Positive correlations are displayed in blue and negative in red.

### 2020-08-05 Thesis_Chapter_1/Supp_Material.Rmd
Supplementary material (new order)

@@
 
-__Table S3.__ Seed:ovule ratio (%) of the different reproductive biology treatments.
+__Table S3.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
 
-__Table S4.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
+__Table S4.__ Seed:ovule ratio (%) of the different reproductive biology treatments.
 
@@
 
-__Figure S1__. Species reproductive biology.
+__Figure S1__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
 
-__Figure S2__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
+__Figure S2__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
 
-__Figure S3__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
+__Figure S3__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.
 
-__Figure S4__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.
+__Figure S4__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.
 
-__Figure S5__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.
+__Figure S5__. Unipartite bidirectional network with asymmetrical effect.
 
-__Figure S6__. Unipartite bidirectional network with asymmetrical effect.
+__Figure S6__. Correlation matrix for all the different traits.
 
-__Figure S7__. Correlation matrix for all the different traits.
+__Figure S7__. Species reproductive biology.
 
@@
 
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(kableExtra)
-dat <- readRDS("Tables/rep_biology_supplementary.rds")
-
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
-The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)
-
-```
-
 \newpage
@@
 
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
+dat <- readRDS("Tables/rep_biology_supplementary.rds")
+
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
+The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S1** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
-The coloured dots, represent the different values of seed:ovule ratio for each treatment."}
-
-setwd("~/R_projects/Hp_pollen_experiment")
-
-#Script to plot the reproductive biology tests
-#load libraries
-library(ggplot2)
-#install.packages("devtools")
-library(devtools)
-#install_github("easyGgplot2", "kassambara")
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-brol <- read.csv("Raw_data/brol_seed_set_final.csv")
-brra <- read.csv("Raw_data/brra_seed_set_final.csv")
-ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
-sial <- read.csv("Raw_data/sial_seed_set_final.csv")
-ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
-ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
-caan <- read.csv("Raw_data/caan_seed_set_final.csv")
-pein <- read.csv("Raw_data/pein_seed_set_final.csv")
-soly <- read.csv("Raw_data/soly_seed_set_final.csv")
-some <- read.csv("Raw_data/some_seed_set_final.csv")
-#loading traits to divide by number of ovules the seed set 
-traits <- read.csv("Data/Csv/traits_scinames.csv")
-
-brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
-brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
-brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
-ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
-sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
-sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
-ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
-ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
-caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
-caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
-pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
-pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
-soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
-some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
-some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
-
-d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
-d$Seed_set[d$Seed_set>100]<-100
-
-#levels(d$Treatment)
-d$Treatment=as.character(d$Treatment)
-d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
-d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
-d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
-d$Treatment[d$Treatment=="Control"]<-"Apomixis"
-d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
-d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
-d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
-
-d$Species=as.character(d$Species)
-d$Species[d$Family=="BROL"]<-"B"
-d$Species[d$Family=="BRRA"]<-"B"
-d$Species[d$Family=="ERSA"]<-"B"
-d$Species[d$Family=="SIAL"]<-"B"
-d$Species[d$Family=="IPPU"]<-"C"
-d$Species[d$Family=="IPAQ"]<-"C"
-d$Species[d$Family=="SOME"]<-"S"
-d$Species[d$Family=="SOLY"]<-"S"
-d$Species[d$Family=="PEIN"]<-"S"
-d$Species[d$Family=="CAAN"]<-"S"
-
-d$Species[d$Species=="BROL"]<-"B. oleracea"
-d$Species[d$Species=="BRRA"]<-"B. rapa"
-d$Species[d$Species=="SIAL"]<-"S. alba"
-d$Species[d$Species=="ERSA"]<-"E. sativa"
-d$Species[d$Species=="IPPU"]<-"I. purpurea"
-d$Species[d$Species=="IPAQ"]<-"I. aquatica"
-d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
-d$Species[d$Species=="SOME"]<-"S. melongena"
-d$Species[d$Species=="PEIN"]<-"P. integrifolia"
-d$Species[d$Species=="CAAN"]<-"C. annuum"
-
-cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
-
- ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
-  geom_violin(scale = "width",draw_quantiles = c(0.5))+
-  geom_dotplot(binaxis='y', 
-               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
-  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
-
-```
-
 \clearpage
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig.
-S2** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
+S1** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
 For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig.
-S3** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+S2** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
 These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig.
-S4** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
+S3** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
 We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S5** Pollen ratios comparisons between the different pollen recipient families The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
+S4** Pollen ratios comparisons between the different pollen recipient families The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
 These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen).
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig.
-S6** Unipartite bidirectional network with asymmetrical effect.
+S5** Unipartite bidirectional network with asymmetrical effect.
 The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species.
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig.
-S7** Graphical representation of the correlation matrix of all the traits measured.
+S6** Graphical representation of the correlation matrix of all the traits measured.
 Positive correlations are displayed in blue and negative in red.
@@
 #Add Compatibility index!
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
+S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
+The coloured dots, represent the different values of seed:ovule ratio for each treatment."}
+
+setwd("~/R_projects/Hp_pollen_experiment")
+
+#Script to plot the reproductive biology tests
+#load libraries
+library(ggplot2)
+#install.packages("devtools")
+library(devtools)
+#install_github("easyGgplot2", "kassambara")
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+brol <- read.csv("Raw_data/brol_seed_set_final.csv")
+brra <- read.csv("Raw_data/brra_seed_set_final.csv")
+ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
+sial <- read.csv("Raw_data/sial_seed_set_final.csv")
+ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
+ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
+caan <- read.csv("Raw_data/caan_seed_set_final.csv")
+pein <- read.csv("Raw_data/pein_seed_set_final.csv")
+soly <- read.csv("Raw_data/soly_seed_set_final.csv")
+some <- read.csv("Raw_data/some_seed_set_final.csv")
+#loading traits to divide by number of ovules the seed set 
+traits <- read.csv("Data/Csv/traits_scinames.csv")
+
+brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
+brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
+brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
+ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
+sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
+ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
+ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
+caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
+pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
+soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
+some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
+
+d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
+d$Seed_set[d$Seed_set>100]<-100
+
+#levels(d$Treatment)
+d$Treatment=as.character(d$Treatment)
+d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="Control"]<-"Apomixis"
+d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
+d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
+
+d$Species=as.character(d$Species)
+d$Species[d$Family=="BROL"]<-"B"
+d$Species[d$Family=="BRRA"]<-"B"
+d$Species[d$Family=="ERSA"]<-"B"
+d$Species[d$Family=="SIAL"]<-"B"
+d$Species[d$Family=="IPPU"]<-"C"
+d$Species[d$Family=="IPAQ"]<-"C"
+d$Species[d$Family=="SOME"]<-"S"
+d$Species[d$Family=="SOLY"]<-"S"
+d$Species[d$Family=="PEIN"]<-"S"
+d$Species[d$Family=="CAAN"]<-"S"
+
+d$Species[d$Species=="BROL"]<-"B. oleracea"
+d$Species[d$Species=="BRRA"]<-"B. rapa"
+d$Species[d$Species=="SIAL"]<-"S. alba"
+d$Species[d$Species=="ERSA"]<-"E. sativa"
+d$Species[d$Species=="IPPU"]<-"I. purpurea"
+d$Species[d$Species=="IPAQ"]<-"I. aquatica"
+d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
+d$Species[d$Species=="SOME"]<-"S. melongena"
+d$Species[d$Species=="PEIN"]<-"P. integrifolia"
+d$Species[d$Species=="CAAN"]<-"C. annuum"
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
+ ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
+  geom_violin(scale = "width",draw_quantiles = c(0.5))+
+  geom_dotplot(binaxis='y', 
+               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+
+  theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
 

### 2020-09-01 Figures_main_text/Figure3_effect_sizes_grouped.Rmd
pfinal edits

--- 2019-10-17 Manuscript_draft/Figure4.Rmd
@@
 ```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=2.5,fig.width=6}
-
+#Load libraries
 library(effsize)
@@
 
-load("effect_size_species/effect_size_total.RData")
-png("Figure4.png", width = 11000, height = 5000, res = 1500)
+#Load data
+#This data is generated in analysis in the "Effect sizes_total.R" file
+#Please see Script-->Analysis
+#Now figure 3 in main text
+setwd("~/R_projects/Hp_pollen_experiment")
+load("Data/RData/effect_size_total.RData")
+#save image
+#png("Figure4.png", width = 11000, height = 5000, res = 1500)
 

### 2020-09-01 Supplementary_material/Supp_Material.tex
Insert table
pfinal edits

--- 2020-04-05 Supplementary_material/Supp_Material.tex
@@
 
-\title{\textbf{Supporting Information:}}
+\usepackage{setspace}\doublespacing
+\usepackage{float}
+\usepackage{caption}
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
 \author{}
@@
 \begin{document}
-\maketitle
 
-\section{Recipient and donor characteristics govern hierarchical
-structure in a heterospecific pollen competition network of co-flowering
-plants}\label{recipient-and-donor-characteristics-govern-hierarchical-structure-in-a-heterospecific-pollen-competition-network-of-co-flowering-plants}
+\captionsetup[figure]{labelformat=empty}
+\captionsetup[table]{labelformat=empty} \renewcommand{\figurename}{}
 
-\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
+\section{Supporting information:}\label{supporting-information}
+
+\section{Recipient and donor characteristics govern the hierarchical
+structure of heterospecific pollen competition
+networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}
+
+\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
 Romina Rader
@@
 
-\textbf{Table S2.} Numerical values of all the traits measured for each
-species.
+\textbf{Table S2.} Trait measurements for all species.
 
-\textbf{Table S3.} Seed set in percentage for hand cross-pollination,
-hand self-pollination, natural selfing and apomixis for all species.
+\textbf{Table S3.} Average number of pollen grains of the recipient and
+donor species per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Table S4.} Species x species matrix with the significance of
-effect ``yes'' or ``no'' of the different donors on the seed set of the
-different recipient species.
+\textbf{Table S4.} Seed:ovule ratio (\%) of the different reproductive
+biology treatments.
 
-\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
-effect of the different 9 donors on each recipient species.
+\textbf{Table S5.} Summary of the effect from the linear models of the
+different pollen donors on each recipient species.
 
-\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
-treatments for the different recipient species.
+\textbf{Table S6.} Estimates, standard error, t-value and \emph{P}-value
+of the effect of the different 9 donors on each recipient species.
 
-\textbf{Table S7.} Phylogenetic signal and significance for all the
-different traits
+\textbf{Table S7.} Total number of seeds produced with the 100\% foreign
+pollen treatments.
 
@@
 
-\textbf{Figure S1.} Correlation matrix for all the different traits.
+\textbf{Table S9.} Phylogenetic signal and significance for all the
+different traits.
 
-\textbf{Figure S2.} Total amount of pollen found for the different
-treatments.
+\textbf{Figure S1}. Average number of pollen grains of recipient and
+donor species per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Figure S3.} Pollen ratios for the different recipient species.
+\textbf{Figure S2}. Average proportion (\%) of conspecific and
+heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Figure S4.} Pollen ratios for the different recipient species by
-family.
+\textbf{Figure S3}. Average proportion (\%) of heterospecific and
+conspecific pollen per stigma and family with the 50:50 mix CP:HP
+pollen.
 
-\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
-pollen donor and recipient.
+\textbf{Figure S4}. Statistical comparison of the percentage of
+heterospecific pollen with the 50:50 pollen mix by family.
 
-\textbf{Figure S6.} Violin plot of the reproductive biology of the
+\textbf{Figure S5}. Unipartite bidirectional network with asymmetrical
+effect.
+
+\textbf{Figure S6}. Correlation matrix for all the different traits.
+
+\textbf{Figure S7}. Species reproductive biology.
+
+\textbf{Figure S8}. Grouped effect sizes by family for each recipient
 species.
 
-Figure S7. Grouped effect sizes by family for each recipient species.
+\newpage
+
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
+\toprule
+\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
+\midrule
+\endfirsthead
+\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
+\toprule
+Species & Common names & Varieties & Source\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
+\addlinespace
+Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
+\addlinespace
+\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
+\addlinespace
+Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
+\addlinespace
+\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
+\addlinespace
+Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
+\addlinespace
+Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
+\addlinespace
+\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
+\addlinespace
+Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
+\end{longtabu}
+
+\endgroup{}
+
+\begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Average values of the trait measurements for each plant species.
+Sample sizes are provided on the methods section.
+Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
+The raw data can be found on the online repository provided within this manuscript.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
+\midrule
+\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
+\addlinespace
+Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
+\addlinespace
+Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
+\addlinespace
+\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
+\addlinespace
+Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
+\addlinespace
+\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
+\addlinespace
+Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
+\addlinespace
+\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
+\addlinespace
+Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\end{landscape}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-3}\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\em}l>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Recipient species} & \textbf{Donor species} & \textbf{Recipient pollen grains} & \textbf{Donor pollen grains}\\
+\midrule
+\rowcolor{gray!6}  C. annuum & I. purpurea & 258 & 11\\
+\addlinespace
+E. sativa & I. purpurea & 1308 & 8\\
+\addlinespace
+\rowcolor{gray!6}  B. oleracea & I. purpurea & 90 & 20\\
+\addlinespace
+B. rapa & I. purpurea & 193 & 2\\
+\addlinespace
+\rowcolor{gray!6}  S. melongena & I. aquatica & 64 & 26\\
+\addlinespace
+P. integrifolia & I. aquatica & 23 & 20\\
+\addlinespace
+\rowcolor{gray!6}  S. lycopersicum & I. aquatica & 56 & 10\\
+\addlinespace
+S. alba & I. aquatica & 1617 & 19\\
+\addlinespace
+\rowcolor{gray!6}  I. purpurea & S. melongena & 138 & 362\\
+\addlinespace
+S. alba & S. melongena & 3054 & 1096\\
+\addlinespace
+\rowcolor{gray!6}  E. sativa & P. integrifolia & 621 & 321\\
+\addlinespace
+B. rapa & S. lycopersicum & 1114 & 246\\
+\addlinespace
+\rowcolor{gray!6}  I. aquatica & C. annuum & 35 & 85\\
+\addlinespace
+B. oleracea & C. annuum & 281 & 209\\
+\addlinespace
+\rowcolor{gray!6}  I. purpurea & E. sativa & 27 & 216\\
+\addlinespace
+S. melongena & E. sativa & 1837 & 2231\\
+\addlinespace
+\rowcolor{gray!6}  P. integrifolia & B. oleracea & 332 & 376\\
+\addlinespace
+I. aquatica & S. alba & 42 & 170\\
+\addlinespace
+\rowcolor{gray!6}  C. annuum & S. alba & 304 & 450\\
+\addlinespace
+S. lycopersicum & B. rapa & 164 & 208\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
+The values provided are the seed:ovule ratios in percentage.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
+\midrule
+\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
+\addlinespace
+Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
+\addlinespace
+Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
+\addlinespace
+\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
+\addlinespace
+Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
+\addlinespace
+\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
+\addlinespace
+Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
+\addlinespace
+\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
+\addlinespace
+Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment.
+Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{\em}l>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright}X>{\raggedright}X}
+\toprule
+\em{} & \em{Brassica oleracea} & \em{Brassica rapa} & \em{Eruca sativa} & \em{Sinapis alba} & \em{Ipomoea aquatica} & \em{Ipomoea purpurea} & \em{Capsicum annuum} & \em{Petunia integrifolia} & \em{Solanum lycopersicum} & \em{Solanum melongena} & \em{$\%$ of significant effect}\\
+\midrule
+\rowcolor{gray!6}  B. oleracea &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 100\\
+\addlinespace
+B. rapa & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 88.9\\
+\addlinespace
+\rowcolor{gray!6}  E. sativa & Yes & No &  & No & Yes & No & No & No & No & No & 22.2\\
+\addlinespace
+S. alba & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 44.4\\
+\addlinespace
+\rowcolor{gray!6}  I. aquatica & Yes & Yes & Yes & Yes &  & Yes & Yes & Yes & Yes & Yes & 100\\
+\addlinespace
+I. purpurea & No & No & Yes & No & No &  & Yes & No & Yes & No & 33.3\\
+\addlinespace
+\rowcolor{gray!6}  C. annuum & Yes & Yes & No & Yes & No & Yes &  & Yes & Yes1 & Yes & 77.8\\
+\addlinespace
+P. integrifolia & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 67.7\\
+\addlinespace
+\rowcolor{gray!6}  S. lycopersicum & No & Yes & Yes & Yes & Yes & Yes & Yes & Yes &  & Yes & 88.9\\
+\addlinespace
+S. melongena & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 55.6\\
+\addlinespace
+\rowcolor{gray!6}   &  &  &  &  &  &  &  &  &  &  & $\bar{X}=67.8$\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\end{landscape}
+
+\clearpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{\em}lrrrr}
+\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments.
+We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
+The first species on the row names are the pollen recipient species and the second species the pollen donor species.
+Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.}\\
+\toprule
+\textbf{ } & \textbf{Estimates} & \textbf{Standard error} & \textbf{t-value} & \textbf{{\textit{P}}-value}\\
+\midrule
+\rowcolor{gray!6}  M1 Petunia integrifolia - (Intercept) & 4.63 & 0.49 & 9.36 & 0.00\\
+\addlinespace
+M1 Petunia integrifolia - Brassica oleracea & -1.84 & 0.81 & -2.27 & 0.03\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Brassica rapa & -0.97 & 0.81 & -1.19 & 0.24\\
+\addlinespace
+M1 Petunia integrifolia - Capsicum annuum & 0.78 & 0.81 & 0.96 & 0.34\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Eruca vesicaria & -0.91 & 0.81 & -1.12 & 0.26\\
+\addlinespace
+M1 Petunia integrifolia - Ipomoea aquatica & -3.18 & 0.81 & -3.92 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Ipomoea purpurea & -4.21 & 0.81 & -5.19 & 0.00\\
+\addlinespace
+M1 Petunia integrifolia - Sinapis alba & -2.99 & 0.81 & -3.69 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M1 Petunia integrifolia - Solanum lycopersicum & -2.40 & 0.81 & -2.96 & 0.00\\
+\addlinespace
+M1 Petunia integrifolia - Solanum melongena & -2.66 & 0.81 & -3.27 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - (Intercept) & 4.39 & 0.24 & 18.54 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Brassica oleracea & -0.47 & 0.41 & -1.14 & 0.26\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Brassica rapa & -2.74 & 0.41 & -6.67 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Capsicum annuum & -4.39 & 0.41 & -10.71 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Eruca vesicaria & -2.97 & 0.41 & -7.25 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Ipomoea aquatica & -4.13 & 0.41 & -10.06 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Ipomoea purpurea & -3.80 & 0.41 & -9.27 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Petunia integrifolia & -1.82 & 0.41 & -4.44 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M2 Solanum lycopersicum - Sinapis alba & -3.72 & 0.41 & -9.08 & 0.00\\
+\addlinespace
+M2 Solanum lycopersicum - Solanum melongena & -1.84 & 0.41 & -4.49 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - (Intercept) & 6.34 & 0.70 & 9.09 & 0.00\\
+\addlinespace
+M3 Solanum melongena - Brassica oleracea & -0.67 & 0.99 & -0.68 & 0.50\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Brassica rapa & -4.33 & 0.99 & -4.39 & 0.00\\
+\addlinespace
+M3 Solanum melongena - Capsicum annuum & -2.33 & 0.99 & -2.36 & 0.02\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Eruca vesicaria & -3.12 & 0.99 & -3.16 & 0.00\\
+\addlinespace
+M3 Solanum melongena - Ipomoea aquatica & -6.34 & 0.99 & -6.43 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Ipomoea purpurea & -2.71 & 0.99 & -2.74 & 0.01\\
+\addlinespace
+M3 Solanum melongena - Petunia integrifolia & -1.43 & 0.99 & -1.45 & 0.15\\
+\addlinespace
+\rowcolor{gray!6}  M3 Solanum melongena - Sinapis alba & -1.11 & 0.99 & -1.12 & 0.26\\
+\addlinespace
+M3 Solanum melongena - Solanum lycopersicum & -0.84 & 0.99 & -0.86 & 0.39\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - (Intercept) & 4.59 & 0.52 & 8.78 & 0.00\\
+\addlinespace
+M4 Capsicum annuum - Brassica oleracea & -1.80 & 0.74 & -2.43 & 0.02\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Brassica rapa & -2.51 & 0.74 & -3.39 & 0.00\\
+\addlinespace
+M4 Capsicum annuum - Eruca vesicaria & -0.63 & 0.74 & -0.85 & 0.40\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Ipomoea aquatica & -1.36 & 0.74 & -1.84 & 0.07\\
+\addlinespace
+M4 Capsicum annuum - Ipomoea purpurea & -4.00 & 0.74 & -5.41 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Petunia integrifolia & -4.59 & 0.74 & -6.21 & 0.00\\
+\addlinespace
+M4 Capsicum annuum - Sinapis alba & -3.63 & 0.74 & -4.92 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M4 Capsicum annuum - Solanum lycopersicum & -1.52 & 0.74 & -2.06 & 0.04\\
+\addlinespace
+M4 Capsicum annuum - Solanum melongena & -3.29 & 0.74 & -4.46 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - (Intercept) & 1.99 & 0.22 & 8.98 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Brassica rapa & -1.37 & 0.31 & -4.35 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Capsicum annuum & -0.87 & 0.31 & -2.76 & 0.01\\
+\addlinespace
+M5 Brassica oleracea - Eruca vesicaria & -1.92 & 0.31 & -6.13 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Ipomoea aquatica & -1.91 & 0.27 & -7.04 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Ipomoea purpurea & -1.99 & 0.31 & -6.35 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Petunia integrifolia & -1.64 & 0.31 & -5.21 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Sinapis alba & -1.57 & 0.31 & -4.99 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M5 Brassica oleracea - Solanum lycopersicum & -1.47 & 0.31 & -4.70 & 0.00\\
+\addlinespace
+M5 Brassica oleracea - Solanum melongena & -1.61 & 0.31 & -5.12 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - (Intercept) & 2.37 & 0.19 & 12.49 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Brassica oleracea & -0.54 & 0.29 & -1.89 & 0.06\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Capsicum annuum & -1.42 & 0.29 & -4.94 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Eruca vesicaria & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Ipomoea aquatica & -1.92 & 0.29 & -6.67 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Ipomoea purpurea & -2.26 & 0.29 & -7.86 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Petunia integrifolia & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Sinapis alba & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M6 Brassica rapa - Solanum lycopersicum & -1.88 & 0.29 & -6.55 & 0.00\\
+\addlinespace
+M6 Brassica rapa - Solanum melongena & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - (Intercept) & 1.34 & 0.35 & 3.80 & 0.00\\
+\addlinespace
+M8 Eruca sativa - Brassica oleracea & -1.34 & 0.50 & -2.69 & 0.01\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Brassica rapa & 0.66 & 0.50 & 1.32 & 0.19\\
+\addlinespace
+M8 Eruca sativa - Capsicum annuum & -0.27 & 0.50 & -0.55 & 0.58\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Ipomoea aquatica & 0.87 & 0.50 & 1.75 & 0.08\\
+\addlinespace
+M8 Eruca sativa - Ipomoea purpurea & -0.19 & 0.50 & -0.39 & 0.70\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Petunia integrifolia & 0.20 & 0.50 & 0.41 & 0.68\\
+\addlinespace
+M8 Eruca sativa - Sinapis alba & 0.32 & 0.50 & 0.65 & 0.52\\
+\addlinespace
+\rowcolor{gray!6}  M8 Eruca sativa - Solanum lycopersicum & -0.52 & 0.50 & -1.04 & 0.30\\
+\addlinespace
+M8 Eruca sativa - Solanum melongena & 0.54 & 0.50 & 1.09 & 0.28\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - (Intercept) & 0.82 & 0.20 & 4.05 & 0.00\\
+\addlinespace
+M9 Ipomoea purpurea - Brassica oleracea & 0.37 & 0.29 & 1.31 & 0.19\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Brassica rapa & -0.41 & 0.29 & -1.43 & 0.16\\
+\addlinespace
+M9 Ipomoea purpurea - Capsicum annuum & -0.82 & 0.29 & -2.86 & 0.01\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Eruca vesicaria & -0.75 & 0.29 & -2.62 & 0.01\\
+\addlinespace
+M9 Ipomoea purpurea - Ipomoea aquatica & 0.41 & 0.29 & 1.44 & 0.15\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Petunia integrifolia & -0.37 & 0.29 & -1.31 & 0.19\\
+\addlinespace
+M9 Ipomoea purpurea - Sinapis alba & -0.33 & 0.29 & -1.14 & 0.26\\
+\addlinespace
+\rowcolor{gray!6}  M9 Ipomoea purpurea - Solanum lycopersicum & -0.82 & 0.29 & -2.86 & 0.01\\
+\addlinespace
+M9 Ipomoea purpurea - Solanum melongena & -0.24 & 0.29 & -0.82 & 0.41\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - (Intercept) & 0.80 & 0.09 & 9.36 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Brassica oleracea & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Brassica rapa & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Capsicum annuum & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Eruca vesicaria & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Ipomoea purpurea & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Petunia integrifolia & -0.59 & 0.12 & -4.89 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Sinapis alba & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\rowcolor{gray!6}  M10 Ipomoea aquatica - Solanum lycopersicum & -0.69 & 0.12 & -5.70 & 0.00\\
+\addlinespace
+M10 Ipomoea aquatica - Solanum melongena & -0.80 & 0.12 & -6.62 & 0.00\\
+\bottomrule
+\end{longtable}
+
+\endgroup{}
+
+\clearpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-7}\textbf{Table S7.} Number of seeds produced with the 100\% foreign pollen treatments (N=900).
+From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
+In this table we show just the treatments that lead to seed production.}
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{\em}l>{\em}lr}
+\toprule
+\textbf{Recipient} & \textbf{Donor (100\% foreign pollen)} & \textbf{Seed number}\\
+\midrule
+\rowcolor{gray!6}  Solnamum lycopersicum & Sinapis alba & 3\\
+\addlinespace
+Solnamum melongena & Petunia integrifolia & 36\\
+\addlinespace
+\rowcolor{gray!6}  Capsicum annuum & Eruca sativa & 3\\
+\addlinespace
+Capsicum annuum & Sinapis alba & 127\\
+\addlinespace
+\rowcolor{gray!6}  Brassica rapa & Brassica oleracea & 2\\
+\addlinespace
+Brassica rapa & Brassica oleracea & 13\\
+\addlinespace
+\rowcolor{gray!6}  Sinapis alba & Brassica oleracea & \vphantom{1} 7\\
+\addlinespace
+Sinapis alba & Brassica oleracea & 5\\
+\addlinespace
+\rowcolor{gray!6}  Sinapis alba & Brassica oleracea & \vphantom{1} 7\\
+\addlinespace
+Sinapis alba & Capsicum annuum & 1\\
+\addlinespace
+\rowcolor{gray!6}  Sinapis alba & Capsicum annuum & 6\\
+\addlinespace
+Sinapis alba & Solanum lycopersicum & 1\\
+\addlinespace
+\rowcolor{gray!6}  Eruca sativa & Petunia integrifolia & 2\\
+\bottomrule
+\multicolumn{3}{l}{\textsuperscript{} * Note: There are some specific cases that we think that hybridization did not occur and that}\\
+\multicolumn{3}{l}{the recipient species were pollen contaminated, like the one of C. annuum with S. alba with 127}\\
+\multicolumn{3}{l}{seeds. This seems to be the case for 5 other crosses that had very low seed production when they}\\
+\multicolumn{3}{l}{were pollinated with 100\% foreign pollen with species of other family members. This represents}\\
+\multicolumn{3}{l}{very few isolated cases (0.67\% of all the 100\% foreign pollen crosses conducted) and we}\\
+\multicolumn{3}{l}{think that our results are not compromised by this fact.}\\
+\end{tabular}}
+\end{table}
+
+\clearpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-8}\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{rrl}
+\toprule
+\textbf{Lambda} & \textbf{P-value} & \textbf{Traits}\\
+\midrule
+\rowcolor{gray!6}  0.95 & 0.20 & Selfing rate\\
+\addlinespace
+1.00 & 0.00 & Pollen size\\
+\addlinespace
+\rowcolor{gray!6}  0.00 & 1.00 & Pollen anther\\
+\addlinespace
+0.00 & 1.00 & Ovule number\\
+\addlinespace
+\rowcolor{gray!6}  0.00 & 1.00 & Pollen-ovule ratio\\
+\addlinespace
+0.89 & 0.01 & Stigmatic area\\
+\addlinespace
+\rowcolor{gray!6}  0.70 & 0.05 & Stigma length\\
+\addlinespace
+0.77 & 0.03 & Stigma width\\
+\addlinespace
+\rowcolor{gray!6}  0.93 & 0.01 & Style length\\
+\addlinespace
+0.00 & 1.00 & Style width\\
+\addlinespace
+\rowcolor{gray!6}  0.47 & 0.30 & Ovary length\\
+\addlinespace
+0.00 & 1.00 & Ovary width\\
+\addlinespace
+\rowcolor{gray!6}  0.00 & 0.02 & SI index\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{rrrll}
+\caption{\label{tab:unnamed-chunk-9}\textbf{Table S9.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.}\\
+\toprule
+\textbf{Correlation (r)} & \textbf{Sum of squares} & \textbf{P-value} & \textbf{Traits} & \textbf{Family}\\
+\midrule
+\rowcolor{gray!6}  0.34 & 0.88 & 0.70 & Selfing rate & All\\
+\addlinespace
+0.36 & 0.87 & 0.42 & Pollen size & All\\
+\addlinespace
+\rowcolor{gray!6}  0.35 & 0.88 & 0.57 & Pollen per anther & All\\
+\addlinespace
+0.33 & 0.89 & 0.55 & Number of ovules & All\\
+\addlinespace
+\rowcolor{gray!6}  0.30 & 0.91 & 0.86 & Pollen-ovule ratio & All\\
+\addlinespace
+0.37 & 0.86 & 0.68 & Stigmatic area & All\\
+\addlinespace
+\rowcolor{gray!6}  0.62 & 0.62 & 0.10 & Stigma length & All\\
+\addlinespace
+0.46 & 0.79 & 0.47 & Stigma width & All\\
+\addlinespace
+\rowcolor{gray!6}  0.43 & 0.82 & 0.45 & Style length & All\\
+\addlinespace
+0.59 & 0.65 & 0.11 & Style width & All\\
+\addlinespace
+\rowcolor{gray!6}  0.34 & 0.88 & 0.57 & Ovary length & All\\
+\addlinespace
+0.35 & 0.88 & 0.93 & Ovary width & All\\
+\addlinespace
+\rowcolor{gray!6}  0.49 & 0.76 & 0.24 & Self-incompatibility index & All\\
+\addlinespace
+0.86 & 0.26 & 0.25 & Selfing rate & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.76 & 0.42 & 0.33 & Pollen size & Solanaceae\\
+\addlinespace
+0.42 & 0.82 & 0.79 & Pollen per anther & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.52 & 0.73 & 0.83 & Number of ovules & Solanaceae\\
+\addlinespace
+0.87 & 0.25 & 0.04 & Pollen-ovule ratio & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.82 & 0.33 & 0.17 & Stigmatic area & Solanaceae\\
+\addlinespace
+0.89 & 0.20 & 0.08 & Stigma length & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.84 & 0.29 & 0.12 & Stigma width & Solanaceae\\
+\addlinespace
+0.78 & 0.39 & 0.50 & Style length & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.52 & 0.73 & 0.71 & Style width & Solanaceae\\
+\addlinespace
+0.64 & 0.60 & 0.79 & Ovary length & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.87 & 0.23 & 0.17 & Ovary width & Solanaceae\\
+\addlinespace
+0.50 & 0.75 & 1.00 & Self-incompatibility index & Solanaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.61 & 0.63 & 0.50 & Selfing rate & Brassicaceae\\
+\addlinespace
+0.60 & 0.64 & 0.71 & Pollen size & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.40 & 0.84 & 0.96 & Pollen per anther & Brassicaceae\\
+\addlinespace
+0.62 & 0.61 & 0.42 & Number of ovules & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.49 & 0.76 & 0.96 & Pollen-ovule ratio & Brassicaceae\\
+\addlinespace
+0.55 & 0.70 & 0.58 & Stigmatic area & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.92 & 0.15 & 0.08 & Stigma length & Brassicaceae\\
+\addlinespace
+0.63 & 0.60 & 0.38 & Stigma width & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.83 & 0.31 & 0.08 & Style length & Brassicaceae\\
+\addlinespace
+0.79 & 0.37 & 0.33 & Style width & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.59 & 0.65 & 0.50 & Ovary length & Brassicaceae\\
+\addlinespace
+0.54 & 0.70 & 1.00 & Ovary width & Brassicaceae\\
+\addlinespace
+\rowcolor{gray!6}  0.50 & 0.75 & 0.83 & Self-incompatibility index & Brassicaceae\\
+\bottomrule
+\end{longtable}
+
+\endgroup{}
+
+\clearpage
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
+20 different treatments (3 replicates per tratment). For each treatment,
+we show the average number of conspecific pollen grains (grey) and
+heterospecific pollen grains (light blue) per stigma. For each pair of
+species on the x-axis, the first species is the recipient species, and
+the second, the donor species.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\textbf{Fig. S2} Average proportion of conspecific and
+heterospecific pollen per stigma grouped by family, A) Brassicaceae, B)
+Solanaceae and C) Convolvulaceae. These proportions (\%) are the number
+of conspecific pollen grains or heterospecific pollen grains divided by
+the total number of pollen grains per stigma for 20 different
+treatments. We conducted 3 count replicates per treatment and then we
+calculated the average number of pollen grains for these treatments. The
+proportion of conspecific and heterospecific pollen are shown in grey
+and light blue respectively. For each pair of species on the y-axis, the
+first species is the pollen recipient and the second the pollen donor.
+The vertical black line represents 50\% pollen of both donor and
+recipient.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\textbf{Fig. S3} Average proportion (\%) of heterospecific and
+conspecific pollen per family for the different 20 treatments counted.
+We conducted 3 count replicates per treatment and then we calculated the
+average number of pollen grains for these different 20 treatments.
+Finally, we grouped by family these treatments in order to see general
+tendencies across families as pollen donor and as pollen recipient.
+Pollen ratios were considered as the number of conspecific or
+heterospecific pollen grains divided by the total number of pollen
+grains per stigma. On the y-axis, the first family on each pair of plant
+families is the recipient one, and the second, the family of the donor.
+The vertical bar on intercept 50, represents equal proportions of both
+recipient (grey) and donor (light blue) pollen.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\textbf{Fig. S4} Pollen ratios comparisons between the
+different pollen recipient families The boxes represent least square
+means, the error bars confidence intervals 95\% and sharing numbers
+indicate no significant differences between groups (Tukey adjusted
+comparisons). These pollen ratios (\%) are the total number of
+heterospecific pollen grains divided by the total quantity of pollen
+(conspecific pollen + heterospecific pollen). Brassicacea family is
+coloured in blue, Convolvulaceae in green and Solanaceae in orange.}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\textbf{Fig. S5} Unipartite bidirectional network with
+asymmetrical effect. The lines with the arrow heads connect the impact
+of foreign pollen (effect size) of each pollen donor species on each
+recipient species. All the arrow heads point to the recipient species of
+the reciprocal interaction. Lines of species that did not have a
+negative impact are not represented. The different nodes and the effect
+of the donor species on the recipient species appear coloured by family:
+Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green). The
+intensity of the effect is represented by the line´s size where a larger
+effect size corresponds to a thicker line and a thinner line to a
+smaller effect size. Species code: BROL: Brassica oleracea, BRRA:
+Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea
+aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia
+integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\textbf{Fig. S6} Graphical representation of the correlation
+matrix of all the traits measured. Positive correlations are displayed
+in blue and negative in red. The intensity, size and colour of the
+circles are proportional to the correlation coefficient from Pearson's
+r.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{\textbf{Fig. S7} Violin plot of the proportion of seeds
+coverted to ovule (\%) for all species with four different
+hand-pollination treatments: apomixis (orange), hand cross pollination
+(green), hand self pollination (blue) and spontaneous selfing (yellow).
+The coloured dots, represent the different values of seed:ovule ratio
+for each treatment.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-17-1.pdf}
+\caption{\textbf{Fig. S8} Grouped effect sizes (95\% confidence
+intervals) of the different families on each focal species. For each
+species, the grouped effect by family is compared with the control
+treatment of hand cross pollination with conspecific pollen. The control
+treatment is represented in yellow and vertically intersected with a
+dashed line through the mean effect size in order to help the visual
+interpretation of the effect sizes. Any value to the left of the
+vertical dashed line represents a negative impact of foreign pollen. The
+different effect sizes and confidence intervals are coloured by family:
+Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).}
+\end{figure}
 

### 2020-09-01 Scripts/Analysis/Old_analysis/Glmm_traits_Hp.R

@@ -1,381 +1,0 @@
-#In this script I'm going to calculate the absolute effect of traits
-#First I have to prepare the data in the desire format for the analysis
-
-#load libraries
-library(reshape2)
-library(lme4)
-library(ggplot2)
-library(fBasics)
-library(lmerTest)
-library(jtools)
-library(ggplot2)
-library(effects)
-library(MASS)
-library(snakecase)
-library(sjPlot)
-library(ggthemes)
-library(ggsci)
-
-#Funtion to plot lm
-ggplotRegression <- function (fit, jit=FALSE) {
-  
-  require(ggplot2)
-  
-  if(jit){
-    fit$model[,1] <- jitter(fit$model[,1])
-    fit$model[,2] <- jitter(fit$model[,2])
-  }
-  
-  ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) +
-    geom_point() +
-    stat_smooth(method = "lm", col = "red") +
-    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                       "Intercept =",signif(fit$coef[[1]],5 ),
-                       " Slope =",signif(fit$coef[[2]], 5),
-                       " P =",signif(anova(fit))))
-}
-#end of function
-
-# Theme for publication
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  library(grid)
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.3)),
-            axis.text=element_text(size = rel(1), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.8, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_line(),
-            panel.grid.minor.y= element_blank()
-      ))
-}
-
-
-#
-##
-###DATA PREPARATION FOR ANALYSES
-##
-#
-
-#load effect sizes
[…]

### 2020-09-01 Scripts/Analysis/Phylogenetic_signal.R

@@ -1,23 +1,16 @@
 library(ape)
 library(phytools)
-pollen_tree=read.tree("Data/Nwk/pollen_tree.nwk")
-#pollen_tree=read.tree("Data/pollen_tree_no_outgroup.nwk")
-#pollen_tree=read.tree("Data/tree_neighbour.nwk")
-png("phylo.png", units="px", width=8000, height=10000, res=2000)
-plot(pollen_tree, font= 3)
-add.scale.bar(x=0, y=1, length = 0.01)
 
-
+#Load data
 pollen_tree=read.tree("Data/Nwk/phylo_all_correct_names.nwk")
 
-png("Figure1.png", units="px", width=12000, height=12000, res=2500)
-plot(pollen_tree, font= 3)
-add.scale.bar(x=0, y=1, length = 0.01)
-
-dev.off()
-
-plot(pollen_tree)
-add.scale.bar(x=0, y=1, length = 0.01)
+#plot phylogenetic tree
+#png("Figure1.png", units="px", width=12000, height=12000, res=2500)
+#plot(pollen_tree, font= 3)
+#add.scale.bar(x=0, y=1, length = 0.01)
+#dev.off()
+#plot(pollen_tree)
+#add.scale.bar(x=0, y=1, length = 0.01)
 #plot(tree_10)
 
 tree_10 <- read.newick("Data/Nwk/pollen_tree_no_outgroup.nwk")

### 2020-09-01 Scripts/Data_preparation/Traits/all_traits.R

@@ -1,8 +1,11 @@
 #In this script I´m going to prepare the full data.frame of traits for analyses
 #First I load an existing table of traits and then I complete it
 
+#load library
+library(stringr)
+
 #load data
-traits_all <- read.csv("Data/tab.csv", sep="", stringsAsFactors = F)
+traits_all <- read.csv("Data/Csv/tab.csv", sep="", stringsAsFactors = F)
 #remove useless columns 
 traits_all <- traits_all[ ,-c(1,2,4,7,10,12)]
 
@@ -16,7 +19,7 @@ traits_all[1:4,2] <- 0
 
 #Load csv with selfing rates (It was done on the script "Analysis_mantel_test)
 
-selfing <- read.csv("Data/selfing_rate.csv")
+selfing <- read.csv("Data/Csv/selfing_rate.csv")
 
 selfing=selfing[,-1]
 colnames(selfing)[2]<- "Selfing_rate"
@@ -30,7 +33,7 @@ traits_all[,3] <- selfing[,2]
 colnames(traits_all)[3]<- "Selfing_rate"
 
 #Add other numerical trais
-morphometry <- read.csv("Data/species_traits.csv")
+morphometry <- read.csv("Data/Csv/species_traits.csv")
 morphometry <- morphometry[, -c(4:15)]
 
 #Now I have to remove the numbers after "_" 
@@ -532,7 +535,7 @@ boxplot(ovary_width_all$um~ovary_width_all$species)
 
 #SOLY
 ovary_length_soly <- subset(ovary, species=="SOLY")
-ovary_length_soly <- subset(ovary_length_soly, measurement=="ovary _ legth")
+ovary_length_soly_1 <- subset(ovary_length_soly, measurement=="ovary_legth_1")
 boxplot(ovary_length_soly$um)
 summary(ovary_length_soly$um)
 ovary_length_soly <- ovary_length_soly[complete.cases(ovary_length_soly),]

### 2020-09-01 Scripts/Project_organization.R

@@ -1,7 +1,0 @@
-#dir.create("Scripts/Species")
-
-#file.rename("Scripts/brassica_oleracea_100.R", "Scripts/Species/brassica_oleracea_100.R")
-
-#file.rename("Scripts/brassica_rapa_100.R", "Scripts/Species/brassica_rapa_100.R")
-
-#file.rename("Scripts/eruca_versicaria_100.R", "Scripts/Species/eruca_versicaria_100.R")

### 2021-01-05 Supplementary_material/Supp_Material.Rmd
Insert table
Edits on figure S7 following the reviewer's advice

--- 2020-04-05 Supplementary_material/Supp_Material.Rmd
@@
 ---
-title: "__Supporting Information:__"
 output:
@@
     fig_caption: yes
-    toc: false
+    toc: no
+  html_document:
+    toc: no
+    df_print: paged
+fontsize: 12pt
+header-includes:
+- \usepackage{setspace}\doublespacing
+- \usepackage{float}
+- \usepackage{caption}
+
 ---
+\captionsetup[figure]{labelformat=empty}
+\captionsetup[table]{labelformat=empty}
+\renewcommand{\figurename}{}
 
-# Recipient and donor characteristics govern hierarchical structure in a heterospecific pollen competition network of co-flowering plants
+# Supporting information:
 
-__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman, Romina Rader
+# Recipient and donor characteristics govern the hierarchical structure of heterospecific pollen competition networks
+
+__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
 
@@
 
-__Table S2.__ Numerical values of all the traits measured for each species.
+__Table S2.__ Trait measurements for all species.
 
-__Table S3.__ Seed set in percentage for hand cross-pollination, hand self-pollination, natural selfing and apomixis for all species.
+__Table S3.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
 
-__Table S4.__ Species x species matrix with the significance of effect “yes” or “no” of the different donors on the seed set of the different recipient species.
+__Table S4.__ Seed:ovule ratio (%) of the different reproductive biology treatments.
 
-__Table S5.__ Estimates, standard error, t-value and P-value of the effect of the different 9 donors on each recipient species.
+__Table S5.__ Summary of the effect from the linear models of the different pollen donors on each recipient species.
 
-__Table S6.__ Number of seeds produced with 100% foreign pollen treatments for the different recipient species.
+__Table S6.__ Estimates, standard error, t-value and _P_-value of the effect of the different 9 donors on each recipient species.
 
-__Table S7.__ Phylogenetic signal and significance for all the different traits
+__Table S7.__ Total number of seeds produced with the 100% foreign pollen treatments.
 
@@
 
-__Figure S1.__ Correlation matrix for all the different traits.
+__Table S9.__ Phylogenetic signal and significance for all the different traits.
 
-__Figure S2.__ Total amount of pollen found for the different treatments.
+__Figure S1__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
 
-__Figure S3.__ Pollen ratios for the different recipient species.
+__Figure S2__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
 
-__Figure S4.__ Pollen ratios for the different recipient species by family.
+__Figure S3__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.
 
-__Figure S5.__ Statistical comparison of pollen ratios by family as pollen donor and recipient.
+__Figure S4__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.
 
-__Figure S6.__ Violin plot of the reproductive biology of the species.
+__Figure S5__. Unipartite bidirectional network with asymmetrical effect.
 
-__Figure S7.__ Grouped effect sizes by family for each recipient species.
+__Figure S6__. Correlation matrix for all the different traits.
+
+__Figure S7__. Species reproductive biology.
+
+__Figure S8__. Grouped effect sizes by family for each recipient species.
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(knitr)
+library(kableExtra)
+Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
+Species <- as.character(Species)
+
+Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")
+Common_names <- as.character(Common_names)
+Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers") 
+Variety <- as.character(Variety)
+Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
+Source <- as.character(Source)
+t <- data.frame(Species, Common_names, Variety, Source)
+colnames(t) <- c("Species", "Common names", "Varieties", "Source")
+kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
+             caption = "\\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.") %>%
+  kable_styling(latex_options = c("repeat_header","striped"), font_size = 10, full_width=T) %>% row_spec(0,bold=TRUE)  %>%
+  column_spec(1,italic =T)
+```
+
+\begin{landscape}
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
+
+dat <- readRDS("Tables/traits_supplementary.rds")
+#Convert to square mm and mm
+dat$stigma_area <- dat$stigma_area/1000000
+dat[,c(7:12)] <- dat[,c(7:12)]/1000
+
+colnames(dat) <- c("Species", "Pollen size $\\mu$m", "Pollen grains per anther", "Ovule number", "Pollen:ovule ratio", "Stigma area $\\mu$m$^{2}$", "Stigma length (mm)", "Stigma width (mm)", "Style length (mm)", "Style width (mm)", "Ovary length (mm)", "Ovary width (mm)", "Selfing rate", "SI index")
+
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Average values of the trait measurements for each plant species.
+Sample sizes are provided on the methods section.
+Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
+The raw data can be found on the online repository provided within this manuscript.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
+```
+
+\end{landscape}
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
+dat <- readRDS("Tables/total_pollen.rds")
+dat <- dat[,-5]
+colnames(dat) <- c("Recipient species", "Donor species", "Recipient pollen grains", "Donor pollen grains")
+
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+library(kableExtra)
+dat <- readRDS("Tables/rep_biology_supplementary.rds")
+
+kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
+The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)
+
+```
+
+\begin{landscape}
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+setwd("~/R_projects/Hp_pollen_experiment")
+d <- read.csv("Data/Csv/Significant_Effect_50_50.csv")
+#Unfortunately this table is not built through clean reproducible code
+#Our collaborators do not work with markdown and some plots were made directly in word
+#I have converted that table to csv and exported in R
+#To reproduce it, the file hp_seed_set_reduction in the folder analysis has everything
+#that is needed to make this table
+
+d <- as.data.frame(d)
+d <- d[,-12]
+d[11,12] <- "$\\bar{X}=67.8$"
+colnames(d) <- c("", "Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena", "$\\%$ of significant effect")
+
+kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment.
+Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
+```
+
+\end{landscape}
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+setwd("~/R_projects/Hp_pollen_experiment")
+d <- readRDS("Data/RData/lm_table.RData")
+#kable(d, format="latex",caption= "\\textbf{Table S6.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
+
+colnames(d) <- c("Estimates", "Standard error", "t-value", "{\\textit{P}}-value")
+
+kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments.
+We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
+The first species on the row names are the pollen recipient species and the second species the pollen donor species.
+Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.") %>%
+  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>%column_spec(1,italic =T)%>% row_spec(0,bold=TRUE)
+```
+
+\clearpage
+
+```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
+setwd("~/R_projects/Hp_pollen_experiment")
+
+library(kableExtra)
+
+#Preparing seed set with 100% pollen
+pein_seed_set_100 <- read.csv("Raw_data/pein_seed_set_100.csv")
+soly_seed_set_100 <- read.csv("Raw_data/soly_seed_set_100.csv")
+some_seed_set_100 <- read.csv("Raw_data/some_seed_set_100.csv")
+caan_seed_set_100 <- read.csv("Raw_data/caan_seed_set_100.csv")
+brol_seed_set_100 <- read.csv("Raw_data/brol_seed_set_100.csv")
+brra_seed_set_100 <- read.csv("Raw_data/brra_seed_set_100.csv")
+sial_seed_set_100 <- read.csv("Raw_data/sial_seed_set_100.csv")
+ersa_seed_set_100 <- read.csv("Raw_data/ersa_seed_set_100.csv")
+ippu_seed_set_100 <- read.csv("Raw_data/ippu_seed_set_100.csv")
+ipaq_seed_set_100 <- read.csv("Raw_data/ipaq_seed_set_100.csv")
+
+all_100 <- rbind(pein_seed_set_100,soly_seed_set_100,some_seed_set_100,caan_seed_set_100,
+      brol_seed_set_100,brra_seed_set_100,sial_seed_set_100,ersa_seed_set_100,
+      ippu_seed_set_100,ipaq_seed_set_100)
+
+all_100_subset <- all_100[grepl("100", all_100$Treatment), , drop = FALSE]
+
+seed_100 <- subset(all_100_subset, all_100_subset$Seed.production>0)
+#str(seed_100)
+seed_100$Species <- as.character(seed_100$Species)
+seed_100$Species[seed_100$Species=="SOLY"] <- "Solnamum lycopersicum"
+seed_100$Species[seed_100$Species=="SOME"] <- "Solnamum melongena"
+seed_100$Species[seed_100$Species=="CAAN"] <- "Capsicum annuum"
+seed_100$Species[seed_100$Species=="BRRA"] <- "Brassica rapa"
+seed_100$Species[seed_100$Species=="SIAL"] <- "Sinapis alba"
+seed_100$Species[seed_100$Species=="ERSA"] <- "Eruca sativa"
+
+seed_100$Treatment <- as.character(seed_100$Treatment)
+
+seed_100$Treatment[seed_100$Treatment=="SIAL 100%"] <- "Sinapis alba"
+seed_100$Treatment[seed_100$Treatment=="ERSA 100%"] <- "Eruca sativa"
+seed_100$Treatment[seed_100$Treatment=="PEIN 100%"] <- "Petunia integrifolia"
+seed_100$Treatment[seed_100$Treatment=="BROL 100%"] <- "Brassica oleracea"
+seed_100$Treatment[seed_100$Treatment=="CAAN 100%"] <- "Capsicum annuum"
+seed_100$Treatment[seed_100$Treatment=="SOLY 100%"] <- "Solanum lycopersicum"
+
+seed_100 <- seed_100[,-c(1,4,6)]
+colnames(seed_100) <- c("Recipient", "Donor (100% foreign pollen)", "Seed number")
+rownames(seed_100) <- NULL
+
+seed_100 <- as.data.frame(seed_100)
+
+kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with the 100\\% foreign pollen treatments (N=900).
+From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
+In this table we show just the treatments that lead to seed production.") %>% kable_styling(font_size = 10,position="left",full_width=F,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>%
+   add_footnote("*            Note: There are some specific cases that we think that hybridization did not occur and that the recipient species were pollen contaminated, like the one of C.
+annuum with S.
+alba with 127 seeds.
+This seems to be the case for 5 other crosses that had very low seed production when they were pollinated with 100% foreign pollen with species of other family members.
+This represents very few isolated cases (0.67% of all the 100% foreign pollen crosses conducted) and we think that our results are not compromised by this fact.
+", notation = "none") %>% column_spec(1,italic =T)%>% column_spec(2,italic =T)
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,  out.width='40%'}
+
+library(kableExtra)
+setwd("~/R_projects/Hp_pollen_experiment")
+load("Data/RData/img_phylo.RData")
+lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
+lambda<- as.numeric(lambda)
+p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
+p <- as.numeric(p)
+trait <- c("Selfing rate", "Pollen size", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "SI index")
+table<- data.frame(lambda,p, trait)
+colnames(table) <- c("Lambda", "P-value", "Traits")
+#kable(table, format="latex",caption= "\\textbf{Table S7.} Phylogenetic signal and significance for all the different traits.", digits = 2)
+
+kable(table, format="latex",escape=F,digits=2, longtable = F,booktabs = T,linesep = "\\addlinespace", caption= "\\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.") %>% kable_styling(font_size = 10, full_width=F,latex_options = c("striped")) %>% row_spec(0,bold=TRUE)
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
+library(kableExtra)
+setwd("~/R_projects/Hp_pollen_experiment")
+
+load("Data/RData/Table_s4.RData")
+
+Correlation <- c(selfing_pro[6], pollen_size_pro[6], mean_pollen_anther_pro[6], mean_ovules_pro[6], pollen_ovule_ratio_pro[6], stigma_area_pro[6], stigma_length_pro[6], stigma_width_pro[6], style_length_pro[6], style_width_pro[6], ovary_width_pro[6], ovary_length_pro[6], si_index_pro[6],selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6],selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
+
+Correlation<- as.numeric(Correlation)
+
+Sum_squares <- c(selfing_pro[3], pollen_size_pro[3], mean_pollen_anther_pro[3], mean_ovules_pro[3], pollen_ovule_ratio_pro[3], stigma_area_pro[3], stigma_length_pro[3], stigma_width_pro[3], style_length_pro[3], style_width_pro[3], ovary_width_pro[3], ovary_length_pro[3],si_index_pro[3], selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3], selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
+
+Sum_squares<- as.numeric(Sum_squares)
+
+Significance <- c(selfing_pro[13], pollen_size_pro[13], mean_pollen_anther_pro[13], mean_ovules_pro[13], pollen_ovule_ratio_pro[13], stigma_area_pro[13], stigma_length_pro[13], stigma_width_pro[13], style_length_pro[13], style_width_pro[13], ovary_width_pro[13], ovary_length_pro[13],si_index_pro[13],selfing_pro_sol[13], pollen_size_pro_sol[13], mean_pollen_anther_pro_sol[13], mean_ovules_pro_sol[13], pollen_ovule_ratio_pro_sol[13], stigma_area_pro_sol[13], stigma_length_pro_sol[13], stigma_width_pro_sol[13], style_length_pro_sol[13], style_width_pro_sol[13], ovary_width_pro_sol[13], ovary_length_pro_sol[13],si_index_pro_sol[13], selfing_pro_bra[13], pollen_size_pro_bra[13], mean_pollen_anther_pro_bra[13], mean_ovules_pro_bra[13], pollen_ovule_ratio_pro_bra[13], stigma_area_pro_bra[13], stigma_length_pro_bra[13], stigma_width_pro_bra[13], style_length_pro_bra[13], style_width_pro_bra[13], ovary_width_pro_bra[13], ovary_length_pro_bra[13],si_index_pro_bra[13])
+
+Significance <- as.numeric(Significance)
+
+Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")
+
+Family <- c(rep("All",13),rep("Solanaceae",13),rep("Brassicaceae",13))
+
+table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
+
+colnames(table) <- c("Correlation (r)","Sum of squares", "P-value", "Traits", "Family")
+
+kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S9.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.") %>%
+  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>% row_spec(0,bold=TRUE)
+
+```
+
+\clearpage
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig.
+S1** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
+For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma.
+For each pair of species on the x-axis, the first species is the recipient species, and the second, the donor species."}
+
+library(ggplot2)
+
+setwd("~/R_projects/Hp_pollen_experiment")
+total_pollen <- read.csv("Data/Csv/total_pollen.csv")
+ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
+  geom_bar(stat='identity', position='dodge')+theme_light()+ 
+  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
+  scale_fill_manual(values=c("#999999","#779799"),labels = c("Conspecific pollen","Heterospecific pollen"))+labs(x = "",y="Pollen grains per stigma")
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig.
+S2** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
+These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments.
+We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these treatments.
+The proportion of conspecific and heterospecific pollen are shown in grey and light blue respectively.
+For each pair of species on the y-axis, the first species is the pollen recipient and the second the pollen donor.
+The vertical black line represents 50% pollen of both donor and recipient."}
+
+par(mar=c(2,13,2,4),xpd=F)
+par(mfrow=c(3,1))
+setwd("~/R_projects/Hp_pollen_experiment")
+ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
+coul = c("#999999","#779799")
+barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E.
+sativa-I.
+purpurea", "B.
+oleracea-I.
+purpurea","B.
+rapa-I.
+purpurea", "S.
+alba-I.
+aquatica", "S.
+alba-S.
+melongena", "E.
+sativa-P.
+integrifolia", "B.
+rapa-S.
+lycopersicum", "B.
+oleracea-C.
+annuum"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
+text(8.3,6.8,"A) Brassicaceae")
+ratio_con <-readRDS("Data/RData/ratio_con.RData")
+barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I.
+purpurea-S.
+melongena","I.
+aquatica-C.
+annuum","I.
+purpurea-E.
+sativa","I.
+aquatica-S.
+alba"))
+abline(v=50,col="black")
+legend(-1,-0.5,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
+text(9,3.5,"B) Convolvulaceae")
+
+ratio_sol <-readRDS("Data/RData/ratio_sol.RData")
+barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
+annuum-I.
+purpurea", "S.
+melongena-I.
+aquatica", "P.
+integrifolia-I.
+aquatica", "S.
+lycopersicum-I aquatica","S.
+melongena-E.
+sativa", "P.
+integrifolia-E.
+sativa", "C.
+annuum-S.
+alba", "S.
+lycopersicum-B.
+rapa"))
+abline(v=50,col="black")
+legend(-1,-0.1,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
+text(6.8,6.8,"C) Solanaceae")
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig.
+S3** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
+We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments.
+Finally, we grouped by family these treatments in order to see general tendencies across families as pollen donor and as pollen recipient.
+Pollen ratios were considered as the number of conspecific or heterospecific pollen grains divided by the total number of pollen grains per stigma.
+On the y-axis, the first family on each pair of plant families is the recipient one, and the second, the family of the donor.
+The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}
+
+par(mar=c(2,8.7,2,2),xpd=F)
+setwd("~/R_projects/Hp_pollen_experiment")
+data_percentage <-readRDS("Data/RData/per.RData")
+data_percentage=as.matrix(data_percentage)
+coul = c("#999999","#779799")
+barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=0.85,cex.names=0.65,names=c("Brassicaceae-Convolvulaceae",
+ "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
+legend(0,-0.5,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul, cex = 0.65)
+abline(v=50,col="black")
+
+#lines(c(0,10),50,col="red")
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
+S4** Pollen ratios comparisons between the different pollen recipient families.
+The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
+These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen).
+Brassicacea family is coloured in blue, Convolvulaceae in green and Solanaceae in orange."}
+
+#Here I try to compare the different proportions of pollen between the different groups
+#I use Tukey method
+
+library(lme4)
+library(emmeans)
+library(reshape2)
+library(multcompView)
+library(lsmeans)
+library(multcomp)
+library(ggplot2)
+library(DHARMa)
+setwd("~/R_projects/Hp_pollen_experiment")
+
+total_pollen <- read.csv("Data/Csv/total_pollen.csv")
+
+total_pollen=total_pollen[,-1]
+colnames(total_pollen)[3] <- "pollen"
+#head(total_pollen)
+
+# Dividing by focal pollen and non focal pollen
+# In order to compare pollen as donor and recipient per family 
+pollen_foc <- subset(total_pollen, variable=="focal_pollen")
+pollen_non <- subset(total_pollen, variable=="non_focal_pollen")
+
+total  <- as.numeric(pollen_foc$pollen) + as.numeric(pollen_non$pollen)
+pollen_non$total_pollen  <- total
+pollen_non$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
+pollen_non$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
+                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
+                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
+                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
+
+pollen_non <- pollen_non[,-c(1,2)]
+colnames(pollen_non)[1] <-"hp_pollen"
+pollen_non$hp_ratio <- as.numeric(pollen_non$hp_pollen)/as.numeric(pollen_non$total_pollen)
+#hist(pollen_non$hp_ratio)
+
+pollen_foc$total_pollen  <- total
+pollen_foc$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
+pollen_foc$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
+                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
+                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
+                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
+
+pollen_foc <- pollen_foc[,-c(1,2)]
+colnames(pollen_foc)[1] <-"hp_pollen"
+pollen_foc$hp_ratio <- as.numeric(pollen_foc$hp_pollen)/as.numeric(pollen_foc$total_pollen)
+#hist(pollen_foc$hp_ratio)
+
+#Analyse data and plot it
+
+junk.glmer = lm(hp_ratio ~ fam_non, data = pollen_non)
+#plot(junk.glmer)
+#goodness of fit of the model
+#testDispersion(junk.glmer)
+#simulationOutput <- simulateResiduals(fittedModel = junk.glmer, plot = T)
+
+#lsm = lsmeans(junk.glmer, "fam_non", type = "response")
+#pairs(lsm)
+#CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
+
+#ggplot(CLD,aes(x= fam_non,y= lsmean,
+#label = .group)) +theme_minimal()+
+#geom_point(shape  = 15,size   = 4) +ggtitle("B) Comparison of ratios as donor")+
+#geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
+#width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+
+#geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black")
+
+#Analyse data and plot it
+junk.glmer = lm(hp_ratio ~ fam_foc, data = pollen_foc)
+lsm = lsmeans(junk.glmer, "fam_foc", type = "response")
+#pairs(lsm)
+CLD <-  multcomp::cld(lsm,alpha=0.05,adjust="tukey")
+
+#theme
+theme_ms <- function(base_size=12, base_family="Helvetica") {
+  library(grid)
+  (theme_bw(base_size = base_size, base_family = base_family)+
+      theme(text=element_text(color="black"),
+            axis.title=element_text( size = rel(1.3)),
+            axis.text=element_text(size = rel(1), color = "black"),
+            legend.title=element_text(face="bold"),
+            legend.text=element_text(),
+            legend.background=element_rect(fill="transparent"),
+            legend.key.size = unit(0.8, 'lines'),
+            panel.border=element_rect(color="black",size=1),
+            panel.grid.minor.x =element_line(),
+            panel.grid.minor.y= element_blank()
+      ))
+}
+
+ggplot(CLD,aes(x= fam_foc,y= lsmean,
+               label = .group)) +theme_ms()+
+  geom_point(data = CLD, aes(x = fam_foc, y = lsmean, color = fam_foc),shape  = 15,size   = 4) +
+scale_color_manual(name = "Families",values = c("Convolvulaceae" = "#009E73", "Solanaceae" = "#D55E00", "Brassicaceae" = "#0072B2"))+ggtitle("")+
+  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = fam_foc),
+                width =  0.2,size =  0.9)+ylab("Least square mean")+xlab("Families")+
+  geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(legend.position = "none")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig.
+S5** Unipartite bidirectional network with asymmetrical effect.
+The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species.
+All the arrow heads point to the recipient species of the reciprocal interaction.
+Lines of species that did not have a negative impact are not represented.
+The different nodes and the effect of the donor species on the recipient species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).
+The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size.
+Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}
+
+library(statnet)
+library(reshape2)
+library(sna)
+library(igraph)
+setwd("~/R_projects/Hp_pollen_experiment")
+
+#######################################
+############ Data preparataion ########
+#######################################
+
+#In this script I'm going to plot the transitivity of the effect oh HP pollen with effect sizes
+effect <- readRDS("Data/RData/matrix_effect_size.RData")
+#Now I convert the few values over 0 to maximum 0 (control)
+effect[effect>0]<-0
+#absolute values so less confusing without negative values
+#So now greater values involve greater effect
+#(opposite way in comparison with negative values as before)
+effect=abs(effect)
+#UNIPARTITE DOUBLE ASSYMETRICAL EFFECT
+G <- graph.adjacency(t(effect),weighted=TRUE,diag=FALSE)
+#plot(G)
+E <- t(apply(get.edgelist(G),1,sort))
+E(G)$curved <- 0
+E(G)[duplicated(E) | duplicated(E,fromLast =TRUE)]$curved <- 0.2
+plot(G, edge.width=E(G)$weight/0.5,  vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),
+              "#D55E00","#0072B2", rep("#D55E00",2)),edge.arrow.size=0.8,edge.color=adjustcolor(c(rep("#0072B2",8),rep("#0072B2",8), rep("#D55E00",7), 
+              rep("#0072B2",9),rep("#009E73",7),rep("#009E73",9),rep("#D55E00",7),rep("#0072B2",8), rep("#D55E00",8), rep("#D55E00",7)), alpha.f = .5))
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig.
+S6** Graphical representation of the correlation matrix of all the traits measured.
+Positive correlations are displayed in blue and negative in red.
+The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
+#install.packages("corrplot")
+library(corrplot)
+setwd("~/R_projects/Hp_pollen_experiment")
+#Example
+#I'm going to try to show our traits on this way
+#M <- cor(mtcars)
+#corrplot(M, method = "circle")
+#We can kill two birds with one stone, showing the correlation and all the traits
+traits_all <- read.csv("Data/Csv/traits_all.csv")
+si_index <- readRDS("Data/RData/si_index.RData")
+traits_all$si_index <- si_index
+traits_all=traits_all[,-c(1,2)]
+traits_all=traits_all[,-c(1,7,11)]
+#Change order of ovary width length I rename below in row and colname
+a<-traits_all[,11]
+b<-traits_all[,12]
+traits_all[,11] <-b
+traits_all[,12]<- a
+traits_all<- cor(traits_all)
+
+rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen grains/anther", "Number of ovules", "Pollen-ovule ratio",
+                         "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
+                         "Ovary length", "Ovary width", "SI index")
+
+colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen grains/anther", "Number of ovules", "Pollen-ovule ratio",
+                "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
+                "Ovary length", "Ovary width", "SI index")
+
+#corrplot(traits_all, method = "circle")
+#corrplot(traits_all, type = "upper")
+par(mar=c(0,4.1,4.1,2.1))
+corrplot(traits_all, type = "lower", tl.cex = 0.8, cl.cex = 0.8, tl.col = "black", tl.srt = 45)
+
+#Add Compatibility index!
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6.5,fig.width=12,  fig.cap="**Fig.
+S7** Violin plot of the proportion of seeds coverted to ovule (%) for all species with four different hand-pollination treatments: apomixis (orange), hand cross pollination (green), hand self pollination (blue) and spontaneous selfing (yellow).
+The species are grouped by family in three different panels that are named with the corresponding family names (Brassicaceae, Convolvulaceae and Solanaceae).
+The coloured dots, represent the different values of seed:ovule ratio for each treatment."}
+
+setwd("~/R_projects/Hp_pollen_experiment")
+#Script to plot the reproductive biology tests
+#load libraries
+library(ggplot2)
+#install.packages("devtools")
+library(devtools)
+#install_github("easyGgplot2", "kassambara")
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+brol <- read.csv("Raw_data/brol_seed_set_final.csv")
+brra <- read.csv("Raw_data/brra_seed_set_final.csv")
+ersa <- read.csv("Raw_data/ersa_seed_set_final.csv")
+sial <- read.csv("Raw_data/sial_seed_set_final.csv")
+ipaq <- read.csv("Raw_data/ipaq_seed_set_final.csv")
+ippu <- read.csv("Raw_data/ippu_seed_set_final.csv")
+caan <- read.csv("Raw_data/caan_seed_set_final.csv")
+pein <- read.csv("Raw_data/pein_seed_set_final.csv")
+soly <- read.csv("Raw_data/soly_seed_set_final.csv")
+some <- read.csv("Raw_data/some_seed_set_final.csv")
+#loading traits to divide by number of ovules the seed set 
+traits <- read.csv("Data/Csv/traits_scinames.csv")
+
+brol_r <- subset(brol, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="FC")
+brol_r$Seed_set <- brol_r$Seed.production/traits[1,8]*100
+brra_r <- subset(brra, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+brra_r$Seed_set <- brra_r$Seed.production/traits[2,8]*100
+ersa_r <- subset(ersa, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+ersa_r$Seed_set <- ersa_r$Seed.production/traits[4,8]*100
+sial_r <- subset(sial, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower Control")
+sial_r$Seed_set <- sial_r$Seed.production/traits[8,8]*100
+ipaq_r <- subset(ipaq, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ipaq_r$Seed_set <- ipaq_r$Seed.production/traits[5,8]*100
+ippu_r <- subset(ippu, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+ippu_r$Seed_set <- ippu_r$Seed.production/traits[6,8]*100
+caan_r <- subset(caan, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+caan_r$Seed_set <- caan_r$Seed.production/traits[3,8]*100
+pein_r <- subset(pein, Treatment=="CROSS"|Treatment=="SELF"|Treatment=="CONTROL"|Treatment=="FLOWER CONTROL")
+pein_r$Seed_set <- pein_r$Seed.production/traits[7,8]*100
+soly_r <- subset(soly, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+soly_r$Seed_set <- soly_r$Seed.production/traits[9,8]*100
+some_r <- subset(some, Treatment=="Cross"|Treatment=="Self"|Treatment=="Control"|Treatment=="Flower control")
+some_r$Seed_set <- some_r$Seed.production/traits[10,8]*100
+
+d <- rbind(brol_r,brra_r,ersa_r,sial_r,ipaq_r,ippu_r,caan_r,pein_r,soly_r,some_r)
+d$Seed_set[d$Seed_set>100]<-100
+
+#levels(d$Treatment)
+d$Treatment=as.character(d$Treatment)
+d$Treatment[d$Treatment=="Cross"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="CROSS"]<-"Hand cross-pollination"
+d$Treatment[d$Treatment=="Self"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="SELF"]<-"Hand self-pollination"
+d$Treatment[d$Treatment=="Control"]<-"Apomixis"
+d$Treatment[d$Treatment=="CONTROL"]<-"Apomixis"
+d$Treatment[d$Treatment=="FC"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower control"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="FLOWER CONTROL"]<-"Spontaneous selfing"
+d$Treatment[d$Treatment=="Flower Control"]<-"Spontaneous selfing"
+
+d$Family=as.character(d$Family)
+d$Family[d$Species=="BROL"]<-"Brassicaceae"
+d$Family[d$Species=="BRRA"]<-"Brassicaceae"
+d$Family[d$Species=="ERSA"]<-"Brassicaceae"
+d$Family[d$Species=="SIAL"]<-"Brassicaceae"
+d$Family[d$Species=="IPPU"]<-"Convolvulaceae"
+d$Family[d$Species=="IPAQ"]<-"Convolvulaceae"
+d$Family[d$Species=="SOME"]<-"Solanaceae"
+d$Family[d$Species=="SOLY"]<-"Solanaceae"
+d$Family[d$Species=="PEIN"]<-"Solanaceae"
+d$Family[d$Species=="CAAN"]<-"Solanaceae"
+
+d$Species=as.character(d$Species)
+d$Species[d$Species=="BROL"]<-"B. oleracea"
+d$Species[d$Species=="BRRA"]<-"B. rapa"
+d$Species[d$Species=="SIAL"]<-"S. alba"
+d$Species[d$Species=="ERSA"]<-"E. sativa"
+d$Species[d$Species=="IPPU"]<-"I. purpurea"
+d$Species[d$Species=="IPAQ"]<-"I. aquatica"
+d$Species[d$Species=="SOLY"]<-"S. lycopersicum"
+d$Species[d$Species=="SOME"]<-"S. melongena"
+d$Species[d$Species=="PEIN"]<-"P. integrifolia"
+d$Species[d$Species=="CAAN"]<-"C. annuum"
+
+cbPalette <- c( "#56B4E9","#E69F00", "#999999", "#009E73")
+
+ggplot(d, aes(x=Species, y=Seed_set, fill=Treatment)) + 
+  geom_violin(scale = "width",draw_quantiles = c(0.5))+
+  geom_dotplot(binaxis='y', 
+               dotsize=0.15,stackdir='center',position = position_jitterdodge(jitter.width = 0.01))+ facet_grid(. ~ Family,scales="free", space="free")+
+  theme_bw()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),
+                                                                                                                                       axis.text.x = element_text(face = "italic"),strip.background = element_rect(color = "black", size = 0.5))
+
+```
+
+\clearpage
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7, fig.cap="**Fig.
+S8** Grouped effect sizes (95% confidence intervals) of the different families on each focal species.
+For each species, the grouped effect by family is compared with the control treatment of hand cross pollination with conspecific pollen.
+The control treatment is represented in yellow and vertically intersected with a dashed line through the mean effect size in order to help the visual interpretation of the effect sizes.
+Any value to the left of the vertical dashed line represents a negative impact of foreign pollen.
+The different effect sizes and confidence intervals are coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green)."}
+
+library(effsize)
+library(dplyr)
+library(ggplot2)
+library(ggpubr)
+library(cowplot)
+library(gridExtra)
+library(egg)
+library(magrittr)
+library(multipanelfigure)
+library(grid)
+
+setwd("~/R_projects/Hp_pollen_experiment")
+load("Data/RData/some_effect_size_family.RData")
+
+pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/soly_effect_size_family.RData")
+
+pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/sial_effect_size_family.RData")
+
+p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/pein_effect_size_family.RData")
+
+p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/ippu_effect_size_family.RData")
+
+p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/ipaq_effect_size_family.RData")
+
+p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/ersa_effect_size_family.RData")
+
+p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/caan_effect_size_family.RData")
+
+p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/brra_effect_size_family.RData")
+
+p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+load("Data/RData/brol_effect_size_family.RData")
+
+p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
+  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
+ymax = Upper,color=factor(Family)))+
+  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
+  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
+  geom_hline(yintercept=0, linetype="dashed", color = "black")
+
+ #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
+grid.newpage()
+ grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
+```

### 2021-01-06 Figures_main_text/Figure2_effect_sizes_per_spp.Rmd

---
output: pdf_document
---
```{r, echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE,fig.margin = TRUE,cache=FALSE,fig.height=9,fig.width=7}

library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)

#Load data
setwd("~/R_projects/Hp_pollen_experiment/Data/RData")
load("all_effect_size.RData")

#save plot
#png("Figure3.png", width = 9000, height = 11000, res = 1400)

#BROL
load("brol_effect_size.RData")
p1<- ggplot(brol_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title=element_text(size=10),title = element_text(vjust=2),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,aes(color=factor(Species_1))) +geom_errorbar(alpha=c(0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5,0.5),size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",3),"#E69F00"))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("A)",italic(' B. oleracea'))))

#BRRA
load("brra_effect_size.RData")
pp2<- ggplot(brra_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",2),"#E69F00","#0072B2"))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+annotate("text", x=10, y=-6, label= "")+ggtitle(substitute(paste("B)",italic(' B. rapa'))))

#ERSA
load("ersa_effect_size.RData")
p3<- ggplot(ersa_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",1),"#E69F00", rep("#0072B2",3)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')))+ggtitle(substitute(paste("C)",italic(' E. sativa'))))

#SIAL
load("sial_effect_size.RData")
p4<- ggplot(sial_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2),"#E69F00", rep("#0072B2",3)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("D)",italic(' S. alba'))))

#IPAQ
load("ipaq_effect_size.RData")
p5<- ggplot(ipaq_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic','italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4), rep("#009E73",1),"#E69F00", rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("E)",italic(' I. aquatica'))))

#IPPU
load("ippu_effect_size.RData")
p6<- ggplot(ippu_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+
  theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",4),"#E69F00", rep("#009E73",1), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("F)",italic(' I. purpurea'))))

#CAAN
load("caan_effect_size.RData")
p7<- ggplot(caan_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0.3,0,1), "cm"),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",3),"#E69F00", rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("G)",italic(' C. annuum'))))

#PEIN
load("pein_effect_size.RData")
p8<- ggplot(pein_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_blank(),plot.margin = unit(c(0,0,0,0), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c(rep("#D55E00",2),"#E69F00","#D55E00", rep("#009E73",2), rep("#0072B2",4)))+
  xlab("") + ylab("") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("H)",italic(' P. integrifolia'))))

#SOLY
load("soly_effect_size.RData")
p9<- ggplot(soly_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),axis.text.y = element_text(size=5,face = c('italic', 'italic', 'italic', 'italic', 'italic','italic', 'italic', 'italic', 'italic', 'italic')),plot.margin = unit(c(0,0.3,0,1), "cm"))+ geom_point(alpha=c(1,1,1,1,1,1,1,1,1,1),size=1.5,show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(alpha=0.5,size=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c(rep("#D55E00",1),"#E69F00",rep("#D55E00",2), rep("#009E73",2), rep("#0072B2",4)))+scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("I)",italic(' S. lycopersicum'))))

#SOME
load("some_effect_size.RData")

p10<- ggplot(some_effect_size, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(plot.title = element_text(size = 10),plot.margin = unit(c(0,0,0,0), "cm"),axis.text.y = element_blank())+ geom_point(size=1.5,alpha=c(1,1,1,1,1,1,1,1,1,1),show.legend = FALSE,aes(color=factor(Species_1))) +geom_errorbar(size=0.6,alpha=0.4,show.legend=FALSE, aes(x = Species_1, ymin = Lower, ymax = Upper,color=factor(Species_1)))+scale_color_manual("Species_1",values=c("#E69F00",rep("#D55E00",3), rep("#009E73",2), rep("#0072B2",4)))+
  scale_fill_manual("Species_1",values=c("#D55E00", "#009E73", "#0072B2"))+
  xlab("") + ylab("Hedges' g") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
  geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena'))))

sp_legend <- readRDS("sp_legend.RData")
p11<- ggplot(sp_legend, aes(Species_1,Cohen_d, size=10)) + theme_bw(base_size=10)+theme(legend.direction="horizontal",legend.title = element_blank(),plot.margin = unit(c(0,0,0,0.3), "cm"),axis.text.y = element_blank())+ geom_point(size=2,alpha=c(1,1,1,1,1,1,1,1,1,1),aes(color=factor(Family))) +geom_errorbar(size=0.6,alpha=0.5, aes(x = Family, ymin = Lower, ymax = Upper,color=factor(Family)))+scale_color_manual("Family",values=c("#0072B2","#009E73","#E69F00","#D55E00"))+ scale_fill_manual("Family",values=c("#D55E00", "#009E73", "#0072B2","#0072B2"))+
  xlab("") + ylab("Hedges' g") +geom_hline(yintercept=0, linetype="dashed", color = "black")+ggtitle(substitute(paste("J)",italic(' S. melongena')))) 
 #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
grid.newpage()

g_legend<-function(a.gplot){
  tmp <- ggplot_gtable(ggplot_build(a.gplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)}

mylegend<-g_legend(p11)

 grid.draw(arrangeGrob(cbind(ggplotGrob(p1+theme(legend.position="none")),ggplotGrob(pp2+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p3+theme(legend.position="none")),ggplotGrob(p4+theme(legend.position="none")),size="last"),cbind(ggplotGrob(p5+theme(legend.position="none")),ggplotGrob(p6+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p7+theme(legend.position="none")),ggplotGrob(p8+theme(legend.position="none")), size="last"),cbind(ggplotGrob(p9+theme(legend.position="none")),ggplotGrob(p10+theme(legend.position="none")),size="last"),mylegend,nrow=6))
#mylegend
 dev.off()

```

### 2021-01-06 Supplementary_material/Supp_Material.tex

--- 2020-04-05 Supplementary_material/Supp_Material.tex
@@
 
-\textbf{Figure S1.} Correlation matrix for all the different traits.
+\textbf{Table S9.} Phylogenetic signal and significance for all the
+different traits.
 
-\textbf{Figure S2.} Total amount of pollen found for the different
-treatments.
+\textbf{Figure S1}. Average number of pollen grains of recipient and
+donor species per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Figure S3.} Pollen ratios for the different recipient species.
+\textbf{Figure S2}. Average proportion (\%) of conspecific and
+heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
 
-\textbf{Figure S4.} Pollen ratios for the different recipient species by
-family.
+\textbf{Figure S3}. Average proportion (\%) of heterospecific and
+conspecific pollen per stigma and family with the 50:50 mix CP:HP
+pollen.
 
-\textbf{Figure S5.} Statistical comparison of pollen ratios by family as
-pollen donor and recipient.
+\textbf{Figure S4}. Statistical comparison of the percentage of
+heterospecific pollen with the 50:50 pollen mix by family.
 
-\textbf{Figure S6.} Violin plot of the reproductive biology of the
+\textbf{Figure S5}. Unipartite bidirectional network with asymmetrical
+effect.
+
+\textbf{Figure S6}. Correlation matrix for all the different traits.
+
+\textbf{Figure S7}. Species reproductive biology.
+
+\textbf{Figure S8}. Grouped effect sizes by family for each recipient
 species.
 
-Figure S7. Grouped effect sizes by family for each recipient species.
+\newpage
+
+\begingroup\fontsize{10}{12}\selectfont
+
+\begin{longtabu} to \linewidth {>{}l>{\raggedright}X>{\raggedright}X>{\raggedright}X}
+\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
+\toprule
+\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
+\midrule
+\endfirsthead
+\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
+\toprule
+\textbf{Species} & \textbf{Common names} & \textbf{Varieties} & \textbf{Source}\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+\em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{Wild cabbage} & \cellcolor{gray!6}{Capitata} & \cellcolor{gray!6}{https://www.mrfothergills.com.au/}\\
+\addlinespace
+\em{Brassica rapa} & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
+\addlinespace
+\em{\cellcolor{gray!6}{Eruca sativa}} & \cellcolor{gray!6}{Rocket} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{https://www.mrfothergills.com.au/}\\
+\addlinespace
+\em{Sinapis alba} & White mustard &  & https://www.mrfothergills.com.au/\\
+\addlinespace
+\em{\cellcolor{gray!6}{Ipomoea aquatica}} & \cellcolor{gray!6}{Water spinach} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{https://www.theseedcollection.com.au/}\\
+\addlinespace
+\em{Ipomoea purpurea} & Morning glory &  & http://www.shaman-australis.com.au\\
+\addlinespace
+\em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{Capsicum} & \cellcolor{gray!6}{California Wonder} & \cellcolor{gray!6}{https://www.edenseeds.com.au}\\
+\addlinespace
+\em{Petunia integrifolia} & Petunia &  & https://www.dianeseeds.com/\\
+\addlinespace
+\em{\cellcolor{gray!6}{Solanum lycopersicum}} & \cellcolor{gray!6}{Tomato} & \cellcolor{gray!6}{Tommy Toe} & \cellcolor{gray!6}{https://www.mrfothergills.com.au/}\\
+\addlinespace
+\em{Solanum melongena} & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
+\end{longtabu}
+
+\endgroup{}
+
+\begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Average values of the trait measurements for each plant species.
+Sample sizes are provided on the methods section.
+Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
+The raw data can be found on the online repository provided within this manuscript.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
+\midrule
+\em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{27.72} & \cellcolor{gray!6}{42033} & \cellcolor{gray!6}{29} & \cellcolor{gray!6}{8696.48} & \cellcolor{gray!6}{0.62} & \cellcolor{gray!6}{0.53} & \cellcolor{gray!6}{0.88} & \cellcolor{gray!6}{2.32} & \cellcolor{gray!6}{0.65} & \cellcolor{gray!6}{5.93} & \cellcolor{gray!6}{1.11} & \cellcolor{gray!6}{0.0} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{Brassica rapa} & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{32.46} & \cellcolor{gray!6}{30761} & \cellcolor{gray!6}{241} & \cellcolor{gray!6}{765.83} & \cellcolor{gray!6}{1.06} & \cellcolor{gray!6}{0.72} & \cellcolor{gray!6}{1.18} & \cellcolor{gray!6}{3.24} & \cellcolor{gray!6}{1.06} & \cellcolor{gray!6}{3.15} & \cellcolor{gray!6}{5.80} & \cellcolor{gray!6}{0.8} & \cellcolor{gray!6}{0.64}\\
+\addlinespace
+\em{Eruca versicaria} & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
+\addlinespace
+\em{\cellcolor{gray!6}{Ipomoea aquatica}} & \cellcolor{gray!6}{70.10} & \cellcolor{gray!6}{858} & \cellcolor{gray!6}{4} & \cellcolor{gray!6}{1072.50} & \cellcolor{gray!6}{3.26} & \cellcolor{gray!6}{1.43} & \cellcolor{gray!6}{2.25} & \cellcolor{gray!6}{19.44} & \cellcolor{gray!6}{0.45} & \cellcolor{gray!6}{2.38} & \cellcolor{gray!6}{1.42} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.75}\\
+\addlinespace
+\em{Ipomoea purpurea} & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
+\addlinespace
+\em{\cellcolor{gray!6}{Petunia integrifolia}} & \cellcolor{gray!6}{24.74} & \cellcolor{gray!6}{34657} & \cellcolor{gray!6}{220} & \cellcolor{gray!6}{787.66} & \cellcolor{gray!6}{1.17} & \cellcolor{gray!6}{0.80} & \cellcolor{gray!6}{1.32} & \cellcolor{gray!6}{14.65} & \cellcolor{gray!6}{0.45} & \cellcolor{gray!6}{3.13} & \cellcolor{gray!6}{1.77} & \cellcolor{gray!6}{0.9} & \cellcolor{gray!6}{0.26}\\
+\addlinespace
+\em{Sinapis alba} & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
+\addlinespace
+\em{\cellcolor{gray!6}{Solanum lycopersicum}} & \cellcolor{gray!6}{22.00} & \cellcolor{gray!6}{28915} & \cellcolor{gray!6}{92} & \cellcolor{gray!6}{1885.76} & \cellcolor{gray!6}{0.09} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{6.47} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{1.16} & \cellcolor{gray!6}{1.13} & \cellcolor{gray!6}{0.7} & \cellcolor{gray!6}{0.48}\\
+\addlinespace
+\em{Solanum melongena} & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\end{landscape}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-3}\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{}l>{}l>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Recipient species} & \textbf{Donor species} & \textbf{Recipient pollen grains} & \textbf{Donor pollen grains}\\
+\midrule
+\em{\cellcolor{gray!6}{C. annuum}} & \em{\cellcolor{gray!6}{I. purpurea}} & \cellcolor{gray!6}{258} & \cellcolor{gray!6}{11}\\
+\addlinespace
+\em{E. sativa} & \em{I. purpurea} & 1308 & 8\\
+\addlinespace
+\em{\cellcolor{gray!6}{B. oleracea}} & \em{\cellcolor{gray!6}{I. purpurea}} & \cellcolor{gray!6}{90} & \cellcolor{gray!6}{20}\\
+\addlinespace
+\em{B. rapa} & \em{I. purpurea} & 193 & 2\\
+\addlinespace
+\em{\cellcolor{gray!6}{S. melongena}} & \em{\cellcolor{gray!6}{I. aquatica}} & \cellcolor{gray!6}{64} & \cellcolor{gray!6}{26}\\
+\addlinespace
+\em{P. integrifolia} & \em{I. aquatica} & 23 & 20\\
+\addlinespace
+\em{\cellcolor{gray!6}{S. lycopersicum}} & \em{\cellcolor{gray!6}{I. aquatica}} & \cellcolor{gray!6}{56} & \cellcolor{gray!6}{10}\\
+\addlinespace
+\em{S. alba} & \em{I. aquatica} & 1617 & 19\\
+\addlinespace
+\em{\cellcolor{gray!6}{I. purpurea}} & \em{\cellcolor{gray!6}{S. melongena}} & \cellcolor{gray!6}{138} & \cellcolor{gray!6}{362}\\
+\addlinespace
+\em{S. alba} & \em{S. melongena} & 3054 & 1096\\
+\addlinespace
+\em{\cellcolor{gray!6}{E. sativa}} & \em{\cellcolor{gray!6}{P. integrifolia}} & \cellcolor{gray!6}{621} & \cellcolor{gray!6}{321}\\
+\addlinespace
+\em{B. rapa} & \em{S. lycopersicum} & 1114 & 246\\
+\addlinespace
+\em{\cellcolor{gray!6}{I. aquatica}} & \em{\cellcolor{gray!6}{C. annuum}} & \cellcolor{gray!6}{35} & \cellcolor{gray!6}{85}\\
+\addlinespace
+\em{B. oleracea} & \em{C. annuum} & 281 & 209\\
+\addlinespace
+\em{\cellcolor{gray!6}{I. purpurea}} & \em{\cellcolor{gray!6}{E. sativa}} & \cellcolor{gray!6}{27} & \cellcolor{gray!6}{216}\\
+\addlinespace
+\em{S. melongena} & \em{E. sativa} & 1837 & 2231\\
+\addlinespace
+\em{\cellcolor{gray!6}{P. integrifolia}} & \em{\cellcolor{gray!6}{B. oleracea}} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{376}\\
+\addlinespace
+\em{I. aquatica} & \em{S. alba} & 42 & 170\\
+\addlinespace
+\em{\cellcolor{gray!6}{C. annuum}} & \em{\cellcolor{gray!6}{S. alba}} & \cellcolor{gray!6}{304} & \cellcolor{gray!6}{450}\\
+\addlinespace
+\em{S. lycopersicum} & \em{B. rapa} & 164 & 208\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\newpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
+The values provided are the seed:ovule ratios in percentage.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabu} to \linewidth {>{}l>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
+\toprule
+\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
+\midrule
+\em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{32.07} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0}\\
+\addlinespace
+\em{Brassica rapa} & 44.97 & 0.00 & 0.00 & 0\\
+\addlinespace
+\em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{80.00} & \cellcolor{gray!6}{56.47} & \cellcolor{gray!6}{19.34} & \cellcolor{gray!6}{0}\\
+\addlinespace
+\em{Eruca sativa} & 23.75 & 0.42 & 0.00 & 0\\
+\addlinespace
+\em{\cellcolor{gray!6}{Ipomoea aquatica}} & \cellcolor{gray!6}{40.00} & \cellcolor{gray!6}{30.00} & \cellcolor{gray!6}{20.00} & \cellcolor{gray!6}{0}\\
+\addlinespace
+\em{Ipomoea purpurea} & 31.67 & 86.67 & 31.67 & 0\\
+\addlinespace
+\em{\cellcolor{gray!6}{Petunia integrifolia}} & \cellcolor{gray!6}{80.16} & \cellcolor{gray!6}{24.77} & \cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0}\\
+\addlinespace
+\em{Sinapis alba} & 41.67 & 48.33 & 5.00 & 15\\
+\addlinespace
+\em{\cellcolor{gray!6}{Solanum lycopersium}} & \cellcolor{gray!6}{85.65} & \cellcolor{gray!6}{41.20} & \cellcolor{gray!6}{68.48} & \cellcolor{gray!6}{0}\\
+\addlinespace
+\em{Solanum melongena} & 60.48 & 74.87 & 21.56 & 0\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\begin{landscape}
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-5}\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species.
+The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment.
+Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.}
+\centering
+\resizebox{\linewidth}{!}{
+\fontsize{6}{8}\selectfont
+\begin{tabu} to \linewidth {>{}l>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright}X>{\raggedright}X}
+\toprule
+\em{} & \em{Brassica oleracea} & \em{Brassica rapa} & \em{Eruca sativa} & \em{Sinapis alba} & \em{Ipomoea aquatica} & \em{Ipomoea purpurea} & \em{Capsicum annuum} & \em{Petunia integrifolia} & \em{Solanum lycopersicum} & \em{Solanum melongena} & \em{$\%$ of significant effect}\\
+\midrule
+\em{\cellcolor{gray!6}{B.
+oleracea}} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{100}\\
+\addlinespace
+\em{B. rapa} & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 88.9\\
+\addlinespace
+\em{\cellcolor{gray!6}{E.
+sativa}} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{22.2}\\
+\addlinespace
+\em{S. alba} & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 44.4\\
+\addlinespace
+\em{\cellcolor{gray!6}{I.
+aquatica}} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{100}\\
+\addlinespace
+\em{I. purpurea} & No & No & Yes & No & No &  & Yes & No & Yes & No & 33.3\\
+\addlinespace
+\em{\cellcolor{gray!6}{C.
+annuum}} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes1} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{77.8}\\
+\addlinespace
+\em{P. integrifolia} & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 67.7\\
+\addlinespace
+\em{\cellcolor{gray!6}{S.
+lycopersicum}} & \cellcolor{gray!6}{No} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{Yes} & \cellcolor{gray!6}{88.9}\\
+\addlinespace
+\em{S. melongena} & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 55.6\\
+\addlinespace
+\em{\cellcolor{gray!6}{}} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{} & \cellcolor{gray!6}{$\bar{X}=67.8$}\\
+\bottomrule
+\end{tabu}}
+\end{table}
+
+\end{landscape}
+
+\clearpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{>{}lrrrr}
+\caption{\label{tab:unnamed-chunk-6}\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments.
+We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
+The first species on the row names are the pollen recipient species and the second species the pollen donor species.
+Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.}\\
+\toprule
+\textbf{ } & \textbf{Estimates} & \textbf{Standard error} & \textbf{t-value} & \textbf{{\textit{P}}-value}\\
+\midrule
+\em{\cellcolor{gray!6}{M1 Petunia integrifolia - (Intercept)}} & \cellcolor{gray!6}{4.63} & \cellcolor{gray!6}{0.49} & \cellcolor{gray!6}{9.36} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M1 Petunia integrifolia - Brassica oleracea} & -1.84 & 0.81 & -2.27 & 0.03\\
+\addlinespace
+\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Brassica rapa}} & \cellcolor{gray!6}{-0.97} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-1.19} & \cellcolor{gray!6}{0.24}\\
+\addlinespace
+\em{M1 Petunia integrifolia - Capsicum annuum} & 0.78 & 0.81 & 0.96 & 0.34\\
+\addlinespace
+\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Eruca vesicaria}} & \cellcolor{gray!6}{-0.91} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-1.12} & \cellcolor{gray!6}{0.26}\\
+\addlinespace
+\em{M1 Petunia integrifolia - Ipomoea aquatica} & -3.18 & 0.81 & -3.92 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Ipomoea purpurea}} & \cellcolor{gray!6}{-4.21} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-5.19} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M1 Petunia integrifolia - Sinapis alba} & -2.99 & 0.81 & -3.69 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M1 Petunia integrifolia - Solanum lycopersicum}} & \cellcolor{gray!6}{-2.40} & \cellcolor{gray!6}{0.81} & \cellcolor{gray!6}{-2.96} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M1 Petunia integrifolia - Solanum melongena} & -2.66 & 0.81 & -3.27 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - (Intercept)}} & \cellcolor{gray!6}{4.39} & \cellcolor{gray!6}{0.24} & \cellcolor{gray!6}{18.54} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M2 Solanum lycopersicum - Brassica oleracea} & -0.47 & 0.41 & -1.14 & 0.26\\
+\addlinespace
+\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Brassica rapa}} & \cellcolor{gray!6}{-2.74} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-6.67} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M2 Solanum lycopersicum - Capsicum annuum} & -4.39 & 0.41 & -10.71 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Eruca vesicaria}} & \cellcolor{gray!6}{-2.97} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-7.25} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M2 Solanum lycopersicum - Ipomoea aquatica} & -4.13 & 0.41 & -10.06 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Ipomoea purpurea}} & \cellcolor{gray!6}{-3.80} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-9.27} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M2 Solanum lycopersicum - Petunia integrifolia} & -1.82 & 0.41 & -4.44 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M2 Solanum lycopersicum - Sinapis alba}} & \cellcolor{gray!6}{-3.72} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{-9.08} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M2 Solanum lycopersicum - Solanum melongena} & -1.84 & 0.41 & -4.49 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M3 Solanum melongena - (Intercept)}} & \cellcolor{gray!6}{6.34} & \cellcolor{gray!6}{0.70} & \cellcolor{gray!6}{9.09} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M3 Solanum melongena - Brassica oleracea} & -0.67 & 0.99 & -0.68 & 0.50\\
+\addlinespace
+\em{\cellcolor{gray!6}{M3 Solanum melongena - Brassica rapa}} & \cellcolor{gray!6}{-4.33} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-4.39} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M3 Solanum melongena - Capsicum annuum} & -2.33 & 0.99 & -2.36 & 0.02\\
+\addlinespace
+\em{\cellcolor{gray!6}{M3 Solanum melongena - Eruca vesicaria}} & \cellcolor{gray!6}{-3.12} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-3.16} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M3 Solanum melongena - Ipomoea aquatica} & -6.34 & 0.99 & -6.43 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M3 Solanum melongena - Ipomoea purpurea}} & \cellcolor{gray!6}{-2.71} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-2.74} & \cellcolor{gray!6}{0.01}\\
+\addlinespace
+\em{M3 Solanum melongena - Petunia integrifolia} & -1.43 & 0.99 & -1.45 & 0.15\\
+\addlinespace
+\em{\cellcolor{gray!6}{M3 Solanum melongena - Sinapis alba}} & \cellcolor{gray!6}{-1.11} & \cellcolor{gray!6}{0.99} & \cellcolor{gray!6}{-1.12} & \cellcolor{gray!6}{0.26}\\
+\addlinespace
+\em{M3 Solanum melongena - Solanum lycopersicum} & -0.84 & 0.99 & -0.86 & 0.39\\
+\addlinespace
+\em{\cellcolor{gray!6}{M4 Capsicum annuum - (Intercept)}} & \cellcolor{gray!6}{4.59} & \cellcolor{gray!6}{0.52} & \cellcolor{gray!6}{8.78} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M4 Capsicum annuum - Brassica oleracea} & -1.80 & 0.74 & -2.43 & 0.02\\
+\addlinespace
+\em{\cellcolor{gray!6}{M4 Capsicum annuum - Brassica rapa}} & \cellcolor{gray!6}{-2.51} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-3.39} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M4 Capsicum annuum - Eruca vesicaria} & -0.63 & 0.74 & -0.85 & 0.40\\
+\addlinespace
+\em{\cellcolor{gray!6}{M4 Capsicum annuum - Ipomoea aquatica}} & \cellcolor{gray!6}{-1.36} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-1.84} & \cellcolor{gray!6}{0.07}\\
+\addlinespace
+\em{M4 Capsicum annuum - Ipomoea purpurea} & -4.00 & 0.74 & -5.41 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M4 Capsicum annuum - Petunia integrifolia}} & \cellcolor{gray!6}{-4.59} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-6.21} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M4 Capsicum annuum - Sinapis alba} & -3.63 & 0.74 & -4.92 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M4 Capsicum annuum - Solanum lycopersicum}} & \cellcolor{gray!6}{-1.52} & \cellcolor{gray!6}{0.74} & \cellcolor{gray!6}{-2.06} & \cellcolor{gray!6}{0.04}\\
+\addlinespace
+\em{M4 Capsicum annuum - Solanum melongena} & -3.29 & 0.74 & -4.46 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M5 Brassica oleracea - (Intercept)}} & \cellcolor{gray!6}{1.99} & \cellcolor{gray!6}{0.22} & \cellcolor{gray!6}{8.98} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M5 Brassica oleracea - Brassica rapa} & -1.37 & 0.31 & -4.35 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M5 Brassica oleracea - Capsicum annuum}} & \cellcolor{gray!6}{-0.87} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{-2.76} & \cellcolor{gray!6}{0.01}\\
+\addlinespace
+\em{M5 Brassica oleracea - Eruca vesicaria} & -1.92 & 0.31 & -6.13 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M5 Brassica oleracea - Ipomoea aquatica}} & \cellcolor{gray!6}{-1.91} & \cellcolor{gray!6}{0.27} & \cellcolor{gray!6}{-7.04} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M5 Brassica oleracea - Ipomoea purpurea} & -1.99 & 0.31 & -6.35 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M5 Brassica oleracea - Petunia integrifolia}} & \cellcolor{gray!6}{-1.64} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{-5.21} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M5 Brassica oleracea - Sinapis alba} & -1.57 & 0.31 & -4.99 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M5 Brassica oleracea - Solanum lycopersicum}} & \cellcolor{gray!6}{-1.47} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{-4.70} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M5 Brassica oleracea - Solanum melongena} & -1.61 & 0.31 & -5.12 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M6 Brassica rapa - (Intercept)}} & \cellcolor{gray!6}{2.37} & \cellcolor{gray!6}{0.19} & \cellcolor{gray!6}{12.49} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M6 Brassica rapa - Brassica oleracea} & -0.54 & 0.29 & -1.89 & 0.06\\
+\addlinespace
+\em{\cellcolor{gray!6}{M6 Brassica rapa - Capsicum annuum}} & \cellcolor{gray!6}{-1.42} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-4.94} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M6 Brassica rapa - Eruca vesicaria} & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M6 Brassica rapa - Ipomoea aquatica}} & \cellcolor{gray!6}{-1.92} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-6.67} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M6 Brassica rapa - Ipomoea purpurea} & -2.26 & 0.29 & -7.86 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M6 Brassica rapa - Petunia integrifolia}} & \cellcolor{gray!6}{-2.37} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-8.24} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M6 Brassica rapa - Sinapis alba} & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M6 Brassica rapa - Solanum lycopersicum}} & \cellcolor{gray!6}{-1.88} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-6.55} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M6 Brassica rapa - Solanum melongena} & -2.37 & 0.29 & -8.24 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M8 Eruca sativa - (Intercept)}} & \cellcolor{gray!6}{1.34} & \cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{3.80} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M8 Eruca sativa - Brassica oleracea} & -1.34 & 0.50 & -2.69 & 0.01\\
+\addlinespace
+\em{\cellcolor{gray!6}{M8 Eruca sativa - Brassica rapa}} & \cellcolor{gray!6}{0.66} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{1.32} & \cellcolor{gray!6}{0.19}\\
+\addlinespace
+\em{M8 Eruca sativa - Capsicum annuum} & -0.27 & 0.50 & -0.55 & 0.58\\
+\addlinespace
+\em{\cellcolor{gray!6}{M8 Eruca sativa - Ipomoea aquatica}} & \cellcolor{gray!6}{0.87} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{1.75} & \cellcolor{gray!6}{0.08}\\
+\addlinespace
+\em{M8 Eruca sativa - Ipomoea purpurea} & -0.19 & 0.50 & -0.39 & 0.70\\
+\addlinespace
+\em{\cellcolor{gray!6}{M8 Eruca sativa - Petunia integrifolia}} & \cellcolor{gray!6}{0.20} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{0.41} & \cellcolor{gray!6}{0.68}\\
+\addlinespace
+\em{M8 Eruca sativa - Sinapis alba} & 0.32 & 0.50 & 0.65 & 0.52\\
+\addlinespace
+\em{\cellcolor{gray!6}{M8 Eruca sativa - Solanum lycopersicum}} & \cellcolor{gray!6}{-0.52} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{-1.04} & \cellcolor{gray!6}{0.30}\\
+\addlinespace
+\em{M8 Eruca sativa - Solanum melongena} & 0.54 & 0.50 & 1.09 & 0.28\\
+\addlinespace
+\em{\cellcolor{gray!6}{M9 Ipomoea purpurea - (Intercept)}} & \cellcolor{gray!6}{0.82} & \cellcolor{gray!6}{0.20} & \cellcolor{gray!6}{4.05} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M9 Ipomoea purpurea - Brassica oleracea} & 0.37 & 0.29 & 1.31 & 0.19\\
+\addlinespace
+\em{\cellcolor{gray!6}{M9 Ipomoea purpurea - Brassica rapa}} & \cellcolor{gray!6}{-0.41} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-1.43} & \cellcolor{gray!6}{0.16}\\
+\addlinespace
+\em{M9 Ipomoea purpurea - Capsicum annuum} & -0.82 & 0.29 & -2.86 & 0.01\\
+\addlinespace
+\em{\cellcolor{gray!6}{M9 Ipomoea purpurea - Eruca vesicaria}} & \cellcolor{gray!6}{-0.75} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-2.62} & \cellcolor{gray!6}{0.01}\\
+\addlinespace
+\em{M9 Ipomoea purpurea - Ipomoea aquatica} & 0.41 & 0.29 & 1.44 & 0.15\\
+\addlinespace
+\em{\cellcolor{gray!6}{M9 Ipomoea purpurea - Petunia integrifolia}} & \cellcolor{gray!6}{-0.37} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-1.31} & \cellcolor{gray!6}{0.19}\\
+\addlinespace
+\em{M9 Ipomoea purpurea - Sinapis alba} & -0.33 & 0.29 & -1.14 & 0.26\\
+\addlinespace
+\em{\cellcolor{gray!6}{M9 Ipomoea purpurea - Solanum lycopersicum}} & \cellcolor{gray!6}{-0.82} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{-2.86} & \cellcolor{gray!6}{0.01}\\
+\addlinespace
+\em{M9 Ipomoea purpurea - Solanum melongena} & -0.24 & 0.29 & -0.82 & 0.41\\
+\addlinespace
+\em{\cellcolor{gray!6}{M10 Ipomoea aquatica - (Intercept)}} & \cellcolor{gray!6}{0.80} & \cellcolor{gray!6}{0.09} & \cellcolor{gray!6}{9.36} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M10 Ipomoea aquatica - Brassica oleracea} & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M10 Ipomoea aquatica - Brassica rapa}} & \cellcolor{gray!6}{-0.80} & \cellcolor{gray!6}{0.12} & \cellcolor{gray!6}{-6.62} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M10 Ipomoea aquatica - Capsicum annuum} & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M10 Ipomoea aquatica - Eruca vesicaria}} & \cellcolor{gray!6}{-0.80} & \cellcolor{gray!6}{0.12} & \cellcolor{gray!6}{-6.62} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M10 Ipomoea aquatica - Ipomoea purpurea} & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M10 Ipomoea aquatica - Petunia integrifolia}} & \cellcolor{gray!6}{-0.59} & \cellcolor{gray!6}{0.12} & \cellcolor{gray!6}{-4.89} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M10 Ipomoea aquatica - Sinapis alba} & -0.80 & 0.12 & -6.62 & 0.00\\
+\addlinespace
+\em{\cellcolor{gray!6}{M10 Ipomoea aquatica - Solanum lycopersicum}} & \cellcolor{gray!6}{-0.69} & \cellcolor{gray!6}{0.12} & \cellcolor{gray!6}{-5.70} & \cellcolor{gray!6}{0.00}\\
+\addlinespace
+\em{M10 Ipomoea aquatica - Solanum melongena} & -0.80 & 0.12 & -6.62 & 0.00\\
+\bottomrule
+\end{longtable}
+
+\endgroup{}
+
+\clearpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-7}\textbf{Table S7.} Number of seeds produced with the 100\% foreign pollen treatments (N=900).
+From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
+In this table we show just the treatments that lead to seed production.}
+\resizebox{\linewidth}{!}{
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{>{}l>{}lr}
+\toprule
+\textbf{Recipient} & \textbf{Donor (100\% foreign pollen)} & \textbf{Seed number}\\
+\midrule
+\em{\cellcolor{gray!6}{Solnamum lycopersicum}} & \em{\cellcolor{gray!6}{Sinapis alba}} & \cellcolor{gray!6}{3}\\
+\addlinespace
+\em{Solnamum melongena} & \em{Petunia integrifolia} & 36\\
+\addlinespace
+\em{\cellcolor{gray!6}{Capsicum annuum}} & \em{\cellcolor{gray!6}{Eruca sativa}} & \cellcolor{gray!6}{3}\\
+\addlinespace
+\em{Capsicum annuum} & \em{Sinapis alba} & 127\\
+\addlinespace
+\em{\cellcolor{gray!6}{Brassica rapa}} & \em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{2}\\
+\addlinespace
+\em{Brassica rapa} & \em{Brassica oleracea} & 13\\
+\addlinespace
+\em{\cellcolor{gray!6}{Sinapis alba}} & \em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{\vphantom{1} 7}\\
+\addlinespace
+\em{Sinapis alba} & \em{Brassica oleracea} & 5\\
+\addlinespace
+\em{\cellcolor{gray!6}{Sinapis alba}} & \em{\cellcolor{gray!6}{Brassica oleracea}} & \cellcolor{gray!6}{7}\\
+\addlinespace
+\em{Sinapis alba} & \em{Capsicum annuum} & 1\\
+\addlinespace
+\em{\cellcolor{gray!6}{Sinapis alba}} & \em{\cellcolor{gray!6}{Capsicum annuum}} & \cellcolor{gray!6}{6}\\
+\addlinespace
+\em{Sinapis alba} & \em{Solanum lycopersicum} & 1\\
+\addlinespace
+\em{\cellcolor{gray!6}{Eruca sativa}} & \em{\cellcolor{gray!6}{Petunia integrifolia}} & \cellcolor{gray!6}{2}\\
+\bottomrule
+\multicolumn{3}{l}{\textsuperscript{} * Note: There are some specific cases that we think that hybridization did not occur and that the recipient species were pollen}\\
+\multicolumn{3}{l}{contaminated, like the one of C. annuum with S. alba with 127 seeds. This seems to be the case for 5 other crosses that had very}\\
+\multicolumn{3}{l}{low seed production when they were pollinated with 100\% foreign pollen with species of other family members. This represents}\\
+\multicolumn{3}{l}{very few isolated cases (0.67\% of all the 100\% foreign pollen crosses conducted) and we think that our results are not}\\
+\multicolumn{3}{l}{compromised by this fact.}\\
+\end{tabular}}
+\end{table}
+
+\clearpage
+
+\begin{table}
+
+\caption{\label{tab:unnamed-chunk-8}\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.}
+\centering
+\fontsize{10}{12}\selectfont
+\begin{tabular}[t]{rrl}
+\toprule
+\textbf{Lambda} & \textbf{P-value} & \textbf{Traits}\\
+\midrule
+\cellcolor{gray!6}{0.95} & \cellcolor{gray!6}{0.20} & \cellcolor{gray!6}{Selfing rate}\\
+\addlinespace
+1.00 & 0.00 & Pollen size\\
+\addlinespace
+\cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{1.00} & \cellcolor{gray!6}{Pollen anther}\\
+\addlinespace
+0.00 & 1.00 & Ovule number\\
+\addlinespace
+\cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{1.00} & \cellcolor{gray!6}{Pollen-ovule ratio}\\
+\addlinespace
+0.89 & 0.01 & Stigmatic area\\
+\addlinespace
+\cellcolor{gray!6}{0.70} & \cellcolor{gray!6}{0.05} & \cellcolor{gray!6}{Stigma length}\\
+\addlinespace
+0.77 & 0.03 & Stigma width\\
+\addlinespace
+\cellcolor{gray!6}{0.93} & \cellcolor{gray!6}{0.01} & \cellcolor{gray!6}{Style length}\\
+\addlinespace
+0.00 & 1.00 & Style width\\
+\addlinespace
+\cellcolor{gray!6}{0.47} & \cellcolor{gray!6}{0.30} & \cellcolor{gray!6}{Ovary length}\\
+\addlinespace
+0.00 & 1.00 & Ovary width\\
+\addlinespace
+\cellcolor{gray!6}{0.00} & \cellcolor{gray!6}{0.02} & \cellcolor{gray!6}{SI index}\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\clearpage
+
+\begingroup\fontsize{7}{9}\selectfont
+
+\begin{longtable}[t]{rrrll}
+\caption{\label{tab:unnamed-chunk-9}\textbf{Table S9.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.}\\
+\toprule
+\textbf{Correlation (r)} & \textbf{Sum of squares} & \textbf{P-value} & \textbf{Traits} & \textbf{Family}\\
+\midrule
+\cellcolor{gray!6}{0.34} & \cellcolor{gray!6}{0.88} & \cellcolor{gray!6}{0.70} & \cellcolor{gray!6}{Selfing rate} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.36 & 0.87 & 0.42 & Pollen size & All\\
+\addlinespace
+\cellcolor{gray!6}{0.35} & \cellcolor{gray!6}{0.88} & \cellcolor{gray!6}{0.57} & \cellcolor{gray!6}{Pollen per anther} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.33 & 0.89 & 0.55 & Number of ovules & All\\
+\addlinespace
+\cellcolor{gray!6}{0.30} & \cellcolor{gray!6}{0.91} & \cellcolor{gray!6}{0.86} & \cellcolor{gray!6}{Pollen-ovule ratio} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.37 & 0.86 & 0.69 & Stigmatic area & All\\
+\addlinespace
+\cellcolor{gray!6}{0.62} & \cellcolor{gray!6}{0.62} & \cellcolor{gray!6}{0.10} & \cellcolor{gray!6}{Stigma length} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.46 & 0.79 & 0.47 & Stigma width & All\\
+\addlinespace
+\cellcolor{gray!6}{0.43} & \cellcolor{gray!6}{0.82} & \cellcolor{gray!6}{0.45} & \cellcolor{gray!6}{Style length} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.59 & 0.65 & 0.11 & Style width & All\\
+\addlinespace
+\cellcolor{gray!6}{0.34} & \cellcolor{gray!6}{0.88} & \cellcolor{gray!6}{0.57} & \cellcolor{gray!6}{Ovary length} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.35 & 0.88 & 0.93 & Ovary width & All\\
+\addlinespace
+\cellcolor{gray!6}{0.49} & \cellcolor{gray!6}{0.76} & \cellcolor{gray!6}{0.24} & \cellcolor{gray!6}{Self-incompatibility index} & \cellcolor{gray!6}{All}\\
+\addlinespace
+0.86 & 0.26 & 0.25 & Selfing rate & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.76} & \cellcolor{gray!6}{0.42} & \cellcolor{gray!6}{0.33} & \cellcolor{gray!6}{Pollen size} & \cellcolor{gray!6}{Solanaceae}\\
+\addlinespace
+0.42 & 0.82 & 0.79 & Pollen per anther & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.52} & \cellcolor{gray!6}{0.73} & \cellcolor{gray!6}{0.83} & \cellcolor{gray!6}{Number of ovules} & \cellcolor{gray!6}{Solanaceae}\\
+\addlinespace
+0.87 & 0.25 & 0.04 & Pollen-ovule ratio & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.82} & \cellcolor{gray!6}{0.33} & \cellcolor{gray!6}{0.17} & \cellcolor{gray!6}{Stigmatic area} & \cellcolor{gray!6}{Solanaceae}\\
+\addlinespace
+0.89 & 0.20 & 0.08 & Stigma length & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.84} & \cellcolor{gray!6}{0.29} & \cellcolor{gray!6}{0.12} & \cellcolor{gray!6}{Stigma width} & \cellcolor{gray!6}{Solanaceae}\\
+\addlinespace
+0.78 & 0.39 & 0.50 & Style length & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.52} & \cellcolor{gray!6}{0.73} & \cellcolor{gray!6}{0.71} & \cellcolor{gray!6}{Style width} & \cellcolor{gray!6}{Solanaceae}\\
+\addlinespace
+0.64 & 0.60 & 0.79 & Ovary length & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.87} & \cellcolor{gray!6}{0.23} & \cellcolor{gray!6}{0.17} & \cellcolor{gray!6}{Ovary width} & \cellcolor{gray!6}{Solanaceae}\\
+\addlinespace
+0.50 & 0.75 & 1.00 & Self-incompatibility index & Solanaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.61} & \cellcolor{gray!6}{0.63} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{Selfing rate} & \cellcolor{gray!6}{Brassicaceae}\\
+\addlinespace
+0.60 & 0.64 & 0.71 & Pollen size & Brassicaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.40} & \cellcolor{gray!6}{0.84} & \cellcolor{gray!6}{0.96} & \cellcolor{gray!6}{Pollen per anther} & \cellcolor{gray!6}{Brassicaceae}\\
+\addlinespace
+0.62 & 0.61 & 0.42 & Number of ovules & Brassicaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.49} & \cellcolor{gray!6}{0.76} & \cellcolor{gray!6}{0.96} & \cellcolor{gray!6}{Pollen-ovule ratio} & \cellcolor{gray!6}{Brassicaceae}\\
+\addlinespace
+0.55 & 0.70 & 0.58 & Stigmatic area & Brassicaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.92} & \cellcolor{gray!6}{0.15} & \cellcolor{gray!6}{0.08} & \cellcolor{gray!6}{Stigma length} & \cellcolor{gray!6}{Brassicaceae}\\
+\addlinespace
+0.63 & 0.60 & 0.38 & Stigma width & Brassicaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.83} & \cellcolor{gray!6}{0.31} & \cellcolor{gray!6}{0.08} & \cellcolor{gray!6}{Style length} & \cellcolor{gray!6}{Brassicaceae}\\
+\addlinespace
+0.79 & 0.37 & 0.33 & Style width & Brassicaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.59} & \cellcolor{gray!6}{0.65} & \cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{Ovary length} & \cellcolor{gray!6}{Brassicaceae}\\
+\addlinespace
+0.54 & 0.70 & 1.00 & Ovary width & Brassicaceae\\
+\addlinespace
+\cellcolor{gray!6}{0.50} & \cellcolor{gray!6}{0.75} & \cellcolor{gray!6}{0.83} & \cellcolor{gray!6}{Self-incompatibility index} & \cellcolor{gray!6}{Brassicaceae}\\
+\bottomrule
+\end{longtable}
+
+\endgroup{}
+
+\clearpage
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-10-1.pdf}
+\caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
+20 different treatments (3 replicates per tratment). For each treatment,
+we show the average number of conspecific pollen grains (grey) and
+heterospecific pollen grains (light blue) per stigma. For each pair of
+species on the x-axis, the first species is the recipient species, and
+the second, the donor species.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-11-1.pdf}
+\caption{\textbf{Fig. S2} Average proportion of conspecific and
+heterospecific pollen per stigma grouped by family, A) Brassicaceae, B)
+Solanaceae and C) Convolvulaceae. These proportions (\%) are the number
+of conspecific pollen grains or heterospecific pollen grains divided by
+the total number of pollen grains per stigma for 20 different
+treatments. We conducted 3 count replicates per treatment and then we
+calculated the average number of pollen grains for these treatments. The
+proportion of conspecific and heterospecific pollen are shown in grey
+and light blue respectively. For each pair of species on the y-axis, the
+first species is the pollen recipient and the second the pollen donor.
+The vertical black line represents 50\% pollen of both donor and
+recipient.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-12-1.pdf}
+\caption{\textbf{Fig. S3} Average proportion (\%) of heterospecific and
+conspecific pollen per family for the different 20 treatments counted.
+We conducted 3 count replicates per treatment and then we calculated the
+average number of pollen grains for these different 20 treatments.
+Finally, we grouped by family these treatments in order to see general
+tendencies across families as pollen donor and as pollen recipient.
+Pollen ratios were considered as the number of conspecific or
+heterospecific pollen grains divided by the total number of pollen
+grains per stigma. On the y-axis, the first family on each pair of plant
+families is the recipient one, and the second, the family of the donor.
+The vertical bar on intercept 50, represents equal proportions of both
+recipient (grey) and donor (light blue) pollen.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-13-1.pdf}
+\caption{\textbf{Fig. S4} Pollen ratios comparisons between the
+different pollen recipient families. The boxes represent least square
+means, the error bars confidence intervals 95\% and sharing numbers
+indicate no significant differences between groups (Tukey adjusted
+comparisons). These pollen ratios (\%) are the total number of
+heterospecific pollen grains divided by the total quantity of pollen
+(conspecific pollen + heterospecific pollen). Brassicacea family is
+coloured in blue, Convolvulaceae in green and Solanaceae in orange.}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-14-1.pdf}
+\caption{\textbf{Fig. S5} Unipartite bidirectional network with
+asymmetrical effect. The lines with the arrow heads connect the impact
+of foreign pollen (effect size) of each pollen donor species on each
+recipient species. All the arrow heads point to the recipient species of
+the reciprocal interaction. Lines of species that did not have a
+negative impact are not represented. The different nodes and the effect
+of the donor species on the recipient species appear coloured by family:
+Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green). The
+intensity of the effect is represented by the line´s size where a larger
+effect size corresponds to a thicker line and a thinner line to a
+smaller effect size. Species code: BROL: Brassica oleracea, BRRA:
+Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea
+aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia
+integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-15-1.pdf}
+\caption{\textbf{Fig. S6} Graphical representation of the correlation
+matrix of all the traits measured. Positive correlations are displayed
+in blue and negative in red. The intensity, size and colour of the
+circles are proportional to the correlation coefficient from Pearson's
+r.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-16-1.pdf}
+\caption{\textbf{Fig. S7} Violin plot of the proportion of seeds
+coverted to ovule (\%) for all species with four different
+hand-pollination treatments: apomixis (orange), hand cross pollination
+(green), hand self pollination (blue) and spontaneous selfing (yellow).
+The species are grouped by family in three different panels that are
+named with the corresponding family names (Brassicaceae, Convolvulaceae
+and Solanaceae). The coloured dots, represent the different values of
+seed:ovule ratio for each treatment.}
+\end{figure}
+
+\clearpage
+
+\begin{figure}
+\centering
+\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-17-1.pdf}
+\caption{\textbf{Fig. S8} Grouped effect sizes (95\% confidence
+intervals) of the different families on each focal species. For each
+species, the grouped effect by family is compared with the control
+treatment of hand cross pollination with conspecific pollen. The control
+treatment is represented in yellow and vertically intersected with a
+dashed line through the mean effect size in order to help the visual
+interpretation of the effect sizes. Any value to the left of the
+vertical dashed line represents a negative impact of foreign pollen. The
+different effect sizes and confidence intervals are coloured by family:
+Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).}
+\end{figure}
 

### 2021-02-14 Supplementary_material/Supp_Material.tex
Updating authorship on supp mat

--- 2020-09-01 Supplementary_material/Supp_Material.tex
@@
 \captionsetup[figure]{labelformat=empty}
-\captionsetup[table]{labelformat=empty} \renewcommand{\figurename}{}
+\captionsetup[table]{labelformat=empty}
+\renewcommand{\figurename}{}
 
-\section{Supporting information:}\label{supporting-information}
+\hypertarget{supporting-information}{%
+\section{Supporting information:}\label{supporting-information}}
 
+\hypertarget{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}{%
 \section{Recipient and donor characteristics govern the hierarchical
 structure of heterospecific pollen competition
-networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}
+networks}\label{recipient-and-donor-characteristics-govern-the-hierarchical-structure-of-heterospecific-pollen-competition-networks}}
 
 \textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
-Romina Rader
+Greg Bible and Romina Rader
 
@@
 \endhead
-
+\
 \endfoot
@@
 \end{longtabu}
-
 \endgroup{}
@@
 \end{longtable}
-
 \endgroup{}
@@
 \caption{\textbf{Fig. S4} Pollen ratios comparisons between the
-different pollen recipient families The boxes represent least square
+different pollen recipient families. The boxes represent least square
 means, the error bars confidence intervals 95\% and sharing numbers
@@
 (green), hand self pollination (blue) and spontaneous selfing (yellow).
-The coloured dots, represent the different values of seed:ovule ratio
-for each treatment.}
+The species are grouped by family in three different panels that are
+named with the corresponding family names (Brassicaceae, Convolvulaceae
+and Solanaceae). The coloured dots, represent the different values of
+seed:ovule ratio for each treatment.}
 \end{figure}

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/Figure_S7.Rmd
reoganization

--- 2020-08-05 Thesis_Chapter_1/Supp_Material.Rmd
@@
 \renewcommand{\figurename}{}
-
-# Supporting information:
-
-# Recipient and donor characteristics govern the hierarchical structure of heterospecific pollen competition networks
-
-__Authors:__ Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
-
-The following Supporting Information is available for this article:
-
-__Table S1.__ Species names, common names, varieties and sources of the different seeds.
-
-__Table S2.__ Trait measurements for all species.
-
-__Table S3.__ Average number of pollen grains of the recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
-
-__Table S4.__ Seed:ovule ratio (%) of the different reproductive biology treatments.
-
-__Table S5.__ Summary of the effect from the linear models of the different pollen donors on each recipient species.
-
-__Table S6.__ Estimates, standard error, t-value and _P_-value of the effect of the different 9 donors on each recipient species.
-
-__Table S7.__ Total number of seeds produced with the 100% foreign pollen treatments.
-
-__Table S8.__ Procrustes analysis results.
-
-__Table S9.__ Phylogenetic signal and significance for all the different traits.
-
-__Figure S1__. Average number of pollen grains of recipient and donor species per stigma with the 50:50 mix CP:HP pollen.
-
-__Figure S2__. Average proportion (%) of conspecific and heterospecific pollen per stigma with the 50:50 mix CP:HP pollen.
-
-__Figure S3__. Average proportion (%) of heterospecific and conspecific pollen per stigma and family with the 50:50 mix CP:HP pollen.
-
-__Figure S4__. Statistical comparison of the percentage of heterospecific pollen with the 50:50 pollen mix by family.
-
-__Figure S5__. Unipartite bidirectional network with asymmetrical effect.
-
-__Figure S6__. Correlation matrix for all the different traits.
-
-__Figure S7__. Species reproductive biology.
-
-__Figure S8__. Grouped effect sizes by family for each recipient species.
-
-\newpage
-
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(knitr)
-library(kableExtra)
-Species <- c("Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena")
-Species <- as.character(Species)
-
-Common_names <- c("Wild cabbage", "Pak choi", "Rocket", "White mustard", "Water spinach", "Morning glory", "Capsicum", "Petunia", "Tomato", "Eggplant")
-Common_names <- as.character(Common_names)
-Variety <- c("Capitata", "Chinensis", "", "", "", "", "California Wonder", "", "Tommy Toe", "Little Fingers") 
-Variety <- as.character(Variety)
-Source <- c("https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.mrfothergills.com.au/", "https://www.theseedcollection.com.au/", "http://www.shaman-australis.com.au", "https://www.edenseeds.com.au", "https://www.dianeseeds.com/", "https://www.mrfothergills.com.au/", "https://www.4seasonsseeds.com.au/")
-Source <- as.character(Source)
-t <- data.frame(Species, Common_names, Variety, Source)
-colnames(t) <- c("Species", "Common names", "Varieties", "Source")
-kable(t, format = "latex", longtable = T, booktabs = T,linesep = "\\addlinespace",
-             caption = "\\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.") %>%
-  kable_styling(latex_options = c("repeat_header","striped"), font_size = 10, full_width=T) %>% row_spec(0,bold=TRUE)  %>%
-  column_spec(1,italic =T)
-```
-
-\begin{landscape}
-
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(kableExtra)
-
-dat <- readRDS("Tables/traits_supplementary.rds")
-#Convert to square mm and mm
-dat$stigma_area <- dat$stigma_area/1000000
-dat[,c(7:12)] <- dat[,c(7:12)]/1000
-
-colnames(dat) <- c("Species", "Pollen size $\\mu$m", "Pollen grains per anther", "Ovule number", "Pollen:ovule ratio", "Stigma area $\\mu$m$^{2}$", "Stigma length (mm)", "Stigma width (mm)", "Style length (mm)", "Style width (mm)", "Ovary length (mm)", "Ovary width (mm)", "Selfing rate", "SI index")
-
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S2.} Average values of the trait measurements for each plant species.
-Sample sizes are provided on the methods section.
-Detailed information of how pollen:ovule ratio, selfing rate and SI index were calculated is available in the plant functional traits section from the methods.
-The raw data can be found on the online repository provided within this manuscript.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "2cm")%>%column_spec(1,italic =T)
-```
-
-\end{landscape}
-
-\newpage
-
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(kableExtra)
-dat <- readRDS("Tables/total_pollen.rds")
-dat <- dat[,-5]
-colnames(dat) <- c("Recipient species", "Donor species", "Recipient pollen grains", "Donor pollen grains")
-
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S3.} Average recipient and donor pollen grains per stigma with the 50:50 mix CP:HP pollen for the subset of 20 counts (3 replicates per treatment).", escape = FALSE,booktabs = T,linesep = "\\addlinespace")%>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down"))%>%column_spec(1,italic =T)%>%column_spec(2,italic =T) %>% row_spec(0,bold=TRUE)
-
-```
-
-\newpage
-
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-library(kableExtra)
-dat <- readRDS("Tables/rep_biology_supplementary.rds")
-
-kable(dat, "latex", longtable = F, caption = "\\textbf{Table S4.} Results of the test of hand cross-pollination, hand self-pollination, spontaneous selfing and apomixis for all species.
-The values provided are the seed:ovule ratios in percentage.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 10, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>% column_spec(1, width = "3cm")%>%column_spec(1,italic =T)
-
-```
-
-\begin{landscape}
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-setwd("~/R_projects/Hp_pollen_experiment")
-d <- read.csv("Data/Csv/Significant_Effect_50_50.csv")
-#Unfortunately this table is not built through clean reproducible code
-#Our collaborators do not work with markdown and some plots were made directly in word
-#I have converted that table to csv and exported in R
-#To reproduce it, the file hp_seed_set_reduction in the folder analysis has everything
-#that is needed to make this table
-
-d <- as.data.frame(d)
-d <- d[,-12]
-d[11,12] <- "$\\bar{X}=67.8$"
-colnames(d) <- c("", "Brassica oleracea", "Brassica rapa", "Eruca sativa", "Sinapis alba", "Ipomoea aquatica", "Ipomoea purpurea", "Capsicum annuum", "Petunia integrifolia", "Solanum lycopersicum", "Solanum melongena", "$\\%$ of significant effect")
-
-kable(d, "latex", longtable = F, caption= "\\textbf{Table S5.} Summary of the heterospecific pollen impacts from the linear models on each pollen recipient species.
-The category of “yes” represents a significant effect of the pollen donor (columns) on the recipient species (rows) and the category of “no” represents a lack of significant seed set reduction in comparison with the control treatment.
-Significance was tested for each species by comparing the different 50-50 CP-HP pollen treatments with the control treatment of hand cross-pollination with conspecific pollen.", escape = FALSE,digits=2,booktabs = T,linesep = "\\addlinespace") %>% kable_styling(font_size = 6, full_width=T,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=FALSE)  %>% column_spec(1, width = "2cm")%>% column_spec(10, width = "1.5cm")%>%column_spec(1,italic =T) %>% row_spec(0,italic =T)
-```
-
-\end{landscape}
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-setwd("~/R_projects/Hp_pollen_experiment")
-d <- readRDS("Data/RData/lm_table.RData")
-#kable(d, format="latex",caption= "\\textbf{Table S6.} Output of linear models of the effect of the different donors on the seed set of each recipient species.", digits = 2)
-
-colnames(d) <- c("Estimates", "Standard error", "t-value", "{\\textit{P}}-value")
-
-kable(d, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S6.} Results of the linear models conducted to test the effect of heterospecific pollen with the 50-50 CP-HP pollen treatments.
-We conducted 10 different linear models (M1, M2, M3, M4, M5, M6, M7 M8, M9 and M10) where the effect of the different 9 pollen donors was compared with the control treatment of hand cross pollination with conspecific pollen for each recipient species (intercept).
-The first species on the row names are the pollen recipient species and the second species the pollen donor species.
-Each treatment is compared with the control or reference treatment that is indicated with the recipient species names and the intercept term between parentheses.") %>%
-  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>%column_spec(1,italic =T)%>% row_spec(0,bold=TRUE)
-```
-
-\clearpage
-
-```{r, echo=FALSE, warning=FALSE, fig.align="center", out.width='80%'}
-setwd("~/R_projects/Hp_pollen_experiment")
-
-library(kableExtra)
-
-#Preparing seed set with 100% pollen
-pein_seed_set_100 <- read.csv("Raw_data/pein_seed_set_100.csv")
-soly_seed_set_100 <- read.csv("Raw_data/soly_seed_set_100.csv")
-some_seed_set_100 <- read.csv("Raw_data/some_seed_set_100.csv")
-caan_seed_set_100 <- read.csv("Raw_data/caan_seed_set_100.csv")
-brol_seed_set_100 <- read.csv("Raw_data/brol_seed_set_100.csv")
-brra_seed_set_100 <- read.csv("Raw_data/brra_seed_set_100.csv")
-sial_seed_set_100 <- read.csv("Raw_data/sial_seed_set_100.csv")
-ersa_seed_set_100 <- read.csv("Raw_data/ersa_seed_set_100.csv")
-ippu_seed_set_100 <- read.csv("Raw_data/ippu_seed_set_100.csv")
-ipaq_seed_set_100 <- read.csv("Raw_data/ipaq_seed_set_100.csv")
-
-all_100 <- rbind(pein_seed_set_100,soly_seed_set_100,some_seed_set_100,caan_seed_set_100,
-      brol_seed_set_100,brra_seed_set_100,sial_seed_set_100,ersa_seed_set_100,
-      ippu_seed_set_100,ipaq_seed_set_100)
-
-all_100_subset <- all_100[grepl("100", all_100$Treatment), , drop = FALSE]
-
-seed_100 <- subset(all_100_subset, all_100_subset$Seed.production>0)
-#str(seed_100)
-seed_100$Species <- as.character(seed_100$Species)
-seed_100$Species[seed_100$Species=="SOLY"] <- "Solnamum lycopersicum"
-seed_100$Species[seed_100$Species=="SOME"] <- "Solnamum melongena"
-seed_100$Species[seed_100$Species=="CAAN"] <- "Capsicum annuum"
-seed_100$Species[seed_100$Species=="BRRA"] <- "Brassica rapa"
-seed_100$Species[seed_100$Species=="SIAL"] <- "Sinapis alba"
-seed_100$Species[seed_100$Species=="ERSA"] <- "Eruca sativa"
-
-seed_100$Treatment <- as.character(seed_100$Treatment)
-
-seed_100$Treatment[seed_100$Treatment=="SIAL 100%"] <- "Sinapis alba"
-seed_100$Treatment[seed_100$Treatment=="ERSA 100%"] <- "Eruca sativa"
-seed_100$Treatment[seed_100$Treatment=="PEIN 100%"] <- "Petunia integrifolia"
-seed_100$Treatment[seed_100$Treatment=="BROL 100%"] <- "Brassica oleracea"
-seed_100$Treatment[seed_100$Treatment=="CAAN 100%"] <- "Capsicum annuum"
-seed_100$Treatment[seed_100$Treatment=="SOLY 100%"] <- "Solanum lycopersicum"
-
-seed_100 <- seed_100[,-c(1,4,6)]
-colnames(seed_100) <- c("Recipient", "Donor (100% foreign pollen)", "Seed number")
-rownames(seed_100) <- NULL
-
-seed_100 <- as.data.frame(seed_100)
-
-kable(seed_100, "latex", longtable = F,digits=2,booktabs = T, linesep = "\\addlinespace", caption= "\\textbf{Table S7.} Number of seeds produced with the 100\\% foreign pollen treatments (N=900).
-From 900 pollination events we found seed production in just 13 specific cases and 0 seed production in the other 887 pollination events.
-In this table we show just the treatments that lead to seed production.") %>% kable_styling(font_size = 10,position="left",full_width=F,latex_options = c("striped","scale_down")) %>% row_spec(0,bold=TRUE)  %>%
-   add_footnote("*            Note: There are some specific cases that we think that hybridization did not occur and that the recipient species were pollen contaminated, like the one of C.
-annuum with S.
-alba with 127 seeds.
-This seems to be the case for 5 other crosses that had very low seed production when they were pollinated with 100% foreign pollen with species of other family members.
-This represents very few isolated cases (0.67% of all the 100% foreign pollen crosses conducted) and we think that our results are not compromised by this fact.
-", notation = "none") %>% column_spec(1,italic =T)%>% column_spec(2,italic =T)
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,  out.width='40%'}
-
-library(kableExtra)
-setwd("~/R_projects/Hp_pollen_experiment")
-load("Data/RData/img_phylo.RData")
-lambda <- c( selfing[1], pollen_size[1], mean_pollen_anther[1], mean_ovules[1], pollen_ovule_ratio[1], stigma_area[1], stigma_length[1], stigma_width[1], style_length[1], style_width[1], ovary_length[1], ovary_width[1],si_index[1])
-lambda<- as.numeric(lambda)
-p <- c(selfing[4], pollen_size[4], mean_pollen_anther[4], mean_ovules[4], pollen_ovule_ratio[4], stigma_area[4], stigma_length[4], stigma_width[4], style_length[4], style_width[4], ovary_length[4], ovary_width[4], si_index[4])
-p <- as.numeric(p)
-trait <- c("Selfing rate", "Pollen size", "Pollen anther", "Ovule number", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width", "Ovary length", "Ovary width", "SI index")
-table<- data.frame(lambda,p, trait)
-colnames(table) <- c("Lambda", "P-value", "Traits")
-#kable(table, format="latex",caption= "\\textbf{Table S7.} Phylogenetic signal and significance for all the different traits.", digits = 2)
-
-kable(table, format="latex",escape=F,digits=2, longtable = F,booktabs = T,linesep = "\\addlinespace", caption= "\\textbf{Table S8.} Phylogenetic signal and significance for the 13 different reproductive traits measured for all species.") %>% kable_styling(font_size = 10, full_width=F,latex_options = c("striped")) %>% row_spec(0,bold=TRUE)
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
-library(kableExtra)
-setwd("~/R_projects/Hp_pollen_experiment")
-
-load("Data/RData/Table_s4.RData")
-
-Correlation <- c(selfing_pro[6], pollen_size_pro[6], mean_pollen_anther_pro[6], mean_ovules_pro[6], pollen_ovule_ratio_pro[6], stigma_area_pro[6], stigma_length_pro[6], stigma_width_pro[6], style_length_pro[6], style_width_pro[6], ovary_width_pro[6], ovary_length_pro[6], si_index_pro[6],selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6],selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
-
-Correlation<- as.numeric(Correlation)
-
-Sum_squares <- c(selfing_pro[3], pollen_size_pro[3], mean_pollen_anther_pro[3], mean_ovules_pro[3], pollen_ovule_ratio_pro[3], stigma_area_pro[3], stigma_length_pro[3], stigma_width_pro[3], style_length_pro[3], style_width_pro[3], ovary_width_pro[3], ovary_length_pro[3],si_index_pro[3], selfing_pro_sol[3], pollen_size_pro_sol[3], mean_pollen_anther_pro_sol[3], mean_ovules_pro_sol[3], pollen_ovule_ratio_pro_sol[3], stigma_area_pro_sol[3], stigma_length_pro_sol[3], stigma_width_pro_sol[3], style_length_pro_sol[3], style_width_pro_sol[3], ovary_width_pro_sol[3], ovary_length_pro_sol[3],si_index_pro_sol[3], selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])
-
-Sum_squares<- as.numeric(Sum_squares)
-
-Significance <- c(selfing_pro[13], pollen_size_pro[13], mean_pollen_anther_pro[13], mean_ovules_pro[13], pollen_ovule_ratio_pro[13], stigma_area_pro[13], stigma_length_pro[13], stigma_width_pro[13], style_length_pro[13], style_width_pro[13], ovary_width_pro[13], ovary_length_pro[13],si_index_pro[13],selfing_pro_sol[13], pollen_size_pro_sol[13], mean_pollen_anther_pro_sol[13], mean_ovules_pro_sol[13], pollen_ovule_ratio_pro_sol[13], stigma_area_pro_sol[13], stigma_length_pro_sol[13], stigma_width_pro_sol[13], style_length_pro_sol[13], style_width_pro_sol[13], ovary_width_pro_sol[13], ovary_length_pro_sol[13],si_index_pro_sol[13], selfing_pro_bra[13], pollen_size_pro_bra[13], mean_pollen_anther_pro_bra[13], mean_ovules_pro_bra[13], pollen_ovule_ratio_pro_bra[13], stigma_area_pro_bra[13], stigma_length_pro_bra[13], stigma_width_pro_bra[13], style_length_pro_bra[13], style_width_pro_bra[13], ovary_width_pro_bra[13], ovary_length_pro_bra[13],si_index_pro_bra[13])
-
-Significance <- as.numeric(Significance)
-
-Trait <- c("Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index", "Selfing rate", "Pollen size", "Pollen per anther", "Number of ovules", "Pollen-ovule ratio", "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width","Ovary length","Ovary width", "Self-incompatibility index")
-
-Family <- c(rep("All",13),rep("Solanaceae",13),rep("Brassicaceae",13))
-
-table<- data.frame(Correlation,Sum_squares, Significance,Trait,Family)
-
-colnames(table) <- c("Correlation (r)","Sum of squares", "P-value", "Traits", "Family")
-
-kable(table, "latex", longtable = T, digits=2, escape=F,booktabs = T,linesep = "\\addlinespace",caption= "\\textbf{Table S9.} Procrustes correlation, sum of squares and significance from Procrustes analysis between the matrix of effect sizes (species x species matrix) and the distance matrix of each trait for all families, just Solanaceae family and just Brassicaceae family.") %>%
-  kable_styling(latex_options = c("striped"), font_size = 7, full_width=F)%>% row_spec(0,bold=TRUE)
-
-```
-
-\clearpage
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6 ,fig.width=7, fig.cap="**Fig.
-S1** Average number of pollen grains per stigma for 20 different treatments (3 replicates per tratment).
-For each treatment, we show the average number of conspecific pollen grains (grey) and heterospecific pollen grains (light blue) per stigma.
-For each pair of species on the x-axis, the first species is the recipient species, and the second, the donor species."}
-
-library(ggplot2)
-
-setwd("~/R_projects/Hp_pollen_experiment")
-total_pollen <- read.csv("Data/Csv/total_pollen.csv")
-ggplot(total_pollen, aes(x=spp, y=ratio, fill=variable,width=.9)) +
-  geom_bar(stat='identity', position='dodge')+theme_light()+ 
-  theme(legend.title = element_blank(),axis.text.x=element_text(angle=60,hjust=1,face="italic"))+
-  scale_fill_manual(values=c("#999999","#779799"),labels = c("Conspecific pollen","Heterospecific pollen"))+labs(x = "",y="Pollen grains per stigma")
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=7,fig.width=7, fig.cap="**Fig.
-S2** Average proportion of conspecific and heterospecific pollen per stigma grouped by family, A) Brassicaceae, B) Solanaceae and C) Convolvulaceae.
-These proportions (%) are the number of conspecific pollen grains or heterospecific pollen grains divided by the total number of pollen grains per stigma for 20 different treatments.
-We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these treatments.
-The proportion of conspecific and heterospecific pollen are shown in grey and light blue respectively.
-For each pair of species on the y-axis, the first species is the pollen recipient and the second the pollen donor.
-The vertical black line represents 50% pollen of both donor and recipient."}
-
-par(mar=c(2,13,2,4),xpd=F)
-par(mfrow=c(3,1))
-setwd("~/R_projects/Hp_pollen_experiment")
-ratio_bra <-readRDS("Data/RData/ratio_bra.RData")
-coul = c("#999999","#779799")
-barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E.
-sativa-I.
-purpurea", "B.
-oleracea-I.
-purpurea","B.
-rapa-I.
-purpurea", "S.
-alba-I.
-aquatica", "S.
-alba-S.
-melongena", "E.
-sativa-P.
-integrifolia", "B.
-rapa-S.
-lycopersicum", "B.
-oleracea-C.
-annuum"))
-abline(v=50,col="black")
-legend(-1,-0.1,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
-text(8.3,6.8,"A) Brassicaceae")
-ratio_con <-readRDS("Data/RData/ratio_con.RData")
-barplot(ratio_con,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("I.
-purpurea-S.
-melongena","I.
-aquatica-C.
-annuum","I.
-purpurea-E.
-sativa","I.
-aquatica-S.
-alba"))
-abline(v=50,col="black")
-legend(-1,-0.5,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
-text(9,3.5,"B) Convolvulaceae")
-
-ratio_sol <-readRDS("Data/RData/ratio_sol.RData")
-barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
-annuum-I.
-purpurea", "S.
-melongena-I.
-aquatica", "P.
-integrifolia-I.
-aquatica", "S.
-lycopersicum-I aquatica","S.
-melongena-E.
-sativa", "P.
-integrifolia-E.
-sativa", "C.
-annuum-S.
-alba", "S.
-lycopersicum-B.
-rapa"))
-abline(v=50,col="black")
-legend(-1,-0.1,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul)
-text(6.8,6.8,"C) Solanaceae")
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=4.5,fig.width=5,  fig.cap="**Fig.
-S3** Average proportion (%) of heterospecific and conspecific pollen per family for the different 20 treatments counted.
-We conducted 3 count replicates per treatment and then we calculated the average number of pollen grains for these different 20 treatments.
-Finally, we grouped by family these treatments in order to see general tendencies across families as pollen donor and as pollen recipient.
-Pollen ratios were considered as the number of conspecific or heterospecific pollen grains divided by the total number of pollen grains per stigma.
-On the y-axis, the first family on each pair of plant families is the recipient one, and the second, the family of the donor.
-The vertical bar on intercept 50, represents equal proportions of both recipient (grey) and donor (light blue) pollen."}
-
-par(mar=c(2,8.7,2,2),xpd=F)
-setwd("~/R_projects/Hp_pollen_experiment")
-data_percentage <-readRDS("Data/RData/per.RData")
-data_percentage=as.matrix(data_percentage)
-coul = c("#999999","#779799")
-barplot(data_percentage,hor=T, xlim=c(-1,100),ylim=c(-2,5),width = 0.5,col=coul ,space=0.5, border="white",srt=80,las=1,cex.axis=0.85,cex.names=0.65,names=c("Brassicaceae-Convolvulaceae",
- "Brassicaceae-Solanaceae","Convolvulaceae-Brassicaceae","Convolvulaceae-Solanaceae","Solanaceae-Convolvulaceae","Solanaceae-Brassicaceae"))
-legend(0,-0.5,legend=c("Conspecific pollen","Heterospecific pollen"),bty="n",fill = coul, cex = 0.65)
-abline(v=50,col="black")
-
-#lines(c(0,10),50,col="red")
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=12,  fig.cap="**Fig.
-S4** Pollen ratios comparisons between the different pollen recipient families The boxes represent least square means, the error bars confidence intervals 95% and sharing numbers indicate no significant differences between groups (Tukey adjusted comparisons).
-These pollen ratios (%) are the total number of heterospecific pollen grains divided by the total quantity of pollen (conspecific pollen + heterospecific pollen).
-Brassicacea family is coloured in blue, Convolvulaceae in green and Solanaceae in orange."}
-
-#Here I try to compare the different proportions of pollen between the different groups
-#I use Tukey method
-
-library(lme4)
-library(emmeans)
-library(reshape2)
-library(multcompView)
-library(lsmeans)
-library(multcomp)
-library(ggplot2)
-library(DHARMa)
-setwd("~/R_projects/Hp_pollen_experiment")
-
-total_pollen <- read.csv("Data/Csv/total_pollen.csv")
-
-total_pollen=total_pollen[,-1]
-colnames(total_pollen)[3] <- "pollen"
-#head(total_pollen)
-
-# Dividing by focal pollen and non focal pollen
-# In order to compare pollen as donor and recipient per family 
-pollen_foc <- subset(total_pollen, variable=="focal_pollen")
-pollen_non <- subset(total_pollen, variable=="non_focal_pollen")
-
-total  <- as.numeric(pollen_foc$pollen) + as.numeric(pollen_non$pollen)
-pollen_non$total_pollen  <- total
-pollen_non$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
-pollen_non$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
-                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
-                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
-                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
-
-pollen_non <- pollen_non[,-c(1,2)]
-colnames(pollen_non)[1] <-"hp_pollen"
-pollen_non$hp_ratio <- as.numeric(pollen_non$hp_pollen)/as.numeric(pollen_non$total_pollen)
-#hist(pollen_non$hp_ratio)
-
-pollen_foc$total_pollen  <- total
-pollen_foc$fam_non <- c(rep("Convolvulaceae", 8), rep("Solanaceae", 6), rep("Brassicaceae", 6))
-pollen_foc$fam_foc <- c("Solanaceae","Brassicaceae","Brassicaceae","Brassicaceae","Solanaceae",
-                        "Solanaceae","Solanaceae","Brassicaceae","Convolvulaceae","Brassicaceae",
-                        "Brassicaceae", "Brassicaceae", "Convolvulaceae", "Brassicaceae", "Convolvulaceae", "Solanaceae",
-                        "Solanaceae", "Convolvulaceae","Solanaceae","Solanaceae")
-
-pollen_foc <- pollen_foc[,-c(1,2)]
-colnames(pollen_foc)[1] <-"hp_pollen"
-pollen_foc$hp_ratio <- as.numeric(pollen_foc$hp_pollen)/as.numeric(pollen_foc$total_pollen)
-#hist(pollen_foc$hp_ratio)
-
-#Analyse data and plot it
-
-junk.glmer = lm(hp_ratio ~ fam_non, data = pollen_non)
-#plot(junk.glmer)
-#goodness of fit of the model
-#testDispersion(junk.glmer)
-#simulationOutput <- simulateResiduals(fittedModel = junk.glmer, plot = T)
-
-#lsm = lsmeans(junk.glmer, "fam_non", type = "response")
-#pairs(lsm)
-#CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
-
-#ggplot(CLD,aes(x= fam_non,y= lsmean,
-#label = .group)) +theme_minimal()+
-#geom_point(shape  = 15,size   = 4) +ggtitle("B) Comparison of ratios as donor")+
-#geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL),
-#width =  0.2,size =  0.7)+ylab("Least square mean")+xlab("Families")+
-#geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black")
-
-#Analyse data and plot it
-junk.glmer = lm(hp_ratio ~ fam_foc, data = pollen_foc)
-lsm = lsmeans(junk.glmer, "fam_foc", type = "response")
-#pairs(lsm)
-CLD <- CLD(lsm,alpha=0.05,adjust="tukey")
-
-#theme
-theme_ms <- function(base_size=12, base_family="Helvetica") {
-  library(grid)
-  (theme_bw(base_size = base_size, base_family = base_family)+
-      theme(text=element_text(color="black"),
-            axis.title=element_text( size = rel(1.3)),
-            axis.text=element_text(size = rel(1), color = "black"),
-            legend.title=element_text(face="bold"),
-            legend.text=element_text(),
-            legend.background=element_rect(fill="transparent"),
-            legend.key.size = unit(0.8, 'lines'),
-            panel.border=element_rect(color="black",size=1),
-            panel.grid.minor.x =element_line(),
-            panel.grid.minor.y= element_blank()
-      ))
-}
-
-ggplot(CLD,aes(x= fam_foc,y= lsmean,
-               label = .group)) +theme_ms()+
-  geom_point(data = CLD, aes(x = fam_foc, y = lsmean, color = fam_foc),shape  = 15,size   = 4) +
-scale_color_manual(name = "Families",values = c("Convolvulaceae" = "#009E73", "Solanaceae" = "#D55E00", "Brassicaceae" = "#0072B2"))+ggtitle("")+
-  geom_errorbar(aes(ymin  =  lower.CL,ymax  =  upper.CL,  color = fam_foc),
-                width =  0.2,size =  0.9)+ylab("Least square mean")+xlab("Families")+
-  geom_text(nudge_x = c(0, 0, 0), nudge_y = c(0.8, 0.8, 0.8),color   = "black") + theme(legend.position = "none")
-
-```
-
-\newpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=12,fig.width=12,  fig.cap="**Fig.
-S5** Unipartite bidirectional network with asymmetrical effect.
-The lines with the arrow heads connect the impact of foreign pollen (effect size) of each pollen donor species on each recipient species.
-All the arrow heads point to the recipient species of the reciprocal interaction.
-Lines of species that did not have a negative impact are not represented.
-The different nodes and the effect of the donor species on the recipient species appear coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green).
-The intensity of the effect is represented by the line´s size where a larger effect size corresponds to a thicker line and a thinner line to a smaller effect size.
-Species code: BROL: Brassica oleracea, BRRA: Brassica rapa, ERSA: Eruca sativa, SIAL: Sinapis alba, IPAQ: Ipomoea aquatica, IPPU: Ipomoea purpurea, CAAN: Capsicum annuum, PEIN: Petunia integrifolia, SOLY: Solanum lycopersicum, SOME: Solanum melongena."}
-
-library(statnet)
-library(reshape2)
-library(sna)
-library(igraph)
-setwd("~/R_projects/Hp_pollen_experiment")
-
-#######################################
-############ Data preparataion ########
-#######################################
-
-#In this script I'm going to plot the transitivity of the effect oh HP pollen with effect sizes
-effect <- readRDS("Data/RData/matrix_effect_size.RData")
-#Now I convert the few values over 0 to maximum 0 (control)
-effect[effect>0]<-0
-#absolute values so less confusing without negative values
-#So now greater values involve greater effect
-#(opposite way in comparison with negative values as before)
-effect=abs(effect)
-#UNIPARTITE DOUBLE ASSYMETRICAL EFFECT
-G <- graph.adjacency(t(effect),weighted=TRUE,diag=FALSE)
-#plot(G)
-E <- t(apply(get.edgelist(G),1,sort))
-E(G)$curved <- 0
-E(G)[duplicated(E) | duplicated(E,fromLast =TRUE)]$curved <- 0.2
-plot(G, edge.width=E(G)$weight/0.5,  vertex.color=c(rep("#0072B2",2),"#D55E00","#0072B2", rep("#009E73",2),
-              "#D55E00","#0072B2", rep("#D55E00",2)),edge.arrow.size=0.8,edge.color=adjustcolor(c(rep("#0072B2",8),rep("#0072B2",8), rep("#D55E00",7), 
-              rep("#0072B2",9),rep("#009E73",7),rep("#009E73",9),rep("#D55E00",7),rep("#0072B2",8), rep("#D55E00",8), rep("#D55E00",7)), alpha.f = .5))
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=6,fig.width=6, fig.cap="**Fig.
-S6** Graphical representation of the correlation matrix of all the traits measured.
-Positive correlations are displayed in blue and negative in red.
-The intensity, size and colour of the circles are proportional to the correlation coefficient from Pearson’s r."}
-#install.packages("corrplot")
-library(corrplot)
-setwd("~/R_projects/Hp_pollen_experiment")
-#Example
-#I'm going to try to show our traits on this way
-#M <- cor(mtcars)
-#corrplot(M, method = "circle")
-#We can kill two birds with one stone, showing the correlation and all the traits
-traits_all <- read.csv("Data/Csv/traits_all.csv")
-si_index <- readRDS("Data/RData/si_index.RData")
-traits_all$si_index <- si_index
-traits_all=traits_all[,-c(1,2)]
-traits_all=traits_all[,-c(1,7,11)]
-#Change order of ovary width length I rename below in row and colname
-a<-traits_all[,11]
-b<-traits_all[,12]
-traits_all[,11] <-b
-traits_all[,12]<- a
-traits_all<- cor(traits_all)
-
-rownames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen grains/anther", "Number of ovules", "Pollen-ovule ratio",
-                         "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
-                         "Ovary length", "Ovary width", "SI index")
-
-colnames(traits_all)<- c("Selfing rate", "Pollen size", "Pollen grains/anther", "Number of ovules", "Pollen-ovule ratio",
-                "Stigmatic area", "Stigma length", "Stigma width", "Style length", "Style width",
-                "Ovary length", "Ovary width", "SI index")
-
-#corrplot(traits_all, method = "circle")
-#corrplot(traits_all, type = "upper")
-par(mar=c(0,4.1,4.1,2.1))
-corrplot(traits_all, type = "lower", tl.cex = 0.8, cl.cex = 0.8, tl.col = "black", tl.srt = 45)
-
-#Add Compatibility index!
-
-```
-
-\clearpage
 
@@
   theme_minimal()+labs(y="Seed:ovule ratio")+scale_fill_manual(name="Treatments",values=c( "#D55E00","#009E73","#0072B2", "#E69F00"))+theme(plot.title = element_text(face = "bold"),axis.text.x = element_text(face = "italic"))
-
-```
-
-\clearpage
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE,cache=FALSE,fig.height=8,fig.width=7, fig.cap="**Fig.
-S8** Grouped effect sizes (95% confidence intervals) of the different families on each focal species.
-For each species, the grouped effect by family is compared with the control treatment of hand cross pollination with conspecific pollen.
-The control treatment is represented in yellow and vertically intersected with a dashed line through the mean effect size in order to help the visual interpretation of the effect sizes.
-Any value to the left of the vertical dashed line represents a negative impact of foreign pollen.
-The different effect sizes and confidence intervals are coloured by family: Solanaceae (orange), Brassicaceae (blue) and Convolvulaceae (green)."}
-
-library(effsize)
-library(dplyr)
-library(ggplot2)
-library(ggpubr)
-library(cowplot)
-library(gridExtra)
-library(egg)
-library(magrittr)
-library(multipanelfigure)
-library(grid)
-
-setwd("~/R_projects/Hp_pollen_experiment")
-load("Data/RData/some_effect_size_family.RData")
-
-pp1<- ggplot(some_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/soly_effect_size_family.RData")
-
-pp2<- ggplot(soly_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/sial_effect_size_family.RData")
-
-p3<- ggplot(sial_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/pein_effect_size_family.RData")
-
-p4<- ggplot(pein_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ippu_effect_size_family.RData")
-
-p5<- ggplot(ippu_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ipaq_effect_size_family.RData")
-
-p6<- ggplot(ipaq_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/ersa_effect_size_family.RData")
-
-p7<- ggplot(ersa_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/caan_effect_size_family.RData")
-
-p8<- ggplot(caan_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/brra_effect_size_family.RData")
-
-p9<- ggplot(brra_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
-load("Data/RData/brol_effect_size_family.RData")
-
-p10<- ggplot(brol_effect_size, aes(Family,Cohen_d, size=10)) + theme_bw(base_size=10)+ geom_point(size=2,show.legend = FALSE,aes(color=factor(Family))) +
-  geom_linerange(size=0.6,shape=3,linetype=1,show.legend=FALSE, aes(x = Family, ymin = Lower, 
-ymax = Upper,color=factor(Family)))+
-  scale_color_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  scale_fill_manual("Family",values=c("#D55E00",  "#009E73","#0072B2", "#E69F00"))+
-  xlab("") + ylab("Cohen's d") + rotate(ylim = c(-6, 2))+guides(fill=FALSE)+
-  geom_hline(yintercept=0, linetype="dashed", color = "black")
-
- #grid.arrange(p1, p5, p3, p4, nrow=2,ncol=2,top="Solanaceae")
-grid.newpage()
- grid.draw(arrangeGrob(cbind(ggplotGrob(pp1),ggplotGrob(pp2), size="last"),cbind(ggplotGrob(p3),ggplotGrob(p4),size="last"),cbind(ggplotGrob(p5),ggplotGrob(p6), size="last"),cbind(ggplotGrob(p7),ggplotGrob(p8), size="last"),cbind(ggplotGrob(p9),ggplotGrob(p10), size="last"),nrow=5))
-```

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/Procrustes_output.Rmd
reoganization

--- 2019-07-03 Manuscript_draft/Table S4_S5_protest.Rmd
@@
 library(kableExtra)
-load("Data/Table_s4.RData")
+setwd("~/R_projects/Hp_pollen_experiment")
+
+load("Data/RData/Table_s4.RData")
 
@@
 library(kableExtra)
-load("Data/Table_s4.RData")
+setwd("~/R_projects/Hp_pollen_experiment")
+
+load("Data/RData/Table_s4.RData")
 
 Correlation <- c(selfing_pro_sol[6], pollen_size_pro_sol[6], mean_pollen_anther_pro_sol[6], mean_ovules_pro_sol[6], pollen_ovule_ratio_pro_sol[6], stigma_area_pro_sol[6], stigma_length_pro_sol[6], stigma_width_pro_sol[6], style_length_pro_sol[6], style_width_pro_sol[6], ovary_width_pro_sol[6], ovary_length_pro_sol[6], si_index_pro_sol[6])
+
 Correlation<- as.numeric(Correlation)
@@
 library(kableExtra)
-load("Data/Table_s4.RData")
+setwd("~/R_projects/Hp_pollen_experiment")
+
+load("Data/RData/Table_s4.RData")
 
 Correlation <- c(selfing_pro_bra[6], pollen_size_pro_bra[6], mean_pollen_anther_pro_bra[6], mean_ovules_pro_bra[6], pollen_ovule_ratio_pro_bra[6], stigma_area_pro_bra[6], stigma_length_pro_bra[6], stigma_width_pro_bra[6], style_length_pro_bra[6], style_width_pro_bra[6], ovary_width_pro_bra[6], ovary_length_pro_bra[6], si_index_pro_bra[6])
+
 Correlation<- as.numeric(Correlation)
+
 Sum_squares <- c(selfing_pro_bra[3], pollen_size_pro_bra[3], mean_pollen_anther_pro_bra[3], mean_ovules_pro_bra[3], pollen_ovule_ratio_pro_bra[3], stigma_area_pro_bra[3], stigma_length_pro_bra[3], stigma_width_pro_bra[3], style_length_pro_bra[3], style_width_pro_bra[3], ovary_width_pro_bra[3], ovary_length_pro_bra[3],si_index_pro_bra[3])

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/Unused_supp/Protest_plot.Rmd
reoganization

--- 2019-07-10 Manuscript_draft/Protest_plot.Rmd
@@
 
-p1<-ggplot(pro_dat,aes(x=traits,y=pro_cor))+
+p1<-ggplot(pro_dat,aes(x=traits,y=pro_cor))+labs(title="All species",x="", y = "Correlation")+
   geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
@@
         axis.ticks.x=element_blank())
-p2<-ggplot(pro_dat,aes(x=traits,y=sum_squ))+
+p2<-ggplot(pro_dat,aes(x=traits,y=sum_squ))+labs(title="",x="", y = "Sum of squares")+
   geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
@@
         axis.ticks.x=element_blank())
-p3<-ggplot(pro_dat,aes(x=traits,y=signif))+
+p3<-ggplot(pro_dat,aes(x=traits,y=signif))+labs(title="",x="Traits", y = "Significance")+
   geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))
@@
         axis.ticks.x=element_blank())
-p2<-ggplot(pro_dat_sol,aes(x=traits_sol,y=sum_squ_sol))+
-  geom_bar(stat="identity",position="dodge")+theme(axis.title.x=element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())
-p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+
+p3<-ggplot(pro_dat_sol,aes(x=traits_sol,y=signif_sol))+labs(title="",x="Traits", y = "Significance")+
   geom_bar(stat="identity",position="dodge")+theme(axis.text.x=element_text(angle=60,hjust=1))

### 2021-02-15 Supplementary_material/Supplementary_mat_plots/pollen_ratios_plots.Rmd
reoganization

--- 2019-05-22 pollen_family.Rmd
@@
 par(mfrow=c(3,1))
-ratio_sol <-readRDS("Rmd/Data/ratio_sol.RData")
-barplot(ratio_sol,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("C.
-annuum-I.
+ratio_bra <-readRDS("Rmd/Data/ratio_bra.RData")
+barplot(ratio_bra,hor=T, xlim=c(-1,100),ylim=c(-2,7),width = 0.5,col=coul ,space=0.5,border="white",srt=80,las=1,cex.axis=1,cex.names=1,font=3,names=c("E.
+sativa-I.
+purpurea", "B.
+oleracea-I.
+purpurea","B.
+rapa-I.
 purpurea", "S.
-melongena-I.
-aquatica", "P.
-integrifolia-I.
+alba-I.
 aquatica", "S.
-lycopersicum-I aquatica","S.
-melongena-E.
-sativa", "P.
-integrifolia-E.
-sativa", "C.
-annuum-S.
-alba", "S.
-lycopersicum-B.
-rapa"))
+alba-S.
+melongena", "E.
+sativa-P.
+integrifolia", "B.
+rapa-S.
+lycopersicum", "B.
+oleracea-C.
+annuum"))
 abline(v=50,col="black")

### 2021-02-15 Scripts/Analysis/Total_pollen_Stigma_area_corr.R

@@ -1,24 +1,22 @@
+##################################################################################################################################################################
+#Correlation Stigma ~ Pollen deposited on stigma
+##################################################################################################################################################################
 #Here I test for correlation between stigma size and total pollen deposited on the stigma
+total_pollen <- read.csv("Data/Csv/total_pollen.csv") #read data
+total_pollen=total_pollen[,-1]  #prepare data
+colnames(total_pollen)[3] <- "total_pollen" #set new colname
+head(total_pollen) #check data
 
-total_pollen <- read.csv("Data/Csv/total_pollen.csv")
-
-total_pollen=total_pollen[,-1]
-colnames(total_pollen)[3] <- "total_pollen"
-head(total_pollen)
-
-#Now I load the trait table to add stigma size
-
+#Now I load the trait table to add stigma size (I prepare stigma width and area for the corr)
 traits_all <- read.csv("Data/Csv/traits_all.csv", sep=",")
-
-stigma_area <- traits_all[,c(2,10)]
-str(stigma_area)
-
-stigma_area$species=as.character(stigma_area$species)
-stigma_width <- traits_all[,c(2,13)]
-stigma_width$species=as.character(stigma_width$species)
-
-
-
+stigma_area <- traits_all[,c(2,10)] #select columns of interest
+str(stigma_area) #check data
+stigma_area$species=as.character(stigma_area$species) #convert to character
+stigma_width <- traits_all[,c(2,13)] #select columns of interest
+stigma_width$species=as.character(stigma_width$species) #convert to character
+##################################################################################################################################################################
+#Rename columns to merge
+##################################################################################################################################################################
 str(total_pollen)
 total_pollen$focal=as.character(total_pollen$focal)
 unique(total_pollen$focal)
@@ -34,12 +32,16 @@ total_pollen$focal[total_pollen$focal=="White mustard"] <- "Sinapis alba"
 total_pollen$focal[total_pollen$focal=="Water morning glory"] <- "Ipomoea aquatica"
 str(total_pollen)
 colnames(total_pollen)[1] <- "species"
+##################################################################################################################################################################
+#Merge data 
+##################################################################################################################################################################
+test_1 <- merge(total_pollen, stigma_area, by="species")
+test_2 <- merge(total_pollen, stigma_width, by="species")
 
-test <- merge(total_pollen, stigma_area, by="species")
-
-cor.test(test$total_pollen, test$stigma_area, method=c("pearson"))
-
-test <- merge(total_pollen, stigma_width, by="species")
[…]

### 2021-02-15 Scripts/Analysis/Traits_correlogram.R

@@ -1,3 +1,6 @@
+##################################################################################################################################################################
+#Correlation plot between traits
+##################################################################################################################################################################
 #install.packages("corrplot")
 library(corrplot)
 
@@ -5,9 +8,8 @@ library(corrplot)
 M <- cor(mtcars)
 corrplot(M, method = "circle")
 
-#We can kill two birds with one stone, showing the correlation and all the traits
 
-
+#read data
 traits_all <- read.csv("Data/Csv/traits_all.csv")
 si_index <- readRDS("Data/RData/si_index.RData")
 traits_all$si_index <- si_index

### 2021-02-15 Scripts/Analysis/t_test_ratios.R

@@ -1,85 +1,0 @@
-#'m going to compare the pollen proportions among families
-#Read data
-d <- read.csv("Data/Csv/pollen_ratios.csv")
-
-d_pollen <- subset(d, variable=="non_focal_pollen")
-#length(d_pollen$X)
-#confirming length of the data.frame
-#add_manually column with family
-d_pollen$family_focal <- c("S","B","B","B","S", "S", "S", "B", "C", "B", "B", "B", "C", "B", "C",
-                           "S", "S", "C","S","S")
-
-d_pollen$family_non_focal <- c("C","C","C","C","C","C","C","C","S","S","S","S","S","S","B","B","B",
-                               "B","B","B")
-#select column of interest
-d_pollen <- d_pollen[,c(4,7,8)]
-
-c_pollen <- subset(d_pollen, family_non_focal=="C")
-s_b_pollen <- subset(d_pollen, family_non_focal=="B"|family_non_focal=="S")
-s_pollen <- subset(d_pollen, family_non_focal=="S")
-b_pollen <- subset(d_pollen, family_non_focal=="B")
-hist(c_pollen$ratio)
-hist(s_b_pollen$ratio)
-
-t.test(c_pollen$ratio,s_b_pollen$ratio,alternative = "two.sided", var.equal = FALSE)
-#Showing differences between big pollen size and small pollen size families 
-#Convolvulacea compared with solanaceae and brassicaceae
-t.test(s_pollen$ratio,b_pollen$ratio,alternative = "two.sided", var.equal = FALSE)
-t.test(c_pollen$ratio,b_pollen$ratio,alternative = "two.sided", var.equal = FALSE)
-t.test(c_pollen$ratio,s_pollen$ratio,alternative = "two.sided", var.equal = FALSE)
-
-t.test(s_b_pollen$ratio,c_pollen$ratio,alternative = "two.sided", var.equal = FALSE)
-
-
-#recipient species
-c_pollen_focal <- subset(d_pollen, family_focal=="C")
-s_b_pollen_focal <- subset(d_pollen, family_focal=="B"|family_focal=="S")
-s_pollen_focal <- subset(d_pollen, family_focal=="S")
-b_pollen_focal <- subset(d_pollen, family_focal=="B")
-hist(c_pollen_focal$ratio)
-hist(s_b_pollen_focal$ratio)
-
[…]
